### 2013-11-26 paper/paper.tex
First commit for the SFI paper.
This commit includes a bare-bones LaTeX file (where we can write each
section in its own file), as well as the most recent minutes.

%%%%% Beginning of preamble %%%%%
\documentclass[12pt]{article}

%What kind of document (article) and what size
%Packages to load which give you useful commands
\usepackage{amssymb, amsmath, amsthm} 
\usepackage{epsfig,graphicx} 
\usepackage{caption}
\usepackage{subcaption}
\usepackage{authblk}
\usepackage{verbatim}

%Sets the margins
\textwidth = 6.5 in 
\textheight = 9 in 
\oddsidemargin = 0.0 in 
\evensidemargin = 0.0 in 
\topmargin = 0.0 in 
\headheight = 0.0 in 
\headsep = 0.0 in \parskip = 0.2in \parindent = 0.0in

\begin{document} 
\title{Working Title}

% \author[1]{David Darmon}
% \author[2]{Elisa Omodei}
% \author[3]{Cesar O. Flores}
% \author[4]{Lu\'is F. Seoane}
% \author[5]{Kevin Stadler}
% \author[6]{Jody Wright}
% \author[7]{Joshua Garland}
% \author[8]{Nix Barnett}
% \affil[1]{Department of Mathematics, University of Maryland, College Park}
% \affil[2]{ISC-PIF, LaTTiCe-CNRS, \'Ecole Normale Sup\'erieure, Paris}
% \affil[3]{School of Physics, Georgia Institute of Technology, Atlanta}
% \affil[4]{ICREA-Complex Systems Lab, Universitat Pompeu Fabra, Barcelona}
% \affil[5]{School of Philosophy, Psychology and Language Sciences, The University of Edinburgh, Edinburgh}
% \affil[6]{Department of Microbiology and Immunology, University of British Columbia, Vancouver}
% \affil[7]{Department of Computer Science, University of Colorado, Boulder}
% \affil[8]{Department of Mathematics and Complexity Sciences Center, University of California, Davis}

\date{\today} 
\maketitle

\abstract{Lorem ipsum}

\input{parts/intro.tex}
\input{parts/community.tex}

\bibliographystyle{plain}
\bibliography{references}

\end{document}

### 2013-11-26 data/content-free/generate_binary.py

@@ -1,0 +1,40 @@
+import datetime
+import numpy
+
+uid = '456'
+
+def create_binary_ts_from_arrival_times(uid):
+	tweets = [] # A placeholder for the times of the tweets.
+
+	with open('tweet_times_2011/tweet_times_{}.dat'.format(uid)) as ofile:
+		for line in ofile:
+			tweets.append(int(line)) # Read in all of the times of the tweets.
+
+	# Keep track of the total number of seconds elapsed from the reference
+	# start to the reference stop.
+
+	reference_start = datetime.datetime(2011, 4, 25, 9, 24, 58)
+
+	reference_stop = datetime.datetime(2011, 6, 25, 14, 31, 59)
+
+	T = (reference_stop - reference_start).total_seconds()
+
+	# binary is a length T vector with a 0 at index n if 
+	# a Tweet occurred and a 1 otherwise.
+
+	binary = numpy.zeros(T, dtype = 'int8')
+
+	binary[tweets] = 1
+
+	return binary
+
+binary = create_binary_ts_from_arrival_times(uid)
+
+# To save to a file. Though you're probably
+# better just generating binary each time 
+# you need to do any computations rather 
+# than writing and then reading from the file.
+
+# with open('tweet_times_2011/tweet_times_binary_{}.dat'.format(uid), 'w') as wfile:
+# 	for bit in binary:
+# 		wfile.write('{}'.format(bit))

### 2013-11-26 data/network-stats/filter_twitter_dataset.py
Added Elisa's files from Google Drive.

@@ -1,0 +1,148 @@
+#!/usr/bin/env python
+# -*- coding: utf-8 -*-
+import sys
+import igraph
+
+def integers_distribution(input_vector,string):
+	outfile = open(string+'_distribution.txt','w')
+	xmax = max(input_vector)
+	hist_vector_temp = []
+	for i in range(xmax+1):
+		hist_vector_temp.append(0)
+	for i in input_vector:
+		hist_vector_temp[i] += 1
+	for i in range(len(hist_vector_temp)):
+		if hist_vector_temp[i] != 0:
+			outfile.write('%d\t%d\n'%(i,hist_vector_temp[i]))
+	outfile.close()
+
+infile = open('data/_follower_15K_user.txt/_follower_15K_user.txt','r')
+lines = infile.readlines()
+nodes = set(); edges = []; neighbors = {}
+for line in lines:
+	row = line.split()
+	user = row[0]
+	follower = row[2]
+	nodes.add(user); nodes.add(follower)
+	edges.append((user,follower))
+	if user in neighbors: neighbors[user].append(follower)
+	else: neighbors[user] = [follower]
+print 'number of nodes:',len(nodes)
+print 'number of edges:',len(edges)
+
+edges_weights = {}
+
+infile = open('data/retweets-mentions/retweets2011_userid.tsv','r')
+lines = infile.readlines()
+user_hasretweeted = {}
+for u in nodes: user_hasretweeted[u] = 0
+user_wasretweeted = {}
+for u in nodes: user_wasretweeted[u] = 0
+retweets_nodes = set()
+for line in lines:
+	row = line.split('\t')	
+	u1 = row[1]
+	u2 = row[2][:-1]
+	retweets_nodes.add(u1)
+	retweets_nodes.add(u2)
+	if u1 in nodes and u2 in nodes:
+		user_hasretweeted[u1] += 1
+		user_wasretweeted[u2] += 1
+		if (u2,u1) in edges_weights: edges_weights[(u2,u1)] += 1
+		else: edges_weights[(u2,u1)] = 1
+
+infile = open('data/retweets-mentions/mentions2011_userid.tsv','r')
+lines = infile.readlines()
+user_hasmentioned = {}
+for u in nodes: user_hasmentioned[u] = 0
+user_wasmentioned = {}
+for u in nodes: user_wasmentioned[u] = 0
+mentions_nodes = set()
+for line in lines:
[…]

### 2013-12-02 paper/parts/intro.tex
Began drafting an outline of the introduction.

\section{Introduction}

Lorem ipsum.

\cite{schreiber2000measuring}, \cite{ver2012information}, \cite{shalizi2007discovering}, \cite{paninski2003estimation}

Our SFI paper: \cite{darmon2013detecting}

### 2013-12-04 paper/parts/intro.tex
Drafted a first stab at an introduction.

@@
 
-Lorem ipsum.
+Networks play a central role in online social networks like Twitter, Facebook, and Google+.
+These services have become popular largely because of the fact that they allow for the interaction of millions of users in ways restricted by the network each user chooses to be part of.
+Central to this interaction is the concept
 
-\cite{schreiber2000measuring}, \cite{ver2012information}, \cite{shalizi2007discovering}, \cite{paninski2003estimation}
+A large body of work exists on methods for automatic detection of communities within networks \textbf{(lots of references go here, starting with Newman and ending with Fortunato)}.
+All these methods \emph{begin} with a given network, and then attempt to uncover structure present in the network.
+That is, they are agnostic to how the network was constructed.
+Because of this, in answering any sort of question about the communities present in a data set, it is important to begin with a clear picture of the type of community under consideration, and then to tailor the construction of the network and the use of detection algorithms
 
-Our SFI paper: \cite{darmon2013detecting}
+This is especially true for social network analysis.
+In online social networks, `community' could mean many things.
+The simplest definition of community might stem from the network of explicit connections between users on a service (friends, followers, etc.).
+On small time scales, these connections are more or less static, and we might instead determine communities based on who is talking to whom.
+On a more abstract level, a user might consider themselves part of a community of people discuss similar topics.
+We might also define communities as collections of people who exhibit similar behaviors on a service, as in a communities of teenagers vs.\ elderly users.
+We can characterize these types of communities based on the types of questions we might ask about them:
+\begin{itemize}
+	\item \textbf{Structural:} Who are you friends with?
+	\item \textbf{Interaction-based:} Who do you talk to?
+	\item \textbf{Topic-based:} What do you talk about?
+	\item \textbf{Behavioral:}  Who do you act like?
+\end{itemize}
+
+Most previous work on communities in online social networks have focused on these types of communities in isolation. For instance \textbf{(References from links.txt go here.)}
+
+We propose looking at when and how communities motivated by different questions overlap, and whether different approaches to asking the question, ``What community are you in?'' leads to different insights about a social network.
+For example, \textbf{(Put a `worked example' here as to how a single person might belong to various different types of communities, and how these types of communities might reveal different insights.)}
+
+In particular, we can break down our approaches into two broad categories: content-free and content-full.
+The content-free approach is motivated by the question of which individuals act in a concerted manner.
+The main tools for answering this question stem from information theory.
+We consider each user on an online social network as an information processing unit, but ignore the content of their messages \textbf{(Cite Shannon here, with his ideas that the content of the message doesn't matter for information theory?)}.
+We have successfully used this viewpoint to gain insight into local behavior in online social networks~\cite{darmon2013understanding}.
+The information processing framework applies to equally well to spatially extended systems.
+In particular, our current content-free approach was originally motivated by a methodology used to detect functional communities within populations of neurons~\cite{shalizi2007discovering}.
+We have extended this work to social systems, detecting communities on Twitter based on undirected information flow~\cite{darmon2013detecting}.
+Others have successfully applied a similar viewpoint.
+For instance, in~\cite{ver2012information}, the authors use transfer entropy, a measure of directed information flow, to perform link detection on Twitter.
+
+In contrast to the content-free approach, a content-full approach would take into account the \emph{content} being transmitted via an online social network.
+This content has a great deal of social information embedded in it.
+For example, on Twitter, a tweet might have a hashtag (indicating a topic), a mention or reply (indicating a directed communication), or a retweet (indicating endorsement of another user).
+This information allows us to build a more complete picture of the \emph{latent} social network, as opposed to the \emph{explicit} social network indicated by friend and follower links.
+
+Many approaches have explicitly accounted for this information in their definition of a community. \textbf{(Put references to work done using mentions / replies / retweets / hash tags, etc.)}
+
+Wrap up. Probably write this \emph{after} more of our results are in.

### 2013-12-05 code/barnett_process.py
Added transfer entropy code.

@@ -1,0 +1,58 @@
+# A simple model from *Transfer Entropy as a Log-likelihood Ratio*
+# by Lionel Barnett and Terry Bossomaier.
+
+import numpy
+import sys
+import os
+
+N = 500000
+
+epsilons = numpy.zeros(N, dtype = 'int8')
+epsilons[numpy.random.rand(N) < 0.5] = 1
+
+etas = numpy.zeros(N, dtype = 'int8')
+etas[numpy.random.rand(N) < 0.5] = 1
+
+theta = 0.4
+phi   = 0.6
+
+us = numpy.zeros(N, dtype = 'int8')
+us[numpy.random.rand(N) < theta] = 1
+
+vs = numpy.zeros(N, dtype = 'int8')
+vs[numpy.random.rand(N) < phi] = 1
+
+Xs = numpy.zeros(N, dtype = 'int8')
+Xs[0] = numpy.random.randint(2)
+
+Ys = numpy.zeros(N, dtype = 'int8')
+Ys[0] = numpy.random.randint(2)
+
+for t in range(1, N):
+	Xs[t] = us[t]*Ys[t-1] + (1 - us[t])*epsilons[t]
+	Ys[t] = vs[t]*Xs[t-1] + (1 - vs[t])*etas[t]
+
+with open('X.dat', 'w') as wfileX:
+	with open('Y.dat', 'w') as wfileY:
+		with open('Z.dat', 'w') as wfileZ:
+			for t in range(N):
+				Xt = Xs[t]
+				Yt = Ys[t]
+
+				wfileX.write('{}'.format(Xt))
+				wfileY.write('{}'.format(Yt))
+
+				if (Xt == 0) and (Yt == 0):
+					Zt = 0
+				elif (Xt == 0) and (Yt == 1):
+					Zt = 1
+				elif (Xt == 1) and (Yt == 0):
+					Zt = 2
+				elif (Xt == 1) and (Yt == 1):
+					Zt = 3
+				else:
+					print 'Nope!'
+
+					sys.exit(1)
+
+				wfileZ.write('{}'.format(Zt))

### 2013-12-05 code/estimate_TE.py

@@ -1,0 +1,201 @@
+# Code to estimate the transfer entropy directly
+# by assuming a lag k and computing the plug-in
+# estimator for the mass function.
+#
+# DMD, 111113-23-10
+
+import numpy
+
+k = 2 # The lag to consider
+
+alphabet_x = 2
+alphabet_y = 2
+
+dir_name = '../data/te/'
+
+# We'll always use the convention that we're computing
+# TE_{Y -> X}, regardless of the names of the variables.
+
+X_filename = 'ts1.dat'
+Y_filename = 'ts0.dat'
+
+X = map(int, open('{}{}'.format(dir_name, X_filename)).readline().strip())
+Y = map(int, open('{}{}'.format(dir_name, Y_filename)).readline().strip())
+
+# Shorten ts for ease of debugging.
+
+# X = X[:100000]
+# Y = Y[:100000]
+
+# Make a 'null' data set where Y should have impact on X.
+
+# numpy.random.shuffle(Y)
+
+N = len(X)
+
+# The stochastic 'matrix' tracking the conditional
+# distributions of X_{t} | X_{t-k}^{t-1}. We'll store
+# this as a dictionary that takes as a key the 
+# past being conditioned on and returns the counts
+# over each of the symbols.
+
+# We still order the key as (x_{t-1}, x_{t-2}, ..., x_{t-k}).
+
+cond_X = {}
+
+# The marginal distribution of X_{t-k}^{t-1}. We use 
+# the same convention as above for indexing into the
+# array.
+
+dims = []
+
+for ind in range(k):
+	dims.append(alphabet_x)
+
+dims = tuple(dims)
+
+marg_X = numpy.zeros(dims)
+
+# cond_XY and marg_XY are the same as above,
+# but now tracking the distribution of 
+# X_{t} | (X_{t-k}^{t-1}, Y_{t-k}^{t-1}).
+
+cond_XY = {}
+
+dims = []
+
+for ind in range(k):
+	dims.append(alphabet_x)
+
+for ind in range(k):
+	dims.append(alphabet_y)
+
+dims = tuple(dims)
+
+marg_XY = numpy.zeros(dims)
+
[…]

### 2013-12-05 code/extract_timeseries_methods.py

@@ -1,0 +1,31 @@
+import ipdb
+import numpy
+import pylab
+import datetime
+import random
+
+def coarse_resolution(binarized, iresolution = 60):
+    # Takes in a binary time series with a time step
+    # of 1 tick, and returns a binary timeseries
+    # with time step iresolution ticks where
+    # a 0 is returned of no 1s occur in the bin,
+    # and a 1 is otherwise.
+
+    # The number of bins we'll have after coarsening.
+
+    n_coarsebins = numpy.divide(binarized.shape[0], iresolution)
+
+    # An (empty) binary time series to hold the
+    # coarsened time series.
+
+    binarized_coarse = numpy.zeros(n_coarsebins)
+
+    for cind in range(n_coarsebins):
+        binarized_coarse[cind] = numpy.sum(binarized[(cind*iresolution):((cind + 1)*iresolution)])
+    
+    # Convert the *number* of tweets in the time interval
+    # into *whether* a tweet occurs in that time interval.
+    
+    binarized_coarse[binarized_coarse != 0] = 1
+    
+    return binarized_coarse

### 2013-12-11 paper/parts/methods.tex
Added a blurb about transfer entropy.
This blurb is probably too long for a 6 page paper. But we can cut it
down as we need to.

\section{Methodology}

\subsection{Activity-Based Communities and Transfer Entropy}

Suppose we have two stochastic processes $\{X_{t}\}$ and $\{ Y_{t}\}$. Lag-$k$ transfer entropy is defined as 
\begin{align}
	\text{TE}_{Y \to X}^{(k)} &= H\left[X_{t} | X_{t-k}^{t-1}\right] - H\left[X_{t} | X_{t-k}^{t-1}, Y_{t-k}^{t-1}\right],
\end{align}
where
\begin{align}
	H\left[X_{t} | X_{t-k}^{t-1}\right] = - E\left[ \log_{2} p(X_{t} | X_{t-k}^{t-1}) \right]
\end{align}
and 
\begin{align}
	H\left[X_{t} | X_{t-k}^{t-1}, Y_{t-k}^{t-1}\right] = - E\left[ \log_{2} p(X_{t} | X_{t-k}^{t-1}, Y_{t-k}^{t-1}) \right]
\end{align}
are the usual conditional entropies over the conditional (predictive) distributions $p(x_{t} | x_{t-k}^{t-1})$ and $p(x_{t} | x_{t-k}^{t-1}, y_{t-k}^{t-1})$. This formulation was originally developed in~\cite{schreiber2000measuring}, where transfer entropy was proposed as an information theoretic measure of \emph{directed} information flow. Formally, recalling that $H\left[X_{t} | X_{t-k}^{t-1}\right]$ is the uncertainty in $X_{t}$ given its values at the previous $k$ time points, and that $H\left[X_{t} | X_{t-k}^{t-1}, Y_{t-k}^{t-1}\right]$ is the uncertainty in $X_{t}$ given the joint process $\{(X_{t}, Y_{t})\}$ at the previous $k$ time points, transfer entropy measures the reduction in uncertainty by including information about $Y_{t}.$ By the `conditioning reduces entropy' result~\cite{cover2012elements}
\begin{align}
	H[X | Y, Z] \leq H[X | Y],
\end{align}
we can see that transfer entropy is always non-negative, and is zero precisely when $H\left[X_{t} | X_{t-k}^{t-1}\right] = H\left[X_{t} | X_{t-k}^{t-1}, Y_{t-k}^{t-1}\right]$, in which case knowing the past $k$ lags of $Y_{t}$ does not reduce the uncertainty in $X_{t}$. If the transfer entropy is positive, then $\{ Y_{t}\}$ is considered causal for $\{ X_{t}\}$ in the Granger sense~\cite{granger1963economic, barnett2012transfer}.
% More generally we can define the transfer entropy as the limit of lag-$k$ transfer entropies,
% \begin{align}
% 	\text{TE}_{Y \to X} &= \lim_{k \to \infty} \text{TE}_{Y \to X}^{(k)},
% \end{align}
% if the limit exists.

In estimating the transfer entropy from finite data, we will assume that the process $(X_{t}, Y_{t})$ is jointly stationary, which gives us that
\begin{align}
	p(x_{t} | x_{t-k}^{t-1}) = p(x_{k+1} | x_{1}^{k})
\end{align}
and
\begin{align}
	p(x_{t} | x_{t-k}^{t-1}, y_{t-k}^{t-1}) = p(x_{k+1} | x_{1}^{k}, y_{1}^{k})
\end{align}
for all $t$. That is, the predictive distribution only depends on the past, not on when the past is observed\footnote{We really only need \emph{conditional} stationarity~\cite{caires2003nonparametric}, but stationarity implies conditional stationarity}. Given this assumption, we compute estimators for $p(x_{k+1} | x_{1}^{k})$ and $p(x_{k+1} | x_{1}^{k}, y_{1}^{k})$ by `counting': for each possible past $(x_{1}^{k}, y_{1}^{k})$, we count the number of times a future of type $x_{k+1}$ occurs, and normalize. Call these estimators $\hat{p}(x_{k+1} | x_{1}^{k})$ and $p(x_{k+1} | x_{1}^{k}, y_{1}^{k})$. Then the plug-in estimator for the transfer entropy is
\begin{align}
	\widehat{\text{TE}}_{Y \to X}^{(k)} &= \hat{H}\left[X_{t} | X_{t-k}^{t-1}\right] - \hat{H}\left[X_{t} | X_{t-k}^{t-1}, Y_{t-k}^{t-1}\right]
\end{align}
where we use the plug-in estimators $\hat{H}\left[X_{t} | X_{t-k}^{t-1}\right]$ and $\hat{H}\left[X_{t} | X_{t-k}^{t-1}, Y_{t-k}^{t-1}\right]$ for the entropies. It is well known that the plug-in estimator for entropy is biased~\cite{paninski2003estimation}. To account for this bias, we use the Miller-Madow adjustment to the plug-in estimator~\cite{miller1955note}.

\subsection{Interaction-Based Communities and Mention / Retweet Weighting}

### 2013-12-15 code/.#timeTester.py
Initial TE calculator (sparse version)

@@ -1,0 +1,1 @@
+admin@admins-MacBook-Pro-2.local.191

### 2013-12-15 code/determine_edge_weights_sync_bak.py

@@ -1,0 +1,540 @@
+from __future__ import division
+from collections import defaultdict
+import datetime
+import numpy
+import sys
+import os
+import igraph
+import pickle
+import pylab
+import math
+import random
+from itertools import islice
+
+MAKE_BINARY_DICT = False
+USE_10MIN_DICT = True
+Testuid1 = '456'
+Testuid2 = '237962820'
+Testuid3 = '243494256'
+strangeuid ='51319087'
+reference_start = datetime.datetime(2011, 4, 25, 9, 24, 58)
+reference_stop = datetime.datetime(2011, 6, 25, 14, 31, 59)
+#SPARSE_BINARY_HISTORY_PICKLE ="../data/tweet_times_2011/sparse_binary_ts_dict_bin-space-of-10min.p"
+#SPARSE_BINARY_HISTORY_PICKLE ="../data/tweet_times_2011/sparse_binary_ts_dict_bin-space-of-1.p"
+#SPARSE_BINARY_HISTORY_PICKLE ="test_histories_factor_600.p"
+#SPARSE_BINARY_HISTORY_PICKLE ="test_histories_factor_600_set_version.p"
+SPARSE_BINARY_HISTORY_PICKLE = "../data/tweet_times_2011/sparse_binary_ts_dict_bin-space-of-10min_set_version.p"
+T = (reference_stop - reference_start).total_seconds()
+
+factor = 600 #this corresponds to the 10-minute history
+#factor = 1
+#factor = int(5288821/4)
+full_length = int(T/factor)
+
+def take(n, iterable):
+    "Return first n items of the iterable as a list"
+    return list(islice(iterable, n))
+
+def  make_test_set(full_history):
+    test_dict ={}
+    n_items = take(50, full_history.iteritems())
+    #print n_items
+    for user in n_items:
+        print user[0]
+        test_dict[user[0]] = full_history[user[0]]
+
+    pickle.dump(test_dict, open("test_histories_factor_600_set_version.p", "wb" ) )
+
+
+
+def coarsen_sparse_dict(sparse_tweet_history_1_sec, factor):
+    coarse_sparse_dict = {}
+    for user in sparse_tweet_history_1_sec:
+        #print "starting the analysis of user**************:",user
+        coarse_sparse_dict[user]=coarse_sparse_resolution(sparse_tweet_history_1_sec[user],T,factor)
+    return coarse_sparse_dict
+
[…]

### 2013-12-15 code/timeTester.py

@@ -1,0 +1,30 @@
+import timeit
+
+setup = '''
+import random
+import pickle
+SPARSE_BINARY_HISTORY_PICKLE ="test_histories_factor_600.p"
+d = pickle.load(open(SPARSE_BINARY_HISTORY_PICKLE, "rb" ) )
+#random.seed('slartibartfast')
+#s = [random.random() for i in range(1000)]
+#timsort = list.sort
+
+tweets = set()
+tweets2 = []
+for x in d: tweets.add(x);
+##print tweets
+tweets2 = sorted(d.keys());
+#print tweets2
+
+for x in tweets:
+     if x not  in tweets2: print "False"
+
+for x in tweets2:
+     if x not in tweets: print "False"
+'''
+#code = 'a=s[:];timsort(a)'
+code1 = 'for x in d: tweets.add(x);'
+code2 = 'tweets2 = sorted(d.keys());'
+print "code1:", min(timeit.Timer(code1, setup=setup).repeat(7, 1000))
+print "code2:", min(timeit.Timer(code2, setup=setup).repeat(7, 1000))
+

### 2014-01-07 notes/020114-preliminary_comm/preliminary_comm.tex
Added a bunch of code for comparing the coverings and the distribution of the weights across coverings.
This is a massive dump. I really should have done this sooner, and in
smaller chunks!

%
%  untitled
%
%  Created by David Darmon on 2014-01-02.
%  Copyright (c) 2014 __MyCompanyName__. All rights reserved.
%
\documentclass[]{article}

% Use utf-8 encoding for foreign characters
\usepackage[utf8]{inputenc}

% Setup for fullpage use
\usepackage{fullpage}

% Uncomment some of the following if you use the features
%
% Running Headers and footers
%\usepackage{fancyhdr}

% Multipart figures
%\usepackage{subfigure}

% More symbols
%\usepackage{amsmath}
%\usepackage{amssymb}
%\usepackage{latexsym}

% Surround parts of graphics with box
\usepackage{boxedminipage}

% Package for including code in the document
\usepackage{listings}

% If you want to generate a toc for each chapter (use with book)
\usepackage{minitoc}

% This is now the recommended way for checking for PDFLaTeX:
\usepackage{ifpdf}

%\newif\ifpdf
%\ifx\pdfoutput\undefined
%\pdffalse % we are not running PDFLaTeX
%\else
%\pdfoutput=1 % we are running PDFLaTeX
%\pdftrue
%\fi

\ifpdf
\usepackage[pdftex]{graphicx}
\else
\usepackage{graphicx}
\fi
\title{}
\author{  }

\date{}

\begin{document}

\ifpdf
\DeclareGraphicsExtensions{.pdf, .jpg, .tif}
\else
\DeclareGraphicsExtensions{.eps, .jpg}
\fi

\maketitle

\begin{figure}[h!]
  \centering
\includegraphics[width=0.50\textwidth]{Figures/nmi_singletons.pdf}
\caption{The normalized mutual information between the coverings for the communities determined using the structural $(i = j = 0)$ and transfer entropy (with lag $i, j \geq 1$) networks. A value of 1 for the normalized mutual information means that the coverings (i.e. communities) are identical.}
\label{Fig-}
\end{figure}

\begin{figure}[h!]
  \centering
\includegraphics[width=0.50\textwidth]{Figures/comm-oslom0.pdf}
\caption{\textbf{Structural Network:} For each of the non-singleton communities, this shows the size of the community as a function of the rank of the community (in terms of size).}
\label{Fig-}
\end{figure}

\begin{figure}[h!]
  \centering
\includegraphics[width=0.50\textwidth]{Figures/comm-oslom1.pdf}
\caption{\textbf{Lag-1 Transfer Entropy Network:} For each of the non-singleton communities, this shows the size of the community as a function of the rank of the community (in terms of size).}
\label{Fig-}
\end{figure}

\begin{figure}[h!]
  \centering
\includegraphics[width=0.50\textwidth]{Figures/comm-oslom3.pdf}
\caption{\textbf{Lag-3 Transfer Entropy Network:} For each of the non-singleton communities, this shows the size of the community as a function of the rank of the community (in terms of size).}
\label{Fig-}
\end{figure}

\begin{figure}[h!]
  \centering
\includegraphics[width=0.50\textwidth]{Figures/comm-oslom5.pdf}
\caption{\textbf{Lag-5 Transfer Entropy Network:} For each of the non-singleton communities, this shows the size of the community as a function of the rank of the community (in terms of size).}
\label{Fig-}
\end{figure}

\begin{figure}[h!]
  \centering
\includegraphics[width=0.50\textwidth]{Figures/comm78_labels-struc_weights-TE1-dens.pdf}
\caption{The empirical density for the weights on edges internal-to-internal (red), internal-to-external (green), and external-to-internal (blue) for community 78 using the communities determined by the structural network and the weights from the lag-1 transfer entropy community.}
\label{Fig-}
\end{figure}

\end{document}

### 2014-01-07 notes/te_bias/te_bias.tex
Added a bunch of code for comparing the coverings and the distribution of the weights across coverings.
This is a massive dump. I really should have done this sooner, and in
smaller chunks!

\documentclass{article}
\usepackage{graphicx}
\usepackage{amssymb, amsmath, amsthm}

\begin{document}

	When estimating an entropy $H[X]$, call the plug-in / nonparametric maximum likelihood estimator (i.e. the estimator you've been using) $\hat{H}[X]$. Call $\hat{\mathcal{X}}$ the \emph{observed} alphabet of $X$. Then the Miller-Madow estimator of the entropy is
	\begin{align}
		\hat{H}_{MM}[X] = \hat{H}[X] + \frac{|\hat{\mathcal{X}}| - 1}{2 n}
	\end{align}
	where $|\mathcal{\hat{X}}|$ is the number of observed symbols and $n$ was the number of samples used to estimate $\hat{H}[X].$

	Using the definition from line 368 of your code, we see that transfer entropy can be written as
	\begin{align}
		TE_{X \to Y}^{(k)} &= H(Y_t | Y_{t-k}^{t-1}) - H(Y_t | Y_{t-k}^{t-1},X_{t-k}^{t-1}) \\ 
		&= H(Y_t,Y_{t-k}^{t-1})-H(Y_{t-k}^{t-1})-H(Y_t,Y_{t-k}^{t-1},X_{t-k}^{t-1})+H(Y_{t-k}^{t-1},X_{t-k}^{t-1}),
	\end{align}
	where $X_{t-k}^{t-1} = (X_{t - k}, X_{t - (k - 1)}, \ldots, X_{t - 1})$. We would apply the Miller-Madow estimator individually to each of the entropy terms. For example, for the first term, we have
	\begin{align}
		\hat{H}_{MM}[Y_{t}, Y_{t - k}^{t-1}] = \hat{H}_{MM}[Y_{t - k}^{t}] = \hat{H}[Y_{t-k}^{t}] + \frac{|\widehat{\mathcal{Y}^{k+1}}| - 1}{2n},
	\end{align}
	where $|\widehat{\mathcal{Y}^{k+1}}|$ is the number of $(k + 1)$-tuples we actually observe (of the $2^{k + 1}$ possible tuples). Doing this for each term, the overall Miller-Madow estimator for the transfer entropy is
	\begin{align}
		\widehat{TE}_{X \to Y}^{(k)} &= \hat{H}_{MM}(Y_t | Y_{t-k}^{t-1}) - \hat{H}_{MM}(Y_t | Y_{t-k}^{t-1},X_{t-k}^{t-1}) \\ 
		&= \hat{H}_{MM}(Y_t,Y_{t-k}^{t-1})-\hat{H}_{MM}(Y_{t-k}^{t-1})-\hat{H}_{MM}(Y_t,Y_{t-k}^{t-1},X_{t-k}^{t-1})+\hat{H}_{MM}(Y_{t-k}^{t-1},X_{t-k}^{t-1}).
	\end{align}
	One possible problem with this estimator is that it can result in \emph{negative} estimates of entropies. That usually occurs when $\hat{H}$ is very small. I usually record both $\hat{H}$ and $\hat{H}_{MM}$.

\end{document}

### 2014-01-07 code/analyze_weights_by_community_types.R

@@ -1,0 +1,108 @@
+library(np)
+
+# Search type to use:
+# 	labels-struc_weights-TE4
+
+label_type = 'struc'
+# label_type = 'TE4'
+# label_type = 'hashtag'
+# label_type = 'mention-retweet'
+
+# weight_type = 'TE4'
+# weight_type = 'hashtag'
+weight_type = 'mention-retweet'
+
+comms = 0:9
+
+for (comm_label in comms){
+	prefix = paste0('comm', comm_label, '_labels-', label_type, '_weights-', weight_type)
+
+	data_i.to.i = read.csv(paste0('../data/edges-by-type/', prefix, '_i-to-i.dat'), header = FALSE)$V1
+
+	data_e.to.i = read.csv(paste0('../data/edges-by-type/', prefix, '_e-to-i.dat'), header = FALSE)$V1
+
+	data_i.to.e = read.csv(paste0('../data/edges-by-type/', prefix, '_i-to-e.dat'), header = FALSE)$V1
+
+	# Deal with NAs
+
+	data_i.to.i[is.na(data_i.to.i)] = 0
+	data_e.to.i[is.na(data_e.to.i)] = 0
+	data_i.to.e[is.na(data_i.to.e)] = 0
+
+	# xmax = 0.2
+	xmax = max(c(data_i.to.i, data_e.to.i, data_i.to.e))
+
+	pdf(paste0('figures/', prefix, '_i-to-i-ecdf.pdf'))
+	plot(ecdf(data_i.to.i), xlim = c(0, xmax), xlab = 'Weight', ylab = 'ECDF', main = '')
+	dev.off()
+
+	pdf(paste0('figures/', prefix, '_e-to-i-ecdf.pdf'))
+	plot(ecdf(data_e.to.i), xlim = c(0, xmax), xlab = 'Weight', ylab = 'ECDF', main = '')
+	dev.off()
+
+	pdf(paste0('figures/', prefix, '_i-to-e-ecdf.pdf'))
+	plot(ecdf(data_i.to.e), xlim = c(0, xmax), xlab = 'Weight', ylab = 'ECDF', main = '')
+	dev.off()
+
+	pdf(paste0('figures/', prefix, '-dens.pdf'))
+	plot(density(data_i.to.i[data_i.to.i != 0]), col = 'red', xlab = 'Weight', ylab = 'Estimated Density', main = '')#, xlim = c(0, 0.006))
+	lines(density(data_e.to.i[data_e.to.i != 0]), col = 'blue')
[…]

### 2014-01-07 code/compare_weights_between_community_types.py

@@ -1,0 +1,200 @@
+# A script to compare the weights for
+# edges inside / outside of a community
+# where we use a community of type C
+# and a weight of type B.
+# 
+# For example, we might consider the
+# communities based on transfer entropy
+# and the weights based on hashtags.
+# 
+# This allows us to narrow in on the 
+# characteristics of the community
+# types.
+
+#	DMD, 311213-18-25
+
+from itertools import islice
+
+# The community type used to determine the
+# weights on edges.
+
+# weight_type = 'TE4'
+# weight_type = 'hashtag'
+weight_type = 'mention-retweet'
+
+if 'TE' in weight_type:
+	lag = weight_type.split('E')[1]
+	weight_file = '../data/content-free/directedweightsTE/edge_weights_bin10minutes_lag_{}_withMMBIAS.dat'.format(lag)
+elif weight_type == 'hashtag':
+	weight_file = '../data/content-full/twitter_network_hashtags_weighted.txt'
+elif weight_type == 'mention-retweet':
+	weight_file = '../data/content-full/twitter_network_contentfull_weighted_arithmeticmean.txt'
+
+# The community type used to determine the
+# community memberships.
+
+# label_type = 'struc'
+# label_type = 'TE4'
+# label_type = 'hashtag'
+label_type = 'mention-retweet'
+
+if label_type == 'struc':
+	label_file  = 'twitter_unweighted_network.txt_oslo_files'
+elif 'TE' in label_type:
+	lag = label_type.split('E')[1]
+	label_file  = 'edge_weights_bin10minutes_lag_{}_withMMBIAS_edgelist.dat_oslo_files'.format(lag)
+elif label_type == 'hashtag':
+	label_file  = 'twitter_network_hashtags_weighted.txt_oslo_files'
+elif label_type == 'mention-retweet':
+	label_file  = 'twitter_network_contentfull_weighted_arithmeticmean.txt_oslo_files'
+
+# Generate a dictionary of the form
+# {user_id : community_id} from the 
+# communities based on the labels.
+
+full_name = '../oslom_outputs/{}/tp'.format(label_file)
+
+comm_dict = {}
+comm_count = 0
+
+with open(full_name) as ofile:
+	line = ofile.readline()
+
+	while line != '':
+		nodes = ofile.readline().strip().split(' ')
+		
+		for node in nodes:
+			comm_dict[node.strip()] = comm_count
+
[…]

### 2014-01-07 code/dsign-gecmi-e0afc3b45c12/src/alve/gecmi/confusion.cpp

@@ -1,0 +1,372 @@
+
+#include "confusion.hpp"
+
+#include <iostream>
+
+#include <boost/numeric/ublas/io.hpp>
+#include <boost/numeric/ublas/vector.hpp>
+#include <boost/foreach.hpp>
+#include <boost/format.hpp>
+
+// #include <boost/math/distributions/binomial.hpp>
+#include <boost/math/special_functions/beta.hpp>
+
+using std::cout;
+using std::endl;
+
+
+namespace alve { namespace gecmi { 
+
+    // void normalize_events( cm, out_double_mat, out_cols, out_rows ) {{{
+    //    Here `normalized' means just "divided by the total so that sum 
+    //    of frequencies/probabilities be one". It doesn't have anything to 
+    //    do with entropies.
+    void normalize_events( counter_matrix_t const& cm, 
+        importance_matrix_t& out_norm_conf,
+        importance_vector_t& out_norm_cols,
+        importance_vector_t& out_norm_rows
+        )
+    {
+        // First I need to calculate the total number of events
+        importance_float_t total_events = 0.0;
+        BOOST_FOREACH( auto int2size , cm.data() )
+        {
+            total_events += int2size.second ;
+        }
+        // That was easy... now I need to reallocate
+        // the matrix dimensions on the output
+        out_norm_conf.resize( cm.size1(), cm.size2() , false );
+        out_norm_conf.clear();
+
+        // And finally put the numbers there... again,
+        // easy enough
+        BOOST_FOREACH( auto int2size , cm.data() )
+        {
+            importance_float_t p = int2size.second / total_events ;
+            out_norm_conf.data()[ int2size.first ] = p ;
+        }
+
+        // Now time to populate the cols and rows vectors
+        out_norm_cols.resize( cm.size2() );
+        out_norm_cols.clear();
+        out_norm_rows.resize( cm.size1() );
+        out_norm_rows.clear();
+        size_t col_count = cm.size2();
+        BOOST_FOREACH( auto int2p , out_norm_conf.data() )
+        {
+            importance_float_t p = int2p.second ;
+            size_t g = int2p.first;
+            // g = i*n+j
+            size_t j = g % col_count;
+            size_t i = g / col_count;
+            out_norm_cols(j) += p ;
+            out_norm_rows(i) += p ;
+        }
+    } // }}}
+
+    // void normalize_events_with_fails( int_mat, out_double_mat ) {{{
[…]

### 2014-01-07 code/dsign-gecmi-e0afc3b45c12/src/alve/gecmi/deep_complete_simulator.cpp

@@ -1,0 +1,296 @@
+
+// includes {{{
+#include "deep_complete_simulator.hpp"
+
+#include <algorithm>
+#include <iostream> // For debug
+
+#include <boost/random/mersenne_twister.hpp>
+#include <boost/random/uniform_int_distribution.hpp>
+#include <boost/random/uniform_smallint.hpp>
+#include <boost/random/uniform_real.hpp>
+#include <boost/random/variate_generator.hpp>
+#include <boost/optional.hpp>
+
+#include <boost/math/special_functions/gamma.hpp>
+#include <boost/math/special_functions/factorials.hpp>
+#include <boost/math/special_functions/powm1.hpp>
+
+#include <alve/gecmi/representants.hpp>
+#include <alve/gecmi/player_automaton.hpp>
+#include <alve/gecmi/bigfloat.hpp>
+// }}}
+
+namespace alve { namespace gecmi {
+
+using std::cout;
+using std::endl;
+
+//size_t __i_count = 0;
+//size_t __d_count = 0;
+
+//struct __print{
+    //~__print() {
+        //cout << "__i_count " << __i_count << endl;
+        //cout << "__d_count " << __d_count << endl;
+    //};
+//};
+    
+// What's the failure proportion before bailing out... if I get 
+// at least this many failures, an excpetion will be raised.
+#define MAX_ACCEPTABLE_FAILURES 10 
+
+//__print p;
+
+// struct simulation_inner_result_t {{{
+struct simulation_inner_result_t {
+    int first;
+    int second;
+    importance_float_t importance;
+
+    simulation_inner_result_t( 
+        size_t first, size_t second, 
+        importance_float_t importance 
+    ):
+        first( first ) , second( second ) , importance( importance )
+    {
+    }
+
+    // Handy for empty init
+    simulation_inner_result_t() {};
+}; // }}}
+
+struct deep_complete_simulator::pimpl_t {
+    
+    // For random number generation.
+    //
+    //   I need a random number generator that picks up a random vertex 
+    //   in the set of remaining vertices. 
+    //
+    typedef boost::mt19937 base_generator_type;
+    typedef boost::random::uniform_smallint<> coin_distribution_type;
+    typedef boost::variate_generator<base_generator_type&, coin_distribution_type> gen_type;
+    typedef std::vector< importance_float_t > importance_vector_t;
+
+    //representant2appereances_map_t repr2apprs;
+
+    // For keeping the bi-correspondences
+    two_relations_ptr vmb;
[…]

### 2014-01-07 code/eda_edges.py

@@ -1,0 +1,24 @@
+import os
+
+# weight_type = 'transfer-entropy'
+# weight_type = 'hashtag'
+weight_type = 'mention-retweet'
+
+print '\nUsing weights of type {}\n'.format(weight_type)
+
+fname = '../data/topK_{}.dat'.format(weight_type)
+
+num_links = 10
+
+with open(fname) as ofile:
+	ofile.readline() # Skip the header line.
+
+	for ind in range(num_links):
+		from_id, to_id, weight = ofile.readline().strip().split(' ')
+
+		print from_id, to_id, weight
+
+		raw_input("")
+
+		os.system("open 'http://twitter.com/account/redirect_by_id?id={}'".format(from_id))
+		os.system("open 'http://twitter.com/account/redirect_by_id?id={}'".format(to_id))

### 2014-01-07 code/eda_weighted-networks.R

@@ -1,0 +1,62 @@
+# weight.type = 'hashtag'
+# weight.type = 'mention-retweet'
+weight.type = 'transfer-entropy'; lag = 6
+
+if (weight.type == 'hashtag'){
+	data = read.csv('../data/content-full/twitter_network_hashtags_weighted.txt', sep = ' ', header = FALSE)
+
+	weights = data$V3
+} else if (weight.type == 'mention-retweet'){
+	data = read.csv('../data/content-full/twitter_network_contentfull_weighted_arithmeticmean.txt', sep = ' ', header = FALSE)
+
+	weights = data$V3
+} else if (weight.type == 'transfer-entropy'){
+	data = read.csv(paste0('../data/content-free/directedweightsTE/edge_weights_bin10minutes_lag_', lag, '_withMMBIAS.dat'), sep = ',', header = TRUE)[, c(1, 2, 4)]
+
+	weights = data[, 3]
+
+	weights[weights < 0] = 0
+
+	weights[is.na(weights)] = 0
+}
+
+cat(sprintf('\nThe min and max weights are %f and %f.\nThe mean weight is %f and the median weight is %f.\n\n', min(weights), max(weights), mean(weights), median(weights)))
+
+cat(quantile(weights, probs = seq(0, 1, by = 0.05)))
+
+# hist(weights, breaks = 1000)
+
+is.increasing = FALSE
+
+if (is.increasing){
+	weights.sort = order(weights)
+} else {
+	weights.sort = order(weights, decreasing = TRUE)
+}
+
+stop.ind = 1000
+
+# Kludge-y way to see how many of the top stop.ind edges
+# are reciprocal:
+
+# data[weights.sort[seq(1, stop.ind, by = 2)],3] - data[weights.sort[seq(2, stop.ind, by = 2)],3]
+
+# Look at the top stop.ind edges.
+
+data[weights.sort[1:stop.ind], ]
+
+col.names = c('from_id', 'to_id', 'weight')
+
+if (weight.type == 'hashtag'){
+	write.table(data[weights.sort[1:stop.ind], ], file = '../data/topK_hashtag.dat', quote = FALSE, row.names = FALSE, col.names = col.names)
+} else if (weight.type == 'mention-retweet'){
+	write.table(data[weights.sort[1:stop.ind], ], file = '../data/topK_mention-retweet.dat', quote = FALSE, row.names = FALSE, col.names = col.names)
[…]

### 2014-01-07 code/mutual3/compare_coverings.py

@@ -1,0 +1,37 @@
+import subprocess
+import sys
+import numpy
+import pylab
+
+from StringIO import StringIO
+
+# singleton_type = 'singletons'
+singleton_type = 'no_singletons'
+
+file_dir = 'coverings/{}/'.format(singleton_type)
+
+num_types = 9
+
+mis = numpy.ones((num_types, num_types))*numpy.nan
+
+for ind1 in range(0, num_types):
+	fname1 = '{}communitites{}_comp.txt'.format(file_dir, ind1)
+	for ind2 in range(0, num_types):
+		fname2 = '{}communitites{}_comp.txt'.format(file_dir, ind2)
+		sp = subprocess.Popen(['./mutual', fname1, fname2], stdin = subprocess.PIPE, stdout = subprocess.PIPE)
+		sp.wait()
+		mi = float(sp.communicate()[0].split()[1])
+
+		mis[ind1, ind2] = mi
+
+print mis
+
+# mis[mis == 1] = numpy.nan
+# mis[mis == 0] = numpy.nan
+
+pylab.figure()
+pylab.imshow(mis, interpolation = 'nearest', vmin = 0, vmax = 1, cmap = pylab.cm.gray_r)#, extent = (0, num_types, num_types, 0))
+pylab.xlabel('Weighting $j$'); pylab.ylabel('Weighting $i$')
+pylab.colorbar()
+pylab.savefig('nmi_{}.pdf'.format(singleton_type))
+# pylab.show()

### 2014-01-07 oslom_outputs/parse_membership-oslom.py

@@ -1,0 +1,91 @@
+# A script to parse a file created using OSLOM.
+
+#	DMD, 261213-15-48
+
+import pylab
+import numpy
+from itertools import islice
+import sys
+
+# All of the communities (or 'modules') are
+# written into the 'tp' files, which have the format
+# 
+# # module n size: N bs: sig_val
+# # node1, node2, node3, ...
+
+weighted_prefixes = ['edge_weights_bin10minutes_lag_{}_withMMBIAS_edgelist.dat_oslo_files'.format(lag) for lag in range(1, 7)]
+
+prefixes = ['twitter_unweighted_network.txt_oslo_files']
+
+prefixes.extend(weighted_prefixes)
+
+prefixes.extend(['twitter_network_hashtags_weighted.txt_oslo_files', 'twitter_network_contentfull_weighted_arithmeticmean.txt_oslo_files'])
+
+for lag, prefix in enumerate(prefixes):
+	full_name = '{}/tp_without_singletons'.format(prefix)
+
+	comm_dict = {}
+	comm_count = 0
+
+	with open(full_name) as ofile:
+		line = ofile.readline()
+
+		while line != '':
+			nodes = ofile.readline().strip().split(' ')
+			comm_dict[comm_count] = nodes
+
+			comm_count += 1
+
+			line = ofile.readline()
+
+	userid_to_username = {}
+
+	with open('/Users/daviddarmon/Documents/Reference/R/Research/2013/network/tweetpredict/user_lookup/user_lookups/user_lookup-2011.tsv') as ofile:
+		for line in islice(ofile, 1, None): # Skip the first line, which is a header line
+			uid, username = line.strip().split('\t')
+
+			userid_to_username[uid] = username
+
+	comm_sizes = []
+
+	to_file = True
+
+	if to_file:
+		out = open('communities/communitites{}.txt'.format(lag), 'w')
+	else:
+		out = sys.stdout
+
+	for c_ind in range(len(comm_dict)):
+		community = comm_dict[c_ind]
+
+		out.write('Community {} has: \t {} members\n'.format(c_ind, len(community)))
+
+		members = ''
+
+		for member in community:
+			members += '{} '.format(userid_to_username.get(member, 'NULL'))
+
+		comm_sizes.append(len(community))
+
+		out.write(members)
+
+		out.write('\n\n')
+
+
+	ranked_comms = ''
+
[…]

### 2014-01-07 oslom_outputs/parse_membership_for_mutual3-oslom.py

@@ -1,0 +1,76 @@
+# A script to parse a file created using OSLOM to
+# be used with mutual from 
+#
+# 	https://sites.google.com/site/andrealancichinetti/mutual
+#
+
+#	DMD, 291213-22-21
+
+import pylab
+import numpy
+from itertools import islice
+import sys
+
+# All of the communities (or 'modules') are
+# written into the 'tp' files, which have the format
+# 
+# # module n size: N bs: sig_val
+# # node1, node2, node3, ...
+
+weighted_prefixes = ['edge_weights_bin10minutes_lag_{}_withMMBIAS_edgelist.dat_oslo_files'.format(lag) for lag in range(1, 7)]
+
+prefixes = ['twitter_unweighted_network.txt_oslo_files']
+
+prefixes.extend(weighted_prefixes)
+
+prefixes.extend(['twitter_network_hashtags_weighted.txt_oslo_files', 'twitter_network_contentfull_weighted_arithmeticmean.txt_oslo_files'])
+
+for lag, prefix in enumerate(prefixes):
+	# full_name = '{}/tp_without_singletons'.format(prefix)
+	full_name = '{}/tp'.format(prefix)
+
+	comm_dict = {}
+	comm_count = 0
+
+	with open(full_name) as ofile:
+		line = ofile.readline()
+
+		while line != '':
+			nodes = ofile.readline().strip().split(' ')
+			comm_dict[comm_count] = nodes
+
+			comm_count += 1
+
+			line = ofile.readline()
+
+	userid_to_username = {}
+
+	with open('/Users/daviddarmon/Documents/Reference/R/Research/2013/network/tweetpredict/user_lookup/user_lookups/user_lookup-2011.tsv') as ofile:
+		for line in islice(ofile, 1, None): # Skip the first line, which is a header line
+			uid, username = line.strip().split('\t')
+
+			userid_to_username[uid] = username
+
+	comm_sizes = []
+
+	to_file = True
+
+	if to_file:
+		out = open('communities/communitites{}_comp.txt'.format(lag), 'w')
+	else:
+		out = sys.stdout
+
+	for c_ind in range(len(comm_dict)):
+		community = comm_dict[c_ind]
+
+		members = ''
+
+		for member in community:
+			members += '{} '.format(member)
+
+		out.write(members)
+
+		out.write('\n')
+
+	if to_file:
+		out.close()

### 2014-01-07 oslom_outputs/parse_overlap-oslom.py

@@ -1,0 +1,62 @@
+# A script to parse a file created using OSLOM.
+
+#	DMD, 261213-15-48
+
+import pylab
+import numpy
+from itertools import islice
+import sys
+
+# All of the communities (or 'modules') are
+# written into the 'tp' files, which have the format
+# 
+# # module n size: N bs: sig_val
+# # node1, node2, node3, ...
+
+lag = '6'
+prefix = 'edge_weights_bin10minutes_lag_{}_withMMBIAS_edgelist.dat_oslo_files'.format(lag)
+
+# fname = '{}/tp'.format(prefix)
+fname = '{}/tp_without_singletons'.format(prefix)
+
+comm_dict = {} # A dictionary of the form {communityid : nodes}
+comm_count = 0
+
+node_dict = {} # A dictionary of the form {nodeid : communities}
+
+with open(fname) as ofile:
+	line = ofile.readline()
+
+	while line != '':
+		nodes = ofile.readline().strip().split(' ')
+		comm_dict[comm_count] = nodes
+
+		for node in nodes:
+			if node in node_dict:
+				node_dict[node].append(comm_count)
+			else:
+				node_dict[node] = [comm_count]
+
+		comm_count += 1
+
+		line = ofile.readline()
+
+userid_to_username = {}
+
+with open('/Users/daviddarmon/Documents/Reference/R/Research/2013/network/tweetpredict/user_lookup/user_lookups/user_lookup-2011.tsv') as ofile:
+	for line in islice(ofile, 1, None): # Skip the first line, which is a header line
+		uid, username = line.strip().split('\t')
+
+		userid_to_username[uid] = username
+
+num_overlap = 0
+
+for nodeid in node_dict:
+	comms = node_dict[nodeid]
+
+	if len(comms) > 1:
+		print len(comms), userid_to_username[nodeid], comms
+
+		num_overlap += 1
+
+print 'There are {} users that belong to more than one community, of {}.'.format(num_overlap, len(node_dict))

### 2014-01-07 paper/parts/methods.tex
Added AAAI author kit files. Put paper into AAAI 'camera-ready' style.
According to

http://icwsm.org/2014/submitting/guidelines/

we should aim for 8 to 10 pages. We currently have 2.
Minor edit to the paper.
Added Elisa's draft sections to the paper.

@@
 \section{Methodology}
+
+\subsection{Community Detection}
+
+In network theory communities are usually defined as group of nodes more densely connected among each other than with the rest of the network.
+Community detection is a well studied but not yet solved problem, and several different methods and algorithms have been proposed.
+For a complete review of the subject we refer the reader to (\textbf{ref: Fortunato, Santo.
+"Community detection in graphs." Physics Reports 486.3 (2010): 75-174.}).
+In our study we deal with \textit{weighted directed} networks, and we are interested in finding \textit{overlapping} modules, rather than partitions of the network, since people can belong to different social groups: they can be interacting with different groups of people (their college friends, their co-workers, their family, etc), and they can belong to different topical communities (a person can be interested both in cycling and politics and talk about the two topics with different groups of people).
+Most community detection algorithms developed so far are built to find partitions and only very few to find overlapping communities (\textbf{ref: J.
+Baumes, M.K.
+Goldberg, M.S.
+Krishnamoorthy, M.M.
+Ismail, N.
+Preston, Finding communities by clustering a graph into overlapping subgraphs, in: N.
+Guimaraes, P.T.
+Isaias (Eds.), IADIS AC, IADIS, 2005, pp.
+97–104; Palla, Gergely, et al.
+ "Uncovering the overlapping community structure of complex networks in nature and society." Nature 435.7043 (2005): 814-818.; S.
+Zhang, R.-S.
+Wang, X.-S.
+Zhang, Identification of overlapping community structure in complex networks using fuzzy c-means clustering, Physica A 374 (2007) 483–490; Gregory S (2007) An algorithm to find overlapping community structure in networks.
+In: Proceedings of the 11th European Conference on Principles and Practice of Knowledge Discovery in Databases (PKDD 2007).
+Berlin, Germany: Springer-Verlag. pp 91–102.; T. Nepusz, A. Petroczi, L. Negyessy, F. Bazso, Fuzzy communities and the concept of bridgeness in complex networks, Phys. Rev. E 77 (1) (2008) 016107; 
+Lancichinetti A, Fortunato S, Kertesz J (2009) Detecting the overlapping and hierarchical community structure in complex networks. New J Phys 11: 033015.; 
+vans TS, Lambiotte R (2009) Line graphs, link partitions, and overlapping communities. Phys Rev E 80: 016105. 25; Kovacs, Istvan A., et al. (2010) 
+Community landscapes: An integrative approach to determine overlapping network module hierarchy, identify key nodes and predict network dynamics. PloS ONE 5: e12528}). 
+Among these, even fewer can also deal with directed or weighted networks.
+Palla et al.
+clique percolation method can for example take into account these two features, but not both at the same time (\textbf{ref: Palla, Gergely, et al.
+"Uncovering the overlapping community structure of complex networks in nature and society." Nature 435.7043 (2005): 814-818.}).
+Lancichinetti et.
+al recently proposed the first method that is able to deal with all these features and a few more at the same time, called OSLOM (Order Statistics Local Optimization Method) (\textbf{ref: Lancichinetti, A., Radicchi, F., Ramasco, J.
+J., and Fortunato, S.
+(2011).
+Finding statistically significant communities in networks.
+PloS one, 6(4), e18961.}).
+Their method "is based on the local optimization of a fitness function expressing the statistical significance of clusters with respect to random fluctuations" (\textbf{taken from their paper, to rephrase}), and it allowed us to detect overlapping communities on our weighted directed networks.
+
+\subsection{The Dataset}
+
+The data consists of the Twitter statuses of 15000 users over a 9 week period (from April 25th to June 25th 2011).
+The users are embedded in a network collected by performing a breadth-first expansion from a seed user.
+Once the seed user was chosen, the network was expanded to include his/her followers, only including users considered to be active (users who tweeted at least once per day over the past one hundred tweets).
+Network collection continued in this fashion by considering the active followers of the active followers of the seed, and so on.
+Since one of the kind of communities we want to explore is based on the explicit interactions between users, based on retweets and mentions, we filter the dataset in order to take into account only users who make use of this kind of features in their tweets.
+We define en event of outgoing information for a given user $u$ as either a mention made by $u$ of another user in the network, or a retweet by another user of one of $u$'s tweets.
+When we mention someone we are in fact sending him some information, and when we are retweeted it means that the person that retweeted us has received some information from us and is sharing it.
+Symmetrically, we define an event of incoming information for $u$ as either being mentioned, or retweeting another user.
+We filtered the network by eliminating all the users that have in their tweeting history less than 9 outgoing information and 9 incoming information events, i.e.
+less than one event per type per week on average.
+We then further restricted our analysis to the strong giant connected component of the unweighted directed network built from the filtered set of users and whose link represent a user-follower relationship.
+In this study the link is directed from the user to the follower because this is the direction in which the information flows.
+The final network consists of 6917 nodes and 1481131 edges.
+
+\textbf{Show the distribution of the number of mentions / retweets / haghstags / tweets / followers per user ?}
 
@@
 Given this assumption, we compute estimators for $p(x_{k+1} | x_{1}^{k})$ and $p(x_{k+1} | x_{1}^{k}, y_{1}^{k})$ by `counting': for each possible past $(x_{1}^{k}, y_{1}^{k})$, we count the number of times a future of type $x_{k+1}$ occurs, and normalize.
-Call these estimators $\hat{p}(x_{k+1} | x_{1}^{k})$ and $p(x_{k+1} | x_{1}^{k}, y_{1}^{k})$.
+Call these estimators $\hat{p}(x_{k+1} | x_{1}^{k})$ and $\hat{p}(x_{k+1} | x_{1}^{k}, y_{1}^{k})$.
 Then the plug-in estimator for the transfer entropy is
@@
 
-\subsection{Interaction-Based Communities and Mention / Retweet Weighting}
+\section{Interaction-Based Communities and Mention / Retweet Weighting}
+A way of tracking the flow of information through users is by considering two useful features of this social network: mentions and retweets.
+Through mentions users can in fact send a direct message to other users.
+And a retweet means that a piece of information from a user has been captured by a follower and shared with his/her own followers.
+We can therefore define interaction-based communities by weighting the user-follower network with a measure proportional to the number of mentions and retweets between users.
+In more details, for each couple of user-follower $u$ and $f$, we use the arithmetic / harmonic (\textbf{which one?}) mean of the two following numbers:
+\begin{equation}
+\frac{\mbox{\# mentions of }f \mbox{ by }u}{\mbox{\# total mentions of }f}
+\end{equation}
+and
+\begin{equation}
+\frac{\mbox{\# retweets of }u \mbox{ by }f}{\mbox{\# total retweets made by }f} \mbox{ .}
+\end{equation}
+
+\section{Topic-based Communities and Hashtag Weighting}
+
+Another kind of community is the one based on the content of the tweets, and relies on the idea of finding people that talk about the same things.
+In order to detect this kind of communities, we weight the edges of the user-follower network through a measure based on the number of common hashtags between the two users.
+Hashtags are in fact a good proxy for this, since they are explicitly meant to be key-words indicating a particular topic.
+Moreover they are widely used and straightforwardly detectable.
+We characterize each user $u$ by a vector $\vec{h}(u)$ of length equal to the number of hashtags in the dataset, and whose elements are defined as
+\begin{equation}
+h_i(u) = n_i(u) * \log{ \frac{N}{n_i} }
+\end{equation}
+where $n_i(u)$ is the frequency of the hashtag $i$ in the set of user $u$'s tweets, $N$ is the total number of users, and $n_i$ is the number of users that have used the hashtag $i$ in their tweets.
+This adapted $tf-idf$ measure (\textbf{ref: Salton, Gerard, and Michael J.
+McGill.
+"Introduction to modern information retrieval." (1986).}) captures the importance of a hashtag in the users's tweets through the first factor, but at the same time smooths it through the second factor by giving less importance to hashtags that are too widely used (as $\frac{N}{n_i}$ approaches one, its logarithm approaches zero).
+For each couple of user linked in the user-follower network, we then compute the cosine similarity of their respective vectors, and assign the obtained value as the weight of the directed edge(s) connecting them.
+This weight captures therefore the similarity between users in terms of topic discussed in their tweets.

### 2014-01-07 code/analyze_weights_by_community_types.R
Modified the code for investigating weights-by-label.

@@ -1,16 +1,18 @@
 library(np)
 
 # Search type to use:
-# 	labels-struc_weights-TE4
+# 	labels-BLANK_weights-BLANK
+#
+# Ex: labels-struc_weights-TE4
 
-label_type = 'struc'
+# label_type = 'struc'
 # label_type = 'TE4'
 # label_type = 'hashtag'
-# label_type = 'mention-retweet'
+label_type = 'mention-retweet'
 
-# weight_type = 'TE4'
+weight_type = 'TE4'
 # weight_type = 'hashtag'
-weight_type = 'mention-retweet'
+# weight_type = 'mention-retweet'
 
 comms = 0:9
 
@@ -44,12 +46,12 @@ for (comm_label in comms){
 	plot(ecdf(data_i.to.e), xlim = c(0, xmax), xlab = 'Weight', ylab = 'ECDF', main = '')
 	dev.off()
 
-	pdf(paste0('figures/', prefix, '-dens.pdf'))
-	plot(density(data_i.to.i[data_i.to.i != 0]), col = 'red', xlab = 'Weight', ylab = 'Estimated Density', main = '')#, xlim = c(0, 0.006))
-	lines(density(data_e.to.i[data_e.to.i != 0]), col = 'blue')
-	lines(density(data_i.to.e[data_i.to.e != 0]), col = 'green')
-	legend('topright', c('Internal-to-Internal', 'External-to-Internal', 'Internal-to-External'), col = c('red', 'blue', 'green'), lty = rep(1, 3))
-	dev.off()
+	# pdf(paste0('figures/', prefix, '-dens.pdf'))
+	# plot(density(data_i.to.i[data_i.to.i != 0]), col = 'red', xlab = 'Weight', ylab = 'Estimated Density', main = '')#, xlim = c(0, 0.006))
+	# lines(density(data_e.to.i[data_e.to.i != 0]), col = 'blue')
+	# lines(density(data_i.to.e[data_i.to.e != 0]), col = 'green')
+	# legend('topright', c('Internal-to-Internal', 'External-to-Internal', 'Internal-to-External'), col = c('red', 'blue', 'green'), lty = rep(1, 3))
+	# dev.off()
 
 	data_all = c(data_i.to.i, data_e.to.i, data_i.to.e)
 
@@ -61,6 +63,8 @@ for (comm_label in comms){
 
 	library(ggplot2)
 
[…]

### 2014-01-07 code/analyze_weights_by_community_types.R
Added a bunch more figures.

@@ -7,12 +7,12 @@ library(np)
 
 # label_type = 'struc'
 # label_type = 'TE4'
-# label_type = 'hashtag'
-label_type = 'mention-retweet'
+label_type = 'hashtag'
+# label_type = 'mention-retweet'
 
-weight_type = 'TE4'
+# weight_type = 'TE4'
 # weight_type = 'hashtag'
-# weight_type = 'mention-retweet'
+weight_type = 'mention-retweet'
 
 comms = 0:9
 
@@ -63,11 +63,11 @@ for (comm_label in comms){
 
 	library(ggplot2)
 
-	cat(sprintf('\n\nFor community %g:\n\nThe mean %s weights internal-to-internal, external-to-internal, and internal-to-external are\n%f\n%f\n%f\n\n', comm_label, weight_type, mean(data_i.to.i), mean(data_e.to.i), mean(data_i.to.e)))
+	cat(sprintf('\n\nFor %s community %g:\n\nThe mean %s weights internal-to-internal, external-to-internal, and internal-to-external are\n%f\n%f\n%f\n\n', label_type, comm_label, weight_type, mean(data_i.to.i), mean(data_e.to.i), mean(data_i.to.e)))
 
 	# For mention-retweet, we have to deal with a *lot* of zero weights.
 
-	if (weight_type == 'mention-retweet'){
+	# if (weight_type == 'mention-retweet'){
 		num.nonzero_i.to.i = sum(data_i.to.i != 0)
 		num.nonzero_e.to.i = sum(data_e.to.i != 0)
 		num.nonzero_i.to.e = sum(data_i.to.e != 0)
@@ -86,7 +86,7 @@ for (comm_label in comms){
 			data_i.to.e = data_i.to.e[-which(data_i.to.e == 0)]
 		}
 		
-	}
+	# }
 
 	dat <- data.frame(xx = c(data_i.to.i, data_e.to.i, data_i.to.e),yy = c(rep(letters[1], length(data_i.to.i)), rep(letters[2], length(data_e.to.i)), rep(letters[3], length(data_i.to.e))))
 

### 2014-01-07 paper/parts/intro.tex
Modified paper to be anonymous.
As per the Anonymity guidelines here:

http://icwsm.org/2014/submitting/guidelines/

@@
 We consider each user on an online social network as an information processing unit, but ignore the content of their messages \textbf{(Cite Shannon here, with his ideas that the content of the message doesn't matter for information theory?)}.
-We have successfully used this viewpoint to gain insight into local behavior in online social networks~\cite{darmon2013understanding}.
-The information processing framework applies to equally well to spatially extended systems.
+This viewpoint has been successfully applied to gain insight into local behavior in online social networks~\cite{darmon2013understanding}.
+The information processing framework applies equally well to spatially extended systems.
 In particular, our current content-free approach was originally motivated by a methodology used to detect functional communities within populations of neurons~\cite{shalizi2007discovering}.
-We have extended this work to social systems, detecting communities on Twitter based on undirected information flow~\cite{darmon2013detecting}.
-Others have successfully applied a similar viewpoint.
-For instance, in~\cite{ver2012information}, the authors use transfer entropy, a measure of directed information flow, to perform link detection on Twitter.
+This approach has been extended to social systems, detecting communities on Twitter based on undirected information flow~\cite{darmon2013detecting}.
+Others have successfully applied a similar viewpoint using transfer entropy, a measure of directed information flow, to perform link detection on Twitter~\cite{ver2012information}.
 

### 2014-01-07 paper/parts/results.tex
Modified paper to be anonymous.
As per the Anonymity guidelines here:

http://icwsm.org/2014/submitting/guidelines/

\section{Results}

% \begin{figure}[h!]
%   \centering
% \includegraphics[width=0.50\textwidth]{figures/edge-types.eps}
% \caption{Lorem ipsum.}
% \label{Fig-edge_types}
% \end{figure}

### 2014-01-07 paper/parts/methods.tex
Unify the notation for the weights across the community types.

@@
 
-Suppose we have two stochastic processes $\{X_{t}\}$ and $\{ Y_{t}\}$. Lag-$k$ transfer entropy is defined as 
+We can view the behavior of a user $u$ on Twitter as a point process, where at any instant $t$ the user has either emitted a tweet ($X_{t}(u) = 1$) or remained silent ($X_{t}(u) = 0$).
+This is the view of a users dynamics taken in \cite{ver2012information} and \cite{darmon2013understanding}.
+Thus, we reduce all of the information generated by a user on Twitter to a time series $\{ X_{t}(u)\}$ where $t$ ranges over the time interval for which we have data (9 weeks in this case).
+Because status updates are only collected in discrete, 1-second time intervals, it is natural to consider the only the discrete times $t = 1 \text{ s}, 2 \text{ s}, \ldots, $ relative to a reference time.
+We can then compute the flow of information between two users $u$ and $v$ by computing the transfer entropy between their time series $X_{t}(u)$ and $X_{t}(v).$
+
+Let $\{X_{t}\}$ and $\{ Y_{t}\}$ be two strong-sense stationary stochastic processes.
+We use the notation $X_{t-k}^{t}$ to denote the values of the stochastic process from time $t-k$ to time $t$, $X_{t-k}^{t} = (X_{t-k}, X_{t-(k-1)}, \ldots, X_{t - 1}, X_{t})$.
+The lag-$k$ transfer entropy of $Y$ on $X$ is defined as
 \begin{align}
@@
 This formulation was originally developed in~\cite{schreiber2000measuring}, where transfer entropy was proposed as an information theoretic measure of \emph{directed} information flow.
-Formally, recalling that $H\left[X_{t} | X_{t-k}^{t-1}\right]$ is the uncertainty in $X_{t}$ given its values at the previous $k$ time points, and that $H\left[X_{t} | X_{t-k}^{t-1}, Y_{t-k}^{t-1}\right]$ is the uncertainty in $X_{t}$ given the joint process $\{(X_{t}, Y_{t})\}$ at the previous $k$ time points, transfer entropy measures the reduction in uncertainty by including information about $Y_{t}.$ By the `conditioning reduces entropy' result~\cite{cover2012elements}
+Formally, recalling that $H\left[X_{t} | X_{t-k}^{t-1}\right]$ is the uncertainty in $X_{t}$ given its values at the previous $k$ time points, and that $H\left[X_{t} | X_{t-k}^{t-1}, Y_{t-k}^{t-1}\right]$ is the uncertainty in $X_{t}$ given the joint process $\{(X_{t}, Y_{t})\}$ at the previous $k$ time points, transfer entropy measures the reduction in uncertainty of $X_{t}$ by including information about $Y_{t-k}^{t-1},$ controlling for the information in $X_{t - k}^{t-1}$.
+By the `conditioning reduces entropy' result~\cite{cover2012elements}
 \begin{align}
@@
 we can see that transfer entropy is always non-negative, and is zero precisely when $H\left[X_{t} | X_{t-k}^{t-1}\right] = H\left[X_{t} | X_{t-k}^{t-1}, Y_{t-k}^{t-1}\right]$, in which case knowing the past $k$ lags of $Y_{t}$ does not reduce the uncertainty in $X_{t}$.
-If the transfer entropy is positive, then $\{ Y_{t}\}$ is considered causal for $\{ X_{t}\}$ in the Granger sense~\cite{granger1963economic, barnett2012transfer}.
+If the transfer entropy is positive, then $\{ Y_{t}\}$ is considered causal for $\{ X_{t}\}$ in the Granger sense~\cite{granger1963economic}.
 % More generally we can define the transfer entropy as the limit of lag-$k$ transfer entropies,
@@
 
+For the communities based on transfer entropy, we weight each edge from a user $u$ to a follower $f$ by the estimated transfer entropy of the user $u$ on $f$, 
+\begin{align}
+	w_{u \to f}^{\text{TE}(k)} = \widehat{\text{TE}}_{X(u) \to X(f)}^{(k)}.
+\end{align}
+
 \section{Interaction-Based Communities and Mention / Retweet Weighting}
@@
 \end{equation}
+For the communities based on mention-retweets, we weight each edge from a user $u$ to a follower $f$ by 
+\begin{align}
+	w_{u \to f}^{\text{MR}} = \frac{1}{2}\left(\frac{\mbox{\# mentions of }f \mbox{ by }u}{\mbox{\# total mentions of }f} + \frac{\mbox{\# retweets of }u \mbox{ by }f}{\mbox{\# total retweets made by }f}\right).
+\end{align}
 
@@
 where $n_i(u)$ is the frequency of the hashtag $i$ in the set of user $u$'s tweets, $N$ is the total number of users, and $n_i$ is the number of users that have used the hashtag $i$ in their tweets.
-This adapted $tf-idf$ measure (\textbf{ref: Salton, Gerard, and Michael J.
+This adapted term frequency--inverse document frequency (tf-idf) measure (\textbf{ref: Salton, Gerard, and Michael J.
 McGill.
@@
 For each couple of user linked in the user-follower network, we then compute the cosine similarity of their respective vectors, and assign the obtained value as the weight of the directed edge(s) connecting them.
-This weight captures therefore the similarity between users in terms of topic discussed in their tweets.
+This weight captures the similarity between users in terms of topic discussed in their tweets.
+Thus, for communities based on hashtag similarity, we weight each edge from a user $u$ to a follower $f$ by
+\begin{align}
+	w_{u \to f}^{\text{HT}} = \frac{\vec{h}(u) \cdot \vec{h}(f)}{||\vec{h}(u)|| \ \ ||\vec{h}(f)||}.
+\end{align}

### 2014-01-07 paper/parts/results.tex
Unify the notation for the weights across the community types.

@@
 
-% \begin{figure}[h!]
-%   \centering
-% \includegraphics[width=0.50\textwidth]{figures/edge-types.eps}
-% \caption{Lorem ipsum.}
-% \label{Fig-edge_types}
-% \end{figure}
+\begin{figure}[h!]
+  \centering
+\includegraphics[width=0.50\textwidth]{figures/nmi_no_singletons.pdf}
+\caption{The normalized mutual information between the communities using the different weightings.
+Weighting 0 corresponds to the structural (binary weighting) network, weightings 1 through 6 correspond to the weighting using the transfer entropy with lag 1 through 6, weighting 7 corresponds to the hashtag similarity, and weighting 8 corresponds to the retweet-mention weighting.
+Values of normalized mutual information close to 1 indicate similarity in the community structure, while values close to 0 indicate dissimilarity.
+The normalized mutual information is computed with the singletons removed.}
+\label{Fig-compare_coverings}
+\end{figure}
+
+\begin{figure}[h!]
+  \centering
+\includegraphics[width=0.50\textwidth]{figures/edge-types.eps}
+\caption{An example of the edges considered in determining the edge weight distribution for a given community (the focal community is in yellow).
+We focus on the internal-to-internal (red), internal-to-external (green), and external-to-internal (blue) edges.
+For a given focal community, all other edges (grey) are not considered.}
+\label{Fig-edge_types}
+\end{figure}

### 2014-01-08 code/eda_qual-comm.py
Added file for doing qualitative exploratory data analysis on the communities.

@@ -1,0 +1,66 @@
+import os
+import numpy
+
+# The weights used to determine the community 
+# labels.
+
+# label_type = 'struc'
+# label_type = 'TE4'
+# label_type = 'hashtag'
+label_type = 'mention-retweet'
+
+print '\nUsing weights of type {}\n'.format(label_type)
+
+if label_type == 'struc':
+	label_file  = 'twitter_unweighted_network.txt_oslo_files'
+elif 'TE' in label_type:
+	lag = label_type.split('E')[1]
+	label_file  = 'edge_weights_bin10minutes_lag_{}_withMMBIAS_edgelist.dat_oslo_files'.format(lag)
+elif label_type == 'hashtag':
+	label_file  = 'twitter_network_hashtags_weighted.txt_oslo_files'
+elif label_type == 'mention-retweet':
+	label_file  = 'twitter_network_contentfull_weighted_arithmeticmean.txt_oslo_files'
+
+full_name = '../oslom_outputs/{}/tp_without_singletons'.format(label_file)
+
+# Generate a dictionary of the form
+# {community_id : [userid1, userid2, ...]}
+# from the communities based on the labels.
+
+comm_dict = {}
+comm_count = 0
+
+comm_sizes = []
+
+with open(full_name) as ofile:
+	line = ofile.readline()
+
+	while line != '':
+		nodes = ofile.readline().strip().split(' ')
+		
+		comm_dict[comm_count] = nodes
+
+		comm_count += 1
+
+		comm_sizes.append(len(nodes))
+
+		line = ofile.readline()
+
+
+# Get out the ranking, in size, of the communities,
+# from smallest to largest.
+
+comm_sorted = numpy.argsort(comm_sizes)
+
+# comm_id = comm_sorted[-1]
+comm_id = comm_sorted[0]
+
+print 'Community {} using the weight type {} has {} members.'.format(comm_id, label_type, len(comm_dict[comm_id]))
+
+at_a_time = 5 # Open this many at a time.
+
+for ind, node in enumerate(comm_dict[comm_id]):
+	os.system("open 'http://twitter.com/account/redirect_by_id?id={}'".format(node))
+
+	if (ind+1)%at_a_time == 0:
+		raw_input("")

### 2014-01-08 paper/parts/methods.tex
Updated paper.
Added note on the coarsening done for the transfer entropy computation,
and added some references for the normalized information comparison.

@@
 We can view the behavior of a user $u$ on Twitter as a point process, where at any instant $t$ the user has either emitted a tweet ($X_{t}(u) = 1$) or remained silent ($X_{t}(u) = 0$).
-This is the view of a users dynamics taken in \cite{ver2012information} and \cite{darmon2013understanding}.
+This is the view of a user's dynamics taken in \cite{ver2012information} and \cite{darmon2013understanding}.
 Thus, we reduce all of the information generated by a user on Twitter to a time series $\{ X_{t}(u)\}$ where $t$ ranges over the time interval for which we have data (9 weeks in this case).
@@
 
+Operationally, we expect users to interact with Twitter on a human time scale, and thus the natural one-second time resolution is too fine.
+We coarsen each time series by considering non-overlapping time intervals ten minutes in length.
+For each time interval, we record a 1 if the user has tweeted during that time interval, and a 0 if they have not.
+Thus, the new coarsened time series now captures whether or not the user has been active on Twitter over any given ten minute time interval in our data set.
+We then compute the transfer entropy on these coarsened time series taking $k$ to range from 1 to 6, which corresponds to a lag of ten minutes to an hour.
+
 \section{Interaction-Based Communities and Mention / Retweet Weighting}

### 2014-01-08 paper/parts/results.tex
Updated paper.
Added note on the coarsening done for the transfer entropy computation,
and added some references for the normalized information comparison.

@@
 \section{Results}
+
+\subsection{Community Statistics (? A better title should go here.)}
+
+Discuss the basic properties of the various types of communities: distribution of sizes, number of singletons, etc.
+
+\subsection{Comparing Community-Types with Normalized Mutual Information}
+
+Because OSLOM detects \emph{coverings} rather than \emph{partitions} of users, standard cluster comparison methods like variation of information~\cite{meilua2003comparing} are not appropriate.
+Instead, we use a generalized variation of information measure, the normalized information, first introduced in~\cite{lancichinetti2009detecting}.
+\textbf{TK: Etc.
+Put more here about NMI, what it does, and how to interpret it.}
+
+The normalized mutual information between the various community-types are shown in Figure~\ref{Fig-compare_coverings}.
 
@@
   \centering
-\includegraphics[width=0.50\textwidth]{figures/nmi_no_singletons.pdf}
+\includegraphics[width=0.50\textwidth]{figures/nmi_singletons.pdf}
 \caption{The normalized mutual information between the communities using the different weightings.
-Weighting 0 corresponds to the structural (binary weighting) network, weightings 1 through 6 correspond to the weighting using the transfer entropy with lag 1 through 6, weighting 7 corresponds to the hashtag similarity, and weighting 8 corresponds to the retweet-mention weighting.
+Weighting 0 corresponds to the structural (binary weighting) network, weightings 1 through 6 correspond to the weighting using the transfer entropy with lag 1 through 6, weighting 7 corresponds to the hashtag similarity, and weightings 8, 9, and 10 correspond to the mention, retweet, and mention-retweet weightings.
 Values of normalized mutual information close to 1 indicate similarity in the community structure, while values close to 0 indicate dissimilarity.
@@
 \end{figure}
+
+\subsection{Comparing Different Flows Across Different Community-Types}
 

### 2014-01-08 code/mutual3/compare_coverings.py

@@ -5,12 +5,12 @@ import pylab
 
 from StringIO import StringIO
 
-# singleton_type = 'singletons'
-singleton_type = 'no_singletons'
+singleton_type = 'singletons'
+# singleton_type = 'no_singletons'
 
 file_dir = 'coverings/{}/'.format(singleton_type)
 
-num_types = 9
+num_types = 11
 
 mis = numpy.ones((num_types, num_types))*numpy.nan
 

### 2014-01-08 oslom_outputs/parse_membership_for_mutual3-oslom.py

@@ -10,6 +10,26 @@ import pylab
 import numpy
 from itertools import islice
 import sys
+import copy
+
+##################################################
+# Option:
+#
+include_singletons = False
+include_orphans = False # Whether or not to include those nodes that end up disconnected from the network
+#
+##################################################
+
+
+# Get out the userids from the full structural network.
+
+user_seen_gold = {}
+
+with open('../data/network-stats/filtered_userids.txt') as ofile:
+	for line in ofile:
+		uid = line.strip()
+
+		user_seen_gold[uid] = 0
 
 # All of the communities (or 'modules') are
 # written into the 'tp' files, which have the format
@@ -23,11 +43,15 @@ prefixes = ['twitter_unweighted_network.txt_oslo_files']
 
 prefixes.extend(weighted_prefixes)
 
-prefixes.extend(['twitter_network_hashtags_weighted.txt_oslo_files', 'twitter_network_contentfull_weighted_arithmeticmean.txt_oslo_files'])
+prefixes.extend(['twitter_network_hashtags_weighted.txt_oslo_files', 'twitter_network_mentions.txt_oslo_files', 'twitter_network_retweets.txt_oslo_files', 'twitter_network_contentfull_weighted_arithmeticmean.txt_oslo_files'])
 
 for lag, prefix in enumerate(prefixes):
-	# full_name = '{}/tp_without_singletons'.format(prefix)
-	full_name = '{}/tp'.format(prefix)
+	user_seen_cur = copy.copy(user_seen_gold)
+
+	if include_singletons:
+		full_name = '{}/tp'.format(prefix)
+	else:
+		full_name = '{}/tp_without_singletons'.format(prefix)
 
 	comm_dict = {}
 	comm_count = 0
@@ -66,11 +90,19 @@ for lag, prefix in enumerate(prefixes):
 		members = ''
 
 		for member in community:
+			user_seen_cur[member] = 1
 			members += '{} '.format(member)
 
 		out.write(members)
 
 		out.write('\n')
+
+	if include_orphans:
+		for userid in user_seen_cur:
+			if user_seen_cur[userid] == 0:
+				out.write('{}\n'.format(userid))
+
+
 
 	if to_file:
 		out.close()

### 2014-01-08 paper/parts/results.tex
Added a rough analysis of the NMI figure.

@@
 Because OSLOM detects \emph{coverings} rather than \emph{partitions} of users, standard cluster comparison methods like variation of information~\cite{meilua2003comparing} are not appropriate.
-Instead, we use a generalized variation of information measure, the normalized information, first introduced in~\cite{lancichinetti2009detecting}.
+Instead, we use a generalization of variation of information measure first introduced in~\cite{lancichinetti2009detecting}, the normalized information.
 \textbf{TK: Etc.
@@
 The normalized mutual information between the various community-types are shown in Figure~\ref{Fig-compare_coverings}.
+We see that similarity between the coverings is dictated by the generic covering type, with distinct community structure between the structural, activity-based, and interaction-based communities.
+Interestingly, the communities resulting from the different weightings are all more similar to each other than to the structural communities from the unweighted network.Also note that the communities based on the hashtag similarities are different from both the activity-based and mention-retweet-based communities.
 

### 2014-01-08 code/.#timeTester.py
Updating transfer code

@@ -1,1 +1,0 @@
-admin@admins-MacBook-Pro-2.local.191

### 2014-01-08 code/determine_edge_weights.py

@@ -197,79 +197,24 @@ def H_transfer_entropy(prob_mass_function):
         H += prob_mass_function[perm]*numpy.log2(prob_mass_function[perm])
     return -H
 
-def joint_mass_function(XT,YT):
-    #This should calculate the joint mass funciton of three variables
-    #In particular P(X_{t-1},Y_{t-1},Yt)
-    #   XT should be the  sparse_binary_tweet history of the followed_by
-    #   YT should be the sparse_binary_tweet history of the follower. 
-    #   we then form a tuple with(X_{t-1},Y_{t-1},Y_t) =((0,1),(1,1),0)
-    #   in the simple case this is ((0),(1),0). Each element in the lag adds a new symbol
-    #   to the x_t-1 random variable alphabet
-    #   full_length = 
-    counts = defaultdict(int)
-
-    nonzero_count = 0
-    for y in YT:
-        #print y,y-1,
-        yt = (1)
-        #yt_1 = (1)
-        if y-1 in YT:
-            yt_1 = 1
-        else:
-            yt_1 = 0
-        if y-1 in XT:
-            xt_1 = (1)
-        else:
-            xt_1 = (0)
-        stencil = (xt_1,yt_1,yt)
-        #print(stencil),(y-1,y-1,y)
-        nonzero_count +=1
-        counts[stencil] +=1
-        if y+1 not in YT:
-            yt = (0)
-            yt_1 = (1)
-            if y in XT:
-                xt_1 = (1)
-            else:
-                xt_1 = (0)
-            stencil = (xt_1,yt_1,yt)
-            #print(stencil),(y,y,y+1)
-            nonzero_count +=1
-            counts[stencil] +=1
-    for xt in XT:
-        #print "xt",xt
-        if xt not in YT and xt+1 not in YT:
-            #print(xt)
-            xt_1 = (1)
-            yt_1 = (0)
-            yt = 0
-            stencil = (xt_1,yt_1,yt)
-            #print(stencil),xt
-            counts[stencil] +=1
-            nonzero_count +=1
-
-    zero_stencil = ((0),(0),0)
-    counts[zero_stencil] = full_length-nonzero_count
-    #print(full_length)
-    #print "Tweets for X:",len(XT)
-    #print "Tweet History for X:",XT
-    #print "Tweet History for Y:", YT
-    #print "Tweets for Y:",len(YT)
-    #print(counts)
-    full_joint_prob_mass_func = {}
[…]

### 2014-01-08 code/determine_edge_weights_sync_bak.py

@@ -1,540 +1,0 @@
-from __future__ import division
-from collections import defaultdict
-import datetime
-import numpy
-import sys
-import os
-import igraph
-import pickle
-import pylab
-import math
-import random
-from itertools import islice
-
-MAKE_BINARY_DICT = False
-USE_10MIN_DICT = True
-Testuid1 = '456'
-Testuid2 = '237962820'
-Testuid3 = '243494256'
-strangeuid ='51319087'
-reference_start = datetime.datetime(2011, 4, 25, 9, 24, 58)
-reference_stop = datetime.datetime(2011, 6, 25, 14, 31, 59)
-#SPARSE_BINARY_HISTORY_PICKLE ="../data/tweet_times_2011/sparse_binary_ts_dict_bin-space-of-10min.p"
-#SPARSE_BINARY_HISTORY_PICKLE ="../data/tweet_times_2011/sparse_binary_ts_dict_bin-space-of-1.p"
-#SPARSE_BINARY_HISTORY_PICKLE ="test_histories_factor_600.p"
-#SPARSE_BINARY_HISTORY_PICKLE ="test_histories_factor_600_set_version.p"
-SPARSE_BINARY_HISTORY_PICKLE = "../data/tweet_times_2011/sparse_binary_ts_dict_bin-space-of-10min_set_version.p"
-T = (reference_stop - reference_start).total_seconds()
-
-factor = 600 #this corresponds to the 10-minute history
-#factor = 1
-#factor = int(5288821/4)
-full_length = int(T/factor)
-
-def take(n, iterable):
-    "Return first n items of the iterable as a list"
-    return list(islice(iterable, n))
-
-def  make_test_set(full_history):
-    test_dict ={}
-    n_items = take(50, full_history.iteritems())
-    #print n_items
-    for user in n_items:
-        print user[0]
-        test_dict[user[0]] = full_history[user[0]]
-
-    pickle.dump(test_dict, open("test_histories_factor_600_set_version.p", "wb" ) )
-
-
-
-def coarsen_sparse_dict(sparse_tweet_history_1_sec, factor):
-    coarse_sparse_dict = {}
-    for user in sparse_tweet_history_1_sec:
-        #print "starting the analysis of user**************:",user
-        coarse_sparse_dict[user]=coarse_sparse_resolution(sparse_tweet_history_1_sec[user],T,factor)
-    return coarse_sparse_dict
-
[…]

### 2014-01-08 code/determine_edge_weights_with_bar.py

@@ -1,0 +1,473 @@
+from __future__ import division
+from collections import defaultdict
+from time import sleep
+import datetime
+import numpy
+import sys
+import os
+import igraph
+import pickle
+import progressbar
+import pylab
+import math
+import random
+from itertools import islice
+
+MAKE_BINARY_DICT = False
+USE_10MIN_DICT = True
+Testuid1 = '456'
+Testuid2 = '237962820'
+Testuid3 = '243494256'
+strangeuid ='51319087'
+reference_start = datetime.datetime(2011, 4, 25, 9, 24, 58)
+reference_stop = datetime.datetime(2011, 6, 25, 14, 31, 59)
+#SPARSE_BINARY_HISTORY_PICKLE ="../data/tweet_times_2011/sparse_binary_ts_dict_bin-space-of-10min.p"
+#SPARSE_BINARY_HISTORY_PICKLE ="../data/tweet_times_2011/sparse_binary_ts_dict_bin-space-of-1.p"
+#SPARSE_BINARY_HISTORY_PICKLE ="test_histories_factor_600.p"
+#SPARSE_BINARY_HISTORY_PICKLE ="test_histories_factor_600_set_version.p"
+SPARSE_BINARY_HISTORY_PICKLE = "../data/tweet_times_2011/sparse_binary_ts_dict_bin-space-of-10min_set_version.p"
+#SPARSE_BINARY_HISTORY_PICKLE = "../data/tweet_times_2011/sparse_binary_ts_dict_bin-space-of-1day_set_version.p"
+#SPARSE_BINARY_HISTORY_PICKLE = "../data/tweet_times_2011/sparse_binary_ts_dict_bin-space-of-1hour_set_version.p"
+#SPARSE_BINARY_HISTORY_PICKLE = "../data/tweet_times_2011/sparse_binary_ts_dict_bin-space-of-2hour_set_version.p"
+
+T = (reference_stop - reference_start).total_seconds()
+
+factor_10Min = 600 #this corresponds to the 10-minute history
+factor_1hour = 3600  #this corresponds to the 1 hour history
+factor_1day = 86400  #this corresponds to the 1 day history
+#factor = 1
+#factor = int(5288821/4)
+#Can I do away with this?
+full_length_1day = int(T/factor_1day)
+full_length_1hour = int(T/factor_1hour)
+full_length_10min = int(T/factor_10Min)
+
+def take(n, iterable):
+    "Return first n items of the iterable as a list"
+    return list(islice(iterable, n))
+
[…]

### 2014-01-08 code/determine_edge_weightsrun2.py

@@ -1,0 +1,473 @@
+from __future__ import division
+from collections import defaultdict
+from time import sleep
+import datetime
+import numpy
+import sys
+import os
+import igraph
+import pickle
+import progressbar
+import pylab
+import math
+import random
+from itertools import islice
+
+MAKE_BINARY_DICT = False
+USE_10MIN_DICT = True
+Testuid1 = '456'
+Testuid2 = '237962820'
+Testuid3 = '243494256'
+strangeuid ='51319087'
+reference_start = datetime.datetime(2011, 4, 25, 9, 24, 58)
+reference_stop = datetime.datetime(2011, 6, 25, 14, 31, 59)
+#SPARSE_BINARY_HISTORY_PICKLE ="../data/tweet_times_2011/sparse_binary_ts_dict_bin-space-of-10min.p"
+SPARSE_BINARY_HISTORY_PICKLE ="../data/tweet_times_2011/sparse_binary_ts_dict_bin-space-of-1.p"
+#SPARSE_BINARY_HISTORY_PICKLE ="test_histories_factor_600.p"
+#SPARSE_BINARY_HISTORY_PICKLE ="test_histories_factor_600_set_version.p"
+#SPARSE_BINARY_HISTORY_PICKLE = "../data/tweet_times_2011/sparse_binary_ts_dict_bin-space-of-10min_set_version.p"
+#SPARSE_BINARY_HISTORY_PICKLE = "../data/tweet_times_2011/sparse_binary_ts_dict_bin-space-of-1day_set_version.p"
+#SPARSE_BINARY_HISTORY_PICKLE = "../data/tweet_times_2011/sparse_binary_ts_dict_bin-space-of-1hour_set_version.p"
+#SPARSE_BINARY_HISTORY_PICKLE = "../data/tweet_times_2011/sparse_binary_ts_dict_bin-space-of-2hour_set_version.p"
+
+T = (reference_stop - reference_start).total_seconds()
+
+factor_10Min = 600 #this corresponds to the 10-minute history
+factor_1hour = 3600  #this corresponds to the 1 hour history
+factor_1day = 86400  #this corresponds to the 1 day history
+#factor = 1
+#factor = int(5288821/4)
+#Can I do away with this?
+full_length_1day = int(T/factor_1day)
+full_length_1hour = int(T/factor_1hour)
+full_length_10min = int(T/factor_10Min)
+
+def take(n, iterable):
+    "Return first n items of the iterable as a list"
+    return list(islice(iterable, n))
+
[…]

### 2014-01-09 paper/paper.tex
Added a blurb about transfer entropy.
This blurb is probably too long for a 6 page paper. But we can cut it
down as we need to.
Added AAAI author kit files. Put paper into AAAI 'camera-ready' style.
According to

http://icwsm.org/2014/submitting/guidelines/

we should aim for 8 to 10 pages. We currently have 2.
Modified paper to be anonymous.
As per the Anonymity guidelines here:

http://icwsm.org/2014/submitting/guidelines/
Unify the notation for the weights across the community types.
Adding titles/authors and abstract slots

@@
-%%%%% Beginning of preamble %%%%%
-\documentclass[12pt]{article}
+%File: formatting-instruction.tex
+\documentclass[letterpaper]{article}
+\usepackage{aaai}
+\usepackage{times}
+\usepackage{helvet}
+\usepackage{courier}
+\usepackage{amssymb, amsmath, amsthm}
+\usepackage{graphicx}
+\frenchspacing
+\setlength{\pdfpagewidth}{8.5in}
+\setlength{\pdfpageheight}{11in}
+\pdfinfo{
+/Title (Input Your Paper Title Here)
+/Author (John Doe, Jane Doe)
+/Keywords (Input your paper’s keywords in this optional area)}
 
-%What kind of document (article) and what size
-%Packages to load which give you useful commands
-\usepackage{amssymb, amsmath, amsthm} 
-\usepackage{epsfig,graphicx} 
-\usepackage{caption}
-\usepackage{subcaption}
-\usepackage{authblk}
-\usepackage{verbatim}
+%%%%%%%%%%
+% Section Numbers
+% Uncomment if you want to use section numbers % and change the 0 to a 1 or 2
+\setcounter{secnumdepth}{0}
 
-%Sets the margins
-\textwidth = 6.5 in 
-\textheight = 9 in 
-\oddsidemargin = 0.0 in 
-\evensidemargin = 0.0 in 
-\topmargin = 0.0 in 
-\headheight = 0.0 in 
-\headsep = 0.0 in \parskip = 0.2in \parindent = 0.0in
+%%%%%%%%%%
+% Body of Paper Begins
+\begin{document}
 
-\begin{document} 
-\title{Working Title}
+% Title, Author, and Address Information
+\title{Followers are not enough: Beyond structure in the detection of communities \\
+Followers are not enough: Exploring the communities that exist beyond structure \\
+Followers are Not Enough: Activity, Interaction, and Topic-based Communities in Online Social Networks \\
+Followers are not enough: Beyond structural communities in online social networks
+ \\
+ Followers are not enough: exploring communities beyond structure
+\\
+ }
+  \author{David Darmon \\
+ Address line\\
+ Address line\\
+ \And Elisa Omodei \\
+ LaTTiCe (CNRS, ENS, Paris 3)\\
+ISC-PIF\\
+elisa.omodei@ens.fr \\
+ \And 
+ Joshua Garland\\
+ University of Colorado at Boulder\\
+Dept. of Computer Science
+joshua.garland@colorado.edu}
 
-% \author[1]{David Darmon}
-% \author[2]{Elisa Omodei}
-% \author[3]{Cesar O. Flores}
-% \author[4]{Lu\'is F. Seoane}
-% \author[5]{Kevin Stadler}
-% \author[6]{Jody Wright}
-% \author[7]{Joshua Garland}
-% \author[8]{Nix Barnett}
-% \affil[1]{Department of Mathematics, University of Maryland, College Park}
-% \affil[2]{ISC-PIF, LaTTiCe-CNRS, \'Ecole Normale Sup\'erieure, Paris}
-% \affil[3]{School of Physics, Georgia Institute of Technology, Atlanta}
-% \affil[4]{ICREA-Complex Systems Lab, Universitat Pompeu Fabra, Barcelona}
-% \affil[5]{School of Philosophy, Psychology and Language Sciences, The University of Edinburgh, Edinburgh}
-% \affil[6]{Department of Microbiology and Immunology, University of British Columbia, Vancouver}
-% \affil[7]{Department of Computer Science, University of Colorado, Boulder}
-% \affil[8]{Department of Mathematics and Complexity Sciences Center, University of California, Davis}
-
-\date{\today} 
 \maketitle
 
-\abstract{Lorem ipsum}
+\begin{abstract}
+\begin{quote}
+[[Joshua]]
+
+[[David]]
+
+[[Elisa]]
+
+\end{quote}
+\end{abstract}
 
@@
 \input{parts/community.tex}
+\input{parts/methods.tex}
+\input{parts/results.tex}
+\input{parts/discussion.tex}
 
-\bibliographystyle{plain}
 \bibliography{references}
+\bibliographystyle{aaai}
 

### 2014-01-09 paper/paper.tex
Added Titles and Names

@@
 % Title, Author, and Address Information
-\title{Followers are not enough: Beyond structure in the detection of communities \\
+\title{
+%Followers are not enough: Beyond structure in the detection of communities \\
 Followers are not enough: Exploring the communities that exist beyond structure \\
-Followers are Not Enough: Activity, Interaction, and Topic-based Communities in Online Social Networks \\
-Followers are not enough: Beyond structural communities in online social networks
- \\
- Followers are not enough: exploring communities beyond structure
-\\
+%Followers are not enough: Activity, Interaction, and Topic-based Communities in Online Social Networks \\
+%Followers are not enough: Beyond structural communities in online social networks
+% \\
+ %Followers are not enough: exploring communities beyond structure
  }
   \author{David Darmon  \\
- Address line\\
- Address line\\
+ University of Maryland\\
+Dept. of Mathematics \\
+ddarmon@math.umd.edu \\
  \And Elisa Omodei \\
@@
  University of Colorado at Boulder\\
-Dept. of Computer Science
+Dept. of Computer Science \\
 joshua.garland@colorado.edu}

### 2014-01-11 code/community_sizes.R
Write script to get out the distribution of community sizes between the different community types.

@@ -1,0 +1,55 @@
+# A script to generate the size distributions for the 
+# various community types.
+
+file.inds = c(0, 4, 7, 8)
+
+colors = c('black', 'blue', 'red', 'darkgreen')
+
+lwd = 2
+
+max.count = 2848
+
+pdf(sprintf('figures/comm_sizes_ecdf.pdf'))
+par(mar=c(4.5,5,2,1), cex.lab = 2, cex.axis = 2)
+plot(0, cex = 0, log = 'x', type = 'l', xlim = c(1, max.count), ylim = c(0, 1), xlab = 'Community Size', ylab = '1 - F(x)')
+
+for (cur.ind in 1:4){
+	file.ind = file.inds[cur.ind]
+
+	inputFile = sprintf("mutual3/coverings/singletons/communitites%g_comp.txt", file.ind)
+	con  = file(inputFile, open = "r")
+
+	comm.sizes = integer()
+
+	oneLine = readLines(con, n = 1, warn = FALSE)
+
+	while (length(oneLine) > 0) {
+	    nodes = strsplit(oneLine, " ")
+	    
+	    comm.sizes = c(comm.sizes, length(nodes[[1]]))
+
+	    oneLine = readLines(con, n = 1, warn = FALSE)
+	  } 
+
+	close(con)
+
+	counts = table(comm.sizes)
+	counts.without.singletons = counts[2:length(counts)]
+
+	cat(sprintf('%g\n\n', max(counts)))
+
+	# pdf(sprintf('figures/comm%gsize_dist.pdf', file.ind))
+	# par(mar=c(4,4.5,2,1), cex.lab = 2, cex.axis = 2)
+	# plot(as.numeric(names(counts.without.singletons)), counts.without.singletons, type = 'h', log = 'y', xlim = c(0, 900), xlab = 'Size of Community', ylab = 'Proportion of Communities')
+	# dev.off()
+
+	# F = ecdf(counts.without.singletons)
+	# x = seq(min(counts.without.singletons), 800, by = 0.01)
+
+	F = ecdf(counts)
+	x = seq(min(counts), max.count, by = 0.01)
+
+	lines(x, 1 - F(x), col = colors[cur.ind], lwd = lwd)
+}
+legend('topright', c('Structural', 'Activity-based', 'Interaction-based', 'Content-based'), lwd = rep(lwd,4), lty = rep(1, 4), col = colors)
+dev.off()

### 2014-01-11 code/mutual3/compare_coverings_onmi.py

@@ -1,0 +1,37 @@
+import subprocess
+import sys
+import numpy
+import pylab
+
+from StringIO import StringIO
+
+singleton_type = 'singletons'
+# singleton_type = 'no_singletons'
+
+file_dir = 'coverings/{}/'.format(singleton_type)
+
+num_types = 11
+
+mis = numpy.ones((num_types, num_types))*numpy.nan
+
+for ind1 in range(0, num_types):
+	fname1 = '{}communitites{}_comp.txt'.format(file_dir, ind1)
+	for ind2 in range(0, num_types):
+		fname2 = '{}communitites{}_comp.txt'.format(file_dir, ind2)
+		sp = subprocess.Popen(['onmi', fname1, fname2], stdin = subprocess.PIPE, stdout = subprocess.PIPE)
+		sp.wait()
+		mi = float(sp.communicate()[0].split()[1])
+
+		mis[ind1, ind2] = mi
+
+print mis
+
+# mis[mis == 1] = numpy.nan
+# mis[mis == 0] = numpy.nan
+
+pylab.figure()
+pylab.imshow(mis, interpolation = 'nearest', vmin = 0, vmax = 1, cmap = pylab.cm.gray_r)#, extent = (0, num_types, num_types, 0))
+pylab.xlabel('Weighting $j$'); pylab.ylabel('Weighting $i$')
+pylab.colorbar()
+pylab.savefig('nmi_{}.pdf'.format(singleton_type))
+# pylab.show()

### 2014-01-11 code/onmi/compare_coverings.py

@@ -1,0 +1,40 @@
+import subprocess
+import sys
+import numpy
+import pylab
+
+from StringIO import StringIO
+
+# NOTE: Use code on CSS computer in the Code
+# directory to generate these normalized
+# mutual informations based off
+#
+# 	https://github.com/aaronmcdaid/Overlapping-NMI
+#
+
+# singleton_type = 'singletons'
+singleton_type = 'no_singletons'
+
+num_types = 11
+
+mis = numpy.ones((num_types, num_types))*numpy.nan
+
+with open('mis_{}.txt'.format(singleton_type)) as ofile:
+	for ind1 in range(0, num_types):
+		for ind2 in range(0, num_types):
+			line = ofile.readline().strip()
+			mi = float(line)
+
+			mis[ind1, ind2] = mi
+
+print mis
+
+# mis[mis == 1] = numpy.nan
+# mis[mis == 0] = numpy.nan
+
+pylab.figure()
+pylab.imshow(mis, interpolation = 'nearest', vmin = 0, vmax = 1, cmap = pylab.cm.gray_r)#, extent = (0, num_types, num_types, 0))
+pylab.xlabel('Weighting $j$'); pylab.ylabel('Weighting $i$')
+pylab.colorbar()
+pylab.savefig('nmi_{}.pdf'.format(singleton_type))
+# pylab.show()

### 2014-01-11 paper/parts/results.tex
Added log-log plot of the distribution of community sizes.

@@
 
-\subsection{Comparing Community-Types with Normalized Mutual Information}
+\begin{figure}[h!]
+  \centering
+\includegraphics[width=0.50\textwidth]{Figures/comm_sizes_ecdf_loglog.pdf}
+\caption{The proportion of communities greater than $c$ in size, across the different community types. Note the logarithmic scale on the horizontal and vertical axes.}
+\label{Fig-community_size_distribution}
+\end{figure}
+
+\subsection{Comparing Community Types with Normalized Mutual Information}
 

### 2014-01-11 code/community_sizes.R

@@ -7,13 +7,14 @@ colors = c('black', 'blue', 'red', 'darkgreen')
 
 lwd = 2
 
-max.count = 2848
+max.comm.size = 811
 
 pdf(sprintf('figures/comm_sizes_ecdf.pdf'))
 par(mar=c(4.5,5,2,1), cex.lab = 2, cex.axis = 2)
-plot(0, cex = 0, log = 'x', type = 'l', xlim = c(1, max.count), ylim = c(0, 1), xlab = 'Community Size', ylab = '1 - F(x)')
+plot(0, cex = 0, log = 'xy', type = 'l', xlim = c(1, max.comm.size), ylim = c(1e-4, 0.5), xlab = 'c', ylab = 'Proportion of communities larger than c')
 
 for (cur.ind in 1:4){
+	cat(sprintf('\n\n====\n\n'))
 	file.ind = file.inds[cur.ind]
 
 	inputFile = sprintf("mutual3/coverings/singletons/communitites%g_comp.txt", file.ind)
@@ -36,7 +37,10 @@ for (cur.ind in 1:4){
 	counts = table(comm.sizes)
 	counts.without.singletons = counts[2:length(counts)]
 
-	cat(sprintf('%g\n\n', max(counts)))
+	cat(sprintf('%g\n\n', max(comm.sizes)))
+	cat(sprintf('Max size of community: %g\n\n', max(comm.sizes)))
+	cat(sprintf('Proportion %f of communities are size 1\n\n', counts[1]/sum(counts)))
+	cat(sprintf('%g are singletons.\n\n', counts[1]))
 
 	# pdf(sprintf('figures/comm%gsize_dist.pdf', file.ind))
 	# par(mar=c(4,4.5,2,1), cex.lab = 2, cex.axis = 2)
@@ -46,10 +50,12 @@ for (cur.ind in 1:4){
 	# F = ecdf(counts.without.singletons)
 	# x = seq(min(counts.without.singletons), 800, by = 0.01)
 
-	F = ecdf(counts)
-	x = seq(min(counts), max.count, by = 0.01)
+	F = ecdf(comm.sizes)
+	x = seq(1, max(comm.sizes), by = 0.01)
+
+	cat(sprintf('%f\n\n', min(1-F(x))))
 
 	lines(x, 1 - F(x), col = colors[cur.ind], lwd = lwd)
 }
[…]

### 2014-01-12 paper/paper.tex
Commented out authors.
Since we need this for the anonymized submission.
Added log-log plot of the distribution of community sizes.
Fixed a buggy figure.

@@
 /Author (John Doe, Jane Doe)
-/Keywords (Input your paper’s keywords in this optional area)}
+/Keywords (Input your paper keywords in this optional area)}
 
@@
  }
-  \author{David Darmon  \\
- University of Maryland\\
-Dept. of Mathematics \\
-ddarmon@math.umd.edu \\
- \And Elisa Omodei \\
- LaTTiCe (CNRS, ENS, Paris 3)\\
-ISC-PIF\\
-elisa.omodei@ens.fr \\
- \And 
- Joshua Garland\\
- University of Colorado at Boulder\\
-Dept. of Computer Science \\
-joshua.garland@colorado.edu}
+%   \author{David Darmon  \\
+%  University of Maryland\\
+% Dept. of Mathematics \\
+% ddarmon@math.umd.edu \\
+%  \And Elisa Omodei \\
+%  LaTTiCe (CNRS, ENS, Paris 3)\\
+% ISC-PIF\\
+% elisa.omodei@ens.fr \\
+%  \And 
+%  Joshua Garland\\
+%  University of Colorado at Boulder\\
+% Dept. of Computer Science \\
+% joshua.garland@colorado.edu}
 
@@
 \input{parts/discussion.tex}
+\input{parts/conclusion.tex}
 

### 2014-01-13 paper/parts/results.tex
Added some text to the paper.

@@
 
-\subsection{Comparing Different Flows Across Different Community-Types}
+\subsection{Comparing Edges Across Different Community-Types}
+
+We have defined communities using four different criteria: structure, activity, interaction, and content.
+For a given type of community, edges for a particular community may be partitioned into three sets: those from a node in the community to another node in the community (internal-to-internal), those from a node in the community to a node outside of the community (internal-to-external), and those from a node outside the community to a node inside the community (external-to-internal).
+See Figure~\ref{Fig-edge_types} for a schematic of this edge partitioning.
+For a meaningful community, we expect the distribution of weights within the community (internal-to-internal weights) to be different from the distribution of weights without the community (internal-to-external and external-to-internal).
 
@@
 \end{figure}
+
+For example, Figure~\ref{Fig-edge_types} shows the distributions of hashtag-based weights for the largest community defined by mention-retweets.
+We see that the distribution of internal-to-internal hashtag weights has a longer tail, with edges
+
+\begin{figure}[h!]
+  \centering
+\includegraphics[width=0.50\textwidth]{Figures/comm0_labels-mention-retweet_weights-hashtag-ecdf.pdf}
+\caption{The proportion of edges with a weight at least as large as the weight on the horizontal axis, across the types of edges described in Figure~\ref{Fig-edge_types}.}
+\label{Fig-dist_across_community}
+\end{figure}
+
+\begin{table}
+	\caption{The median value for the ratio of the median external/internal-to-internal/external weight to median internal-to-internal weight for the different community/weight pairings.}
+	\centering
+	\begin{tabular}{c | c | c  c  c  c}
+		& & \multicolumn{4}{ c }{Community} \\ \hline
+		\multirow{4}{*}{Weight} & & S & TE & MR & HT \\ \hline
+		& TE & $0.0 / 0.0$ & $0.0 / 0.0$ & $0.0 / 0.0$ & $0.0 / 0.0$\\
+		& MR & $0.0 / 0.0$ & $0.0 / 0.0$ & $0.0 / 0.0$ & $0.0 / 0.0$\\
+		& HT & $0.0 / 0.0$ & $0.0 / 0.0$ & $0.0 / 0.0$ & $0.0 / 0.0$
+	\end{tabular}
+\end{table}

### 2014-01-13 code/compare_weights_between_community_types.py

@@ -14,21 +14,14 @@
 #	DMD, 311213-18-25
 
 from itertools import islice
+import numpy
 
 # The community type used to determine the
 # weights on edges.
 
 # weight_type = 'TE4'
 # weight_type = 'hashtag'
-weight_type = 'mention-retweet'
-
-if 'TE' in weight_type:
-	lag = weight_type.split('E')[1]
-	weight_file = '../data/content-free/directedweightsTE/edge_weights_bin10minutes_lag_{}_withMMBIAS.dat'.format(lag)
-elif weight_type == 'hashtag':
-	weight_file = '../data/content-full/twitter_network_hashtags_weighted.txt'
-elif weight_type == 'mention-retweet':
-	weight_file = '../data/content-full/twitter_network_contentfull_weighted_arithmeticmean.txt'
+# weight_type = 'mention-retweet'
 
 # The community type used to determine the
 # community memberships.
@@ -36,165 +29,189 @@ elif weight_type == 'mention-retweet':
 # label_type = 'struc'
 # label_type = 'TE4'
 # label_type = 'hashtag'
-label_type = 'mention-retweet'
+# label_type = 'mention-retweet'
 
-if label_type == 'struc':
-	label_file  = 'twitter_unweighted_network.txt_oslo_files'
-elif 'TE' in label_type:
-	lag = label_type.split('E')[1]
-	label_file  = 'edge_weights_bin10minutes_lag_{}_withMMBIAS_edgelist.dat_oslo_files'.format(lag)
-elif label_type == 'hashtag':
-	label_file  = 'twitter_network_hashtags_weighted.txt_oslo_files'
-elif label_type == 'mention-retweet':
-	label_file  = 'twitter_network_contentfull_weighted_arithmeticmean.txt_oslo_files'
+for weight_type in ['TE4', 'hashtag', 'mention-retweet']:
+	for label_type in ['struc', 'TE4', 'hashtag', 'mention-retweet']:
+		print 'Working on {}/{} pairing...'.format(weight_type, label_type)
 
-# Generate a dictionary of the form
-# {user_id : community_id} from the 
-# communities based on the labels.
+		if 'TE' in weight_type:
+			lag = weight_type.split('E')[1]
+			weight_file = '../data/content-free/directedweightsTE/edge_weights_bin10minutes_lag_{}_withMMBIAS.dat'.format(lag)
+		elif weight_type == 'hashtag':
+			weight_file = '../data/content-full/twitter_network_hashtags_weighted.txt'
[…]

### 2014-01-13 code/compare_weights_between_community_types_aggregate.py

@@ -1,0 +1,44 @@
+# Get out the change in median weight for in-to-in vs. in/out-to-out/in
+# edges.
+#
+#	DMD, 120114-19-48
+
+import numpy
+
+label_type = 'struc'
+weight_type = 'hashtag'
+
+print 'Using the {}/{} pairing.'.format(label_type, weight_type)
+
+ratio_e_to_i = []
+ratio_i_to_e = []
+
+for comm_rank in range(100):
+	file_prefix = 'comm{}_labels-{}_weights-{}'.format(comm_rank, label_type, weight_type)
+
+	i_to_i = numpy.loadtxt('../data/edges-by-type/{}_i-to-i.dat'.format(file_prefix))
+	e_to_i = numpy.loadtxt('../data/edges-by-type/{}_e-to-i.dat'.format(file_prefix))
+	i_to_e = numpy.loadtxt('../data/edges-by-type/{}_i-to-e.dat'.format(file_prefix))
+
+	# print 'The i-to-i, e-to-i, and i-to-e medians are {}, {}, {}.'.format(numpy.median(i_to_i), numpy.median(e_to_i), numpy.median(i_to_e))
+
+	if weight_type == 'mention-retweet':
+		i_to_i = i_to_i[i_to_i != 0]
+		e_to_i = e_to_i[e_to_i != 0]
+		i_to_e = i_to_e[i_to_e != 0]
+
+	med_i_to_i = numpy.median(i_to_i)
+	med_e_to_i = numpy.median(e_to_i)
+	med_i_to_e = numpy.median(i_to_e)
+
+	# print med_i_to_i, med_e_to_i, med_i_to_e
+
+	rat_e_to_i = med_i_to_i/med_e_to_i
+	rat_i_to_e = med_i_to_i/med_i_to_e
+
+	print '{}\t{}'.format(rat_e_to_i, rat_i_to_e)
+
+	ratio_e_to_i.append(rat_e_to_i)
+	ratio_i_to_e.append(rat_i_to_e)
+
+print 'The median e-to-i ratio is {} ({}).\nThe median i-to-e ratio is {} ({}).'.format(numpy.median(ratio_e_to_i), numpy.mean(ratio_e_to_i), numpy.median(ratio_i_to_e), numpy.mean(ratio_i_to_e))

### 2014-01-13 code/compare_weights_between_community_types_aggregate.py
Added my attempt at the abstract.

@@ -7,38 +7,39 @@ import numpy
 
 label_type = 'struc'
 weight_type = 'hashtag'
+for weight_type in ['TE4', 'mention-retweet', 'hashtag']:
+	for label_type in ['struc', 'TE4', 'mention-retweet', 'hashtag']:
+		print 'Using the {}/{} pairing.'.format(label_type, weight_type)
 
-print 'Using the {}/{} pairing.'.format(label_type, weight_type)
+		ratio_e_to_i = []
+		ratio_i_to_e = []
 
-ratio_e_to_i = []
-ratio_i_to_e = []
+		for comm_rank in range(100):
+			file_prefix = 'comm{}_labels-{}_weights-{}'.format(comm_rank, label_type, weight_type)
 
-for comm_rank in range(100):
-	file_prefix = 'comm{}_labels-{}_weights-{}'.format(comm_rank, label_type, weight_type)
+			i_to_i = numpy.loadtxt('../data/edges-by-type/{}_i-to-i.dat'.format(file_prefix))
+			e_to_i = numpy.loadtxt('../data/edges-by-type/{}_e-to-i.dat'.format(file_prefix))
+			i_to_e = numpy.loadtxt('../data/edges-by-type/{}_i-to-e.dat'.format(file_prefix))
 
-	i_to_i = numpy.loadtxt('../data/edges-by-type/{}_i-to-i.dat'.format(file_prefix))
-	e_to_i = numpy.loadtxt('../data/edges-by-type/{}_e-to-i.dat'.format(file_prefix))
-	i_to_e = numpy.loadtxt('../data/edges-by-type/{}_i-to-e.dat'.format(file_prefix))
+			# print 'The i-to-i, e-to-i, and i-to-e medians are {}, {}, {}.'.format(numpy.median(i_to_i), numpy.median(e_to_i), numpy.median(i_to_e))
 
-	# print 'The i-to-i, e-to-i, and i-to-e medians are {}, {}, {}.'.format(numpy.median(i_to_i), numpy.median(e_to_i), numpy.median(i_to_e))
+			if weight_type == 'mention-retweet':
+				i_to_i = i_to_i[i_to_i != 0]
+				e_to_i = e_to_i[e_to_i != 0]
+				i_to_e = i_to_e[i_to_e != 0]
 
[…]

### 2014-01-13 code/eda_qual-comm.py
Changed interface for eda_qual-comm.py.

@@ -1,4 +1,4 @@
-import os
+import webbrowser
 import numpy
 
 # The weights used to determine the community 
@@ -52,15 +52,15 @@ with open(full_name) as ofile:
 
 comm_sorted = numpy.argsort(comm_sizes)
 
-# comm_id = comm_sorted[-1]
-comm_id = comm_sorted[0]
+# comm_id = comm_sorted[-1] # Start with the largest community
+comm_id = comm_sorted[0] # Start with the smallest community
 
 print 'Community {} using the weight type {} has {} members.'.format(comm_id, label_type, len(comm_dict[comm_id]))
 
 at_a_time = 5 # Open this many at a time.
 
 for ind, node in enumerate(comm_dict[comm_id]):
-	os.system("open 'http://twitter.com/account/redirect_by_id?id={}'".format(node))
+	webbrowser.open('http://twitter.com/account/redirect_by_id?id={}'.format(node))
 
 	if (ind+1)%at_a_time == 0:
 		raw_input("")

### 2014-01-13 paper/parts/results.tex
Added more details to the paper about weights across the community boundaries.

--- 2014-01-11 paper/parts/results.tex
@@
 Discuss the basic properties of the various types of communities: distribution of sizes, number of singletons, etc.
+
+\begin{figure}[h!]
+  \centering
+\includegraphics[width=0.50\textwidth]{Figures/overlap_by_type.pdf}
+\caption{Lorem ipsum.}
+\label{Fig-}
+\end{figure}
 
@@
 
-\subsection{Comparing Different Flows Across Different Community-Types}
+\subsection{Comparing Edges Across Different Community-Types}
+
+We have defined communities using four different criteria: structure, activity, interaction, and content.
+For a fixed community type, edges for a particular community may be partitioned into three sets: those from a node in the community to another node in the community (internal-to-internal), those from a node in the community to a node outside of the community (internal-to-external), and those from a node outside the community to a node inside the community (external-to-internal).
+See Figure~\ref{Fig-edge_types} for a schematic of this edge partitioning.
+For a meaningful community, we expect the distribution of weights within the community (internal-to-internal weights) to be different from the distribution of weights without the community (internal-to-external and external-to-internal).
 
@@
 \end{figure}
+
+For example, Figure~\ref{Fig-edge_types} shows the distributions of hashtag-based weights for the largest community defined by the mention-retweet network.
+We see that the distribution of internal-to-internal hashtag weights has a longer tail than either the external-to-internal or internal-to-external hashtag weights, with edges within the community having higher weights than edges crossing the boundary of the community.
+Thus, while the community was defined in terms of interactions, we still see a shift in the distribution of \emph{topic-similarity}.
+
+\begin{figure}[h!]
+  \centering
+\includegraphics[width=0.50\textwidth]{Figures/comm0_labels-mention-retweet_weights-hashtag-ecdf.pdf}
+\caption{The proportion of edges with a weight at least as large as the weight on the horizontal axis, across the types of edges described in Figure~\ref{Fig-edge_types}.
+The community is defined by user interactions, and the edge weights are determined by topics.}
+\label{Fig-dist_across_community}
+\end{figure}
+
+This shift in the distribution was typical of many of the community type / weight pairings.
+To explore this further, for each of the top 100 largest communities defined by a particular community type (structure-based, behavior-based, content-based, or activity-based), we computed the median internal-to-internal, external-to-internal, and internal-to-external weight for that community for each weight type.
+These values summarize the typical value of each of these types of edges.
+We can then compute the ratio of the median internal-to-internal weight and the median external/internal-to-internal/external weight, which captures the proportional shift in the distribution.
+Finally, we compute the median of this proportional shift across all 100 of the largest communities.
+These values are summarized in Table~\ref{Table-medians}.
+
+% \begin{table}
+% 	\caption{The median value for the ratio of the median external/internal-to-internal/external weight to median internal-to-internal weight for the different community/weight pairings.}
+% 	\centering
+% 	\begin{tabular}{c | c | c  c  c  c}
+% 		& & \multicolumn{4}{ c }{Community} \\ \hline
+% 		\multirow{4}{*}{Weight} & & S & TE & MR & HT \\ \hline
+% 		& TE & $0.0 / 0.0$ & $0.0 / 0.0$ & $0.0 / 0.0$ & $0.0 / 0.0$\\
+% 		& MR & $0.0 / 0.0$ & $0.0 / 0.0$ & $0.0 / 0.0$ & $0.0 / 0.0$\\
+% 		& HT & $0.0 / 0.0$ & $0.0 / 0.0$ & $0.0 / 0.0$ & $0.0 / 0.0$
+% 	\end{tabular}
+% \end{table}
+
+\begin{table}
+	\label{Table-medians}
+	\caption{The median value across the 100 largest communities for the ratio of the median internal-to-internal weight to median external/internal-to-internal/external weight for the different community/weight pairings.
+\\ * For mention-retweet weights, weight zero edges were excluded from the computation of the median.}
+	\centering
+	\begin{tabular}{c | c | c  c  c}
+		& & \multicolumn{3}{ c }{Weight} \\ \hline
+		\multirow{4}{*}{Community} & & TE & MR & HT \\ \hline
+		& S & $0.96/0.94$& $1.7/2.1$*& $9.0/8.0$\\
+		& TE & $1.0/0.96$& $1.5/2.4$*& $24/17$\\
+		& MR & $0.83/0.86$& $3.2/4.4$& $10/8.5$\\
+		& HT & $0.9/0.89$& $2.4/2.6$*& $28/26$
+	\end{tabular}
+\end{table}
+
+We see that overall, the

### 2014-01-13 code/count_users_with_overlap.py

@@ -1,0 +1,47 @@
+# A script to count the number of users
+# who belong to more than one community,
+# by community-type.
+#
+#	DMD, 130114-10-28
+
+from collections import Counter
+
+comm_types = [0, 4, 7, 10]
+
+community_labels = {0 : 'structural', 4 : 'behavior', 7 : 'topic', 10 : 'activity'}
+
+with open('tmp.dat', 'w') as wfile:
+	for comm_type in comm_types:
+		label_file = 'mutual3/coverings/no_singletons/communitites{}_comp.txt'.format(comm_type)
+
+		# A dictionary of the form
+		# 	{userid : num_communities}
+
+		user_dict = Counter()
+		overlap_dict = Counter()
+
+		with open(label_file) as ofile:
+			for comm_id, line in enumerate(ofile):
+				nodes = line.strip().split(' ')
+
+				for node in nodes:
+					user_dict[node] += 1
+
+		num_nodes_with_overlap = 0
+
+		for node in user_dict:
+			if user_dict[node] > 1:
+				overlap_dict[user_dict[node]] += 1
+				num_nodes_with_overlap += 1
+				# print node, user_dict[node]
+
+		print label_file, num_nodes_with_overlap, overlap_dict
+
+		# to_print = '{} '.format(community_labels[comm_type])
+
+		for ind in range(2, 5):
+			# print '{} {} {}'.format(community_labels[comm_type], ind, overlap_dict[ind])
+
+			# to_print += '{} '.format(overlap_dict[ind])
+			for cur_ind in range(overlap_dict[ind]):
+				wfile.write('{} {}\n'.format(community_labels[comm_type], ind))

### 2014-01-14 paper/drafts/results.tex
Added sections on aggregate statistics for the different community-types.

%File: formatting-instruction.tex
\documentclass[letterpaper]{article}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\usepackage{amssymb, amsmath, amsthm}
\usepackage{graphicx}
\usepackage{multirow}

\begin{document}

\subsection{Comparing Aggregate Statistics of Community Structure}

We begin by examining the overall statistics for the communities inferred by OSLOM using the weightings defined in Sections \ref{method-activity}, \ref{method-interaction}, and \ref{method-topic}. The number of communities by community type is given in Table~\ref{Table-comm_count}. We see that the topic- and interaction-based networks admit the most communities. The activity-based network admits the least number of communities.  One advantage of the OSLOM over many other community detection algorithms is that it explicitly accounts for singleton `communities': those nodes who do not belong to \emph{any} extant communities. This is especially important when a network is collected via a breadth-first search, as in our network, where we begin from a seed node and then branch out. Such a search, once terminated, will result in a collection of nodes on the periphery of the network that may not belong to any community in the core.

% See here
% 	http://arxiv.org/pdf/1202.2684v2.pdf
% for possible useful references on core-periphery networks.

The number of singletons by community type is also shown in Table~\ref{Table-comm_count}. We see that the topic- and interaction-based communities have the most singletons, with the activity-based community dominating this measure. This result for the activity-based community is an artifact of a property of the retweet/mention weighting: many of the users in the data set (\textbf{TK: give actual number}) did not interact with each other, and thus all of their edges were zero-weighted, leading to trivial singletons.

\begin{table}[ht]
	\label{Table-comm_count}
	\caption{Number of non-singleton communities and singletons by community type: S(tructural), A(ctivity -based), T(opic-based), and I(nteraction-based).}
	\centering
	\begin{tabular}{| c | c | c |}
		\hline Community Type & \# of Communities & \# of Singletons \\ \hline
		% Structural & 201 \\
		% Activity, Lag 1 & 101 \\
		% Activity, Lag 2 & 99 \\
		% Activity, Lag 3 & 106 \\
		% Activity, Lag 4 & 105 \\
		% Activity, Lag 5 & 107 \\
		% Activity, Lag 6 & 106 \\
		% Topic & 289 \\
		% Interaction & 252 \\ \hline
		S & 201 & 308 \\
		A, Lag 1 & 101 & 951 \\
		A, Lag 2 & 99 & 600 \\
		A, Lag 3 & 106 & 611 \\
		A, Lag 4 & 105 & 668 \\
		A, Lag 5 & 107 & 632 \\
		A, Lag 6 & 106 & 642 \\
		T & 289 & 1064 \\
		I & 252 & 2436 \\ \hline
	\end{tabular}
\end{table}

Next we consider the distribution of community sizes across the community types. The complementary cumulative distribution of community sizes is given in Figure~\ref{Fig-community_size_distribution}. Note that the axes are plotted on log-scale, and the horizontal axis begins with non-singleton communities. Thus, for a fixed community size $c$, Figure~\ref{Fig-community_size_distribution} shows the proportion of communities of size greater than $c$ for each community type. The largest communities for the structural, activity-based, topic-based, and interaction-based networks are 198, 358, 338, and 811 respectively.

\begin{figure}[ht]
  \centering
\includegraphics[width=0.50\textwidth]{../Figures/comm_sizes_ecdf_loglog.pdf}
\caption{The proportion of communities greater than $c$ in size, across the different community types. Note the logarithmic scale on the horizontal and vertical axes.}
\label{Fig-community_size_distribution}
\end{figure}

Next, we compare the number of users which belong to more than one community. Figure~\ref{Fig-overlap_plot} shows the number of users belonging to 2, 3, or 4 communities. We see that as the number of mixed membership communities increases, the number of users with that number of mixed memberships decreases. This is especially true for the activity-based community \textbf{TK: speculate on what this means? Or save for the results section?}.  In addition, \textbf{TK: mention the 5, 6, and 7 cases, not included in the figure}. This corresponded to \textbf{TK: investigate which users are the high-overlap and what communities they belong to.}

% The user with a structural overlap of 7 communities was 1630261,
%	https://twitter.com/marksilva

\begin{figure}[ht]
  \centering
\includegraphics[width=0.50\textwidth]{../Figures/overlap_by_type.pdf}
\caption{The number of users belonging to 2, 3, or 4 communities, by community type.}
\label{Fig-overlap_plot}
\end{figure}

\end{document}

### 2014-01-14 paper/parts/methods.tex
Added sections on aggregate statistics for the different community-types.

@@
 \subsection{Activity-Based Communities and Transfer Entropy}
+
+\label{method-activity}
 
@@
 \section{Interaction-Based Communities and Mention / Retweet Weighting}
+
+\label{method-interaction}
+
 A way of tracking the flow of information through users is by considering two useful features of this social network: mentions and retweets.
@@
 
+\label{method-topic}
+
 Another kind of community is the one based on the content of the tweets, and relies on the idea of finding people that talk about the same things.

### 2014-01-14 paper/parts/results.tex
Added sections on aggregate statistics for the different community-types.

@@
 
-\subsection{Community Statistics (? A better title should go here.)}
+\subsection{Comparing Aggregate Statistics of Community Structure}
 
-Discuss the basic properties of the various types of communities: distribution of sizes, number of singletons, etc.
+We begin by examining the overall statistics for the communities inferred by OSLOM using the weightings defined in Sections \ref{method-activity}, \ref{method-interaction}, and \ref{method-topic}.
+The number of communities by community type is given in Table~\ref{Table-comm_count}.
+We see that the topic- and interaction-based networks admit the most communities.
+The activity-based network admits the least number of communities.
+One advantage of the OSLOM over many other community detection algorithms is that it explicitly accounts for singleton `communities': those nodes who do not belong to \emph{any} extant communities.
+This is especially important when a network is collected via a breadth-first search, as in our network, where we begin from a seed node and then branch out.
+Such a search, once terminated, will result in a collection of nodes on the periphery of the network that may not belong to any community in the core.
 
-\begin{figure}[h!]
+% See here
+% 	http://arxiv.org/pdf/1202.2684v2.pdf
+% for possible useful references on core-periphery networks.
+
+The number of singletons by community type is also shown in Table~\ref{Table-comm_count}.
+We see that the topic- and interaction-based communities have the most singletons, with the activity-based community dominating this measure.
+This result for the activity-based community is an artifact of a property of the retweet/mention weighting: many of the users in the data set (\textbf{TK: give actual number}) did not interact with each other, and thus all of their edges were zero-weighted, leading to trivial singletons.
+
+\begin{table}[ht]
+	\label{Table-comm_count}
+	\caption{Number of non-singleton communities and singletons by community type: S(tructural), A(ctivity -based), T(opic-based), and I(nteraction-based).}
 	\centering
-\includegraphics[width=0.50\textwidth]{Figures/overlap_by_type.pdf}
-\caption{Lorem ipsum.}
-\label{Fig-}
-\end{figure}
+	\begin{tabular}{| c | c | c |}
+		\hline Community Type & \# of Communities & \# of Singletons \\ \hline
+		% Structural & 201 \\
+		% Activity, Lag 1 & 101 \\
+		% Activity, Lag 2 & 99 \\
+		% Activity, Lag 3 & 106 \\
+		% Activity, Lag 4 & 105 \\
+		% Activity, Lag 5 & 107 \\
+		% Activity, Lag 6 & 106 \\
+		% Topic & 289 \\
+		% Interaction & 252 \\ \hline
+		S & 201 & 308 \\
+		A, Lag 1 & 101 & 951 \\
+		A, Lag 2 & 99 & 600 \\
+		A, Lag 3 & 106 & 611 \\
+		A, Lag 4 & 105 & 668 \\
+		A, Lag 5 & 107 & 632 \\
+		A, Lag 6 & 106 & 642 \\
+		T & 289 & 1064 \\
+		I & 252 & 2436 \\ \hline
+	\end{tabular}
+\end{table}
 
-\begin{figure}[h!]
+Next we consider the distribution of community sizes across the community types.
+The complementary cumulative distribution of community sizes is given in Figure~\ref{Fig-community_size_distribution}.
+Note that the axes are plotted on log-scale, and the horizontal axis begins with non-singleton communities.
+Thus, for a fixed community size $c$, Figure~\ref{Fig-community_size_distribution} shows the proportion of communities of size greater than $c$ for each community type.
+The largest communities for the structural, activity-based, topic-based, and interaction-based networks are 198, 358, 338, and 811 respectively.
+
+\begin{figure}[ht]
   \centering
@@
 \label{Fig-community_size_distribution}
+\end{figure}
+
+Next, we compare the number of users which belong to more than one community.
+Figure~\ref{Fig-overlap_plot} shows the number of users belonging to 2, 3, or 4 communities.
+We see that as the number of mixed membership communities increases, the number of users with that number of mixed memberships decreases.
+This is especially true for the activity-based community \textbf{TK: speculate on what this means?
+Or save for the results section?}.
+In addition, \textbf{TK: mention the 5, 6, and 7 cases, not included in the figure}.
+This corresponded to \textbf{TK: investigate which users are the high-overlap and what communities they belong to.}
+
+% The user with a structural overlap of 7 communities was 1630261,
+%	https://twitter.com/marksilva
+
+\begin{figure}[ht]
+  \centering
+\includegraphics[width=0.50\textwidth]{Figures/overlap_by_type.pdf}
+\caption{The number of users belonging to 2, 3, or 4 communities, by community type.}
+\label{Fig-overlap_plot}
 \end{figure}

### 2014-01-14 code/count_communities.py

@@ -1,0 +1,36 @@
+# A script to count the number of non-singleton
+# communities for each of the community types.
+#
+#	DMD, 140114-09-45
+
+from collections import Counter
+
+# comm_types = [0, 4, 7, 10]
+comm_types = range(11)
+
+for comm_type in comm_types:
+	# Count number of non-singleton communities.
+
+	label_file = 'mutual3/coverings/no_singletons/communitites{}_comp.txt'.format(comm_type)
+
+	comm_count = 0
+
+	with open(label_file) as ofile:
+		for line in ofile:
+			comm_count += 1
+
+	# print comm_type, comm_count
+
+	# Count number of singleton communities.
+
+	label_file = 'mutual3/coverings/singletons/communitites{}_comp.txt'.format(comm_type)
+
+	singleton_count = 0
+
+	with open(label_file) as ofile:
+		for line in ofile:
+			if len(line.strip().split(' ')) == 1:
+				# print line.split(' ')
+				singleton_count += 1
+
+	print comm_type, singleton_count

### 2014-01-14 code/count_users_with_overlap.py

@@ -8,9 +8,10 @@ from collections import Counter
 
 comm_types = [0, 4, 7, 10]
 
-community_labels = {0 : 'structural', 4 : 'behavior', 7 : 'topic', 10 : 'activity'}
+community_labels = {0 : 'structure', 4 : 'activity', 7 : 'topic', 10 : 'interaction'}
 
-with open('tmp.dat', 'w') as wfile:
+with open('overlap_counts.txt', 'w') as wfile:
+	wfile.write('type count\n')
 	for comm_type in comm_types:
 		label_file = 'mutual3/coverings/no_singletons/communitites{}_comp.txt'.format(comm_type)
 
@@ -35,9 +36,12 @@ with open('tmp.dat', 'w') as wfile:
 				num_nodes_with_overlap += 1
 				# print node, user_dict[node]
 
-		print label_file, num_nodes_with_overlap, overlap_dict
+				if user_dict[node] == 7:
+					print node
 
-		# to_print = '{} '.format(community_labels[comm_type])
+		# print label_file, num_nodes_with_overlap, overlap_dict
+
+		to_print = '{} '.format(community_labels[comm_type])
 
 		for ind in range(2, 5):
 			# print '{} {} {}'.format(community_labels[comm_type], ind, overlap_dict[ind])

### 2014-01-14 paper/code-table_and_figure/barplot.R

@@ -1,0 +1,15 @@
+library(ggplot2)
+library(scales)
+
+data = read.table('overlap_counts.txt', sep = ' ', header = TRUE, row.names = NULL)
+
+# data = data = read.table('overlap_counts_old.txt', sep = ' ', header = TRUE, row.names = NULL)
+
+# data$size=factor(data$size) 
+
+data$type = factor(data$type, levels = c('structure', 'activity', 'topic', 'interaction'))
+data$count = factor(data$count)
+
+# ggplot(data, aes(count, fill = type)) + geom_bar(position="dodge") + xlab('Size of Overlap') + ylab('Number of Users') #+ scale_y_continuous(trans=log10_trans())
+ggplot(data, aes(type, fill = type)) + geom_bar() + facet_wrap(~ count, scales = 'free') + xlab('Number of Memberships') + ylab('Number of Users') + theme(text = element_text(size=20)) + theme(axis.text.x=element_text(angle=90))
+ggsave('overlap_by_type.pdf')

### 2014-01-14 code/compare_communities.py
added distributions and code for manual inpection of communities

@@ -1,0 +1,66 @@
+#!/usr/bin/env python
+# -*- coding: utf-8 -*-
+import sys
+
+hashtags_file = open('../data/users_hashtags.txt','r')
+hashtags_vector = {}
+lines = hashtags_file.readlines()
+for line in lines:
+	row = line.split(';')
+	user = row[0]
+	hashtags_vector[user] = []
+	elements = row[1][:-1].split('\t')
+	for element in elements[:-1]:
+		h = element.split()[0]
+		tfidf = float(element.split()[1])
+		#hashtags_vector[user].append((tfidf,h))
+		hashtags_vector[user].append(h)
+
+
+hashtags_communities_file = open('../oslom_outputs/twitter_network_hashtags_weighted.txt_oslo_files/tp_without_singletons','r')
+hashtag_communities_size = {}; hashtag_communities_bs = {}; hashtag_communities_users = {}
+lines = hashtags_communities_file.readlines()
+for i in range(len(lines)):
+	if i % 2 == 0:
+		line = lines[i].split()
+		module = line[1]
+		size =  int(line[3])
+		bs = float(line[5])
+		hashtag_communities_size[module] = size
+		hashtag_communities_bs[module] = bs
+		users = lines[i+1].split()
+		hashtag_communities_users[module] = users
+
+for c in hashtag_communities_users:
+	#hashtags = {}
+	#for u in hashtag_communities_users[c]:
+	#	#if c == '114': print u,hashtags_vector[u]
+	#	hashtags[u] = set()
+	#	for (score,h) in hashtags_vector[u]:
+	#		hashtags[u].add(h)
+	#hashtags_intersection = set.intersection(*hashtags.values())
+	#print c,hashtag_communities_size[c],hashtag_communities_bs[c],hashtags_intersection
+	hashtags = set()
+	hashtag_nbusers = {}
+	for u in hashtag_communities_users[c]:
+		for h in hashtags_vector[u]: 
+			hashtags.add(h)
+			if h in hashtag_nbusers: hashtag_nbusers[h] += 1
+			else: hashtag_nbusers[h] = 1
+	nb_hashtags = {}
+	for h in hashtag_nbusers:
+		n = hashtag_nbusers[h]
+		if n in nb_hashtags: nb_hashtags[n].append(h)
+		else: nb_hashtags[n] = [h]
+	print c,hashtag_communities_size[c],hashtag_communities_bs[c]
[…]

### 2014-01-14 code/eda_qual-comm.py

@@ -1,4 +1,4 @@
-import os
+import webbrowser
 import numpy
 
 # The weights used to determine the community 
@@ -6,8 +6,8 @@ import numpy
 
 # label_type = 'struc'
 # label_type = 'TE4'
-# label_type = 'hashtag'
-label_type = 'mention-retweet'
+label_type = 'hashtag'
+#label_type = 'mention-retweet'
 
 print '\nUsing weights of type {}\n'.format(label_type)
 
@@ -52,15 +52,15 @@ with open(full_name) as ofile:
 
 comm_sorted = numpy.argsort(comm_sizes)
 
-# comm_id = comm_sorted[-1]
-comm_id = comm_sorted[0]
+# comm_id = comm_sorted[-1] # Start with the largest community
+comm_id = comm_sorted[0] # Start with the smallest community
 
 print 'Community {} using the weight type {} has {} members.'.format(comm_id, label_type, len(comm_dict[comm_id]))
 
 at_a_time = 5 # Open this many at a time.
 
 for ind, node in enumerate(comm_dict[comm_id]):
-	os.system("open 'http://twitter.com/account/redirect_by_id?id={}'".format(node))
+	webbrowser.open('http://twitter.com/account/redirect_by_id?id={}'.format(node))
 
 	if (ind+1)%at_a_time == 0:
 		raw_input("")

### 2014-01-14 code/filter_twitter_dataset.py

@@ -1,0 +1,346 @@
+#!/usr/bin/env python
+# -*- coding: utf-8 -*-
+import sys
+import igraph
+import math
+
+def integers_distribution(input_vector,string):
+	outfile = open(string+'_distribution.txt','w')
+	xmax = max(input_vector)
+	hist_vector_temp = []
+	for i in range(xmax+1):
+		hist_vector_temp.append(0)
+	for i in input_vector:
+		hist_vector_temp[i] += 1
+	for i in range(len(hist_vector_temp)):
+		if hist_vector_temp[i] != 0:
+			outfile.write('%d\t%d\n'%(i,hist_vector_temp[i]))
+	outfile.close()
+
+isuser = 0
+isfollower = 0
+
+infile = open('data/_follower_15K_user.txt/_follower_15K_user.txt','r')
+lines = infile.readlines()
+nodes = set(); edges = []; neighbors = {}
+for line in lines:
+	row = line.split()
+	user = row[0]
+	follower = row[2]
+	nodes.add(user); nodes.add(follower)
+	edges.append((user,follower))
+#	if user == '51319087':
+#		isuser += 1
+#	if follower == '51319087':
+#		isfollower += 1
+	if user in neighbors: neighbors[user].append(follower)
+	else: neighbors[user] = [follower]
+infile.close()
+print 'number of nodes:',len(nodes)
+print 'number of edges:',len(edges)
+
+#print isuser,isfollower
+
+edges_weights = {}
+retweet_edges_weights = {}
+mentions_edges_weights = {}
+
+#hasretweeted = 0
+#wasretweeted = 0
+#hasmentioned = 0
+#wasmentioned = 0
+
+infile = open('data/retweets-mentions/retweets2011_userid.tsv','r')
+lines = infile.readlines()
+user_hasretweeted = {}
+for u in nodes: user_hasretweeted[u] = 0
+user_wasretweeted = {}
+for u in nodes: user_wasretweeted[u] = 0
+retweets_nodes = set()
+nb_retweets = 0
+for line in lines:
+	row = line.split('\t')	
+	u1 = row[1]
+	u2 = row[2][:-1]
+	retweets_nodes.add(u1)
+	retweets_nodes.add(u2)
+#	if u1 == '51319087':
+#		hasretweeted += 1
+#	if u2 == '51319087':
+#		wasretweeted += 1
+	if u1 in nodes and u2 in nodes:
+		nb_retweets += 1
+		user_hasretweeted[u1] += 1
[…]

### 2014-01-14 paper/paper.tex
Added some text to the paper.
Added my attempt at the abstract.
Added sections on aggregate statistics for the different community-types.
Modify Elisa's abstract.
Added References Final Title and Added Abstract

@@
 \usepackage{graphicx}
+\usepackage{multirow}
 \frenchspacing
@@
 /Title (Input Your Paper Title Here)
-/Author (John Doe, Jane Doe)
+/Author (David Darmon, Elisa Omodei, Joshua Garland)
 /Keywords (Input your paper keywords in this optional area)}
@@
 %Followers are not enough: Beyond structure in the detection of communities \\
-Followers are not enough: Exploring the communities that exist beyond structure \\
+Followers are Not Enough: Beyond Structural Communities in Online Social Networks%\\
 %Followers are not enough: Activity, Interaction, and Topic-based Communities in Online Social Networks \\
-%Followers are not enough: Beyond structural communities in online social networks
-% \\
 %Followers are not enough: exploring communities beyond structure
  }
+
 % \author{David Darmon  \\
@@
 \begin{quote}
-[[Joshua]]
-
-[[David]]
-
-[[Elisa]]
-
+Community detection in online social networks is typically based on the analysis of the explicit connections between users, such as ``friends" on Facebook and ``followers" on Twitter.
+But online users often have hundreds or even thousands of such connections, and many of these connections do not correspond to real friendships or more generally to accounts that users interact with.
+We claim that community detection in online social networks should be question-oriented and rely on additional information beyond the simple structure of the network.
+The concept of `community' is very general, and different questions such as ``who do we interact with?" and ``with whom do we share similar interests?" can lead to the discovery of different social groups.
+In this paper we focus on three types of communities beyond structural communities: activity-based, topic-based, and interaction-based.
+We analyze a Twitter dataset using three different weightings of the structural network meant to highlight these three community types, and then infer the communities associated with these weightings.
+We show that the communities obtained in the three weighted cases are highly different from each other, and from the communities obtained by considering only the unweighted structural network.
+Our results confirm that asking a precise question is an unavoidable first step in community detection in online social networks, and that different questions can lead to different insights into the network under study.
 \end{quote}
@@
 \input{parts/discussion.tex}
-\input{parts/conclusion.tex}
+\input{parts/conclusions.tex}
 

### 2014-01-14 paper/parts/methods.tex
Added References Final Title and Added Abstract

@@
 Community detection is a well studied but not yet solved problem, and several different methods and algorithms have been proposed.
-For a complete review of the subject we refer the reader to (\textbf{ref: Fortunato, Santo.
-"Community detection in graphs." Physics Reports 486.3 (2010): 75-174.}).
+For a complete review of the subject we refer the reader to \cite{fortunato2010community}.
 In our study we deal with \textit{weighted directed} networks, and we are interested in finding \textit{overlapping} modules, rather than partitions of the network, since people can belong to different social groups: they can be interacting with different groups of people (their college friends, their co-workers, their family, etc), and they can belong to different topical communities (a person can be interested both in cycling and politics and talk about the two topics with different groups of people).
-Most community detection algorithms developed so far are built to find partitions and only very few to find overlapping communities (\textbf{ref: J.
-Baumes, M.K.
-Goldberg, M.S.
-Krishnamoorthy, M.M.
-Ismail, N.
-Preston, Finding communities by clustering a graph into overlapping subgraphs, in: N.
-Guimaraes, P.T.
-Isaias (Eds.), IADIS AC, IADIS, 2005, pp.
-97–104; Palla, Gergely, et al.
- "Uncovering the overlapping community structure of complex networks in nature and society." Nature 435.7043 (2005): 814-818.; S.
-Zhang, R.-S.
-Wang, X.-S.
-Zhang, Identification of overlapping community structure in complex networks using fuzzy c-means clustering, Physica A 374 (2007) 483–490; Gregory S (2007) An algorithm to find overlapping community structure in networks.
-In: Proceedings of the 11th European Conference on Principles and Practice of Knowledge Discovery in Databases (PKDD 2007).
-Berlin, Germany: Springer-Verlag. pp 91–102.; T. Nepusz, A. Petroczi, L. Negyessy, F. Bazso, Fuzzy communities and the concept of bridgeness in complex networks, Phys. Rev. E 77 (1) (2008) 016107; 
-Lancichinetti A, Fortunato S, Kertesz J (2009) Detecting the overlapping and hierarchical community structure in complex networks. New J Phys 11: 033015.; 
-vans TS, Lambiotte R (2009) Line graphs, link partitions, and overlapping communities. Phys Rev E 80: 016105. 25; Kovacs, Istvan A., et al. (2010) 
-Community landscapes: An integrative approach to determine overlapping network module hierarchy, identify key nodes and predict network dynamics. PloS ONE 5: e12528}). 
-Among these, even fewer can also deal with directed or weighted networks.
+Most community detection algorithms developed so far are built to find partitions and only very few to find overlapping communities \cite{BaumesGKMP05,PalEtAl05,ZhaWanZha07,Gre07,PhysRevE.77.016107,Lancichinetti2009,PhysRevE.80.016105,Kovacs2010} Among these, even fewer can also deal with directed or weighted networks.
 Palla et al.
-clique percolation method can for example take into account these two features, but not both at the same time (\textbf{ref: Palla, Gergely, et al.
-"Uncovering the overlapping community structure of complex networks in nature and society." Nature 435.7043 (2005): 814-818.}).
+clique percolation method can for example take into account these two features, but not both at the same time \cite{PalEtAl05}.
 Lancichinetti et.
-al recently proposed the first method that is able to deal with all these features and a few more at the same time, called OSLOM (Order Statistics Local Optimization Method) (\textbf{ref: Lancichinetti, A., Radicchi, F., Ramasco, J.
-J., and Fortunato, S.
-(2011).
-Finding statistically significant communities in networks.
-PloS one, 6(4), e18961.}).
+al recently proposed the first method that is able to deal with all these features and a few more at the same time, called OSLOM (Order Statistics Local Optimization Method) \cite{LancichinettiPlos}.
 Their method "is based on the local optimization of a fitness function expressing the statistical significance of clusters with respect to random fluctuations" (\textbf{taken from their paper, to rephrase}), and it allowed us to detect overlapping communities on our weighted directed networks.

### 2014-01-14 paper/parts/methods.tex
new references

@@
 where $n_i(u)$ is the frequency of the hashtag $i$ in the set of user $u$'s tweets, $N$ is the total number of users, and $n_i$ is the number of users that have used the hashtag $i$ in their tweets.
-This adapted term frequency--inverse document frequency (tf-idf) measure (\textbf{ref: Salton, Gerard, and Michael J.
-McGill.
-"Introduction to modern information retrieval." (1986).}) captures the importance of a hashtag in the users's tweets through the first factor, but at the same time smooths it through the second factor by giving less importance to hashtags that are too widely used (as $\frac{N}{n_i}$ approaches one, its logarithm approaches zero).
+This adapted term frequency--inverse document frequency (tf-idf) measure \cite{salton_introduction_1983} captures the importance of a hashtag in the users's tweets through the first factor, but at the same time smooths it through the second factor by giving less importance to hashtags that are too widely used (as $\frac{N}{n_i}$ approaches one, its logarithm approaches zero).
 For each couple of user linked in the user-follower network, we then compute the cosine similarity of their respective vectors, and assign the obtained value as the weight of the directed edge(s) connecting them.

### 2014-01-14 paper/parts/results.tex
Fixed some broken pointers to tables / sections. Modified the header to include section numbers.

@@
 
-We begin by examining the overall statistics for the communities inferred by OSLOM using the weightings defined in Sections \ref{method-activity}, \ref{method-interaction}, and \ref{method-topic}.
+We begin by examining the overall statistics for the communities inferred by OSLOM using the weightings defined in Sections \ref{sec:method-activity}, \ref{sec:method-interaction}, and \ref{sec:method-topic}.
 The number of communities by community type is given in Table~\ref{Table-comm_count}.
@@
 \begin{table}[ht]
-	\label{Table-comm_count}
 	\caption{Number of non-singleton communities and singletons by community type: S(tructural), A(ctivity -based), T(opic-based), and I(nteraction-based).}
@@
 	\end{tabular}
+	\label{Table-comm_count}
 \end{table}
@@
 
-\begin{figure}[h!]
+\begin{figure}[ht]
   \centering

### 2014-01-15 paper/drafts/intro.tex
Starting on rewrite of the intro.
Rewrote more of the intro. Added a related works section.

--- 2013-12-02 paper/parts/intro.tex
@@
+%File: formatting-instruction.tex
+\documentclass[letterpaper]{article}
+\usepackage{times}
+\usepackage{helvet}
+\usepackage{courier}
+\usepackage{amssymb, amsmath, amsthm}
+\usepackage{graphicx}
+\usepackage{multirow}
+
+\begin{document}
+
 \section{Introduction}
 
-Lorem ipsum.
+Networks play a central role in online social networks like Twitter, Facebook, and Google+.
+These services allow a user to interact with other based on the online social network they curate, also known as contact filtering~\cite{cazabet2012automated}.
+For example, `friends' on Facebook represent reciprocal links for sharing information, while `followers' on Twitter allow a single user to broadcast information in a one-to-many fashion.
+Central to all of these interactions is the fact that the \emph{structure} of the social network dictates the ways that information can be broadcast or diffuse through the service.
 
-\cite{schreiber2000measuring}, \cite{ver2012information}, \cite{shalizi2007discovering}, \cite{paninski2003estimation}
+Because of the importance of structural networks, a large amount of work has focused on using structural networks to detect communities in online social media.
+Here, we use the term community to mean the standard definition of collection of nodes (users) within the network who are more highly connected to each than to users outside of the community~\cite{newman2004finding}.
+For instance, in~\cite{java2009we}, the authors use a friendship network to determine communities within Twitter, and note that conversations tend to occur within these communities.
+The approach of focusing on structural networks makes sense for `real-world' sociological experiments, where obtaining additional information about users interactions may be expensive and time-consuming.
+However, with the prevalence of large, rich data sets for online social networks, additional information beyond the structure alone may be incorporated, and more realistically reflects how users interact with each other on social media services.
 
-Our SFI paper: \cite{darmon2013detecting}
+% \cite{tang2010community} lectures on community detection
+
+% \cite{conover2011political} Retweet-mention analysis for political polarization analysis
+% http://truthy.indiana.edu/site_media/pdfs/conover_icwsm2011_polarization.pdf
+
+% \cite{de2011generalized} Develop a method for using structural network on Facebook.
+
+% \cite{nguyen2011adaptive} Uses a dynamic community detection algorithm (that uses snapshots of the network), but still focuses on \emph{structural} ties (Facebook friendship relationships)
+
+% \cite{xu2011sentiment} Generate 'sentiment' networks.
+
+% \cite{lim2012tweets} This one is *very* important: they also note that structural links do not indicate communication.
+They use an interaction-based approach (mentions only).
+But they do not use a weighted version of the structural network.
+Instead, they use .
+And they do not go into much depth comparing how the two types of communities (structural and activity-based) differ.
+Moreover, they explicitly seed their network to focus around a particular topic (country music, tennis, basketball, etc.)
+
+A large body of work exists on methods for automatic detection of communities within networks~\cite{newman2004fast,newman2004finding,rosvall2008maps, blondel2008fast,LancichinettiPlos}.
+See~\cite{fortunato2010community} for a recent review.
+All these methods \emph{begin} with a given network, and then attempt to uncover structure present in the network.
+That is, they are agnostic to how the network was constructed.
+Because of this, we propose that in answering any sort of question about the communities present in a data set, it is important to begin with a clear picture of the type of community under consideration, and then to tailor the construction of the network and the use of detection algorithms towards that goal.
+
+This is especially true for social network analysis.
+In online social networks, `community' could could refer to several possible structures.
+The simplest definition of community, as we have seen, might stem from the network of explicit connections between users on a service (friends, followers, etc.).
+On small time scales, these connections are more or less static, and we might instead determine communities based on who is talking to whom.
+On a more abstract level, a user might consider themselves part of a community of people discuss similar topics.
+We might also define communities as collections of people who exhibit similar behaviors on a service, as in a communities of teenagers vs.\ elderly users.
+We can characterize these types of communities based on the types of questions we might ask about them:
+\begin{itemize}
+	\item \textbf{Structure-based:} Who are you friends with? Who do you follow?
+	\item \textbf{Activity-based:} Who do you act like?
+	\item \textbf{Topic-based:} What do you talk about?
+	\item \textbf{Interaction-based:} Who do you talk to? Who do you talk about?
+\end{itemize}
+
+We propose looking at when and how communities motivated by different questions overlap, and whether different approaches to asking the question, ``What community are you in?'' leads to different insights about a social network.
+For example, a user on Twitter might connect mostly with computational social scientists, talk mostly about machine learning, interact soley with close friends (who may or may not be computational social scientists), and utilize the service only on nights and weekends.
+Each of these different `profiles' of the user would be highlighted by a different view of the users social network.
+We divide our approaches into four categories based on the questions outlined above: structure-based, activity-based, topic-based, and interaction-based.
+The structure-based approach, as outlined above, is most common, and for our data relies on reported follower relationships.
+
+The activity-based approach is motivated by the question of which individuals act in a concerted manner.
+The main tools for answering this question stem from information theory.
+We consider each user on an online social network as an information processing unit, but ignore the content of their messages.
+This viewpoint has been successfully applied to gain insight into local behavior in online social networks~\cite{darmon2013understanding}.
+The information processing framework applies equally well to spatially extended systems.
+In particular, our current activity-based approach was originally motivated by a methodology used to detect functional communities within populations of neurons~\cite{shalizi2007discovering}.
+This approach has been extended to social systems, detecting communities on Twitter based on undirected information flow~\cite{darmon2013detecting}.
+Others have successfully applied a similar viewpoint using transfer entropy, a measure of directed information flow, to perform link detection on Twitter~\cite{ver2012information}.
+However, the use of transfer entropy has not been used for community detection, and we extend this previous work to incorporate transfer entropy-based communities.
+
+Our topic-based and interaction-based approaches, in contrast to the activity-based approach, rely on the \emph{content} of a user's interaction and ignore its temporal component.
+The content contains a great deal of information about the communication between users.
+For example, a popular approach to analyzing social media data is to use Latent Dirichlet Allocation (LDA) to infer topics based on the prevalence of words within a status~\cite{zhao2011comparing,michelson2010discovering}.
+The LDA model can then be used to infer distributions over latent topics, and the similarity of two users with respect to topics may be defined in terms of the distance between their associated topic distributions.
+Because our focus is not on topic identification, we apply a simpler approach using hashtags as a proxy for topics~\cite{becker2011beyond,tsur2012s}.
+We can then define the similarity of two users in terms of their hashtags, and use this similarity to build a topic-based network.
+The interaction-based approach relies on meta-data about who a user converses with on the social media service.
+On Twitter, we can use mentions (indicating a directed communication) and retweets (indicating endorsement of another user) to identify conversation.
+Moreover, we can define a directed influence between two users by considering the attention paid to that user compared to all other users.
+This allows us to generate a network based on conversations and user interaction.
+
+The activity-based, topic-based, and interaction-based networks allow us to build a more complete picture of the \emph{latent} social network present in online social media, as opposed to the \emph{explicit} social network indicated by structural links.
+In this paper, we explore the relation between these various possible networks and their corresponding communities.
+We begin by describing the methodologies used to generate the various types of networks, and infer their community structure.
+We then explore how the communities of users differ depending on the type of network used.
+\textbf{TK: Put a blurb here about the qualitative study.} Finally, we explore how the different communities relate in terms
+
+\section{Related Work}
+
+Most previous work on communities in online social networks have focused on these types of communities in isolation. For instance \textbf{(References from links.txt go here.)}
+
+A notable exception to the analysis of different types of networks is~\cite{lim2012tweets}, which considered both structure-based and interaction-based communities on Twitter. However ...
+
+\textbf{TK: Look into the use of `multilevel' / hybrid networks in social media.}
+
+\end{document}

### 2014-01-15 paper/parts/intro.tex
Added some text to the paper.
Rewrote more of the intro. Added a related works section.

--- 2013-12-02 paper/parts/intro.tex
@@
 
-Lorem ipsum.
+Networks play a central role in online social networks like Twitter, Facebook, and Google+.
+These services allow a user to interact with other based on the online social network they curate, also known as contact filtering\cite{cazabet2012automated}.
+For example, `friends' on Facebook represent reciprocal links for sharing information, while `followers' on Twitter allow a single user to broadcast information in a one-to-many fashion.
+Central to all of these interactions is the fact that the \emph{structure} of the social network dictates the ways that information can be broadcast or diffuse through the service.
 
-\cite{schreiber2000measuring}, \cite{ver2012information}, \cite{shalizi2007discovering}, \cite{paninski2003estimation}
+Because of the importance of structural networks, a large amount of work has focused on using structural networks to detect communities in online social media.
+Here, we use the term community to mean the standard definition of collection of nodes (users) within the network who are more highly connected to each than to users outside of the community~\cite{newman2004finding}.
+For instance, in~\cite{java2009we}, the authors use a friendship network to determine communities within Twitter, and note that conversations tend to occur within these communities.
+The approach of focusing on structural networks makes sense for `real-world' sociological experiments, where obtaining additional information about users interactions may be expensive and time-consuming.
+However, with the prevalence of large, rich data sets for online social networks, additional information beyond the structure alone may be incorporated, and more realistically reflects how users interact with each other on social media services.
 
-Our SFI paper: \cite{darmon2013detecting}
+% \cite{tang2010community} lectures on community detection
+
+% \cite{conover2011political} Retweet-mention analysis for political polarization analysis
+% http://truthy.indiana.edu/site_media/pdfs/conover_icwsm2011_polarization.pdf
+
+% \cite{de2011generalized} Develop a method for using structural network on Facebook.
+
+% \cite{nguyen2011adaptive} Uses a dynamic community detection algorithm (that uses snapshots of the network), but still focuses on \emph{structural} ties (Facebook friendship relationships)
+
+% \cite{xu2011sentiment} Generate 'sentiment' networks.
+
+% \cite{lim2012tweets} This one is *very* important: they also note that structural links do not indicate communication.
+They use an interaction-based approach (mentions only).
+But they do not use a weighted version of the structural network.
+Instead, they use .
+And they do not go into much depth comparing how the two types of communities (structural and activity-based) differ.
+Moreover, they explicitly seed their network to focus around a particular topic (country music, tennis, basketball, etc.)
+
+A large body of work exists on methods for automatic detection of communities within networks~\cite{newman2004fast,newman2004finding,rosvall2008maps, blondel2008fast,LancichinettiPlos}.
+See~\cite{fortunato2010community} for a recent review.
+All these methods \emph{begin} with a given network, and then attempt to uncover structure present in the network.
+That is, they are agnostic to how the network was constructed.
+Because of this, we propose that in answering any sort of question about the communities present in a data set, it is important to begin with a clear picture of the type of community under consideration, and then to tailor the construction of the network and the use of detection algorithms towards that goal.
+
+This is especially true for social network analysis.
+In online social networks, `community' could could refer to several possible structures.
+The simplest definition of community, as we have seen, might stem from the network of explicit connections between users on a service (friends, followers, etc.).
+On small time scales, these connections are more or less static, and we might instead determine communities based on who is talking to whom.
+On a more abstract level, a user might consider themselves part of a community of people discuss similar topics.
+We might also define communities as collections of people who exhibit similar behaviors on a service, as in a communities of teenagers vs.\ elderly users.
+We can characterize these types of communities based on the types of questions we might ask about them:
+\begin{itemize}
+	\item \textbf{Structure-based:} Who are you friends with? Who do you follow?
+	\item \textbf{Activity-based:} Who do you act like?
+	\item \textbf{Topic-based:} What do you talk about?
+	\item \textbf{Interaction-based:} Who do you talk to? Who do you talk about?
+\end{itemize}
+
+We propose looking at when and how communities motivated by different questions overlap, and whether different approaches to asking the question, ``What community are you in?'' leads to different insights about a social network.
+For example, a user on Twitter might connect mostly with computational social scientists, talk mostly about machine learning, interact soley with close friends (who may or may not be computational social scientists), and utilize the service only on nights and weekends.
+Each of these different `profiles' of the user would be highlighted by a different view of the users social network.
+We divide our approaches into four categories based on the questions outlined above: structure-based, activity-based, topic-based, and interaction-based.
+The structure-based approach, as outlined above, is most common, and for our data relies on reported follower relationships.
+
+The activity-based approach is motivated by the question of which individuals act in a concerted manner.
+The main tools for answering this question stem from information theory.
+We consider each user on an online social network as an information processing unit, but ignore the content of their messages.
+This viewpoint has been successfully applied to gain insight into local behavior in online social networks~\cite{darmon2013understanding}.
+The information processing framework applies equally well to spatially extended systems.
+In particular, our current activity-based approach was originally motivated by a methodology used to detect functional communities within populations of neurons~\cite{shalizi2007discovering}.
+This approach has been extended to social systems, detecting communities on Twitter based on undirected information flow~\cite{darmon2013detecting}.
+Others have successfully applied a similar viewpoint using transfer entropy, a measure of directed information flow, to perform link detection on Twitter~\cite{ver2012information}.
+However, the use of transfer entropy has not been used for community detection, and we extend this previous work to incorporate transfer entropy-based communities.
+
+Our topic-based and interaction-based approaches, in contrast to the activity-based approach, rely on the \emph{content} of a user's interaction and ignore its temporal component.
+The content contains a great deal of information about the communication between users.
+For example, a popular approach to analyzing social media data is to use Latent Dirichlet Allocation (LDA) to infer topics based on the prevalence of words within a status\cite{zhao2011comparing,michelson2010discovering}.
+The LDA model can then be used to infer distributions over latent topics, and the similarity of two users with respect to topics may be defined in terms of the distance between their associated topic distributions.
+Because our focus is not on topic identification, we apply a simpler approach using hashtags as a proxy for topics\cite{becker2011beyond,tsur2012s}.
+We can then define the similarity of two users in terms of their hashtags, and use this similarity to build a topic-based network.
+The interaction-based approach relies on meta-data about who a user converses with on the social media service.
+On Twitter, we can use mentions (indicating a directed communication) and retweets (indicating endorsement of another user) to identify conversation.
+Moreover, we can define a directed influence between two users by considering the attention paid to that user compared to all other users.
+This allows us to generate a network based on conversations and user interaction.
+
+The activity-based, topic-based, and interaction-based networks allow us to build a more complete picture of the \emph{latent} social network present in online social media, as opposed to the \emph{explicit} social network indicated by structural links.
+In this paper, we explore the relation between these various possible networks and their corresponding communities.
+We begin by describing the methodologies used to generate the various types of networks, and infer their community structure.
+We then explore how the communities of users differ depending on the type of network used.
+\textbf{TK: Put a blurb here about the qualitative study.} Finally, we explore how the different communities relate in terms
+
+\section{Related Work}
+
+Most previous work on communities in online social networks have focused on these types of communities in isolation. For instance \textbf{(References from links.txt go here.)}
+
+A notable exception to the analysis of different types of networks is~\cite{lim2012tweets}, which considered both structure-based and interaction-based communities on Twitter. However ...
+
+\textbf{TK: Look into the use of `multilevel' / hybrid networks in social media.}

### 2014-01-15 paper/drafts/intro.tex
Reworked more of the introduction and added a related work section.

@@
 The approach of focusing on structural networks makes sense for `real-world' sociological experiments, where obtaining additional information about users interactions may be expensive and time-consuming.
-However, with the prevalence of large, rich data sets for online social networks, additional information beyond the structure alone may be incorporated, and more realistically reflects how users interact with each other on social media services.
-
-% \cite{tang2010community} lectures on community detection
-
-% \cite{conover2011political} Retweet-mention analysis for political polarization analysis
-% http://truthy.indiana.edu/site_media/pdfs/conover_icwsm2011_polarization.pdf
-
-% \cite{de2011generalized} Develop a method for using structural network on Facebook.
-
-% \cite{nguyen2011adaptive} Uses a dynamic community detection algorithm (that uses snapshots of the network), but still focuses on \emph{structural} ties (Facebook friendship relationships)
-
-% \cite{xu2011sentiment} Generate 'sentiment' networks.
-
-% \cite{lim2012tweets} This one is *very* important: they also note that structural links do not indicate communication.
-They use an interaction-based approach (mentions only).
-But they do not use a weighted version of the structural network.
-Instead, they use .
-And they do not go into much depth comparing how the two types of communities (structural and activity-based) differ.
-Moreover, they explicitly seed their network to focus around a particular topic (country music, tennis, basketball, etc.)
+However, with the prevalence of large, rich data sets for online social networks, additional information beyond the structure alone may be incorporated, and more realistically reflects how users interact with each other on social media services~\cite{grabowicz2012social}.
 
@@
 Others have successfully applied a similar viewpoint using transfer entropy, a measure of directed information flow, to perform link detection on Twitter~\cite{ver2012information}.
-However, the use of transfer entropy has not been used for community detection, and we extend this previous work to incorporate transfer entropy-based communities.
+However, transfer entropy has not been used for community detection, and we extend this previous work to incorporate transfer entropy-based communities.
 
@@
 
-Most previous work on communities in online social networks have focused on these types of communities in isolation. For instance \textbf{(References from links.txt go here.)}
+Most previous work on communities in online social networks have focused on detecting communities based on a single type of network.
+For example, an early paper considered the communities, and associated statistics, for communities determined using a friendship network in Twitter~\cite{java2009we}.
+More recent work has considered the dynamics of communities based on structural links in Facebook~\cite{nguyen2011adaptive}.
 
-A notable exception to the analysis of different types of networks is~\cite{lim2012tweets}, which considered both structure-based and interaction-based communities on Twitter. However ...
+Information theoretic, activity-based approaches have been applied previously to the analysis of networks arising in online social media~\cite{ver2012information,darmon2013detecting}, but to the best of our knowledge this is the first use of transfer entropy for community detection.
 
-\textbf{TK: Look into the use of `multilevel' / hybrid networks in social media.}
+For interaction-based networks, \cite{conover2011political} considered both mention and retweet networks in isolation for a collection of users chosen for their political orientation.
+In~\cite{deitrick2013mutually}, the authors construct a dynamic network based on simple counts time-windowed of mentions and retweets, and use the evolution of this network to aid in community detection.
+
+There are two broad approaches to topic-based communities in the literature.
+\cite{rossi2012conversation} used a set of users collected based on their use of a single hashtag, and tracked the formation of follower and friendship links within the set of users.
+In~\cite{lim2012following}, the authors chose a set of topics to explore, and then seeded a network from a celebrity chosen to exemplify a particular topic.
+Both approaches thus begin with a particular topic in mind, and perform the data collection accordingly.
+Other approaches use probabilistic for the topics that treat community membership as a latent variable~\cite{yin2012latent}.
+
+% Structural:
+% ==========
+
+% \cite{java2009we} Determine friendship network on Twitter to define communities.
+
+% \cite{nguyen2011adaptive} Uses a dynamic community detection algorithm (that uses snapshots of the network), but still focuses on \emph{structural} ties (Facebook friendship relationships)
+
+% Interaction-based:
+% ==================
+
+% \cite{deitrick2013mutually} use 'dynamic' mention-retweet network to detect communities, but just augment the count of mentions retweets in the weighting (instead of using a proportion), and don't combine mentions and retweets.
+
+% \cite{conover2011political} Retweet-mention analysis for political polarization analysis
+% http://truthy.indiana.edu/site_media/pdfs/conover_icwsm2011_polarization.pdf
+
+% Activity-based:
+% ===============
+
+% None, to the best of our knowledge.
+
+% Topic-based:
+% ============
+
+% \cite{lim2012following} "We propose an efficient approach for detecting communities that share common interests on Twitter, based on linkages among followers of celebrities representing an interest category." Use both InfoMAP and clique percolation.
+
+% \cite{rossi2012conversation} Collect users who use the same hashtag (a *single* hashtag, #XF5, for XFactor 5), and then note if this impacts the friend/follower network.
+
+% \cite{xu2011sentiment} Generate 'sentiment' networks.
+
+% Most-relevant:
+% ==============
+
+% \cite{lim2012tweets} This one is *very* important: they also note that structural links do not indicate communication.
+They use an interaction-based approach (mentions only).
+But they do not use a weighted version of the structural network.
+Instead, they use .
+And they do not go into much depth comparing how the two types of communities (structural and activity-based) differ.
+Moreover, they explicitly seed their network to focus around a particular topic (country music, tennis, basketball, etc.)
+
+A notable exception to the analysis of isolated types of networks is~\cite{lim2012tweets}, which considered both structure-based and interaction-based communities on Twitter, as we have defined them.
+However, this study focuses on data collected based on particular topics (country music, tennis, and basketball), and not on a generic subpopulation of Twitter users.
+Moreover, it did not explore the differences in community structure resulting from the different network weightings, and focuses on aggregate statistics (community size, network statistics, etc.).
+Another notable exception is~\cite{kao2013talison}, where the authors use a tensor representation of user data to incorporate retweet and hashtag information into a study of the social media coverage of the Occupy Movement.
+The tensor can then be decomposed into factors in a generalization of the singular value decomposition of a matrix, and these factors can be used to determine `salient' users.
+However, this approach focused on data for a particular topic (the Occupy Movement) and did not collect users based on a structural network.
 

### 2014-01-15 paper/parts/intro.tex
Reworked more of the introduction and added a related work section.

@@
 Networks play a central role in online social networks like Twitter, Facebook, and Google+.
-These services allow a user to interact with other based on the online social network they curate, also known as contact filtering\cite{cazabet2012automated}.
+These services allow a user to interact with other based on the online social network they curate, also known as contact filtering~\cite{cazabet2012automated}.
 For example, `friends' on Facebook represent reciprocal links for sharing information, while `followers' on Twitter allow a single user to broadcast information in a one-to-many fashion.
@@
 The approach of focusing on structural networks makes sense for `real-world' sociological experiments, where obtaining additional information about users interactions may be expensive and time-consuming.
-However, with the prevalence of large, rich data sets for online social networks, additional information beyond the structure alone may be incorporated, and more realistically reflects how users interact with each other on social media services.
+However, with the prevalence of large, rich data sets for online social networks, additional information beyond the structure alone may be incorporated, and more realistically reflects how users interact with each other on social media services~\cite{grabowicz2012social}.
 
-% \cite{tang2010community} lectures on community detection
-
-% \cite{conover2011political} Retweet-mention analysis for political polarization analysis
-% http://truthy.indiana.edu/site_media/pdfs/conover_icwsm2011_polarization.pdf
-
-% \cite{de2011generalized} Develop a method for using structural network on Facebook.
-
-% \cite{nguyen2011adaptive} Uses a dynamic community detection algorithm (that uses snapshots of the network), but still focuses on \emph{structural} ties (Facebook friendship relationships)
-
-% \cite{xu2011sentiment} Generate 'sentiment' networks.
-
-% \cite{lim2012tweets} This one is *very* important: they also note that structural links do not indicate communication.
-They use an interaction-based approach (mentions only).
-But they do not use a weighted version of the structural network.
-Instead, they use .
-And they do not go into much depth comparing how the two types of communities (structural and activity-based) differ.
-Moreover, they explicitly seed their network to focus around a particular topic (country music, tennis, basketball, etc.)
-
-A large body of work exists on methods for automatic detection of communities within networks~\cite{newman2004fast,newman2004finding,rosvall2008maps, blondel2008fast,LancichinettiPlos}.
+A large body of work exists on methods for automatic detection of communities within networks~\cite{newman2004fast,newman2004finding,rosvall2008maps,blondel2008fast,LancichinettiPlos}.
 See~\cite{fortunato2010community} for a recent review.
@@
 That is, they are agnostic to how the network was constructed.
-Because of this, we propose that in answering any sort of question about the communities present in a data set, it is important to begin with a clear picture of the type of community under consideration, and then to tailor the construction of the network and the use of detection algorithms towards that goal.
+Because of this, we propose that in answering any sort of question about the communities present in a data set, it is important to begin with a clear picture of the community type under consideration, and then to tailor the construction of the network and the use of detection algorithms towards that goal.
 
@@
 On small time scales, these connections are more or less static, and we might instead determine communities based on who is talking to whom.
-On a more abstract level, a user might consider themselves part of a community of people discuss similar topics.
+On a more abstract level, a user might consider themselves part of a community of people discussing similar topics.
 We might also define communities as collections of people who exhibit similar behaviors on a service, as in a communities of teenagers vs.\ elderly users.
@@
 For example, a user on Twitter might connect mostly with computational social scientists, talk mostly about machine learning, interact soley with close friends (who may or may not be computational social scientists), and utilize the service only on nights and weekends.
-Each of these different `profiles' of the user would be highlighted by a different view of the users social network.
+Each of these different `profiles' of the user highlight different views of the user's social network, and represent different types of communities.
 We divide our approaches into four categories based on the questions outlined above: structure-based, activity-based, topic-based, and interaction-based.
@@
 The content contains a great deal of information about the communication between users.
-For example, a popular approach to analyzing social media data is to use Latent Dirichlet Allocation (LDA) to infer topics based on the prevalence of words within a status\cite{zhao2011comparing,michelson2010discovering}.
+For example, a popular approach to analyzing social media data is to use Latent Dirichlet Allocation (LDA) to infer topics based on the prevalence of words within a status~\cite{zhao2011comparing,michelson2010discovering}.
 The LDA model can then be used to infer distributions over latent topics, and the similarity of two users with respect to topics may be defined in terms of the distance between their associated topic distributions.
-Because our focus is not on topic identification, we apply a simpler approach using hashtags as a proxy for topics\cite{becker2011beyond,tsur2012s}.
+Because our focus is not on topic identification, we apply a simpler approach using hashtags as a proxy for topics~\cite{becker2011beyond,tsur2012s}.
 We can then define the similarity of two users in terms of their hashtags, and use this similarity to build a topic-based network.
+
 The interaction-based approach relies on meta-data about who a user converses with on the social media service.
@@
 Moreover, we can define a directed influence between two users by considering the attention paid to that user compared to all other users.
-This allows us to generate a network based on conversations and user interaction.
+This allows us to generate a network based on conversations and user interactions.
 
@@
 We then explore how the communities of users differ depending on the type of network used.
-\textbf{TK: Put a blurb here about the qualitative study.} Finally, we explore how the different communities relate in terms
+\textbf{TK: Put a blurb here about the qualitative study.} Finally, we explore how communication patterns differ across and within the different community types.
 
@@
 
-Most previous work on communities in online social networks have focused on these types of communities in isolation. For instance \textbf{(References from links.txt go here.)}
+Most previous work on communities in online social networks have focused on detecting communities based on a single type of network.
+For example, an early paper considered the communities, and associated statistics, inferred from a friendship network in Twitter~\cite{java2009we}.
+More recent work has considered the dynamics of communities based on structural links in Facebook~\cite{nguyen2011adaptive}.
 
-A notable exception to the analysis of different types of networks is~\cite{lim2012tweets}, which considered both structure-based and interaction-based communities on Twitter. However ...
+Information theoretic, activity-based approaches have been applied previously to the analysis of networks arising in online social media~\cite{ver2012information,darmon2013detecting}, but to the best of our knowledge this is the first use of transfer entropy for community detection.
 
-\textbf{TK: Look into the use of `multilevel' / hybrid networks in social media.}
+For interaction-based networks, \cite{conover2011political} considered both mention and retweet networks in isolation for a collection of users chosen for their political orientation.
+In~\cite{deitrick2013mutually}, the authors construct a dynamic network based on simple time-windowed counts of mentions and retweets, and use the evolution of this network to aid in community detection.
+
+There are two broad approaches to topic-based communities in the literature.
+\cite{rossi2012conversation} used a set of users collected based on their use of a single hashtag, and tracked the formation of follower and friendship links within that set of users.
+In~\cite{lim2012following}, the authors chose a set of topics to explore, and then seeded a network from a celebrity chosen to exemplify a particular topic.
+Both approaches thus begin with a particular topic in mind, and perform the data collection accordingly.
+Other approaches use probabilistic models for the topics that treat community membership as a latent variable~\cite{yin2012latent}.
+
+% Structural:
+% ==========
+
+% \cite{java2009we} Determine friendship network on Twitter to define communities.
+
+% \cite{nguyen2011adaptive} Uses a dynamic community detection algorithm (that uses snapshots of the network), but still focuses on \emph{structural} ties (Facebook friendship relationships)
+
+% Interaction-based:
+% ==================
+
+% \cite{deitrick2013mutually} use 'dynamic' mention-retweet network to detect communities, but just augment the count of mentions retweets in the weighting (instead of using a proportion), and don't combine mentions and retweets.
+
+% \cite{conover2011political} Retweet-mention analysis for political polarization analysis
+% http://truthy.indiana.edu/site_media/pdfs/conover_icwsm2011_polarization.pdf
+
+% Activity-based:
+% ===============
+
+% None, to the best of our knowledge.
+
+% Topic-based:
+% ============
+
+% \cite{lim2012following} "We propose an efficient approach for detecting communities that share common interests on Twitter, based on linkages among followers of celebrities representing an interest category." Use both InfoMAP and clique percolation.
+
+% \cite{rossi2012conversation} Collect users who use the same hashtag (a *single* hashtag, #XF5, for XFactor 5), and then note if this impacts the friend/follower network.
+
+% \cite{xu2011sentiment} Generate 'sentiment' networks.
+
+% Most-relevant:
+% ==============
+
+% \cite{lim2012tweets} This one is *very* important: they also note that structural links do not indicate communication.
+They use an interaction-based approach (mentions only).
+But they do not use a weighted version of the structural network.
+Instead, they use .
+And they do not go into much depth comparing how the two types of communities (structural and activity-based) differ.
+Moreover, they explicitly seed their network to focus around a particular topic (country music, tennis, basketball, etc.)
+
+A notable exception to the analysis of isolated types of networks is~\cite{lim2012tweets}, which considered both structure-based and interaction-based communities on Twitter.
+However, this study focuses on data collected based on particular topics (country music, tennis, and basketball), and not on a generic subpopulation of Twitter users.
+Moreover, it did not explore the differences in community structure resulting from the different network weightings, and focuses on aggregate statistics (community size, network statistics, etc.).
+Another notable exception is~\cite{kao2013talison}, where the authors use a tensor representation of user data to incorporate retweet and hashtag information into a study of the social media coverage of the Occupy Movement.
+The tensor can then be decomposed into factors in a generalization of the singular value decomposition of a matrix, and these factors can be used to determine `salient' users.
+However, this approach focused on data for a particular topic (the Occupy Movement) and did not collect users based on a structural network.

### 2014-01-15 paper/parts/methods.tex
Fixed some broken pointers to tables / sections. Modified the header to include section numbers.
Fixed minor typo.

@@
 \subsection{Activity-Based Communities and Transfer Entropy}
-
-\label{method-activity}
+\label{sec:method-activity}
 
@@
 for all $t$.
-That is, the predictive distribution only depends on the past, not on when the past is observed\footnote{We really only need \emph{conditional} stationarity~\cite{caires2003nonparametric}, but stationarity implies conditional stationarity}.
+That is, the predictive distribution only depends on the past, not on when the past is observed\footnote{We really only need \emph{conditional} stationarity~\cite{caires2003nonparametric}, but stationarity implies conditional stationarity.}.
 Given this assumption, we compute estimators for $p(x_{k+1} | x_{1}^{k})$ and $p(x_{k+1} | x_{1}^{k}, y_{1}^{k})$ by `counting': for each possible past $(x_{1}^{k}, y_{1}^{k})$, we count the number of times a future of type $x_{k+1}$ occurs, and normalize.
@@
 
-\section{Interaction-Based Communities and Mention / Retweet Weighting}
-
-\label{method-interaction}
+\subsection{Interaction-Based Communities and Mention / Retweet Weighting}
+\label{sec:method-interaction}
 
@@
 
-\section{Topic-based Communities and Hashtag Weighting}
-
-\label{method-topic}
+\subsection{Topic-based Communities and Hashtag Weighting}
+\label{sec:method-topic}
 

### 2014-01-16 code/community_sizes.R
Fix complementary ecdf.

@@ -11,7 +11,7 @@ max.comm.size = 811
 
 pdf(sprintf('figures/comm_sizes_ecdf.pdf'))
 par(mar=c(4.5,5,2,1), cex.lab = 2, cex.axis = 2)
-plot(0, cex = 0, log = 'xy', type = 'l', xlim = c(1, max.comm.size), ylim = c(1e-4, 0.5), xlab = 'c', ylab = 'Proportion of communities larger than c')
+plot(0, cex = 0, log = 'xy', type = 'l', xlim = c(1, max.comm.size), ylim = c(1e-4, 1), xlab = 'c', ylab = 'Proportion of communities larger than c')
 
 for (cur.ind in 1:4){
 	cat(sprintf('\n\n====\n\n'))
@@ -51,7 +51,7 @@ for (cur.ind in 1:4){
 	# x = seq(min(counts.without.singletons), 800, by = 0.01)
 
 	F = ecdf(comm.sizes)
-	x = seq(1, max(comm.sizes), by = 0.01)
+	x = seq(0.1, max(comm.sizes), by = 0.01)
 
 	cat(sprintf('%f\n\n', min(1-F(x))))
 

### 2014-01-16 paper/parts/intro.tex

@@
 Networks play a central role in online social networks like Twitter, Facebook, and Google+.
-These services allow a user to interact with other based on the online social network they curate, also known as contact filtering~\cite{cazabet2012automated}.
+These services allow a user to interact with others based on the online social network they curate, also known as contact filtering~\cite{cazabet2012automated}.
 For example, `friends' on Facebook represent reciprocal links for sharing information, while `followers' on Twitter allow a single user to broadcast information in a one-to-many fashion.
@@
 Because of the importance of structural networks, a large amount of work has focused on using structural networks to detect communities in online social media.
-Here, we use the term community to mean the standard definition of collection of nodes (users) within the network who are more highly connected to each than to users outside of the community~\cite{newman2004finding}.
+Here, we use the term community with the standard definition: a collection of nodes (users) within the network who are more highly connected to each other than to users outside of the community~\cite{newman2004finding}.
 For instance, in~\cite{java2009we}, the authors use a friendship network to determine communities within Twitter, and note that conversations tend to occur within these communities.
@@
 See~\cite{fortunato2010community} for a recent review.
-All these methods \emph{begin} with a given network, and then attempt to uncover structure present in the network.
-That is, they are agnostic to how the network was constructed.
-Because of this, we propose that in answering any sort of question about the communities present in a data set, it is important to begin with a clear picture of the community type under consideration, and then to tailor the construction of the network and the use of detection algorithms towards that goal.
+All these methods \emph{begin} with a given network, and then attempt to uncover structure present in the network, i.e., they are agnostic to how the network was constructed.
+As opposed to this agnostic analysis, we propose and illustrate the importance of a deeper analysis.
+We believe that in order to understand the communities present in a data set, it is important to begin with a clear picture of the community type under consideration, and then to tailor the construction of the network and the use of detection algorithms towards that goal.
 
 This is especially true for social network analysis.
-In online social networks, `community' could could refer to several possible structures.
+In online social networks, `community' could refer to several possible structures.
 The simplest definition of community, as we have seen, might stem from the network of explicit connections between users on a service (friends, followers, etc.).
@@
 
-The activity-based approach is motivated by the question of which individuals act in a concerted manner.
+The activity-based approach is motivated by the question of which individuals act in a concerted manner, e.g., which users use a service with similar frequency and at similar times of day.
 The main tools for answering this question stem from information theory.

### 2014-01-16 paper/parts/results.tex
Fixed figure. Fixed a few minor typos.

@@
 
-For example, Figure~\ref{Fig-edge_types} shows the distributions of hashtag-based weights for the largest community defined by the mention-retweet network.
+For example, Figure~\ref{Fig-dist_across_community} shows the distributions of hashtag-based weights for the largest community defined by the mention-retweet network.
 We see that the distribution of internal-to-internal hashtag weights has a longer tail than either the external-to-internal or internal-to-external hashtag weights, with edges within the community having higher weights than edges crossing the boundary of the community.
@@
 We see that overall, the
+
+\subsection{Qualitative Analysis}
+
+In order to further explore the differences between the communities obtained through the various weightings, we also performed a qualitative analysis of such communities.
+Some interesting examples are, for instance, communities in the topic-based network such as one composed of 83 users who talk about environmental issues and frequently use hashtags such as \#green, \#eco and \#sustainability, and another one 47 users talking about small businesses and entrepreneurship, characterized by hashtags such as \#smallbiz, \#marketing and \#enterpreneur.
+In both cases most members of the topic-based communities are not found in the same community in the other networks, indicating that these people talk about the same things and can therefore be considered a thematic community, but do not strongly interact with each other nor behave the same, and so belong to different social groups with respect to interactions and behavior.
+Another interesting example is the one of a community thematically focused on Denver and Colorado, whose users do not belong to the same community in the interaction networks, but most of them do belong to the same community in the information based network.
+This indicates that these users react on the same events and issues regarding Colorado and are therefore strongly connected in the topic-based and in the activity-based networks, but at the same time they do not directly interact with each other and are therefore more loosely connected in the interaction-based networks, where they belong to different communities.

### 2014-01-16 code/analyze_weights_by_community_types.R

@@ -39,11 +39,11 @@ kde.positive.support = function(x){
 # weight_type = 'hashtag'
 # weight_type = 'mention-retweet'
 
-label_types = c('struc', 'TE4', 'hashtag', 'mention-retweet')
-weight_types = c('TE4', 'hashtag', 'mention-retweet')
+# label_types = c('struc', 'TE4', 'hashtag', 'mention-retweet')
+# weight_types = c('TE4', 'hashtag', 'mention-retweet')
 
-# label_types = c('struc')
-# weight_types = c('hashtag')
+label_types = c('mention-retweet')
+weight_types = c('hashtag')
 
 comms = 0:9
 
@@ -65,7 +65,7 @@ for (comm_label in comms){
 	data_e.to.i[is.na(data_e.to.i)] = 0
 	data_i.to.e[is.na(data_i.to.e)] = 0
 
-	# xmax = 0.2
+	# xmax = 0.05
 	xmax = max(c(data_i.to.i, data_e.to.i, data_i.to.e))
 
 	# pdf(paste0('figures/', prefix, '_i-to-i-ecdf.pdf'))
@@ -83,7 +83,7 @@ for (comm_label in comms){
 	lwd = 2
 
 	pdf(paste0('figures/', prefix, '-ecdf.pdf'))
-	plot(ecdf(data_i.to.i), xlim = c(0, xmax), xlab = 'Weight', ylab = 'ECDF', main = '', col = 'red', lwd = lwd)
+	plot(ecdf(data_i.to.i), xlim = c(0, xmax), xlab = 'Weight', ylab = 'Empirical Distribution of Weights', main = '', col = 'red', lwd = lwd)
 	lines(ecdf(data_e.to.i), xlim = c(0, xmax), xlab = 'Weight', ylab = 'ECDF', main = '', col = 'blue', lwd = lwd)
 	lines(ecdf(data_i.to.e), xlim = c(0, xmax), xlab = 'Weight', ylab = 'ECDF', main = '', col = 'green', lwd = lwd)
 	legend('bottomright', c('Internal-to-Internal', 'External-to-Internal', 'Internal-to-External'), col = c('red', 'blue', 'green'), lwd = lwd, lty = rep(1, 3))

### 2014-01-16 paper/parts/methods.tex
Edits of Sections 1-3

@@
 \section{Methodology}
-
+\textbf{[[Add a quick paragraph that transitions and roadmaps this section]]}
 \subsection{Community Detection}
 
-In network theory communities are usually defined as group of nodes more densely connected among each other than with the rest of the network.
-Community detection is a well studied but not yet solved problem, and several different methods and algorithms have been proposed.
-For a complete review of the subject we refer the reader to \cite{fortunato2010community}.
-In our study we deal with \textit{weighted directed} networks, and we are interested in finding \textit{overlapping} modules, rather than partitions of the network, since people can belong to different social groups: they can be interacting with different groups of people (their college friends, their co-workers, their family, etc), and they can belong to different topical communities (a person can be interested both in cycling and politics and talk about the two topics with different groups of people).
-Most community detection algorithms developed so far are built to find partitions and only very few to find overlapping communities \cite{BaumesGKMP05,PalEtAl05,ZhaWanZha07,Gre07,PhysRevE.77.016107,Lancichinetti2009,PhysRevE.80.016105,Kovacs2010} Among these, even fewer can also deal with directed or weighted networks.
-Palla et al.
-clique percolation method can for example take into account these two features, but not both at the same time \cite{PalEtAl05}.
-Lancichinetti et.
-al recently proposed the first method that is able to deal with all these features and a few more at the same time, called OSLOM (Order Statistics Local Optimization Method) \cite{LancichinettiPlos}.
-Their method "is based on the local optimization of a fitness function expressing the statistical significance of clusters with respect to random fluctuations" (\textbf{taken from their paper, to rephrase}), and it allowed us to detect overlapping communities on our weighted directed networks.
+%[[Already defined]]In network theory communities are usually defined as group of %nodes more densely connected among each other than with the rest of the network.
+As discussed in the introduction, we adopt the usual definition of \emph{community}: a collection of nodes (users) within a network who are more densely connected to each other than with the rest of the network.
+Structural community detection is a well studied problem and several different methods and algorithms have been proposed; for a complete review of this subject we refer the reader to \cite{fortunato2010community}.
+In this paper however we focus on a class of networks and communities that is far less studied, in particular we study networks which are both \textit{weighted} and \textit{directed} and communities within those weighted directed networks that can (but need not) \emph{overlap}.
+When selecting a detection algorithm we propose that all three (weight, direction and overlap) are important for the following reasons: Twitter is a directed network and we wish to maintain this structure.
+But we are interested in not just structure but function, to capture function we use edge weightings which must be used in the community detection process.
+Finally, since people can belong to multiple and possibly overlapping social (e.g., college friends, co-workers, family, etc.) and topical (e.g., a user can be interested in both cycling and politics and use the network to discuss the two topics with the two different communities) communities, we are interested in finding \textit{overlapping} modules, rather than partitions of the weighted directed network.
+%For example, users can belong to multiple social groups such as college friends, %co-workers, family, etc.
+and these groups may but need not overlap.
+A user can also %belong to multiple topical communities, e.g., a user can be interested in both %cycling and politics and use the network to discuss the two topics with the two %different communities.
 
-\subsection{The Dataset}
+This poses an interesting problem because the majority of community detection algorithms developed so far are built to find partitions of a network and very few are aimed at finding overlapping communities \cite{BaumesGKMP05,PalEtAl05,ZhaWanZha07,Gre07,PhysRevE.77.016107,Lancichinetti2009,PhysRevE.80.016105,Kovacs2010}.
+Among these methods, even fewer deal with directed or weighted networks.
+\cite{PalEtAl05} clique percolation method can for example take into account these two features, but not both at the same time.
+\cite{LancichinettiPlos} recently proposed OSLOM (Order Statistics Local Optimization Method) which is the first method that is able to deal with all of these features at the same time; their method "is based on the local optimization of a fitness function expressing the statistical significance of clusters with respect to random fluctuations" (\textbf{taken from their paper, to rephrase}).
+For this paper we use OSLOM as it allowed us to detect \emph{overlapping} communities present in our \emph{weighted} \emph{and} \emph{directed} network.
 
-The data consists of the Twitter statuses of 15000 users over a 9 week period (from April 25th to June 25th 2011).
-The users are embedded in a network collected by performing a breadth-first expansion from a seed user.
-Once the seed user was chosen, the network was expanded to include his/her followers, only including users considered to be active (users who tweeted at least once per day over the past one hundred tweets).
-Network collection continued in this fashion by considering the active followers of the active followers of the seed, and so on.
-Since one of the kind of communities we want to explore is based on the explicit interactions between users, based on retweets and mentions, we filter the dataset in order to take into account only users who make use of this kind of features in their tweets.
-We define en event of outgoing information for a given user $u$ as either a mention made by $u$ of another user in the network, or a retweet by another user of one of $u$'s tweets.
-When we mention someone we are in fact sending him some information, and when we are retweeted it means that the person that retweeted us has received some information from us and is sharing it.
-Symmetrically, we define an event of incoming information for $u$ as either being mentioned, or retweeting another user.
-We filtered the network by eliminating all the users that have in their tweeting history less than 9 outgoing information and 9 incoming information events, i.e.
-less than one event per type per week on average.
-We then further restricted our analysis to the strong giant connected component of the unweighted directed network built from the filtered set of users and whose link represent a user-follower relationship.
-In this study the link is directed from the user to the follower because this is the direction in which the information flows.
-The final network consists of 6917 nodes and 1481131 edges.
+\subsection{The Initial Dataset and Network Construction}
+
+The dataset for this study consisted of the tweets of 15,000 Twitter users over a 9 week period (from April 25th to June 25th 2011).
+The users are embedded in a network collected by performing an intelligent breadth-first expansion from a random seed user.
+In particular, once the seed user was chosen, the network was expanded to include his/her followers, but only included users considered to be `active' (i.e., users who tweeted at least once per day over the past one hundred days).
+Network collection continued in this fashion by considering the active followers of the active followers of the seed, and so on until 15,000 users were added to the network.
+
+Since our goal is to explore the functional communities of this network, we filter this network down to the subset of users which actively interact with each other (e.g., retweets and mentions).
+We do this through a metric we call (incoming/outgoing) information events.
+We define an outgoing information event for a given user $u$ as either a mention made by $u$ of another user in the network, or if another user in the network retweets a tweet made by $u$.
+The logic for this definition is as follows, if $u$ mentions a user $v$ this can be thought of as $u$ directly sending information to $v$, and if $u$ is retweeted by $v$ then $v$ received information from $u$ and rebroadcast it to their followers.
+In either case there was information outgoing from $u$ which affected the network in the some way.
+Analogously, we define the incoming information event for $u$ as either being mentioned by a different user in the network, or by retweeting another user in the network.
+%function and information share is important We then filter down this starting %network to include only users that [[what??]]. To do this 
+%Since one of the community types we want to explore is based on the explicit interactions ( between users, we filter the dataset in order to take into account only users who make use of these kinds of features in their tweets.
+[[Seeems out of place]]
+%We define an event of outgoing information for a given user $u$ as either a mention made by $u$ of another user in the network, or a retweet by another user of one of $u$'s tweets. 
+%[[Switched the readers perspective]]When we mention someone we are in fact sending him some information, and when we are retweeted it means that the person that retweeted us has received some information from us and is sharing it.
+With (incoming/outgoing) information events defined we filtered the network by eliminating all users with less than 9 outgoing \emph{and} incoming information events, i.e., less than one information event per type per week on average.
+We then further restricted our analysis to the strong giant connected component of the network built from the (incoming/outgoing) information filtered set of users.
+%and whose link represent a user-follower relationship.
+In this study the link is directed from the user to the follower because this is the direction in which the information flows.\textbf{[[Josh: Is this the case for all the analysis or just the transfer entropy?]]} The final network consists of 6,917 nodes and 1,481,131 edges.
 
@@
 Thus, we reduce all of the information generated by a user on Twitter to a time series $\{ X_{t}(u)\}$ where $t$ ranges over the time interval for which we have data (9 weeks in this case).
-Because status updates are only collected in discrete, 1-second time intervals, it is natural to consider the only the discrete times $t = 1 \text{ s}, 2 \text{ s}, \ldots, $ relative to a reference time.
+Since tweets are only collected in discrete, 1-second time intervals, it is natural to consider only the discrete times $t = 1 \text{s}, 2 \text{s}, \ldots, $ relative to a reference time.
 We can then compute the flow of information between two users $u$ and $v$ by computing the transfer entropy between their time series $X_{t}(u)$ and $X_{t}(v).$
@@
 We then compute the transfer entropy on these coarsened time series taking $k$ to range from 1 to 6, which corresponds to a lag of ten minutes to an hour.
+\textbf{[[Josh: Dave do you think we should talk about why we chose 1-6 and why we chose 10 minutes.
+If so this would be a good place.
+I think this is a great explanation however.]] }
 
@@
 
-A way of tracking the flow of information through users is by considering two useful features of this social network: mentions and retweets.
-Through mentions users can in fact send a direct message to other users.
-And a retweet means that a piece of information from a user has been captured by a follower and shared with his/her own followers.
-We can therefore define interaction-based communities by weighting the user-follower network with a measure proportional to the number of mentions and retweets between users.
-In more details, for each couple of user-follower $u$ and $f$, we use the arithmetic / harmonic (\textbf{which one?}) mean of the two following numbers:
+Retweets and mentions are two useful features of Twitter networks which can be used to track information flow through the network.
+%A way of tracking the flow of information through users is by considering two useful features of this social network: mentions and retweets. 
+With mentions users are sending directed information to other users and with retweets users are rebroadcasting information from a user they follow to all of their followers. 
+%information from a user has been captured by a follower and shared with his/her own followers. 
+This type of information flow defines a community in a much different way than transfer entropy did.
+Instead of defining communities by the loss of uncertainty in one users tweeting history based on anothers, we define an interaction-based communities by weighting the user-follower network with a measure proportional to the number of mentions and/or retweets between users.
+% We can therefore define interaction-based communities by weighting the user-follower network with a measure proportional to the number of mentions and retweets between users. 
+For the interaction-based communities we consider three weighting schema: proportional retweets
 \begin{equation}
-\frac{\mbox{\# mentions of }f \mbox{ by }u}{\mbox{\# total mentions of }f}
+w_{u \to f}^{\text{R}}=pR=\frac{\mbox{\# retweets of }u \mbox{ by }f}{\mbox{\# total retweets made by }f}
 \end{equation}
-and
+proportional mentions 
 \begin{equation}
-\frac{\mbox{\# retweets of }u \mbox{ by }f}{\mbox{\# total retweets made by }f} \mbox{ .}
+w_{u \to f}^{\text{M}} = pM = \frac{\mbox{\# mentions of }f \mbox{ by }u}{\mbox{\# total mentions of }f}
 \end{equation}
-For the communities based on mention-retweets, we weight each edge from a user $u$ to a follower $f$ by 
+and mention-retweet as the arithmetic mean of these two measures:
+%we weight each edge from a user $u$ to a follower $f$ through a combination of proportional mentions ($pM$):
+% In more details, for each couple of user-follower $u$ and $f$, we use the arithmetic mean of the two following numbers:
+%\begin{equation}
+%w_{u \to f}^{\text{M}} = pM = \frac{\mbox{\# mentions of }f \mbox{ by }u}{\mbox{\# %total mentions of }f}
+%\end{equation}
 \begin{align}
-	w_{u \to f}^{\text{MR}} = \frac{1}{2}\left(\frac{\mbox{\# mentions of }f \mbox{ by }u}{\mbox{\# total mentions of }f} + \frac{\mbox{\# retweets of }u \mbox{ by }f}{\mbox{\# total retweets made by }f}\right).
+	w_{u \to f}^{\text{MR}} = \frac{(pM+pR)}{2}.
 \end{align}
+
+%	w_{u \to f}^{\text{MR}} = \frac{1}{2}\left(\frac{\mbox{\# mentions of }f %\mbox{ by }u}{\mbox{\# total mentions of }f} + \frac{\mbox{\# retweets of }u \mbox{ by }f}{\mbox{\# total retweets made by }f}\right).
 
@@
 
-Another kind of community is the one based on the content of the tweets, and relies on the idea of finding people that talk about the same things.
-In order to detect this kind of communities, we weight the edges of the user-follower network through a measure based on the number of common hashtags between the two users.
-Hashtags are in fact a good proxy for this, since they are explicitly meant to be key-words indicating a particular topic.
-Moreover they are widely used and straightforwardly detectable.
-We characterize each user $u$ by a vector $\vec{h}(u)$ of length equal to the number of hashtags in the dataset, and whose elements are defined as
+The final community we consider is a topic-based or topical community, i.e., a community defined by the content (topics) they discuss.
+So in a topical community, users are defined to be a member of a community if they tweet \emph{about} similar topics as other members of the community.
+%Another kind of community is the one based on the content of the tweets, and relies on the idea of finding people that talk about the same things. 
+In order to detect the topical communities, we weight the edges of the user-follower network through a measure based on the number of common hashtags between pairs of users.
+Hashtags are a good proxy for a tweets content as hashtags are explicitly meant to be keywords indicating the topic of the tweet.
+Moreover they are widely used and straightforward to detect.
+
+To this end, we characterize each user $u$ by a vector $\vec{h}(u)$ of length equal to the number of unique hashtags in the dataset, and whose elements are defined as
 \begin{equation}
@@
 \end{equation}
-where $n_i(u)$ is the frequency of the hashtag $i$ in the set of user $u$'s tweets, $N$ is the total number of users, and $n_i$ is the number of users that have used the hashtag $i$ in their tweets.
+where $n_i(u)$ is the frequency of hashtag $i$ occuring in user $u$'s tweets, $N$ is the total number of users, and $n_i$ is the number of users that have used the hashtag $i$ in their tweets.
 This adapted term frequency--inverse document frequency (tf-idf) measure \cite{salton_introduction_1983} captures the importance of a hashtag in the users's tweets through the first factor, but at the same time smooths it through the second factor by giving less importance to hashtags that are too widely used (as $\frac{N}{n_i}$ approaches one, its logarithm approaches zero).
-For each couple of user linked in the user-follower network, we then compute the cosine similarity of their respective vectors, and assign the obtained value as the weight of the directed edge(s) connecting them.
-This weight captures the similarity between users in terms of topic discussed in their tweets.
-Thus, for communities based on hashtag similarity, we weight each edge from a user $u$ to a follower $f$ by
+
+For the topical communities we weight each directed edge from a user $u$ to a follower $f$ with the cosine similarity of their respective vectors $\vec{h}(u)$ and $\vec{h}(f)$:
 \begin{align}
@@
 \end{align}
+This weight captures the similarity between users in terms of topic discussed in their tweets.

### 2014-01-17 paper/paper.tex
Fixed some broken pointers to tables / sections. Modified the header to include section numbers.
Made some modifications to the transfer entropy section.

@@
 \pdfinfo{
-/Title (Input Your Paper Title Here)
+/Title (Followers Are Not Enough: Beyond Structural Communities in Online Social Networks)
 /Author (David Darmon, Elisa Omodei, Joshua Garland)
-/Keywords (Input your paper keywords in this optional area)}
+/Keywords (community detection, functional communities, social network analysis)}
 
@@
 % Uncomment if you want to use section numbers % and change the 0 to a 1 or 2
-\setcounter{secnumdepth}{0}
+\setcounter{secnumdepth}{2}
 
@@
 %Followers are not enough: Beyond structure in the detection of communities \\
-Followers are Not Enough: Beyond Structural Communities in Online Social Networks%\\
+Followers Are Not Enough: Beyond Structural Communities in Online Social Networks%\\
 %Followers are not enough: Activity, Interaction, and Topic-based Communities in Online Social Networks \\
@@
 \input{parts/intro.tex}
-\input{parts/community.tex}
 \input{parts/methods.tex}

### 2014-01-17 paper/parts/methods.tex
Made some modifications to the transfer entropy section.

--- 2014-01-15 paper/parts/methods.tex
@@
 In our study we deal with \textit{weighted directed} networks, and we are interested in finding \textit{overlapping} modules, rather than partitions of the network, since people can belong to different social groups: they can be interacting with different groups of people (their college friends, their co-workers, their family, etc), and they can belong to different topical communities (a person can be interested both in cycling and politics and talk about the two topics with different groups of people).
-Most community detection algorithms developed so far are built to find partitions and only very few to find overlapping communities \cite{BaumesGKMP05,PalEtAl05,ZhaWanZha07,Gre07,PhysRevE.77.016107,Lancichinetti2009,PhysRevE.80.016105,Kovacs2010} Among these, even fewer can also deal with directed or weighted networks.
+Most community detection algorithms developed so far are built to find partitions and only very few to find overlapping communities \cite{newman2004finding,BaumesGKMP05,PalEtAl05,ZhaWanZha07,Gre07,PhysRevE.77.016107,Lancichinetti2009,PhysRevE.80.016105,Kovacs2010} Among these, even fewer can also deal with directed or weighted networks.
 Palla et al.
@@
 
-\textbf{Show the distribution of the number of mentions / retweets / haghstags / tweets / followers per user ?}
-
 \subsection{Activity-Based Communities and Transfer Entropy}
@@
 
-We can view the behavior of a user $u$ on Twitter as a point process, where at any instant $t$ the user has either emitted a tweet ($X_{t}(u) = 1$) or remained silent ($X_{t}(u) = 0$).
+For the activity-based communities, we consider only the timing of each users tweets and ignore any additional content.
+From this starting point, we can view the behavior of a user $u$ on Twitter as a point process, where at any instant $t$ the user has either emitted a tweet ($X_{t}(u) = 1$) or remained silent ($X_{t}(u) = 0$).
 This is the view of a user's dynamics taken in \cite{ver2012information} and \cite{darmon2013understanding}.
@@
 We then compute the transfer entropy on these coarsened time series taking $k$ to range from 1 to 6, which corresponds to a lag of ten minutes to an hour.
+The choice of lag must balance a trade-off between additional information and sparsity of samples: as we increase the lag, we account for longer range dependencies, but we also decrease the number of samples availabe to infer a higher dimensional predictive distribution.
+Ultimately, due to similarities in the underlying communities (see Figure \ref{Fig-compare_coverings}), we chose a lag-4 transfer entropy.
+All references to activity-based weights, unless otherwise noted, refer to this choice of lag.
 
@@
 We can therefore define interaction-based communities by weighting the user-follower network with a measure proportional to the number of mentions and retweets between users.
-In more details, for each couple of user-follower $u$ and $f$, we use the arithmetic / harmonic (\textbf{which one?}) mean of the two following numbers:
+In more details, for each couple of user-follower $u$ and $f$, we use the arithmetic mean of the two following numbers:
 \begin{equation}

### 2014-01-17 paper/parts/methods.tex

--- 2014-01-16 paper/parts/methods.tex
@@
 
-We can view the behavior of a user $u$ on Twitter as a point process, where at any instant $t$ the user has either emitted a tweet ($X_{t}(u) = 1$) or remained silent ($X_{t}(u) = 0$).
+For the activity-based communities, we consider only the timing of each users tweets and ignore any additional content.
+From this starting point, we can view the behavior of a user $u$ on Twitter as a point process, where at any instant $t$ the user has either emitted a tweet ($X_{t}(u) = 1$) or remained silent ($X_{t}(u) = 0$).
 This is the view of a user's dynamics taken in \cite{ver2012information} and \cite{darmon2013understanding}.
 Thus, we reduce all of the information generated by a user on Twitter to a time series $\{ X_{t}(u)\}$ where $t$ ranges over the time interval for which we have data (9 weeks in this case).
-Since tweets are only collected in discrete, 1-second time intervals, it is natural to consider only the discrete times $t = 1 \text{s}, 2 \text{s}, \ldots, $ relative to a reference time.
+Because status updates are only collected in discrete, 1-second time intervals, it is natural to consider the only the discrete times $t = 1 \text{ s}, 2 \text{ s}, \ldots, $ relative to a reference time.
 We can then compute the flow of information between two users $u$ and $v$ by computing the transfer entropy between their time series $X_{t}(u)$ and $X_{t}(v).$
@@
 We then compute the transfer entropy on these coarsened time series taking $k$ to range from 1 to 6, which corresponds to a lag of ten minutes to an hour.
-\textbf{[[Josh: Dave do you think we should talk about why we chose 1-6 and why we chose 10 minutes.
-If so this would be a good place.
-I think this is a great explanation however.]] }
+The choice of lag must balance a trade-off between additional information and sparsity of samples: as we increase the lag, we account for longer range dependencies, but we also decrease the number of samples availabe to infer a higher dimensional predictive distribution.
+Ultimately, due to similarities in the underlying communities (see Figure \ref{Fig-compare_coverings}), we chose a lag-4 transfer entropy.
+All references to activity-based weights, unless otherwise noted, refer to this choice of lag.
 

### 2014-01-17 paper/drafts/results.tex
Expanded on the section on normalized mutual information.

@@
 
-\subsection{Comparing Aggregate Statistics of Community Structure}
-
-We begin by examining the overall statistics for the communities inferred by OSLOM using the weightings defined in Sections \ref{method-activity}, \ref{method-interaction}, and \ref{method-topic}.
-The number of communities by community type is given in Table~\ref{Table-comm_count}.
-We see that the topic- and interaction-based networks admit the most communities.
-The activity-based network admits the least number of communities.
-One advantage of the OSLOM over many other community detection algorithms is that it explicitly accounts for singleton `communities': those nodes who do not belong to \emph{any} extant communities.
-This is especially important when a network is collected via a breadth-first search, as in our network, where we begin from a seed node and then branch out.
-Such a search, once terminated, will result in a collection of nodes on the periphery of the network that may not belong to any community in the core.
-
-% See here
-% 	http://arxiv.org/pdf/1202.2684v2.pdf
-% for possible useful references on core-periphery networks.
-
-The number of singletons by community type is also shown in Table~\ref{Table-comm_count}.
-We see that the topic- and interaction-based communities have the most singletons, with the activity-based community dominating this measure.
-This result for the activity-based community is an artifact of a property of the retweet/mention weighting: many of the users in the data set (\textbf{TK: give actual number}) did not interact with each other, and thus all of their edges were zero-weighted, leading to trivial singletons.
-
-\begin{table}[ht]
-	\label{Table-comm_count}
-	\caption{Number of non-singleton communities and singletons by community type: S(tructural), A(ctivity -based), T(opic-based), and I(nteraction-based).}
-	\centering
-	\begin{tabular}{| c | c | c |}
-		\hline Community Type & \# of Communities & \# of Singletons \\ \hline
-		% Structural & 201 \\
-		% Activity, Lag 1 & 101 \\
-		% Activity, Lag 2 & 99 \\
-		% Activity, Lag 3 & 106 \\
-		% Activity, Lag 4 & 105 \\
-		% Activity, Lag 5 & 107 \\
-		% Activity, Lag 6 & 106 \\
-		% Topic & 289 \\
-		% Interaction & 252 \\ \hline
-		S & 201 & 308 \\
-		A, Lag 1 & 101 & 951 \\
-		A, Lag 2 & 99 & 600 \\
-		A, Lag 3 & 106 & 611 \\
-		A, Lag 4 & 105 & 668 \\
-		A, Lag 5 & 107 & 632 \\
-		A, Lag 6 & 106 & 642 \\
-		T & 289 & 1064 \\
-		I & 252 & 2436 \\ \hline
-	\end{tabular}
-\end{table}
-
-Next we consider the distribution of community sizes across the community types.
-The complementary cumulative distribution of community sizes is given in Figure~\ref{Fig-community_size_distribution}.
-Note that the axes are plotted on log-scale, and the horizontal axis begins with non-singleton communities.
-Thus, for a fixed community size $c$, Figure~\ref{Fig-community_size_distribution} shows the proportion of communities of size greater than $c$ for each community type.
-The largest communities for the structural, activity-based, topic-based, and interaction-based networks are 198, 358, 338, and 811 respectively.
-
-\begin{figure}[ht]
-  \centering
-\includegraphics[width=0.50\textwidth]{../Figures/comm_sizes_ecdf_loglog.pdf}
-\caption{The proportion of communities greater than $c$ in size, across the different community types. Note the logarithmic scale on the horizontal and vertical axes.}
-\label{Fig-community_size_distribution}
-\end{figure}
-
-Next, we compare the number of users which belong to more than one community.
-Figure~\ref{Fig-overlap_plot} shows the number of users belonging to 2, 3, or 4 communities.
-We see that as the number of mixed membership communities increases, the number of users with that number of mixed memberships decreases.
-This is especially true for the activity-based community \textbf{TK: speculate on what this means?
-Or save for the results section?}.
-In addition, \textbf{TK: mention the 5, 6, and 7 cases, not included in the figure}.
-This corresponded to \textbf{TK: investigate which users are the high-overlap and what communities they belong to.}
-
-% The user with a structural overlap of 7 communities was 1630261,
-%	https://twitter.com/marksilva
-
-\begin{figure}[ht]
-  \centering
-\includegraphics[width=0.50\textwidth]{../Figures/overlap_by_type.pdf}
-\caption{The number of users belonging to 2, 3, or 4 communities, by community type.}
-\label{Fig-overlap_plot}
-\end{figure}
-
 \end{document}

### 2014-01-17 paper/parts/results.tex
Expanded on the section on normalized mutual information.

@@
-\section{Results}
+\section{Results and Discussion}
 
@@
 
-We begin by examining the overall statistics for the communities inferred by OSLOM using the weightings defined in Sections \ref{sec:method-activity}, \ref{sec:method-interaction}, and \ref{sec:method-topic}.
+We begin by examining the overall statistics for the communities inferred by OSLOM using the weightings defined in the previous sections.
 The number of communities by community type is given in Table~\ref{Table-comm_count}.
@@
 We see that the topic- and interaction-based communities have the most singletons, with the activity-based community dominating this measure.
-This result for the activity-based community is an artifact of a property of the retweet/mention weighting: many of the users in the data set (\textbf{TK: give actual number}) did not interact with each other, and thus all of their edges were zero-weighted, leading to trivial singletons.
+This result for the activity-based community is an artifact of a property of the retweet/mention weighting: 717 of the users were removed in the process \textbf{TK: Fix after clarification from Elisa}.
 
@@
 		T & 289 & 1064 \\
-		I & 252 & 2436 \\ \hline
+		I & 252 & 2436 (1719) \\ \hline
 	\end{tabular}
@@
 The complementary cumulative distribution of community sizes is given in Figure~\ref{Fig-community_size_distribution}.
-Note that the axes are plotted on log-scale, and the horizontal axis begins with non-singleton communities.
+Note that both axes are plotted on log-scale, and the horizontal axis begins with non-singleton communities.
 Thus, for a fixed community size $c$, Figure~\ref{Fig-community_size_distribution} shows the proportion of communities of size greater than $c$ for each community type.
-The largest communities for the structural, activity-based, topic-based, and interaction-based networks are 198, 358, 338, and 811 respectively.
+We see that the community distributions have longer tails for the non-structural networks, and that the interaction-based network has the longest tail.
+The largest communities for the structural, activity-based, topic-based, and interaction-based networks have 198, 358, 338, and 811 members, respectively.
+Most importantly, we see that the distributions are heterogeneous across the network types, highlighting that the different networks give rise to different large-scale community structure dependent on the particular weighting of the structural network.
 
@@
 
-Next, we compare the number of users which belong to more than one community.
+% Next, we compare the number of users which belong to more than one community.
 Figure~\ref{Fig-overlap_plot} shows the number of users belonging to 2, 3, or 4 communities.
@@
 
-% The user with a structural overlap of 7 communities was 1630261,
-%	https://twitter.com/marksilva
+% % The user with a structural overlap of 7 communities was 1630261,
+% %	https://twitter.com/marksilva
 
-\begin{figure}[ht]
-  \centering
-\includegraphics[width=0.50\textwidth]{Figures/overlap_by_type.pdf}
-\caption{The number of users belonging to 2, 3, or 4 communities, by community type.}
-\label{Fig-overlap_plot}
-\end{figure}
+% \begin{figure}[ht]
+%   \centering
+% \includegraphics[width=0.50\textwidth]{Figures/overlap_by_type.pdf}
+% \caption{The number of users belonging to 2, 3, or 4 communities, by community type.}
+% \label{Fig-overlap_plot}
+% \end{figure}
 
-\subsection{Comparing Community Types with Normalized Mutual Information}
+\subsection{Comparing Community Structure with Normalized Mutual Information}
 
-Because OSLOM detects \emph{coverings} rather than \emph{partitions} of users, standard cluster comparison methods like variation of information~\cite{meilua2003comparing} are not appropriate.
-Instead, we use a generalization of variation of information measure first introduced in~\cite{lancichinetti2009detecting}, the normalized information.
-\textbf{TK: Etc.
-Put more here about NMI, what it does, and how to interpret it.}
+In the previous section, we saw that the large scale statistics of the communities were highly dependent on the type of community under consideration.
+However, macroscale network statistics do not account for differences in community structure that result from operations such as splitting or merging of communities.
+Moreover, this view does not account for which users belong to which communities, and in particular which users belong to the same communities across community types.
+To answer this question, we invoke methods for cluster comparisons: given two different clusterings of nodes into communities, how similar are the two clusters?
+The standard approach to answering this question is to define a metric on the space of clusterings.
+Because OSLOM detects \emph{coverings} rather than \emph{partitions} of users, standard cluster comparison metrics like variation of information~\cite{meilua2003comparing} are not appropriate.
+Instead, we use a generalization of variation of information first introduced in~\cite{lancichinetti2009detecting}, the normalized mutual information.
+The normalized mutual information stems from treating clustering as a community identification problem: given that we know a node's community membership(s) in the first clustering, how much information do we have about its community membership(s) in the second clustering, and vice versa?
+Consider the two coverings $\mathcal{C}_{1}$ and $\mathcal{C}_{2}.$We think of the community memberships of a randomly chosen node in $\mathcal{C}_{1}$ as a binary random vector $\mathbf{X} \in \{0, 1\}^{|\mathcal{C}_{1}|}$ where the $i^{\text{th}}$ entry of the vector is 1 if the node belongs to community $i$ and 0 otherwise.
+Similarly, $\mathbf{Y} \in \{ 0, 1\}^{|\mathcal{C}_{2}|}$ is a binary random vector indicating the community memberships of the node in $\mathcal{C}_{2}$.
+Then the normalized mutual information is defined as
+\begin{align}
+	\text{NMI}(\mathcal{C}_{1}, \mathcal{C}_{2}) = 1 - \frac{1}{2} \left( \frac{H[\mathbf{X} | \mathbf{Y}]}{H[\mathbf{X}]} + \frac{H[\mathbf{Y} | \mathbf{X}]}{H[\mathbf{Y}]}\right)
+\end{align}
+where $H[\cdot]$ is a marginal entropy and $H[\cdot | \cdot]$ is a conditional entropy.
+The normalized mutual information varies from 0 to 1, attaining the value of 1 only when $\mathcal{C}_{1}$ and $\mathcal{C}_{2}$ are identical coverings up to a permutation of their labels.
+See the appendix of~\cite{lancichinetti2009detecting} for more details.
 
-The normalized mutual information between the various community-types are shown in Figure~\ref{Fig-compare_coverings}.
-We see that similarity between the coverings is dictated by the generic covering type, with distinct community structure between the structural, activity-based, and interaction-based communities.
-Interestingly, the communities resulting from the different weightings are all more similar to each other than to the structural communities from the unweighted network.Also note that the communities based on the hashtag similarities are different from both the activity-based and mention-retweet-based communities.
+We considered the normalized mutual information between the communities inferred from the structural network and the networks weighted with lag 1 through 6 transfer entropies, hashtag similarity, and mention, retweet, and mention-retweet activity.
+The resulting $\text{NMI}(\mathcal{C}_{i}, \mathcal{C}_{j})$ are shown in Figure~\ref{Fig-compare_coverings}.
+We see that similarity between the coverings is dictated by the generic community type (structural, activity-based, etc.).
+That is, the transfer entropy coverings are more similar to each other than to any of the other coverings, with a similar result for the mention, retweet, and mention-retweet coverings.
+Interestingly, the coverings resulting from the different weightings are all more similar to each other than to the structural covering from the unweighted network.
+Also note that the covering based on the hashtag similarities are different from all of the other weight-based coverings.
 
@@
 \caption{The normalized mutual information between the communities using the different weightings.
-Weighting 0 corresponds to the structural (binary weighting) network, weightings 1 through 6 correspond to the weighting using the transfer entropy with lag 1 through 6, weighting 7 corresponds to the hashtag similarity, and weightings 8, 9, and 10 correspond to the mention, retweet, and mention-retweet weightings.
+Weighting 0 corresponds to the structural (binary weighting) network, weightings 1 through 6 correspond to the weighting using the transfer entropies with lag 1 through 6, weighting 7 corresponds to the hashtag similarity, and weightings 8, 9, and 10 correspond to the mention, retweet, and mention-retweet weightings.
 Values of normalized mutual information close to 1 indicate similarity in the community structure, while values close to 0 indicate dissimilarity.
@@
 \end{figure}
+
+Thus, we see that although the activity-based, interaction-based, and topic-based communities relied on the structural network, their community structure differs \emph{the most} from the community structure of the follower network.
+This agrees with the results from the previous section, and reinforces that the follower network is a necessary but not sufficient part of detecting communities in online social networks.
 

### 2014-01-17 code/community_sizes.R

@@ -57,5 +57,5 @@ for (cur.ind in 1:4){
 
 	lines(x, 1 - F(x), col = colors[cur.ind], lwd = lwd)
 }
-legend('topright', c('Structural', 'Activity-based', 'Content-based', 'Interaction-based'), lwd = rep(lwd,4), lty = rep(1, 4), col = colors)
+legend('topright', c('Structural', 'Activity-based', 'Topic-based', 'Interaction-based'), lwd = rep(lwd,4), lty = rep(1, 4), col = colors)
 dev.off()

### 2014-01-17 code/count_communities.py

@@ -19,7 +19,7 @@ for comm_type in comm_types:
 		for line in ofile:
 			comm_count += 1
 
-	# print comm_type, comm_count
+	print comm_type, comm_count
 
 	# Count number of singleton communities.
 

### 2014-01-17 paper/parts/results.tex
Expanded and (hopefully) clarified the section on weights-across communities. Reworked parts of Elisa's qualitative study.

@@
 \end{align}
-where $H[\cdot]$ is a marginal entropy and $H[\cdot | \cdot]$ is a conditional entropy.
+where $H[\cdot]$ denotes a marginal entropy and $H[\cdot | \cdot]$ denotes a conditional entropy.
 The normalized mutual information varies from 0 to 1, attaining the value of 1 only when $\mathcal{C}_{1}$ and $\mathcal{C}_{2}$ are identical coverings up to a permutation of their labels.
@@
 
-\subsection{Comparing Edges Across Different Community-Types}
+\subsection{Comparing Edges Across Different Community Types}
 
-We have defined communities using four different criteria: structure, activity, interaction, and content.
-For a fixed community type, edges for a particular community may be partitioned into three sets: those from a node in the community to another node in the community (internal-to-internal), those from a node in the community to a node outside of the community (internal-to-external), and those from a node outside the community to a node inside the community (external-to-internal).
+We have defined communities using four different criteria: structure, activity, interaction, and topic.
+We next explore how edge weights, and thus different forms of information flow, differ between community types.
+For a fixed community type, edges for a particular community may be partitioned into three sets: those from a user in the community to another user in the community (internal-to-internal), those from a user in the community to a user outside of the community (internal-to-external), and those from a user outside the community to a user inside the community (external-to-internal).
 See Figure~\ref{Fig-edge_types} for a schematic of this edge partitioning.
@@
 
-For example, Figure~\ref{Fig-dist_across_community} shows the distributions of hashtag-based weights for the largest community defined by the mention-retweet network.
+As an example, Figure~\ref{Fig-dist_across_community} shows the distributions of hashtag-based weights for the largest community in the mention-retweet network.
 We see that the distribution of internal-to-internal hashtag weights has a longer tail than either the external-to-internal or internal-to-external hashtag weights, with edges within the community having higher weights than edges crossing the boundary of the community.
-Thus, while the community was defined in terms of interactions, we still see a shift in the distribution of \emph{topic-similarity}.
+Thus, while the community was defined in terms of interactions, we still see a shift in the distribution of topic-similarity.
 
@@
   \centering
-\includegraphics[width=0.50\textwidth]{Figures/comm0_labels-mention-retweet_weights-hashtag-ecdf.pdf}
+\includegraphics[width=0.50\textwidth]{figures/comm0_labels-mention-retweet_weights-hashtag-ecdf.pdf}
 \caption{The proportion of edges with a weight at least as large as the weight on the horizontal axis, across the types of edges described in Figure~\ref{Fig-edge_types}.
-The community is defined by user interactions, and the edge weights are determined by topics.}
+The community is defined by user interactions, and the edge weights are determined by topic similarity.
+The dashed horizontal lines indicate the median weight for each type of edge.
+Note the logarithmic scale on the horizontal axis.}
 \label{Fig-dist_across_community}
@@
 
-This shift in the distribution was typical of many of the community type / weight pairings.
-To explore this further, for each of the top 100 largest communities defined by a particular community type (structure-based, behavior-based, content-based, or activity-based), we computed the median internal-to-internal, external-to-internal, and internal-to-external weight for that community for each weight type.
-These values summarize the typical value of each of these types of edges.
-We can then compute the ratio of the median internal-to-internal weight and the median external/internal-to-internal/external weight, which captures the proportional shift in the distribution.
-Finally, we compute the median of this proportional shift across all 100 of the largest communities.
-These values are summarized in Table~\ref{Table-medians}.
+This change in the tail of the distribution between edge types was typical of many of the community type / weight pairings.
+A useful summary statistic to quantify the change involves the median weights across the three types of edges, as demonstrated in Figure~\ref{Fig-dist_across_community}.
+In particular, by computing the ratio of the median weight for the internal-to-internal edges to the median weight for the internal/external-to-external/internal edges, we can quantify the ratio change in weight strength internal vs.
+external to a community.
+We computed this quantity for each of the top 100 largest communities defined by a particular community type (structure-based, activity-based, interaction-based, or topic-based), and report the median value across the 100 largest communities for each type in Table~\ref{Table-medians}.
+This statistic represents the typical ratio shift for each community type / weight pairing.
+Values greater than 1 indicate that the edge weights tend to be higher within the community, and values less than 1 indicate that the edge weights tend to be higher for those edges crossing the community boundary.
 
@@
 
+% \begin{table}
+% 	\label{Table-medians}
+% 	\caption{The median value across the 100 largest communities for the ratio of the median internal-to-internal weight to the median external-to-internal / internal-to-external weight for the different community / weight pairings.
+Note: For mention-retweet weights, weight zero edges were excluded from the computation of the median.
+We indicate such cases with an asterisk.}
+% 	\centering
+% 	\begin{tabular}{c | c | c  c  c}
+% 		& & \multicolumn{3}{ c }{Weight Type} \\ \cline{3-5}
+% 		& & TE & MR & HT \\ \cline{2-5}
+% 		\multirow{4}{*}{Community Type} & S & $0.96/0.94$& $1.7/2.1$*& $9.0/8.0$\\
+% 		& A & $1.0/0.96$& $1.5/2.4$*& $24/17$\\
+% 		& I & $0.83/0.86$& $3.2/4.4$& $10/8.5$\\
+% 		& T & $0.9/0.89$& $2.4/2.6$*& $28/26$
+% 	\end{tabular}
+% \end{table}
+
 \begin{table}
+	\caption{The median value across the 100 largest communities for the ratio of the median internal-to-internal weight to the median external-to-internal / internal-to-external weight for the different community / weight pairings.
+Note: For mention-retweet weights, zero weight edges were excluded from the computation of the median.
+We indicate such cases with an asterisk.}
+	\centering
+	\begin{tabular}{c  c | c  c  c}
+		& & \multicolumn{3}{ c }{Weight Type} \\ %\cline{3-5}
+		& & TE & MR & HT \\ \cline{1-5}
+		\multirow{4}{*}{Community} & S & $0.96/0.94$& $1.7/2.1$*& $9.0/8.0$\\
+		\multirow{4}{*}{Type} & A & $1.0/0.96$& $1.5/2.4$*& $24/17$\\
+		& I & $0.83/0.86$& $3.2/4.4$& $10/8.5$\\
+		& T & $0.9/0.89$& $2.4/2.6$*& $28/26$
+	\end{tabular}
 	\label{Table-medians}
-	\caption{The median value across the 100 largest communities for the ratio of the median internal-to-internal weight to median external/internal-to-internal/external weight for the different community/weight pairings.
-\\ * For mention-retweet weights, weight zero edges were excluded from the computation of the median.}
-	\centering
-	\begin{tabular}{c | c | c  c  c}
-		& & \multicolumn{3}{ c }{Weight} \\ \hline
-		\multirow{4}{*}{Community} & & TE & MR & HT \\ \hline
-		& S & $0.96/0.94$& $1.7/2.1$*& $9.0/8.0$\\
-		& TE & $1.0/0.96$& $1.5/2.4$*& $24/17$\\
-		& MR & $0.83/0.86$& $3.2/4.4$& $10/8.5$\\
-		& HT & $0.9/0.89$& $2.4/2.6$*& $28/26$
-	\end{tabular}
 \end{table}
 
-We see that overall, the
+We see that for all weight types except the transfer entropy, the weight on the edges internal to the communities tend to be higher than those entering or exiting the communities, ranging from a factor of 1.5 times larger for the activity-based/mention-retweet pairing to a factor of 28 times larger for the topic-based/hashtag similarity pairing.
+As stated above, we expect this ratio to be high for community / weight pairings that match (e.g.
+considering mention-retweet weighting for interaction-based communities), and we see that this is the case for all but the activity-based / transfer entropy pairing.
+Moreover, for both the mention-retweet and hashtag weightings, the ratio is largest when they match with the interaction-based and topic-based communities, respectively.
 
-\subsection{Qualitative Analysis}
+For all four community types, the transfer entropy tended to be higher for edges crossing community boundaries than for those internal to community boundaries.
+Recall that the transfer entropy $\text{TE}_{X(u) \to X(f)}$ quantifies the reduction in uncertainty about a follower $f$'s activity from knowing the activity of a user $u$.
+This result therefore implies that, in terms of prediction, it is more useful to know the time series of a user followed outside of the community compared to a user followed inside of the community.
+Thus, in an information theoretic sense, we see that novel information useful for prediction is more likely to flow \emph{across} community boundaries than \emph{within} community boundaries.
 
-In order to further explore the differences between the communities obtained through the various weightings, we also performed a qualitative analysis of such communities.
-Some interesting examples are, for instance, communities in the topic-based network such as one composed of 83 users who talk about environmental issues and frequently use hashtags such as \#green, \#eco and \#sustainability, and another one 47 users talking about small businesses and entrepreneurship, characterized by hashtags such as \#smallbiz, \#marketing and \#enterpreneur.
-In both cases most members of the topic-based communities are not found in the same community in the other networks, indicating that these people talk about the same things and can therefore be considered a thematic community, but do not strongly interact with each other nor behave the same, and so belong to different social groups with respect to interactions and behavior.
-Another interesting example is the one of a community thematically focused on Denver and Colorado, whose users do not belong to the same community in the interaction networks, but most of them do belong to the same community in the information based network.
-This indicates that these users react on the same events and issues regarding Colorado and are therefore strongly connected in the topic-based and in the activity-based networks, but at the same time they do not directly interact with each other and are therefore more loosely connected in the interaction-based networks, where they belong to different communities.
+Note that the communities defined by the follower network do tend to have higher edge weights internal compared to across community boundaries.
+Thus, we do see that the structural communities capture some information about the functional behavior of users in terms of topics and interaction.
+However, the ratio is not as large as when we explicitly seek out communities based on a particular type of functional community.
+This again emphasizes the importance of properly formulating the goal of a community detection study in the context of online social networks.
+
+% \begin{tabular}{cc|ccc}
+% & & \multicolumn{3}{ c| }{Weight Type} \\ \cline{3-5}
+% & & 2 & 3 & 5  \\ \cline{1-5}
+% \multicolumn{1}{ c| }{\multirow{4}{*}{Powers} } &
+% \multicolumn{1}{ c| }{504} & 3 & 2 & 0    \\ \cline{2-5}
+% \multicolumn{1}{ c|  }{}                        &
+% \multicolumn{1}{ c| }{540} & 2 & 3 & 1     \\
+% \multicolumn{1}{ c| }{gcd} & 2 & 2 & 0 \\ \cline{2-5}
+% \multicolumn{1}{ c  }{}                        &
+% \multicolumn{1}{ c| }{lcm} & 3 & 3 & 1 \\ \cline{1-5}
+% \end{tabular}
+
+\subsection{Qualitative Analysis of Community Memberships Across Types}
+
+As demonstrated in~\cite{good2010performance} in the context of modularity maximization-based community detection, an exponential number of nearby partitions may exist that nearly maximize an objective function used to measure the goodness-of-fit of the graph partition used for community detection.
+Because of this and related issues, it is always wise to perform some sort of curated study of the communities returned by any  community detection algorithm to verify their meaningfulness with respect to the scientific question at hand.
+In this section, we consider a collection of communities in such a study.
+
+In the topic-based communities, we find a single community consisting of 83 users who tweet about environmental issues and frequently use hashtags such as \#green, \#eco and \#sustainability.
+We also find a different community of 47 users who tweet about small businesses and entrepreneurship, using hashtags such as \#smallbiz, \#marketing and \#enterpreneur.
+In both cases most members of the topic-based communities are not found in the same community in the other networks, indicating that while these people talk about the same things and can therefore be considered a community based on their content, they do not strongly interact with each other nor behave the same, and so belong to different social groups with respect to interactions and behavior.
+
+Another interesting example is the one of a community whose topics tend focus on Denver and Colorado.
+These users do not belong to the same community in the interaction-based network, but most of them do belong to the same community in the activity-based network.
+This indicates that these users react to the same events and issues regarding Colorado and are therefore strongly connected in the topic-based and activity-based networks, but at the same time they do not directly interact with each other and are therefore more loosely connected in the interaction-based networks, where they belong to different communities.

### 2014-01-17 code/analyze_weights_by_community_types.R

@@ -43,7 +43,8 @@ kde.positive.support = function(x){
 # weight_types = c('TE4', 'hashtag', 'mention-retweet')
 
 label_types = c('mention-retweet')
-weight_types = c('hashtag')
+weight_types = c('TE4')
+# weight_types = c('hashtag')
 
 comms = 0:9
 
@@ -51,6 +52,7 @@ for (label_type in label_types){
 for (weight_type in weight_types){
 
 for (comm_label in comms){
+# for (comm_label in c(0)){
 	prefix = paste0('comm', comm_label, '_labels-', label_type, '_weights-', weight_type)
 
 	data_i.to.i = read.csv(paste0('../data/edges-by-type/', prefix, '_i-to-i.dat'), header = FALSE)$V1
@@ -65,8 +67,19 @@ for (comm_label in comms){
 	data_e.to.i[is.na(data_e.to.i)] = 0
 	data_i.to.e[is.na(data_i.to.e)] = 0
 
+	# For some reason min is behaving strangely here...
+
+	min1 = log10(min(data_i.to.i)); min2 = log10(min(data_e.to.i)); min3 = log10(min(data_i.to.e))
+
 	# xmax = 0.05
 	xmax = max(c(data_i.to.i, data_e.to.i, data_i.to.e))
+# 	xmin = 10^(min(c(min1, min2, min3)))
+	xmin = 10^(min(c(min1, min2, min3)))
+	if (xmin == 0.){
+		xmin = 1e-10
+	}
+
+	cat(sprintf('\n\nUsing xmin = %e and xmax = %e\n\n', xmin, xmax))
 
 	# pdf(paste0('figures/', prefix, '_i-to-i-ecdf.pdf'))
 	# plot(ecdf(data_i.to.i), xlim = c(0, xmax), xlab = 'Weight', ylab = 'ECDF', main = '')
@@ -83,10 +96,12 @@ for (comm_label in comms){
 	lwd = 2
 
 	pdf(paste0('figures/', prefix, '-ecdf.pdf'))
-	plot(ecdf(data_i.to.i), xlim = c(0, xmax), xlab = 'Weight', ylab = 'Empirical Distribution of Weights', main = '', col = 'red', lwd = lwd)
-	lines(ecdf(data_e.to.i), xlim = c(0, xmax), xlab = 'Weight', ylab = 'ECDF', main = '', col = 'blue', lwd = lwd)
[…]

### 2014-01-17 paper/parts/methods.tex
Fixed the explanation of orphans for the interaction-based community.

@@
 %and whose link represent a user-follower relationship.
-In this study the link is directed from the user to the follower because this is the direction in which the information flows.\textbf{[[Josh: Is this the case for all the analysis or just the transfer entropy?]]} The final network consists of 6,917 nodes and 1,481,131 edges.
+In this study the link is directed from the user to the follower because this is the direction in which the information (in the case of transfer entropy) or influence (in the case of mention-retweets) flows.
+The final network consists of 6,917 nodes and 1,481,131 edges.
 

### 2014-01-17 paper/parts/results.tex
Fixed the explanation of orphans for the interaction-based community.

@@
 We see that the topic- and interaction-based communities have the most singletons, with the activity-based community dominating this measure.
-This result for the activity-based community is an artifact of a property of the retweet/mention weighting: 717 of the users were removed in the process \textbf{TK: Fix after clarification from Elisa}.
+This result for the activity-based community is partially an artifact of a property of the retweet/mention weighting: 717 of the users were disconnected from the network by how the weights were defined, resulting in `orphan' nodes which we have included in the collection of singletons for all of our analyses.
+However, even after accounting for this artifact, the interaction-based network still has the most non-orphan singletons.
+This seems to indicate that a large fraction of the 6917 (nearly 25\%) do not interact with each other in a concerted way that would mark them as a community under our interaction-based definition.
 
@@
 The community is defined by user interactions, and the edge weights are determined by topic similarity.
-The dashed horizontal lines indicate the median weight for each type of edge.
+The dashed vertical lines indicate the median weight for each type of edge.
 Note the logarithmic scale on the horizontal axis.}

### 2014-01-18 paper/parts/methods.tex
Added another round of corrections to the paper.

@@
 \section{Methodology}
-\textbf{[[Add a quick paragraph that transitions and roadmaps this section]]}
+
+In the following sections, we introduce the problem of community detection, and present the data set used for our analyses.
+We then describe our methodology for constructing the question-specific networks under study.
+In particular, we introduce an information theoretic method for activity-based communities, a retweet-mention summary of communication for interaction-based communities, and a hashtag similarity metric for defining topic-based communities.
+
 \subsection{Community Detection}
@@
 %[[Already defined]]In network theory communities are usually defined as group of %nodes more densely connected among each other than with the rest of the network.
-As discussed in the introduction, we adopt the usual definition of \emph{community}: a collection of nodes (users) within a network who are more densely connected to each other than with the rest of the network.
+As discussed in the introduction, we adopt the standard definition of \emph{community}: a collection of nodes (users) within a network who are more densely connected to each other than with the rest of the network.
 Structural community detection is a well studied problem and several different methods and algorithms have been proposed; for a complete review of this subject we refer the reader to \cite{fortunato2010community}.
@@
 But we are interested in not just structure but function, to capture function we use edge weightings which must be used in the community detection process.
-Finally, since people can belong to multiple and possibly overlapping social (e.g., college friends, co-workers, family, etc.) and topical (e.g., a user can be interested in both cycling and politics and use the network to discuss the two topics with the two different communities) communities, we are interested in finding \textit{overlapping} modules, rather than partitions of the weighted directed network.
+Finally, since people can belong to multiple and possibly overlapping social (e.g., college friends, co-workers, family, etc.) and topical (e.g., a user can be interested in both cycling and politics and use the network to discuss the two topics with the two different communities) communities, we are interested in finding \textit{overlapping} communities, rather than partitions of the weighted directed network.
 %For example, users can belong to multiple social groups such as college friends, %co-workers, family, etc.
@@
 Among these methods, even fewer deal with directed or weighted networks.
-\cite{PalEtAl05} clique percolation method can for example take into account these two features, but not both at the same time.
-\cite{LancichinettiPlos} recently proposed OSLOM (Order Statistics Local Optimization Method) which is the first method that is able to deal with all of these features at the same time; their method "is based on the local optimization of a fitness function expressing the statistical significance of clusters with respect to random fluctuations" (\textbf{taken from their paper, to rephrase}).
-For this paper we use OSLOM as it allowed us to detect \emph{overlapping} communities present in our \emph{weighted} \emph{and} \emph{directed} network.
+For example, the work of~\cite{PalEtAl05} on clique percolation can account for both features, but not at the same time.
+A recent method proposed by~\cite{LancichinettiPlos}, OSLOM (Order Statistics Local Optimization Method), is one of the first methods  able to deal with all of these features simultaneously.
+Their method relies on a fitness function that measures the statistical significance of clusters with respect to random fluctuations, and attempts to optimize this fitness function across all clusters.
+For this paper we use OSLOM as it allowed us to detect \emph{overlapping} communities present in our \emph{weighted} and \emph{directed} network.
 
@@
 We do this through a metric we call (incoming/outgoing) information events.
-We define an outgoing information event for a given user $u$ as either a mention made by $u$ of another user in the network, or if another user in the network retweets a tweet made by $u$.
-The logic for this definition is as follows, if $u$ mentions a user $v$ this can be thought of as $u$ directly sending information to $v$, and if $u$ is retweeted by $v$ then $v$ received information from $u$ and rebroadcast it to their followers.
+We define an outgoing information event for a given user $u$ as either a mention made by $u$ of another user in the network, or a retweet of one of $u$'s tweets by another user in the network.
+The logic for this definition is as follows: if $u$ mentions a user $v$ this can be thought of as $u$ directly sending information to $v$, and if $u$ is retweeted by $v$ then $v$ received information from $u$ and rebroadcast it to their followers.
 In either case there was information outgoing from $u$ which affected the network in the some way.
-Analogously, we define the incoming information event for $u$ as either being mentioned by a different user in the network, or by retweeting another user in the network.
+Analogously, we define the incoming information event for $u$ as either being mentioned by a different user in the network, or as retweeting another user in the network.
 %function and information share is important We then filter down this starting %network to include only users that [[what??]]. To do this 
@@
 
-For the activity-based communities, we consider only the timing of each users tweets and ignore any additional content.
+For the activity-based communities, we consider only the timing of each user's tweets and ignore any additional content.
 From this starting point, we can view the behavior of a user $u$ on Twitter as a point process, where at any instant $t$ the user has either emitted a tweet ($X_{t}(u) = 1$) or remained silent ($X_{t}(u) = 0$).
-This is the view of a user's dynamics taken in \cite{ver2012information} and \cite{darmon2013understanding}.
+This is the view of a user's dynamics taken in~\cite{ver2012information} and~\cite{darmon2013understanding}.
 Thus, we reduce all of the information generated by a user on Twitter to a time series $\{ X_{t}(u)\}$ where $t$ ranges over the time interval for which we have data (9 weeks in this case).
@@
 %information from a user has been captured by a follower and shared with his/her own followers. 
-This type of information flow defines a community in a much different way than transfer entropy did.
-Instead of defining communities by the loss of uncertainty in one users tweeting history based on anothers, we define an interaction-based communities by weighting the user-follower network with a measure proportional to the number of mentions and/or retweets between users.
+This type of information flow defines a community in a much different way than transfer entropy.
+Instead of defining communities by the loss of uncertainty in one user's tweeting history based on another's, we define an interaction-based communities by weighting the user-follower network with a measure proportional to the number of mentions and/or retweets between users.
 % We can therefore define interaction-based communities by weighting the user-follower network with a measure proportional to the number of mentions and retweets between users. 
-For the interaction-based communities we consider three weighting schema: proportional retweets
+For the interaction-based communities we consider three weighting schemes: proportional retweets,
 \begin{equation}
-w_{u \to f}^{\text{R}}=pR=\frac{\mbox{\# retweets of }u \mbox{ by }f}{\mbox{\# total retweets made by }f}
+w_{u \to f}^{\text{R}}=pR=\frac{\mbox{\# retweets of }u \mbox{ by }f}{\mbox{\# total retweets made by }f},
 \end{equation}
-proportional mentions 
+proportional mentions,
 \begin{equation}
-w_{u \to f}^{\text{M}} = pM = \frac{\mbox{\# mentions of }f \mbox{ by }u}{\mbox{\# total mentions of }f}
+w_{u \to f}^{\text{M}} = pM = \frac{\mbox{\# mentions of }f \mbox{ by }u}{\mbox{\# total mentions of }f},
 \end{equation}
-and mention-retweet as the arithmetic mean of these two measures:
+and mention-retweet as the arithmetic mean of these two measures,
 %we weight each edge from a user $u$ to a follower $f$ through a combination of proportional mentions ($pM$):
@@
 \end{align}
-This weight captures the similarity between users in terms of topic discussed in their tweets.
+This weight captures the similarity between users in terms of the topics discussed in their tweets.

### 2014-01-18 paper/parts/results.tex
Added another round of corrections to the paper.

@@
 Moreover, this view does not account for which users belong to which communities, and in particular which users belong to the same communities across community types.
-To answer this question, we invoke methods for cluster comparisons: given two different clusterings of nodes into communities, how similar are the two clusters?
-The standard approach to answering this question is to define a metric on the space of clusterings.
-Because OSLOM detects \emph{coverings} rather than \emph{partitions} of users, standard cluster comparison metrics like variation of information~\cite{meilua2003comparing} are not appropriate.
+To answer this question, we invoke methods for the comparison of clusters: given two different clusterings of nodes into communities, how similar are the two clusters?
+The standard approach to answering this question is to define a metric on the space of possible partitions.
+Because OSLOM detects \emph{coverings} rather than \emph{partitions} of users (that is, it allows for communities to overlap), standard cluster comparison metrics like variation of information~\cite{meilua2003comparing} are not appropriate.
 Instead, we use a generalization of variation of information first introduced in~\cite{lancichinetti2009detecting}, the normalized mutual information.
-The normalized mutual information stems from treating clustering as a community identification problem: given that we know a node's community membership(s) in the first clustering, how much information do we have about its community membership(s) in the second clustering, and vice versa?
+The normalized mutual information stems from treating clustering as a community identification problem: given that we know a node's community membership(s) in the first covering, how much information do we have about its community membership(s) in the second covering, and vice versa?
 Consider the two coverings $\mathcal{C}_{1}$ and $\mathcal{C}_{2}.$We think of the community memberships of a randomly chosen node in $\mathcal{C}_{1}$ as a binary random vector $\mathbf{X} \in \{0, 1\}^{|\mathcal{C}_{1}|}$ where the $i^{\text{th}}$ entry of the vector is 1 if the node belongs to community $i$ and 0 otherwise.
@@
 Note that the communities defined by the follower network do tend to have higher edge weights internal compared to across community boundaries.
-Thus, we do see that the structural communities capture some information about the functional behavior of users in terms of topics and interaction.
+Thus, we do see that the structural communities capture some information about the functional behavior of communities of users in terms of topics and interaction.
 However, the ratio is not as large as when we explicitly seek out communities based on a particular type of functional community.
@@
 As demonstrated in~\cite{good2010performance} in the context of modularity maximization-based community detection, an exponential number of nearby partitions may exist that nearly maximize an objective function used to measure the goodness-of-fit of the graph partition used for community detection.
-Because of this and related issues, it is always wise to perform some sort of curated study of the communities returned by any  community detection algorithm to verify their meaningfulness with respect to the scientific question at hand.
+Because of this and related issues, it is always wise to perform some sort of qualitative study of the communities returned by any  community detection algorithm to verify their meaningfulness with respect to the scientific question at hand.
 In this section, we consider a collection of communities in such a study.

### 2014-01-18 paper/drafts/conclusions.tex
Added the beginning of a draft for the conclusion.

%File: formatting-instruction.tex
\documentclass[letterpaper]{article}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\usepackage{amssymb, amsmath, amsthm}
\usepackage{graphicx}
\usepackage{multirow}

\begin{document}

\section{Conclusion}

% What have we done:
% ==================

In this study, we have demonstrated that the communities observed in online social networks are highly question-dependent, and that different definitions of communities reveal different relationships between users. More importantly, we have shown that these different views of the network are not revealed by using the structural network alone. We found that community structure differs across community types on both the macro (e.g. number of communities and their size distribution) and micro (e.g. specific membership) scale. We demonstrated that boundaries between communities do represent meaningful internal/external divisions, with conversations and topics tending to be most highly concentrated within communities than without. We found this to be the case even when the community- and edge-types did not agree.

% * Defined four types of communities based natural questions one might ask about users in online social media.

% * Proposed three weightings to detect such communities.

% * Demonstrated that the community structure differed between

% Why Care? (i.e. impact):
% ========================

% What does this mean for researchers in online social media? Businesses?

% Using concepts like centrality to determine influence 
% 	* These metrics are based solely on the structural network.
% 	* Your *activity* may be more important than your *topology* in determining
% 	  your influence.

Our findings have important implications to a common problem in social network analysis: identification of influential individuals. Many network measures of influence are based on the various types of centrality (degree, betweenness, closeness, eigenvector, etc.)~\cite{newman2009networks}. Most centralities explicitly depend on the structure of the network under consideration. But we have seen in our study that a structural network is not sufficient to capture user interaction in online social media. Thus, a naive application of centrality measures to a structural network for influence detection may give rise to erroneous results. This result has been explored previously~\cite{kitsak2010identification}, and our work further highlights its importance. Moreover, weighted generalizations of these centralities might lead to better insights about who is actually influential in a social network.

% Future Work:
% ============

% More with transfer entropy.
% 	Why did information tend to flow *across*, rather than within, community boundaries?

% Longitudinal study:
% 	How do the different types of communities change over time? Are activity-based communities more stable than interaction-based, etc.? For example, preliminary studies indicate that `conversations,' as defined by mentions and retweets, tend to move outside of structural communities over time.

Our work has introduced a novel use of transfer entropy for the detection of activity-based communities. In previous work on online social media~\cite{ver2012information}, transfer entropy was found useful for identifying influence between users. It is thus interesting that we find influence tends to be higher across community boundaries than within them. This counterintuitive result warrants further investigation. In addition, more rigorous choices of both the lag and coarsening resolution based on methods for model selection should be explored~\cite{claeskens2008model}.

\end{document}

### 2014-01-19 paper/drafts/conclusions.tex
Minor tweaks to the conclusion.

@@
 number of communities and their size distribution) and micro (e.g.
-specific membership) scale.
-We demonstrated that boundaries between communities do represent meaningful internal/external divisions, with conversations and topics tending to be most highly concentrated within communities than without.
-We found this to be the case even when the community- and edge-types did not agree.
+specific memberships, comemberships) scale.
+
+We have also demonstrated that boundaries between communities represent meaningful internal/external divisions, with conversations and topics tending to be most highly concentrated within communities than without.
+We found this to be the case even when the communities were defined by a different criteria from the edge weights.
 
@@
 
-% * Demonstrated that the community structure differed between
-
-% Why Care? (i.e. impact):
-% ========================
-
-% What does this mean for researchers in online social media? Businesses?
-
-% Using concepts like centrality to determine influence 
-% 	* These metrics are based solely on the structural network.
-% 	* Your *activity* may be more important than your *topology* in determining
-% 	  your influence.
-
-Our findings have important implications to a common problem in social network analysis: identification of influential individuals.
-Many network measures of influence are based on the various types of centrality (degree, betweenness, closeness, eigenvector, etc.)~\cite{newman2009networks}.
-Most centralities explicitly depend on the structure of the network under consideration.
-But we have seen in our study that a structural network is not sufficient to capture user interaction in online social media.
-Thus, a naive application of centrality measures to a structural network for influence detection may give rise to erroneous results.
-This result has been explored previously~\cite{kitsak2010identification}, and our work further highlights its importance.
-Moreover, weighted generalizations of these centralities might lead to better insights about who is actually influential in a social network.
+% * Demonstrated that the community structure differed between weighting to weighting.
 
@@
 This counterintuitive result warrants further investigation.
-In addition, more rigorous choices of both the lag and coarsening resolution based on methods for model selection should be explored~\cite{claeskens2008model}.
+In addition, more rigorous choices of both the lag and time resolution based on methods for model selection should be explored~\cite{claeskens2008model}.
+
+% Why Care? (i.e. impact):
+% ========================
+
+% What does this mean for researchers in online social media? Businesses?
+
+% Using concepts like centrality to determine influence 
+% 	* These metrics are based solely on the structural network.
+% 	* Your *activity* may be more important than your *topology* in determining
+% 	  your influence.
+
+Our findings have important implications to a common problem in social network analysis: identification of influential individuals.
+Many network measures of influence are based on the various types of centrality (degree, betweenness, closeness, eigenvector, etc.)~\cite{newman2009networks}.
+Most centralities depend explicitly on the structure of the network under consideration.
+But we have seen in our study that a structural network is not sufficient to capture user interaction in online social media.
+Thus, a naive application of centrality measures to a structural network for influence detection may give rise to erroneous results.
+This result has been explored previously~\cite{kitsak2010identification}, and our work further highlights its importance.
+Moreover, weighted generalizations of these centralities might lead to better insights about who is actually influential in an online social network.
+
+% More generally, our work demonstrates that asking the proper question is an unavoidable first step to community detection, and that the rich data sets available from
 

### 2014-01-19 paper/parts/results.tex
a few edits

--- 2014-01-17 paper/parts/results.tex
@@
 We see that the community distributions have longer tails for the non-structural networks, and that the interaction-based network has the longest tail.
-The largest communities for the structural, activity-based, topic-based, and interaction-based networks have 198, 358, 338, and 811 members, respectively.
-Most importantly, we see that the distributions are heterogeneous across the network types, highlighting that the different networks give rise to different large-scale community structure dependent on the particular weighting of the structural network.
+The largest communities for the structural, activity-based, topic-based, and interaction-based networks have 198, 358, 338, and 811 members, respectively.[[Dave, I am not sure what the following sentence is trying to get across.]] Most importantly, we see that the distributions are heterogeneous across the network types, highlighting that the different networks give rise to different large-scale community structure dependent on the particular weighting of the structural network.
 
@@
 
-Another interesting example is the one of a community whose topics tend focus on Denver and Colorado.
+Another interesting example is the one of a community whose topics tend to focus on Denver and Colorado.
 These users do not belong to the same community in the interaction-based network, but most of them do belong to the same community in the activity-based network.

### 2014-01-19 paper/parts/intro.tex

@@
 Networks play a central role in online social networks like Twitter, Facebook, and Google+.
-These services allow a user to interact with others based on the online social network they curate, also known as contact filtering~\cite{cazabet2012automated}.
+These services allow a user to interact with others based on the online social network they curate through a process known as contact filtering~\cite{cazabet2012automated}.
 For example, `friends' on Facebook represent reciprocal links for sharing information, while `followers' on Twitter allow a single user to broadcast information in a one-to-many fashion.
@@
 
-Because of the importance of structural networks, a large amount of work has focused on using structural networks to detect communities in online social media.
-Here, we use the term community with the standard definition: a collection of nodes (users) within the network who are more highly connected to each other than to users outside of the community~\cite{newman2004finding}.
+Because of the importance of structural networks in online social media, a large amount of work has focused on using structural networks to detect communities in online social media.
+Here, by `community' we mean the standard definition from the literature: a collection of nodes (users) within the network who are more highly connected to each other than to nodes (users) outside of the community~\cite{newman2004finding}.
 For instance, in~\cite{java2009we}, the authors use a friendship network to determine communities within Twitter, and note that conversations tend to occur within these communities.
@@
 All these methods \emph{begin} with a given network, and then attempt to uncover structure present in the network, i.e., they are agnostic to how the network was constructed.
-As opposed to this agnostic analysis, we propose and illustrate the importance of a deeper analysis.
+As opposed to this agnostic analysis, we propose and illustrate the importance of a question-focused analysis.
 We believe that in order to understand the communities present in a data set, it is important to begin with a clear picture of the community type under consideration, and then to tailor the construction of the network and the use of detection algorithms towards that goal.
@@
 The simplest definition of community, as we have seen, might stem from the network of explicit connections between users on a service (friends, followers, etc.).
-On small time scales, these connections are more or less static, and we might instead determine communities based on who is talking to whom.
+On small time scales, these connections are more or less static, and we might instead determine communities based on who is talking to whom, providing a more dynamic.
 On a more abstract level, a user might consider themselves part of a community of people discussing similar topics.
@@
 We then explore how the communities of users differ depending on the type of network used.
-\textbf{TK: Put a blurb here about the qualitative study.} Finally, we explore how communication patterns differ across and within the different community types.
+Finally, we explore how communication patterns differ across and within the different community types.
 

### 2014-01-21 paper/parts/intro.tex
Incorporate suggestions from Josh, Keith, and Michelle.

@@
 \begin{itemize}
-	\item \textbf{Structure-based:} Who are you friends with? Who do you follow?
+	\item \textbf{Structure-based:} Who are you connected to?
 	\item \textbf{Activity-based:} Who do you act like?
 	\item \textbf{Topic-based:} What do you talk about?
-	\item \textbf{Interaction-based:} Who do you talk to? Who do you talk about?
+	\item \textbf{Interaction-based:} Who do you communicate with?
 \end{itemize}
@@
 
-Most previous work on communities in online social networks have focused on detecting communities based on a single type of network.
+Previous research on communities in social networks focused almost exclusively on different network types in isolation.
 For example, an early paper considered the communities, and associated statistics, inferred from a friendship network in Twitter~\cite{java2009we}.
-More recent work has considered the dynamics of communities based on structural links in Facebook~\cite{nguyen2011adaptive}.
+More recent work has considered the dynamics of communities based on structural links in Facebook~\cite{nguyen2011adaptive} and how structural communities impact mentions and retweets on Twitter~\cite{grabowicz2012social}.
 
@@
 
-There are two broad approaches to topic-based communities in the literature.
+There are two broad approaches to topic-based networks in the literature.
 \cite{rossi2012conversation} used a set of users collected based on their use of a single hashtag, and tracked the formation of follower and friendship links within that set of users.

### 2014-01-21 paper/parts/results.tex
Incorporate suggestions from Josh, Keith, and Michelle.

@@
 \begin{table}[ht]
-	\caption{Number of non-singleton communities and singletons by community type: S(tructural), A(ctivity -based), T(opic-based), and I(nteraction-based).}
+	\caption{Number of non-singleton communities and singletons by community type: S(tructural), A(ctivity-based), T(opic-based), and I(nteraction-based).}
 	\centering
@@
 \includegraphics[width=0.50\textwidth]{figures/nmi_singletons.pdf}
-\caption{The normalized mutual information between the communities using the different weightings.
-Weighting 0 corresponds to the structural (binary weighting) network, weightings 1 through 6 correspond to the weighting using the transfer entropies with lag 1 through 6, weighting 7 corresponds to the hashtag similarity, and weightings 8, 9, and 10 correspond to the mention, retweet, and mention-retweet weightings.
+\caption{The normalized mutual information between the coverings inferred from the different community types.
+Community type 0 corresponds to the structural communities, community types 1 through 6 correspond to the activity-based communities with lag 1 through 6 transfer entropies, community type 7 corresponds to the topic-based communities, and community types 8, 9, and 10 correspond to the interaction-based communities using mentions, retweets, and both mentions and retweets.
 Values of normalized mutual information close to 1 indicate similarity in the community structure, while values close to 0 indicate dissimilarity.
-The normalized mutual information is computed with the singletons removed.}
+The normalized mutual information is computed with singletons and orphan nodes included.}
 \label{Fig-compare_coverings}
@@
 
-We have defined communities using four different criteria: structure, activity, interaction, and topic.
 We next explore how edge weights, and thus different forms of information flow, differ between community types.
@@
 	\caption{The median value across the 100 largest communities for the ratio of the median internal-to-internal weight to the median external-to-internal / internal-to-external weight for the different community / weight pairings.
+Community types correspond to S(tructural), A(ctivity-based), T(opic-based), and I(nteraction-based) communities.
+Weight types correspond to T(ransfer) E(ntropy), M(ention-)R(etweet), and H(ash)T(ag).
 Note: For mention-retweet weights, zero weight edges were excluded from the computation of the median.
@@
 
-We see that for all weight types except the transfer entropy, the weight on the edges internal to the communities tend to be higher than those entering or exiting the communities, ranging from a factor of 1.5 times larger for the activity-based/mention-retweet pairing to a factor of 28 times larger for the topic-based/hashtag similarity pairing.
+We see that for every weight type except transfer entropy, the weight on edges internal to the communities tend to be higher than on edges entering or exiting the communities, ranging from a factor of 1.5 times larger for the activity-based/mention-retweet pairing to a factor of 28 times larger for the topic-based/hashtag similarity pairing.
 As stated above, we expect this ratio to be high for community / weight pairings that match (e.g.
@@
 
-As demonstrated in~\cite{good2010performance} in the context of modularity maximization-based community detection, an exponential number of nearby partitions may exist that nearly maximize an objective function used to measure the goodness-of-fit of the graph partition used for community detection.
+As demonstrated by~\cite{good2010performance} in the context of modularity maximization-based community detection, an exponential number of nearby partitions may exist that nearly maximize the objective function used to measure the goodness-of-fit of the graph partition used for community detection.
 Because of this and related issues, it is always wise to perform some sort of qualitative study of the communities returned by any  community detection algorithm to verify their meaningfulness with respect to the scientific question at hand.

### 2014-01-21 paper/parts/conclusions.tex
Minor tweaks to the conclusion.

--- 2014-01-19 paper/drafts/conclusions.tex
@@
-%File: formatting-instruction.tex
-\documentclass[letterpaper]{article}
-\usepackage{times}
-\usepackage{helvet}
-\usepackage{courier}
-\usepackage{amssymb, amsmath, amsthm}
-\usepackage{graphicx}
-\usepackage{multirow}
-
-\begin{document}
-
 \section{Conclusion}
@@
 In previous work on online social media~\cite{ver2012information}, transfer entropy was found useful for identifying influence between users.
-It is thus interesting that we find influence tends to be higher across community boundaries than within them.
-This counterintuitive result warrants further investigation.
-In addition, more rigorous choices of both the lag and time resolution based on methods for model selection should be explored~\cite{claeskens2008model}.
+Our transfer entropy results thus reflect that influence tends to be higher across community boundaries than within them.
+This result echos the `strength of weak ties' theory from~\cite{granovetter1973strength}, which has found empirical support in~\cite{grabowicz2012social}.
+In addition to exploring this phenomenon further, we plan to consider more rigorous choices of both the lag and time resolution based on methods for model selection~\cite{claeskens2008model}.
 
@@
 % More generally, our work demonstrates that asking the proper question is an unavoidable first step to community detection, and that the rich data sets available from
-
-\end{document}

### 2014-01-21 paper/parts/methods.tex

@@
 
-Since our goal is to explore the functional communities of this network, we filter this network down to the subset of users which actively interact with each other (e.g., retweets and mentions).
+Since our goal is to explore the functional communities of this network, we filter this network down to the subset of users which actively interact with each other (e.g., via retweets and mentions).
 We do this through a metric we call (incoming/outgoing) information events.
@@
 
-\subsection{Topic-based Communities and Hashtag Weighting}
+\subsection{Topic-Based Communities and Hashtag Weighting}
 \label{sec:method-topic}

### 2014-01-22 paper/parts/conclusions.tex
notes in conclusion

@@
 
-In this study, we have demonstrated that the communities observed in online social networks are highly question-dependent, and that different definitions of communities reveal different relationships between users.
+In this study, we have demonstrated that the communities observed in online social networks are highly question-dependent [[Joshua:maybe reword this sentence to explicitly say what we mean by question-dependent", might be a little confusing]], and that different definitions of communities reveal different relationships between users.
 More importantly, we have shown that these different views of the network are not revealed by using the structural network alone.
@@
 We found this to be the case even when the communities were defined by a different criteria from the edge weights.
+[[Wasn't this the opposite in the transfer entropy case?
+Maybe I am remembering wrong.
+If so maybe we can spend a few sentences explaining why this is so leading into the next paragraph]]
 
@@
 
-Our work has introduced a novel use of transfer entropy for the detection of activity-based communities.
+[[This paragraph needs to be recrafted a bit.
+It just reads a little confusing]]Our work has introduced a novel use of transfer entropy for the detection of activity-based communities.
 In previous work on online social media~\cite{ver2012information}, transfer entropy was found useful for identifying influence between users.
@@
 % 	  your influence.
-
+[[While I agree with this next paragraph completely I am not sure we covered this topic enough to be the final paragraph of the conclussion or even in the conclusion. I need to think about this...]]
 Our findings have important implications to a common problem in social network analysis: identification of influential individuals.

### 2014-01-22 paper/parts/intro.tex
Fixed typos / grammatical errors found yesterday.

@@
 
-Networks play a central role in online social networks like Twitter, Facebook, and Google+.
+Networks play a central role in online social media services like Twitter, Facebook, and Google+.
 These services allow a user to interact with others based on the online social network they curate through a process known as contact filtering~\cite{cazabet2012automated}.
@@
 
-Because of the importance of structural networks in online social media, a large amount of work has focused on using structural networks to detect communities in online social media.
+Because of the importance of structural networks in online social media, a large amount of work in this area has focused on using structural networks.
 Here, by `community' we mean the standard definition from the literature: a collection of nodes (users) within the network who are more highly connected to each other than to nodes (users) outside of the community~\cite{newman2004finding}.
 For instance, in~\cite{java2009we}, the authors use a friendship network to determine communities within Twitter, and note that conversations tend to occur within these communities.
-The approach of focusing on structural networks makes sense for `real-world' sociological experiments, where obtaining additional information about users interactions may be expensive and time-consuming.
-However, with the prevalence of large, rich data sets for online social networks, additional information beyond the structure alone may be incorporated, and more realistically reflects how users interact with each other on social media services~\cite{grabowicz2012social}.
+The approach of focusing on structural networks makes sense for `real-world' sociological experiments, where obtaining additional information about user interactions may be expensive and time-consuming.
+However, with the prevalence of large, rich data sets for online social networks, additional information beyond the structure alone may be incorporated, and these augmented networks more realistically reflects how users interact with each other on social media services~\cite{grabowicz2012social}.
 
@@
 All these methods \emph{begin} with a given network, and then attempt to uncover structure present in the network, i.e., they are agnostic to how the network was constructed.
-As opposed to this agnostic analysis, we propose and illustrate the importance of a question-focused analysis.
+As opposed to this agnostic analysis, we propose and illustrate the importance of a question-focused approach.
 We believe that in order to understand the communities present in a data set, it is important to begin with a clear picture of the community type under consideration, and then to tailor the construction of the network and the use of detection algorithms towards that goal.
@@
 The simplest definition of community, as we have seen, might stem from the network of explicit connections between users on a service (friends, followers, etc.).
-On small time scales, these connections are more or less static, and we might instead determine communities based on who is talking to whom, providing a more dynamic.
+On small time scales, these connections are more or less static, and we might instead determine communities based on who is talking to whom, providing a more dynamic picture.
 On a more abstract level, a user might consider themselves part of a community of people discussing similar topics.
-We might also define communities as collections of people who exhibit similar behaviors on a service, as in a communities of teenagers vs.\ elderly users.
+We might also define communities as collections of people who exhibit similar behaviors on a service, as in communities of teenagers vs.\ elderly users.
 We can characterize these types of communities based on the types of questions we might ask about them:
@@
 We propose looking at when and how communities motivated by different questions overlap, and whether different approaches to asking the question, ``What community are you in?'' leads to different insights about a social network.
-For example, a user on Twitter might connect mostly with computational social scientists, talk mostly about machine learning, interact soley with close friends (who may or may not be computational social scientists), and utilize the service only on nights and weekends.
+For example, a user on Twitter might connect mostly with computational social scientists, talk mostly about machine learning, interact solely with close friends (who may or may not be computational social scientists), and utilize the service only on nights and weekends.
 Each of these different `profiles' of the user highlight different views of the user's social network, and represent different types of communities.
@@
 
-The activity-based approach is motivated by the question of which individuals act in a concerted manner, e.g., which users use a service with similar frequency and at similar times of day.
+The activity-based approach is motivated by the question of which individuals act in a concerted manner, e.g., which users use a service in a similar way.
 The main tools for answering this question stem from information theory.
@@
 
-Our topic-based and interaction-based approaches, in contrast to the activity-based approach, rely on the \emph{content} of a user's interaction and ignore its temporal component.
+Our topic-based and interaction-based approaches, in contrast to the activity-based approach, rely on the \emph{content} of a user's interactions and ignore their temporal components.
 The content contains a great deal of information about the communication between users.
@@
 Both approaches thus begin with a particular topic in mind, and perform the data collection accordingly.
-Other approaches use probabilistic models for the topics that treat community membership as a latent variable~\cite{yin2012latent}.
+Other approaches use probabilistic models for the topics and treat community membership as a latent variable~\cite{yin2012latent}.
 
@@
 A notable exception to the analysis of isolated types of networks is~\cite{lim2012tweets}, which considered both structure-based and interaction-based communities on Twitter.
-However, this study focuses on data collected based on particular topics (country music, tennis, and basketball), and not on a generic subpopulation of Twitter users.
+However, this study focused on data collected based on particular topics (country music, tennis, and basketball), and not on a generic subpopulation of Twitter users.
 Moreover, it did not explore the differences in community structure resulting from the different network weightings, and focuses on aggregate statistics (community size, network statistics, etc.).
-Another notable exception is~\cite{kao2013talison}, where the authors use a tensor representation of user data to incorporate retweet and hashtag information into a study of the social media coverage of the Occupy Movement.
+Another notable exception is~\cite{kao2013talison}, where the authors used a tensor representation of user data to incorporate retweet and hashtag information into a study of the social media coverage of the Occupy Movement.
 The tensor can then be decomposed into factors in a generalization of the singular value decomposition of a matrix, and these factors can be used to determine `salient' users.

### 2014-01-22 paper/parts/methods.tex
Fixed typos / grammatical errors found yesterday.

@@
 We then describe our methodology for constructing the question-specific networks under study.
-In particular, we introduce an information theoretic method for activity-based communities, a retweet-mention summary of communication for interaction-based communities, and a hashtag similarity metric for defining topic-based communities.
+In particular, we introduce an information theoretic method for activity-based communities, a retweet-mention statistic for interaction-based communities, and a hashtag similarity metric for defining topic-based communities.
 
@@
 When selecting a detection algorithm we propose that all three (weight, direction and overlap) are important for the following reasons: Twitter is a directed network and we wish to maintain this structure.
-But we are interested in not just structure but function, to capture function we use edge weightings which must be used in the community detection process.
+But we are interested in not just structure but function, to capture function we use edge weightings which must be incorporated into the community detection process.
 Finally, since people can belong to multiple and possibly overlapping social (e.g., college friends, co-workers, family, etc.) and topical (e.g., a user can be interested in both cycling and politics and use the network to discuss the two topics with the two different communities) communities, we are interested in finding \textit{overlapping} communities, rather than partitions of the weighted directed network.
@@
 
-Since our goal is to explore the functional communities of this network, we filter this network down to the subset of users which actively interact with each other (e.g., via retweets and mentions).
+Since our goal is to explore the functional communities of this network, we filter the network down to the subset of users which actively interact with each other (e.g., via retweets and mentions).
 We do this through a metric we call (incoming/outgoing) information events.
@@
 Thus, we reduce all of the information generated by a user on Twitter to a time series $\{ X_{t}(u)\}$ where $t$ ranges over the time interval for which we have data (9 weeks in this case).
-Because status updates are only collected in discrete, 1-second time intervals, it is natural to consider the only the discrete times $t = 1 \text{ s}, 2 \text{ s}, \ldots, $ relative to a reference time.
+Because status updates are only collected in discrete, 1-second time intervals, it is natural to consider only the discrete times $t = 1 \text{ s}, 2 \text{ s}, \ldots, $ relative to a reference time.
 We can then compute the flow of information between two users $u$ and $v$ by computing the transfer entropy between their time series $X_{t}(u)$ and $X_{t}(v).$
@@
 
-The final community we consider is a topic-based or topical community, i.e., a community defined by the content (topics) they discuss.
+The final community we consider is a topic-based or topical community, i.e., a community defined by the content (topics) users discuss.
 So in a topical community, users are defined to be a member of a community if they tweet \emph{about} similar topics as other members of the community.
@@
 In order to detect the topical communities, we weight the edges of the user-follower network through a measure based on the number of common hashtags between pairs of users.
-Hashtags are a good proxy for a tweets content as hashtags are explicitly meant to be keywords indicating the topic of the tweet.
+Hashtags are a good proxy for a tweet's content as hashtags are explicitly meant to be keywords indicating the topic of the tweet.
 Moreover they are widely used and straightforward to detect.

### 2014-01-22 paper/parts/results.tex
Fixed typos / grammatical errors found yesterday.

@@
 The complementary cumulative distribution of community sizes is given in Figure~\ref{Fig-community_size_distribution}.
-Note that both axes are plotted on log-scale, and the horizontal axis begins with non-singleton communities.
+Note that both axes are plotted on log-scales.
 Thus, for a fixed community size $c$, Figure~\ref{Fig-community_size_distribution} shows the proportion of communities of size greater than $c$ for each community type.
 We see that the community distributions have longer tails for the non-structural networks, and that the interaction-based network has the longest tail.
-The largest communities for the structural, activity-based, topic-based, and interaction-based networks have 198, 358, 338, and 811 members, respectively.[[Dave, I am not sure what the following sentence is trying to get across.]] Most importantly, we see that the distributions are heterogeneous across the network types, highlighting that the different networks give rise to different large-scale community structure dependent on the particular weighting of the structural network.
+The largest communities for the structural, activity-based, topic-based, and interaction-based networks have 198, 358, 338, and 811 members, respectively.
+Most importantly, we see that the distributions of community sizes differ across the community types, highlighting that the different networks give rise to different large-scale community structure dependent on the particular weighting of the structural network.
 
@@
 
-As demonstrated by~\cite{good2010performance} in the context of modularity maximization-based community detection, an exponential number of nearby partitions may exist that nearly maximize the objective function used to measure the goodness-of-fit of the graph partition used for community detection.
+As demonstrated by~\cite{good2010performance} in the context of modularity maximization-based community detection, an exponential number of nearby partitions may exist that nearly maximize an objective function used to measure the goodness-of-fit of a graph partition used for community detection.
 Because of this and related issues, it is always wise to perform some sort of qualitative study of the communities returned by any  community detection algorithm to verify their meaningfulness with respect to the scientific question at hand.
@@
 
-Another interesting example is the one of a community whose topics tend to focus on Denver and Colorado.
+Another interesting example is a community whose topics tend to focus on Denver and Colorado.
 These users do not belong to the same community in the interaction-based network, but most of them do belong to the same community in the activity-based network.

### 2014-01-22 paper/parts/intro.tex
Incorporated Bill's suggestions.

@@
 For example, `friends' on Facebook represent reciprocal links for sharing information, while `followers' on Twitter allow a single user to broadcast information in a one-to-many fashion.
-Central to all of these interactions is the fact that the \emph{structure} of the social network dictates the ways that information can be broadcast or diffuse through the service.
+Central to all of these interactions is the fact that the \emph{structure} of the social network influences how information can be broadcast or diffuse through the service.
 
 Because of the importance of structural networks in online social media, a large amount of work in this area has focused on using structural networks.
-Here, by `community' we mean the standard definition from the literature: a collection of nodes (users) within the network who are more highly connected to each other than to nodes (users) outside of the community~\cite{newman2004finding}.
-For instance, in~\cite{java2009we}, the authors use a friendship network to determine communities within Twitter, and note that conversations tend to occur within these communities.
+Here, by `community' we mean the standard definition from the literature on social networks: a collection of nodes (users) within the network who are more highly connected to each other than to nodes (users) outside of the community~\cite{newman2004finding}.
+For instance, in~\cite{java2009we}, the authors use a follower network to determine communities within Twitter, and note that conversations tend to occur within these communities.
 The approach of focusing on structural networks makes sense for `real-world' sociological experiments, where obtaining additional information about user interactions may be expensive and time-consuming.
@@
 As opposed to this agnostic analysis, we propose and illustrate the importance of a question-focused approach.
-We believe that in order to understand the communities present in a data set, it is important to begin with a clear picture of the community type under consideration, and then to tailor the construction of the network and the use of detection algorithms towards that goal.
+We believe that in order to understand the communities present in a data set, it is important to begin with a clear picture of the community type under consideration, and then perform the network collection and community detection with that community type in mind.
 
 This is especially true for social network analysis.
-In online social networks, `community' could refer to several possible structures.
+In online social networks, a `community' could refer to several possible structures.
 The simplest definition of community, as we have seen, might stem from the network of explicit connections between users on a service (friends, followers, etc.).
@@
 \begin{itemize}
-	\item \textbf{Structure-based:} Who are you connected to?
+	\item \textbf{Structure-based:} Who have you stated you are friends with? Who do you follow?
 	\item \textbf{Activity-based:} Who do you act like?
@@
 
+This is not meant to be an exhaustive list, but rather a list of some of the more common types of communities observed in social networks.
 We propose looking at when and how communities motivated by different questions overlap, and whether different approaches to asking the question, ``What community are you in?'' leads to different insights about a social network.
@@
 
-The activity-based approach is motivated by the question of which individuals act in a concerted manner, e.g., which users use a service in a similar way.
+The activity-based approach is motivated by the question of which individuals act in a homogeneous manner, e.g., which users use a service in a similar way.
 The main tools for answering this question stem from information theory.
 We consider each user on an online social network as an information processing unit, but ignore the content of their messages.
-This viewpoint has been successfully applied to gain insight into local behavior in online social networks~\cite{darmon2013understanding}.
-The information processing framework applies equally well to spatially extended systems.
 In particular, our current activity-based approach was originally motivated by a methodology used to detect functional communities within populations of neurons~\cite{shalizi2007discovering}.
-This approach has been extended to social systems, detecting communities on Twitter based on undirected information flow~\cite{darmon2013detecting}.
-Others have successfully applied a similar viewpoint using transfer entropy, a measure of directed information flow, to perform link detection on Twitter~\cite{ver2012information}.
+Similar information theoretic approaches have been used with social systems to gain insight into local behavior in online social networks~\cite{darmon2013understanding}, to detect communities on Twitter based on undirected information flow~\cite{darmon2013detecting}, and to perform link detection on Twitter via transfer entropy, a directed measure of information flow~\cite{ver2012information}.
 However, transfer entropy has not been used for community detection, and we extend this previous work to incorporate transfer entropy-based communities.
@@
 
-The interaction-based approach relies on meta-data about who a user converses with on the social media service.
+Finally, the interaction-based approach relies on meta-data and the text of the message to identify who a user converses with on the social media service.
 On Twitter, we can use mentions (indicating a directed communication) and retweets (indicating endorsement of another user) to identify conversation.
@@
 
-There are two broad approaches to topic-based networks in the literature.
+There are two broad approaches to topic-based communities in the literature.
 \cite{rossi2012conversation} used a set of users collected based on their use of a single hashtag, and tracked the formation of follower and friendship links within that set of users.

### 2014-01-22 paper/parts/methods.tex
Added labels for equations.
Merge branch 'master' of https://github.com/ddarmon/sfi-dynComm
Conflicts:
	paper/paper.tex

@@
 In the following sections, we introduce the problem of community detection, and present the data set used for our analyses.
-We then describe our methodology for constructing the question-specific networks under study.
+We then describe our methodology for constructing the question-specific networks.
 In particular, we introduce an information theoretic method for activity-based communities, a retweet-mention statistic for interaction-based communities, and a hashtag similarity metric for defining topic-based communities.
@@
 In this paper however we focus on a class of networks and communities that is far less studied, in particular we study networks which are both \textit{weighted} and \textit{directed} and communities within those weighted directed networks that can (but need not) \emph{overlap}.
-When selecting a detection algorithm we propose that all three (weight, direction and overlap) are important for the following reasons: Twitter is a directed network and we wish to maintain this structure.
-But we are interested in not just structure but function, to capture function we use edge weightings which must be incorporated into the community detection process.
+When selecting a detection algorithm we propose that all three (weight, direction, and overlap) are important for the following reasons.
+First, communication on Twitter occurs in a directed manner, with users broadcasting information to their followers.
+An undirected representation of the network would ignore this fact, and could lead to communities composed of users who do not actually share information.
+Second, we are interested in not just the structure of links but also in their function, and to capture this we use edge weightings which must be incorporated into the community detection process.
 Finally, since people can belong to multiple and possibly overlapping social (e.g., college friends, co-workers, family, etc.) and topical (e.g., a user can be interested in both cycling and politics and use the network to discuss the two topics with the two different communities) communities, we are interested in finding \textit{overlapping} communities, rather than partitions of the weighted directed network.
@@
 
-This poses an interesting problem because the majority of community detection algorithms developed so far are built to find partitions of a network and very few are aimed at finding overlapping communities \cite{BaumesGKMP05,PalEtAl05,ZhaWanZha07,Gre07,PhysRevE.77.016107,Lancichinetti2009,PhysRevE.80.016105,Kovacs2010}.
+This last criterion in particular poses a problem because the majority of community detection algorithms developed so far are built to find partitions of a network and few are aimed at finding overlapping communities \cite{BaumesGKMP05,PalEtAl05,ZhaWanZha07,Gre07,PhysRevE.77.016107,Lancichinetti2009,PhysRevE.80.016105,Kovacs2010}.
 Among these methods, even fewer deal with directed or weighted networks.
@@
 Their method relies on a fitness function that measures the statistical significance of clusters with respect to random fluctuations, and attempts to optimize this fitness function across all clusters.
-For this paper we use OSLOM as it allowed us to detect \emph{overlapping} communities present in our \emph{weighted} and \emph{directed} network.
+For this paper we use OSLOM since it allowed us to detect \emph{overlapping} communities present in our \emph{weighted} and \emph{directed} network.
 
@@
 Since our goal is to explore the functional communities of this network, we filter the network down to the subset of users which actively interact with each other (e.g., via retweets and mentions).
-We do this through a metric we call (incoming/outgoing) information events.
+We do this by measuring what we call (incoming/outgoing) information events.
 We define an outgoing information event for a given user $u$ as either a mention made by $u$ of another user in the network, or a retweet of one of $u$'s tweets by another user in the network.
@@
 In this study the link is directed from the user to the follower because this is the direction in which the information (in the case of transfer entropy) or influence (in the case of mention-retweets) flows.
+Thus, for a pair of users $u$ and $v$, an edge $a_{v \to u}$ in the structural network has weight 1 if user $u$ follows $v$, and 0 otherwise.
 The final network consists of 6,917 nodes and 1,481,131 edges.
@@
 \begin{align}
-	w_{u \to f}^{\text{TE}(k)} = \widehat{\text{TE}}_{X(u) \to X(f)}^{(k)}.
+	w_{u \to f}^{\text{TE}(k)} = \widehat{\text{TE}}_{X(u) \to X(f)}^{(k)}. \label{Eqn-EW-activity}
 \end{align}
 
-Operationally, we expect users to interact with Twitter on a human time scale, and thus the natural one-second time resolution is too fine.
+Operationally, we expect users to interact with Twitter on a human time scale, and thus the natural one-second time resolution is too fine since most humans do not write tweets at the time scale of seconds.
 We coarsen each time series by considering non-overlapping time intervals ten minutes in length.
@@
 The choice of lag must balance a trade-off between additional information and sparsity of samples: as we increase the lag, we account for longer range dependencies, but we also decrease the number of samples availabe to infer a higher dimensional predictive distribution.
-Ultimately, due to similarities in the underlying communities (see Figure \ref{Fig-compare_coverings}), we chose a lag-4 transfer entropy.
+Ultimately, due to similarities in the underlying communities we chose a lag-4 transfer entropy.
 All references to activity-based weights, unless otherwise noted, refer to this choice of lag.
@@
 This type of information flow defines a community in a much different way than transfer entropy.
-Instead of defining communities by the loss of uncertainty in one user's tweeting history based on another's, we define an interaction-based communities by weighting the user-follower network with a measure proportional to the number of mentions and/or retweets between users.
+Instead of defining communities by the loss of uncertainty in one user's tweeting history based on another's, we define interaction-based communities by weighting the user-follower network with a measure proportional to the number of mentions and/or retweets between users.
 % We can therefore define interaction-based communities by weighting the user-follower network with a measure proportional to the number of mentions and retweets between users. 
@@
 \begin{align}
-	w_{u \to f}^{\text{MR}} = \frac{(pM+pR)}{2}.
+	w_{u \to f}^{\text{MR}} = \frac{(pM+pR)}{2}. \label{Eqn-EW-interaction}
 \end{align}
@@
 \begin{align}
-	w_{u \to f}^{\text{HT}} = \frac{\vec{h}(u) \cdot \vec{h}(f)}{||\vec{h}(u)|| \ \ ||\vec{h}(f)||}.
+	w_{u \to f}^{\text{HT}} = \frac{\vec{h}(u) \cdot \vec{h}(f)}{||\vec{h}(u)|| \ \ ||\vec{h}(f)||}. \label{Eqn-EW-topic}
 \end{align}

### 2014-01-22 paper/parts/results.tex
Merge branch 'master' of https://github.com/ddarmon/sfi-dynComm
Conflicts:
	paper/paper.tex

@@
 
-The number of singletons by community type is also shown in Table~\ref{Table-comm_count}.
-We see that the topic- and interaction-based communities have the most singletons, with the activity-based community dominating this measure.
+We see in Table~\ref{Table-comm_count} that the topic- and interaction-based communities have the most singletons, with the activity-based community dominating this measure.
 This result for the activity-based community is partially an artifact of a property of the retweet/mention weighting: 717 of the users were disconnected from the network by how the weights were defined, resulting in `orphan' nodes which we have included in the collection of singletons for all of our analyses.
@@
 This seems to indicate that a large fraction of the 6917 (nearly 25\%) do not interact with each other in a concerted way that would mark them as a community under our interaction-based definition.
+This agrees with a result previously reported in~\cite{romero2011influence} about how most users passively interact with incoming information on Twitter.
 
@@
 Thus, we see that although the activity-based, interaction-based, and topic-based communities relied on the structural network, their community structure differs \emph{the most} from the community structure of the follower network.
-This agrees with the results from the previous section, and reinforces that the follower network is a necessary but not sufficient part of detecting communities in online social networks.
+This agrees with the results from the previous section, and reinforces that the follower network is a necessary but not sufficient part of detecting communities characterized by properties beyond follower-followee relationships.
 
@@
 
-We next explore how edge weights, and thus different forms of information flow, differ between community types.
+We next explore how the edge weights defined by equations (\ref{Eqn-EW-activity}), (\ref{Eqn-EW-interaction}), and (\ref{Eqn-EW-topic}), and thus different forms of information flow, differ between community types.
 For a fixed community type, edges for a particular community may be partitioned into three sets: those from a user in the community to another user in the community (internal-to-internal), those from a user in the community to a user outside of the community (internal-to-external), and those from a user outside the community to a user inside the community (external-to-internal).
@@
 	\caption{The median value across the 100 largest communities for the ratio of the median internal-to-internal weight to the median external-to-internal / internal-to-external weight for the different community / weight pairings.
+For each entry $a/b$ in the table, $a$ corresponds to median ratio value for edges external-to-internal, and $b$ corresponds to the median ratio value for edges internal-to-external .
 Community types correspond to S(tructural), A(ctivity-based), T(opic-based), and I(nteraction-based) communities.

### 2014-01-22 paper/parts/conclusions.tex

--- 2014-01-21 paper/parts/conclusions.tex
@@
-\section{Conclusion}
+\section{Conclusion and Future Works}
 
@@
 
-In this study, we have demonstrated that the communities observed in online social networks are highly question-dependent, and that different definitions of communities reveal different relationships between users.
+%In this study, we have demonstrated that the communities observed in online social %networks are highly question-dependent 
+%[[Joshua:maybe reword this sentence to explicitly say what we mean by question-dependent", might be a little confusing]]
+%, and that different definitions of communities reveal different relationships between users.
 More importantly, we have shown that these different views of the network are not revealed by using the structural network alone.
@@
 
-We have also demonstrated that boundaries between communities represent meaningful internal/external divisions, with conversations and topics tending to be most highly concentrated within communities than without.
+In this study, we have demonstrated that the communities observed in online social networks are highly question-dependent i.e., the questions posed about a network a priori have a strong impact on the communities observed.
+Moreover, using different definitions of \emph{community} reveal different and interesting relationships between users.
+More importantly, we have shown that these different views of the network are not revealed by using the structural network or any one weighting schema alone.
+By varying the questions we asked about the network and then deriving weighting schema to answer that particular question, we found that community structure differed across community types on both the macro (e.g.
+number of communities and their size distribution) and micro (e.g.
+specific memberships, comemberships) scale in interesting ways.
+
+%We have also demonstrated that boundaries between communities represent meaningful internal/external divisions, with conversations and topics tending to be most highly concentrated within communities than without.
 We found this to be the case even when the communities were defined by a different criteria from the edge weights.
+[[Wasn't this the opposite in the transfer entropy case?
+Maybe I am remembering wrong.
+If so maybe we can spend a few sentences explaining why this is so leading into the next paragraph]]
+
+To verify the validity of these communities we demonstrated that boundaries between communities represent meaningful internal/external divisions.
+In particular, conversations (e.g., retweets and mentions) and topics (e.g., hashtags) tended to be most highly concentrated within communities.
+We found this to be the case even when the communities were defined by a different criteria from the edge weights.
+
+At first glance the boundaries defined for the communities in the activity based network (those weighted with transfer entropy) seemed less meaningful.
+However, upon further investigation our novel use of transfer entropy for the detection of activity-based communities\footnote{It should be noted that while in previous work on online social media~\cite{ver2012information}, transfer entropy was found useful for identifying influence between users, it has not to the best of our knowledge been used to aid in the identification of communities.} brought to light a very interesting fact about this social network: influence tends to be higher across community boundaries than within them.
+This result echos the `strength of weak ties' theory from~\cite{granovetter1973strength}, which was supported empirically in~\cite{grabowicz2012social}.
+This means that our novel use of transfer entropy not only defines boundaries that are meaningful divisions between communities but it helps illustrate that influential users of a community need not be a member of that community.
+
+%Start of futre work**
+[[Should this future works paragraph be its own section?]]
+This findings has important implications to a common problem in social network analysis: identification of influential individuals.
+Many network measures of influence are based on the various types of centrality (degree, betweenness, closeness, eigenvector, etc.)~\cite{newman2009networks}.
+Most centralities depend explicitly on the structure of the network under consideration.
+But we have seen in our study that a structural network alone is not sufficient to capture user interaction or influence in online social media.
+Thus, a na\"ive application of centrality measures to a structural network for influence detection may give rise to erroneous results.
+This result has been explored previously~\cite{kitsak2010identification}, and our work further highlights its importance.
+We believe that weighted generalizations of these centralities using transfer entropy might lead to better insights about who is actually influential in an online social network.
+In addition to exploring this phenomenon further, we plan to explore a broader selection of choices for both the transfer-entropy lag and tweet history time resolution.
+We believe that by doing an in-depth analysis of both of these parameters we can discover interesting activity-based communities that occur on much broader time scales.
+%End of futre work**
+  %based on methods for model selection~\cite{claeskens2008model}.
+
+%Our work has introduced a novel use of transfer entropy for the detection of activity-based communities.
+
+%Our transfer entropy results thus reflect that influence tends to be higher across community boundaries than within them.
+This result echos the `strength of weak ties' theory from~\cite{granovetter1973strength}, which has found empirical support in~\cite{grabowicz2012social}.
+In addition to exploring this phenomenon further, we plan to consider more rigorous choices of both the lag and time resolution based on methods for model selection~\cite{claeskens2008model}.
 
@@
 
-Our work has introduced a novel use of transfer entropy for the detection of activity-based communities.
+%[[This paragraph needs to be recrafted a bit. It just reads a little confusing]]
+
+%Our work has introduced a novel use of transfer entropy for the detection of activity-based communities.
 In previous work on online social media~\cite{ver2012information}, transfer entropy was found useful for identifying influence between users.
@@
 % 	  your influence.
-
-Our findings have important implications to a common problem in social network analysis: identification of influential individuals.
-Many network measures of influence are based on the various types of centrality (degree, betweenness, closeness, eigenvector, etc.)~\cite{newman2009networks}.
-Most centralities depend explicitly on the structure of the network under consideration.
-But we have seen in our study that a structural network is not sufficient to capture user interaction in online social media.
-Thus, a naive application of centrality measures to a structural network for influence detection may give rise to erroneous results.
-This result has been explored previously~\cite{kitsak2010identification}, and our work further highlights its importance.
-Moreover, weighted generalizations of these centralities might lead to better insights about who is actually influential in an online social network.
+%[[While I agree with this next paragraph completely I am not sure we covered this topic enough to be the final paragraph of the conclussion or even in the conclusion. I need to think about this...]]
 
 % More generally, our work demonstrates that asking the proper question is an unavoidable first step to community detection, and that the rich data sets available from
+
+This work demonstrates that asking the proper question and then crafting a weighting scheme to answer that question is an unavoidable first step to community detection.
+More generally, this work illustrates that many rich and interesting communities present in online social networks are invisible if no clear idea of community is defined a priori and the use of question-oriented community detection can easily bring all of these communities into the light.

### 2014-01-22 paper/parts/conclusions.tex
Minor changes to Josh's rewrite of the conclusion.

@@
 
-In this study, we have demonstrated that the communities observed in online social networks are highly question-dependent i.e., the questions posed about a network a priori have a strong impact on the communities observed.
+In this study, we have demonstrated that the communities observed in online social networks are highly question-dependent.
+The questions posed about a network \emph{a priori} have a strong impact on the communities observed.
 Moreover, using different definitions of \emph{community} reveal different and interesting relationships between users.
-More importantly, we have shown that these different views of the network are not revealed by using the structural network or any one weighting schema alone.
+More importantly, we have shown that these different views of the network are not revealed by using the structural network or any one weighting scheme alone.
 By varying the questions we asked about the network and then deriving weighting schema to answer that particular question, we found that community structure differed across community types on both the macro (e.g.
@@
 To verify the validity of these communities we demonstrated that boundaries between communities represent meaningful internal/external divisions.
-In particular, conversations (e.g., retweets and mentions) and topics (e.g., hashtags) tended to be most highly concentrated within communities.
+In particular, conversations (e.g.
+retweets and mentions) and topics (e.g.
+hashtags) tended to be most highly concentrated within communities.
 We found this to be the case even when the communities were defined by a different criteria from the edge weights.
 
-At first glance the boundaries defined for the communities in the activity based network (those weighted with transfer entropy) seemed less meaningful.
+% At first glance the boundaries defined by the communities in the activity-based network (those weighted with transfer entropy) seemed less meaningful.
 However, upon further investigation our novel use of transfer entropy for the detection of activity-based communities\footnote{It should be noted that while in previous work on online social media~\cite{ver2012information}, transfer entropy was found useful for identifying influence between users, it has not to the best of our knowledge been used to aid in the identification of communities.} brought to light a very interesting fact about this social network: influence tends to be higher across community boundaries than within them.
@@
 
-%Start of futre work**
-[[Should this future works paragraph be its own section?]]
-This findings has important implications to a common problem in social network analysis: identification of influential individuals.
+% Removed the footnote.
+
+At first glance the boundaries defined by the activity-based communities derived from the transfer entropy weighting seemed less meaningful.
+However, upon further investigation our novel use of transfer entropy for the detection of activity-based communities highlighted an important fact about this social network: influence tended to be higher across community boundaries than within them.
+This result echos the `strength of weak ties' theory from~\cite{granovetter1973strength}, which has found empirical support in~\cite{grabowicz2012social} for online social networks.
+This means that our novel use of transfer entropy not only defines boundaries that are meaningful divisions between communities but also illustrates that users who have a strong influence on a community need not be a member of that community.
+
+%Start of future work**
+Our findings have important implications to a common problem in social network analysis: identification of influential individuals.
 Many network measures of influence are based on the various types of centrality (degree, betweenness, closeness, eigenvector, etc.)~\cite{newman2009networks}.
@@
 
-This work demonstrates that asking the proper question and then crafting a weighting scheme to answer that question is an unavoidable first step to community detection.
-More generally, this work illustrates that many rich and interesting communities present in online social networks are invisible if no clear idea of community is defined a priori and the use of question-oriented community detection can easily bring all of these communities into the light.
+This work demonstrates that asking the proper question and then crafting an appropriate weighting scheme to answer that question is an unavoidable first step for community detection in online social media.
+More generally, this work illustrates that without a clear definition of community, many rich and interesting communities present in online social networks remain invisible.
+Question-oriented community detection can bring those hidden communities into the light.

### 2014-01-22 paper/parts/results.tex
Minor changes to Josh's rewrite of the conclusion.

@@
 
-\subsection{Qualitative Analysis of Community Memberships Across Types}
+% \subsection{Qualitative Analysis of Community Memberships Across Types}
 
-As demonstrated by~\cite{good2010performance} in the context of modularity maximization-based community detection, an exponential number of nearby partitions may exist that nearly maximize an objective function used to measure the goodness-of-fit of a graph partition used for community detection.
+% As demonstrated by~\cite{good2010performance} in the context of modularity maximization-based community detection, an exponential number of nearby partitions may exist that nearly maximize an objective function used to measure the goodness-of-fit of a graph partition used for community detection.
 Because of this and related issues, it is always wise to perform some sort of qualitative study of the communities returned by any  community detection algorithm to verify their meaningfulness with respect to the scientific question at hand.
@@
 
-In the topic-based communities, we find a single community consisting of 83 users who tweet about environmental issues and frequently use hashtags such as \#green, \#eco and \#sustainability.
+% In the topic-based communities, we find a single community consisting of 83 users who tweet about environmental issues and frequently use hashtags such as \#green, \#eco and \#sustainability.
 We also find a different community of 47 users who tweet about small businesses and entrepreneurship, using hashtags such as \#smallbiz, \#marketing and \#enterpreneur.
@@
 
-Another interesting example is a community whose topics tend to focus on Denver and Colorado.
+% Another interesting example is a community whose topics tend to focus on Denver and Colorado.
 These users do not belong to the same community in the interaction-based network, but most of them do belong to the same community in the activity-based network.

### 2014-01-22 paper/parts/results.tex
Addressed Elisa's comments.

@@
 The standard approach to answering this question is to define a metric on the space of possible partitions.
-Because OSLOM detects \emph{coverings} rather than \emph{partitions} of users (that is, it allows for communities to overlap), standard cluster comparison metrics like variation of information~\cite{meilua2003comparing} are not appropriate.
+Because we detect coverings rather than partitions, standard cluster comparison metrics like variation of information~\cite{meilua2003comparing} are not appropriate.
 Instead, we use a generalization of variation of information first introduced in~\cite{lancichinetti2009detecting}, the normalized mutual information.

### 2014-01-23 paper/parts/intro.tex
Made final round of changes.

@@
 
-Because of the importance of structural networks in online social media, a large amount of work in this area has focused on using structural networks.
+Because of the importance of structural networks in online social media, a large amount of work in this area has focused on using structural networks for community detection.
 Here, by `community' we mean the standard definition from the literature on social networks: a collection of nodes (users) within the network who are more highly connected to each other than to nodes (users) outside of the community~\cite{newman2004finding}.
@@
 This is not meant to be an exhaustive list, but rather a list of some of the more common types of communities observed in social networks.
-We propose looking at when and how communities motivated by different questions overlap, and whether different approaches to asking the question, ``What community are you in?'' leads to different insights about a social network.
+We propose looking at when and how communities motivated by these different questions overlap, and whether different approaches to asking the question, ``What community are you in?'' leads to different insights about a social network.
 For example, a user on Twitter might connect mostly with computational social scientists, talk mostly about machine learning, interact solely with close friends (who may or may not be computational social scientists), and utilize the service only on nights and weekends.
@@
 In particular, our current activity-based approach was originally motivated by a methodology used to detect functional communities within populations of neurons~\cite{shalizi2007discovering}.
-Similar information theoretic approaches have been used with social systems to gain insight into local behavior in online social networks~\cite{darmon2013understanding}, to detect communities on Twitter based on undirected information flow~\cite{darmon2013detecting}, and to perform link detection on Twitter via transfer entropy, a directed measure of information flow~\cite{ver2012information}.
-However, transfer entropy has not been used for community detection, and we extend this previous work to incorporate transfer entropy-based communities.
+Similar information theoretic approaches have been used with data arising from online social networks to gain insight into local user behavior~\cite{darmon2013understanding}, to detect communities based on undirected information flow~\cite{darmon2013detecting}, and to perform link detection~\cite{ver2012information}.
 
@@
 
-Finally, the interaction-based approach relies on meta-data and the text of the message to identify who a user converses with on the social media service.
+Finally, the interaction-based approach relies on the meta-data and text of messages to identify who a user converses with on the social media service.
 On Twitter, we can use mentions (indicating a directed communication) and retweets (indicating endorsement of another user) to identify conversation.
@@
 Previous research on communities in social networks focused almost exclusively on different network types in isolation.
-For example, an early paper considered the communities, and associated statistics, inferred from a friendship network in Twitter~\cite{java2009we}.
+For example, an early paper considered the communities, and associated statistics, inferred from a follower network on Twitter~\cite{java2009we}.
 More recent work has considered the dynamics of communities based on structural links in Facebook~\cite{nguyen2011adaptive} and how structural communities impact mentions and retweets on Twitter~\cite{grabowicz2012social}.
 
-Information theoretic, activity-based approaches have been applied previously to the analysis of networks arising in online social media~\cite{ver2012information,darmon2013detecting}, but to the best of our knowledge this is the first use of transfer entropy for community detection.
+Information theoretic, activity-based approaches have been applied previously to the analysis of networks arising in online social media~\cite{ver2012information,darmon2013detecting}, but to the best of our knowledge this is the first use of transfer entropy, an information theoretic measure of directed influence, for community detection.
 
-For interaction-based networks, \cite{conover2011political} considered both mention and retweet networks in isolation for a collection of users chosen for their political orientation.
+For interaction-based communities, \cite{conover2011political} considered both mention and retweet networks in isolation for a collection of users chosen for their political orientation.
 In~\cite{deitrick2013mutually}, the authors construct a dynamic network based on simple time-windowed counts of mentions and retweets, and use the evolution of this network to aid in community detection.
@@
 
-A notable exception to the analysis of isolated types of networks is~\cite{lim2012tweets}, which considered both structure-based and interaction-based communities on Twitter.
+A notable exception to the analysis of isolated types of communities is~\cite{lim2012tweets}, which considered both structure-based and interaction-based communities on Twitter.
 However, this study focused on data collected based on particular topics (country music, tennis, and basketball), and not on a generic subpopulation of Twitter users.

### 2014-03-18 code/compare_communities.py
edits

@@ -13,9 +13,7 @@ for line in lines:
 	for element in elements[:-1]:
 		h = element.split()[0]
 		tfidf = float(element.split()[1])
-		#hashtags_vector[user].append((tfidf,h))
 		hashtags_vector[user].append(h)
-
 
 hashtags_communities_file = open('../oslom_outputs/twitter_network_hashtags_weighted.txt_oslo_files/tp_without_singletons','r')
 hashtag_communities_size = {}; hashtag_communities_bs = {}; hashtag_communities_users = {}
@@ -31,15 +29,64 @@ for i in range(len(lines)):
 		users = lines[i+1].split()
 		hashtag_communities_users[module] = users
 
+retweets_communities_file = open('../oslom_outputs/twitter_network_retweets.txt_oslo_files/tp_without_singletons','r')
+retweets_communities_size = {}; retweets_communities_bs = {}; retweets_communities_users = {}
+lines = retweets_communities_file.readlines()
+for i in range(len(lines)):
+	if i % 2 == 0:
+		line = lines[i].split()
+		module = line[1]
+		size =  int(line[3])
+		bs = float(line[5])
+		retweets_communities_size[module] = size
+		retweets_communities_bs[module] = bs
+		users = lines[i+1].split()
+		retweets_communities_users[module] = users
+
+mentions_communities_file = open('../oslom_outputs/twitter_network_mentions.txt_oslo_files/tp_without_singletons','r')
+mentions_communities_size = {}; mentions_communities_bs = {}; mentions_communities_users = {}
+lines = mentions_communities_file.readlines()
+for i in range(len(lines)):
+	if i % 2 == 0:
+		line = lines[i].split()
+		module = line[1]
+		size =  int(line[3])
+		bs = float(line[5])
+		mentions_communities_size[module] = size
+		mentions_communities_bs[module] = bs
+		users = lines[i+1].split()
+		mentions_communities_users[module] = users
+
+contentfull_communities_file = open('../oslom_outputs/twitter_network_contentfull_weighted_arithmeticmean.txt_oslo_files/tp_without_singletons','r')
+contentfull_communities_size = {}; contentfull_communities_bs = {}; contentfull_communities_users = {}
+lines = contentfull_communities_file.readlines()
+for i in range(len(lines)):
+	if i % 2 == 0:
+		line = lines[i].split()
[…]

### 2014-03-22 paper-generic/parts/results.tex
Added notes from our meeting on Wednesday. Created a 'generic format' version of our paper.

--- 2014-01-22 paper/parts/results.tex
@@
 The normalized mutual information stems from treating clustering as a community identification problem: given that we know a node's community membership(s) in the first covering, how much information do we have about its community membership(s) in the second covering, and vice versa?
-Consider the two coverings $\mathcal{C}_{1}$ and $\mathcal{C}_{2}.$We think of the community memberships of a randomly chosen node in $\mathcal{C}_{1}$ as a binary random vector $\mathbf{X} \in \{0, 1\}^{|\mathcal{C}_{1}|}$ where the $i^{\text{th}}$ entry of the vector is 1 if the node belongs to community $i$ and 0 otherwise.
+Consider the two coverings $\mathcal{C}_{1}$ and $\mathcal{C}_{2}.$ We think of the community memberships of a randomly chosen node in $\mathcal{C}_{1}$ as a binary random vector $\mathbf{X} \in \{0, 1\}^{|\mathcal{C}_{1}|}$ where the $i^{\text{th}}$ entry of the vector is 1 if the node belongs to community $i$ and 0 otherwise.
 Similarly, $\mathbf{Y} \in \{ 0, 1\}^{|\mathcal{C}_{2}|}$ is a binary random vector indicating the community memberships of the node in $\mathcal{C}_{2}$.

### 2014-03-22 paper-icwsm/parts/methods.tex
Added notes from our meeting on Wednesday. Created a 'generic format' version of our paper.

--- 2014-01-22 paper/parts/methods.tex
@@
 As discussed in the introduction, we adopt the standard definition of \emph{community}: a collection of nodes (users) within a network who are more densely connected to each other than with the rest of the network.
-Structural community detection is a well studied problem and several different methods and algorithms have been proposed; for a complete review of this subject we refer the reader to \cite{fortunato2010community}.
+Structural community detection is a well studied problem and several different methods and algorithms have been proposed.
+For a complete review of this subject we refer the reader to \cite{fortunato2010community}.
 In this paper however we focus on a class of networks and communities that is far less studied, in particular we study networks which are both \textit{weighted} and \textit{directed} and communities within those weighted directed networks that can (but need not) \emph{overlap}.
@@
 \end{align}
+A positive value for the transfer entropy of the user $u$ on $f$ indicates that $u$ influences $f$, or that $u$ and $f$ share a common influencer~\cite{ver2012information}.
 
-Operationally, we expect users to interact with Twitter on a human time scale, and thus the natural one-second time resolution is too fine since most humans do not write tweets at the time scale of seconds.
+Operationally, we expect users to interact with Twitter on a human time scale, and thus the natural one-second time resolution is too fine since most humans do not write tweets on the time scale of seconds.
 We coarsen each time series by considering non-overlapping time intervals ten minutes in length.
@@
 We then compute the transfer entropy on these coarsened time series taking $k$ to range from 1 to 6, which corresponds to a lag of ten minutes to an hour.
-The choice of lag must balance a trade-off between additional information and sparsity of samples: as we increase the lag, we account for longer range dependencies, but we also decrease the number of samples availabe to infer a higher dimensional predictive distribution.
+The choice of lag must balance a trade-off between additional information and sparsity of samples: as we increase the lag, we account for longer range dependencies, but we also decrease the number of samples available to infer a higher dimensional predictive distribution.
 Ultimately, due to similarities in the underlying communities we chose a lag-4 transfer entropy.

### 2014-03-22 code/mutual3/compare_coverings.py

@@ -10,7 +10,7 @@ singleton_type = 'singletons'
 
 file_dir = 'coverings/{}/'.format(singleton_type)
 
-num_types = 11
+num_types = 12
 
 mis = numpy.ones((num_types, num_types))*numpy.nan
 

### 2014-03-22 paper-icwsm/code-table_and_figure/median_weights.py

@@ -1,0 +1,19 @@
+import sys
+
+wfile = sys.stdout
+
+with open('../../code/median_weights.txt') as ofile:
+	for ind1 in range(4):
+		for ind2 in range(3):
+
+			line = ofile.readline()
+			label, weight, medians = line.split(', ')
+
+			e_to_i, i_to_e = map(float, medians.split('/'))
+
+			if ind2 == 2:
+				wfile.write('${:0.2}/{:0.2}$\\\\\n'.format(e_to_i, i_to_e))
+			else:
+				wfile.write('${:0.2}/{:0.2}$& '.format(e_to_i, i_to_e))
+
+		# wfile.write('\n')

### 2014-03-30 paper-generic/parts/results.tex
added a few things to the qualitative analysis

@@
   \centering
-\includegraphics[width=0.50\textwidth]{Figures/comm_sizes_ecdf_loglog.pdf}
+\includegraphics[width=0.50\textwidth]{figures/comm_sizes_ecdf_loglog.pdf}
 \caption{The proportion of communities greater than $c$ in size, across the different community types. Note the logarithmic scale on the horizontal and vertical axes.}
@@
 
-% \subsection{Qualitative Analysis of Community Memberships Across Types}
+\subsection{Qualitative Analysis of Community Memberships Across Types}
 
-% As demonstrated by~\cite{good2010performance} in the context of modularity maximization-based community detection, an exponential number of nearby partitions may exist that nearly maximize an objective function used to measure the goodness-of-fit of a graph partition used for community detection.
+As demonstrated by~\cite{good2010performance} in the context of modularity maximization-based community detection, an exponential number of nearby partitions may exist that nearly maximize an objective function used to measure the goodness-of-fit of a graph partition used for community detection.
 Because of this and related issues, it is always wise to perform some sort of qualitative study of the communities returned by any  community detection algorithm to verify their meaningfulness with respect to the scientific question at hand.
@@
 
-% In the topic-based communities, we find a single community consisting of 83 users who tweet about environmental issues and frequently use hashtags such as \#green, \#eco and \#sustainability.
+In the topic-based communities, we find a single community consisting of 83 users who tweet about environmental issues and frequently use hashtags such as \#green, \#eco and \#sustainability.
 We also find a different community of 47 users who tweet about small businesses and entrepreneurship, using hashtags such as \#smallbiz, \#marketing and \#enterpreneur.
@@
 
-% Another interesting example is a community whose topics tend to focus on Denver and Colorado.
+Another interesting example is a community whose topics tend to focus on Denver and Colorado.
 These users do not belong to the same community in the interaction-based network, but most of them do belong to the same community in the activity-based network.
 This indicates that these users react to the same events and issues regarding Colorado and are therefore strongly connected in the topic-based and activity-based networks, but at the same time they do not directly interact with each other and are therefore more loosely connected in the interaction-based networks, where they belong to different communities.
+As expected, among the most influential users (in terms of transfer entropy) we find \@Colorado, which is the state official Twitter account, \@ConnectColorado, a page created to connect Coloradans, and CBS Denver account.
+
+Last but not least, it is interesting noticing that in the top ten most influential users (ranked using the total outgoing strength in the activity-based network) we find two users (Ann Tran and Jessica Northey) that were listed by Forbes in the "Top 10 Social Media Influencers".

### 2014-03-31 paper-generic/parts/results.tex
Adding minutes from last weeks meeting.

@@
   \centering
-\includegraphics[width=0.50\textwidth]{figures/comm_sizes_ecdf_loglog.pdf}
+\includegraphics[width=0.50\textwidth]{Figures/comm_sizes_ecdf_loglog.pdf}
 \caption{The proportion of communities greater than $c$ in size, across the different community types. Note the logarithmic scale on the horizontal and vertical axes.}
@@
 This indicates that these users react to the same events and issues regarding Colorado and are therefore strongly connected in the topic-based and activity-based networks, but at the same time they do not directly interact with each other and are therefore more loosely connected in the interaction-based networks, where they belong to different communities.
-As expected, among the most influential users (in terms of transfer entropy) we find \@Colorado, which is the state official Twitter account, \@ConnectColorado, a page created to connect Coloradans, and CBS Denver account.
-
-Last but not least, it is interesting noticing that in the top ten most influential users (ranked using the total outgoing strength in the activity-based network) we find two users (Ann Tran and Jessica Northey) that were listed by Forbes in the "Top 10 Social Media Influencers".

### 2014-03-31 paper-for_arxiv/parts/methods.tex
Attempted to put paper into a collection that arXiv will support.

--- 2014-03-22 paper-icwsm/parts/methods.tex
@@
 Their method relies on a fitness function that measures the statistical significance of clusters with respect to random fluctuations, and attempts to optimize this fitness function across all clusters.
-For this paper we use OSLOM since it allowed us to detect \emph{overlapping} communities present in our \emph{weighted} and \emph{directed} network.
+For this paper we use OSLOM since it allowed us to detect \emph{overlapping} communities present in our \emph{weighted} and \emph{directed} network, and its authors showed that it performs very well on various types of artificial benchmark graphs and also on several real networks.
 

### 2014-03-31 paper-for_arxiv/conclusions.tex
moving around and files

--- 2014-01-22 paper/parts/conclusions.tex
@@
-\section{Conclusion and Future Works}
+\section{Conclusion and Future Work}
 
@@
 More importantly, we have shown that these different views of the network are not revealed by using the structural network or any one weighting scheme alone.
-By varying the questions we asked about the network and then deriving weighting schema to answer that particular question, we found that community structure differed across community types on both the macro (e.g.
+By varying the questions we asked about the network and then deriving weighting schema to answer each question, we found that community structure differed across community types on both the macro (e.g.
 number of communities and their size distribution) and micro (e.g.
@@
 hashtags) tended to be most highly concentrated within communities.
-We found this to be the case even when the communities were defined by a different criteria from the edge weights.
+We found this to be the case even when the communities were defined by a different criterion from the edge weights under study.
 
@@
 This result echos the `strength of weak ties' theory from~\cite{granovetter1973strength}, which has found empirical support in~\cite{grabowicz2012social} for online social networks.
-This means that our novel use of transfer entropy not only defines boundaries that are meaningful divisions between communities but also illustrates that users who have a strong influence on a community need not be a member of that community.
+This means that our use of transfer entropy not only defines boundaries that are meaningful divisions between communities but also illustrates that users who have a strong influence on a community need not be a member of that community.
 

### 2014-03-31 paper-for_arxiv/results.tex
moving around and files

--- 2014-03-30 paper-generic/parts/results.tex
@@
   \centering
-\includegraphics[width=0.50\textwidth]{figures/comm_sizes_ecdf_loglog.pdf}
+\includegraphics[width=0.50\textwidth]{comm_sizes_ecdf_loglog.pdf}
 \caption{The proportion of communities greater than $c$ in size, across the different community types. Note the logarithmic scale on the horizontal and vertical axes.}
@@
   \centering
-\includegraphics[width=0.50\textwidth]{figures/nmi_singletons.pdf}
+\includegraphics[width=0.50\textwidth]{nmi_singletons.pdf}
 \caption{The normalized mutual information between the coverings inferred from the different community types.
@@
   \centering
-\includegraphics[width=0.50\textwidth]{figures/edge-types.eps}
+\includegraphics[width=0.50\textwidth]{edge-types.eps}
 \caption{An example of the edges considered in determining the edge weight distribution for a given community (the focal community is in yellow).
@@
   \centering
-\includegraphics[width=0.50\textwidth]{figures/comm0_labels-mention-retweet_weights-hashtag-ecdf.pdf}
+\includegraphics[width=0.50\textwidth]{comm0_labels-mention-retweet_weights-hashtag-ecdf.pdf}
 \caption{The proportion of edges with a weight at least as large as the weight on the horizontal axis, across the types of edges described in Figure~\ref{Fig-edge_types}.

### 2014-04-01 code/TE_centrality.py
Added script to compute transfer entropy-based centrality measures.

@@ -1,0 +1,86 @@
+from itertools import islice
+import numpy
+
+with open('../data/content-free/directedweightsTE/edge_weights_bin10minutes_lag_4_withMMBIAS.dat') as ofile:
+	# The header for this file is 
+	# 
+	# followed_by, follower, transfer_entropy,transfer_entropy_corrected(MM)
+
+	incoming_dict = {}
+	outgoing_dict = {}
+
+	for line in islice(ofile, 1, None):
+		fromid, toid, TE_B, TE = map(str.strip, line.split(','))
+
+		TE = float(TE)
+
+		if numpy.isnan(TE):
+			print 'Warning: Transforming a nan into 0.'
+
+			TE = 0.
+		elif TE < 0.:
+			TE = 0.
+
+		if fromid in outgoing_dict:
+			outgoing_dict[fromid].append(TE)
+		else:
+			outgoing_dict[fromid] = [TE]
+
+		if toid in incoming_dict:
+			incoming_dict[toid].append(TE)
+		else:
+			incoming_dict[toid] = [TE]
+
+incoming_centrality = []; outgoing_centrality = []
+
+userids = incoming_dict.keys()
+
+for userid in userids:
+	incoming_centrality.append(numpy.mean(incoming_dict[userid]))
+
+	outgoing_centrality.append(numpy.mean(outgoing_dict[userid]))
+
+print 'The min and max incoming centralities are: {} / {}'.format(numpy.min(incoming_centrality), numpy.max(incoming_centrality))
+print 'The min and max outgoing centralities are: {} / {}'.format(numpy.min(outgoing_centrality), numpy.max(outgoing_centrality))
+
+import pylab
+
+pylab.plot(incoming_centrality, outgoing_centrality, '.')
+pylab.xlabel('Influencability'); pylab.ylabel('Influence')
+pylab.plot([0, numpy.max(incoming_centrality)], [0, numpy.max(outgoing_centrality)], 'r-')
+pylab.show()
+
+order_incoming_centrality = numpy.argsort(incoming_centrality)[::-1]
+order_outgoing_centrality = numpy.argsort(outgoing_centrality)[::-1]
+
+K = 10
+
+print 'The top {} influential users are:'.format(K)
+
+for ind in range(K):
[…]

### 2014-04-01 paper-for_arxiv/paper.tex
Attempted to put paper into a collection that arXiv will support.
moving stuff around and fixing links
reaady for arxiv

--- 2014-01-17 paper/paper.tex
@@
 \documentclass[letterpaper]{article}
-\usepackage{aaai}
 \usepackage{times}
@@
 \usepackage{multirow}
+\usepackage{authblk}
 \frenchspacing
@@
 % Uncomment if you want to use section numbers % and change the 0 to a 1 or 2
-\setcounter{secnumdepth}{2}
+\setcounter{secnumdepth}{0}
 
@@
 \title{
-%Followers are not enough: Beyond structure in the detection of communities \\
-Followers Are Not Enough: Beyond Structural Communities in Online Social Networks%\\
-%Followers are not enough: Activity, Interaction, and Topic-based Communities in Online Social Networks \\
-%Followers are not enough: exploring communities beyond structure
+Followers Are Not Enough: Beyond Structural Communities in Online Social Networks
  }
@@
 
+ \author[1]{David Darmon}
+ \author[2]{Elisa Omodei}
+ \author[3]{Joshua Garland}
+ \affil[1]{University of Maryland\\
+ Dept. of Mathematics}
+ \affil[2]{
+ LaTTiCe (CNRS, ENS, Paris 3)\\
+ ISC-PIF}
+ \affil[3]{
+ University of Colorado at Boulder\\
+ Dept. of Computer Science
+ }
+
 \maketitle
@@
 
-\input{parts/intro.tex}
-\input{parts/methods.tex}
-\input{parts/results.tex}
-\input{parts/discussion.tex}
-\input{parts/conclusions.tex}
+\newpage
 
-\bibliography{references}
-\bibliographystyle{aaai}
+\section{Introduction}
+
+Networks play a central role in online social media services like Twitter, Facebook, and Google+.
+These services allow a user to interact with others based on the online social network they curate through a process known as contact filtering~\cite{cazabet2012automated}.
+For example, `friends' on Facebook represent reciprocal links for sharing information, while `followers' on Twitter allow a single user to broadcast information in a one-to-many fashion.
+Central to all of these interactions is the fact that the \emph{structure} of the social network influences how information can be broadcast or diffuse through the service.
+
+Because of the importance of structural networks in online social media, a large amount of work in this area has focused on using structural networks for community detection.
+Here, by `community' we mean the standard definition from the literature on social networks: a collection of nodes (users) within the network who are more highly connected to each other than to nodes (users) outside of the community~\cite{newman2004finding}.
+For instance, in~\cite{java2009we}, the authors use a follower network to determine communities within Twitter, and note that conversations tend to occur within these communities.
+The approach of focusing on structural networks makes sense for `real-world' sociological experiments, where obtaining additional information about user interactions may be expensive and time-consuming.
+However, with the prevalence of large, rich data sets for online social networks, additional information beyond the structure alone may be incorporated, and these augmented networks more realistically reflects how users interact with each other on social media services~\cite{grabowicz2012social}.
+
+A large body of work exists on methods for automatic detection of communities within networks~\cite{newman2004fast,newman2004finding,rosvall2008maps,blondel2008fast,LancichinettiPlos}.
+See~\cite{fortunato2010community} for a recent review.
+All these methods \emph{begin} with a given network, and then attempt to uncover structure present in the network, i.e., they are agnostic to how the network was constructed.
+As opposed to this agnostic analysis, we propose and illustrate the importance of a question-focused approach.
+We believe that in order to understand the communities present in a data set, it is important to begin with a clear picture of the community type under consideration, and then perform the network collection and community detection with that community type in mind.
+
+This is especially true for social network analysis.
+In online social networks, a `community' could refer to several possible structures.
+The simplest definition of community, as we have seen, might stem from the network of explicit connections between users on a service (friends, followers, etc.).
+On small time scales, these connections are more or less static, and we might instead determine communities based on who is talking to whom, providing a more dynamic picture.
+On a more abstract level, a user might consider themselves part of a community of people discussing similar topics.
+We might also define communities as collections of people who exhibit similar behaviors on a service, as in communities of teenagers vs.\ elderly users.
+We can characterize these types of communities based on the types of questions we might ask about them:
+\begin{itemize}
+	\item \textbf{Structure-based:} Who have you stated you are friends with? Who do you follow?
+	\item \textbf{Activity-based:} Who do you act like?
+	\item \textbf{Topic-based:} What do you talk about?
+	\item \textbf{Interaction-based:} Who do you communicate with?
+\end{itemize}
+
+This is not meant to be an exhaustive list, but rather a list of some of the more common types of communities observed in social networks.
+We propose looking at when and how communities motivated by these different questions overlap, and whether different approaches to asking the question, ``What community are you in?'' leads to different insights about a social network.
+For example, a user on Twitter might connect mostly with computational social scientists, talk mostly about machine learning, interact solely with close friends (who may or may not be computational social scientists), and utilize the service only on nights and weekends.
+Each of these different `profiles' of the user highlight different views of the user's social network, and represent different types of communities.
+We divide our approaches into four categories based on the questions outlined above: structure-based, activity-based, topic-based, and interaction-based.
+The structure-based approach, as outlined above, is most common, and for our data relies on reported follower relationships.
+
+The activity-based approach is motivated by the question of which individuals act in a homogeneous manner, e.g., which users use a service in a similar way.
+The main tools for answering this question stem from information theory.
+We consider each user on an online social network as an information processing unit, but ignore the content of their messages.
+In particular, our current activity-based approach was originally motivated by a methodology used to detect functional communities within populations of neurons~\cite{shalizi2007discovering}.
+Similar information theoretic approaches have been used with data arising from online social networks to gain insight into local user behavior~\cite{darmon2013understanding}, to detect communities based on undirected information flow~\cite{darmon2013detecting}, and to perform link detection~\cite{ver2012information}.
+
+Our topic-based and interaction-based approaches, in contrast to the activity-based approach, rely on the \emph{content} of a user's interactions and ignore their temporal components.
+The content contains a great deal of information about the communication between users.
+For example, a popular approach to analyzing social media data is to use Latent Dirichlet Allocation (LDA) to infer topics based on the prevalence of words within a status~\cite{zhao2011comparing,michelson2010discovering}.
+The LDA model can then be used to infer distributions over latent topics, and the similarity of two users with respect to topics may be defined in terms of the distance between their associated topic distributions.
+Because our focus is not on topic identification, we apply a simpler approach using hashtags as a proxy for topics~\cite{becker2011beyond,tsur2012s}.
+We can then define the similarity of two users in terms of their hashtags, and use this similarity to build a topic-based network.
+
+Finally, the interaction-based approach relies on the meta-data and text of messages to identify who a user converses with on the social media service.
+On Twitter, we can use mentions (indicating a directed communication) and retweets (indicating endorsement of another user) to identify conversation.
+Moreover, we can define a directed influence between two users by considering the attention paid to that user compared to all other users.
+This allows us to generate a network based on conversations and user interactions.
+
+The activity-based, topic-based, and interaction-based networks allow us to build a more complete picture of the \emph{latent} social network present in online social media, as opposed to the \emph{explicit} social network indicated by structural links.
+In this paper, we explore the relation between these various possible networks and their corresponding communities.
+We begin by describing the methodologies used to generate the various types of networks, and infer their community structure.
+We then explore how the communities of users differ depending on the type of network used.
+Finally, we explore how communication patterns differ across and within the different community types.
+
+\section{Related Work}
+
+Previous research on communities in social networks focused almost exclusively on different network types in isolation.
+For example, an early paper considered the communities, and associated statistics, inferred from a follower network on Twitter~\cite{java2009we}.
+More recent work has considered the dynamics of communities based on structural links in Facebook~\cite{nguyen2011adaptive} and how structural communities impact mentions and retweets on Twitter~\cite{grabowicz2012social}.
+
+Information theoretic, activity-based approaches have been applied previously to the analysis of networks arising in online social media~\cite{ver2012information,darmon2013detecting}, but to the best of our knowledge this is the first use of transfer entropy, an information theoretic measure of directed influence, for community detection.
+
+For interaction-based communities, \cite{conover2011political} considered both mention and retweet networks in isolation for a collection of users chosen for their political orientation.
+In~\cite{deitrick2013mutually}, the authors construct a dynamic network based on simple time-windowed counts of mentions and retweets, and use the evolution of this network to aid in community detection.
+
+There are two broad approaches to topic-based communities in the literature.
+\cite{rossi2012conversation} used a set of users collected based on their use of a single hashtag, and tracked the formation of follower and friendship links within that set of users.
+In~\cite{lim2012following}, the authors chose a set of topics to explore, and then seeded a network from a celebrity chosen to exemplify a particular topic.
+Both approaches thus begin with a particular topic in mind, and perform the data collection accordingly.
+Other approaches use probabilistic models for the topics and treat community membership as a latent variable~\cite{yin2012latent}.
+
+% Structural:
+% ==========
+
+% \cite{java2009we} Determine friendship network on Twitter to define communities.
+
+% \cite{nguyen2011adaptive} Uses a dynamic community detection algorithm (that uses snapshots of the network), but still focuses on \emph{structural} ties (Facebook friendship relationships)
+
+% Interaction-based:
+% ==================
+
+% \cite{deitrick2013mutually} use 'dynamic' mention-retweet network to detect communities, but just augment the count of mentions retweets in the weighting (instead of using a proportion), and don't combine mentions and retweets.
+
+% \cite{conover2011political} Retweet-mention analysis for political polarization analysis
+% http://truthy.indiana.edu/site_media/pdfs/conover_icwsm2011_polarization.pdf
+
+% Activity-based:
+% ===============
+
+% None, to the best of our knowledge.
+
+% Topic-based:
+% ============
+
+% \cite{lim2012following} "We propose an efficient approach for detecting communities that share common interests on Twitter, based on linkages among followers of celebrities representing an interest category." Use both InfoMAP and clique percolation.
+
+% \cite{rossi2012conversation} Collect users who use the same hashtag (a *single* hashtag, #XF5, for XFactor 5), and then note if this impacts the friend/follower network.
+
+% \cite{xu2011sentiment} Generate 'sentiment' networks.
+
+% Most-relevant:
+% ==============
+
+% \cite{lim2012tweets} This one is *very* important: they also note that structural links do not indicate communication.
+They use an interaction-based approach (mentions only).
+But they do not use a weighted version of the structural network.
+Instead, they use .
+And they do not go into much depth comparing how the two types of communities (structural and activity-based) differ.
+Moreover, they explicitly seed their network to focus around a particular topic (country music, tennis, basketball, etc.)
+
+A notable exception to the analysis of isolated types of communities is~\cite{lim2012tweets}, which considered both structure-based and interaction-based communities on Twitter.
+However, this study focused on data collected based on particular topics (country music, tennis, and basketball), and not on a generic subpopulation of Twitter users.
+Moreover, it did not explore the differences in community structure resulting from the different network weightings, and focuses on aggregate statistics (community size, network statistics, etc.).
+Another notable exception is~\cite{kao2013talison}, where the authors used a tensor representation of user data to incorporate retweet and hashtag information into a study of the social media coverage of the Occupy Movement.
+The tensor can then be decomposed into factors in a generalization of the singular value decomposition of a matrix, and these factors can be used to determine `salient' users.
+However, this approach focused on data for a particular topic (the Occupy Movement) and did not collect users based on a structural network.
+\input{methods.tex}
+\input{results.tex}
+\input{conclusions.tex}
+
+ %\bibliography{paper.bbl}
+% \bibliographystyle{plain}
+
+\input{paper.bbl}
 

### 2014-04-22 paper-for_arxiv/intro.tex
expanded the community detection part in the methodology section

--- 2014-04-01 paper-for_arxiv/paper.tex
@@
-%File: formatting-instruction.tex
-\documentclass[letterpaper]{article}
-\usepackage{times}
-\usepackage{helvet}
-\usepackage{courier}
-\usepackage{amssymb, amsmath, amsthm}
-\usepackage{graphicx}
-\usepackage{multirow}
-\usepackage{authblk}
-\frenchspacing
-\setlength{\pdfpagewidth}{8.5in}
-\setlength{\pdfpageheight}{11in}
-\pdfinfo{
-/Title (Followers Are Not Enough: Beyond Structural Communities in Online Social Networks)
-/Author (David Darmon, Elisa Omodei, Joshua Garland)
-/Keywords (community detection, functional communities, social network analysis)}
-
-%%%%%%%%%%
-% Section Numbers
-% Uncomment if you want to use section numbers % and change the 0 to a 1 or 2
-\setcounter{secnumdepth}{0}
-
-%%%%%%%%%%
-% Body of Paper Begins
-\begin{document}
-
-% Title, Author, and Address Information
-\title{
-Followers Are Not Enough: Beyond Structural Communities in Online Social Networks
- }
-
- % \author{David Darmon  \\
- % University of Maryland\\
- % Dept. of Mathematics \\
- % ddarmon@math.umd.edu \\
- % \And Elisa Omodei \\
- % LaTTiCe (CNRS, ENS, Paris 3)\\
- % ISC-PIF\\
- % elisa.omodei@ens.fr \\
- % \And 
- % Joshua Garland\\
- % University of Colorado at Boulder\\
- % Dept. of Computer Science \\
- % joshua.garland@colorado.edu}
-
- \author[1]{David Darmon}
- \author[2]{Elisa Omodei}
- \author[3]{Joshua Garland}
- \affil[1]{University of Maryland\\
- Dept. of Mathematics}
- \affil[2]{
- LaTTiCe (CNRS, ENS, Paris 3)\\
- ISC-PIF}
- \affil[3]{
- University of Colorado at Boulder\\
- Dept. of Computer Science
- }
-
-\maketitle
-
-\begin{abstract}
-\begin{quote}
-Community detection in online social networks is typically based on the analysis of the explicit connections between users, such as ``friends" on Facebook and ``followers" on Twitter.
-But online users often have hundreds or even thousands of such connections, and many of these connections do not correspond to real friendships or more generally to accounts that users interact with.
-We claim that community detection in online social networks should be question-oriented and rely on additional information beyond the simple structure of the network.
-The concept of `community' is very general, and different questions such as ``who do we interact with?" and ``with whom do we share similar interests?" can lead to the discovery of different social groups.
-In this paper we focus on three types of communities beyond structural communities: activity-based, topic-based, and interaction-based.
-We analyze a Twitter dataset using three different weightings of the structural network meant to highlight these three community types, and then infer the communities associated with these weightings.
-We show that the communities obtained in the three weighted cases are highly different from each other, and from the communities obtained by considering only the unweighted structural network.
-Our results confirm that asking a precise question is an unavoidable first step in community detection in online social networks, and that different questions can lead to different insights into the network under study.
-\end{quote}
-\end{abstract}
-
-\newpage
-
 \section{Introduction}
@@
 
-A large body of work exists on methods for automatic detection of communities within networks~\cite{newman2004fast,newman2004finding,rosvall2008maps,blondel2008fast,LancichinettiPlos}.
+%A large body of work exists on methods for automatic detection of communities within networks~\cite{newman2004fast,newman2004finding,rosvall2008maps,blondel2008fast,LancichinettiPlos}.
 See~\cite{fortunato2010community} for a recent review.
+\textcolor{red}{A large body of work exists on methods for automatic detection of communities within networks, among which we recall Girvann and Newman algorithm [32, 33], Infomap [39], Leuven [3], and the recently introduced OSLOM [24].}
 All these methods \emph{begin} with a given network, and then attempt to uncover structure present in the network, i.e., they are agnostic to how the network was constructed.
@@
 Finally, the interaction-based approach relies on the meta-data and text of messages to identify who a user converses with on the social media service.
-On Twitter, we can use mentions (indicating a directed communication) and retweets (indicating endorsement of another user) to identify conversation.
+On Twitter, we can use mentions (indicating a directed communication) and \textcolor{blue}{retweets (indicating endorsement of another user)} to identify conversation.
 Moreover, we can define a directed influence between two users by considering the attention paid to that user compared to all other users.
@@
 However, this approach focused on data for a particular topic (the Occupy Movement) and did not collect users based on a structural network.
-\input{methods.tex}
-\input{results.tex}
-\input{conclusions.tex}
-
- %\bibliography{paper.bbl}
-% \bibliographystyle{plain}
-
-\input{paper.bbl}
-
-\end{document}

### 2014-04-22 paper-for_arxiv/methods.tex
expanded the community detection part in the methodology section

--- 2014-03-22 paper-icwsm/parts/methods.tex
@@
 Their method relies on a fitness function that measures the statistical significance of clusters with respect to random fluctuations, and attempts to optimize this fitness function across all clusters.
-For this paper we use OSLOM since it allowed us to detect \emph{overlapping} communities present in our \emph{weighted} and \emph{directed} network.
+\textcolor{red}{Following~\cite{Lancichinetti2010}, the significance measure is defined as the probability of finding the cluster in a network without community structure.
+The null model used is basically the same as the one adopted by Newman and Girvan to define modularity, i.e.
+it is a model that generates random graphs with a given degree distribution.
+The authors tested their algorithm on different benchmarks (LFR and Girvan-Newman) and real networks (such as the US air transportation and the word association network), and compared its performance against the best algorithms
+currently available (i.e the ones mentioned in the introduction), and found excelent results.
+Moreover, they showed that OSLOM is also able to recognize the absence, and not simply the presence, of community structure, by testing it on random graphs.
+This feature of the algorithm plays an important role in the analysis of real data networks, since it is not always the case that a community structure is indeed present and it is therefore useful to be able to detect its absence too.
+Therefore, given its versatily and its performance, in this paper we used OSLOM to detect \emph{overlapping} communities present in our \emph{weighted} and \emph{directed} network.}
+%For this paper we use OSLOM since it allowed us to detect \emph{overlapping} communities present in our \emph{weighted} and \emph{directed} network, and its authors showed that it performs very well on various types of artificial benchmark graphs and also on several real networks.
 

### 2014-04-22 paper-for_arxiv/paper.tex
expanded the community detection part in the methodology section

@@
 \usepackage{authblk}
+\usepackage{color}
 \frenchspacing

### 2014-04-22 paper-for_arxiv/results.tex
expanded the community detection part in the methodology section

--- 2014-03-31 paper-generic/parts/results.tex
@@
   \centering
-\includegraphics[width=0.50\textwidth]{Figures/comm_sizes_ecdf_loglog.pdf}
+\includegraphics[width=0.50\textwidth]{comm_sizes_ecdf_loglog.pdf}
 \caption{The proportion of communities greater than $c$ in size, across the different community types. Note the logarithmic scale on the horizontal and vertical axes.}
@@
   \centering
-\includegraphics[width=0.50\textwidth]{figures/comm0_labels-mention-retweet_weights-hashtag-ecdf.pdf}
+\includegraphics[width=0.50\textwidth]{comm0_labels-hashtag_weights-mention-retweet-ecdf.pdf}
 \caption{The proportion of edges with a weight at least as large as the weight on the horizontal axis, across the types of edges described in Figure~\ref{Fig-edge_types}.
@@
 This indicates that these users react to the same events and issues regarding Colorado and are therefore strongly connected in the topic-based and activity-based networks, but at the same time they do not directly interact with each other and are therefore more loosely connected in the interaction-based networks, where they belong to different communities.
+\textcolor{red}{As expected, among the most influential users (in terms of transfer entropy) we find \@Colorado, which is the state official Twitter account, \@ConnectColorado, a page created to connect Coloradans, and CBS Denver account.}
+
+\textcolor{red}{Last but not least, it is interesting noticing that in the top ten most influential users (ranked using the total outgoing strength in the activity-based network) we find two users (Ann Tran and Jessica Northey) that were listed by Forbes in the "Top 10 Social Media Influencers".}

### 2014-04-22 code/TE_centrality.py
Minor changes.

@@ -53,7 +53,7 @@ pylab.show()
 order_incoming_centrality = numpy.argsort(incoming_centrality)[::-1]
 order_outgoing_centrality = numpy.argsort(outgoing_centrality)[::-1]
 
-K = 10
+K = 100
 
 print 'The top {} influential users are:'.format(K)
 

### 2014-04-22 paper-for_arxiv/intro.tex
Minor edits to Elisa's additions / revisions.

@@
 See~\cite{fortunato2010community} for a recent review.
-\textcolor{red}{A large body of work exists on methods for automatic detection of communities within networks, among which we recall Girvann and Newman algorithm [32, 33], Infomap [39], Leuven [3], and the recently introduced OSLOM [24].}
+\textcolor{red}{A large body of work exists on methods for automatic detection of communities within networks, among which we recall the Girvan and Newman algorithm~\cite{newman2004finding}, Infomap~\cite{rosvall2008maps}, Louvain\cite{~blondel2008fast}, and the recently introduced OSLOM\cite{LancichinettiPlos}.}
 All these methods \emph{begin} with a given network, and then attempt to uncover structure present in the network, i.e., they are agnostic to how the network was constructed.

### 2014-04-22 paper-for_arxiv/methods.tex
Minor edits to Elisa's additions / revisions.

@@
 The authors tested their algorithm on different benchmarks (LFR and Girvan-Newman) and real networks (such as the US air transportation and the word association network), and compared its performance against the best algorithms
-currently available (i.e the ones mentioned in the introduction), and found excelent results.
+currently available (i.e the ones mentioned in the introduction), and found excellent results.
 Moreover, they showed that OSLOM is also able to recognize the absence, and not simply the presence, of community structure, by testing it on random graphs.
 This feature of the algorithm plays an important role in the analysis of real data networks, since it is not always the case that a community structure is indeed present and it is therefore useful to be able to detect its absence too.
-Therefore, given its versatily and its performance, in this paper we used OSLOM to detect \emph{overlapping} communities present in our \emph{weighted} and \emph{directed} network.}
+Therefore, given its versatility and performance with benchmark network, in this paper we used OSLOM to detect \emph{overlapping} communities present in our \emph{weighted} and \emph{directed} network.}
 %For this paper we use OSLOM since it allowed us to detect \emph{overlapping} communities present in our \emph{weighted} and \emph{directed} network, and its authors showed that it performs very well on various types of artificial benchmark graphs and also on several real networks.

### 2014-04-22 paper-for_arxiv/results.tex
Minor edits to Elisa's additions / revisions.

@@
 
-\textcolor{red}{Last but not least, it is interesting noticing that in the top ten most influential users (ranked using the total outgoing strength in the activity-based network) we find two users (Ann Tran and Jessica Northey) that were listed by Forbes in the "Top 10 Social Media Influencers".}
+\textcolor{red}{Lastly, it is interesting to note that in the top ten most influential users (ranked using the total outgoing strength in the activity-based network) we find two users (Ann Tran and Jessica Northey) that were listed by Forbes in the "Top 10 Social Media Influencers".}

### 2014-04-22 code/weight_distribution_by_community_type.R
Added script for edge type analysis.
I have a new idea for the edge-type analysis. Much simpler and easier
to interpret. The script is in:

weight_distribution_by_community_type.R

@@ -1,0 +1,113 @@
+# A script that computes the distribution of 
+# i-to-i, e-to-i, and i-to-e weights *across
+# communities*. Compare this to 
+#
+# 	analyze_weights_by_community_types.R
+# 
+# which does this individually for *each*
+# community.
+#
+# DMD, 22 April 2014
+
+# Search type to use:
+# 	labels-BLANK_weights-BLANK
+#
+# Ex: labels-struc_weights-TE4
+
+# label_type = 'struc'
+# label_type = 'TE4'
+# label_type = 'hashtag'
+# label_type = 'mention-retweet'
+
+# weight_type = 'TE4'
+# weight_type = 'hashtag'
+# weight_type = 'mention-retweet'
+
+label_types = c('struc', 'TE4', 'hashtag', 'mention-retweet')
+weight_types = c('TE4', 'hashtag', 'mention-retweet')
+
+# label_types = c('struc')
+# label_types = c('TE4')
+# label_types = c('hashtag')
+# label_types = c('mention-retweet')
+
+# weight_types = c('TE4')
+# weight_types = c('hashtag')
+# weight_types = c('mention-retweet')
+
+comms = c(0:19)
+
+for (label_type in label_types){
+for (weight_type in weight_types){
+
+data_e.to.i_aggregate = c()
+data_i.to.e_aggregate = c()
+data_i.to.i_aggregate = c()
+
+for (comm_label in comms){
+# for (comm_label in c(0)){
+	prefix = paste0('comm', comm_label, '_labels-', label_type, '_weights-', weight_type)
+
+	data_i.to.i = read.csv(paste0('../data/edges-by-type/', prefix, '_i-to-i.dat'), header = FALSE)$V1
+	data_e.to.i = read.csv(paste0('../data/edges-by-type/', prefix, '_e-to-i.dat'), header = FALSE)$V1
+	data_i.to.e = read.csv(paste0('../data/edges-by-type/', prefix, '_i-to-e.dat'), header = FALSE)$V1
+
+	# Deal with NAs
+
+	data_i.to.i[is.na(data_i.to.i)] = 0
+	data_e.to.i[is.na(data_e.to.i)] = 0
+	data_i.to.e[is.na(data_i.to.e)] = 0
+
[…]

### 2014-04-22 paper-for_arxiv/results.tex
Reworking edges-across-communities section.

@@
 
-This change in the tail of the distribution between edge types was typical of many of the community type / weight pairings.
+% \begin{figure}
+%         \centering
+%         \begin{subfigure}[b]{0.2\textwidth}
+%                 \includegraphics[width=\textwidth]{labels-struc_weights-TE4-ecdf_by_type.pdf}
+%         \end{subfigure}
+%         \begin{subfigure}[b]{0.2\textwidth}
+%                 \includegraphics[width=\textwidth]{labels-struc_weights-hashtag-ecdf_by_type.pdf}
+%         \end{subfigure}
+%         \begin{subfigure}[b]{0.2\textwidth}
+%                 \includegraphics[width=\textwidth]{labels-struc_weights-mention-retweet-ecdf_by_type.pdf}
+%         \end{subfigure}
+%         \caption{Lorem ipsum.}
+% \end{figure}
+
+% This change in the tail of the distribution between edge types was typical of many of the community type / weight pairings.
 A useful summary statistic to quantify the change involves the median weights across the three types of edges, as demonstrated in Figure~\ref{Fig-dist_across_community}.
@@
 
-\begin{table}
-	\caption{The median value across the 100 largest communities for the ratio of the median internal-to-internal weight to the median external-to-internal / internal-to-external weight for the different community / weight pairings.
+% \begin{table}
+% 	\caption{The median value across the 100 largest communities for the ratio of the median internal-to-internal weight to the median external-to-internal / internal-to-external weight for the different community / weight pairings.
 For each entry $a/b$ in the table, $a$ corresponds to median ratio value for edges external-to-internal, and $b$ corresponds to the median ratio value for edges internal-to-external .
@@
 We indicate such cases with an asterisk.}
-	\centering
-	\begin{tabular}{c  c | c  c  c}
-		& & \multicolumn{3}{ c }{Weight Type} \\ %\cline{3-5}
-		& & TE & MR & HT \\ \cline{1-5}
-		\multirow{4}{*}{Community} & S & $0.96/0.94$& $1.7/2.1$*& $9.0/8.0$\\
-		\multirow{4}{*}{Type} & A & $1.0/0.96$& $1.5/2.4$*& $24/17$\\
-		& I & $0.83/0.86$& $3.2/4.4$& $10/8.5$\\
-		& T & $0.9/0.89$& $2.4/2.6$*& $28/26$
-	\end{tabular}
-	\label{Table-medians}
-\end{table}
+% 	\centering
+% 	\begin{tabular}{c  c | c  c  c}
+% 		& & \multicolumn{3}{ c }{Weight Type} \\ %\cline{3-5}
+% 		& & TE & MR & HT \\ \cline{1-5}
+% 		\multirow{4}{*}{Community} & S & $0.96/0.94$& $1.7/2.1$*& $9.0/8.0$\\
+% 		\multirow{4}{*}{Type} & A & $1.0/0.96$& $1.5/2.4$*& $24/17$\\
+% 		& I & $0.83/0.86$& $3.2/4.4$& $10/8.5$\\
+% 		& T & $0.9/0.89$& $2.4/2.6$*& $28/26$
+% 	\end{tabular}
+% 	\label{Table-medians}
+% \end{table}
 
-We see that for every weight type except transfer entropy, the weight on edges internal to the communities tend to be higher than on edges entering or exiting the communities, ranging from a factor of 1.5 times larger for the activity-based/mention-retweet pairing to a factor of 28 times larger for the topic-based/hashtag similarity pairing.
+% We see that for every weight type except transfer entropy, the weight on edges internal to the communities tend to be higher than on edges entering or exiting the communities, ranging from a factor of 1.5 times larger for the activity-based/mention-retweet pairing to a factor of 28 times larger for the topic-based/hashtag similarity pairing.
 As stated above, we expect this ratio to be high for community / weight pairings that match (e.g.

### 2014-04-22 code/weight_distribution_by_community_type.R

@@ -35,7 +35,7 @@ weight_types = c('TE4', 'hashtag', 'mention-retweet')
 # weight_types = c('hashtag')
 # weight_types = c('mention-retweet')
 
-comms = c(0:19)
+comms = c(0:9)
 
 for (label_type in label_types){
 for (weight_type in weight_types){

### 2014-04-29 abstract-eccs14/eccs14_abstract.tex
added folder with abstract for eccs14

\documentclass[10pt,a4paper]{article}
\usepackage[latin1]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[top=0.15in, bottom=0.35in, left=0.35in, right=0.35in]{geometry}
\pagenumbering{gobble}

\title{Going Beyond Structural Communities in Online Social Networks}
\author{David Darmon, Elisa Omodei, Joshua Garland}
\date{}

\begin{document}

\maketitle

Community detection in online social networks is typically based on the analysis of the explicit connections between users, such as ``friends" on Facebook and ``followers" on Twitter. But online users often have hundreds or even thousands of such connections, and many of these connections do not correspond to real friendships or more generally to accounts that users interact with. We claim that community detection in online social networks should be question-oriented and rely on additional information beyond the simple structure of the network. The concept of `community' is very general, and different questions such as ``who do we interact with?" and ``with whom do we share similar interests?" can lead to the discovery of different social groups. We propose looking at when and how communities motivated by these different questions overlap, and whether different approaches to asking the question, ``What community are you in?'' leads to different insights about a social network. For example, a user on Twitter might connect mostly with computational social scientists, talk mostly about machine learning, interact solely with close friends (who may or may not be computational social scientists), and utilize the service only on nights and weekends. Each of these different `profiles' of the user highlight different views of the user's social network, and represent different types of communities. We divide our approaches into four categories based on the questions outlined above: structure-based, activity-based, topic-based, and interaction-based. The structure-based approach, is most common, and for our data relies on reported follower relationships. To detect the other kinds of communities we weight the structural edges with different scores that aim to measure the different kinds of interactions. For the activity-based communities, we consider only the timing of each user's tweets and ignore any additional content. From this starting point, we can view the behavior of a user $u$ on Twitter as a point process, where at any instant $t$ the user has either emitted a tweet ($X_{t}(u) = 1$) or remained silent ($X_{t}(u) = 0$). Thus, we reduce all of the information generated by a user on Twitter to a time series $\{ X_{t}(u)\}$. We can then compute the flow of information between two users $u$ and $v$ by computing the transfer entropy between their time series $X_{t}(u)$ and $X_{t}(v).$ For the interaction-based communities, we weight the user-follower network with a measure proportional to the number of mentions and/or retweets between users. Lastly, in order to detect the topical communities, we weight the edges of the user-follower network through a measure based on the number of common hashtags between pairs of users. Hashtags are a good proxy for a tweet's content as hashtags are explicitly meant to be keywords indicating the topic of the tweet. We then used the OSLOM algorithm~\cite{LancichinettiPlos} to detect overlapping communities present in the four weighted, directed networks. We then compared with several different methods the communities obtained in the different weightings, in particular we considered the normalized mutual information. We see that similarity between the coverings is dictated by the generic community type (structural, activity-based, etc.). That is, the transfer entropy coverings are more similar to each other than to any of the other coverings, with a similar result for the mention, retweet, and mention-retweet coverings. Interestingly, the coverings resulting from the different weightings are all more similar to each other than to the structural covering from the unweighted network. Also the covering based on the hashtag similarities are different from all of the other weight-based coverings. We also explored the results qualitatively and found topic-based communities in which most members are not found in the same community in the other networks, indicating that while these people talk about the same things and can therefore be considered a community based on their content, they do not strongly interact with each other nor behave the same, and so belong to different social groups with respect to interactions and behavior. Another interesting example is a community whose topics tend to focus on Colorado. These users do not belong to the same community in the interaction-based network, but most of them do belong to the same community in the activity-based network. This indicates that these users react to the same events and issues regarding Colorado and are therefore strongly connected in the topic-based and activity-based networks, but at the same time they do not directly interact with each other and are therefore more loosely connected in the interaction-based networks, where they belong to different communities. This work demonstrates that asking the proper question and then crafting an appropriate weighting scheme to answer that question is an unavoidable first step for community detection in online social media, and that, without a clear definition of community, many rich and interesting communities present in online social networks remain invisible.

\footnotesize
\input{paper_partial.bbl}

\end{document}

### 2014-04-29 paper-for_arxiv/results.tex
Added files related to link analysis.

@@
 
-\textcolor{red}{Lastly, it is interesting to note that in the top ten most influential users (ranked using the total outgoing strength in the activity-based network) we find two users (Ann Tran and Jessica Northey) that were listed by Forbes in the "Top 10 Social Media Influencers".}
+\textcolor{red}{Lastly, it is interesting to note that in the top ten most influential users (ranked using the total outgoing strength in the activity-based network) we find two users (Ann Tran and Jessica Northey) that were listed by Forbes in the ``Top 10 Social Media Influencers".}

### 2014-04-29 code/compare_weights_inter_v_intra_community.py

@@ -1,0 +1,190 @@
+# A script to compare the weights for
+# edges inside / outside of a community
+# where we use a community of type C
+# and a weight of type B.
+# 
+# For example, we might consider the
+# communities based on transfer entropy
+# and the weights based on hashtags.
+# 
+# This allows us to narrow in on the 
+# characteristics of the community
+# types.
+
+#	DMD, 23 April 2014
+
+from itertools import islice
+import numpy
+import collections
+
+# The community type used to determine the
+# weights on edges.
+
+# weight_type = 'TE4'
+# weight_type = 'hashtag'
+# weight_type = 'mention-retweet'
+
+# The community type used to determine the
+# community memberships.
+
+# label_type = 'struc'
+# label_type = 'TE4'
+# label_type = 'hashtag'
+# label_type = 'mention-retweet'
+
+for weight_type in ['TE4', 'hashtag', 'mention-retweet']:
+	for label_type in ['struc', 'TE4', 'hashtag', 'mention-retweet']:
+		print 'Working on {}/{} pairing...'.format(weight_type, label_type)
+
+		if 'TE' in weight_type:
+			lag = weight_type.split('E')[1]
+			weight_file = '../data/content-free/directedweightsTE/edge_weights_bin10minutes_lag_{}_withMMBIAS.dat'.format(lag)
+		elif weight_type == 'hashtag':
+			weight_file = '../data/content-full/twitter_network_hashtags_weighted.txt'
+		elif weight_type == 'mention-retweet':
+			weight_file = '../data/content-full/twitter_network_contentfull_weighted_arithmeticmean.txt'
+
+		if label_type == 'struc':
+			label_file  = 'twitter_unweighted_network.txt_oslo_files'
+		elif 'TE' in label_type:
+			lag = label_type.split('E')[1]
+			label_file  = 'edge_weights_bin10minutes_lag_{}_withMMBIAS_edgelist.dat_oslo_files'.format(lag)
+		elif label_type == 'hashtag':
+			label_file  = 'twitter_network_hashtags_weighted.txt_oslo_files'
+		elif label_type == 'mention-retweet':
+			label_file  = 'twitter_network_contentfull_weighted_arithmeticmean.txt_oslo_files'
+
+		# Generate a dictionary of the form
+		# {user_id : community_id} from the 
+		# communities based on the labels.
+
+		full_name = '../oslom_outputs/{}/tp'.format(label_file)
+
+		comm_dict = collections.defaultdict(set)
+		comm_count = 0
+
[…]

### 2014-04-29 code/weight_distribution_by_community_type_old.R

@@ -9,6 +9,8 @@
 #
 # DMD, 22 April 2014
 
+library(reldist)
+
 # Search type to use:
 # 	labels-BLANK_weights-BLANK
 #
@@ -23,15 +25,15 @@
 # weight_type = 'hashtag'
 # weight_type = 'mention-retweet'
 
-label_types = c('struc', 'TE4', 'hashtag', 'mention-retweet')
-weight_types = c('TE4', 'hashtag', 'mention-retweet')
+# label_types = c('struc', 'TE4', 'hashtag', 'mention-retweet')
+# weight_types = c('TE4', 'hashtag', 'mention-retweet')
 
 # label_types = c('struc')
 # label_types = c('TE4')
-# label_types = c('hashtag')
+label_types = c('hashtag')
 # label_types = c('mention-retweet')
 
-# weight_types = c('TE4')
+weight_types = c('TE4')
 # weight_types = c('hashtag')
 # weight_types = c('mention-retweet')
 
@@ -97,7 +99,7 @@ ecdf.lw = 3
 
 prefix.pdf = paste0('labels-', label_type, '_weights-', weight_type)
 
-pdf(paste0('figures/', prefix.pdf, '-ecdf_by_type.pdf'))
+# pdf(paste0('figures/', prefix.pdf, '-ecdf_by_type.pdf'))
 par(mar=c(5,6,2,1), cex.lab = 2, cex.axis = 2)
 plot(ecdf(data_i.to.i_aggregate), col = 'red', xlim = xlim, ylab = expression(paste('P(', W[i*j] <= w, '| ', T == t, ')')), xlab = expression(paste('Weight, ', w)), lw = ecdf.lw, main = sprintf('Community Type %s, Weight Type %s', label_type, weight_type), lty = 1)
 lines(ecdf(data_e.to.i_aggregate), col = 'blue', lw = ecdf.lw, lty = 2)
@@ -106,7 +108,13 @@ legend('bottomright', legend = c('Internal-to-Internal', 'External-to-Internal',
 abline(v = median(data_i.to.i_aggregate), col = 'red', lw = ab.lw, lty = 1)
 abline(v = median(data_e.to.i_aggregate), col = 'blue', lw = ab.lw, lty = 2)
 abline(v = median(data_i.to.e_aggregate), col = 'green', lw = ab.lw, lty = 3)
-dev.off()
+# dev.off()
+
[…]

### 2014-04-29 code/weight_distribution_by_community_type.R
A script to analyze links.

@@ -1,0 +1,109 @@
+# A script that computes the distribution of 
+# i-to-i, e-to-i, and i-to-e weights *across
+# communities*. Compare this to 
+#
+# 	analyze_weights_by_community_types.R
+# 
+# which does this individually for *each*
+# community.
+#
+# DMD, 22 April 2014
+
+# library(reldist)
+
+# Search type to use:
+# 	labels-BLANK_weights-BLANK
+#
+# Ex: labels-struc_weights-TE4
+
+# label_type = 'struc'
+# label_type = 'TE4'
+# label_type = 'hashtag'
+# label_type = 'mention-retweet'
+
+# weight_type = 'TE4'
+# weight_type = 'hashtag'
+# weight_type = 'mention-retweet'
+
+label_types = c('struc', 'TE4', 'hashtag', 'mention-retweet')
+weight_types = c('TE4', 'hashtag', 'mention-retweet')
+
+# label_types = c('struc')
+# label_types = c('TE4')
+# label_types = c('hashtag')
+# label_types = c('mention-retweet')
+
+# weight_types = c('TE4')
+# weight_types = c('hashtag')
+# weight_types = c('mention-retweet')
+
+for (label_type in label_types){
+for (weight_type in weight_types){
+
+	cat(sprintf('Working with %s / %s\n\n', label_type, weight_type))
+
+prefix = paste0('interintramulti_labels-', label_type, '_weights-', weight_type)
+
+cat(sprintf('Loading data...\n\n'))
+
+data_inter = read.csv(paste0('../data/edges-by-type/', prefix, '_inter.dat'), header = FALSE)$V1
+data_intra = read.csv(paste0('../data/edges-by-type/', prefix, '_intra.dat'), header = FALSE)$V1
+data_multi = read.csv(paste0('../data/edges-by-type/', prefix, '_multi.dat'), header = FALSE)$V1
+
+cat(sprintf('Finished loading data...\n\n'))
+
+if ((weight_type == 'mention-retweet') || (weight_type == 'hashtag')){
+	cat(sprintf('\n\n\n\n\n!!!Warning: Removing 0 edges!!!!\n\n\n\n\n'))
+
+	which_inter = which(data_inter == 0)
+	if (length(which_inter > 0)){
+		data_inter = data_inter[-which_inter]
+	}
+
[…]

### 2014-04-29 paper-for_arxiv/results.tex
Rewriting section on edge types.

@@
 
-\subsection{Comparing Edges Across Different Community Types}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+%============================================================
+% Old section on 'Comparing Edges Across Different Community Types'
 
-We next explore how the edge weights defined by equations (\ref{Eqn-EW-activity}), (\ref{Eqn-EW-interaction}), and (\ref{Eqn-EW-topic}), and thus different forms of information flow, differ between community types.
+% \subsection{Comparing Edges Across Different Community Types}
+
+% We next explore how the edge weights defined by equations (\ref{Eqn-EW-activity}), (\ref{Eqn-EW-interaction}), and (\ref{Eqn-EW-topic}), and thus different forms of information flow, differ between community types.
 For a fixed community type, edges for a particular community may be partitioned into three sets: those from a user in the community to another user in the community (internal-to-internal), those from a user in the community to a user outside of the community (internal-to-external), and those from a user outside the community to a user inside the community (external-to-internal).
@@
 
-\begin{figure}[ht]
-  \centering
-\includegraphics[width=0.50\textwidth]{edge-types.eps}
-\caption{An example of the edges considered in determining the edge weight distribution for a given community (the focal community is in yellow).
+% \begin{figure}[ht]
+%   \centering
+% \includegraphics[width=0.50\textwidth]{edge-types.eps}
+% \caption{An example of the edges considered in determining the edge weight distribution for a given community (the focal community is in yellow).
 We focus on the internal-to-internal (red), internal-to-external (green), and external-to-internal (blue) edges.
 For a given focal community, all other edges (grey) are not considered.}
-\label{Fig-edge_types}
-\end{figure}
+% \label{Fig-edge_types}
+% \end{figure}
 
-As an example, Figure~\ref{Fig-dist_across_community} shows the distributions of hashtag-based weights for the largest community in the mention-retweet network.
+% As an example, Figure~\ref{Fig-dist_across_community} shows the distributions of hashtag-based weights for the largest community in the mention-retweet network.
 We see that the distribution of internal-to-internal hashtag weights has a longer tail than either the external-to-internal or internal-to-external hashtag weights, with edges within the community having higher weights than edges crossing the boundary of the community.
@@
 
-\begin{figure}[ht]
-  \centering
-\includegraphics[width=0.50\textwidth]{comm0_labels-hashtag_weights-mention-retweet-ecdf.pdf}
-\caption{The proportion of edges with a weight at least as large as the weight on the horizontal axis, across the types of edges described in Figure~\ref{Fig-edge_types}.
+% \begin{figure}[ht]
+%   \centering
+% \includegraphics[width=0.50\textwidth]{comm0_labels-hashtag_weights-mention-retweet-ecdf.pdf}
+% \caption{The proportion of edges with a weight at least as large as the weight on the horizontal axis, across the types of edges described in Figure~\ref{Fig-edge_types}.
 The community is defined by user interactions, and the edge weights are determined by topic similarity.
@@
 Note the logarithmic scale on the horizontal axis.}
-\label{Fig-dist_across_community}
-\end{figure}
+% \label{Fig-dist_across_community}
+% \end{figure}
 
@@
 
-For all four community types, the transfer entropy tended to be higher for edges crossing community boundaries than for those internal to community boundaries.
+% For all four community types, the transfer entropy tended to be higher for edges crossing community boundaries than for those internal to community boundaries.
 Recall that the transfer entropy $\text{TE}_{X(u) \to X(f)}$ quantifies the reduction in uncertainty about a follower $f$'s activity from knowing the activity of a user $u$.
@@
 
-Note that the communities defined by the follower network do tend to have higher edge weights internal compared to across community boundaries.
+% Note that the communities defined by the follower network do tend to have higher edge weights internal compared to across community boundaries.
 Thus, we do see that the structural communities capture some information about the functional behavior of communities of users in terms of topics and interaction.
@@
 % \end{tabular}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+%============================================================
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+%============================================================
+% New section on 'Comparing Edges Across Different Community Types'
+
+\subsection{Comparing Edges Across Different Community Types}
+
+Any covering determined by OSLOM induces a natural partition of the edges in a directed network.
+In particular, Let $u$ and $f$ be two users in the network, and let $M_{u}$ and $M_{f}$ be their community memberships.
+Then any edge $e_{u \to f}$ can be partitioned into one of three classes by
+\begin{align}
+	T(e_{u \to f}) = \left\{ \begin{array}{ll}
+		\text{Inter-edge} &: \ \ \ |M_{u} \cap M_{f}| = 0 \\
+		\text{Intra-edge} &: \ \ \ |M_{u} \cap M_{f}| = 1, |M_{u}| = |M_{f}| = 1 \\
+		\text{Multi-edge} &: \ \ \ |M_{u} \cap M_{f}| \geq 1, \max \{|M_{u}|, |M_{f}| \} > 1 \\
+	\end{array}\right. \label{Eqn-edge_types}.
+\end{align}
+In words, an inter-edge connects two users who share no community memberships, an intra-edge connects two users who each belong to the same, and only one, community, and a multi-edge connects two users who share a community membership under the restriction that at least one of the users belongs to a single community.
+See Figure~\ref{Fig-edge_types} for a schematic of this edge partitioning.
+Thus, inter-edges cross community boundaries, intra-edges lie within community boundaries, and multi-edges lie at the borders of community boundaries.
+
+\begin{figure}[!h]
+	\centering
+	\includegraphics[width=0.8\textwidth]{edge-types.pdf}
+	\caption{Lorem ipsum.}
+	\label{Fig-edge_types}
+\end{figure}
+
+Each community type (Structural, Activity-based, Topic-based, Interaction-based) induces a different partition of the edges, and each edge type (Transfer Entropy, Hashtag, Mention-Retweet) induces a different distribution of weights.
+That is, let $W_{u \to f}$ be the weight on a randomly selected edge $E_{u \to f}$ from the network, and compute
+\begin{align}
+	P(W_{u \to f} \leq w | T(E_{u \to f}) = t)
+\end{align}
+where $t$ is one of inter, intra, and multi. For meaningful community structure, we expect the distribution of edge weights to differ depending on the edge type.
+These distributions are shown in Figure~\ref{Fig-distributions_by_types}.
+
+Each \emph{column} of Figure~\ref{Fig-distributions_by_types} demonstrates how the distribution of a particular edge weight changes with the community type used to induce the partition.
+For example, the second column shows how the distributions of hashtag weights change based on the community partition.
+Unsurprisingly, we see that the greatest difference between the distributions occurs when we consider the topic-based communities, since the topic-based communities are determined based on the hashtag weights.
+However, we also see differences in distributions when the Community-type / Weight-type pairs are different.
+
+% $(\text{Structural, Activity-based, Topic-based, Interaction-based}) \times (\text{Transfer Entropy, Hashtag, Mention-Retweet})$.
+
+\begin{figure}[!h]
+	\centering
+	\includegraphics[width=1\textwidth]{distributions-edges.eps}
+	\caption{A schematic of how, given a covering, the edges of the network can be partitioned using \ref{Eqn-edge_types}.}
+	\label{Fig-distributions_by_types}
+\end{figure}
 

### 2014-04-29 code/analyze_weights_by_community_types.R

@@ -1,203 +1,0 @@
-library(np)
-
-kde.positive.support = function(x){
-  bwmethod = 'normal-reference'
-  # bwmethod = 'cv.ml'
-  # bwmethod = 'cv.ls'
-  
-  bw = npudensbw(~x, bwmethod = bwmethod)
-  fhat = npudens(bw)
-  
-  dt = (max(x)-min(x))/999
-
-  x.eval = seq(min(x), max(x), by = dt)
-  
-  y = log(x)
-  
-  bw.y = npudensbw(~y, bwmethod = bwmethod)
-  
-  trans.x = log(x.eval)
-  
-  fhat.trimmed = fitted(npudens(edat = trans.x, bws=bw.y))/x.eval
-  
-  out = list(x.eval = x.eval, fhat = fhat.trimmed)
-  
-  return(out)
-}
-
-# Search type to use:
-# 	labels-BLANK_weights-BLANK
-#
-# Ex: labels-struc_weights-TE4
-
-# label_type = 'struc'
-# label_type = 'TE4'
-# label_type = 'hashtag'
-# label_type = 'mention-retweet'
-
-# weight_type = 'TE4'
-# weight_type = 'hashtag'
-# weight_type = 'mention-retweet'
-
-# label_types = c('struc', 'TE4', 'hashtag', 'mention-retweet')
-# weight_types = c('TE4', 'hashtag', 'mention-retweet')
-
-label_types = c('mention-retweet')
-weight_types = c('TE4')
-# weight_types = c('hashtag')
-
-comms = 0:9
-
-for (label_type in label_types){
-for (weight_type in weight_types){
-
-for (comm_label in comms){
-# for (comm_label in c(0)){
-	prefix = paste0('comm', comm_label, '_labels-', label_type, '_weights-', weight_type)
-
-	data_i.to.i = read.csv(paste0('../data/edges-by-type/', prefix, '_i-to-i.dat'), header = FALSE)$V1
-
-	data_e.to.i = read.csv(paste0('../data/edges-by-type/', prefix, '_e-to-i.dat'), header = FALSE)$V1
-
-	data_i.to.e = read.csv(paste0('../data/edges-by-type/', prefix, '_i-to-e.dat'), header = FALSE)$V1
-
-	# Deal with NAs
-
-	data_i.to.i[is.na(data_i.to.i)] = 0
-	data_e.to.i[is.na(data_e.to.i)] = 0
[…]

### 2014-04-29 code/ecdf_distribution_by_community_type.R

@@ -1,0 +1,118 @@
+# A script that computes the distribution of 
+# i-to-i, e-to-i, and i-to-e weights *across
+# communities*. Compare this to 
+#
+# 	analyze_weights_by_community_types.R
+# 
+# which does this individually for *each*
+# community.
+#
+# DMD, 22 April 2014
+
+# library(reldist)
+
+# Search type to use:
+# 	labels-BLANK_weights-BLANK
+#
+# Ex: labels-struc_weights-TE4
+
+# label_type = 'struc'
+# label_type = 'TE4'
+# label_type = 'hashtag'
+# label_type = 'mention-retweet'
+
+# weight_type = 'TE4'
+# weight_type = 'hashtag'
+# weight_type = 'mention-retweet'
+
+label_types = c('struc', 'TE4', 'hashtag', 'mention-retweet')
+weight_types = c('TE4', 'hashtag', 'mention-retweet')
+
+# label_types = c('struc')
+# label_types = c('TE4')
+# label_types = c('hashtag')
+# label_types = c('mention-retweet')
+
+# weight_types = c('TE4')
+# weight_types = c('hashtag')
+# weight_types = c('mention-retweet')
+
+output.filename = 'stats_for_edges.dat'
+
+cat('comm.type\tweight.type\tmed.intra\tmed.inter\tmed.multi\tn.intra\tn.inter\tn.multi\n', file = output.filename, append = FALSE)
+
+for (label_type in label_types){
+for (weight_type in weight_types){
+
+	cat(sprintf('Working with %s / %s\n\n', label_type, weight_type))
+
+prefix = paste0('interintramulti_labels-', label_type, '_weights-', weight_type)
+
+cat(sprintf('Loading data...\n\n'))
+
+data_inter = read.csv(paste0('../data/edges-by-type/', prefix, '_inter.dat'), header = FALSE)$V1
+data_intra = read.csv(paste0('../data/edges-by-type/', prefix, '_intra.dat'), header = FALSE)$V1
+data_multi = read.csv(paste0('../data/edges-by-type/', prefix, '_multi.dat'), header = FALSE)$V1
+
+cat(sprintf('Finished loading data...\n\n'))
+
+if ((weight_type == 'mention-retweet') || (weight_type == 'hashtag')){
[…]

### 2014-04-29 code/ecdf_weights_by_community_types.R

@@ -1,0 +1,203 @@
+library(np)
+
+kde.positive.support = function(x){
+  bwmethod = 'normal-reference'
+  # bwmethod = 'cv.ml'
+  # bwmethod = 'cv.ls'
+  
+  bw = npudensbw(~x, bwmethod = bwmethod)
+  fhat = npudens(bw)
+  
+  dt = (max(x)-min(x))/999
+
+  x.eval = seq(min(x), max(x), by = dt)
+  
+  y = log(x)
+  
+  bw.y = npudensbw(~y, bwmethod = bwmethod)
+  
+  trans.x = log(x.eval)
+  
+  fhat.trimmed = fitted(npudens(edat = trans.x, bws=bw.y))/x.eval
+  
+  out = list(x.eval = x.eval, fhat = fhat.trimmed)
+  
+  return(out)
+}
+
+# Search type to use:
+# 	labels-BLANK_weights-BLANK
+#
+# Ex: labels-struc_weights-TE4
+
+# label_type = 'struc'
+# label_type = 'TE4'
+# label_type = 'hashtag'
+# label_type = 'mention-retweet'
+
+# weight_type = 'TE4'
+# weight_type = 'hashtag'
+# weight_type = 'mention-retweet'
+
+# label_types = c('struc', 'TE4', 'hashtag', 'mention-retweet')
+# weight_types = c('TE4', 'hashtag', 'mention-retweet')
+
+label_types = c('mention-retweet')
+weight_types = c('TE4')
+# weight_types = c('hashtag')
+
+comms = 0:9
+
+for (label_type in label_types){
+for (weight_type in weight_types){
+
+for (comm_label in comms){
+# for (comm_label in c(0)){
+	prefix = paste0('comm', comm_label, '_labels-', label_type, '_weights-', weight_type)
+
+	data_i.to.i = read.csv(paste0('../data/edges-by-type/', prefix, '_i-to-i.dat'), header = FALSE)$V1
+
+	data_e.to.i = read.csv(paste0('../data/edges-by-type/', prefix, '_e-to-i.dat'), header = FALSE)$V1
+
+	data_i.to.e = read.csv(paste0('../data/edges-by-type/', prefix, '_i-to-e.dat'), header = FALSE)$V1
+
+	# Deal with NAs
+
+	data_i.to.i[is.na(data_i.to.i)] = 0
+	data_e.to.i[is.na(data_e.to.i)] = 0
[…]

### 2014-04-29 code/scatter_distribution_by_community_type.R

@@ -1,0 +1,111 @@
+# A script that computes the distribution of 
+# i-to-i, e-to-i, and i-to-e weights *across
+# communities*. Compare this to 
+#
+# 	analyze_weights_by_community_types.R
+# 
+# which does this individually for *each*
+# community.
+#
+# DMD, 22 April 2014
+
+# library(reldist)
+
+# Search type to use:
+# 	labels-BLANK_weights-BLANK
+#
+# Ex: labels-struc_weights-TE4
+
+# label_type = 'struc'
+# label_type = 'TE4'
+# label_type = 'hashtag'
+# label_type = 'mention-retweet'
+
+# weight_type = 'TE4'
+# weight_type = 'hashtag'
+# weight_type = 'mention-retweet'
+
+label_types = c('struc', 'TE4', 'hashtag', 'mention-retweet')
+weight_types = c('TE4', 'hashtag', 'mention-retweet')
+
+# label_types = c('struc')
+# label_types = c('TE4')
+# label_types = c('hashtag')
+# label_types = c('mention-retweet')
+
+# weight_types = c('TE4')
+# weight_types = c('hashtag')
+# weight_types = c('mention-retweet')
+
+for (label_type in label_types){
+for (weight_type in weight_types){
+
+	cat(sprintf('Working with %s / %s\n\n', label_type, weight_type))
+
+prefix = paste0('interintramulti_labels-', label_type, '_weights-', weight_type)
+
+cat(sprintf('Loading data...\n\n'))
+
+data_inter = read.csv(paste0('../data/edges-by-type/', prefix, '_inter.dat'), header = FALSE)$V1
+data_intra = read.csv(paste0('../data/edges-by-type/', prefix, '_intra.dat'), header = FALSE)$V1
+data_multi = read.csv(paste0('../data/edges-by-type/', prefix, '_multi.dat'), header = FALSE)$V1
+
+cat(sprintf('Finished loading data...\n\n'))
+
+if ((weight_type == 'mention-retweet') || (weight_type == 'hashtag')){
+	cat(sprintf('\n\n\n\n\n!!!Warning: Removing 0 edges!!!!\n\n\n\n\n'))
+
+	which_inter = which(data_inter == 0)
+	if (length(which_inter > 0)){
+		data_inter = data_inter[-which_inter]
+	}
+
[…]

### 2014-04-29 code/weight_distribution_by_community_type.R

@@ -1,109 +1,0 @@
-# A script that computes the distribution of 
-# i-to-i, e-to-i, and i-to-e weights *across
-# communities*. Compare this to 
-#
-# 	analyze_weights_by_community_types.R
-# 
-# which does this individually for *each*
-# community.
-#
-# DMD, 22 April 2014
-
-# library(reldist)
-
-# Search type to use:
-# 	labels-BLANK_weights-BLANK
-#
-# Ex: labels-struc_weights-TE4
-
-# label_type = 'struc'
-# label_type = 'TE4'
-# label_type = 'hashtag'
-# label_type = 'mention-retweet'
-
-# weight_type = 'TE4'
-# weight_type = 'hashtag'
-# weight_type = 'mention-retweet'
-
-label_types = c('struc', 'TE4', 'hashtag', 'mention-retweet')
-weight_types = c('TE4', 'hashtag', 'mention-retweet')
-
-# label_types = c('struc')
-# label_types = c('TE4')
-# label_types = c('hashtag')
-# label_types = c('mention-retweet')
-
-# weight_types = c('TE4')
-# weight_types = c('hashtag')
-# weight_types = c('mention-retweet')
-
-for (label_type in label_types){
-for (weight_type in weight_types){
-
-	cat(sprintf('Working with %s / %s\n\n', label_type, weight_type))
-
-prefix = paste0('interintramulti_labels-', label_type, '_weights-', weight_type)
-
-cat(sprintf('Loading data...\n\n'))
-
-data_inter = read.csv(paste0('../data/edges-by-type/', prefix, '_inter.dat'), header = FALSE)$V1
-data_intra = read.csv(paste0('../data/edges-by-type/', prefix, '_intra.dat'), header = FALSE)$V1
-data_multi = read.csv(paste0('../data/edges-by-type/', prefix, '_multi.dat'), header = FALSE)$V1
-
-cat(sprintf('Finished loading data...\n\n'))
-
-if ((weight_type == 'mention-retweet') || (weight_type == 'hashtag')){
-	cat(sprintf('\n\n\n\n\n!!!Warning: Removing 0 edges!!!!\n\n\n\n\n'))
-
-	which_inter = which(data_inter == 0)
-	if (length(which_inter > 0)){
-		data_inter = data_inter[-which_inter]
-	}
-
[…]

### 2014-04-29 abstract-eccs14/eccs14_abstract.tex
my edits for the abstract

@@
 
+%"The structure-based approach, is most common in the literature (e.g., citation), and relies solely on the reported relationships between users---completely ignoring user activity tweet content, or user interaction."
+
 Community detection in online social networks is typically based on the analysis of the explicit connections between users, such as ``friends" on Facebook and ``followers" on Twitter.
-But online users often have hundreds or even thousands of such connections, and many of these connections do not correspond to real friendships or more generally to accounts that users interact with.
-We claim that community detection in online social networks should be question-oriented and rely on additional information beyond the simple structure of the network.
-The concept of `community' is very general, and different questions such as ``who do we interact with?" and ``with whom do we share similar interests?" can lead to the discovery of different social groups.
-We propose looking at when and how communities motivated by these different questions overlap, and whether different approaches to asking the question, ``What community are you in?'' leads to different insights about a social network.
+This so-called \emph{structure-based} approach, relies solely on the reported relationships between users---completely ignoring the users activity, content, or interactions.
+However, users often have hundreds or even thousands of such structural-connections, many of which do not correspond to real friendships or even accounts the user interacts with.
+We claim that community detection in online social networks should be \emph{question-oriented} and rely on additional information beyond the simple (often spurious) structure of the network.
+The concept of `community' is very general, and we have found that different questions such as ``who does a user interact with?", ``from whom does a user receive information?" and ``with whom does a user share similar interests?" can lead to the discovery of many rich \emph{and} interesting communities that the structure-based analysis alone is completely blind to.
+%We propose looking at when and how communities motivated by these different questions overlap, and whether different approaches to asking the question, ``What community are you in?'' leads to different insights about a social network.
 For example, a user on Twitter might connect mostly with computational social scientists, talk mostly about machine learning, interact solely with close friends (who may or may not be computational social scientists), and utilize the service only on nights and weekends.
-Each of these different `profiles' of the user highlight different views of the user's social network, and represent different types of communities.
+We argue that each of these different `profiles' of the user highlight different views of the user's social network, and represent different types of communities.
+
 We divide our approaches into four categories based on the questions outlined above: structure-based, activity-based, topic-based, and interaction-based.
-The structure-based approach, is most common, and for our data relies on reported follower relationships.
-To detect the other kinds of communities we weight the structural edges with different scores that aim to measure the different kinds of interactions.
-For the activity-based communities, we consider only the timing of each user's tweets and ignore any additional content.
-From this starting point, we can view the behavior of a user $u$ on Twitter as a point process, where at any instant $t$ the user has either emitted a tweet ($X_{t}(u) = 1$) or remained silent ($X_{t}(u) = 0$).
-Thus, we reduce all of the information generated by a user on Twitter to a time series $\{ X_{t}(u)\}$.
-We can then compute the flow of information between two users $u$ and $v$ by computing the transfer entropy between their time series $X_{t}(u)$ and $X_{t}(v).$ For the interaction-based communities, we weight the user-follower network with a measure proportional to the number of mentions and/or retweets between users.
-Lastly, in order to detect the topical communities, we weight the edges of the user-follower network through a measure based on the number of common hashtags between pairs of users.
+The structure-based approach, outlined above, relies solely on the known follower relationships, and is used here purely for comparison with the standard.
+To detect the \emph{question-oriented} communities we weight the structural edges with different scores derived to both answer and give insight into the question posed about the network.
+For the \emph{activity-based} communities, we consider only the timing of each user's tweets and ignore any additional content, i.e., we view the behavior of a user $u$ on Twitter as a point process, where at any instant $t$ the user has either emitted a tweet ($X_{t}(u) = 1$) or remained silent ($X_{t}(u) = 0$)---reducing all of the information generated by a user to a symbolic time series: $\{ X_{t}(u)\}$.
+We then compute the directed flow of information between two users $u$ and $v$ by computing the so-called \emph{transfer entropy} between their time series $X_{t}(u)$ and $X_{t}(v)$; a novel approach which gives interesting insights into how information transmits in a network as well as giving insight into who the influential users are.
+For the \emph{interaction-based} communities, we weight the structural network with a measure proportional to the number of mentions and/or retweets between users.
+Lastly, in order to detect the topical communities, we weight the edges of the structural network through a measure based on the number of common hashtags between pairs of users.
 Hashtags are a good proxy for a tweet's content as hashtags are explicitly meant to be keywords indicating the topic of the tweet.
-We then used the OSLOM algorithm~\cite{LancichinettiPlos} to detect overlapping communities present in the four weighted, directed networks.
-We then compared with several different methods the communities obtained in the different weightings, in particular we considered the normalized mutual information.
-We see that similarity between the coverings is dictated by the generic community type (structural, activity-based, etc.).
-That is, the transfer entropy coverings are more similar to each other than to any of the other coverings, with a similar result for the mention, retweet, and mention-retweet coverings.
-Interestingly, the coverings resulting from the different weightings are all more similar to each other than to the structural covering from the unweighted network.
-Also the covering based on the hashtag similarities are different from all of the other weight-based coverings.
-We also explored the results qualitatively and found topic-based communities in which most members are not found in the same community in the other networks, indicating that while these people talk about the same things and can therefore be considered a community based on their content, they do not strongly interact with each other nor behave the same, and so belong to different social groups with respect to interactions and behavior.
+It should be noted that a user may be a member of multiple communities simultaneously in a given network, e.g., a user may tweet about ``Complexity" \emph{and} "Lucca, Italy", which may be two separate topical communities, but may overlap for example when a collection of users tweet about ECCS'14.
+For this reason we seek overlapping communities---often called \emph{coverings}.
+
+To detect covering of each weighted, directed network we use the OSLOM algorithm~\cite{LancichinettiPlos} .
+We then applied several statistical measures (e.g., mutual information) to compare the communities derived from the different questions with intriguing and informative results.
+Not surprisingly, there was similarity between coverings dictated by each generic community type (structural, activity-based, etc.).
+% e.g., the coverings derived from transfer-entropy are more similar to each other than to any of the other coverings, with a similar result for the mention, retweet, and mention-retweet coverings. 
+Interestingly, the coverings resulting from the \emph{question-oriented} weightings were all more similar to each other than to the covering from the \emph{structure-based} analysis.
+We found that the coverings derived from the \emph{topic-based} questions (hashtag weightings) were significantly different from all of the other question-oriented coverings.
+
+We explored these coverings qualitatively and found interesting insight into these networks.
+For example, we found topic-based communities containing members that were otherwise disjoint based on interaction or activity.
+These indicate users who tweet about the same content and should therefore be considered a topical community, but do not strongly interact with each other nor use twitter to transmit information to each other, and should therefore belong to different communities with respect to interactions and activity.
 Another interesting example is a community whose topics tend to focus on Colorado.
@@
 This indicates that these users react to the same events and issues regarding Colorado and are therefore strongly connected in the topic-based and activity-based networks, but at the same time they do not directly interact with each other and are therefore more loosely connected in the interaction-based networks, where they belong to different communities.
+These are very nice empirical examples that illustrate our main hypothesis: the \emph{questions} you ask about the network dictate the communities which are discoverable and it is insufficient to simply do a single (weighted or unweighted) community detection, to fully understand a networks community structure several weightings should be derived from interesting questions about the network and then the coverings should be compared qualitatively.
+
  This work demonstrates that asking the proper question and then crafting an appropriate weighting scheme to answer that question is an unavoidable first step for community detection in online social media, and that, without a clear definition of community, many rich and interesting communities present in online social networks remain invisible.
@@
 \footnotesize
-\input{paper_partial.bbl}
+\input{abstract.bbl}
 

### 2014-04-30 paper-for_arxiv/results.tex
Added more revisions to edge work.

@@
 	T(e_{u \to f}) = \left\{ \begin{array}{ll}
-		\text{Inter-edge} &: \ \ \ |M_{u} \cap M_{f}| = 0 \\
-		\text{Intra-edge} &: \ \ \ |M_{u} \cap M_{f}| = 1, |M_{u}| = |M_{f}| = 1 \\
-		\text{Multi-edge} &: \ \ \ |M_{u} \cap M_{f}| \geq 1, \max \{|M_{u}|, |M_{f}| \} > 1 \\
+		\text{Inter-edge} &: \ \ \ M_{u} \cap M_{f} = \emptyset \\
+		\text{Intra-edge} &: \ \ \ M_{u} = M_{f}\\
+		\text{Multi-edge} &: \ \ \ \text{ otherwise} \\
 	\end{array}\right. \label{Eqn-edge_types}.
 \end{align}
-In words, an inter-edge connects two users who share no community memberships, an intra-edge connects two users who each belong to the same, and only one, community, and a multi-edge connects two users who share a community membership under the restriction that at least one of the users belongs to a single community.
+In words, an inter-edge connects two users who share no community memberships, an intra-edge connects two users who each belong to the same communities, and a multi-edge connects two users who share some, but not all, community memberships.
+Thus, inter-edges cross community boundaries, intra-edges lie within community boundaries, and multi-edges lie at the borders of community boundaries.
 See Figure~\ref{Fig-edge_types} for a schematic of this edge partitioning.
-Thus, inter-edges cross community boundaries, intra-edges lie within community boundaries, and multi-edges lie at the borders of community boundaries.
 
@@
 	\includegraphics[width=0.8\textwidth]{edge-types.pdf}
-	\caption{Lorem ipsum.}
+	\caption{A schematic of how, given a covering, the edges of the network can be partitioned using \ref{Eqn-edge_types} into inter-edges, intra-edges, and multi-edges.
+Inter-edges (red) cross community boundaries.
+Intra-edges (blue) remain inside community boundaries.
+Multi-edges (purple) both remain in and cross community boundaries due to overlap in community membership.
+Each column corresponds to the same collection of weights, but partitioned using a different covering.
+Each row corresponds to the same covering, but for the different weights.}
 	\label{Fig-edge_types}
@@
 
-Each \emph{column} of Figure~\ref{Fig-distributions_by_types} demonstrates how the distribution of a particular edge weight changes with the community type used to induce the partition.
+Each \emph{column} of Figure~\ref{Fig-distributions_by_types} demonstrates how the distribution of weights change with the community type used to induce the partition.
 For example, the second column shows how the distributions of hashtag weights change based on the community partition.
 Unsurprisingly, we see that the greatest difference between the distributions occurs when we consider the topic-based communities, since the topic-based communities are determined based on the hashtag weights.
-However, we also see differences in distributions when the Community-type / Weight-type pairs are different.
-
-% $(\text{Structural, Activity-based, Topic-based, Interaction-based}) \times (\text{Transfer Entropy, Hashtag, Mention-Retweet})$.
+However, we also see differences in the distributions when the Community-type / Weight-type pairs do not match.
+For example, for the covering corresponding to the activity-based community, the distribution of
 
@@
 	\includegraphics[width=1\textwidth]{distributions-edges.eps}
-	\caption{A schematic of how, given a covering, the edges of the network can be partitioned using \ref{Eqn-edge_types}.}
+	\caption{The distribution of edge weights for different community types and weight types. }
 	\label{Fig-distributions_by_types}

### 2014-04-30 code/compute_Jensen.py

@@ -1,0 +1,58 @@
+# Use Greg Ver Steeg's entropy estimation package to
+# compute the Jensen-Shannon divergence between the
+# edge distributions.
+#
+# DMD, 29 April 2014
+
+import entropy_estimators as ee
+import math
+
+label_types = ['struc', 'TE4', 'hashtag', 'mention-retweet']
+weight_types = ['TE4', 'hashtag', 'mention-retweet']
+
+print 'Label Type\tWeight Type\tD(inter, intra)'
+
+for label_type in label_types:
+	for weight_type in weight_types:
+		data_inter = []
+		data_intra = []
+		data_multi = []
+
+		prefix = 'interintramulti_labels-{}_weights-{}'.format(label_type, weight_type)
+
+		with open('../data/edges-by-type/{}_inter.dat'.format(prefix)) as ofile:
+			for line in ofile:
+				val = float(line)
+
+				if val == 0 or math.isnan(val):
+					pass
+				else:
+					data_inter.append([val])
+
+		with open('../data/edges-by-type/{}_intra.dat'.format(prefix)) as ofile:
+			for line in ofile:
+				val = float(line)
+
+				if val == 0 or math.isnan(val):
+					pass
+				else:
+					data_intra.append([float(line)])
+
+		with open('../data/edges-by-type/{}_multi.dat'.format(prefix)) as ofile:
+			for line in ofile:
+				val = float(line)
+
+				if val == 0 or math.isnan(val):
+					pass
+				else:
+					data_multi.append([float(line)])
+
+		K = 5
+
+		KLxy = ee.kldiv(data_inter[:5000], data_intra[:5000], k = K)
+
+		KLyx = ee.kldiv(data_intra[:5000], data_inter[:5000], k = K)
+
+		JS = 0.5*(KLxy + KLyx)
+
+		print label_type, weight_type, JS

### 2014-04-30 code/entropy_estimators.py

@@ -1,0 +1,205 @@
+#python2.7
+#Written by Greg Ver Steeg
+#See readme.pdf for documentation
+#Or go to http://www.isi.edu/~gregv/npeet.html
+
+import scipy.spatial as ss
+from scipy.special import digamma,gamma
+from math import log,pi
+import numpy.random as nr
+import numpy as np
+import random
+
+#####CONTINUOUS ESTIMATORS
+
+def entropy(x,k=3,base=2):
+  """ The classic K-L k-nearest neighbor continuous entropy estimator
+      x should be a list of vectors, e.g. x = [[1.3],[3.7],[5.1],[2.4]]
+      if x is a one-dimensional scalar and we have four samples
+  """
+  assert k <= len(x)-1, "Set k smaller than num. samples - 1"
+  d = len(x[0])
+  N = len(x)
+  intens = 1e-10 #small noise to break degeneracy, see doc.
+  x = [list(p + intens*nr.rand(len(x[0]))) for p in x]
+  tree = ss.cKDTree(x)
+  nn = [tree.query(point,k+1,p=float('inf'))[0][k] for point in x]
+  const = digamma(N)-digamma(k) + d*log(2)
+  return (const + d*np.mean(map(log,nn)))/log(base)
+
+def mi(x,y,k=3,base=2):
+  """ Mutual information of x and y
+      x,y should be a list of vectors, e.g. x = [[1.3],[3.7],[5.1],[2.4]]
+      if x is a one-dimensional scalar and we have four samples
+  """
+  assert len(x)==len(y), "Lists should have same length"
+  assert k <= len(x) - 1, "Set k smaller than num. samples - 1"
+  intens = 1e-10 #small noise to break degeneracy, see doc.
+  x = [list(p + intens*nr.rand(len(x[0]))) for p in x]
+  y = [list(p + intens*nr.rand(len(y[0]))) for p in y]
+  points = zip2(x,y)
+  #Find nearest neighbors in joint space, p=inf means max-norm
+  tree = ss.cKDTree(points)
+  dvec = [tree.query(point,k+1,p=float('inf'))[0][k] for point in points]
+  a,b,c,d = avgdigamma(x,dvec), avgdigamma(y,dvec), digamma(k), digamma(len(x)) 
+  return (-a-b+c+d)/log(base)
+
+def cmi(x,y,z,k=3,base=2):
+  """ Mutual information of x and y, conditioned on z
[…]

### 2014-04-30 abstract-eccs14/eccs14_abstract.tex
Beginning to incorporate reviewer comments.

@@
 Community detection in online social networks is typically based on the analysis of the explicit connections between users, such as ``friends" on Facebook and ``followers" on Twitter.
-This so-called \emph{structure-based} approach, relies solely on the reported relationships between users---completely ignoring the users activity, content, or interactions.
+This so-called \emph{structure-based} approach relies solely on the reported relationships between users---completely ignoring the users activity, content, or interactions.
 However, users often have hundreds or even thousands of such structural-connections, many of which do not correspond to real friendships or even accounts the user interacts with.
@@
 For the \emph{activity-based} communities, we consider only the timing of each user's tweets and ignore any additional content, i.e., we view the behavior of a user $u$ on Twitter as a point process, where at any instant $t$ the user has either emitted a tweet ($X_{t}(u) = 1$) or remained silent ($X_{t}(u) = 0$)---reducing all of the information generated by a user to a symbolic time series: $\{ X_{t}(u)\}$.
-We then compute the directed flow of information between two users $u$ and $v$ by computing the so-called \emph{transfer entropy} between their time series $X_{t}(u)$ and $X_{t}(v)$; a novel approach which gives interesting insights into how information transmits in a network as well as giving insight into who the influential users are.
+We then compute the directed flow of information between two users $u$ and $v$ by computing the \emph{transfer entropy} between their time series $X_{t}(u)$ and $X_{t}(v)$; an information theoretic approach which gives insights into how information transmits in a network as well as insights into who the influential users are.
 For the \emph{interaction-based} communities, we weight the structural network with a measure proportional to the number of mentions and/or retweets between users.
@@
 Hashtags are a good proxy for a tweet's content as hashtags are explicitly meant to be keywords indicating the topic of the tweet.
-It should be noted that a user may be a member of multiple communities simultaneously in a given network, e.g., a user may tweet about ``Complexity" \emph{and} "Lucca, Italy", which may be two separate topical communities, but may overlap for example when a collection of users tweet about ECCS'14.
+It should be noted that a user may be a member of multiple communities simultaneously in a given network, e.g., a user may tweet about ``Complexity'' \emph{and} ``Lucca, Italy'', which may be two separate topical communities, but may overlap for example when a collection of users tweet about ECCS'14.
 For this reason we seek overlapping communities---often called \emph{coverings}.
 
-To detect covering of each weighted, directed network we use the OSLOM algorithm~\cite{LancichinettiPlos} .
+To detect covering of each weighted, directed network we use the OSLOM algorithm~\cite{LancichinettiPlos}.
 We then applied several statistical measures (e.g., mutual information) to compare the communities derived from the different questions with intriguing and informative results.

### 2014-04-30 paper-for_arxiv/intro.tex
Beginning to incorporate reviewer comments.

@@
 
-The activity-based, topic-based, and interaction-based networks allow us to build a more complete picture of the \emph{latent} social network present in online social media, as opposed to the \emph{explicit} social network indicated by structural links.
+The activity-based, topic-based, and interaction-based networks allow us to build a more complete picture of the \emph{implicit} social network present in online social media, as opposed to the \emph{explicit} social network indicated by structural links.
 In this paper, we explore the relation between these various possible networks and their corresponding communities.

### 2014-04-30 paper-for_arxiv/methods.tex
Beginning to incorporate reviewer comments.

@@
 
-Let $\{X_{t}\}$ and $\{ Y_{t}\}$ be two strong-sense stationary stochastic processes.
-We use the notation $X_{t-k}^{t}$ to denote the values of the stochastic process from time $t-k$ to time $t$, $X_{t-k}^{t} = (X_{t-k}, X_{t-(k-1)}, \ldots, X_{t - 1}, X_{t})$.
+Let $\{X_{t}\}$ and $\{ Y_{t}\}$ be two strong-sense stationary stochastic processes\footnote{Recall that a a stochastic process is strong-sense stationary if the distribution over process evaluated at finitely many time points is invariant to an overall timeshift~\cite{grimmett2001probability}.}.
+In our work, these would correspond to two user activities, $X_{t}(u)$ and $X_{t}(v).$ We use the notation $X_{t-k}^{t}$ to denote the values of the stochastic process from time $t-k$ to time $t$, $X_{t-k}^{t} = (X_{t-k}, X_{t-(k-1)}, \ldots, X_{t - 1}, X_{t})$.
 The lag-$k$ transfer entropy of $Y$ on $X$ is defined as
@@
 for all $t$.
-That is, the predictive distribution only depends on the past, not on when the past is observed\footnote{We really only need \emph{conditional} stationarity~\cite{caires2003nonparametric}, but stationarity implies conditional stationarity.}.
+That is, the predictive distribution only depends on the past, not on when the past is observed.
 Given this assumption, we compute estimators for $p(x_{k+1} | x_{1}^{k})$ and $p(x_{k+1} | x_{1}^{k}, y_{1}^{k})$ by `counting': for each possible past $(x_{1}^{k}, y_{1}^{k})$, we count the number of times a future of type $x_{k+1}$ occurs, and normalize.

### 2014-04-30 paper-for_arxiv/results.tex
Beginning to incorporate reviewer comments.

@@
 However, we also see differences in the distributions when the Community-type / Weight-type pairs do not match.
-For example, for the covering corresponding to the activity-based community, the distribution of
+For example, for the covering corresponding to the activity-based communities, the hashtag weights tend to be higher for edges internal to communities than between communities.
+Similarly, for the covering corresponding to the topic-based communities, the transfer entropy weights tend to be higher on edges within (intra) and between (inter) communities, and lower for edges between members with multiple, non-identical memberships (multi).
 
@@
 	\includegraphics[width=1\textwidth]{distributions-edges.eps}
-	\caption{The distribution of edge weights for different community types and weight types. }
+	\caption{The distribution of edge weights for different community types (rows) and weight types (columns).
+The red,  blue, and magenta values below each distribution indicate the median of weight on intra-, inter-, and multi-edges, respectively.}
 	\label{Fig-distributions_by_types}

### 2014-04-30 paper-for_arxiv/intro.tex
Fixed references and removed coloring.

@@
 See~\cite{fortunato2010community} for a recent review.
-\textcolor{red}{A large body of work exists on methods for automatic detection of communities within networks, among which we recall the Girvan and Newman algorithm~\cite{newman2004finding}, Infomap~\cite{rosvall2008maps}, Louvain\cite{~blondel2008fast}, and the recently introduced OSLOM\cite{LancichinettiPlos}.}
+A large body of work exists on methods for automatic detection of communities within networks, among which we recall the Girvan and Newman algorithm~\cite{newman2004finding}, Infomap~\cite{Rosvall08mapsof}, Louvain~\cite{blondel2008fast}, and the recently introduced OSLOM~\cite{LancichinettiPlos}.
 All these methods \emph{begin} with a given network, and then attempt to uncover structure present in the network, i.e., they are agnostic to how the network was constructed.
@@
 Finally, the interaction-based approach relies on the meta-data and text of messages to identify who a user converses with on the social media service.
-On Twitter, we can use mentions (indicating a directed communication) and \textcolor{blue}{retweets (indicating endorsement of another user)} to identify conversation.
+On Twitter, we can use mentions (indicating a directed communication) and retweets (indicating endorsement of another user) to identify conversation.
 Moreover, we can define a directed influence between two users by considering the attention paid to that user compared to all other users.

### 2014-04-30 paper-for_arxiv/methods.tex
Fixed references and removed coloring.

@@
 Their method relies on a fitness function that measures the statistical significance of clusters with respect to random fluctuations, and attempts to optimize this fitness function across all clusters.
-\textcolor{red}{Following~\cite{Lancichinetti2010}, the significance measure is defined as the probability of finding the cluster in a network without community structure.
+Following~\cite{LancichinettiPlos}, the significance measure is defined as the probability of finding the cluster in a network without community structure.
 The null model used is basically the same as the one adopted by Newman and Girvan to define modularity, i.e.
@@
 This feature of the algorithm plays an important role in the analysis of real data networks, since it is not always the case that a community structure is indeed present and it is therefore useful to be able to detect its absence too.
-Therefore, given its versatility and performance with benchmark network, in this paper we used OSLOM to detect \emph{overlapping} communities present in our \emph{weighted} and \emph{directed} network.}
+Therefore, given its versatility and performance with benchmark network, in this paper we used OSLOM to detect \emph{overlapping} communities present in our \emph{weighted} and \emph{directed} network.
 %For this paper we use OSLOM since it allowed us to detect \emph{overlapping} communities present in our \emph{weighted} and \emph{directed} network, and its authors showed that it performs very well on various types of artificial benchmark graphs and also on several real networks.

### 2014-04-30 paper-for_arxiv/results.tex
Fixed references and removed coloring.

@@
 This indicates that these users react to the same events and issues regarding Colorado and are therefore strongly connected in the topic-based and activity-based networks, but at the same time they do not directly interact with each other and are therefore more loosely connected in the interaction-based networks, where they belong to different communities.
-\textcolor{red}{As expected, among the most influential users (in terms of transfer entropy) we find \@Colorado, which is the state official Twitter account, \@ConnectColorado, a page created to connect Coloradans, and CBS Denver account.}
+As expected, among the most influential users (in terms of transfer entropy) we find \@Colorado, which is the state official Twitter account, \@ConnectColorado, a page created to connect Coloradans, and CBS Denver account.
 
-\textcolor{red}{Lastly, it is interesting to note that in the top ten most influential users (ranked using the total outgoing strength in the activity-based network) we find two users (Ann Tran and Jessica Northey) that were listed by Forbes in the ``Top 10 Social Media Influencers".}
+Lastly, it is interesting to note that in the top ten most influential users (ranked using the total outgoing strength in the activity-based network) we find two users (Ann Tran and Jessica Northey) that were listed by Forbes in the ``Top 10 Social Media Influencers".

### 2014-04-30 paper-for_arxiv/results.tex
Added more discussion to the edge-type work.

@@
 \begin{align}
-	P(W_{u \to f} \leq w | T(E_{u \to f}) = t)
+	P(W_{u \to f} \leq w | T(E_{u \to f}) = t),
 \end{align}
-where $t$ is one of inter, intra, and multi. For meaningful community structure, we expect the distribution of edge weights to differ depending on the edge type.
+the empirical distribution over the edge weights conditioned on $t$ being one of inter, intra, and multi.
+For meaningful community structure, we expect the distribution of edge weights to differ with the edge type $t$.
+If the community structure were arbitrary, the edge weights would be independent of the edge type, and all three conditional distributions would be identical.
 These distributions are shown in Figure~\ref{Fig-distributions_by_types}.
@@
 For example, the second column shows how the distributions of hashtag weights change based on the community partition.
+In general, the distributions differ in non-trivial ways across the edge types and coverings.
+However, we see that the medians of the distributions provide a useful summary statistic.
+Under each collection of distribution functions, we list the median value of the inter, intra, and multi-edges in red, blue, and magenta, respectively.
 Unsurprisingly, we see that the greatest difference between the distributions occurs when we consider the topic-based communities, since the topic-based communities are determined based on the hashtag weights.
@@
 \end{figure}
+
+We also note that the distribution of transfer entropy weights always tend to be higher for edges crossing community boundaries (inter- or multi-edges) compared to those edges within community boundaries (intra-edges).
+This is a property not exhibited by either the hashtag or mention-retweet weights, independent of the covering used to partition the edges.
+Moreover, for all but the activity-based covering, the weights of multi-edges tend to be highest overall.
+Recall that the transfer entropy $\text{TE}_{X(u) \to X(f)}$ quantifies the reduction in uncertainty about a follower $f$'s activity from knowing the activity of a user $u$.
+This result therefore implies that, in terms of prediction, it is more useful to know the time series of a user followed outside of the community compared to a user followed inside of the community, and even more useful to know the time series of a user that shares some, but not all, of the same community memberships.
+Thus, in an information theoretic sense, we see that novel information useful for prediction is more likely to flow \emph{across} community boundaries than \emph{within} community boundaries.
 

### 2014-04-30 paper-for_arxiv/methods.tex
Minor revisions.

@@
 
-Let $\{X_{t}\}$ and $\{ Y_{t}\}$ be two strong-sense stationary stochastic processes\footnote{Recall that a a stochastic process is strong-sense stationary if the distribution over process evaluated at finitely many time points is invariant to an overall timeshift~\cite{grimmett2001probability}.}.
-In our work, these would correspond to two user activities, $X_{t}(u)$ and $X_{t}(v).$ We use the notation $X_{t-k}^{t}$ to denote the values of the stochastic process from time $t-k$ to time $t$, $X_{t-k}^{t} = (X_{t-k}, X_{t-(k-1)}, \ldots, X_{t - 1}, X_{t})$.
+Let $\{X_{t}\}$ and $\{ Y_{t}\}$ be two strong-sense stationary stochastic processes\footnote{Recall that a stochastic process is strong-sense stationary if the joint distribution for the process evaluated at finitely many time points is invariant to an overall timeshift~\cite{grimmett2001probability}.}.
+In our work, these would correspond to the activities, $X_{t}(u)$ and $X_{t}(v),$ of two users $u$ and $v$.
+We use the notation $X_{t-k}^{t}$ to denote the values of the stochastic process from time $t-k$ to time $t$, $X_{t-k}^{t} = (X_{t-k}, X_{t-(k-1)}, \ldots, X_{t - 1}, X_{t})$.
 The lag-$k$ transfer entropy of $Y$ on $X$ is defined as

### 2014-05-06 code/ecdf_distribution_by_community_type.R
Added figure with densities by edge type.
This is to replace the distribution by edge type figure.

@@ -26,7 +26,7 @@
 # weight_type = 'mention-retweet'
 
 label_types = c('struc', 'TE4', 'hashtag', 'mention-retweet')
-weight_types = c('TE4', 'hashtag', 'mention-retweet')
+# weight_types = c('TE4', 'hashtag', 'mention-retweet')
 
 # label_types = c('struc')
 # label_types = c('TE4')
@@ -34,7 +34,7 @@ weight_types = c('TE4', 'hashtag', 'mention-retweet')
 # label_types = c('mention-retweet')
 
 # weight_types = c('TE4')
-# weight_types = c('hashtag')
+weight_types = c('hashtag')
 # weight_types = c('mention-retweet')
 
 output.filename = 'stats_for_edges.dat'
@@ -109,10 +109,49 @@ main.text = sprintf('Community Type %s, Weight Type %s', label_type, weight_type
 plot(ecdf(data_inter), verticals = vertical, do.points = to.do.points, col = 'blue', ylab = expression(paste('P(', W[i*j] <= w, '| ', T == t, ')')), xlab = expression(paste('Weight, ', w)), lwd = lwd.cdf, main = '', lty = 1, xlim = xlim)
 lines(ecdf(data_intra), verticals = vertical, do.points = to.do.points, col = 'red', lwd = lwd.cdf, lty = 2)
 lines(ecdf(data_multi), verticals = vertical, do.points = to.do.points, col = 'darkmagenta', lwd = lwd.cdf, lty = 3)
-# legend('bottomright', legend = c('Intra', 'Inter', 'Multi'), col = c('red', 'green', 'blue'), lty = 1:3, lwd = 3)
+# legend('bottomright', legend = c('Intra', 'Inter', 'Multi'), col = c('blue', 'red', 'darkmagenta'), lty = 1:3, lwd = 3)
 dev.off()
+
+fs = c(density(data_inter, from = 0)$y, density(data_intra, from = 0)$y, density(data_multi, from = 0)$y)
+
+if (weight_type == 'TE4'){
+	xlim = c(0, 0.04)
+	ylim = c(0, 150)
+	log  = ''
+} else if (weight_type == 'hashtag'){
+	xlim = c(0, 0.02)
+	# ylim = c(0, max(fs))
+	ylim = c(0, 2000)
+	log  = ''
+} else if (weight_type == 'mention-retweet'){
+	xlim = c(0, 0.1)
+	ylim = c(0, 80)
+	log = ''
+}
[…]

### 2014-05-06 paper-for_arxiv/results.tex
Added figure with densities by edge type.
This is to replace the distribution by edge type figure.
Added proportion of each edge type by community.

@@
 
+\begin{table}
+	\caption{The percentage of intra-, inter-, and multi-edges associated with the coverings for each of the four community types.}
+	\centering
+	\begin{tabular}{l | r r r}
+		Community Type & Intra & Inter & Multi \\
+		\hline
+		Structural & 7.5 & 87.0 &  5.5 \\
+		Activity-based & 10.7 & 81.9 & 7.4 \\
+		Topic-based & 7.3 & 89.0  & 3.7 \\
+		Interaction-based & 42.3 & 47.9 & 9.8
+	\end{tabular}
+\end{table}
+
 Each community type (Structural, Activity-based, Topic-based, Interaction-based) induces a different partition of the edges, and each edge type (Transfer Entropy, Hashtag, Mention-Retweet) induces a different distribution of weights.
@@
 
+\begin{figure}[!h]
+	\centering
+	\includegraphics[width=1\textwidth]{densities-edges.eps}
+	\caption{The density of edge weights for different community types (rows) and weight types (columns).
+The red,  blue, and magenta values below each collection of densities indicate the median of weight on intra-, inter-, and multi-edges, respectively.}
+	\label{Fig-distributions_by_types}
+\end{figure}
+
 We also note that the distribution of transfer entropy weights always tend to be higher for edges crossing community boundaries (inter- or multi-edges) compared to those edges within community boundaries (intra-edges).

### 2014-05-06 code/count_edge_types.py

@@ -1,0 +1,35 @@
+# A script to count the number of 
+# intra-, inter-, and multi-edges
+# induced by each community type.
+
+# DMD, 6 May 2014
+
+import sys
+import numpy
+
+output = sys.stdout
+
+weight_type = 'hashtag'
+
+for label_type in ['struc', 'TE4', 'hashtag', 'mention-retweet']:
+	print 'Considering communities defined by {}...'.format(label_type)
+
+	count_edge_types = numpy.zeros(3)
+
+	for edge_ind, edge_type in enumerate(['intra', 'inter', 'multi']):
+		prefix = 'interintramulti_labels-{}_weights-{}'.format(label_type, weight_type)
+
+		with open('../data/edges-by-type/{}_{}.dat'.format(prefix, edge_type)) as ofile:
+			counter = 0
+			for line in ofile:
+				counter+=1
+
+			count_edge_types[edge_ind] = counter
+
+		output.write('{}\t{}\t{}\n'.format(counter, label_type, edge_type))
+
+	print 'Total number of edges = {}'.format(int(numpy.sum(count_edge_types)))
+
+	print label_type, count_edge_types/numpy.sum(count_edge_types)
+
+	print ''

### 2014-05-09 Infomap-0.15.1/src/infomap/FlowNetwork.cpp
Added Infomap community detection results

@@ -1,0 +1,272 @@
+/**********************************************************************************
+
+ Infomap software package for multi-level network clustering
+
+ Copyright (c) 2013 Daniel Edler, Martin Rosvall
+ 
+ For more information, see <http://www.mapequation.org>
+ 
+
+ This file is part of Infomap software package.
+
+ Infomap software package is free software: you can redistribute it and/or modify
+ it under the terms of the GNU Affero General Public License as published by
+ the Free Software Foundation, either version 3 of the License, or
+ (at your option) any later version.
+
+ Infomap software package is distributed in the hope that it will be useful,
+ but WITHOUT ANY WARRANTY; without even the implied warranty of
+ MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ GNU Affero General Public License for more details.
+
+ You should have received a copy of the GNU Affero General Public License
+ along with Infomap software package.  If not, see <http://www.gnu.org/licenses/>.
+
+**********************************************************************************/
+
+
+#include "FlowNetwork.h"
+#include <iostream>
+#include <cmath>
+
+FlowNetwork::FlowNetwork()
+{
+}
+
+FlowNetwork::~FlowNetwork()
+{
+}
+
+void FlowNetwork::calculateFlow(const Network& network, const Config& config)
+{
+	std::cout << "Calculating global flow... ";
+
+	// Prepare data in sequence containers for fast access of individual elements
+	unsigned int numNodes = network.numNodes();
+	m_nodeOutDegree.assign(numNodes, 0);
+	m_sumLinkOutWeight.assign(numNodes, 0.0);
+	m_nodeFlow.assign(numNodes, 0.0);
+	m_nodeTeleportRates.assign(numNodes, 0.0);
+
+	const LinkMap& linkMap = network.linkMap();
+	unsigned int numLinks = network.numLinks();
+	m_flowLinks.resize(numLinks);
+	double totalLinkWeight = network.totalLinkWeight();
[…]

### 2014-05-09 Infomap-0.15.1/src/infomap/FlowNetwork.h

@@ -1,0 +1,83 @@
+/**********************************************************************************
+
+ Infomap software package for multi-level network clustering
+
+ Copyright (c) 2013 Daniel Edler, Martin Rosvall
+ 
+ For more information, see <http://www.mapequation.org>
+ 
+
+ This file is part of Infomap software package.
+
+ Infomap software package is free software: you can redistribute it and/or modify
+ it under the terms of the GNU Affero General Public License as published by
+ the Free Software Foundation, either version 3 of the License, or
+ (at your option) any later version.
+
+ Infomap software package is distributed in the hope that it will be useful,
+ but WITHOUT ANY WARRANTY; without even the implied warranty of
+ MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ GNU Affero General Public License for more details.
+
+ You should have received a copy of the GNU Affero General Public License
+ along with Infomap software package.  If not, see <http://www.gnu.org/licenses/>.
+
+**********************************************************************************/
+
+
+#ifndef FLOWNETWORK_H_
+#define FLOWNETWORK_H_
+
+#include <string>
+#include <map>
+#include <vector>
+#include <utility>
+#include "Network.h"
+#include "../io/Config.h"
+
+class FlowNetwork
+{
+public:
+	struct Link
+	{
+		Link(unsigned int sourceIndex = 0, unsigned int targetIndex = 0, double weight = 0.0) :
+			source(sourceIndex),
+			target(targetIndex),
+			weight(weight),
+			flow(weight)
+		{}
+		Link(const Link& other) :
+			source(other.source),
+			target(other.target),
+			weight(other.weight),
+			flow(other.flow)
+		{}
+		unsigned int source;
+		unsigned int target;
+		double weight;
+		double flow;
+	};
+
+	typedef Network::LinkMap										LinkMap;
+	typedef std::vector<Link>										LinkVec;
+
+	FlowNetwork();
+	virtual ~FlowNetwork();
+
+	virtual void calculateFlow(const Network& network, const Config& config);
+
+	const std::vector<double>& getNodeFlow() const { return m_nodeFlow; }
+	const std::vector<double>& getNodeTeleportRates() const { return m_nodeTeleportRates; }
+	const LinkVec& getFlowLinks() const { return m_flowLinks; }
+
+protected:
+
[…]

### 2014-05-09 Infomap-0.15.1/src/infomap/InfomapBase.cpp

@@ -1,0 +1,1722 @@
+/**********************************************************************************
+
+ Infomap software package for multi-level network clustering
+
+ Copyright (c) 2013 Daniel Edler, Martin Rosvall
+ 
+ For more information, see <http://www.mapequation.org>
+ 
+
+ This file is part of Infomap software package.
+
+ Infomap software package is free software: you can redistribute it and/or modify
+ it under the terms of the GNU Affero General Public License as published by
+ the Free Software Foundation, either version 3 of the License, or
+ (at your option) any later version.
+
+ Infomap software package is distributed in the hope that it will be useful,
+ but WITHOUT ANY WARRANTY; without even the implied warranty of
+ MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ GNU Affero General Public License for more details.
+
+ You should have received a copy of the GNU Affero General Public License
+ along with Infomap software package.  If not, see <http://www.gnu.org/licenses/>.
+
+**********************************************************************************/
+
+
+#include "InfomapBase.h"
+#include "../utils/Logger.h"
+#include <algorithm>
+#include "../utils/FileURI.h"
+#include "../io/SafeFile.h"
+#include "../io/TreeDataWriter.h"
+#include <cmath>
+#include "../io/ClusterReader.h"
+#include <limits>
+#include <sstream>
+#include <iomanip>
+#include "../utils/infomath.h"
+#include "../io/convert.h"
+#include "../utils/Stopwatch.h"
+#include "MemFlowNetwork.h"
+#include "MemNetwork.h"
+#include "MultiplexNetwork.h"
+#ifdef _OPENMP
+#include <omp.h>
+#include <stdio.h>
+#endif
+#include <map>
+#include "../utils/Date.h"
+#include "Network.h"
+#include "FlowNetwork.h"
+#include "../io/version.h"
+#include <functional>
+
+void InfomapBase::run()
+{
+	DEBUG_OUT("InfomapBase::run()..." << std::endl);
+	ASSERT(m_subLevel == 0);
+
+#ifdef _OPENMP
[…]

### 2014-05-09 Infomap-0.15.1/src/infomap/InfomapContext.cpp

@@ -1,0 +1,65 @@
+/**********************************************************************************
+
+ Infomap software package for multi-level network clustering
+
+ Copyright (c) 2013 Daniel Edler, Martin Rosvall
+ 
+ For more information, see <http://www.mapequation.org>
+ 
+
+ This file is part of Infomap software package.
+
+ Infomap software package is free software: you can redistribute it and/or modify
+ it under the terms of the GNU Affero General Public License as published by
+ the Free Software Foundation, either version 3 of the License, or
+ (at your option) any later version.
+
+ Infomap software package is distributed in the hope that it will be useful,
+ but WITHOUT ANY WARRANTY; without even the implied warranty of
+ MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ GNU Affero General Public License for more details.
+
+ You should have received a copy of the GNU Affero General Public License
+ along with Infomap software package.  If not, see <http://www.gnu.org/licenses/>.
+
+**********************************************************************************/
+
+
+#include "InfomapContext.h"
+#include "flowData_traits.h"
+#include "InfomapGreedyTypeSpecialized.h"
+
+// InfomapFactory::create(const Config& config)
+// {
+// 	if (config.isUndirected())
+// 		return std::auto_ptr<InfomapBase>(new InfomapGreedySpecialized<InfomapType<FlowUndirected, WithMemory> >(m_config));
+// 	if (m_config.undirdir || m_config.outdirdir || m_config.rawdir)
+// 		return std::auto_ptr<InfomapBase>(new InfomapGreedySpecialized<InfomapType<FlowDirectedNonDetailedBalance, WithMemory> >(m_config));
+// 	if (m_config.recordedTeleportation)
+// 		return std::auto_ptr<InfomapBase>(new InfomapGreedySpecialized<InfomapType<FlowDirectedWithTeleportation, WithMemory> >(m_config));
+// 	// unrecorded teleportation
+// 	return std::auto_ptr<InfomapBase>(new InfomapGreedySpecialized<InfomapType<FlowDirectedNonDetailedBalanceWithTeleportation, WithMemory> >(m_config));
+
+// }
+
+InfomapContext::InfomapContext(const Config& config)
+: m_config(config)
+{
+	if (config.isMemoryNetwork())
[…]

### 2014-05-09 Infomap-0.15.1/src/infomap/InfomapGreedy.h

@@ -1,0 +1,683 @@
+/**********************************************************************************
+
+ Infomap software package for multi-level network clustering
+
+ Copyright (c) 2013 Daniel Edler, Martin Rosvall
+ 
+ For more information, see <http://www.mapequation.org>
+ 
+
+ This file is part of Infomap software package.
+
+ Infomap software package is free software: you can redistribute it and/or modify
+ it under the terms of the GNU Affero General Public License as published by
+ the Free Software Foundation, either version 3 of the License, or
+ (at your option) any later version.
+
+ Infomap software package is distributed in the hope that it will be useful,
+ but WITHOUT ANY WARRANTY; without even the implied warranty of
+ MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ GNU Affero General Public License for more details.
+
+ You should have received a copy of the GNU Affero General Public License
+ along with Infomap software package.  If not, see <http://www.gnu.org/licenses/>.
+
+**********************************************************************************/
+
+
+#ifndef INFOMAPGREEDY_H_
+#define INFOMAPGREEDY_H_
+#include "InfomapBase.h"
+#include "Node.h"
+#include "NodeFactory.h"
+#include "flowData_traits.h"
+#include "../utils/Logger.h"
+#include "../utils/infomath.h"
+#include <map>
+#include <utility>
+#include "../io/TreeDataWriter.h"
+#include "../utils/FileURI.h"
+#include "../utils/types.h"
+#include "../io/SafeFile.h"
+#include <sstream>
+#include <iomanip>
+#include "../io/convert.h"
+#include "../io/HierarchicalNetwork.h"
+#include <deque>
+#include <functional>
+#include "../io/version.h"
+
+
+template<typename InfomapImplementation>
+class InfomapGreedy : public InfomapBase
+{
+public:
+	typedef typename derived_traits<InfomapImplementation>::flow_type	FlowType;
+	typedef typename flowData_traits<FlowType>::detailed_balance_type 	DetailedBalanceType;
[…]

### 2014-05-09 Infomap-0.15.1/src/infomap/InfomapGreedyCommon.h

@@ -1,0 +1,691 @@
+/**********************************************************************************
+
+ Infomap software package for multi-level network clustering
+
+ Copyright (c) 2013 Daniel Edler, Martin Rosvall
+ 
+ For more information, see <http://www.mapequation.org>
+ 
+
+ This file is part of Infomap software package.
+
+ Infomap software package is free software: you can redistribute it and/or modify
+ it under the terms of the GNU Affero General Public License as published by
+ the Free Software Foundation, either version 3 of the License, or
+ (at your option) any later version.
+
+ Infomap software package is distributed in the hope that it will be useful,
+ but WITHOUT ANY WARRANTY; without even the implied warranty of
+ MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ GNU Affero General Public License for more details.
+
+ You should have received a copy of the GNU Affero General Public License
+ along with Infomap software package.  If not, see <http://www.gnu.org/licenses/>.
+
+**********************************************************************************/
+
+
+#ifndef INFOMAPGREEDYCOMMON_H_
+#define INFOMAPGREEDYCOMMON_H_
+#include "InfomapGreedySpecialized.h"
+#include <memory>
+
+
+template<typename InfomapGreedyDerivedType>
+class InfomapGreedyCommon : public InfomapGreedySpecialized<typename derived_traits<InfomapGreedyDerivedType>::flow_type>
+{
+	typedef typename derived_traits<InfomapGreedyDerivedType>::flow_type				FlowType;
+	// typedef FlowDirectedNonDetailedBalance 												FlowType; // DEBUG!!
+	typedef InfomapGreedySpecialized<FlowType>							Super;
+	typedef typename flowData_traits<FlowType>::detailed_balance_type 	DetailedBalanceType;
+	typedef typename flowData_traits<FlowType>::directed_with_recorded_teleportation_type DirectedWithRecordedTeleportationType;
+	typedef typename flowData_traits<FlowType>::teleportation_type 		TeleportationType;
+	typedef typename flowData_traits<FlowType>::is_directed_type		IsDirectedType;
[…]

### 2014-05-09 Infomap-0.15.1/src/infomap/InfomapGreedySpecialized.h

@@ -1,0 +1,475 @@
+/**********************************************************************************
+
+ Infomap software package for multi-level network clustering
+
+ Copyright (c) 2013 Daniel Edler, Martin Rosvall
+ 
+ For more information, see <http://www.mapequation.org>
+ 
+
+ This file is part of Infomap software package.
+
+ Infomap software package is free software: you can redistribute it and/or modify
+ it under the terms of the GNU Affero General Public License as published by
+ the Free Software Foundation, either version 3 of the License, or
+ (at your option) any later version.
+
+ Infomap software package is distributed in the hope that it will be useful,
+ but WITHOUT ANY WARRANTY; without even the implied warranty of
+ MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ GNU Affero General Public License for more details.
+
+ You should have received a copy of the GNU Affero General Public License
+ along with Infomap software package.  If not, see <http://www.gnu.org/licenses/>.
+
+**********************************************************************************/
+
+
+#ifndef INFOMAPGREEDYSPECIALIZED_H_
+#define INFOMAPGREEDYSPECIALIZED_H_
+#include "InfomapGreedy.h"
+
+struct DeltaFlow;
+
+template<typename FlowType>
+class InfomapGreedySpecialized : public InfomapGreedy<InfomapGreedySpecialized<FlowType> >
+{
+	friend class InfomapGreedy<InfomapGreedySpecialized<FlowType> >;
+	typedef InfomapGreedySpecialized<FlowType>							SelfType;
+	typedef InfomapGreedy<SelfType>										Super;
+	typedef typename flowData_traits<FlowType>::detailed_balance_type 	DetailedBalanceType;
+	typedef typename flowData_traits<FlowType>::directed_with_recorded_teleportation_type DirectedWithRecordedTeleportationType;
+	typedef typename flowData_traits<FlowType>::teleportation_type 		TeleportationType;
+	typedef MemNode<FlowType>											NodeType;
[…]

### 2014-05-09 Infomap-0.15.1/src/infomap/InfomapGreedyTypeSpecialized.h

@@ -1,0 +1,653 @@
+/**********************************************************************************
+
+ Infomap software package for multi-level network clustering
+
+ Copyright (c) 2013 Daniel Edler, Martin Rosvall
+ 
+ For more information, see <http://www.mapequation.org>
+ 
+
+ This file is part of Infomap software package.
+
+ Infomap software package is free software: you can redistribute it and/or modify
+ it under the terms of the GNU Affero General Public License as published by
+ the Free Software Foundation, either version 3 of the License, or
+ (at your option) any later version.
+
+ Infomap software package is distributed in the hope that it will be useful,
+ but WITHOUT ANY WARRANTY; without even the implied warranty of
+ MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ GNU Affero General Public License for more details.
+
+ You should have received a copy of the GNU Affero General Public License
+ along with Infomap software package.  If not, see <http://www.gnu.org/licenses/>.
+
+**********************************************************************************/
+
+
+#ifndef INFOMAPGREEDYTYPESPECIALIZED_H_
+#define INFOMAPGREEDYTYPESPECIALIZED_H_
+#include "InfomapGreedyCommon.h"
+#include "../io/version.h"
+
+template<typename FlowType, typename NetworkType>
+class InfomapGreedyTypeSpecialized : public InfomapGreedyCommon<InfomapGreedyTypeSpecialized<FlowType, NetworkType> >
+{
+	friend class InfomapGreedyCommon<InfomapGreedyTypeSpecialized<FlowType, NetworkType> >;
+	typedef InfomapGreedyCommon<InfomapGreedyTypeSpecialized<FlowType, NetworkType> >		Super;
+	typedef typename flowData_traits<FlowType>::detailed_balance_type 						DetailedBalanceType;
+	typedef typename flowData_traits<FlowType>::directed_with_recorded_teleportation_type 	DirectedWithRecordedTeleportationType;
+	typedef typename flowData_traits<FlowType>::teleportation_type 							TeleportationType;
[…]

### 2014-05-09 Infomap-0.15.1/src/infomap/MemFlowNetwork.h

@@ -1,0 +1,47 @@
+/**********************************************************************************
+
+ Infomap software package for multi-level network clustering
+
+ Copyright (c) 2013 Daniel Edler, Martin Rosvall
+
+ For more information, see <http://www.mapequation.org>
+
+
+ This file is part of Infomap software package.
+
+ Infomap software package is free software: you can redistribute it and/or modify
+ it under the terms of the GNU Affero General Public License as published by
+ the Free Software Foundation, either version 3 of the License, or
+ (at your option) any later version.
+
+ Infomap software package is distributed in the hope that it will be useful,
+ but WITHOUT ANY WARRANTY; without even the implied warranty of
+ MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ GNU Affero General Public License for more details.
+
+ You should have received a copy of the GNU Affero General Public License
+ along with Infomap software package.  If not, see <http://www.gnu.org/licenses/>.
+
+**********************************************************************************/
+
+
+#ifndef MEMFLOWNETWORK_H_
+#define MEMFLOWNETWORK_H_
+
+#include "FlowNetwork.h"
+#include "MemNetwork.h"
+
+class MemFlowNetwork: public FlowNetwork {
+public:
+	MemFlowNetwork();
+	virtual ~MemFlowNetwork();
+
+	virtual void calculateFlow(const Network& network, const Config& config);
+
+	const std::vector<M2Node>& getM2Nodes() const { return m_m2nodes; }
+
+protected:
+	std::vector<M2Node> m_m2nodes;
+};
+
+#endif /* MEMFLOWNETWORK_H_ */

### 2014-05-09 Infomap-0.15.1/src/infomap/MemNetwork.h

@@ -1,0 +1,233 @@
+/**********************************************************************************
+
+ Infomap software package for multi-level network clustering
+
+ Copyright (c) 2013 Daniel Edler, Martin Rosvall
+
+ For more information, see <http://www.mapequation.org>
+
+
+ This file is part of Infomap software package.
+
+ Infomap software package is free software: you can redistribute it and/or modify
+ it under the terms of the GNU Affero General Public License as published by
+ the Free Software Foundation, either version 3 of the License, or
+ (at your option) any later version.
+
+ Infomap software package is distributed in the hope that it will be useful,
+ but WITHOUT ANY WARRANTY; without even the implied warranty of
+ MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ GNU Affero General Public License for more details.
+
+ You should have received a copy of the GNU Affero General Public License
+ along with Infomap software package.  If not, see <http://www.gnu.org/licenses/>.
+
+**********************************************************************************/
+
+
+#ifndef MEMNETWORK_H_
+#define MEMNETWORK_H_
+
+#include "Network.h"
+
+#include <map>
+#include <utility>
+#include <deque>
+
+#include "../io/Config.h"
+#include "../utils/types.h"
+using std::map;
+using std::pair;
+
+struct M2Node
+{
+	unsigned int priorState;
+	unsigned int physIndex;
+	M2Node() :
+		priorState(0), physIndex(0)
+	{}
+	M2Node(unsigned int priorState, unsigned int physIndex) :
+		priorState(priorState), physIndex(physIndex)
+	{}
+	M2Node(const M2Node& other) :
+		priorState(other.priorState), physIndex(other.physIndex)
+	{}
+
+	bool operator<(M2Node other) const
+	{
+		return priorState == other.priorState ? physIndex < other.physIndex : priorState < other.priorState;
+	}
+
+	bool operator==(M2Node other) const
+	{
[…]

### 2014-05-09 Infomap-0.15.1/src/infomap/Network.cpp

@@ -1,0 +1,598 @@
+/**********************************************************************************
+
+ Infomap software package for multi-level network clustering
+
+ Copyright (c) 2013 Daniel Edler, Martin Rosvall
+ 
+ For more information, see <http://www.mapequation.org>
+ 
+
+ This file is part of Infomap software package.
+
+ Infomap software package is free software: you can redistribute it and/or modify
+ it under the terms of the GNU Affero General Public License as published by
+ the Free Software Foundation, either version 3 of the License, or
+ (at your option) any later version.
+
+ Infomap software package is distributed in the hope that it will be useful,
+ but WITHOUT ANY WARRANTY; without even the implied warranty of
+ MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ GNU Affero General Public License for more details.
+
+ You should have received a copy of the GNU Affero General Public License
+ along with Infomap software package.  If not, see <http://www.gnu.org/licenses/>.
+
+**********************************************************************************/
+
+
+#include "Network.h"
+#include "../utils/FileURI.h"
+#include "../io/convert.h"
+#include "../io/SafeFile.h"
+#include <cmath>
+#include "../utils/Logger.h"
+#include <cstdlib>
+#include <cstring>
+#include <cstdio>
+
+using std::make_pair;
+
+void Network::readInputData()
+{
+	std::string filename = m_config.networkFile;
+	FileURI networkFilename(filename, false);
+	std::string format = m_config.inputFormat;
+
+	if (format == "")
+	{
+		std::string type = networkFilename.getExtension();
+		if (type == "net")
+			format = "pajek";
+		else if (type == "txt")
+			format = "link-list";
+	}
+	if (format == "")
+		throw UnknownFileTypeError("No known input format specified or implied by file extension.");
+
+	if (format == "pajek")
+		parsePajekNetwork(filename);
+	else if (format == "link-list")
+		parseLinkList(filename);
+	else
[…]

### 2014-05-09 Infomap-0.15.1/src/infomap/flowData.h

@@ -1,0 +1,391 @@
+/**********************************************************************************
+
+ Infomap software package for multi-level network clustering
+
+ Copyright (c) 2013 Daniel Edler, Martin Rosvall
+ 
+ For more information, see <http://www.mapequation.org>
+ 
+
+ This file is part of Infomap software package.
+
+ Infomap software package is free software: you can redistribute it and/or modify
+ it under the terms of the GNU Affero General Public License as published by
+ the Free Software Foundation, either version 3 of the License, or
+ (at your option) any later version.
+
+ Infomap software package is distributed in the hope that it will be useful,
+ but WITHOUT ANY WARRANTY; without even the implied warranty of
+ MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ GNU Affero General Public License for more details.
+
+ You should have received a copy of the GNU Affero General Public License
+ along with Infomap software package.  If not, see <http://www.gnu.org/licenses/>.
+
+**********************************************************************************/
+
+
+#ifndef FLOWDATA_H_
+#define FLOWDATA_H_
+#include <ostream>
+
+struct FlowUndirected
+{
+	FlowUndirected(double flow = 1.0, double teleportWeight = 1.0) :
+		flow(flow),
+		exitFlow(0.0),
+		enterFlow(exitFlow)
+	{}
+	FlowUndirected(const FlowUndirected& other) :
+		flow(other.flow),
+		exitFlow(other.exitFlow),
+		enterFlow(exitFlow)
+	{}
+	FlowUndirected& operator=(const FlowUndirected& other)
+	{
+		flow = other.flow;
+		exitFlow = other.exitFlow;
+		return *this;
+	}
+
+	double flow;
+	double exitFlow;
+	double& enterFlow;
+
+	FlowUndirected& operator+=(const FlowUndirected& other)
+	{
+		flow += other.flow;
+		exitFlow += other.exitFlow;
+		return *this;
+	}
+
+	FlowUndirected& operator-=(const FlowUndirected& other)
+	{
+		flow -= other.flow;
+		exitFlow -= other.exitFlow;
[…]

### 2014-05-09 Infomap-0.15.1/src/infomap/flowData_traits.h

@@ -1,0 +1,148 @@
+/**********************************************************************************
+
+ Infomap software package for multi-level network clustering
+
+ Copyright (c) 2013 Daniel Edler, Martin Rosvall
+ 
+ For more information, see <http://www.mapequation.org>
+ 
+
+ This file is part of Infomap software package.
+
+ Infomap software package is free software: you can redistribute it and/or modify
+ it under the terms of the GNU Affero General Public License as published by
+ the Free Software Foundation, either version 3 of the License, or
+ (at your option) any later version.
+
+ Infomap software package is distributed in the hope that it will be useful,
+ but WITHOUT ANY WARRANTY; without even the implied warranty of
+ MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ GNU Affero General Public License for more details.
+
+ You should have received a copy of the GNU Affero General Public License
+ along with Infomap software package.  If not, see <http://www.gnu.org/licenses/>.
+
+**********************************************************************************/
+
+
+#ifndef FLOWDATA_TRAITS_H_
+#define FLOWDATA_TRAITS_H_
+#include "flowData.h"
+
+// A boolean type as function templates can't be partially specialized.
+template<bool> struct bool2type {};
+
+struct WithMemory {};
+struct WithoutMemory {};
+
+struct DetailedBalance {};
+struct NoDetailedBalance {};
+
+struct WithTeleportation {};
+struct WithRecordedTeleportation {};
+struct WithUnrecordedTeleportation {};
+struct WithoutTeleportation {};
+
+struct Directed {};
+struct Undirected {};
+
+struct DirectedWithRecordedTeleportation {};
+struct NotDirectedWithRecordedTeleportation {};
+
+struct true_type { operator bool() const { return true; }};
+struct false_type { operator bool() const { return false; }};
+
+template<typename FlowType, typename NetworkType>
+struct InfomapType
+{
+	typedef FlowType	flow_type;
+	typedef NetworkType	network_type;
+};
+
+
+template<typename InfomapType>
+struct flowData_traits;
+
+template<>
+struct flowData_traits<FlowUndirected>
+{
+	typedef DetailedBalance								detailed_balance_type;
+	typedef NotDirectedWithRecordedTeleportation		directed_with_recorded_teleportation_type;
[…]

### 2014-05-09 Infomap-0.15.1/src/io/HierarchicalNetwork.h

@@ -1,0 +1,558 @@
+/**********************************************************************************
+
+ Infomap software package for multi-level network clustering
+
+ Copyright (c) 2013 Daniel Edler, Martin Rosvall
+ 
+ For more information, see <http://www.mapequation.org>
+ 
+
+ This file is part of Infomap software package.
+
+ Infomap software package is free software: you can redistribute it and/or modify
+ it under the terms of the GNU Affero General Public License as published by
+ the Free Software Foundation, either version 3 of the License, or
+ (at your option) any later version.
+
+ Infomap software package is distributed in the hope that it will be useful,
+ but WITHOUT ANY WARRANTY; without even the implied warranty of
+ MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ GNU Affero General Public License for more details.
+
+ You should have received a copy of the GNU Affero General Public License
+ along with Infomap software package.  If not, see <http://www.gnu.org/licenses/>.
+
+**********************************************************************************/
+
+
+#ifndef HIERARCHICALNETWORK_H_
+#define HIERARCHICALNETWORK_H_
+
+#include <vector>
+#include <map>
+#include <iostream>
+#include <sstream>
+#include <fstream>
+#include <ios>
+#include <deque>
+#include <algorithm>
+#include <set>
+#include <functional>   // std::greater
+#include <limits>
+#include "SafeFile.h"
+
+enum EdgeAggregationPolicy { NONE, PARTIAL, FULL };
+
+//static const unsigned int SIZE_OF_UNSIGNED_INT = sizeof(unsigned int);		// 4 byte (32 bit)
+//static const unsigned int SIZE_OF_CHAR = sizeof(char);						// 1 byte (8 bit)
+//static const unsigned int SIZE_OF_FLOAT = sizeof(float); 					// 4 byte (32 bit)
+//static const unsigned int SIZE_OF_UNSIGNED_SHORT = sizeof(unsigned short);	// 2 byte (16 bit)
+
+namespace SerialTypes {
+	typedef unsigned short nameSize_t;
+	typedef float flow_t;
+	typedef unsigned int childSize_t;
+	typedef unsigned int childPos_t;
[…]

### 2014-05-09 Infomap-0.15.1/src/io/SafeFile.h

@@ -1,0 +1,268 @@
+/**********************************************************************************
+
+ Infomap software package for multi-level network clustering
+
+ Copyright (c) 2013 Daniel Edler, Martin Rosvall
+ 
+ For more information, see <http://www.mapequation.org>
+ 
+
+ This file is part of Infomap software package.
+
+ Infomap software package is free software: you can redistribute it and/or modify
+ it under the terms of the GNU Affero General Public License as published by
+ the Free Software Foundation, either version 3 of the License, or
+ (at your option) any later version.
+
+ Infomap software package is distributed in the hope that it will be useful,
+ but WITHOUT ANY WARRANTY; without even the implied warranty of
+ MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ GNU Affero General Public License for more details.
+
+ You should have received a copy of the GNU Affero General Public License
+ along with Infomap software package.  If not, see <http://www.gnu.org/licenses/>.
+
+**********************************************************************************/
+
+
+#ifndef SAFEFILE_H_
+#define SAFEFILE_H_
+#include <iostream>
+#include <fstream>
+#include <ios>
+#include <stdexcept>
+#include "convert.h"
+#include <cstdio>
+
+using std::ifstream;
+using std::ofstream;
+
+class FileOpenError : public std::runtime_error {
+public:
+	FileOpenError(std::string const& s)
+	: std::runtime_error(s)
+	{ }
+};
+
+/**
+ * A wrapper for the C++ file stream class that automatically closes
+ * the file stream when the destructor is called. Allocate it on the
+ * stack to have it automatically closed when going out of scope.
+ *
+ * Note:
+ * In C++, the only code that can be guaranteed to be executed after an
+ * exception is thrown are the destructors of objects residing on the stack.
+ *
+ * You can exploit that fact to avoid resource leaks by tying all resources
+ * to the lifespan of an object allocated on the stack. This technique is
+ * called Resource Acquisition Is Initialization (RAII).
+ *
+ */
+class SafeInFile : public ifstream
+{
+public:
[…]

### 2014-05-09 Infomap-0.15.1/src/io/convert.h

@@ -1,0 +1,152 @@
+/**********************************************************************************
+
+ Infomap software package for multi-level network clustering
+
+ Copyright (c) 2013 Daniel Edler, Martin Rosvall
+ 
+ For more information, see <http://www.mapequation.org>
+ 
+
+ This file is part of Infomap software package.
+
+ Infomap software package is free software: you can redistribute it and/or modify
+ it under the terms of the GNU Affero General Public License as published by
+ the Free Software Foundation, either version 3 of the License, or
+ (at your option) any later version.
+
+ Infomap software package is distributed in the hope that it will be useful,
+ but WITHOUT ANY WARRANTY; without even the implied warranty of
+ MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ GNU Affero General Public License for more details.
+
+ You should have received a copy of the GNU Affero General Public License
+ along with Infomap software package.  If not, see <http://www.gnu.org/licenses/>.
+
+**********************************************************************************/
+
+
+#ifndef CONVERT_H_
+#define CONVERT_H_
+
+#include <iostream>
+#include <sstream>
+#include <string>
+#include <stdexcept>
+
+class AbortAndHelp : public std::runtime_error {
+public:
+	AbortAndHelp(std::string const& s) : std::runtime_error(s) { }
+};
+
+class InputSyntaxError : public std::runtime_error {
+public:
+	InputSyntaxError(std::string const& s) : std::runtime_error(s) { }
+};
+
+class UnknownFileTypeError : public std::runtime_error {
+public:
+	UnknownFileTypeError(std::string const& s) : std::runtime_error(s) { }
+};
+
+class FileFormatError : public std::runtime_error {
+public:
+	FileFormatError(std::string const& s) : std::runtime_error(s) { }
+};
+
+class InputDomainError : public std::runtime_error {
+public:
+	InputDomainError(std::string const& s) : std::runtime_error(s) { }
+};
+
+class BadConversionError : public std::runtime_error {
+public:
+	BadConversionError(std::string const& s) : std::runtime_error(s) { }
+};
+
+class MisMatchError : public std::runtime_error {
+public:
+	MisMatchError(std::string const& s) : std::runtime_error(s) { }
+};
+
+class InternalOrderError : public std::logic_error {
+public:
[…]

### 2014-05-09 Infomap-0.15.1/src/io/version.cpp

@@ -1,0 +1,30 @@
+/**********************************************************************************
+
+ Infomap software package for multi-level network clustering
+
+ Copyright (c) 2013 Daniel Edler, Martin Rosvall
+ 
+ For more information, see <http://www.mapequation.org>
+ 
+
+ This file is part of Infomap software package.
+
+ Infomap software package is free software: you can redistribute it and/or modify
+ it under the terms of the GNU Affero General Public License as published by
+ the Free Software Foundation, either version 3 of the License, or
+ (at your option) any later version.
+
+ Infomap software package is distributed in the hope that it will be useful,
+ but WITHOUT ANY WARRANTY; without even the implied warranty of
+ MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ GNU Affero General Public License for more details.
+
+ You should have received a copy of the GNU Affero General Public License
+ along with Infomap software package.  If not, see <http://www.gnu.org/licenses/>.
+
+**********************************************************************************/
+
+
+#include "version.h"
+
+const char* INFOMAP_VERSION = "0.15.1";

### 2014-06-14 code/determine_edge_weights_with_bar.py
finished prediction code

@@ -19,8 +19,13 @@ Testuid1 = '456'
 Testuid2 = '237962820'
 Testuid3 = '243494256'
 strangeuid ='51319087'
+#Split Time "Start at 2011/4/25 9am and stop at 2011/5/23 9am."
 reference_start = datetime.datetime(2011, 4, 25, 9, 24, 58)
+prediction_splitpoint = datetime.datetime(2011,5,23,9,0,0)
+
 reference_stop = datetime.datetime(2011, 6, 25, 14, 31, 59)
+
+
 #SPARSE_BINARY_HISTORY_PICKLE ="../data/tweet_times_2011/sparse_binary_ts_dict_bin-space-of-10min.p"
 #SPARSE_BINARY_HISTORY_PICKLE ="../data/tweet_times_2011/sparse_binary_ts_dict_bin-space-of-1.p"
 #SPARSE_BINARY_HISTORY_PICKLE ="test_histories_factor_600.p"
@@ -30,19 +35,29 @@ reference_stop = datetime.datetime(2011, 6, 25, 14, 31, 59)
 #SPARSE_BINARY_HISTORY_PICKLE = "../data/tweet_times_2011/sparse_binary_ts_dict_bin-space-of-1hour_set_version.p"
 #SPARSE_BINARY_HISTORY_PICKLE = "../data/tweet_times_2011/sparse_binary_ts_dict_bin-space-of-2hour_set_version.p"
 #SPARSE_BINARY_HISTORY_PICKLE ="../data/tweet_times_2011/sparse_binary_ts_dict_bin-space-of-1w75percentofTS.p"
-SPARSE_BINARY_HISTORY_PICKLE ="../data/tweet_times_2011/sparse_binary_ts_dict_bin-space-of-10Min_75PercentOfTimeSeries_set_version.p"
-T = (reference_stop - reference_start).total_seconds()
-predictTCutOff = T*.75
+#SPARSE_BINARY_HISTORY_PICKLE ="../data/tweet_times_2011/sparse_binary_ts_dict_bin-space-of-10Min_75PercentOfTimeSeries_set_version.p"
+#SPARSE_BINARY_HISTORY_PICKLE="../data/tweet_times_2011/sparse_binary_ts_dict_bin-space-of-1wfirsthalf.p"
+SPARSE_BINARY_HISTORY_PICKLE= "../data/tweet_times_2011/sparse_binary_ts_dict_bin-space-of-1wsecondhalf.p"
[…]

### 2014-06-15 paper-for_arxiv/results.tex
Minor changes to paper.

--- 2014-04-30 paper-for_arxiv/results.tex
@@
 		\text{Intra-edge} &: \ \ \ M_{u} = M_{f}\\
-		\text{Multi-edge} &: \ \ \ \text{ otherwise} \\
+		\text{Mixed-edge} &: \ \ \ \text{ otherwise} \\
 	\end{array}\right. \label{Eqn-edge_types}.
 \end{align}
-In words, an inter-edge connects two users who share no community memberships, an intra-edge connects two users who each belong to the same communities, and a multi-edge connects two users who share some, but not all, community memberships.
-Thus, inter-edges cross community boundaries, intra-edges lie within community boundaries, and multi-edges lie at the borders of community boundaries.
+In words, an inter-edge connects two users who share no community memberships, an intra-edge connects two users who each belong to the same communities, and a mixed-edge connects two users who share some, but not all, community memberships.
+Thus, inter-edges cross community boundaries, intra-edges lie within community boundaries, and mixed-edges lie at the borders of community boundaries.
 See Figure~\ref{Fig-edge_types} for a schematic of this edge partitioning.
@@
 	\includegraphics[width=0.8\textwidth]{edge-types.pdf}
-	\caption{A schematic of how, given a covering, the edges of the network can be partitioned using \ref{Eqn-edge_types} into inter-edges, intra-edges, and multi-edges.
+	\caption{A schematic of how, given a covering, the edges of the network can be partitioned using \ref{Eqn-edge_types} into inter-edges, intra-edges, and mixed-edges.
 Inter-edges (red) cross community boundaries.
 Intra-edges (blue) remain inside community boundaries.
-Multi-edges (purple) both remain in and cross community boundaries due to overlap in community membership.
+Mixed-edges (purple) both remain in and cross community boundaries due to overlap in community membership.
 Each column corresponds to the same collection of weights, but partitioned using a different covering.
@@
 \end{figure}
+
+\begin{table}
+	\caption{The percentage of intra-, inter-, and mixed-edges associated with the coverings for each of the four community types.}
+	\centering
+	\begin{tabular}{l | r r r}
+		Community Type & Intra & Inter & Mixed \\
+		\hline
+		Structural & 7.5 & 87.0 &  5.5 \\
+		Activity-based & 10.7 & 81.9 & 7.4 \\
+		Topic-based & 7.3 & 89.0  & 3.7 \\
+		Interaction-based & 42.3 & 47.9 & 9.8
+	\end{tabular}
+\end{table}
 
@@
 \end{align}
-the empirical distribution over the edge weights conditioned on $t$ being one of inter, intra, and multi.
+the empirical distribution over the edge weights conditioned on $t$ being one of inter, intra, and mixed.
 For meaningful community structure, we expect the distribution of edge weights to differ with the edge type $t$.
 If the community structure were arbitrary, the edge weights would be independent of the edge type, and all three conditional distributions would be identical.
-These distributions are shown in Figure~\ref{Fig-distributions_by_types}.
+The densities associated with these distributions are shown in Figure~\ref{Fig-distributions_by_types}.
 
-Each \emph{column} of Figure~\ref{Fig-distributions_by_types} demonstrates how the distribution of weights change with the community type used to induce the partition.
-For example, the second column shows how the distributions of hashtag weights change based on the community partition.
-In general, the distributions differ in non-trivial ways across the edge types and coverings.
+Each \emph{column} of Figure~\ref{Fig-distributions_by_types} demonstrates how the density of weights change with the community type used to induce the partition.
+For example, the second column shows how the density of hashtag weights change based on the community partition.
+In general, the densities differ in non-trivial ways across the edge types and coverings.
 However, we see that the medians of the distributions provide a useful summary statistic.
-Under each collection of distribution functions, we list the median value of the inter, intra, and multi-edges in red, blue, and magenta, respectively.
+Under each collection of density functions, we list the median value of the inter, intra, and mixed-edges in red, blue, and magenta, respectively.
 Unsurprisingly, we see that the greatest difference between the distributions occurs when we consider the topic-based communities, since the topic-based communities are determined based on the hashtag weights.
@@
 For example, for the covering corresponding to the activity-based communities, the hashtag weights tend to be higher for edges internal to communities than between communities.
-Similarly, for the covering corresponding to the topic-based communities, the transfer entropy weights tend to be higher on edges within (intra) and between (inter) communities, and lower for edges between members with multiple, non-identical memberships (multi).
+Similarly, for the covering corresponding to the topic-based communities, the transfer entropy weights tend to be higher on edges within (intra) and between (inter) communities, and lower for edges between members with multiple, non-identical memberships (mixed).
+
+% \begin{figure}[!h]
+% 	\centering
+% 	\includegraphics[width=1\textwidth]{distributions-edges.eps}
+% 	\caption{The distribution of edge weights for different community types (rows) and weight types (columns).
+The red,  blue, and magenta values below each distribution indicate the median of weight on intra-, inter-, and mixed-edges, respectively.}
+% 	\label{Fig-distributions_by_types}
+% \end{figure}
 
@@
 	\centering
-	\includegraphics[width=1\textwidth]{distributions-edges.eps}
-	\caption{The distribution of edge weights for different community types (rows) and weight types (columns).
-The red,  blue, and magenta values below each distribution indicate the median of weight on intra-, inter-, and multi-edges, respectively.}
+	\includegraphics[width=1\textwidth]{densities-edges.eps}
+	\caption{The density of edge weights for different community types (rows) and weight types (columns).
+The red,  blue, and magenta values below each collection of densities indicate the median of weight on intra-, inter-, and mixed-edges, respectively.}
 	\label{Fig-distributions_by_types}
@@
 
-We also note that the distribution of transfer entropy weights always tend to be higher for edges crossing community boundaries (inter- or multi-edges) compared to those edges within community boundaries (intra-edges).
+We also note that the distribution of transfer entropy weights always tend to be higher for edges crossing community boundaries (inter- or mixed-edges) compared to those edges within community boundaries (intra-edges).
 This is a property not exhibited by either the hashtag or mention-retweet weights, independent of the covering used to partition the edges.
-Moreover, for all but the activity-based covering, the weights of multi-edges tend to be highest overall.
+Moreover, for all but the activity-based covering, the weights of mixed-edges tend to be highest overall.
 Recall that the transfer entropy $\text{TE}_{X(u) \to X(f)}$ quantifies the reduction in uncertainty about a follower $f$'s activity from knowing the activity of a user $u$.
@@
 Thus, in an information theoretic sense, we see that novel information useful for prediction is more likely to flow \emph{across} community boundaries than \emph{within} community boundaries.
+
+\subsection{Demonstration of the Question-Oriented Appraoch}
+
+\begin{table}
+	\caption{Lorem ipsum.}
+	\centering
+	\begin{tabular}{l | c c}
+		Community Type & Percentage of Retweets Internal & Percentage of Mentions Internal \\
+		\hline
+		Structural & 45.4 & 69.9 \\
+		Activity-based & 54.1 & 72.9 \\
+		Topic-based & 52.3 & 74.1  \\
+		Interaction-based & 64.3 & 81.7
+	\end{tabular}
+\end{table}
 

### 2014-06-16 paper-for_arxiv/results.tex
Minor changes to paper.

@@
 
-\subsection{Demonstration of the Question-Oriented Appraoch}
+\subsection{Demonstration of the Question-Oriented Approach}
+
+Next, we demonstrate a particular instance of a question-oriented approach.
+Suppose we were interested in tracking where conversations occur in a social network.
+That is, we want to track groups of individuals who interact more with each other than with users outside of their group.
+This notion of community naturally falls within our interaction-based framework outlined above.
+We demonstrate how much is gained by tailoring the community detection problem to this question.
+
+% * We want to track *where* conversations are occurring: amongst what group of people.
+
+% * This motivates using the interaction-based communities.
+
+The data set was divided into two disjoint time periods: from 9am April 25th 2011 to 9am May 23rd 2011 and from 9am May 23rd 2011 to 9am June 25th 2011.
+We then constructed the three weighted networks (the structural network is unchanged) using the activity, retweets, mentions, and hashtags from the first time period, as described in the methodology section.
+We then used OSLOM to infer the community structure in these weighted networks.
 
 \begin{table}
-	\caption{Lorem ipsum.}
+	\caption{The percentage of retweets and mentions that occur internal to communities for each of the four community types.}
 	\centering
@@
 		Topic-based & 52.3 & 74.1  \\
-		Interaction-based & 64.3 & 81.7
+		Interaction-based & \textbf{64.3} & \textbf{81.7}
 	\end{tabular}

### 2014-06-29 paper-for_arxiv/results.tex
Modified sections on conversation tracking.

@@
 That is, we want to track groups of individuals who interact more with each other than with users outside of their group.
-This notion of community naturally falls within our interaction-based framework outlined above.
-We demonstrate how much is gained by tailoring the community detection problem to this question.
+For example, we might wish to select a seed group of individuals in order to spread a message to a subpopulation of a social network.
+We now demonstrate how the performance on this tracking problem depends on the community type under consideration.
 
@@
 
-The data set was divided into two disjoint time periods: from 9am April 25th 2011 to 9am May 23rd 2011 and from 9am May 23rd 2011 to 9am June 25th 2011.
+The data set was divided into two disjoint time periods: from 9am April 25th 2011 to 9am May 23rd 2011 (28 days) and from 9am May 23rd 2011 to 9am June 25th 2011 (33 days).
 We then constructed the three weighted networks (the structural network is unchanged) using the activity, retweets, mentions, and hashtags from the first time period, as described in the methodology section.
-We then used OSLOM to infer the community structure in these weighted networks.
+Using the coverings inferred by OSLOM for the weighted network, we define the inside and outside of a community in the same way as depicted in Figure~\ref{Fig-edge_types}, where now we consider mixed-type edges to be internal.
+Based on this partitioning of the edges, we then track how many of the retweets / mentions in the second time period fall inside vs outside of the communities.
+The percentages of retweets and mentions that occur internal to each of the community types are given in Table~\ref{Tab-mentionretweets}.
 
@@
 		\hline
-		Structural & 45.4 & 69.9 \\
-		Activity-based & 54.1 & 72.9 \\
-		Topic-based & 52.3 & 74.1  \\
-		Interaction-based & \textbf{64.3} & \textbf{81.7}
+		Structural & 47.5 & 70.9 \\
+		Activity-based & 54.7 & 75.6 \\
+		Topic-based & 49.4 & 66.8  \\
+		Interaction-based & \textbf{67.2} & \textbf{84.2}
 	\end{tabular}
+	\label{Tab-mentionretweets}
+\end{table}
+
+Let $I_{c}$ be the number of conversations (defined as a retweet or mention) occuring internal to community $c$, and let $|\mathcal{C}|_{c}$ be the size of community $c$.
+Finally, let $N$ be the total number of conversations, both internal and external, involving the nodes.
+An alternative scoring function is then
+\begin{align}
+	\frac{1}{N}\sum_{c} \frac{I_{c}}{|\mathcal{C}_{c}|}.
+	\label{conversation-metric}
+\end{align}
+That is, this measures the average number of internal conversations per user in a community.
+This will be maximized when the communities are small and the number of internal conversations are large compared to the total number of conversations.
+
+\begin{table}
+	\caption{The metric (\ref{conversation-metric}) for the four community types, computed using the held-out data.}
+	\centering
+	\begin{tabular}{l | c c}
+		Community Type & Retweets & Mentions \\
+		\hline
+		Structural & 0.0289 & 0.0344 \\
+		Activity-based & 0.0793 & 0.0645 \\
+		Topic-based & 0.1031 & 0.1020  \\
+		Interaction-based & 0.0690 & 0.0977
+	\end{tabular}
+	\label{Tab-mentionretweets2}
 \end{table}

### 2014-07-02 code/compare_mentions_retweets_v3.py
Code for Elisa's analysis + results in paper.

@@ -1,0 +1,307 @@
+# Compare how often a mention / retweet occurs
+# inter vs intra community, based on the community
+# partitioning.
+
+# 	DMD, 13 May 2014
+
+# Outline:
+
+# 1: Extract the userids of the users in the 
+# 	 mention-retweet network.
+#
+# 2: For each network type, determine whether
+#    an edge occurs inter- / intra-community.
+#
+# 3: For each retweet (mention) *made between users 
+# 	 from the mention-retweet network*, determine
+# 	 whether the retweet (mention) occurs internal
+# 	 / external to a community.
+#
+# UPDATE (2 July 2014): This implementation uses
+# Elisa's conversation tracking idea from the 
+# 1 July 2014 email.
+
+from itertools import islice
+from collections import Counter
+
+import ipdb
+
+# community_type = '0'
+
+community_types = ['0', '4', '7', '10']
+# community_types = ['0', '4', '10']
+# community_types = ['4', '7', '10']
+# community_types = ['0']
+
+# community_types = ['10']
+
+suffix = '' # For OSLOM
+# suffix = 'WSBM_K4' # For WSBM
+
+time_frame = '' # For communities inferred using the entire data set
+# time_frame = '-partial' # For communities inferred using only the first 3/4 of the data set.
+
+data_type = 'mentions'
+# data_type = 'retweets'
+
+print 'Counting {}...'.format(data_type)
+
+# The training set runs 
+#
+# 	2011/4/25 9am to 2011/5/23 9am.
+# 
+# which is 28 days or 2419200 seconds.
+
+seconds_train = 2419200
+
+user_files = {'0' : '../data/twitter_network_filtered_edges.txt', '4' : '../data/content-free/directedweightsTE/edge_weights_bin10minutes_lag_4_withMMBIAS.dat', '7' : '../data/content-full/twitter_network_hashtags_weighted.txt', '10' : '../data/content-full/twitter_network_contentfull_weighted_arithmeticmean.txt'}
+
+# user_files = {'4' : '../data/content-free/directedweightsTE/edge_weights_bin10minutes_lag_4_withMMBIAS.dat', '7' : '../data/content-full/twitter_network_hashtags_weighted.txt', '10' : '../data/content-full/twitter_network_contentfull_weighted_arithmeticmean.txt'}
+
+# 2: For each network type, determine whether
+#    an edge occurs inter- / intra-community.
+
[…]

### 2014-07-03 code/compare_mentions_retweets_v4.py
Added another analysis file.

@@ -1,0 +1,306 @@
+# Compare how often a mention / retweet occurs
+# inter vs intra community, based on the community
+# partitioning.
+
+# 	DMD, 13 May 2014
+
+# Outline:
+
+# 1: Extract the userids of the users in the 
+# 	 mention-retweet network.
+#
+# 2: For each network type, determine whether
+#    an edge occurs inter- / intra-community.
+#
+# 3: For each retweet (mention) *made between users 
+# 	 from the mention-retweet network*, determine
+# 	 whether the retweet (mention) occurs internal
+# 	 / external to a community.
+#
+# UPDATE (2 July 2014): This implementation uses
+# Elisa's conversation tracking idea from the 
+# 1 July 2014 email.
+# 
+# UPDATE (3 July 2014): Tracking both mentions
+# and retweets simulataneously as 'conversations'.
+
+from itertools import islice
+from collections import Counter
+
+import ipdb
+
+# community_type = '0'
+
+community_types = ['0', '4', '7', '10']
+# community_types = ['0', '4', '10']
+# community_types = ['4', '7', '10']
+# community_types = ['0']
+
+# community_types = ['10']
+
+suffix = '' # For OSLOM
+# suffix = 'WSBM_K4' # For WSBM
+
+time_frame = '' # For communities inferred using the entire data set
+# time_frame = '-partial' # For communities inferred using only the first 1/2 of the data set.
+
+# The training set runs 
+#
+# 	2011/4/25 9am to 2011/5/23 9am.
+# 
+# which is 28 days or 2419200 seconds.
+
+seconds_train = 2419200
+
+user_files = {'0' : '../data/twitter_network_filtered_edges.txt', '4' : '../data/content-free/directedweightsTE/edge_weights_bin10minutes_lag_4_withMMBIAS.dat', '7' : '../data/content-full/twitter_network_hashtags_weighted.txt', '10' : '../data/content-full/twitter_network_contentfull_weighted_arithmeticmean.txt'}
+
+# user_files = {'4' : '../data/content-free/directedweightsTE/edge_weights_bin10minutes_lag_4_withMMBIAS.dat', '7' : '../data/content-full/twitter_network_hashtags_weighted.txt', '10' : '../data/content-full/twitter_network_contentfull_weighted_arithmeticmean.txt'}
+
+# 2: For each network type, determine whether
+#    an edge occurs inter- / intra-community.
+
[…]

### 2014-07-11 paper-for_arxiv/paper.tex
Reworking edges-across-communities section.
Beginning to incorporate reviewer comments.
Fixed references and removed coloring.
formatting references and adding style files

--- 2014-01-17 paper/paper.tex
@@
 %File: formatting-instruction.tex
-\documentclass[letterpaper]{article}
-\usepackage{aaai}
+\documentclass[]{article}
+%\documentclass{comnet}
 \usepackage{times}
@@
 \usepackage{multirow}
-\frenchspacing
-\setlength{\pdfpagewidth}{8.5in}
-\setlength{\pdfpageheight}{11in}
+\usepackage{authblk}
+\usepackage{color}
+\usepackage{subfigure}
+%\frenchspacing
+%\setlength{\pdfpagewidth}{8.5in}
+%\setlength{\pdfpageheight}{11in}
+%\textwidth=126mm
 \pdfinfo{
@@
 \begin{abstract}
-\begin{quote}
+%\begin{quote}
 Community detection in online social networks is typically based on the analysis of the explicit connections between users, such as ``friends" on Facebook and ``followers" on Twitter.
@@
 Our results confirm that asking a precise question is an unavoidable first step in community detection in online social networks, and that different questions can lead to different insights into the network under study.
-\end{quote}
+%\end{quote}
 \end{abstract}
 
-\input{parts/intro.tex}
-\input{parts/methods.tex}
-\input{parts/results.tex}
-\input{parts/discussion.tex}
-\input{parts/conclusions.tex}
+\newpage
 
-\bibliography{references}
-\bibliographystyle{aaai}
+\input{intro.tex}
+\input{methods.tex}
+\input{results.tex}
+\input{conclusions.tex}
+
+\bibliographystyle{comnet}
+\bibliography{references.bib}
+
+% \input{paper.bbl}
 

### 2014-07-11 paper-for_arxiv/results.tex
Code for Elisa's analysis + results in paper.
updating more citations

@@
 Because we detect coverings rather than partitions, standard cluster comparison metrics like variation of information~\cite{meilua2003comparing} are not appropriate.
-Instead, we use a generalization of variation of information first introduced in~\cite{lancichinetti2009detecting}, the normalized mutual information.
+Instead, we use a generalization of variation of information first introduced in~\cite{Lancichinetti2009}, the normalized mutual information.
 The normalized mutual information stems from treating clustering as a community identification problem: given that we know a node's community membership(s) in the first covering, how much information do we have about its community membership(s) in the second covering, and vice versa?
@@
 The normalized mutual information varies from 0 to 1, attaining the value of 1 only when $\mathcal{C}_{1}$ and $\mathcal{C}_{2}$ are identical coverings up to a permutation of their labels.
-See the appendix of~\cite{lancichinetti2009detecting} for more details.
+See the appendix of~\cite{Lancichinetti2009} for more details.
 
@@
 
+\begin{table}
+	\caption{The value of the conversation metric proposed by Elisa, averaged over all of the communities in a given covering.}
+	\centering
+	\begin{tabular}{ l | c c}
+		Community Type & Mentions & Retweets \\
+		\hline
+		Structural & 2.9347 & 0.4734 \\
+		Activity-based & \textbf{3.3893} & 0.5173 \\
+		Topic-based & 2.5944 & 0.5580 \\
+		Interaction-based & 2.1984 & \textbf{1.1069}
+	\end{tabular}
+\end{table}
+
 \subsection{Qualitative Analysis of Community Memberships Across Types}

### 2014-07-14 code/compare_mentions_retweets_v3.py
Minor changes to scripts.

@@ -28,9 +28,9 @@ import ipdb
 
 # community_type = '0'
 
-community_types = ['0', '4', '7', '10']
+# community_types = ['0', '4', '7', '10']
 # community_types = ['0', '4', '10']
-# community_types = ['4', '7', '10']
+community_types = ['4', '7', '10']
 # community_types = ['0']
 
 # community_types = ['10']
@@ -38,8 +38,8 @@ community_types = ['0', '4', '7', '10']
 suffix = '' # For OSLOM
 # suffix = 'WSBM_K4' # For WSBM
 
-time_frame = '' # For communities inferred using the entire data set
-# time_frame = '-partial' # For communities inferred using only the first 3/4 of the data set.
+# time_frame = '' # For communities inferred using the entire data set
+time_frame = '-partial' # For communities inferred using only the first 3/4 of the data set.
 
 data_type = 'mentions'
 # data_type = 'retweets'
@@ -239,16 +239,16 @@ for community_type_ind, community_type in enumerate(['{}{}'.format(community_typ
 			else:
 				uid1, uid2, weight = map(str.strip, line.strip().split(' '))
 			
-			# if len(userid_to_community.get(uid1, [])) == 0:
-			# 	pass
-			# elif len(userid_to_community.get(uid2, [])) == 0:
-			# 	pass
-			# else:
-			if uid1 == '51319087':
+			if len(userid_to_community.get(uid1, [])) == 0:
 				pass
-			elif uid2 == '51319087':
+			elif len(userid_to_community.get(uid2, [])) == 0:
 				pass
 			else:
+			# if uid1 == '51319087':
+			# 	pass
+			# elif uid2 == '51319087':
+			# 	pass
+			# else:
 				# The shared communities between the two users engaged
 				# in conversation.
 				

### 2014-07-14 code/compare_mentions_retweets_v4.py

@@ -31,18 +31,18 @@ import ipdb
 
 # community_type = '0'
 
-community_types = ['0', '4', '7', '10']
+# community_types = ['0', '4', '7', '10']
 # community_types = ['0', '4', '10']
 # community_types = ['4', '7', '10']
-# community_types = ['0']
+community_types = ['10']
 
 # community_types = ['10']
 
 suffix = '' # For OSLOM
 # suffix = 'WSBM_K4' # For WSBM
 
-time_frame = '' # For communities inferred using the entire data set
-# time_frame = '-partial' # For communities inferred using only the first 1/2 of the data set.
+# time_frame = '' # For communities inferred using the entire data set
+time_frame = '-partial' # For communities inferred using only the first 1/2 of the data set.
 
 # The training set runs 
 #
@@ -147,16 +147,16 @@ for community_type_ind, community_type in enumerate(['{}{}'.format(community_typ
 			else:
 				uid1, uid2, weight = map(str.strip, line.strip().split(' '))
 			
-			# if len(userid_to_community.get(uid1, [])) == 0:
-			# 	pass
-			# elif len(userid_to_community.get(uid2, [])) == 0:
-			# 	pass
-			# else:
-			if uid1 == '51319087':
+			if len(userid_to_community.get(uid1, [])) == 0:
 				pass
-			elif uid2 == '51319087':
+			elif len(userid_to_community.get(uid2, [])) == 0:
 				pass
 			else:
+			# if uid1 == '51319087':
+			# 	pass
+			# elif uid2 == '51319087':
+			# 	pass
+			# else:
 				# The shared communities between the two users engaged
 				# in conversation.
 				
@@ -286,6 +286,8 @@ for community_type_ind, community_type in enumerate(['{}{}'.format(community_typ
 	
 	running_sum = 0 # the sum of the ratios of ic/(ec + 1) across all of the communities
 	
+	ratios = []
+	
 	for commid in range(comm_count):
 		if i_edge_counts_by_community[commid] == 0 or e_edge_counts_by_community[commid] == 0:
 			num_comms_excluded += 1 # Deal with singletons and communities without non-inter-type edges
@@ -297,7 +299,9 @@ for community_type_ind, community_type in enumerate(['{}{}'.format(community_typ
 			
 			if ec == 0:
 				num_wo_ec += 1
-
+			
+			ratios.append(ic/float(ec+1))
+			
 			running_sum += ic/float(ec+1)
 			
 	

### 2014-07-14 paper-for_arxiv/appendices.tex
Incorporated Michelle's suggestions.

--- 2014-04-30 paper-for_arxiv/methods.tex
@@
-\section{Methodology}
+\appendix
 
-In the following sections, we introduce the problem of community detection, and present the data set used for our analyses.
-We then describe our methodology for constructing the question-specific networks.
-In particular, we introduce an information theoretic method for activity-based communities, a retweet-mention statistic for interaction-based communities, and a hashtag similarity metric for defining topic-based communities.
-
-\subsection{Community Detection}
-
-%[[Already defined]]In network theory communities are usually defined as group of %nodes more densely connected among each other than with the rest of the network.
-As discussed in the introduction, we adopt the standard definition of \emph{community}: a collection of nodes (users) within a network who are more densely connected to each other than with the rest of the network.
-Structural community detection is a well studied problem and several different methods and algorithms have been proposed.
-For a complete review of this subject we refer the reader to \cite{fortunato2010community}.
-In this paper however we focus on a class of networks and communities that is far less studied, in particular we study networks which are both \textit{weighted} and \textit{directed} and communities within those weighted directed networks that can (but need not) \emph{overlap}.
-When selecting a detection algorithm we propose that all three (weight, direction, and overlap) are important for the following reasons.
-First, communication on Twitter occurs in a directed manner, with users broadcasting information to their followers.
-An undirected representation of the network would ignore this fact, and could lead to communities composed of users who do not actually share information.
-Second, we are interested in not just the structure of links but also in their function, and to capture this we use edge weightings which must be incorporated into the community detection process.
-Finally, since people can belong to multiple and possibly overlapping social (e.g., college friends, co-workers, family, etc.) and topical (e.g., a user can be interested in both cycling and politics and use the network to discuss the two topics with the two different communities) communities, we are interested in finding \textit{overlapping} communities, rather than partitions of the weighted directed network.
-%For example, users can belong to multiple social groups such as college friends, %co-workers, family, etc.
-and these groups may but need not overlap.
-A user can also %belong to multiple topical communities, e.g., a user can be interested in both %cycling and politics and use the network to discuss the two topics with the two %different communities.
-
-This last criterion in particular poses a problem because the majority of community detection algorithms developed so far are built to find partitions of a network and few are aimed at finding overlapping communities \cite{BaumesGKMP05,PalEtAl05,ZhaWanZha07,Gre07,PhysRevE.77.016107,Lancichinetti2009,PhysRevE.80.016105,Kovacs2010}.
-Among these methods, even fewer deal with directed or weighted networks.
-For example, the work of~\cite{PalEtAl05} on clique percolation can account for both features, but not at the same time.
-A recent method proposed by~\cite{LancichinettiPlos}, OSLOM (Order Statistics Local Optimization Method), is one of the first methods  able to deal with all of these features simultaneously.
-Their method relies on a fitness function that measures the statistical significance of clusters with respect to random fluctuations, and attempts to optimize this fitness function across all clusters.
-Following~\cite{LancichinettiPlos}, the significance measure is defined as the probability of finding the cluster in a network without community structure.
-The null model used is basically the same as the one adopted by Newman and Girvan to define modularity, i.e.
-it is a model that generates random graphs with a given degree distribution.
-The authors tested their algorithm on different benchmarks (LFR and Girvan-Newman) and real networks (such as the US air transportation and the word association network), and compared its performance against the best algorithms
-currently available (i.e the ones mentioned in the introduction), and found excellent results.
-Moreover, they showed that OSLOM is also able to recognize the absence, and not simply the presence, of community structure, by testing it on random graphs.
-This feature of the algorithm plays an important role in the analysis of real data networks, since it is not always the case that a community structure is indeed present and it is therefore useful to be able to detect its absence too.
-Therefore, given its versatility and performance with benchmark network, in this paper we used OSLOM to detect \emph{overlapping} communities present in our \emph{weighted} and \emph{directed} network.
-%For this paper we use OSLOM since it allowed us to detect \emph{overlapping} communities present in our \emph{weighted} and \emph{directed} network, and its authors showed that it performs very well on various types of artificial benchmark graphs and also on several real networks.
-
-\subsection{The Initial Dataset and Network Construction}
-
-The dataset for this study consisted of the tweets of 15,000 Twitter users over a 9 week period (from April 25th to June 25th 2011).
-The users are embedded in a network collected by performing an intelligent breadth-first expansion from a random seed user.
-In particular, once the seed user was chosen, the network was expanded to include his/her followers, but only included users considered to be `active' (i.e., users who tweeted at least once per day over the past one hundred days).
-Network collection continued in this fashion by considering the active followers of the active followers of the seed, and so on until 15,000 users were added to the network.
-
-Since our goal is to explore the functional communities of this network, we filter the network down to the subset of users which actively interact with each other (e.g., via retweets and mentions).
-We do this by measuring what we call (incoming/outgoing) information events.
-We define an outgoing information event for a given user $u$ as either a mention made by $u$ of another user in the network, or a retweet of one of $u$'s tweets by another user in the network.
-The logic for this definition is as follows: if $u$ mentions a user $v$ this can be thought of as $u$ directly sending information to $v$, and if $u$ is retweeted by $v$ then $v$ received information from $u$ and rebroadcast it to their followers.
-In either case there was information outgoing from $u$ which affected the network in the some way.
-Analogously, we define the incoming information event for $u$ as either being mentioned by a different user in the network, or as retweeting another user in the network.
-%function and information share is important We then filter down this starting %network to include only users that [[what??]]. To do this 
-%Since one of the community types we want to explore is based on the explicit interactions ( between users, we filter the dataset in order to take into account only users who make use of these kinds of features in their tweets.
-[[Seeems out of place]]
-%We define an event of outgoing information for a given user $u$ as either a mention made by $u$ of another user in the network, or a retweet by another user of one of $u$'s tweets. 
-%[[Switched the readers perspective]]When we mention someone we are in fact sending him some information, and when we are retweeted it means that the person that retweeted us has received some information from us and is sharing it.
-With (incoming/outgoing) information events defined we filtered the network by eliminating all users with less than 9 outgoing \emph{and} incoming information events, i.e., less than one information event per type per week on average.
-We then further restricted our analysis to the strong giant connected component of the network built from the (incoming/outgoing) information filtered set of users.
-%and whose link represent a user-follower relationship.
-In this study the link is directed from the user to the follower because this is the direction in which the information (in the case of transfer entropy) or influence (in the case of mention-retweets) flows.
-Thus, for a pair of users $u$ and $v$, an edge $a_{v \to u}$ in the structural network has weight 1 if user $u$ follows $v$, and 0 otherwise.
-The final network consists of 6,917 nodes and 1,481,131 edges.
-
-\subsection{Activity-Based Communities and Transfer Entropy}
-\label{sec:method-activity}
-
-For the activity-based communities, we consider only the timing of each user's tweets and ignore any additional content.
-From this starting point, we can view the behavior of a user $u$ on Twitter as a point process, where at any instant $t$ the user has either emitted a tweet ($X_{t}(u) = 1$) or remained silent ($X_{t}(u) = 0$).
-This is the view of a user's dynamics taken in~\cite{ver2012information} and~\cite{darmon2013understanding}.
-Thus, we reduce all of the information generated by a user on Twitter to a time series $\{ X_{t}(u)\}$ where $t$ ranges over the time interval for which we have data (9 weeks in this case).
-Because status updates are only collected in discrete, 1-second time intervals, it is natural to consider only the discrete times $t = 1 \text{ s}, 2 \text{ s}, \ldots, $ relative to a reference time.
-We can then compute the flow of information between two users $u$ and $v$ by computing the transfer entropy between their time series $X_{t}(u)$ and $X_{t}(v).$
+\section{Appendix A: Transfer Entropy and Its Estimation from Data}
 
@@
 We use the notation $X_{t-k}^{t}$ to denote the values of the stochastic process from time $t-k$ to time $t$, $X_{t-k}^{t} = (X_{t-k}, X_{t-(k-1)}, \ldots, X_{t - 1}, X_{t})$.
-The lag-$k$ transfer entropy of $Y$ on $X$ is defined as
+The lag-$k$ transfer entropy~\cite{schreiber2000measuring} of $Y$ on $X$ is defined as
 \begin{align}
-	\text{TE}_{Y \to X}^{(k)} &= H\left[X_{t} | X_{t-k}^{t-1}\right] - H\left[X_{t} | X_{t-k}^{t-1}, Y_{t-k}^{t-1}\right],
+	\text{TE}_{Y \to X}^{(k)} &= H\left[X_{t} | X_{t-k}^{t-1}\right] - H\left[X_{t} | X_{t-k}^{t-1}, Y_{t-k}^{t-1}\right], \label{Eqn-TE}
 \end{align}
@@
 If the transfer entropy is positive, then $\{ Y_{t}\}$ is considered causal for $\{ X_{t}\}$ in the Granger sense~\cite{granger1963economic}.
-% More generally we can define the transfer entropy as the limit of lag-$k$ transfer entropies,
-% \begin{align}
-% 	\text{TE}_{Y \to X} &= \lim_{k \to \infty} \text{TE}_{Y \to X}^{(k)},
-% \end{align}
-% if the limit exists.
 
-In estimating the transfer entropy from finite data, we will assume that the process $(X_{t}, Y_{t})$ is jointly stationary, which gives us that
+In estimating the transfer entropy from finite data, we will assume that the process $\{(X_{t}, Y_{t})\}$ is jointly stationary, which gives us that
 \begin{align}
@@
 That is, the predictive distribution only depends on the past, not on when the past is observed.
-Given this assumption, we compute estimators for $p(x_{k+1} | x_{1}^{k})$ and $p(x_{k+1} | x_{1}^{k}, y_{1}^{k})$ by `counting': for each possible past $(x_{1}^{k}, y_{1}^{k})$, we count the number of times a future of type $x_{k+1}$ occurs, and normalize.
+Given this assumption, we compute estimators for $p(x_{k+1} | x_{1}^{k})$ and $p(x_{k+1} | x_{1}^{k}, y_{1}^{k})$ by `counting': for each possible marginal and joint past $x_{1}^{k}$ and $(x_{1}^{k}, y_{1}^{k})$, we count the number of times a future of type $x_{k+1}$ occurs, and normalize to obtain the appropriate estimators of the one-step-ahead predictive distributions.
 Call these estimators $\hat{p}(x_{k+1} | x_{1}^{k})$ and $\hat{p}(x_{k+1} | x_{1}^{k}, y_{1}^{k})$.
@@
 To account for this bias, we use the Miller-Madow adjustment to the plug-in estimator~\cite{miller1955note}.
+For a random variable $X$ taking on finitely many values from an alphabet $\mathcal{X}$, the Miller-Madow estimator is
+	\begin{align}
+		\tilde{H}[X] = \hat{H}[X] + \frac{|\hat{\mathcal{X}}| - 1}{2 n}
+	\end{align}
+	where $|\mathcal{\hat{X}}|$ is the number of observed symbols from the alphabet $\mathcal{X}$ and $n$ was the number of samples used to estimate $\hat{H}[X].$ The definition of transfer entropy~(\ref{Eqn-TE}) can be rewritten in terms of joint entropies as
+	\begin{align}
+		TE_{Y \to X}^{(k)} &= H[X_t | X_{t-k}^{t-1}] - H[X_t | X_{t-k}^{t-1},Y_{t-k}^{t-1}] \\ 
+		&= H[X_t,X_{t-k}^{t-1}]-H[X_{t-k}^{t-1}]-H[X_t,X_{t-k}^{t-1},Y_{t-k}^{t-1}]+H[X_{t-k}^{t-1},Y_{t-k}^{t-1}],
+	\end{align}
+	We then apply the Miller-Madow adjustment individually to each of the entropy terms. For example, for the first term, we have
+	\begin{align}
+		\tilde{H}[X_{t}, X_{t - k}^{t-1}] = \tilde{H}[X_{t - k}^{t}] = \hat{H}[X_{t-k}^{t}] + \frac{|\widehat{\mathcal{X}^{k+1}}| - 1}{2n},
+	\end{align}
+	where $|\widehat{\mathcal{X}^{k+1}}|$ is the number of $(k + 1)$-tuples we actually observe (of the $2^{k + 1}$ possible tuples).
+Doing this for each term, the overall Miller-Madow estimator for the transfer entropy is
+	\begin{align}
+		\widetilde{TE}_{Y \to X}^{(k)} &= \tilde{H}[X_t | X_{t-k}^{t-1}] - \tilde{H}[X_t | X_{t-k}^{t-1},Y_{t-k}^{t-1}] \\ 
+		&= \tilde{H}[X_t,X_{t-k}^{t-1}]-\tilde{H}[X_{t-k}^{t-1}]-\tilde{H}[X_t,X_{t-k}^{t-1},Y_{t-k}^{t-1}]+\tilde{H}[X_{t-k}^{t-1},Y_{t-k}^{t-1}].
+	\end{align}
+	One possible problem with this estimator is that it can result in \emph{negative} estimates of entropies.
+That usually occurs when $\hat{H}$ is very small.
+In these cases, we truncate set the estimator to zero.
 
-For the communities based on transfer entropy, we weight each edge from a user $u$ to a follower $f$ by the estimated transfer entropy of the user $u$ on $f$, 
-\begin{align}
-	w_{u \to f}^{\text{TE}(k)} = \widehat{\text{TE}}_{X(u) \to X(f)}^{(k)}. \label{Eqn-EW-activity}
-\end{align}
-A positive value for the transfer entropy of the user $u$ on $f$ indicates that $u$ influences $f$, or that $u$ and $f$ share a common influencer~\cite{ver2012information}.
+\section{Appendix B: Comparing Edges Across Different Community Types}
 
-Operationally, we expect users to interact with Twitter on a human time scale, and thus the natural one-second time resolution is too fine since most humans do not write tweets on the time scale of seconds.
-We coarsen each time series by considering non-overlapping time intervals ten minutes in length.
-For each time interval, we record a 1 if the user has tweeted during that time interval, and a 0 if they have not.
-Thus, the new coarsened time series now captures whether or not the user has been active on Twitter over any given ten minute time interval in our data set.
-We then compute the transfer entropy on these coarsened time series taking $k$ to range from 1 to 6, which corresponds to a lag of ten minutes to an hour.
-The choice of lag must balance a trade-off between additional information and sparsity of samples: as we increase the lag, we account for longer range dependencies, but we also decrease the number of samples available to infer a higher dimensional predictive distribution.
-Ultimately, due to similarities in the underlying communities we chose a lag-4 transfer entropy.
-All references to activity-based weights, unless otherwise noted, refer to this choice of lag.
-
-\subsection{Interaction-Based Communities and Mention / Retweet Weighting}
-\label{sec:method-interaction}
-
-Retweets and mentions are two useful features of Twitter networks which can be used to track information flow through the network.
-%A way of tracking the flow of information through users is by considering two useful features of this social network: mentions and retweets. 
-With mentions users are sending directed information to other users and with retweets users are rebroadcasting information from a user they follow to all of their followers. 
-%information from a user has been captured by a follower and shared with his/her own followers. 
-This type of information flow defines a community in a much different way than transfer entropy.
-Instead of defining communities by the loss of uncertainty in one user's tweeting history based on another's, we define interaction-based communities by weighting the user-follower network with a measure proportional to the number of mentions and/or retweets between users.
-% We can therefore define interaction-based communities by weighting the user-follower network with a measure proportional to the number of mentions and retweets between users. 
-For the interaction-based communities we consider three weighting schemes: proportional retweets,
-\begin{equation}
-w_{u \to f}^{\text{R}}=pR=\frac{\mbox{\# retweets of }u \mbox{ by }f}{\mbox{\# total retweets made by }f},
-\end{equation}
-proportional mentions,
-\begin{equation}
-w_{u \to f}^{\text{M}} = pM = \frac{\mbox{\# mentions of }f \mbox{ by }u}{\mbox{\# total mentions of }f},
-\end{equation}
-and mention-retweet as the arithmetic mean of these two measures,
-%we weight each edge from a user $u$ to a follower $f$ through a combination of proportional mentions ($pM$):
-% In more details, for each couple of user-follower $u$ and $f$, we use the arithmetic mean of the two following numbers:
-%\begin{equation}
-%w_{u \to f}^{\text{M}} = pM = \frac{\mbox{\# mentions of }f \mbox{ by }u}{\mbox{\# %total mentions of }f}
-%\end{equation}
-\begin{align}
-	w_{u \to f}^{\text{MR}} = \frac{(pM+pR)}{2}. \label{Eqn-EW-interaction}
-\end{align}
-
-%	w_{u \to f}^{\text{MR}} = \frac{1}{2}\left(\frac{\mbox{\# mentions of }f %\mbox{ by }u}{\mbox{\# total mentions of }f} + \frac{\mbox{\# retweets of }u \mbox{ by }f}{\mbox{\# total retweets made by }f}\right).
-
-\subsection{Topic-Based Communities and Hashtag Weighting}
-\label{sec:method-topic}
-
-The final community we consider is a topic-based or topical community, i.e., a community defined by the content (topics) users discuss.
-So in a topical community, users are defined to be a member of a community if they tweet \emph{about} similar topics as other members of the community.
-%Another kind of community is the one based on the content of the tweets, and relies on the idea of finding people that talk about the same things. 
-In order to detect the topical communities, we weight the edges of the user-follower network through a measure based on the number of common hashtags between pairs of users.
-Hashtags are a good proxy for a tweet's content as hashtags are explicitly meant to be keywords indicating the topic of the tweet.
-Moreover they are widely used and straightforward to detect.
-
-To this end, we characterize each user $u$ by a vector $\vec{h}(u)$ of length equal to the number of unique hashtags in the dataset, and whose elements are defined as
-\begin{equation}
-h_i(u) = n_i(u) * \log{ \frac{N}{n_i} }
-\end{equation}
-where $n_i(u)$ is the frequency of hashtag $i$ occuring in user $u$'s tweets, $N$ is the total number of users, and $n_i$ is the number of users that have used the hashtag $i$ in their tweets.
-This adapted term frequency--inverse document frequency (tf-idf) measure \cite{salton_introduction_1983} captures the importance of a hashtag in the users's tweets through the first factor, but at the same time smooths it through the second factor by giving less importance to hashtags that are too widely used (as $\frac{N}{n_i}$ approaches one, its logarithm approaches zero).
-
-For the topical communities we weight each directed edge from a user $u$ to a follower $f$ with the cosine similarity of their respective vectors $\vec{h}(u)$ and $\vec{h}(f)$:
-\begin{align}
-	w_{u \to f}^{\text{HT}} = \frac{\vec{h}(u) \cdot \vec{h}(f)}{||\vec{h}(u)|| \ \ ||\vec{h}(f)||}. \label{Eqn-EW-topic}
-\end{align}
-This weight captures the similarity between users in terms of the topics discussed in their tweets.
+\begin{figure}[!h]
+	\centering
+	\includegraphics[width=1\textwidth]{densities-edges.eps}
+	\caption{The density of edge weights for different community types (rows) and weight types (columns).
+The red,  blue, and magenta values below each collection of densities indicate the median of weight on intra-, inter-, and mixed-edges, respectively.}
+	\label{Fig-distributions_by_types}
+\end{figure}

### 2014-07-14 paper-for_arxiv/conclusions.tex
Incorporated Michelle's suggestions.

@@
 However, upon further investigation our novel use of transfer entropy for the detection of activity-based communities highlighted an important fact about this social network: influence tended to be higher across community boundaries than within them.
-This result echos the `strength of weak ties' theory from~\cite{granovetter1973strength}, which has found empirical support in~\cite{grabowicz2012social} for online social networks.
+This result echos the `strength of weak ties' theory from~\cite{granovetter1973strength}, which has found empirical support in online social networks~\cite{grabowicz2012social}.
 This means that our use of transfer entropy not only defines boundaries that are meaningful divisions between communities but also illustrates that users who have a strong influence on a community need not be a member of that community.

### 2014-07-14 paper-for_arxiv/intro.tex
Incorporated Michelle's suggestions.

@@
 Because of the importance of structural networks in online social media, a large amount of work in this area has focused on using structural networks for community detection.
-Here, by `community' we mean the standard definition from the literature on social networks: a collection of nodes (users) within the network who are more highly connected to each other than to nodes (users) outside of the community~\cite{newman2004finding}.
+Here, by `community' we mean the standard definition from the literature on social networks: a collection of nodes (users) within the network which are more highly connected to each other than to nodes (users) outside of the community~\cite{girvan2002a, newman2004finding}.
 For instance, in~\cite{java2009we}, the authors use a follower network to determine communities within Twitter, and note that conversations tend to occur within these communities.
-The approach of focusing on structural networks makes sense for `real-world' sociological experiments, where obtaining additional information about user interactions may be expensive and time-consuming.
+The approach of focusing on the structure of networks makes sense for `real-world' sociological experiments, where obtaining additional information about user interactions may be expensive and time-consuming.
 However, with the prevalence of large, rich data sets for online social networks, additional information beyond the structure alone may be incorporated, and these augmented networks more realistically reflects how users interact with each other on social media services~\cite{grabowicz2012social}.
@@
 \begin{itemize}
-	\item \textbf{Structure-based:} Who have you stated you are friends with? Who do you follow?
-	\item \textbf{Activity-based:} Who do you act like?
+	\item \textbf{Structure-based:} Who are your stated friends? Whom do you follow?
+	\item \textbf{Activity-based:} Whom do you act like?
 	\item \textbf{Topic-based:} What do you talk about?
-	\item \textbf{Interaction-based:} Who do you communicate with?
+	\item \textbf{Interaction-based:} Whom do you communicate with?
 \end{itemize}
@@
 
-Finally, the interaction-based approach relies on the meta-data and text of messages to identify who a user converses with on the social media service.
+Finally, the interaction-based approach relies on the meta-data and text of messages to identify whom a user converses with on the social media service.
 On Twitter, we can use mentions (indicating a directed communication) and retweets (indicating endorsement of another user) to identify conversation.
@@
 
-The activity-based, topic-based, and interaction-based networks allow us to build a more complete picture of the \emph{implicit} social network present in online social media, as opposed to the \emph{explicit} social network indicated by structural links.
+The activity-based, topic-based, and interaction-based networks allow us to build a more complete picture of the \emph{implicit} network present in online social media, as opposed to the \emph{explicit} social network indicated by structural links.
 In this paper, we explore the relation between these various possible networks and their corresponding communities.

### 2014-07-14 paper-for_arxiv/methods.tex
Incorporated Michelle's suggestions.

--- 2014-04-30 paper-for_arxiv/methods.tex
@@
 
-%[[Already defined]]In network theory communities are usually defined as group of %nodes more densely connected among each other than with the rest of the network.
 As discussed in the introduction, we adopt the standard definition of \emph{community}: a collection of nodes (users) within a network who are more densely connected to each other than with the rest of the network.
 Structural community detection is a well studied problem and several different methods and algorithms have been proposed.
-For a complete review of this subject we refer the reader to \cite{fortunato2010community}.
+For a complete review of this subject we refer the reader to \cite{porter2009communities, fortunato2010community}.
 In this paper however we focus on a class of networks and communities that is far less studied, in particular we study networks which are both \textit{weighted} and \textit{directed} and communities within those weighted directed networks that can (but need not) \emph{overlap}.
@@
 %[[Switched the readers perspective]]When we mention someone we are in fact sending him some information, and when we are retweeted it means that the person that retweeted us has received some information from us and is sharing it.
-With (incoming/outgoing) information events defined we filtered the network by eliminating all users with less than 9 outgoing \emph{and} incoming information events, i.e., less than one information event per type per week on average.
+With (incoming/outgoing) information events defined we filtered the network by eliminating all users with less than a total of 9 outgoing \emph{and} incoming information events, i.e., less than one information event per type per week on average.
 We then further restricted our analysis to the strong giant connected component of the network built from the (incoming/outgoing) information filtered set of users.
@@
 
-Let $\{X_{t}\}$ and $\{ Y_{t}\}$ be two strong-sense stationary stochastic processes\footnote{Recall that a a stochastic process is strong-sense stationary if the distribution over process evaluated at finitely many time points is invariant to an overall timeshift~\cite{grimmett2001probability}.}.
-In our work, these would correspond to two user activities, $X_{t}(u)$ and $X_{t}(v).$ We use the notation $X_{t-k}^{t}$ to denote the values of the stochastic process from time $t-k$ to time $t$, $X_{t-k}^{t} = (X_{t-k}, X_{t-(k-1)}, \ldots, X_{t - 1}, X_{t})$.
-The lag-$k$ transfer entropy of $Y$ on $X$ is defined as
-\begin{align}
-	\text{TE}_{Y \to X}^{(k)} &= H\left[X_{t} | X_{t-k}^{t-1}\right] - H\left[X_{t} | X_{t-k}^{t-1}, Y_{t-k}^{t-1}\right],
-\end{align}
-where
-\begin{align}
-	H\left[X_{t} | X_{t-k}^{t-1}\right] = - E\left[ \log_{2} p(X_{t} | X_{t-k}^{t-1}) \right]
-\end{align}
-and 
-\begin{align}
-	H\left[X_{t} | X_{t-k}^{t-1}, Y_{t-k}^{t-1}\right] = - E\left[ \log_{2} p(X_{t} | X_{t-k}^{t-1}, Y_{t-k}^{t-1}) \right]
-\end{align}
-are the usual conditional entropies over the conditional (predictive) distributions $p(x_{t} | x_{t-k}^{t-1})$ and $p(x_{t} | x_{t-k}^{t-1}, y_{t-k}^{t-1})$.
-This formulation was originally developed in~\cite{schreiber2000measuring}, where transfer entropy was proposed as an information theoretic measure of \emph{directed} information flow.
-Formally, recalling that $H\left[X_{t} | X_{t-k}^{t-1}\right]$ is the uncertainty in $X_{t}$ given its values at the previous $k$ time points, and that $H\left[X_{t} | X_{t-k}^{t-1}, Y_{t-k}^{t-1}\right]$ is the uncertainty in $X_{t}$ given the joint process $\{(X_{t}, Y_{t})\}$ at the previous $k$ time points, transfer entropy measures the reduction in uncertainty of $X_{t}$ by including information about $Y_{t-k}^{t-1},$ controlling for the information in $X_{t - k}^{t-1}$.
-By the `conditioning reduces entropy' result~\cite{cover2012elements}
-\begin{align}
-	H[X | Y, Z] \leq H[X | Y],
-\end{align}
-we can see that transfer entropy is always non-negative, and is zero precisely when $H\left[X_{t} | X_{t-k}^{t-1}\right] = H\left[X_{t} | X_{t-k}^{t-1}, Y_{t-k}^{t-1}\right]$, in which case knowing the past $k$ lags of $Y_{t}$ does not reduce the uncertainty in $X_{t}$.
-If the transfer entropy is positive, then $\{ Y_{t}\}$ is considered causal for $\{ X_{t}\}$ in the Granger sense~\cite{granger1963economic}.
-% More generally we can define the transfer entropy as the limit of lag-$k$ transfer entropies,
-% \begin{align}
-% 	\text{TE}_{Y \to X} &= \lim_{k \to \infty} \text{TE}_{Y \to X}^{(k)},
-% \end{align}
-% if the limit exists.
-
-In estimating the transfer entropy from finite data, we will assume that the process $(X_{t}, Y_{t})$ is jointly stationary, which gives us that
-\begin{align}
-	p(x_{t} | x_{t-k}^{t-1}) = p(x_{k+1} | x_{1}^{k})
-\end{align}
-and
-\begin{align}
-	p(x_{t} | x_{t-k}^{t-1}, y_{t-k}^{t-1}) = p(x_{k+1} | x_{1}^{k}, y_{1}^{k})
-\end{align}
-for all $t$.
-That is, the predictive distribution only depends on the past, not on when the past is observed.
-Given this assumption, we compute estimators for $p(x_{k+1} | x_{1}^{k})$ and $p(x_{k+1} | x_{1}^{k}, y_{1}^{k})$ by `counting': for each possible past $(x_{1}^{k}, y_{1}^{k})$, we count the number of times a future of type $x_{k+1}$ occurs, and normalize.
-Call these estimators $\hat{p}(x_{k+1} | x_{1}^{k})$ and $\hat{p}(x_{k+1} | x_{1}^{k}, y_{1}^{k})$.
-Then the plug-in estimator for the transfer entropy is
-\begin{align}
-	\widehat{\text{TE}}_{Y \to X}^{(k)} &= \hat{H}\left[X_{t} | X_{t-k}^{t-1}\right] - \hat{H}\left[X_{t} | X_{t-k}^{t-1}, Y_{t-k}^{t-1}\right]
-\end{align}
-where we use the plug-in estimators $\hat{H}\left[X_{t} | X_{t-k}^{t-1}\right]$ and $\hat{H}\left[X_{t} | X_{t-k}^{t-1}, Y_{t-k}^{t-1}\right]$ for the entropies.
-It is well known that the plug-in estimator for entropy is biased~\cite{paninski2003estimation}.
-To account for this bias, we use the Miller-Madow adjustment to the plug-in estimator~\cite{miller1955note}.
-
 For the communities based on transfer entropy, we weight each edge from a user $u$ to a follower $f$ by the estimated transfer entropy of the user $u$ on $f$, 
 \begin{align}
-	w_{u \to f}^{\text{TE}(k)} = \widehat{\text{TE}}_{X(u) \to X(f)}^{(k)}. \label{Eqn-EW-activity}
+	w_{u \to f}^{\text{TE}(k)} = \widetilde{\text{TE}}_{X(u) \to X(f)}^{(k)}. \label{Eqn-EW-activity}
 \end{align}
 A positive value for the transfer entropy of the user $u$ on $f$ indicates that $u$ influences $f$, or that $u$ and $f$ share a common influencer~\cite{ver2012information}.
+See Appendix A for a detailed introduction to transfer entropy and its estimation from data.
 
@@
 %A way of tracking the flow of information through users is by considering two useful features of this social network: mentions and retweets. 
-With mentions users are sending directed information to other users and with retweets users are rebroadcasting information from a user they follow to all of their followers. 
+With mentions, users are sending directed information to other users and with retweets users are rebroadcasting information from a user they follow to all of their followers. 
 %information from a user has been captured by a follower and shared with his/her own followers. 

### 2014-07-14 paper-for_arxiv/paper.tex
finishing references,many of the conferences are now abbreviated
Incorporated Michelle's suggestions.

@@
 \usepackage{subfigure}
+\usepackage{appendix}
 %\frenchspacing
@@
 %\setlength{\pdfpageheight}{11in}
-%\textwidth=126mm
+\textwidth=126mm
 \pdfinfo{
@@
 We claim that community detection in online social networks should be question-oriented and rely on additional information beyond the simple structure of the network.
-The concept of `community' is very general, and different questions such as ``who do we interact with?" and ``with whom do we share similar interests?" can lead to the discovery of different social groups.
+The concept of `community' is very general, and different questions such as ``whom do we interact with?" and ``with whom do we share similar interests?" can lead to the discovery of different social groups.
 In this paper we focus on three types of communities beyond structural communities: activity-based, topic-based, and interaction-based.
@@
 
+\section{Acknowledgments}
+
+Thanks to Cesar Flores, Lu\'is Seoane, Kevin Stadler, Jody Wright, and Nix Barnett to their contributions of preliminary ideas related to this paper and to Michelle Girvan, William Rand, and Aaron Clauset for their valuable comments and suggestions.
+This work was partially
+
 \bibliographystyle{comnet}
 \bibliography{references.bib}
+
+\input{appendices.tex}
 

### 2014-07-14 paper-for_arxiv/results.tex
Incorporated Michelle's suggestions.

--- 2014-06-16 paper-for_arxiv/results.tex
@@
 We see that the topic- and interaction-based networks admit the most communities.
-The activity-based network admits the least number of communities.
+The activity-based network admits the fewest communities.
 One advantage of the OSLOM over many other community detection algorithms is that it explicitly accounts for singleton `communities': those nodes who do not belong to \emph{any} extant communities.
@@
 Note that both axes are plotted on log-scales.
-Thus, for a fixed community size $c$, Figure~\ref{Fig-community_size_distribution} shows the proportion of communities of size greater than $c$ for each community type.
+Thus, for a fixed community size $s$, Figure~\ref{Fig-community_size_distribution} shows the proportion of communities of size greater than $s$ for each community type.
 We see that the community distributions have longer tails for the non-structural networks, and that the interaction-based network has the longest tail.
@@
 \includegraphics[width=0.50\textwidth]{comm_sizes_ecdf_loglog.pdf}
-\caption{The proportion of communities greater than $c$ in size, across the different community types. Note the logarithmic scale on the horizontal and vertical axes.}
+\caption{The proportion of communities greater than $s$ in size, across the different community types. Note the logarithmic scale on the horizontal and vertical axes.}
 \label{Fig-community_size_distribution}
@@
 If the community structure were arbitrary, the edge weights would be independent of the edge type, and all three conditional distributions would be identical.
-The densities associated with these distributions are shown in Figure~\ref{Fig-distributions_by_types}.
+The densities associated with these distributions are shown in Figure~\ref{Fig-distributions_by_types}, included in Appendix B.
 
@@
 
-% \begin{figure}[!h]
-% 	\centering
-% 	\includegraphics[width=1\textwidth]{distributions-edges.eps}
-% 	\caption{The distribution of edge weights for different community types (rows) and weight types (columns).
-The red,  blue, and magenta values below each distribution indicate the median of weight on intra-, inter-, and mixed-edges, respectively.}
-% 	\label{Fig-distributions_by_types}
-% \end{figure}
-
-\begin{figure}[!h]
-	\centering
-	\includegraphics[width=1\textwidth]{densities-edges.eps}
-	\caption{The density of edge weights for different community types (rows) and weight types (columns).
-The red,  blue, and magenta values below each collection of densities indicate the median of weight on intra-, inter-, and mixed-edges, respectively.}
-	\label{Fig-distributions_by_types}
-\end{figure}
-
 We also note that the distribution of transfer entropy weights always tend to be higher for edges crossing community boundaries (inter- or mixed-edges) compared to those edges within community boundaries (intra-edges).
@@
 
-\subsection{Demonstration of the Question-Oriented Approach}
-
-Next, we demonstrate a particular instance of a question-oriented approach.
+% \subsection{Demonstration of the Question-Oriented Approach}
+%
+% Next, we demonstrate a particular instance of a question-oriented approach.
 Suppose we were interested in tracking where conversations occur in a social network.
 That is, we want to track groups of individuals who interact more with each other than with users outside of their group.
-This notion of community naturally falls within our interaction-based framework outlined above.
-We demonstrate how much is gained by tailoring the community detection problem to this question.
-
-% * We want to track *where* conversations are occurring: amongst what group of people.
-
-% * This motivates using the interaction-based communities.
-
-The data set was divided into two disjoint time periods: from 9am April 25th 2011 to 9am May 23rd 2011 and from 9am May 23rd 2011 to 9am June 25th 2011.
+For example, we might wish to select a seed group of individuals in order to spread a message to a subpopulation of a social network.
+We now demonstrate how the performance on this tracking problem depends on the community type under consideration.
+%
+% % * We want to track *where* conversations are occurring: amongst what group of people.
+%
+% % * This motivates using the interaction-based communities.
+%
+% The data set was divided into two disjoint time periods: from 9am April 25th 2011 to 9am May 23rd 2011 (28 days) and from 9am May 23rd 2011 to 9am June 25th 2011 (33 days).
 We then constructed the three weighted networks (the structural network is unchanged) using the activity, retweets, mentions, and hashtags from the first time period, as described in the methodology section.
-We then used OSLOM to infer the community structure in these weighted networks.
-
-\begin{table}
-	\caption{The percentage of retweets and mentions that occur internal to communities for each of the four community types.}
-	\centering
-	\begin{tabular}{l | c c}
-		Community Type & Percentage of Retweets Internal & Percentage of Mentions Internal \\
-		\hline
-		Structural & 45.4 & 69.9 \\
-		Activity-based & 54.1 & 72.9 \\
-		Topic-based & 52.3 & 74.1  \\
-		Interaction-based & \textbf{64.3} & \textbf{81.7}
-	\end{tabular}
-\end{table}
+Using the coverings inferred by OSLOM for the weighted network, we define the inside and outside of a community in the same way as depicted in Figure~\ref{Fig-edge_types}, where now we consider mixed-type edges to be internal.
+Based on this partitioning of the edges, we then track how many of the retweets / mentions in the second time period fall inside vs outside of the communities.
+The percentages of retweets and mentions that occur internal to each of the community types are given in Table~\ref{Tab-mentionretweets}.
+%
+% \begin{table}
+% 	\caption{The percentage of retweets and mentions that occur internal to communities for each of the four community types.}
+% 	\centering
+% 	\begin{tabular}{l | c c}
+% 		Community Type & Percentage of Retweets Internal & Percentage of Mentions Internal \\
+% 		\hline
+% 		Structural & 47.5 & 70.9 \\
+% 		Activity-based & 54.7 & 75.6 \\
+% 		Topic-based & 49.4 & 66.8  \\
+% 		Interaction-based & \textbf{67.2} & \textbf{84.2}
+% 	\end{tabular}
+% 	\label{Tab-mentionretweets}
+% \end{table}
+%
+% Let $I_{c}$ be the number of conversations (defined as a retweet or mention) occuring internal to community $c$, and let $|\mathcal{C}|_{c}$ be the size of community $c$.
+Finally, let $N$ be the total number of conversations, both internal and external, involving the nodes.
+An alternative scoring function is then
+% \begin{align}
+% 	\frac{1}{N}\sum_{c} \frac{I_{c}}{|\mathcal{C}_{c}|}.
+% 	\label{conversation-metric}
+% \end{align}
+% That is, this measures the average number of internal conversations per user in a community.
+This will be maximized when the communities are small and the number of internal conversations are large compared to the total number of conversations.
+%
+% \begin{table}
+% 	\caption{The metric (\ref{conversation-metric}) for the four community types, computed using the held-out data.}
+% 	\centering
+% 	\begin{tabular}{l | c c}
+% 		Community Type & Retweets & Mentions \\
+% 		\hline
+% 		Structural & 0.0289 & 0.0344 \\
+% 		Activity-based & 0.0793 & 0.0645 \\
+% 		Topic-based & 0.1031 & 0.1020  \\
+% 		Interaction-based & 0.0690 & 0.0977
+% 	\end{tabular}
+% 	\label{Tab-mentionretweets2}
+% \end{table}
+%
+% \begin{table}
+% 	\caption{The value of the conversation metric proposed by Elisa, averaged over all of the communities in a given covering.}
+% 	\centering
+% 	\begin{tabular}{ l | c c}
+% 		Community Type & Mentions & Retweets \\
+% 		\hline
+% 		Structural & 2.9347 & 0.4734 \\
+% 		Activity-based & \textbf{3.3893} & 0.5173 \\
+% 		Topic-based & 2.5944 & 0.5580 \\
+% 		Interaction-based & 2.1984 & \textbf{1.1069}
+% 	\end{tabular}
+% \end{table}
 

### 2014-07-14 code/community_sizes.R

@@ -11,7 +11,7 @@ max.comm.size = 811
 
 pdf(sprintf('figures/comm_sizes_ecdf.pdf'))
 par(mar=c(4.5,5,2,1), cex.lab = 2, cex.axis = 2)
-plot(0, cex = 0, log = 'xy', type = 'l', xlim = c(1, max.comm.size), ylim = c(1e-4, 1), xlab = 'c', ylab = 'Proportion of communities larger than c')
+plot(0, cex = 0, log = 'xy', type = 'l', xlim = c(1, max.comm.size), ylim = c(1e-4, 1), xlab = 'Size of community (s)', ylab = 'Proportion of communities larger than s')
 
 for (cur.ind in 1:4){
 	cat(sprintf('\n\n====\n\n'))

### 2014-07-14 paper-for_arxiv/paper.tex
Minor changes to acknowledgments section.

@@
 
-Thanks to Cesar Flores, Lu\'is Seoane, Kevin Stadler, Jody Wright, and Nix Barnett to their contributions of preliminary ideas related to this paper and to Michelle Girvan, William Rand, and Aaron Clauset for their valuable comments and suggestions.
-This work was partially
+Thanks to Cesar Flores, Lu\'is Seoane, Kevin Stadler, Jody Wright, and Nix Barnett for their contributions to preliminary ideas related to this paper and to Michelle Girvan, William Rand, and Aaron Clauset for their valuable comments and suggestions.
+This work was partially funded by...
 

### 2014-07-24 paper-for_arxiv/results.tex
fixing normalized mutual information figure

@@
   \centering
-\includegraphics[width=0.50\textwidth]{nmi_singletons.pdf}
+  \begin{tabu}{cl}
+    \toprule
+    Normalized Mutual Information & Community Types \\
+    \midrule
+    \multirow{8}[8]{*}{\includegraphics[width=0.50\textwidth]{nmi_singletons.pdf}}&0---Structural \bigstrut\\
+    &1-6---Activity-Based with Lags 1-6\bigstrut\\
+    %&2---Activity-Based with Lag 2\bigstrut\\
+    %&3---Activity-Based with Lag 3\bigstrut\\
+    %&4---Activity-Based with Lag 4\bigstrut\\
+    %&5---Activity-Based with Lag 5\bigstrut\\
+    %&6---Activity-Based with Lag 6\bigstrut\\
+    &7---Topic-Based \bigstrut\\
+    &8---Interaction-Based with Mentions\bigstrut\\
+    &9---Interaction-Based with Retweets\bigstrut\\
+    &10---Interaction-Based with both \bigstrut\\
+    &\,\,\,\,\,\,\,\,\,\,\,\,\,\,Mentions and Retweets\bigstrut\\
+    &\bigstrut\\
+    \bottomrule
+\end{tabu}
 \caption{The normalized mutual information between the coverings inferred from the different community types. 
-Community type 0 corresponds to the structural communities, community types 1 through 6 correspond to the activity-based communities with lag 1 through 6 transfer entropies, community type 7 corresponds to the topic-based communities, and community types 8, 9, and 10 correspond to the interaction-based communities using mentions, retweets, and both mentions and retweets.
+%Community type 0 corresponds to the structural communities, community types 1 through 6 correspond to the activity-based communities with lag 1 through 6 transfer entropies, community type 7 corresponds to the topic-based communities, and community types 8, 9, and 10 correspond to the interaction-based communities using mentions, retweets, and both mentions and retweets.
 Values of normalized mutual information close to 1 indicate similarity in the community structure, while values close to 0 indicate dissimilarity.

### 2014-07-24 code/compare_weights_intraintermulti_totalmass.py
Added communities and size dist for TE.
I added the community sizes for the TE{1, 2, 3, 5, 6} communities.

@@ -1,0 +1,204 @@
+# A script to compare the weights for
+# edges inside / outside of a community
+# where we use a community of type C
+# and a weight of type B.
+# 
+# For example, we might consider the
+# communities based on transfer entropy
+# and the weights based on hashtags.
+# 
+# This allows us to narrow in on the 
+# characteristics of the community
+# types.
+
+#	DMD, 23 April 2014
+
+from itertools import islice
+import numpy
+import collections
+
+# The community type used to determine the
+# weights on edges.
+
+# weight_type = 'TE4'
+# weight_type = 'hashtag'
+# weight_type = 'mention-retweet'
+
+# The community type used to determine the
+# community memberships.
+
+# label_type = 'struc'
+# label_type = 'TE4'
+# label_type = 'hashtag'
+# label_type = 'mention-retweet'
+
+# The community detection algorithm, either 
+# '', which corresponds to OSLOM, or 'i',
+# which corresponds to InfoMap.
+
+comm_alg = ''
+
+# comm_alg = 'i' # For InfoMap
+#
+# comm_alg = 'WSBM_K10' # For WSBM
+
+label_type_to_number = {'struc' : 0, 'TE4' : 4, 'hashtag' : 7, 'mention-retweet' : 10}
+
+# for weight_type in ['TE4', 'hashtag', 'mention-retweet']:
+for weight_type in ['TE4']:
+	# for label_type in ['struc', 'TE4', 'hashtag', 'mention-retweet']:
+	# for label_type in ['struc', 'mention-retweet']:
+	for label_type in ['TE4']:
+		print 'Working on {}/{} pairing...'.format(weight_type, label_type)
+
+		if 'TE' in weight_type:
+			lag = weight_type.split('E')[1]
+			weight_file = '../data/content-free/directedweightsTE/edge_weights_bin10minutes_lag_{}_withMMBIAS.dat'.format(lag)
+		elif weight_type == 'hashtag':
+			weight_file = '../data/content-full/twitter_network_hashtags_weighted.txt'
+		elif weight_type == 'mention-retweet':
+			weight_file = '../data/content-full/twitter_network_contentfull_weighted_arithmeticmean.txt'
+
+		label_file  = '../data/coverings/communities{}{}_comp.txt'.format(label_type_to_number[label_type], comm_alg)
+
+		# Generate a dictionary of the form
+		# {user_id : community_id} from the 
+		# communities based on the labels.
+
+		comm_dict = collections.defaultdict(set)
+		comm_count = 0
+
[…]

### 2014-07-24 code/parse_intraintermulti_mass.R

@@ -1,0 +1,19 @@
+cat(sprintf('comm\tsum intra\tmean intra\tsum inter\tmean inter\tmore in than out\n'))
+
+num.comms = 100
+
+more.in.than.out = rep(0, num.comms)
+
+for (comm.ind in 0:(num.comms-1)){
+	intra = read.csv(sprintf('../data/edges-by-type/interintramulti_labels-TE4_weights-TE4_comm%g_intra.dat', comm.ind), header = FALSE)$V1
+	
+	# inter = read.csv(sprintf('../data/edges-by-type/interintramulti_labels-TE4_weights-TE4_comm%g_inter_in.dat', comm.ind), header = FALSE)$V1
+	inter = read.csv(sprintf('../data/edges-by-type/interintramulti_labels-TE4_weights-TE4_comm%g_inter_out.dat', comm.ind), header = FALSE)$V1
+	
+	if (mean(intra, na.rm = TRUE) > mean(inter, na.rm = TRUE)){
+		more.in.than.out[comm.ind + 1] = 1
+	}
+	
+	cat(sprintf('%g\t%g\t%g\t%g\t%g\t%g\n',comm.ind, sum(intra, na.rm = TRUE), mean(intra, na.rm = TRUE), sum(inter, na.rm = TRUE), mean(inter, na.rm = TRUE), more.in.than.out[comm.ind + 1]))
+}
+

### 2014-07-25 paper-for_arxiv/appendices.tex
making some changes

@@
 
-\section{Appendix B: Comparing Edges Across Different Community Types}
-
-\begin{figure}[!h]
-	\centering
-	\includegraphics[width=1\textwidth]{densities-edges.eps}
-	\caption{The density of edge weights for different community types (rows) and weight types (columns).
-The red,  blue, and magenta values below each collection of densities indicate the median of weight on intra-, inter-, and mixed-edges, respectively.}
-	\label{Fig-distributions_by_types}
-\end{figure}
+%\section{Appendix B: Comparing Edges Across Different Community Types}

### 2014-07-25 paper-for_arxiv/results.tex
making some changes

@@
 
-\begin{table}
-	\caption{The percentage of intra-, inter-, and mixed-edges associated with the coverings for each of the four community types.}
-	\centering
-	\begin{tabular}{l | r r r}
-		Community Type & Intra & Inter & Mixed \\
-		\hline
-		Structural & 7.5 & 87.0 &  5.5 \\
-		Activity-based & 10.7 & 81.9 & 7.4 \\
-		Topic-based & 7.3 & 89.0  & 3.7 \\
-		Interaction-based & 42.3 & 47.9 & 9.8
-	\end{tabular}
-\end{table}
+%\begin{table}
+%	\caption{The percentage of intra-, inter-, and mixed-edges associated %with the coverings for each of the four community types.}
+%	\centering
+%	\begin{tabular}{l | r r r}
+%		Community Type & Intra & Inter & Mixed \\
+%		\hline
+%		Structural & 7.5 & 87.0 &  5.5 \\
+%		Activity-based & 10.7 & 81.9 & 7.4 \\
+%		Topic-based & 7.3 & 89.0  & 3.7 \\
+%		Interaction-based & 42.3 & 47.9 & 9.8
+%	\end{tabular}
+%\end{table}
 
@@
 If the community structure were arbitrary, the edge weights would be independent of the edge type, and all three conditional distributions would be identical.
-The densities associated with these distributions are shown in Figure~\ref{Fig-distributions_by_types}, included in Appendix B.
+The densities associated with these distributions are shown in Figure~\ref{Fig-distributions_by_types}.
+\begin{figure}[!h]
+	\centering
+	\includegraphics[width=1\textwidth]{densities-edges.eps}
+	\caption{The density of edge weights for different community types (rows) and weight types (columns).
+The red,  blue, and magenta values below each collection of densities indicate the median of weight on intra-, inter-, and mixed-edges, respectively.}
+	\label{Fig-distributions_by_types}
+\end{figure}
 

### 2014-07-25 paper-for_arxiv/paper.tex
added elisa's financial support
Added Dave's acknowledgements.
fixing normalized mutual information figure
adding citation and removing asterick

@@
 \usepackage{multirow}
+\usepackage{bigstrut}
+\usepackage{booktabs}
+\usepackage{multirow,bigstrut}
+\usepackage{tabu}
 \usepackage{authblk}
@@
 \title{
-Followers Are Not Enough: Beyond Structural Communities in Online Social Networks
+Followers Are Not Enough: Beyond Structural Communities in Online Social Networks \\Followers Are Not Enough: A Question-Oriented Approach to Community Detection
  }
@@
 Thanks to Cesar Flores, Lu\'is Seoane, Kevin Stadler, Jody Wright, and Nix Barnett for their contributions to preliminary ideas related to this paper and to Michelle Girvan, William Rand, and Aaron Clauset for their valuable comments and suggestions.
-This work was partially funded by...
+Elisa Omodei is partially supported by a PhD grant from the Région Ile-de-France (DIM 2011) and by the French National Agency of Research (ANR) through the grant Algopol (ANR-12-CORD-0018).
+We are grateful to DARPA for the support of David Darmon.
 

### 2014-07-25 paper-for_arxiv/methods.tex
adding citation and removing asterick
adding citation

@@
 
-This last criterion in particular poses a problem because the majority of community detection algorithms developed so far are built to find partitions of a network and few are aimed at finding overlapping communities \cite{BaumesGKMP05,PalEtAl05,ZhaWanZha07,Gre07,PhysRevE.77.016107,Lancichinetti2009,PhysRevE.80.016105,Kovacs2010}.
+This last criterion in particular poses a problem because the majority of community detection algorithms developed so far are built to find partitions of a network and few are aimed at finding overlapping communities \cite{Aicher26062014,BaumesGKMP05,PalEtAl05,ZhaWanZha07,Gre07,PhysRevE.77.016107,Lancichinetti2009,PhysRevE.80.016105,Kovacs2010}.
 Among these methods, even fewer deal with directed or weighted networks.
@@
 \begin{equation}
-h_i(u) = n_i(u) * \log{ \frac{N}{n_i} }
+h_i(u) = n_i(u)\log{ \frac{N}{n_i} }
 \end{equation}

### 2014-07-25 paper-for_arxiv/paper.tex
Taking care of proper Journal formatting

@@
-%File: formatting-instruction.tex
+%%File: formatting-instruction.tex
 \documentclass[]{article}
-%\documentclass{comnet}
+%\usepackage{times}
+%\usepackage{helvet}
+%\usepackage{courier}
+%\usepackage{amssymb, amsmath, amsthm}
+%\usepackage{graphicx}
+%\usepackage{multirow}
+%\usepackage{bigstrut}
+%\usepackage{booktabs}
+%\usepackage{multirow,bigstrut}
+%\usepackage{tabu}
+\usepackage{authblk}
+%\usepackage{color}
+%\usepackage{subfigure}
+%\usepackage{appendix}
+%%\frenchspacing
+%%\setlength{\pdfpagewidth}{8.5in}
+%%\setlength{\pdfpageheight}{11in}
+%\textwidth=126mm
+
+%Before this was old one
+
+%\documentclass{COMNET}%%%%where comnet is the template name
+%%%% To get the unnumbered reference the authors should use unnumbib in the optional of \documentclass.
+%%%% Ex:\documentclass[unnumbib]{comnet}
+
+\usepackage{amsmath} %for dealing with mathematics,
+\usepackage{amsfonts}	%for dealing with mathematics,
+\usepackage{amsthm} %for dealing with theorem environments,
+%\usepackage{hyperref} %for linking the cross references % CA: I couldn't get it to work properly with this package
+\usepackage{graphicx} %for dealing with figures.
+%\usepackage{algorithm}
+%\usepackage{algorithmic} %for describing algorithms
+\usepackage{subfigure} %for getting the subfigures e.g., "Figure 1a and 1b" etc.
 \usepackage{times}
 \usepackage{helvet}
-\usepackage{courier}
-\usepackage{amssymb, amsmath, amsthm}
-\usepackage{graphicx}
+%\usepackage{courier}
 \usepackage{multirow}
@@
 \usepackage{color}
-\usepackage{subfigure}
+%\usepackage{subfigure}
 \usepackage{appendix}
-%\frenchspacing
-%\setlength{\pdfpagewidth}{8.5in}
-%\setlength{\pdfpageheight}{11in}
-\textwidth=126mm
-\pdfinfo{
-/Title (Followers Are Not Enough: Beyond Structural Communities in Online Social Networks)
-/Author (David Darmon, Elisa Omodei, Joshua Garland)
-/Keywords (community detection, functional communities, social network analysis)}
+\usepackage{url} %CA: I want to use hyperref -> but we get errors (see above)
+\usepackage{enumitem}
+
+\usepackage[sort&compress,numbers]{natbib} % CA: comnet.cls file had errors -> This is a fix%
+\renewcommand{\bibnumfmt}[1]{\textbf #1.\ }
+\setlength{\bibsep}{0pt}
+
+%\pdfinfo{
+%/Title (Followers Are Not Enough: Beyond Structural Communities in Online %Social Networks)
+%/Author (David Darmon, Elisa Omodei, Joshua Garland)
+%%/Keywords (community detection, functional communities, social network analysis)}
 
@@
 % Uncomment if you want to use section numbers % and change the 0 to a 1 or 2
-\setcounter{secnumdepth}{0}
+%\setcounter{secnumdepth}{0}
 
@@
 
-% Title, Author, and Address Information
-\title{
-Followers Are Not Enough: Beyond Structural Communities in Online Social Networks \\Followers Are Not Enough: A Question-Oriented Approach to Community Detection
+\title{Followers Are Not Enough: Beyond Structural Communities in Online Social Networks \\Followers Are Not Enough: A Question-Oriented Approach to Community Detection}
+
+ \author[1]{David Darmon}
+ \author[2]{Elisa Omodei}
+ \author[3]{Joshua Garland}
+ \affil[1]{University of Maryland\\
+ Dept. of Mathematics}
+ \affil[2]{
+ LaTTiCe (CNRS, ENS, Paris 3)\\
+ ISC-PIF}
+ \affil[3]{
+ University of Colorado at Boulder\\
+ Dept. of Computer Science
  }
+
+%\shorttitle{Followers Are Not Enough}
+%\shortauthorlist{D. Darmon \emph{ET AL.}} %%% for verso running head
+
+%\author{
+%%%%% First author details
+%\name{David Darmon$^*$}
+%\address{Department of Mathematics, University of Maryland, College Park, MD 20740\email{$^*$Corresponding author: ddarmon@math.umd.edu}}
+%%%%%%%% Second author details
+%\name{Elisa Omodei}
+%\address{LaTTiCe (CNRS, ENS, Paris 3)\\
+% ISC-PIF}
+%%%%%%%%
+%\and
+%%%%%%%% Third author details
+%\name{Joshua Garland}
+%\address{Department of Computer Science, University of Colorado, Boulder, CO 80309}
+%}
+
+\maketitle
 
@@
 
- \author[1]{David Darmon}
- \author[2]{Elisa Omodei}
- \author[3]{Joshua Garland}
- \affil[1]{University of Maryland\\
- Dept. of Mathematics}
- \affil[2]{
- LaTTiCe (CNRS, ENS, Paris 3)\\
- ISC-PIF}
- \affil[3]{
- University of Colorado at Boulder\\
- Dept. of Computer Science
- }
-
 \maketitle
@@
 %\begin{quote}
+%The Keywords
+%Community detection, functional communities, social network analysis
+
 Community detection in online social networks is typically based on the analysis of the explicit connections between users, such as ``friends" on Facebook and ``followers" on Twitter.
@@
 
-\bibliographystyle{comnet}
+%\bibliographystyle{comnet}
+\bibliographystyle{plainnat}
 \bibliography{references.bib}

### 2014-07-29 paper-for_arxiv/intro.tex
fixing elderly people

@@
 On a more abstract level, a user might consider themselves part of a community of people discussing similar topics.
-We might also define communities as collections of people who exhibit similar behaviors on a service, as in communities of teenagers vs.\ elderly users.
+We might also define communities as collections of people who exhibit similar behaviors on a service, as in communities of similar activity profiles, \emph{e.g.,} weekday versus weekend users or daytime versus nighttime users.
 We can characterize these types of communities based on the types of questions we might ask about them:

### 2014-07-29 paper-for_arxiv/intro.tex
working on influence stuff, lots of notes but not finished

@@
 The main tools for answering this question stem from information theory.
-We consider each user on an online social network as an information processing unit, but ignore the content of their messages.
-In particular, our current activity-based approach was originally motivated by a methodology used to detect functional communities within populations of neurons~\cite{shalizi2007discovering}.
-Similar information theoretic approaches have been used with data arising from online social networks to gain insight into local user behavior~\cite{darmon2013understanding}, to detect communities based on undirected information flow~\cite{darmon2013detecting}, and to perform link detection~\cite{ver2012information}.
+For this approach, we consider each user on Twitter as an information processing unit, but ignore the content of their tweets, and weight the directed edges between users with the so-called \emph{transfer entropy}.
+This activity-based approach was motivated by a methodology originally used to detect functional communities within populations of neurons~\cite{shalizi2007discovering}.
+Information theoretic approaches have been used for data arising from online social networks to gain insight into local user behavior~\cite{darmon2013understanding}\alert{using ....}, to detect communities based on \emph{undirected} information flow~\cite{darmon2013detecting} using mutual information, and to perform link detection\alert{Dave, is this right or is it network inference and link prediction}~\cite{ver2012information}.
+
+While various information theoretic measures has been applied previously to the analysis of networks arising in online social media~\cite{ver2012information,darmon2013detecting}, to the best of our knowledge this is the first use of transfer entropy for community detection in social media networks.
+Transfer Entropy was originally proposed in~\cite{schreiber2000measuring} as an information theoretic measure of \emph{directed} information flow.
+Transfer entropy is often thought of as being a measure of \emph{influence} in an information theoretic sense; this is because if the transfer entropy between a user $u$ and a user $v$ is positive, then this relationship is considered causal in the Granger sense~\cite{granger1963economic}.
+Effectively, if there is a positive transfer entropy from user $u$ to $v$ then there is a reduction in uncertantiy about user \alert{$u$/$v$} tweeting given the recent tweet history of user \alert{$u$/$v$}.
+This can easily be interpreted as a form of influence, if user \alert{$u$/$v$} reduces the uncertainty about \alert{$u$/$v$} tweeting then it may be the case that this was a form of social influence.
+We are fully aware that the difference between information theoretic and social influence are different but think this may be an interesting area to explore.
+Later we show that using this measure alone we can detect ``influential users" who are also listed as \alert{Forbes ...}.
+We instead treat this weighting as a way to quantify which users activity are quantified by each other, i.e., communities that use twitter in similar ways.
 
@@
 More recent work has considered the dynamics of communities based on structural links in Facebook~\cite{nguyen2011adaptive} and how structural communities impact mentions and retweets on Twitter~\cite{grabowicz2012social}.
-
-Information theoretic, activity-based approaches have been applied previously to the analysis of networks arising in online social media~\cite{ver2012information,darmon2013detecting}, but to the best of our knowledge this is the first use of transfer entropy, an information theoretic measure of directed influence, for community detection.
 
@@
 However, this study focused on data collected based on particular topics (country music, tennis, and basketball), and not on a generic subpopulation of Twitter users.
-Moreover, it did not explore the differences in community structure resulting from the different network weightings, and focuses on aggregate statistics (community size, network statistics, etc.).
+Moreover, it did not explore the differences in community structure resulting from the different network weightings, and focused on aggregate statistics (community size, network statistics, etc.).
 Another notable exception is~\cite{kao2013talison}, where the authors used a tensor representation of user data to incorporate retweet and hashtag information into a study of the social media coverage of the Occupy Movement.

### 2014-07-29 paper-for_arxiv/intro.tex
fixing influence stuff in intro

--- 2014-07-29 paper-for_arxiv/intro.tex
@@
 	\item \textbf{Structure-based:} Who are your stated friends? Whom do you follow?
-	\item \textbf{Activity-based:} Whom do you act like?
+	\item \textbf{Activity-based:} Whose activity influences you?
 	\item \textbf{Topic-based:} What do you talk about?
@@
 
-The activity-based approach is motivated by the question of which individuals act in a homogeneous manner, e.g., which users use a service in a similar way.
-The main tools for answering this question stem from information theory.
-We consider each user on an online social network as an information processing unit, but ignore the content of their messages.
-In particular, our current activity-based approach was originally motivated by a methodology used to detect functional communities within populations of neurons~\cite{shalizi2007discovering}.
-Similar information theoretic approaches have been used with data arising from online social networks to gain insight into local user behavior~\cite{darmon2013understanding}, to detect communities based on undirected information flow~\cite{darmon2013detecting}, and to perform link detection~\cite{ver2012information}.
+The activity-based approach is motivated by the question of which user's activity ``influences" the activity of another user, \emph{i.e.}, which user(s) cause a user(s) to interact with the network.
+With this question in mind, a community can then be thought of as those individuals who ``influence" each other's activity on the network.
+In general, quantifying the influence of one user on another is a large and ill-understood problem.
+For that reason, we focus on a smaller subset of that problem, \emph{viz.}, quantifying influence purely from an information theoretic framework.
+%The primary tool for answering this question is the  For this approach
+%\alert{Maybe add a sentence hedging influence}
+
+To accomplish this, we consider each user on Twitter as an information processing unit, but completely ignore the \emph{content} of their tweets.
+We then weight the directed edges (the reported follower-followee relationships) between users with the so-called \emph{transfer entropy} introduced in~\cite{schreiber2000measuring}.
+Transfer entropy is an information theoretic measure of \emph{directed} information flow.
+It has been shown~\cite{ver2012information} that a positive transfer entropy between a user $u$ and a follower $f$ indicates that $u$ ``influences" $f$, or that $u$ and $f$ share a common influencer.
+In particular, positive transfer entropy from a user $u$ to a follower $f$ implies that this relationship is causal in the Granger sense~\cite{granger1963economic}.
+As a result, transfer entropy is often thought of as a measure of ``influence" in an information theoretic sense.
+Thus, communities detected in this way have members whose tweet histories are causally related in a Granger sense, \emph{i.e.}, members who ``influence" each others activity on the network.
+%Obviously the concept of ``influence" is extremely broad and quantifying influence in a social network is neither well understood nor well defined in the literature.
+
+We want to reiterate that we do not imply that this information theoretic measure completely captures social ``influence" in general.
+However, we conjecture, it does capture a useful subset of that relationship.
+In this paper, when we say \emph{influence} we explicitly refer to a reduction in uncertainty of whether user $u$ will be active or not given the past history of a user $f$.
+We will however show later in this paper that this information theoretic measure of influence agrees with other concepts of influence such as the Forbes list of ``Top 10 Social Media Influencers" and corroborates with the so-called strength of weak ties\cite{granovetter1973strength}.
+
+%emphasize that we are not saying these casual relationships necessarily suggest social or \alert{??
+} influence, but simply a casual re.
+In this paper when we say that a user $u$ influences a user $f$ we simply mean that there is a reduction in uncertanity about whether user $u$ will be active or not given the past history of user $f$.
+We will show that this information theoretic view of influence is a useful and
+%Effectively, if there is a positive transfer entropy from user $u$ to $v$ then there is a reduction in uncertainty about user \alert{$u$/$v$} tweeting given the recent tweet history of user \alert{$u$/$v$}.
+This can and has been interpreted as a form of influence, if user \alert{$u$/$v$} reduces the uncertainty about \alert{$u$/$v$} tweeting then it may be the case that this was a form of social influence.
+We are fully aware that the difference between information theoretic and social influence are different but think this may be an interesting area to explore.
+Later we show that using this measure alone we can detect ``influential users" who are also listed as \alert{Forbes ...}.
+We instead treat this weighting as a way to quantify which users activity are quantified by each other, i.e., communities that use twitter in similar ways.
+%A positive value for the transfer entropy of the user $u$ on $f$ indicates that $u$ influences $f$, or that $u$ and $f$ share a common influencer~\cite{ver2012information}. $T_{u \to f}$
+%think this paragrpah should be something like we use it as a way to quantify activity but we think it may have applicaitons in influence detection for example if one user has high transfer entropy with an entire community, then this may imply that user has strong social influence on the activity of a given community defined with this weighting scheme.
+For example, Denver Broncos tweet that they fired John Elway and an entire network of Broncos fans begins tweeting this may be a rank of influence.
+
+This activity-based approach was motivated by a method used by Shalizi \emph{et al.} in ~\cite{shalizi2007discovering} to detect functional communities within populations of neurons, but to the best of our knowledge, this is the first use of transfer entropy for community detection in online social networks.
+Various other information theoretic approaches have been used successfully to analyze online social networks, \emph{e.g.,} to gain insight into local user behavior~\cite{darmon2013understanding}, to detect communities based on \emph{undirected} information flow~\cite{darmon2013detecting}, and to perform network inference and link prediction\cite{ver2012information}.
+%While various information theoretic measures has been applied previously to the analysis of networks arising in online social media~\cite{ver2012information,darmon2013detecting},
 

### 2014-07-30 paper-for_arxiv/intro.tex
fixing some stuff in intro

@@
 On a more abstract level, a user might consider themselves part of a community of people discussing similar topics.
-We might also define communities as collections of people who exhibit similar behaviors on a service, as in communities of similar activity profiles, \emph{e.g.,} weekday versus weekend users or daytime versus nighttime users.
+We might also define communities as collections of people who exhibit similar activity profiles and seem to ``influence" each other's activity on the network.
 We can characterize these types of communities based on the types of questions we might ask about them:
@@
 	\item \textbf{Structure-based:} Who are your stated friends? Whom do you follow?
-	\item \textbf{Activity-based:} Whose activity influences you?
+	\item \textbf{Activity-based:} Whose activity influences your activity?
 	\item \textbf{Topic-based:} What do you talk about?
@@
 We propose looking at when and how communities motivated by these different questions overlap, and whether different approaches to asking the question, ``What community are you in?'' leads to different insights about a social network.
-For example, a user on Twitter might connect mostly with computational social scientists, talk mostly about machine learning, interact solely with close friends (who may or may not be computational social scientists), and utilize the service only on nights and weekends.
+For example, a user on Twitter might connect mostly with computational social scientists, utilize the service nearly every time a particular user or group of users is active, talk mostly about machine learning, and interact solely with close friends (who may or may not be computational social scientists).
 Each of these different `profiles' of the user highlight different views of the user's social network, and represent different types of communities.
@@
 
-The activity-based approach is motivated by the question of which user's activity ``influences" the activity of another user, \emph{i.e.}, which user(s) cause a user(s) to interact with the network.
-With this question in mind, a community can then be thought of as those individuals who ``influence" each other's activity on the network.
+The activity-based approach is motivated by the question of ``Which user's activity ``influences" the activity of another user?", %, \emph{i.e.}, which user(s) cause a user(s) to interact with the network.
+ with this question in mind, a community can then be thought of as those individuals who ``influence" each other's activity on the network.
 In general, quantifying the influence of one user on another is a large and ill-understood problem.
@@
 Transfer entropy is an information theoretic measure of \emph{directed} information flow.
-It has been shown~\cite{ver2012information} that a positive transfer entropy between a user $u$ and a follower $f$ indicates that $u$ ``influences" $f$, or that $u$ and $f$ share a common influencer.
-In particular, positive transfer entropy from a user $u$ to a follower $f$ implies that this relationship is causal in the Granger sense~\cite{granger1963economic}.
+It has been shown in~\cite{ver2012information} that a positive transfer entropy between a user $u$ and a follower $f$ indicates that $u$ ``influences" $f$, or that $u$ and $f$ share a common influencer.
+In particular, positive transfer entropy from the tweet history of a user $u$ to a follower $f$'s tweet history implies that this relationship is causal in the Granger sense~\cite{granger1963economic}.
 As a result, transfer entropy is often thought of as a measure of ``influence" in an information theoretic sense.
@@
 
-We want to reiterate that we do not imply that this information theoretic measure completely captures social ``influence" in general.
+We want to reiterate that we do not imply that this information theoretic measure completely captures social influence in general.
 However, we conjecture, it does capture a useful subset of that relationship.
-In this paper, when we say \emph{influence} we explicitly refer to a reduction in uncertainty of whether user $u$ will be active or not given the past history of a user $f$.
-We will however show later in this paper that this information theoretic measure of influence agrees with other concepts of influence such as the Forbes list of ``Top 10 Social Media Influencers" and corroborates with the so-called strength of weak ties\cite{granovetter1973strength}.
+In this paper, when we say \emph{influence} we explicitly refer to a reduction in uncertainty of whether a follower $f$ will be active or not given the past history of a user $u$.
+We will however show later in this paper that this information theoretic measure of influence agrees with other concepts of influence such as the Forbes list of ``Top 10 Social Media Influencers" and corroborates with the so-called strength of weak ties~\cite{granovetter1973strength}.
 
@@
 This activity-based approach was motivated by a method used by Shalizi \emph{et al.} in ~\cite{shalizi2007discovering} to detect functional communities within populations of neurons, but to the best of our knowledge, this is the first use of transfer entropy for community detection in online social networks.
-Various other information theoretic approaches have been used successfully to analyze online social networks, \emph{e.g.,} to gain insight into local user behavior~\cite{darmon2013understanding}, to detect communities based on \emph{undirected} information flow~\cite{darmon2013detecting}, and to perform network inference and link prediction\cite{ver2012information}.
+Various other information theoretic approaches have been used successfully to analyze online social networks, \emph{e.g.,} to gain insight into local user behavior~\cite{darmon2013understanding}, to detect communities based on \emph{undirected} information flow~\cite{darmon2013detecting}, and to perform network inference and link prediction\cite{ver2012information}, but not transfer entropy applied to community detection.
 %While various information theoretic measures has been applied previously to the analysis of networks arising in online social media~\cite{ver2012information,darmon2013detecting},

### 2014-07-30 paper-for_arxiv/methods.tex
fixing influence stuff in intro
consistency in methods

@@
 From this starting point, we can view the behavior of a user $u$ on Twitter as a point process, where at any instant $t$ the user has either emitted a tweet ($X_{t}(u) = 1$) or remained silent ($X_{t}(u) = 0$).
-This is the view of a user's dynamics taken in~\cite{ver2012information} and~\cite{darmon2013understanding}.
+This is the view of a user's dynamics taken in~\cite{darmon2013understanding} and~\cite{ver2012information}.
 Thus, we reduce all of the information generated by a user on Twitter to a time series $\{ X_{t}(u)\}$ where $t$ ranges over the time interval for which we have data (9 weeks in this case).
-Because status updates are only collected in discrete, 1-second time intervals, it is natural to consider only the discrete times $t = 1 \text{ s}, 2 \text{ s}, \ldots, $ relative to a reference time.
-We can then compute the flow of information between two users $u$ and $v$ by computing the transfer entropy between their time series $X_{t}(u)$ and $X_{t}(v).$
-
-For the communities based on transfer entropy, we weight each edge from a user $u$ to a follower $f$ by the estimated transfer entropy of the user $u$ on $f$, 
-\begin{align}
-	w_{u \to f}^{\text{TE}(k)} = \widetilde{\text{TE}}_{X(u) \to X(f)}^{(k)}. \label{Eqn-EW-activity}
-\end{align}
-A positive value for the transfer entropy of the user $u$ on $f$ indicates that $u$ influences $f$, or that $u$ and $f$ share a common influencer~\cite{ver2012information}.
-See Appendix A for a detailed introduction to transfer entropy and its estimation from data.
+Because status updates are only collected in discrete, 1-second time intervals, it is natural to consider only the discrete times $t = 1 \text{s}, 2 \text{s}, \ldots, $ relative to a reference time.
 
@@
 Thus, the new coarsened time series now captures whether or not the user has been active on Twitter over any given ten minute time interval in our data set.
-We then compute the transfer entropy on these coarsened time series taking $k$ to range from 1 to 6, which corresponds to a lag of ten minutes to an hour.
-The choice of lag must balance a trade-off between additional information and sparsity of samples: as we increase the lag, we account for longer range dependencies, but we also decrease the number of samples available to infer a higher dimensional predictive distribution.
+We can then compute the flow of information between two users $u$ and $v$ by computing the transfer entropy between their time series $X_{t}(u)$ and $X_{t}(v).$ See Appendix A for a detailed introduction to transfer entropy and its estimation from data.
+
+For the communities based on transfer entropy, we weighted each edge from a user $u$ to a follower $f$ by the estimated transfer entropy of the user $u$ on $f$, 
+\begin{align}
+	w_{u \to f}^{\text{TE}(k)} = \widetilde{\text{TE}}_{X(u) \to X(f)}^{(k)}. \label{Eqn-EW-activity}
+\end{align}
+As discussed in the introduction, a positive value for the transfer entropy of the user $u$ on $f$ indicates that $u$ influences $f$, or that $u$ and $f$ share a common influencer~\cite{ver2012information}, and that the time series $X(u)$ and $X(f)$, are casually related in a Granger sense.
+
+ We computed the transfer entropy on each coarsened time series with lag $k$ ranging from 1 to 6, this corresponds to a lag of ten minutes to an hour.
+The choice of lag must balance a trade-off between additional information and sparsity of samples: as we increase the lag $k$, we account for longer range dependencies, but we also decrease the number of samples available to infer a higher dimensional predictive distribution, see Appendix A for a discussion.
 Ultimately, due to similarities in the underlying communities we chose a lag-4 transfer entropy.

### 2014-07-30 paper-for_arxiv/results.tex
new figure for comm sizes
starting conc

@@
   \centering
-\includegraphics[width=0.50\textwidth]{comm_sizes_ecdf_loglog.pdf}
+%\includegraphics[width=0.50\textwidth]{comm_sizes_ecdf_loglog.pdf}
+\includegraphics[width=0.6\textwidth,angle=270]{cdf_comm_sizes.eps}
 \caption{The proportion of communities greater than $s$ in size, across the different community types. Note the logarithmic scale on the horizontal and vertical axes.}
@@
 
+\alert{work from here after Crossfit}
 Another interesting example is a community whose topics tend to focus on Denver and Colorado.

### 2014-07-30 paper-for_arxiv/results.tex

--- 2014-07-25 paper-for_arxiv/results.tex
@@
 This indicates that these users react to the same events and issues regarding Colorado and are therefore strongly connected in the topic-based and activity-based networks, but at the same time they do not directly interact with each other and are therefore more loosely connected in the interaction-based networks, where they belong to different communities.
-As expected, among the most influential users (in terms of transfer entropy) we find \@Colorado, which is the state official Twitter account, \@ConnectColorado, a page created to connect Coloradans, and CBS Denver account.
 
-Lastly, it is interesting to note that in the top ten most influential users (ranked using the total outgoing strength in the activity-based network) we find two users (Ann Tran and Jessica Northey) that were listed by Forbes in the ``Top 10 Social Media Influencers".
+As an aside, it is interesting to examine who the most influential users are in these communities, as determined by transfer entropy.
+Recall that influence in this context refers to a reduction in uncertainty about a follower(s) activity on Twitter given the tweet history of a followee.
+Said differently, higher transfer entropy, or a higher reduction in uncertainty, implies more influence.
+Interestingly, among the most influential users in these communities, those with highest transfer entropy on average, we find \@Colorado, which is the state official Twitter account, \@ConnectColorado, a page created to connect Coloradans, and the CBS Denver account, a popular news agency.
+This means that these accounts had high influence in terms of their followers activity on Twitter.
+This is not surprising as these communities discuss Colorado and these accounts provide information on this topic.
+However, this does provide a nice sanity check that this measure of activity based influence makes sense and suggests this could be a nice measure for influence on social media if used with other measures.
+This is discussed more in future work.
+
+Lastly, it is interesting to note that two of the Forbes ``Top 10 Social Media Influencers", % ranked using the total outgoing strength in the activity-based network, 
+ happen to be in our network, \emph{viz.}, Ann Tran and Jessica Northey, and transfer entropy also quantified these two users as highly influential.% members, as categorized by transfer entropy. 
+ This does not prove, but suggests that this measure of activity-based or information-theoretic influence may be useful in finding influential members purely based on their temporal tweet history while completely ignoring both tweet content and social class.

### 2014-07-30 paper-for_arxiv/conclusions.tex
fixing influence in conclusion

@@
 %Start of future work**
-Our findings have important implications to a common problem in social network analysis: identification of influential individuals.
+Our findings may have important implications to a common problem in social network analysis: identification of influential individuals---but further work must be carried out.
 Many network measures of influence are based on the various types of centrality (degree, betweenness, closeness, eigenvector, etc.)~\cite{newman2009networks}.
 Most centralities depend explicitly on the structure of the network under consideration.
-But we have seen in our study that a structural network alone is not sufficient to capture user interaction or influence in online social media.
+But we have seen in our study that a structural network alone is not sufficient to capture user interaction or even activity-based influence in online social media.
 Thus, a na\"ive application of centrality measures to a structural network for influence detection may give rise to erroneous results.
 This result has been explored previously~\cite{kitsak2010identification}, and our work further highlights its importance.
-We believe that weighted generalizations of these centralities using transfer entropy might lead to better insights about who is actually influential in an online social network.
+
+Based on our preliminary results, we conjecture that weighted generalizations of these centrality measures using transfer entropy might lead to better insights about who is actually influential in an online social network.
 In addition to exploring this phenomenon further, we plan to explore a broader selection of choices for both the transfer-entropy lag and tweet history time resolution.
@@
 
-This work demonstrates that asking the proper question and then crafting an appropriate weighting scheme to answer that question is an unavoidable first step for community detection in online social media.
+This work demonstrates that asking the proper question, and then crafting an appropriate weighting scheme to answer that question, is an unavoidable first step for community detection in online social media.
 More generally, this work illustrates that without a clear definition of community, many rich and interesting communities present in online social networks remain invisible.

### 2014-07-30 paper-for_arxiv/intro.tex
merged previous works with intro

@@
 The approach of focusing on the structure of networks makes sense for `real-world' sociological experiments, where obtaining additional information about user interactions may be expensive and time-consuming.
-However, with the prevalence of large, rich data sets for online social networks, additional information beyond the structure alone may be incorporated, and these augmented networks more realistically reflects how users interact with each other on social media services~\cite{grabowicz2012social}.
+However, with the prevalence of large, rich data sets for online social networks, additional information beyond the structure alone may be incorporated, and these augmented networks more realistically reflects how users interact with each other on social media services~\cite{nguyen2011adaptive},~\cite{grabowicz2012social}.
 
@@
 The content contains a great deal of information about the communication between users.
+There are two broad approaches to topic-based communities in the literature.
+\cite{rossi2012conversation} used a set of users collected based on their use of a single hashtag, and tracked the formation of follower and friendship links within that set of users.
+In~\cite{lim2012following}, the authors chose a set of topics to explore, and then seeded a network from a celebrity chosen to exemplify a particular topic.
+Both approaches thus begin with a particular topic in mind, and perform the data collection accordingly.
+Other approaches use probabilistic models for the topics and treat community membership as a latent variable~\cite{yin2012latent}.
 For example, a popular approach to analyzing social media data is to use Latent Dirichlet Allocation (LDA) to infer topics based on the prevalence of words within a status~\cite{zhao2011comparing,michelson2010discovering}.
@@
 This allows us to generate a network based on conversations and user interactions.
+A few works already focused on this type of communities.
+For example, \cite{conover2011political} considered both mention and retweet networks in isolation for a collection of users chosen for their political orientation.
+In~\cite{deitrick2013mutually}, the authors construct a dynamic network based on simple time-windowed counts of mentions and retweets, and use the evolution of this network to aid in community detection.
+
+Previous research on communities in social networks focused almost exclusively on different network types in isolation.
+A notable exception to the analysis of isolated types of communities is~\cite{lim2012tweets}, which considered both structure-based and interaction-based communities on Twitter.
+However, this study focused on data collected based on particular topics (country music, tennis, and basketball), and not on a generic subpopulation of Twitter users.
+Moreover, it did not explore the differences in community structure resulting from the different network weightings, and focused on aggregate statistics (community size, network statistics, etc.).
+Another notable exception is~\cite{kao2013talison}, where the authors used a tensor representation of user data to incorporate retweet and hashtag information into a study of the social media coverage of the Occupy Movement.
+The tensor can then be decomposed into factors in a generalization of the singular value decomposition of a matrix, and these factors can be used to determine `salient' users.
+However, this approach focused on data for a particular topic (the Occupy Movement) and did not collect users based on a structural network.
 
@@
 
-\section{Related Work}
-
-Previous research on communities in social networks focused almost exclusively on different network types in isolation.
-For example, an early paper considered the communities, and associated statistics, inferred from a follower network on Twitter~\cite{java2009we}.
-More recent work has considered the dynamics of communities based on structural links in Facebook~\cite{nguyen2011adaptive} and how structural communities impact mentions and retweets on Twitter~\cite{grabowicz2012social}.
-
-For interaction-based communities, \cite{conover2011political} considered both mention and retweet networks in isolation for a collection of users chosen for their political orientation.
-In~\cite{deitrick2013mutually}, the authors construct a dynamic network based on simple time-windowed counts of mentions and retweets, and use the evolution of this network to aid in community detection.
-
-There are two broad approaches to topic-based communities in the literature.
-\cite{rossi2012conversation} used a set of users collected based on their use of a single hashtag, and tracked the formation of follower and friendship links within that set of users.
-In~\cite{lim2012following}, the authors chose a set of topics to explore, and then seeded a network from a celebrity chosen to exemplify a particular topic.
-Both approaches thus begin with a particular topic in mind, and perform the data collection accordingly.
-Other approaches use probabilistic models for the topics and treat community membership as a latent variable~\cite{yin2012latent}.
+%\section{Related Work}
 
@@
 Moreover, they explicitly seed their network to focus around a particular topic (country music, tennis, basketball, etc.)
-
-A notable exception to the analysis of isolated types of communities is~\cite{lim2012tweets}, which considered both structure-based and interaction-based communities on Twitter.
-However, this study focused on data collected based on particular topics (country music, tennis, and basketball), and not on a generic subpopulation of Twitter users.
-Moreover, it did not explore the differences in community structure resulting from the different network weightings, and focused on aggregate statistics (community size, network statistics, etc.).
-Another notable exception is~\cite{kao2013talison}, where the authors used a tensor representation of user data to incorporate retweet and hashtag information into a study of the social media coverage of the Occupy Movement.
-The tensor can then be decomposed into factors in a generalization of the singular value decomposition of a matrix, and these factors can be used to determine `salient' users.
-However, this approach focused on data for a particular topic (the Occupy Movement) and did not collect users based on a structural network.

### 2014-07-31 paper-for_arxiv/intro.tex
modified sentence in intro

@@
 As opposed to this agnostic analysis, we propose and illustrate the importance of a question-focused approach.
-We believe that in order to understand the communities present in a data set, it is important to begin with a clear picture of the community type under consideration, and then perform the network collection and community detection with that community type in mind.
+We believe that in order to understand the communities present in a data set, it is important to begin with a clear picture of the community type under consideration (for example, are we looking for groups of friends, or for groups of people having a common interest?), and then perform community detection with that community type in mind.
 

### 2014-07-31 paper-for_arxiv/methods.tex
Addressed revisions from next actions.

@@
 Network collection continued in this fashion by considering the active followers of the active followers of the seed, and so on until 15,000 users were added to the network.
+The only biasing steps in this procedure are the selection of the seed node and the filtering out of inactive users.
+However, because all of the community types we are interested in involve some sort of interaction between users, each other, and their content, the procedure provides a relatively question-agnostic follower-followee network for use with the different question-based analyses.
 
@@
 The choice of lag must balance a trade-off between additional information and sparsity of samples: as we increase the lag $k$, we account for longer range dependencies, but we also decrease the number of samples available to infer a higher dimensional predictive distribution, see Appendix A for a discussion.
-Ultimately, due to similarities in the underlying communities we chose a lag-4 transfer entropy.
-All references to activity-based weights, unless otherwise noted, refer to this choice of lag.
+As we will see, the underlying communities resulting from the different lags have similar structure.
 

### 2014-07-31 paper-for_arxiv/results.tex
Addressed revisions from next actions.

@@
 
-We see in Table~\ref{Table-comm_count} that the topic- and interaction-based communities have the most singletons, with the activity-based community dominating this measure.
-This result for the activity-based community is partially an artifact of a property of the retweet/mention weighting: 717 of the users were disconnected from the network by how the weights were defined, resulting in `orphan' nodes which we have included in the collection of singletons for all of our analyses.
+We see in Table~\ref{Table-comm_count} that the topic- and interaction-based communities have the most singletons.
+This result for the interaction-based community is partially an artifact of the retweet/mention weighting: 717 of the users were disconnected from the network by how the weights were defined, resulting in `orphan' nodes which we have included in the collection of singletons for all of our analyses.
 However, even after accounting for this artifact, the interaction-based network still has the most non-orphan singletons.
@@
 We see that the community distributions have longer tails for the non-structural networks, and that the interaction-based network has the longest tail.
-The largest communities for the structural, activity-based, topic-based, and interaction-based networks have 198, 358, 338, and 811 members, respectively.
+%The largest communities for the structural, activity-based, topic-based, and interaction-based networks have 198, 358, 338, and 811 members, respectively.
+Note that the activity-based communities, using transfer entropy estimated with varying lags, seem to converge on a similar large-scale community structure around lag 3.
+That is, the communities based on lag 1 and lag 2 transfer entropies are generally larger, and these communities resolve into smaller communities as the lag increases beyond 2.
+The distribution of community sizes for lag larger than 2 is insensitive to the lag.
 Most importantly, we see that the distributions of community sizes differ across the community types, highlighting that the different networks give rise to different large-scale community structure dependent on the particular weighting of the structural network.
@@
 Also note that the covering based on the hashtag similarities are different from all of the other weight-based coverings.
+In agreement with the results reported in the previous section, we see that the activity-based communities share similar structure for lags greater than 2.
+Because of these two results, in the remainder of the paper, we focus on the activity-based communities inferred using the lag-4 transfer entropy.
 
@@
 	\includegraphics[width=0.8\textwidth]{edge-types.pdf}
-	\caption{A schematic of how, given a covering, the edges of the network can be partitioned using \ref{Eqn-edge_types} into inter-edges, intra-edges, and mixed-edges.
-Inter-edges (red) cross community boundaries.
-Intra-edges (blue) remain inside community boundaries.
-Mixed-edges (purple) both remain in and cross community boundaries due to overlap in community membership.
+	\caption{A schematic of how, given a covering, the edges of the network can be partitioned using (\ref{Eqn-edge_types}) into inter-edges, intra-edges, and mixed-edges.
+Inter-edges (red dashed) cross community boundaries.
+Intra-edges (blue solid) remain inside community boundaries.
+Mixed-edges (purple dotted) both remain in and cross community boundaries due to overlap in community membership.
 Each column corresponds to the same collection of weights, but partitioned using a different covering.
@@
 Each community type (Structural, Activity-based, Topic-based, Interaction-based) induces a different partition of the edges, and each edge type (Transfer Entropy, Hashtag, Mention-Retweet) induces a different distribution of weights.
-That is, let $W_{u \to f}$ be the weight on a randomly selected edge $E_{u \to f}$ from the network, and compute
+That is, let $W_{u \to f}$ be the weight on an edge $E_{u \to f}$ chosen uniformly at random from the network, and compute
 \begin{align}
-	P(W_{u \to f} \leq w | T(E_{u \to f}) = t),
+	P(W_{u \to f} \leq w_{u \to f} | T(E_{u \to f}) = t),
 \end{align}
-the empirical distribution over the edge weights conditioned on $t$ being one of inter, intra, and mixed.
+the empirical distribution over the edge weights conditioned on the edge type $t$ being one of inter, intra, and mixed.
 For meaningful community structure, we expect the distribution of edge weights to differ with the edge type $t$.
@@
 	\caption{The density of edge weights for different community types (rows) and weight types (columns).
-The red,  blue, and magenta values below each collection of densities indicate the median of weight on intra-, inter-, and mixed-edges, respectively.}
+The red,  blue, and purple values below each collection of densities indicate the median of weight on intra-, inter-, and mixed-edges, respectively.}
 	\label{Fig-distributions_by_types}
@@
 However, we see that the medians of the distributions provide a useful summary statistic.
-Under each collection of density functions, we list the median value of the inter, intra, and mixed-edges in red, blue, and magenta, respectively.
+Under each collection of density functions, we list the median value of the inter, intra, and mixed-edges in red, blue, and purple, respectively.
 Unsurprisingly, we see that the greatest difference between the distributions occurs when we consider the topic-based communities, since the topic-based communities are determined based on the hashtag weights.

### 2014-07-31 paper-for_arxiv/paper.tex
Taking care of proper Journal formatting
fixing elderly people
working on influence stuff, lots of notes but not finished
fixing margins and title

@@
 %%File: formatting-instruction.tex
-\documentclass[]{article}
-%\usepackage{times}
-%\usepackage{helvet}
-%\usepackage{courier}
-%\usepackage{amssymb, amsmath, amsthm}
-%\usepackage{graphicx}
-%\usepackage{multirow}
-%\usepackage{bigstrut}
-%\usepackage{booktabs}
-%\usepackage{multirow,bigstrut}
-%\usepackage{tabu}
+\documentclass{article}
 \usepackage{authblk}
@@
 
+\newcommand{\alert}[1]{{\color{red}#1}}
+
+% *** Do not adjust lengths that control margins, column widths, etc. ***
+%\oddsidemargin= 0.25in % 1in margins at left and right
+%\evensidemargin= 0in
+\textwidth= 5in % US paper is 8.5in wide     ultra conservative = 5in
+\marginparwidth= 0in
+
+\textheight=7.6667in % US paper is 11.0in high %%% ultra conservative = 7.6in
+
 %\pdfinfo{
@@
 
-\title{Followers Are Not Enough: Beyond Structural Communities in Online Social Networks \\Followers Are Not Enough: A Question-Oriented Approach to Community Detection}
+\title{Followers Are Not Enough: A Question-Oriented Approach to Community Detection}
 
@@
 
+%BELOW IS FOR JCN guidelines
 %\shorttitle{Followers Are Not Enough}
@@
 %The Keywords
-%Community detection, functional communities, social network analysis
+%Community detection, functional communities, social network analysis, transfer entropy
 
@@
 
-%\bibliographystyle{comnet}
-\bibliographystyle{plainnat}
+\bibliographystyle{comnet}
+%\bibliographystyle{plainnat}
 \bibliography{references.bib}

### 2014-07-31 paper-for_arxiv/paper.tex
fixing ordering and adding funding section

@@
 
+\section{Funding}
+Elisa Omodei is partially supported by a PhD grant from the Région Ile-de-France (DIM 2011) and by the French National Agency of Research (ANR) through the grant Algopol (ANR-12-CORD-0018).
+We are grateful to DARPA for the support of David Darmon.
 \section{Acknowledgments}
@@
 Thanks to Cesar Flores, Lu\'is Seoane, Kevin Stadler, Jody Wright, and Nix Barnett for their contributions to preliminary ideas related to this paper and to Michelle Girvan, William Rand, and Aaron Clauset for their valuable comments and suggestions.
-Elisa Omodei is partially supported by a PhD grant from the Région Ile-de-France (DIM 2011) and by the French National Agency of Research (ANR) through the grant Algopol (ANR-12-CORD-0018).
-We are grateful to DARPA for the support of David Darmon.
+
+\input{appendices.tex}
 
@@
 
-\input{appendices.tex}
-
 % \input{paper.bbl}

### 2014-07-31 paper-for_arxiv/paper.tex
adding SFI to acknowledgements
adding Ryan James to the ack. for help with TE code

@@
 
-Thanks to Cesar Flores, Lu\'is Seoane, Kevin Stadler, Jody Wright, and Nix Barnett for their contributions to preliminary ideas related to this paper and to Michelle Girvan, William Rand, and Aaron Clauset for their valuable comments and suggestions.
+Thanks to Cesar Flores, Lu\'is Seoane, Kevin Stadler, Jody Wright, and Nix Barnett for their contributions to preliminary ideas related to this paper and to Michelle Girvan, William Rand, and Aaron Clauset, and Ryan James for their valuable comments and suggestions.
+Finally, we would like to acknowledge the Santa Fe Institute, where this project began\alert{not sure how to word this last sentence}.
 

### 2014-08-01 code/compare_weights_inter_v_intra_community-NEW.py
Code for investigation of edges weighted by TE.

@@ -38,13 +38,15 @@ import collections
 
 # comm_alg = 'i' # For InfoMap
 #
-comm_alg = 'WSBM_K10' # For WSBM
+# comm_alg = 'WSBM_K10' # For WSBM
+
+comm_alg = '' # For OSLOM
 
 label_type_to_number = {'struc' : 0, 'TE4' : 4, 'hashtag' : 7, 'mention-retweet' : 10}
 
 for weight_type in ['TE4', 'hashtag', 'mention-retweet']:
-	# for label_type in ['struc', 'TE4', 'hashtag', 'mention-retweet']:
-	for label_type in ['struc', 'mention-retweet']:
+	for label_type in ['struc', 'TE4', 'hashtag', 'mention-retweet']:
+	# for label_type in ['struc', 'mention-retweet']:
 		print 'Working on {}/{} pairing...'.format(weight_type, label_type)
 
 		if 'TE' in weight_type:
@@ -165,7 +167,8 @@ for weight_type in ['TE4', 'hashtag', 'mention-retweet']:
 
 					if len(I) == 0:
 						inter.append(weight)
-					elif len(A) == len(B) and len(A) == len(I):
+					# elif len(A) == len(B) and len(A) == len(I):
+					elif A == B:
 						intra.append(weight)
 					else:
 						multi.append(weight)

### 2014-08-01 code/compare_weights_intraintermulti_totalmass.py

@@ -42,13 +42,13 @@ comm_alg = ''
 #
 # comm_alg = 'WSBM_K10' # For WSBM
 
-label_type_to_number = {'struc' : 0, 'TE4' : 4, 'hashtag' : 7, 'mention-retweet' : 10}
+label_type_to_number = {'struc' : 0, 'TE1': 1, 'TE2' : 2, 'TE3' : 3, 'TE4' : 4, 'TE5' : 5, 'TE6' : 6, 'hashtag' : 7, 'mention-retweet' : 10}
 
 # for weight_type in ['TE4', 'hashtag', 'mention-retweet']:
-for weight_type in ['TE4']:
+for weight_type in ['TE6']:
 	# for label_type in ['struc', 'TE4', 'hashtag', 'mention-retweet']:
 	# for label_type in ['struc', 'mention-retweet']:
-	for label_type in ['TE4']:
+	for label_type in ['TE6']:
 		print 'Working on {}/{} pairing...'.format(weight_type, label_type)
 
 		if 'TE' in weight_type:
@@ -174,7 +174,7 @@ for weight_type in ['TE4']:
 						
 						for b in B:
 							inter_out[b].append(weight)
-					elif len(A.intersection(B)) == len(B.intersection(A)) and len(A.intersection(B)) != 0:
+					elif A == B:
 						for i in I:
 							intra[i].append(weight)
 					else:

### 2014-08-01 code/ecdf_distribution_by_community_type-coverings.R

@@ -26,7 +26,7 @@
 # weight_type = 'mention-retweet'
 
 label_types = c('struc', 'TE4', 'hashtag', 'mention-retweet')
-# weight_types = c('TE4', 'hashtag', 'mention-retweet')
+weight_types = c('TE4', 'hashtag', 'mention-retweet')
 
 # label_types = c('struc')
 # label_types = c('TE4')
@@ -34,7 +34,7 @@ label_types = c('struc', 'TE4', 'hashtag', 'mention-retweet')
 # label_types = c('mention-retweet')
 
 # weight_types = c('TE4')
-weight_types = c('hashtag')
+# weight_types = c('hashtag')
 # weight_types = c('mention-retweet')
 
 output.filename = 'stats_for_edges.dat'

### 2014-08-01 code/parse_intraintermulti_mass.R

@@ -1,19 +1,44 @@
+
+
 cat(sprintf('comm\tsum intra\tmean intra\tsum inter\tmean inter\tmore in than out\n'))
 
-num.comms = 100
+for (comm.ind in 1:6){
+	weight.type = sprintf('TE%g', comm.ind)
 
-more.in.than.out = rep(0, num.comms)
+	comm.type = sprintf('TE%g', comm.ind) # Need to change these *together*.
+	comm.type.num = comm.ind
 
-for (comm.ind in 0:(num.comms-1)){
-	intra = read.csv(sprintf('../data/edges-by-type/interintramulti_labels-TE4_weights-TE4_comm%g_intra.dat', comm.ind), header = FALSE)$V1
+	comm.sizes = read.csv(sprintf('../data/coverings/communities%g_comp_sizes.txt', comm.type.num), header = FALSE)$V1
+
+	num.comms = length(comm.sizes[comm.sizes > 2])
+
+	more.in.than.out = rep(0, num.comms)
+
+	for (comm.ind in 0:(num.comms-1)){
+		intra = read.csv(sprintf('../data/edges-by-type/interintramulti_labels-%s_weights-%s_comm%g_intra.dat', weight.type, comm.type, comm.ind), header = FALSE)$V1
 	
-	# inter = read.csv(sprintf('../data/edges-by-type/interintramulti_labels-TE4_weights-TE4_comm%g_inter_in.dat', comm.ind), header = FALSE)$V1
-	inter = read.csv(sprintf('../data/edges-by-type/interintramulti_labels-TE4_weights-TE4_comm%g_inter_out.dat', comm.ind), header = FALSE)$V1
+		inter.in = read.csv(sprintf('../data/edges-by-type/interintramulti_labels-%s_weights-%s_comm%g_inter_in.dat', weight.type, comm.type, comm.ind), header = FALSE)$V1
+		inter.out = read.csv(sprintf('../data/edges-by-type/interintramulti_labels-%s_weights-%s_comm%g_inter_out.dat', weight.type, comm.type, comm.ind), header = FALSE)$V1
 	
-	if (mean(intra, na.rm = TRUE) > mean(inter, na.rm = TRUE)){
-		more.in.than.out[comm.ind + 1] = 1
+		# inter = inter.in
+		# inter = inter.out
+		inter = c(inter.in, inter.out)
+	
[…]

### 2014-08-01 paper-for_arxiv/intro.tex
Added modifications after pass through paper.

@@
 For example, `friends' on Facebook represent reciprocal links for sharing information, while `followers' on Twitter allow a single user to broadcast information in a one-to-many fashion.
-Central to all of these interactions is the fact that the \emph{structure} of the social network influences how information can be broadcast or diffuse through the service.
+Central to all these interactions is the fact that the \emph{structure} of the social network influences how information can be broadcast or diffuse through the service.
 
@@
 
-The activity-based approach is motivated by the question of ``Which user's activity ``influences" the activity of another user?", %, \emph{i.e.}, which user(s) cause a user(s) to interact with the network.
- with this question in mind, a community can then be thought of as those individuals who ``influence" each other's activity on the network.
-In general, quantifying the influence of one user on another is a large and ill-understood problem.
+The activity-based approach is motivated by the question of ``Which user's activity `influences' the activity of another user?" %, \emph{i.e.}, which user(s) cause a user(s) to interact with the network.
+ With this question in mind, a community can then be thought of as those individuals who ``influence" each other's activity on the network.
+In general, quantifying the influence of one user on another is a difficult and ill-understood problem.
 For that reason, we focus on a smaller subset of that problem, \emph{viz.}, quantifying influence purely from an information theoretic framework.
@@
 This activity-based approach was motivated by a method used by Shalizi \emph{et al.} in ~\cite{shalizi2007discovering} to detect functional communities within populations of neurons, but to the best of our knowledge, this is the first use of transfer entropy for community detection in online social networks.
-Various other information theoretic approaches have been used successfully to analyze online social networks, \emph{e.g.,} to gain insight into local user behavior~\cite{darmon2013understanding}, to detect communities based on \emph{undirected} information flow~\cite{darmon2013detecting}, and to perform network inference and link prediction\cite{ver2012information}, but not transfer entropy applied to community detection.
+Various other information theoretic approaches have been used successfully to analyze online social networks, \emph{e.g.,} to gain insight into local user behavior~\cite{darmon2013understanding}, to detect communities based on \emph{undirected} information flow~\cite{darmon2013detecting}, and to perform network inference and link prediction~\cite{ver2012information}.
 %While various information theoretic measures has been applied previously to the analysis of networks arising in online social media~\cite{ver2012information,darmon2013detecting},
@@
 Our topic-based and interaction-based approaches, in contrast to the activity-based approach, rely on the \emph{content} of a user's interactions and ignore their temporal components.
-The content contains a great deal of information about the communication between users.
+The content contains a great deal of information about communication between users.
 There are two broad approaches to topic-based communities in the literature.
@@
 This allows us to generate a network based on conversations and user interactions.
-A few works already focused on this type of communities.
+A few works have investigated this type of community.
 For example, \cite{conover2011political} considered both mention and retweet networks in isolation for a collection of users chosen for their political orientation.
@@
 
-The activity-based, topic-based, and interaction-based networks allow us to build a more complete picture of the \emph{implicit} network present in online social media, as opposed to the \emph{explicit} social network indicated by structural links.
+The activity-based, topic-based, and interaction-based networks allow us to build a more complete picture of the \emph{implicit} networks present in online social media, as opposed to the \emph{explicit} social network indicated by structural links.
 In this paper, we explore the relation between these various possible networks and their corresponding communities.

### 2014-08-01 paper-for_arxiv/methods.tex
Added modifications after pass through paper.

@@
 We then describe our methodology for constructing the question-specific networks.
-In particular, we introduce an information theoretic method for activity-based communities, a retweet-mention statistic for interaction-based communities, and a hashtag similarity metric for defining topic-based communities.
+In particular, we introduce an information theoretic statistic for activity-based communities, a retweet-mention statistic for interaction-based communities, and a hashtag similarity metric for defining topic-based communities.
 
@@
 The dataset for this study consisted of the tweets of 15,000 Twitter users over a 9 week period (from April 25th to June 25th 2011).
-The users are embedded in a network collected by performing an intelligent breadth-first expansion from a random seed user.
+The users are embedded in a network collected by performing a breadth-first expansion from a random seed user.
 In particular, once the seed user was chosen, the network was expanded to include his/her followers, but only included users considered to be `active' (i.e., users who tweeted at least once per day over the past one hundred days).
@@
  We computed the transfer entropy on each coarsened time series with lag $k$ ranging from 1 to 6, this corresponds to a lag of ten minutes to an hour.
-The choice of lag must balance a trade-off between additional information and sparsity of samples: as we increase the lag $k$, we account for longer range dependencies, but we also decrease the number of samples available to infer a higher dimensional predictive distribution, see Appendix A for a discussion.
+The choice of lag must balance a trade-off between additional information and sparsity of samples: as we increase the lag $k$, we account for longer range dependencies, but we also decrease the number of samples available to infer a higher dimensional predictive distribution.
+See Appendix A for a discussion of the estimation of transfer entropy from data.
 As we will see, the underlying communities resulting from the different lags have similar structure.
@@
 \begin{align}
-	w_{u \to f}^{\text{HT}} = \frac{\vec{h}(u) \cdot \vec{h}(f)}{||\vec{h}(u)|| \ \ ||\vec{h}(f)||}. \label{Eqn-EW-topic}
+	w_{u \to f}^{\text{HT}} = \frac{\vec{h}(u) \cdot \vec{h}(f)}{\left|\left|\vec{h}(u)\right|\right| \ \ \left|\left|\vec{h}(f)\right|\right|}. \label{Eqn-EW-topic}
 \end{align}

### 2014-08-01 paper-for_arxiv/paper.tex
Added modifications after pass through paper.

--- 2014-07-31 paper-for_arxiv/paper.tex
@@
 
-\title{Followers Are Not Enough: A Question-Oriented Approach to Community Detection}
+\title{Followers Are Not Enough: A Question-Oriented Approach to Community Detection in Online Social Networks}
 
@@
 We show that the communities obtained in the three weighted cases are highly different from each other, and from the communities obtained by considering only the unweighted structural network.
-Our results confirm that asking a precise question is an unavoidable first step in community detection in online social networks, and that different questions can lead to different insights into the network under study.
+Our results confirm that asking a precise question is an unavoidable first step in community detection in online social networks, and that different questions can lead to different insights about the network under study.
 %\end{quote}
@@
 
-Thanks to Cesar Flores, Lu\'is Seoane, Kevin Stadler, Jody Wright, and Nix Barnett for their contributions to preliminary ideas related to this paper and to Michelle Girvan, William Rand, and Aaron Clauset for their valuable comments and suggestions.
+Thanks to Cesar Flores, Lu\'is Seoane, Kevin Stadler, Jody Wright, and Nix Barnett for their contributions to preliminary ideas related to this paper and to Michelle Girvan, William Rand, Aaron Clauset, and Ryan James for their valuable comments and suggestions.
+Finally, we would like to acknowledge the Santa Fe Institute and its Complex Systems Summer School for providing the intellectually stimulating environment where this project began.
 

### 2014-08-01 paper-for_arxiv/results.tex
Added modifications after pass through paper.

@@
 The activity-based network admits the fewest communities.
-One advantage of the OSLOM over many other community detection algorithms is that it explicitly accounts for singleton `communities': those nodes who do not belong to \emph{any} extant communities.
+One advantage of OSLOM over many other community detection algorithms is that it explicitly accounts for singleton `communities': those nodes who do not belong to \emph{any} extant communities.
 This is especially important when a network is collected via a breadth-first search, as in our network, where we begin from a seed node and then branch out.
@@
 	\centering
-	\includegraphics[width=1\textwidth]{densities-edges.eps}
+	\includegraphics[width=1\textwidth]{densities-edges.pdf}
 	\caption{The density of edge weights for different community types (rows) and weight types (columns).
@@
 Under each collection of density functions, we list the median value of the inter, intra, and mixed-edges in red, blue, and purple, respectively.
-Unsurprisingly, we see that the greatest difference between the distributions occurs when we consider the topic-based communities, since the topic-based communities are determined based on the hashtag weights.
+Unsurprisingly, we see that the greatest difference between the distributions occurs when we consider matching Community-type / Weight-type pairs, since the communities are determined based on the corresponding weights.
 However, we also see differences in the distributions when the Community-type / Weight-type pairs do not match.
@@
 Interestingly, among the most influential users in these communities, those with highest transfer entropy on average, we find \@Colorado, which is the state official Twitter account, \@ConnectColorado, a page created to connect Coloradans, and the CBS Denver account, a popular news agency.
-This means that these accounts had high influence in terms of their followers activity on Twitter.
+This means that these accounts had high influence in terms of their followers' activity on Twitter.
 This is not surprising as these communities discuss Colorado and these accounts provide information on this topic.
-However, this does provide a nice sanity check that this measure of activity based influence makes sense and suggests this could be a nice measure for influence on social media if used with other measures.
+However, this does provide a check that this measure of activity based influence makes sense and suggests this could be a nice measure for influence on social media if used with other measures.
 This is discussed more in future work.
@@
  happen to be in our network, \emph{viz.}, Ann Tran and Jessica Northey, and transfer entropy also quantified these two users as highly influential.% members, as categorized by transfer entropy. 
- This does not prove, but suggests that this measure of activity-based or information-theoretic influence may be useful in finding influential members purely based on their temporal tweet history while completely ignoring both tweet content and social class.
+This suggests that activity-based or information-theoretic influence may be useful in finding influential members purely based on their temporal tweet history while completely ignoring both tweet content and social status.

### 2014-08-02 paper-for_arxiv/methods.tex
minor edits

@@
 This feature of the algorithm plays an important role in the analysis of real data networks, since it is not always the case that a community structure is indeed present and it is therefore useful to be able to detect its absence too.
-Therefore, given its versatility and performance with benchmark network, in this paper we used OSLOM to detect \emph{overlapping} communities present in our \emph{weighted} and \emph{directed} network.
+Therefore, given its versatility and performance with benchmark network, in this paper we used OSLOM to detect \emph{overlapping} communities present in our \emph{weighted} and \emph{directed} networks.
 %For this paper we use OSLOM since it allowed us to detect \emph{overlapping} communities present in our \emph{weighted} and \emph{directed} network, and its authors showed that it performs very well on various types of artificial benchmark graphs and also on several real networks.

### 2014-08-02 paper-for_arxiv/paper.tex
minor edits

@@
 \section{Funding}
-Elisa Omodei is partially supported by a PhD grant from the Région Ile-de-France (DIM 2011) and by the French National Agency of Research (ANR) through the grant Algopol (ANR-12-CORD-0018).
+%Elisa Omodei is partially supported by a PhD grant from the R\'{e}gion \^{I}le-de-France (DIM 2011) and by the French National Agency of Research (ANR) through the grant Algopol (ANR-12-CORD-0018).
+This work was supported by the R\'{e}gion \^{I}le-de-France [DIM 2011 to E.O.]; and by the French National Agency of Research [ANR-12-CORD-0018 to E.O.].
 We are grateful to DARPA for the support of David Darmon.
+
 \section{Acknowledgments}

### 2014-08-02 paper-for_arxiv/results.tex
minor edits

@@
 This is not surprising as these communities discuss Colorado and these accounts provide information on this topic.
-However, this does provide a check that this measure of activity based influence makes sense and suggests this could be a nice measure for influence on social media if used with other measures.
+However, this does provide a check that this measure of activity-based influence makes sense and suggests this could be a useful measure for influence on social media if used with other measures.
 This is discussed more in future work.
@@
 Lastly, it is interesting to note that two of the Forbes ``Top 10 Social Media Influencers", % ranked using the total outgoing strength in the activity-based network, 
- happen to be in our network, \emph{viz.}, Ann Tran and Jessica Northey, and transfer entropy also quantified these two users as highly influential.% members, as categorized by transfer entropy. 
+ happen to be in our network, \emph{viz.}, Ann Tran and Jessica Northey, and transfer entropy also quantified these two users as highly influential.
+% members, as categorized by transfer entropy. 
 This suggests that activity-based or information-theoretic influence may be useful in finding influential members purely based on their temporal tweet history while completely ignoring both tweet content and social status.

### 2014-08-02 paper-for_arxiv/intro.tex
new reference

@@
 See~\cite{fortunato2010community} for a recent review.
-A large body of work exists on methods for automatic detection of communities within networks, among which we recall the Girvan and Newman algorithm~\cite{newman2004finding}, Infomap~\cite{Rosvall08mapsof}, Louvain~\cite{blondel2008fast}, and the recently introduced OSLOM~\cite{LancichinettiPlos}.
+A large body of work exists on methods for automatic detection of communities within networks, among which we recall the stochastic blockmodel~\cite{Holland1983} (and its recent generalization to weighted networks~\cite{Aicher26062014}), the Girvan and Newman algorithm~\cite{newman2004finding}, clique percolation~\cite{PalEtAl05}, Infomap~\cite{Rosvall08mapsof}, Louvain~\cite{blondel2008fast}, and the recently introduced OSLOM~\cite{LancichinettiPlos}.
 All these methods \emph{begin} with a given network, and then attempt to uncover structure present in the network, i.e., they are agnostic to how the network was constructed.

### 2014-08-07 code/ecdf_distribution_by_community_type-coverings.R
Minor changes to figures.

@@ -129,7 +129,8 @@ if (weight_type == 'TE4'){
 	log = ''
 }
 
-tiff(paste0('figures/', prefix.pdf, '-pdf_by_type.tiff'), res = 120)
+# tiff(paste0('figures/', prefix.pdf, '-pdf_by_type.tiff'), res = 120)
+pdf(paste0('figures/', prefix.pdf, '-pdf_by_type.pdf'))
 par(mar=c(5,5,2,1), cex.lab = 2, cex.axis = 2)
 plot(density(data_inter, from = 0), col = 'blue', xlim = xlim, ylim = ylim, lty = 1, lwd = lwd.cdf, main = '', xlab = expression(paste('Weight, ', w)), ylab = expression(paste('f(', w, '| ', T == t, ')')), log = log)
 lines(density(data_intra, from = 0), col = 'red', lty = 2, lwd = lwd.cdf)

### 2014-08-07 paper-for_arxiv/methods.tex
Reworded wonky sentence.

@@
 The only biasing steps in this procedure are the selection of the seed node and the filtering out of inactive users.
-However, because all of the community types we are interested in involve some sort of interaction between users, each other, and their content, the procedure provides a relatively question-agnostic follower-followee network for use with the different question-based analyses.
+However, because all of the community types we are interested in involve some aspect of the interaction between users, each other, and their content, the procedure provides a relatively question-agnostic follower-followee network for use with the different question-based analyses.
 

### 2014-08-18 paper-for_arxiv/methods.tex
minor edits

@@
 For example, the work of~\cite{PalEtAl05} on clique percolation can account for both features, but not at the same time.
-A recent method proposed by~\cite{LancichinettiPlos}, OSLOM (Order Statistics Local Optimization Method), is one of the first methods  able to deal with all of these features simultaneously.
-Their method relies on a fitness function that measures the statistical significance of clusters with respect to random fluctuations, and attempts to optimize this fitness function across all clusters.
+A recent method proposed in~\cite{LancichinettiPlos}, OSLOM (Order Statistics Local Optimization Method), is one of the first methods  able to deal with all of these features simultaneously.
+This method of Lancichinetti et al.
+relies on a fitness function that measures the statistical significance of clusters with respect to random fluctuations, and attempts to optimize this fitness function across all clusters.
 Following~\cite{LancichinettiPlos}, the significance measure is defined as the probability of finding the cluster in a network without community structure.
-The null model used is basically the same as the one adopted by Newman and Girvan to define modularity, i.e.
-it is a model that generates random graphs with a given degree distribution.
+The null model used is basically the same as the one adopted by Newman and Girvan in \cite{newman2004finding} to define modularity, {\it i.e.} it is a model that generates random graphs with a given degree distribution.
 The authors tested their algorithm on different benchmarks (LFR and Girvan-Newman) and real networks (such as the US air transportation and the word association network), and compared its performance against the best algorithms
@@
 This feature of the algorithm plays an important role in the analysis of real data networks, since it is not always the case that a community structure is indeed present and it is therefore useful to be able to detect its absence too.
-Therefore, given its versatility and performance with benchmark network, in this paper we used OSLOM to detect \emph{overlapping} communities present in our \emph{weighted} and \emph{directed} networks.
+Therefore, given its versatility and performance with benchmark networks, in this paper we used OSLOM to detect \emph{overlapping} communities present in our \emph{weighted} and \emph{directed} networks.
 %For this paper we use OSLOM since it allowed us to detect \emph{overlapping} communities present in our \emph{weighted} and \emph{directed} network, and its authors showed that it performs very well on various types of artificial benchmark graphs and also on several real networks.
@@
 The logic for this definition is as follows: if $u$ mentions a user $v$ this can be thought of as $u$ directly sending information to $v$, and if $u$ is retweeted by $v$ then $v$ received information from $u$ and rebroadcast it to their followers.
-In either case there was information outgoing from $u$ which affected the network in the some way.
+In either case there was information outgoing from $u$ which affected the network in some way.
 Analogously, we define the incoming information event for $u$ as either being mentioned by a different user in the network, or as retweeting another user in the network.
@@
 %[[Switched the readers perspective]]When we mention someone we are in fact sending him some information, and when we are retweeted it means that the person that retweeted us has received some information from us and is sharing it.
-With (incoming/outgoing) information events defined we filtered the network by eliminating all users with less than a total of 9 outgoing \emph{and} incoming information events, i.e., less than one information event per type per week on average.
+With (incoming/outgoing) information events defined we filtered the network by eliminating all users with less than a total of 9 outgoing \emph{and} incoming information events, {\it i.e.,} less than one information event per type per week on average.
 We then further restricted our analysis to the strong giant connected component of the network built from the (incoming/outgoing) information filtered set of users.
 %and whose link represent a user-follower relationship.
-In this study the link is directed from the user to the follower because this is the direction in which the information (in the case of transfer entropy) or influence (in the case of mention-retweets) flows.
+In this study the link is directed from the user to the follower because this is the direction in which information flows.
 Thus, for a pair of users $u$ and $v$, an edge $a_{v \to u}$ in the structural network has weight 1 if user $u$ follows $v$, and 0 otherwise.
@@
 
-Operationally, we expect users to interact with Twitter on a human time scale, and thus the natural one-second time resolution is too fine since most humans do not write tweets on the time scale of seconds.
-We coarsen each time series by considering non-overlapping time intervals ten minutes in length.
+Operationally, we expect users to interact with Twitter on a human time scale, and thus the natural one-second time resolution is too fine; since most humans do not write tweets on the time scale of seconds.
+For this reason, we coarsen each time series by considering non-overlapping time intervals ten minutes in length.
 For each time interval, we record a 1 if the user has tweeted during that time interval, and a 0 if they have not.
@@
 The choice of lag must balance a trade-off between additional information and sparsity of samples: as we increase the lag $k$, we account for longer range dependencies, but we also decrease the number of samples available to infer a higher dimensional predictive distribution.
-See Appendix A for a discussion of the estimation of transfer entropy from data.
-As we will see, the underlying communities resulting from the different lags have similar structure.
+See Appendix A for a discussion of these issues.
+As we will show, the underlying communities resulting from the different lags have similar structure.
 
@@
 The final community we consider is a topic-based or topical community, i.e., a community defined by the content (topics) users discuss.
-So in a topical community, users are defined to be a member of a community if they tweet \emph{about} similar topics as other members of the community.
+In a topical community, users are defined to be a member of a community if they tweet \emph{about} similar topics as other members of the community.
 %Another kind of community is the one based on the content of the tweets, and relies on the idea of finding people that talk about the same things. 
@@
 \begin{equation}
-h_i(u) = n_i(u)\log{ \frac{N}{n_i} }
+h_i(u) = \phi_i(u)\log{ \frac{N}{n_i} }
 \end{equation}
-where $n_i(u)$ is the frequency of hashtag $i$ occuring in user $u$'s tweets, $N$ is the total number of users, and $n_i$ is the number of users that have used the hashtag $i$ in their tweets.
+where $\phi_i(u)$ is the frequency of hashtag $i$ occuring in user $u$'s tweets, $N$ is the total number of users, and $n_i$ is the number of users that have used the hashtag $i$ in their tweets.
 This adapted term frequency--inverse document frequency (tf-idf) measure \cite{salton_introduction_1983} captures the importance of a hashtag in the users's tweets through the first factor, but at the same time smooths it through the second factor by giving less importance to hashtags that are too widely used (as $\frac{N}{n_i}$ approaches one, its logarithm approaches zero).

### 2014-08-18 paper-for_arxiv/paper.tex
Removed DARPA acknowledgement.
formatting
minor edits

@@
 %Elisa Omodei is partially supported by a PhD grant from the R\'{e}gion \^{I}le-de-France (DIM 2011) and by the French National Agency of Research (ANR) through the grant Algopol (ANR-12-CORD-0018).
-This work was supported by the R\'{e}gion \^{I}le-de-France [DIM 2011 to E.O.]; and by the French National Agency of Research [ANR-12-CORD-0018 to E.O.].
-We are grateful to DARPA for the support of David Darmon.
+This work was partially supported by the R\'{e}gion \^{I}le-de-France [DIM 2011 to E.O.]; and by the French National Agency of Research [ANR-12-CORD-0018 to E.O.].
+%We are grateful to DARPA for the support of David Darmon.
 

### 2014-08-18 paper-for_arxiv/results.tex
Modified ecdf figure to match LaTeX font.
minor edits

@@
 %\includegraphics[width=0.50\textwidth]{comm_sizes_ecdf_loglog.pdf}
-\includegraphics[width=0.6\textwidth,angle=270]{cdf_comm_sizes.eps}
+\includegraphics[width=1\textwidth]{cdf_comm_sizes.pdf}
 \caption{The proportion of communities greater than $s$ in size, across the different community types. Note the logarithmic scale on the horizontal and vertical axes.}
@@
 Any covering determined by OSLOM induces a natural partition of the edges in a directed network.
-In particular, Let $u$ and $f$ be two users in the network, and let $M_{u}$ and $M_{f}$ be their community memberships.
+In particular, let $u$ and $f$ be two users in the network, and let $M_{u}$ and $M_{f}$ be their community memberships.
 Then any edge $e_{u \to f}$ can be partitioned into one of three classes by

### 2014-08-25 paper-for_arxiv/conclusions.tex
Added modifications after pass through paper.
random edits

@@
 The questions posed about a network \emph{a priori} have a strong impact on the communities observed.
-Moreover, using different definitions of \emph{community} reveal different and interesting relationships between users.
+Moreover, using different definitions of community reveal different and interesting relationships between users.
 More importantly, we have shown that these different views of the network are not revealed by using the structural network or any one weighting scheme alone.
-By varying the questions we asked about the network and then deriving weighting schema to answer each question, we found that community structure differed across community types on both the macro (e.g.
-number of communities and their size distribution) and micro (e.g.
-specific memberships, comemberships) scale in interesting ways.
+By varying the questions we asked about the network and then deriving weighting schema to answer each question, we found that community structure differed across community types on both the macro ({\it e.g.,} number of communities and their size distribution) and micro ({\it e.g.,} specific memberships, comemberships) scale in interesting ways.
 
@@
 To verify the validity of these communities we demonstrated that boundaries between communities represent meaningful internal/external divisions.
-In particular, conversations (e.g.
-retweets and mentions) and topics (e.g.
-hashtags) tended to be most highly concentrated within communities.
+In particular, conversations ({\it e.g.,} retweets and mentions) and topics ({\it e.g.,} hashtags) tended to be most highly concentrated within communities.
 We found this to be the case even when the communities were defined by a different criterion from the edge weights under study.

### 2014-08-25 paper-for_arxiv/results.tex
random edits

@@
 %\includegraphics[width=0.50\textwidth]{comm_sizes_ecdf_loglog.pdf}
-\includegraphics[width=1\textwidth]{cdf_comm_sizes.pdf}
+\includegraphics[width=1\textwidth]{cdf_comm_sizes}
 \caption{The proportion of communities greater than $s$ in size, across the different community types. Note the logarithmic scale on the horizontal and vertical axes.}
@@
     \midrule
-    \multirow{8}[8]{*}{\includegraphics[width=0.50\textwidth]{nmi_singletons.pdf}}&0---Structural \bigstrut\\
+    \multirow{8}[8]{*}{\includegraphics[width=0.50\textwidth]{nmi_singletons}}&0---Structural \bigstrut\\
     &1-6---Activity-Based with Lags 1-6\bigstrut\\
@@
 	\centering
-	\includegraphics[width=0.8\textwidth]{edge-types.pdf}
+	\includegraphics[width=0.8\textwidth]{edge-types}
 	\caption{A schematic of how, given a covering, the edges of the network can be partitioned using (\ref{Eqn-edge_types}) into inter-edges, intra-edges, and mixed-edges.
@@
 	\centering
-	\includegraphics[width=1\textwidth]{densities-edges.pdf}
+	\includegraphics[width=1\textwidth]{densities-edges}
 	\caption{The density of edge weights for different community types (rows) and weight types (columns).

### 2014-10-29 paper-postreview/intro.tex
Revision version and next actions.
I created pre- and post-review versions of the paper. And added action
items in the post-review directory in the file titled
“action-items-291014.txt”.

--- 2014-08-01 paper-for_arxiv/intro.tex
@@
 Because of the importance of structural networks in online social media, a large amount of work in this area has focused on using structural networks for community detection.
-Here, by `community' we mean the standard definition from the literature on social networks: a collection of nodes (users) within the network which are more highly connected to each other than to nodes (users) outside of the community~\cite{girvan2002a, newman2004finding}.
+In this traditional view, `community' is defined as a collection of nodes (users) within the network which are more highly connected to each other than to nodes (users) outside of the community
+%Here, by `community' we mean the standard definition from the literature on social networks: a collection of nodes (users) within the network which are more highly connected to each other than to nodes (users) outside of the community
+~\cite{girvan2002a, newman2004finding}.
 For instance, in~\cite{java2009we}, the authors use a follower network to determine communities within Twitter, and note that conversations tend to occur within these communities.
 The approach of focusing on the structure of networks makes sense for `real-world' sociological experiments, where obtaining additional information about user interactions may be expensive and time-consuming.
-However, with the prevalence of large, rich data sets for online social networks, additional information beyond the structure alone may be incorporated, and these augmented networks more realistically reflects how users interact with each other on social media services~\cite{nguyen2011adaptive},~\cite{grabowicz2012social}.
+However, with the prevalence of large, rich data sets for online social networks, additional information beyond the structure alone may be incorporated, and these augmented networks more realistically reflect how users interact with each other on social media services~\cite{nguyen2011adaptive},~\cite{grabowicz2012social}.
 
@@
 See~\cite{fortunato2010community} for a recent review.
-A large body of work exists on methods for automatic detection of communities within networks, among which we recall the Girvan and Newman algorithm~\cite{newman2004finding}, Infomap~\cite{Rosvall08mapsof}, Louvain~\cite{blondel2008fast}, and the recently introduced OSLOM~\cite{LancichinettiPlos}.
+A large body of work exists on methods for automatic detection of communities within networks, {\it e.g.,} the stochastic blockmodel~\cite{Holland1983} (and its recent generalization to weighted networks~\cite{Aicher26062014}), the Newman and Girvan algorithm~\cite{newman2004finding}, clique percolation~\cite{PalEtAl05}, Infomap~\cite{Rosvall08mapsof}, Louvain~\cite{blondel2008fast}, and the recently introduced OSLOM~\cite{LancichinettiPlos}.
 All these methods \emph{begin} with a given network, and then attempt to uncover structure present in the network, i.e., they are agnostic to how the network was constructed.
 As opposed to this agnostic analysis, we propose and illustrate the importance of a question-focused approach.
-We believe that in order to understand the communities present in a data set, it is important to begin with a clear picture of the community type under consideration (for example, are we looking for groups of friends, or for groups of people having a common interest?), and then perform community detection with that community type in mind.
+We believe that in order to understand the communities present in a data set, it is important to begin with a clear picture of the community type under consideration---{\it e.g.,} are we looking for groups of friends?
+or for groups of people having a common interest?---and then perform community detection with that community type in mind.
 
@@
 Each of these different `profiles' of the user highlight different views of the user's social network, and represent different types of communities.
-We divide our approaches into four categories based on the questions outlined above: structure-based, activity-based, topic-based, and interaction-based.
-The structure-based approach, as outlined above, is most common, and for our data relies on reported follower relationships.
+We now consider in more detail how each of these types of questions motivates a question-specific community.
 
@@
 Previous research on communities in social networks focused almost exclusively on different network types in isolation.
-A notable exception to the analysis of isolated types of communities is~\cite{lim2012tweets}, which considered both structure-based and interaction-based communities on Twitter.
+A notable exception to the analysis of isolated types of communities is~\cite{lim2012tweets}, that considered both structure-based and interaction-based communities on Twitter.
 However, this study focused on data collected based on particular topics (country music, tennis, and basketball), and not on a generic subpopulation of Twitter users.

### 2014-10-29 paper-prereview/appendices.tex
Revision version and next actions.
I created pre- and post-review versions of the paper. And added action
items in the post-review directory in the file titled
“action-items-291014.txt”.

--- 2014-07-25 paper-for_arxiv/appendices.tex
@@
 \end{align}
-we can see that transfer entropy is always non-negative, and is zero precisely when $H\left[X_{t} | X_{t-k}^{t-1}\right] = H\left[X_{t} | X_{t-k}^{t-1}, Y_{t-k}^{t-1}\right]$, in which case knowing the past $k$ lags of $Y_{t}$ does not reduce the uncertainty in $X_{t}$.
+we can see that transfer entropy is always non-negative, and is zero precisely when $$H\left[X_{t} | X_{t-k}^{t-1}\right] = H\left[X_{t} | X_{t-k}^{t-1}, Y_{t-k}^{t-1}\right]$$, in which case knowing the past $k$ lags of $Y_{t}$ does not reduce the uncertainty in $X_{t}$.
 If the transfer entropy is positive, then $\{ Y_{t}\}$ is considered causal for $\{ X_{t}\}$ in the Granger sense~\cite{granger1963economic}.
 
-In estimating the transfer entropy from finite data, we will assume that the process $\{(X_{t}, Y_{t})\}$ is jointly stationary, which gives us that
+When estimating transfer entropy from finite data, we will assume that the process $\{(X_{t}, Y_{t})\}$ is jointly stationary, which gives us that
 \begin{align}

### 2014-10-29 paper-prereview/intro.tex
Revision version and next actions.
I created pre- and post-review versions of the paper. And added action
items in the post-review directory in the file titled
“action-items-291014.txt”.

--- 2014-10-29 paper-postreview/intro.tex
@@
 Each of these different `profiles' of the user highlight different views of the user's social network, and represent different types of communities.
-We now consider in more detail how each of these types of questions motivates a question-specific community.
+We divide our approaches into four categories based on the questions outlined above: structure-based, activity-based, topic-based, and interaction-based.
+The structure-based approach, as outlined above, is most common, and for our data relies on reported follower relationships.
 

### 2014-11-14 paper-postreview/intro.tex
working on influence in the intro

@@
 A large body of work exists on methods for automatic detection of communities within networks, {\it e.g.,} the stochastic blockmodel~\cite{Holland1983} (and its recent generalization to weighted networks~\cite{Aicher26062014}), the Newman and Girvan algorithm~\cite{newman2004finding}, clique percolation~\cite{PalEtAl05}, Infomap~\cite{Rosvall08mapsof}, Louvain~\cite{blondel2008fast}, and the recently introduced OSLOM~\cite{LancichinettiPlos}.
-All these methods \emph{begin} with a given network, and then attempt to uncover structure present in the network, i.e., they are agnostic to how the network was constructed.
-As opposed to this agnostic analysis, we propose and illustrate the importance of a question-focused approach.
-We believe that in order to understand the communities present in a data set, it is important to begin with a clear picture of the community type under consideration---{\it e.g.,} are we looking for groups of friends?
-or for groups of people having a common interest?---and then perform community detection with that community type in mind.
+All these methods begin with a given network, and then attempt to uncover structure present in the network, \emph{i.e.,} they are agnostic to how the network was constructed.
+As opposed to this agnostic analysis, we propose---and illustrate the importance of---a \emph{multi-faceted question-focused} approach.
+We believe that in order to understand all of the communities present in a data set, it is important to take two crucial steps:
+\begin{enumerate}
+\item Form a clear question about what \emph{type} of community we wish to consider---{\it e.g.,} are we looking for groups of friends?
+or for groups of people having a common interest?---and then perform community detection with that question in mind.
+\item Ask more than one question about the users in a network. Do several rounds of community detection, each of which is aimed at revealing a new facet of the communities present in the network. 
+\end{enumerate}
 
@@
 On a more abstract level, a user might consider themselves part of a community of people discussing similar topics.
-We might also define communities as collections of people who exhibit similar activity profiles and seem to ``influence" each other's activity on the network.
+We might also define communities as collections of people who exhibit similar activity profiles.
 We can characterize these types of communities based on the types of questions we might ask about them:
@@
 	\item \textbf{Structure-based:} Who are your stated friends? Whom do you follow?
-	\item \textbf{Activity-based:} Whose activity influences your activity?
+	\item \textbf{Activity-based:} Who shares similar activity profiles?
 	\item \textbf{Topic-based:} What do you talk about?
@@
 We now consider in more detail how each of these types of questions motivates a question-specific community.
+Later in Section~\ref{sec:conc} we will show how asking \emph{all} of these questions---instead of just one which is the standard---gives a much deeper multi-faceted view of the overlapping \emph{and} disjoint communities users belong to.
 
-The activity-based approach is motivated by the question of ``Which user's activity `influences' the activity of another user?" %, \emph{i.e.}, which user(s) cause a user(s) to interact with the network.
- With this question in mind, a community can then be thought of as those individuals who ``influence" each other's activity on the network.
-In general, quantifying the influence of one user on another is a difficult and ill-understood problem.
-For that reason, we focus on a smaller subset of that problem, \emph{viz.}, quantifying influence purely from an information theoretic framework.
-%The primary tool for answering this question is the  For this approach
-%\alert{Maybe add a sentence hedging influence}
+The activity-based approach is motivated by the question of ``Which user's have similar activity profiles?".%, \emph{i.e.,} which user(s) cause groups of users to become active on the network.
+%, \emph{i.e.}, which user(s) cause a user(s) to interact with the network.
+ With this question in mind, a community can then be thought of as those individuals who use the service in a similar way.
+More generally, these communities can be thought of as groups of users who hold so-called ``predictive capacity" with the other users in the community.
+That is, given two users in a community $u$ and follower $f$, there exists a reduction in uncertainty that user $f$ will interact with Twitter, given that user $u$ just interacted.
+Effectively, there is a predictive capacity in the tweet history of user $f$ given the information gained from the activity of user $u$.
 
@@
 Transfer entropy is an information theoretic measure of \emph{directed} information flow.
-It has been shown in~\cite{ver2012information} that a positive transfer entropy between a user $u$ and a follower $f$ indicates that $u$ ``influences" $f$, or that $u$ and $f$ share a common influencer.
+It was shown in~\cite{ver2012information} that a positive transfer entropy between a user $u$ and a follower $f$ indicates that $u$ ``influences" $f$, or that $u$ and $f$ share a common influencer.
 In particular, positive transfer entropy from the tweet history of a user $u$ to a follower $f$'s tweet history implies that this relationship is causal in the Granger sense~\cite{granger1963economic}.
 As a result, transfer entropy is often thought of as a measure of ``influence" in an information theoretic sense.
-Thus, communities detected in this way have members whose tweet histories are causally related in a Granger sense, \emph{i.e.}, members who ``influence" each others activity on the network.
-%Obviously the concept of ``influence" is extremely broad and quantifying influence in a social network is neither well understood nor well defined in the literature.
+Thus, communities detected in this way have members whose tweet histories are causally related in a Granger sense.
 
-We want to reiterate that we do not imply that this information theoretic measure completely captures social influence in general.
-However, we conjecture, it does capture a useful subset of that relationship.
-In this paper, when we say \emph{influence} we explicitly refer to a reduction in uncertainty of whether a follower $f$ will be active or not given the past history of a user $u$.
-We will however show later in this paper that this information theoretic measure of influence agrees with other concepts of influence such as the Forbes list of ``Top 10 Social Media Influencers" and corroborates with the so-called strength of weak ties~\cite{granovetter1973strength}.
+We would like to say however that we are skeptical whether this measure truly captures social influence.
+We instead treat this weighting as a way to explicitly quantify a reduction in uncertainty of whether a follower $f$ will be active or not given the past history of a user $u$.
+This provides an information theoretic framework in which we can capture communities with predictive capacity between users or users with similar activity profiles.
+We call this relation $PV-AC$.
 
-%emphasize that we are not saying these casual relationships necessarily suggest social or \alert{??
-} influence, but simply a casual re.
-In this paper when we say that a user $u$ influences a user $f$ we simply mean that there is a reduction in uncertanity about whether user $u$ will be active or not given the past history of user $f$.
-We will show that this information theoretic view of influence is a useful and
-%Effectively, if there is a positive transfer entropy from user $u$ to $v$ then there is a reduction in uncertainty about user \alert{$u$/$v$} tweeting given the recent tweet history of user \alert{$u$/$v$}.
-This can and has been interpreted as a form of influence, if user \alert{$u$/$v$} reduces the uncertainty about \alert{$u$/$v$} tweeting then it may be the case that this was a form of social influence.
-We are fully aware that the difference between information theoretic and social influence are different but think this may be an interesting area to explore.
-Later we show that using this measure alone we can detect ``influential users" who are also listed as \alert{Forbes ...}.
-We instead treat this weighting as a way to quantify which users activity are quantified by each other, i.e., communities that use twitter in similar ways.
-%A positive value for the transfer entropy of the user $u$ on $f$ indicates that $u$ influences $f$, or that $u$ and $f$ share a common influencer~\cite{ver2012information}. $T_{u \to f}$
-%think this paragrpah should be something like we use it as a way to quantify activity but we think it may have applicaitons in influence detection for example if one user has high transfer entropy with an entire community, then this may imply that user has strong social influence on the activity of a given community defined with this weighting scheme.
-For example, Denver Broncos tweet that they fired John Elway and an entire network of Broncos fans begins tweeting this may be a rank of influence.
+While we are skeptical that this measure can capture social influence, later in this paper we show that this information theoretic measure agrees with other concepts of influence such as the Forbes list of ``Top 10 Social Media Influencers" and corroborates with the so-called strength of weak ties~\cite{granovetter1973strength}.
 

### 2014-11-17 paper-postreview/intro.tex
first round of edits

@@
 As opposed to this agnostic analysis, we propose---and illustrate the importance of---a \emph{multi-faceted question-focused} approach.
-We believe that in order to understand all of the communities present in a data set, it is important to take two crucial steps:
+We believe that in order to understand all of the communities present in a network, it is important to take two crucial steps:
 \begin{enumerate}
@@
 
-The activity-based approach is motivated by the question of ``Which user's have similar activity profiles?".%, \emph{i.e.,} which user(s) cause groups of users to become active on the network.
+Na\"ively the activity-based approach is motivated by the question of ``Which users in a network have similar activity profiles?".%, \emph{i.e.,} which user(s) cause groups of users to become active on the network.
 %, \emph{i.e.}, which user(s) cause a user(s) to interact with the network.
- With this question in mind, a community can then be thought of as those individuals who use the service in a similar way.
-More generally, these communities can be thought of as groups of users who hold so-called ``predictive capacity" with the other users in the community.
-That is, given two users in a community $u$ and follower $f$, there exists a reduction in uncertainty that user $f$ will interact with Twitter, given that user $u$ just interacted.
-Effectively, there is a predictive capacity in the tweet history of user $f$ given the information gained from the activity of user $u$.
+ With this question in mind, a community can then be thought of as those users who use (or do not use) the service at similar times.
+However, the measure we use is slightly more subtle that this.
+In particular, these communities can be thought of as groups of users who possess so-called ``predictive capacity" with one another, i.e., given a user $u$ and follower $f$ who are members of a community detected with this weighting, there exists a reduction in uncertainty about the activity profile of follower $f$ (tweeting or remaining silent), given the tweet history of user $u$.
 
@@
 Transfer entropy is an information theoretic measure of \emph{directed} information flow.
-It was shown in~\cite{ver2012information} that a positive transfer entropy between a user $u$ and a follower $f$ indicates that $u$ ``influences" $f$, or that $u$ and $f$ share a common influencer.
-In particular, positive transfer entropy from the tweet history of a user $u$ to a follower $f$'s tweet history implies that this relationship is causal in the Granger sense~\cite{granger1963economic}.
+A positive transfer entropy from the tweet history of a user $u$ to a follower $f$'s tweet history implies that this relationship is causal in the Granger sense~\cite{granger1963economic}.
+Thus, communities detected in this way have members whose tweet histories are causally related in a Granger sense.
 As a result, transfer entropy is often thought of as a measure of ``influence" in an information theoretic sense.
-Thus, communities detected in this way have members whose tweet histories are causally related in a Granger sense.
 
-We would like to say however that we are skeptical whether this measure truly captures social influence.
-We instead treat this weighting as a way to explicitly quantify a reduction in uncertainty of whether a follower $f$ will be active or not given the past history of a user $u$.
+According to~\cite{ver2012information} a positive transfer entropy between a user $u$ and a follower $f$ indicates that $u$ ``influences" $f$, or that $u$ and $f$ share a common influencer.
+We would like to point out however that we are skeptical whether this measure truly captures social influence in its entirety.
+We instead treat this weighting as a way to explicitly quantify a reduction in uncertainty of whether a follower $f$ will be active or not given the tweet history of a user $u$.
 This provides an information theoretic framework in which we can capture communities with predictive capacity between users or users with similar activity profiles.
-We call this relation $PV-AC$.
-
+We call this relation ``PV-AC".
 While we are skeptical that this measure can capture social influence, later in this paper we show that this information theoretic measure agrees with other concepts of influence such as the Forbes list of ``Top 10 Social Media Influencers" and corroborates with the so-called strength of weak ties~\cite{granovetter1973strength}.
+Even so, we do not explicitly treat---and we do not believe it should be treated---as a quantification of social influence.
+Instead this measure should be treated merely as a way to suggest users with casually related (in a Granger sense) tweet histories, i.e., users with PV-AC.
 
@@
 Various other information theoretic approaches have been used successfully to analyze online social networks, \emph{e.g.,} to gain insight into local user behavior~\cite{darmon2013understanding}, to detect communities based on \emph{undirected} information flow~\cite{darmon2013detecting}, and to perform network inference and link prediction~\cite{ver2012information}.
-%While various information theoretic measures has been applied previously to the analysis of networks arising in online social media~\cite{ver2012information,darmon2013detecting},
 
-Our topic-based and interaction-based approaches, in contrast to the activity-based approach, rely on the \emph{content} of a user's interactions and ignore their temporal components.
+The topic-based and interaction-based approaches, in contrast to the activity-based approach, rely on the \emph{content} of a user's interactions and ignore their temporal components.
 The content contains a great deal of information about communication between users.
@@
 The LDA model can then be used to infer distributions over latent topics, and the similarity of two users with respect to topics may be defined in terms of the distance between their associated topic distributions.
-Because our focus is not on topic identification, we apply a simpler approach using hashtags as a proxy for topics~\cite{becker2011beyond,tsur2012s}.
+Because our focus is not on topic identification, we apply a simpler approach using hashtags as a proxy for topics similar to the approaches presented in~\cite{becker2011beyond,tsur2012s}.
 We can then define the similarity of two users in terms of their hashtags, and use this similarity to build a topic-based network.
@@
 On Twitter, we can use mentions (indicating a directed communication) and retweets (indicating endorsement of another user) to identify conversation.
-Moreover, we can define a directed influence between two users by considering the attention paid to that user compared to all other users.
+\alert{Wonder if the following sentence can be removed, to remove confusion between this and activity} Moreover, we can define a directed influence between two users by considering the attention paid to that user compared to all other users.
 This allows us to generate a network based on conversations and user interactions.
@@
 
-The activity-based, topic-based, and interaction-based networks allow us to build a more complete picture of the \emph{implicit} networks present in online social media, as opposed to the \emph{explicit} social network indicated by structural links.
+Studying the intersections and lack-thereof of the communities derived from follower-followee, activity-based, topic-based, and interaction-based networks allow us to build a more complete picture of the \emph{implicit} networks present in online social media, as opposed to the \emph{explicit} social network indicated by structural links alone.
 In this paper, we explore the relation between these various possible networks and their corresponding communities.
@@
 Finally, we explore how communication patterns differ across and within the different community types.
-
+We conclude by illustrating that this multi-faceted question-oriented approach to community detection provides interesting insight into the intricate multi-faceted structure of several different users communities; information that would not be available if only a single round of community detection was performed.
 %\section{Related Work}

### 2014-11-17 paper-postreview/methods.tex
first round of edits

--- 2014-08-18 paper-for_arxiv/methods.tex
@@
 \end{align}
-As discussed in the introduction, a positive value for the transfer entropy of the user $u$ on $f$ indicates that $u$ influences $f$, or that $u$ and $f$ share a common influencer~\cite{ver2012information}, and that the time series $X(u)$ and $X(f)$, are casually related in a Granger sense.
+As discussed in the introduction, a positive value for the transfer entropy of the user $u$ on $f$ indicates that the time series $X(u)$ and $X(f)$, are casually related in a Granger sense, i.e, users $u$ and $f$ have PV-AC.
 

### 2014-11-18 paper-postreview/conclusions.tex
editing influence stuff

--- 2014-08-25 paper-for_arxiv/conclusions.tex
@@
 At first glance the boundaries defined by the activity-based communities derived from the transfer entropy weighting seemed less meaningful.
-However, upon further investigation our novel use of transfer entropy for the detection of activity-based communities highlighted an important fact about this social network: influence tended to be higher across community boundaries than within them.
+However, upon further investigation our novel use of transfer entropy for the detection of activity-based communities highlighted an important fact about this social network: information transmission tended to be higher across community boundaries than within them.
 This result echos the `strength of weak ties' theory from~\cite{granovetter1973strength}, which has found empirical support in online social networks~\cite{grabowicz2012social}.
-This means that our use of transfer entropy not only defines boundaries that are meaningful divisions between communities but also illustrates that users who have a strong influence on a community need not be a member of that community.
+This means that our use of transfer entropy not only defines boundaries that are meaningful divisions between communities but also illustrates that users who have a strong PV-AC on a community need not be a member of that community.
 
@@
 Our findings may have important implications to a common problem in social network analysis: identification of influential individuals---but further work must be carried out.
+\alert{maybe move the top 10 people here}
  Many network measures of influence are based on the various types of centrality (degree, betweenness, closeness, eigenvector, etc.)~\cite{newman2009networks}.
@@
 
-This work demonstrates that asking the proper question, and then crafting an appropriate weighting scheme to answer that question, is an unavoidable first step for community detection in online social media.
-More generally, this work illustrates that without a clear definition of community, many rich and interesting communities present in online social networks remain invisible.
+This work demonstrates that asking the proper question, and then crafting an appropriate weighting scheme to answer that question, is an unavoidable first step for community detection in online social media.\alert{need to add to the paragraph the asking multiple question} More generally, this work illustrates that without a clear definition of community, many rich and interesting communities present in online social networks remain invisible.
 Question-oriented community detection can bring those hidden communities into the light.

### 2014-11-18 paper-postreview/results.tex
editing influence stuff

--- 2014-08-25 paper-for_arxiv/results.tex
@@
 
+\alert{need to reword this to hedge or remove the influence...}
 As an aside, it is interesting to examine who the most influential users are in these communities, as determined by transfer entropy.

### 2014-11-18 paper-postreview/results.tex
Addressed next actions.
Addressed my next actions from

action-items-141114.txt

@@
 the empirical distribution over the edge weights conditioned on the edge type $t$ being one of inter, intra, and mixed.
-For meaningful community structure, we expect the distribution of edge weights to differ with the edge type $t$.
+The densities associated with these distributions are shown in Figure~\ref{Fig-distributions_by_types}.
+By considering how the weights vary conditional on the edge type, we can explore whether and how each of the follower-, interaction-, activity-, and topic-based communities define functional units within the network.
+For example, if users interact more-or-less independently of the topics they discuss, then the distributions of the interaction-based / topic-based edge weights should be independent of the edge type determined from the topic-based / interaction-based communities.
+By contrast, if users tend to interact mostly with those users who discuss similar topics, then the edge weight distributions should vary with the edge type.
+%For meaningful community structure, we expect the distribution of edge weights to differ with the edge type $t$.
 If the community structure were arbitrary, the edge weights would be independent of the edge type, and all three conditional distributions would be identical.
-The densities associated with these distributions are shown in Figure~\ref{Fig-distributions_by_types}.
 \begin{figure}[!h]

### 2014-11-18 paper-postreview/appendices.tex
working on influece

--- 2014-10-29 paper-prereview/appendices.tex
@@
 \end{align}
-we can see that transfer entropy is always non-negative, and is zero precisely when $$H\left[X_{t} | X_{t-k}^{t-1}\right] = H\left[X_{t} | X_{t-k}^{t-1}, Y_{t-k}^{t-1}\right]$$, in which case knowing the past $k$ lags of $Y_{t}$ does not reduce the uncertainty in $X_{t}$.
+we can see that transfer entropy is always non-negative, and is zero precisely when $$H\left[X_{t} | X_{t-k}^{t-1}\right] = H\left[X_{t} | X_{t-k}^{t-1}, Y_{t-k}^{t-1}\right],$$ in which case knowing the past $k$ lags of $Y_{t}$ does not reduce the uncertainty in $X_{t}$.
 If the transfer entropy is positive, then $\{ Y_{t}\}$ is considered causal for $\{ X_{t}\}$ in the Granger sense~\cite{granger1963economic}.

### 2014-11-18 paper-postreview/results.tex
working on influece

--- 2014-08-25 paper-for_arxiv/results.tex
@@
 
-As an aside, it is interesting to examine who the most influential users are in these communities, as determined by transfer entropy.
-Recall that influence in this context refers to a reduction in uncertainty about a follower(s) activity on Twitter given the tweet history of a followee.
-Said differently, higher transfer entropy, or a higher reduction in uncertainty, implies more influence.
-Interestingly, among the most influential users in these communities, those with highest transfer entropy on average, we find \@Colorado, which is the state official Twitter account, \@ConnectColorado, a page created to connect Coloradans, and the CBS Denver account, a popular news agency.
-This means that these accounts had high influence in terms of their followers' activity on Twitter.
+As an aside, it is interesting to examine which users had the greatest PV-AC in these communities.
+Recall that this refers to a reduction in uncertainty about a follower(s) activity on Twitter given the tweet history of a followee.
+%Said differently, higher transfer entropy, or a higher reduction in uncertainty, implies more influence.
+Interestingly, among the highest PV-AC users in these communities--- those with highest transfer entropy on average---we find @Colorado, which is the state official Twitter account, @ConnectColorado, a page created to connect Coloradans, and the CBS Denver account, a popular news agency.
+This means that these accounts had high predictive capacity in terms of their followers' activity on Twitter.
 This is not surprising as these communities discuss Colorado and these accounts provide information on this topic.
-However, this does provide a check that this measure of activity-based influence makes sense and suggests this could be a useful measure for influence on social media if used with other measures.
-This is discussed more in future work.
+However, this does provides a brief proof of concept that this measure makes sense and suggests this could be a useful measure for identifying individuals who possess high predictive capacity with a communities activity on social media networks.
 

### 2014-11-18 paper-postreview/conclusions.tex

@@
 \section{Conclusion and Future Work}
+
+\label{sec:conc}
 
@@
 Most centralities depend explicitly on the structure of the network under consideration.
-But we have seen in our study that a structural network alone is not sufficient to capture user interaction or even activity-based influence in online social media.
-Thus, a na\"ive application of centrality measures to a structural network for influence detection may give rise to erroneous results.
-This result has been explored previously~\cite{kitsak2010identification}, and our work further highlights its importance.
+But we have seen in our study that the structural network only highlights one of many possible ways that users interact with online social media.
+%But we have seen in our study that a structural network alone is not sufficient to capture user interaction or even activity-based influence in online social media.
+Thus, a na\"ive application of centrality measures to a structural network may be answering a different question than the one motivating influence detection.
+For example, a user exhibiting high closeness centrality based on the structural network may be able to make a message visible to most other users in a social network, but this does not mean that those other users are likely to respond to or propagate that message.
+The importance of correctly framing network measures of influence has been explored previously~\cite{kitsak2010identification}, and our work further highlights its importance.
 

### 2014-11-18 paper-postreview/intro.tex

@@
 See~\cite{fortunato2010community} for a recent review.
-A large body of work exists on methods for automatic detection of communities within networks, {\it e.g.,} the stochastic blockmodel~\cite{Holland1983} (and its recent generalization to weighted networks~\cite{Aicher26062014}), the Newman and Girvan algorithm~\cite{newman2004finding}, clique percolation~\cite{PalEtAl05}, Infomap~\cite{Rosvall08mapsof}, Louvain~\cite{blondel2008fast}, and the recently introduced OSLOM~\cite{LancichinettiPlos}.
+A large body of work exists on methods for automatic detection of communities within networks, {\it e.g.,} the stochastic blockmodel~\cite{Holland1983} (and its recent generalization to weighted networks~\cite{Aicher26062014}), the Girvan-Newman algorithm~\cite{newman2004finding}, clique percolation~\cite{PalEtAl05}, Infomap~\cite{Rosvall08mapsof}, Louvain~\cite{blondel2008fast}, and the recently introduced OSLOM~\cite{LancichinettiPlos}.
 All these methods begin with a given network, and then attempt to uncover structure present in the network, \emph{i.e.,} they are agnostic to how the network was constructed.
@@
 For example, a user on Twitter might connect mostly with computational social scientists, utilize the service nearly every time a particular user or group of users is active, talk mostly about machine learning, and interact solely with close friends (who may or may not be computational social scientists).
-Each of these different `profiles' of the user highlight different views of the user's social network, and represent different types of communities.
+For this user, the answers to each question therefore correspond to more or less distinct communities.
+By contrast, a teenage user may only connect and interact with their friends, will most likely exhibit similar activity patterns dictated by the academic and extracurricular schedule of a student.
+For this user, the answers to each question map to the same community of users.
+Thus, each question acts to highlight a particular `profile' of a user, and these profiles can help identify the ways in which a user interacts with and like other users in their online social network.
 We now consider in more detail how each of these types of questions motivates a question-specific community.
-Later in Section~\ref{sec:conc} we will show how asking \emph{all} of these questions---instead of just one which is the standard---gives a much deeper multi-faceted view of the overlapping \emph{and} disjoint communities users belong to.
+Later in Section~\ref{sec:conc} we will show how asking \emph{all} of these questions---instead of focusing on only one---gives a much deeper multi-faceted view of the overlapping \emph{and} disjoint communities that users belong to.
 
-Na\"ively the activity-based approach is motivated by the question of ``Which users in a network have similar activity profiles?".%, \emph{i.e.,} which user(s) cause groups of users to become active on the network.
+Na\"ively the activity-based approach is motivated by the question of ``Which users in a network have similar activity profiles?"%, \emph{i.e.,} which user(s) cause groups of users to become active on the network.
 %, \emph{i.e.}, which user(s) cause a user(s) to interact with the network.
@@
 On Twitter, we can use mentions (indicating a directed communication) and retweets (indicating endorsement of another user) to identify conversation.
-\alert{Wonder if the following sentence can be removed, to remove confusion between this and activity} Moreover, we can define a directed influence between two users by considering the attention paid to that user compared to all other users.
-This allows us to generate a network based on conversations and user interactions.
 A few works have investigated this type of community.
@@
 
-Studying the intersections and lack-thereof of the communities derived from follower-followee, activity-based, topic-based, and interaction-based networks allow us to build a more complete picture of the \emph{implicit} networks present in online social media, as opposed to the \emph{explicit} social network indicated by structural links alone.
+Studying the intersections and lack-thereof of the communities derived from follower-followee, activity-based, topic-based, and interaction-based networks allow us to build a more complete picture of the \emph{implicit} networks present in online social media, as opposed to the \emph{explicit} social network indicated by follower links alone.
 In this paper, we explore the relation between these various possible networks and their corresponding communities.
@@
 Finally, we explore how communication patterns differ across and within the different community types.
-We conclude by illustrating that this multi-faceted question-oriented approach to community detection provides interesting insight into the intricate multi-faceted structure of several different users communities; information that would not be available if only a single round of community detection was performed.
+We conclude by illustrating that this multi-faceted question-oriented approach to community detection provides interesting insight into the intricate multi-faceted structure of several different users' communities; information that would not be available if only a single form of community detection was performed.
 %\section{Related Work}

### 2014-11-18 paper-postreview/methods.tex

@@
 The only biasing steps in this procedure are the selection of the seed node and the filtering out of inactive users.
-However, because all of the community types we are interested in involve some aspect of the interaction between users, each other, and their content, the procedure provides a relatively question-agnostic follower-followee network for use with the different question-based analyses.
+However, because all of the community types we are interested in involve some aspect of the interaction between users, each other, and their content, this procedure provides a reasonable follower-followee network for use with the different question-based analyses.
 
@@
 In this study the link is directed from the user to the follower because this is the direction in which information flows.
-Thus, for a pair of users $u$ and $v$, an edge $a_{v \to u}$ in the structural network has weight 1 if user $u$ follows $v$, and 0 otherwise.
+Thus, for a pair of users $u$ and $v$, an edge $a_{v \to u}$ in the follower-followee network has weight 1 if user $u$ follows $v$, and 0 otherwise.
 The final network consists of 6,917 nodes and 1,481,131 edges.

### 2014-11-18 paper-postreview/paper.tex
first round of edits

--- 2014-08-18 paper-for_arxiv/paper.tex
@@
 
-\title{Followers Are Not Enough: A Question-Oriented Approach to Community Detection in Online Social Networks}
+\title{Followers Are Not Enough: A Multi-faceted Approach to Community Detection in Online Social Networks}
 
@@
 Community detection in online social networks is typically based on the analysis of the explicit connections between users, such as ``friends" on Facebook and ``followers" on Twitter.
-But online users often have hundreds or even thousands of such connections, and many of these connections do not correspond to real friendships or more generally to accounts that users interact with.
-We claim that community detection in online social networks should be question-oriented and rely on additional information beyond the simple structure of the network.
+But online users often have hundreds or even thousands of such connections, many of which connect them with news outlets, governmental organizations, etc., in addition to their friends and associates.
+Because of the multi-faceted nature of these networks, we claim that community detection in online social networks should be question-oriented and rely on additional information beyond the simple structure of the network.
 The concept of `community' is very general, and different questions such as ``whom do we interact with?" and ``with whom do we share similar interests?" can lead to the discovery of different social groups.

### 2014-11-19 paper-postreview/conclusions.tex
working on adding the second goal everywhere

@@
 
-This work demonstrates that asking the proper question, and then crafting an appropriate weighting scheme to answer that question, is an unavoidable first step for community detection in online social media.\alert{need to add to the paragraph the asking multiple question} More generally, this work illustrates that without a clear definition of community, many rich and interesting communities present in online social networks remain invisible.
-Question-oriented community detection can bring those hidden communities into the light.
+This work demonstrates the utility of a multi-faceted question-oriented approach to community detection.
+This work shows that crafting \emph{several} facet-driven weighting schema, doing community detection for each weighting scheme and then comparing the similarities and differences across community types, is an unavoidable process for unconvering the multi-leveled community structure present in online social media.
+More generally, this work illustrates that without a clear definition of community---or even only using a \emph{single} definition of community---many rich and interesting communities present in online social networks remain invisible.
+Multi-faceted question-oriented community detection can bring those hidden communities into the light.

### 2014-11-19 paper-postreview/intro.tex
working on adding the second goal everywhere

@@
 \begin{enumerate}
-\item Form a clear question about what \emph{type} of community we wish to consider---{\it e.g.,} are we looking for groups of friends?
+\item Form a clear question about what \emph{type} of community under consideration---{\it e.g.,} are we looking for groups of friends?
 or for groups of people having a common interest?---and then perform community detection with that question in mind.
-\item Ask more than one question about the users in a network. Do several rounds of community detection, each of which is aimed at revealing a new facet of the communities present in the network. 
+\item Ask more than one question about the users in a network and perform several rounds of community detection, each of which is aimed at revealing a new facet of the communities present in the network.
 \end{enumerate}
@@
 
-Studying the intersections and lack-thereof of the communities derived from follower-followee, activity-based, topic-based, and interaction-based networks allow us to build a more complete picture of the \emph{implicit} networks present in online social media, as opposed to the \emph{explicit} social network indicated by follower links alone.
+Studying how the communities derived from follower-followee, activity-based, topic-based, and interaction-based networks are disjoint as well as overlapping allow for a more complete picture of the \emph{implicit} networks present in online social media, as opposed to the \emph{explicit} social network indicated by follower links alone.
 In this paper, we explore the relation between these various possible networks and their corresponding communities.

### 2014-11-19 paper-postreview/results.tex
working on adding the second goal everywhere

@@
 
-As an aside, it is interesting to examine which users had the greatest PV-AC in these communities.
+As an aside, it is interesting to examine which users had the highest PV-AC in these communities.
 Recall that this refers to a reduction in uncertainty about a follower(s) activity on Twitter given the tweet history of a followee.
-%Said differently, higher transfer entropy, or a higher reduction in uncertainty, implies more influence.
-Interestingly, among the highest PV-AC users in these communities--- those with highest transfer entropy on average---we find @Colorado, which is the state official Twitter account, @ConnectColorado, a page created to connect Coloradans, and the CBS Denver account, a popular news agency.
+Said differently, users with the highest PV-AC in an activity-based community provide the highest reduction in uncertainty about that communities activity or inactivity on Twitter.
+Interestingly, among the highest PV-AC users in these communities---those with highest transfer entropy on average---we find @Colorado, which is the state official Twitter account, @ConnectColorado, a page created to connect Coloradans, and the CBS Denver account, a popular news agency.
 This means that these accounts had high predictive capacity in terms of their followers' activity on Twitter.
 This is not surprising as these communities discuss Colorado and these accounts provide information on this topic.
-However, this does provides a brief proof of concept that this measure makes sense and suggests this could be a useful measure for identifying individuals who possess high predictive capacity with a communities activity on social media networks.
+This provides a brief proof of concept that this measure makes sense and suggests this could be a useful measure for identifying individuals who possess high predictive capacity with a communities activity on a social media network.
+However, more work needs to be done to quantify this more fully.
 
-Lastly, it is interesting to note that two of the Forbes ``Top 10 Social Media Influencers", % ranked using the total outgoing strength in the activity-based network, 
- happen to be in our network, \emph{viz.}, Ann Tran and Jessica Northey, and transfer entropy also quantified these two users as highly influential.
+Lastly, it is interesting to note that two of the Forbes ``Top 10 Social Media Influencers",
+ happen to be in our network, \emph{viz.}, Ann Tran and Jessica Northey, and transfer entropy also quantified these two users as having high PV-AC, i.e., the uncertainty about their followers activity on Twitter was reduced given their tweet histories.
+While we do not believe this information theoretic measure can capture social influence in its entirety,
 % members, as categorized by transfer entropy. 
-This suggests that activity-based or information-theoretic influence may be useful in finding influential members purely based on their temporal tweet history while completely ignoring both tweet content and social status.
+this suggests that this activity-based measure may be useful in finding influential members purely based on their temporal tweet history; even completely ignoring both tweet content and social status.
+However, a deeper analysis would need to be carried out to verify this finding.

### 2014-11-19 paper-postreview/methods.tex
modif sec 2.4

@@
 %A way of tracking the flow of information through users is by considering two useful features of this social network: mentions and retweets. 
-With mentions, users are sending directed information to other users and with retweets users are rebroadcasting information from a user they follow to all of their followers. 
+With mentions, users are sending direct information to other users and with retweets users are rebroadcasting information from a user they follow to all of their followers.
 %information from a user has been captured by a follower and shared with his/her own followers. 
@@
 % We can therefore define interaction-based communities by weighting the user-follower network with a measure proportional to the number of mentions and retweets between users. 
-For the interaction-based communities we consider three weighting schemes: proportional retweets,
+% For the interaction-based communities we consider three weighting schemes: proportional retweets,
+We define three weighting schemes.
+Firstly, we consider the number of tweets of a user $u$ that were rebroadcast by a follower $f$, indicating a flow of information from $u$ to $f$.
+Since different users produce different amounts of tweets and retweets, in order to take into account the relative importance of this measure we normalize it by dividing over the total number of retweets made by $f$,
 \begin{equation}
-w_{u \to f}^{\text{R}}=pR=\frac{\mbox{\# retweets of }u \mbox{ by }f}{\mbox{\# total retweets made by }f},
+w_{u \to f}^{\text{R}}=\frac{\mbox{\# retweets of }u \mbox{ by }f}{\mbox{\# total retweets made by }f},
 \end{equation}
-proportional mentions,
+Secondly, we consider the number of mentions of $f$ made by user $u$.
+To account for the fact that some users/accounts are very popular and are often mentioned by so many other users that there is not real flow of information from the latter to the former, we normalize this measure by dividing over the total number of mentions received by $f$.
 \begin{equation}
-w_{u \to f}^{\text{M}} = pM = \frac{\mbox{\# mentions of }f \mbox{ by }u}{\mbox{\# total mentions of }f},
+w_{u \to f}^{\text{M}} = \frac{\mbox{\# mentions of }f \mbox{ by }u}{\mbox{\# total mentions of }f},
 \end{equation}
-and mention-retweet as the arithmetic mean of these two measures,
+Finally, we define the mention-retweet proportion as the arithmetic mean of the two measures just defined,
 %we weight each edge from a user $u$ to a follower $f$ through a combination of proportional mentions ($pM$):
@@
 \begin{align}
-	w_{u \to f}^{\text{MR}} = \frac{(pM+pR)}{2}. \label{Eqn-EW-interaction}
+	w_{u \to f}^{\text{MR}} = \frac{(w_{u \to f}^{\text{R}}+w_{u \to f}^{\text{M}})}{2}. \label{Eqn-EW-interaction}
 \end{align}

### 2014-11-19 paper-postreview/results.tex
editing results for PV-AC stuff

@@
 
-As an aside, it is interesting to examine which users had the highest PV-AC in these communities.
+As a sanity check, it is interesting to examine the intersection between this topic-based community and the overlapping activity-based communities and explore which users in the intersection of these community types had the highest PV-AC.
 Recall that this refers to a reduction in uncertainty about a follower(s) activity on Twitter given the tweet history of a followee.
@@
 This means that these accounts had high predictive capacity in terms of their followers' activity on Twitter.
-This is not surprising as these communities discuss Colorado and these accounts provide information on this topic.
-This provides a brief proof of concept that this measure makes sense and suggests this could be a useful measure for identifying individuals who possess high predictive capacity with a communities activity on a social media network.
+This is not surprising as these activity-based communities heavily overlapped with the topic-based communities that discuss Colorado (mentioned above) and these accounts provide information on this topic.
+This provides a brief proof of concept that this measure makes sense and suggests this could be a useful measure for identifying individuals who possess high predictive capacity for a communities activity on a social media network.
 However, more work needs to be done to quantify this more fully.
 
-Lastly, it is interesting to note that two of the Forbes ``Top 10 Social Media Influencers",
- happen to be in our network, \emph{viz.}, Ann Tran and Jessica Northey, and transfer entropy also quantified these two users as having high PV-AC, i.e., the uncertainty about their followers activity on Twitter was reduced given their tweet histories.
+Lastly, it is interesting to note that two of the Forbes ``Top 10 Social Media Influencers", happen to be in our network, \emph{viz.}, Ann Tran and Jessica Northey, and transfer entropy also quantified these two users as having high PV-AC, i.e., the uncertainty about their followers activity on Twitter was reduced given their tweet histories.
 While we do not believe this information theoretic measure can capture social influence in its entirety,

### 2014-11-20 paper-postreview/results.tex
modif sec 3.4

@@
 
-\subsection{Qualitative Analysis of Community Memberships Across Types}
+%\subsection{Qualitative Analysis of Community Memberships Across Types}
+\subsection{Answering the Questions}
 
-As demonstrated by~\cite{good2010performance} in the context of modularity maximization-based community detection, an exponential number of nearby partitions may exist that nearly maximize an objective function used to measure the goodness-of-fit of a graph partition used for community detection.
+%As demonstrated by~\cite{good2010performance} in the context of modularity maximization-based community detection, an exponential number of nearby partitions may exist that nearly maximize an objective function used to measure the goodness-of-fit of a graph partition used for community detection.
 Because of this and related issues, it is always wise to perform some sort of qualitative study of the communities returned by any  community detection algorithm to verify their meaningfulness with respect to the scientific question at hand.
 In this section, we consider a collection of communities in such a study.
+
+In the previous sections we showed how the communities emerging from the different weightings of the follower-followee network differ quantitatively both at the macro and at the micro scale.
+Here we present some concrete examples of such different communities, in order to show more precisely the interest of using a multi-faceted approach to community detection.
+We explore this at two scale: firstly at the community level, and then at the individual level.
 
@@
 However, a deeper analysis would need to be carried out to verify this finding.
+
+On an individual-based level, we also found some interesting cases of membership to different communities, which show that asking different questions leads indeed to finding different kinds of communities a user belongs to.
+For example, the user @JohnReaves belongs to two different topic communities: one talking about healthcare and the other talking about innovation and creativity.
+There is a almost $70\%$ overlap between the users in the innovation and creativity topic community and the interaction-based community and the activity-based community the user is in, whereas there is almost no overlap between these two and the healthcare community.
+This means that he interacts and behaves alike the people talking about innovation and creativity, whereas he also talks about healthcare but he does not interact with (nor behave alike) the people talking about that.
+Secondly, user @jenajean also belongs to two different topic communities: she talks about Nasa and space but she does not interact nor behave alike people in that communities, whereas she also talks a lot about leadership and the people she interacts with highly overlap with the people belonging to the topic-based community on leadership she belongs to.
+Lastly, @rajean, @Tekee, @Kimbirly and @mamamonroe are examples of users belonging to the topic community talking about Denver and Colorado (and to only that topic communitiy).
+The activity-based community they belong to highly overlaps with the topic community (therefore they behave like the people that talk about Colorado), but they belong to different interaction-based communities, each of which does NOT overlap with the topic community a part for one or two users max.
+Therefore they interact with other groups of people.

### 2014-11-20 paper-postreview/results.tex
modif sec 3.4

@@
 This means that he interacts and behaves alike the people talking about innovation and creativity, whereas he also talks about healthcare but he does not interact with (nor behave alike) the people talking about that.
-Secondly, user @jenajean also belongs to two different topic communities: she talks about Nasa and space but she does not interact nor behave alike people in that communities, whereas she also talks a lot about leadership and the people she interacts with highly overlap with the people belonging to the topic-based community on leadership she belongs to.
+Secondly, user @jenajean also belongs to two different topic communities: she talks about Nasa and space but she does not interact nor behave alike people in that communities, whereas she also talks a lot about leadership, and the people she interacts with highly overlap with the people belonging to the topic-based community on leadership she belongs to.
 Lastly, @rajean, @Tekee, @Kimbirly and @mamamonroe are examples of users belonging to the topic community talking about Denver and Colorado (and to only that topic communitiy).
-The activity-based community they belong to highly overlaps with the topic community (therefore they behave like the people that talk about Colorado), but they belong to different interaction-based communities, each of which does NOT overlap with the topic community a part for one or two users max.
+The activity-based community they belong to highly overlaps with the topic community (therefore they behave like the people that talk about Colorado), but they belong to different interaction-based communities, each of which does not overlap with the topic community a part for one or two users.
 Therefore they interact with other groups of people.

### 2014-11-20 paper-postreview/methods.tex
edits

@@
 Thus, the new coarsened time series now captures whether or not the user has been active on Twitter over any given ten minute time interval in our data set.
-We can then compute the flow of information between two users $u$ and $v$ by computing the transfer entropy between their time series $X_{t}(u)$ and $X_{t}(v).$ See Appendix A for a detailed introduction to transfer entropy and its estimation from data.
+It should be noted that, as (most) users are not constantly tweeting, these time series are quite sparse.
+This sparsity will skew the distribution of tweet activity toward being inactive, as the distribution should be to reflect realistic interaction patterns.
+However, if this measure is to be used in practice a deeper analysis of the effects of binning, the resulting sparsity and their role in the activity-based community structure should be carried out.
 
+We can then compute the flow of information from a user  $u$ to a follower $f$ by computing the transfer entropy between their time series $X_{t}(u)$ and $X_{t}(f).$ See Appendix A for a detailed introduction to transfer entropy and its estimation from data.
 For the communities based on transfer entropy, we weighted each edge from a user $u$ to a follower $f$ by the estimated transfer entropy of the user $u$ on $f$,
@@
 \end{align}
-As discussed in the introduction, a positive value for the transfer entropy of the user $u$ on $f$ indicates that the time series $X(u)$ and $X(f)$, are casually related in a Granger sense, i.e, users $u$ and $f$ have PV-AC.
+As discussed in the introduction, a positive value for the transfer entropy of the user $u$ on $f$ indicates that the time series $X(u)$ and $X(f)$, are casually related in a Granger sense, i.e, user $u$ has PV-AC with follower $f$.
+Said differently, there is a reduction in uncertainty about the activity of $f$ given the tweet history of user $u$.
 
@@
 The choice of lag must balance a trade-off between additional information and sparsity of samples: as we increase the lag $k$, we account for longer range dependencies, but we also decrease the number of samples available to infer a higher dimensional predictive distribution.
+Interestingly, as we will show later, the underlying communities resulting from the different lags have similar structure.
 See Appendix A for a discussion of these issues.
-As we will show, the underlying communities resulting from the different lags have similar structure.
 

### 2014-11-20 paper-postreview/conclusions.tex
massive edits including abstract and title replace and finishing action list

@@
 But we have seen in our study that the structural network only highlights one of many possible ways that users interact with online social media.
-%But we have seen in our study that a structural network alone is not sufficient to capture user interaction or even activity-based influence in online social media.
 Thus, a na\"ive application of centrality measures to a structural network may be answering a different question than the one motivating influence detection.
@@
 
-This work demonstrates the utility of a multi-faceted question-oriented approach to community detection.
-This work shows that crafting \emph{several} facet-driven weighting schema, doing community detection for each weighting scheme and then comparing the similarities and differences across community types, is an unavoidable process for unconvering the multi-leveled community structure present in online social media.
+This work demonstrates the utility of a multifaceted question-oriented approach to community detection.
+This work shows that crafting \emph{several} facet-driven weighting schema, doing community detection for each weighting scheme and then comparing the similarities and differences across community types, is an unavoidable process for uncovering the hidden layered community structure present in online social networks.
 More generally, this work illustrates that without a clear definition of community---or even only using a \emph{single} definition of community---many rich and interesting communities present in online social networks remain invisible.
-Multi-faceted question-oriented community detection can bring those hidden communities into the light.
+Multifaceted question-oriented community detection can bring those hidden communities into the light.

### 2014-11-20 paper-postreview/intro.tex
massive edits including abstract and title replace and finishing action list

@@
 All these methods begin with a given network, and then attempt to uncover structure present in the network, \emph{i.e.,} they are agnostic to how the network was constructed.
-As opposed to this agnostic analysis, we propose---and illustrate the importance of---a \emph{multi-faceted question-focused} approach.
-We believe that in order to understand all of the communities present in a network, it is important to take two crucial steps:
+As opposed to this agnostic analysis, we propose---and illustrate the importance of---a \emph{multifaceted question-focused} approach.
+We believe that in order to understand all of the communities present in a network, it is important to take the following crucial steps:
 \begin{enumerate}
-\item Form a clear question about what \emph{type} of community under consideration---{\it e.g.,} are we looking for groups of friends?
-or for groups of people having a common interest?---and then perform community detection with that question in mind.
-\item Ask more than one question about the users in a network and perform several rounds of community detection, each of which is aimed at revealing a new facet of the communities present in the network.
+
+\item Ask \emph{several} questions about the communities that may be present in the network, each of which is aimed at revealing a new facet of the community present in the network---{\it e.g.,} which users are tightly connected structurally?
+which groups of users have similar topical interests?
+
+\item Derive a weighting scheme aimed at answering each of the questions asked in the first step and then perform community detection on each weighted network.
+\item Compare the disjoint \emph{and} overlapping communities that arise from this series of experiments on a micro and macro scale to unveil all the interesting facets of community present in the social network.
 \end{enumerate}
@@
 This is especially true for social network analysis.
-In online social networks, a `community' could refer to several possible structures.
+In social networks, a `community' could refer to several possible structures.
 The simplest definition of community, as we have seen, might stem from the network of explicit connections between users on a service (friends, followers, etc.).
-On small time scales, these connections are more or less static, and we might instead determine communities based on who is talking to whom, providing a more dynamic picture.
-On a more abstract level, a user might consider themselves part of a community of people discussing similar topics.
-We might also define communities as collections of people who exhibit similar activity profiles.
+On small time scales, these connections are more or less static, and we might instead determine communities, as is standard in the literature\alert{david or elisa can you add some citations please}\cite{}, based on who is talking to whom or which users talk about similar topics, providing a more dynamic picture of community.
+More abstractly, we could even define communities as groups of people who exhibit similar activity profiles.
 We can characterize these types of communities based on the types of questions we might ask about them:
@@
 
-This is not meant to be an exhaustive list, but rather a list of some of the more common types of communities observed in social networks.
-We propose looking at when and how communities motivated by these different questions overlap, and whether different approaches to asking the question, ``What community are you in?'' leads to different insights about a social network.
+This is not meant to be an exhaustive list, but rather a list of some of the more common types of communities observed and studied in social networks.
+Instead of looking at each of these questions in isolation---which is the standard approach---we propose looking at when, why, and how communities motivated by these different questions overlap and are disjoint, and whether different approaches to asking the question, ``What community are you in?'' leads to different insights about a social network.
 For example, a user on Twitter might connect mostly with computational social scientists, utilize the service nearly every time a particular user or group of users is active, talk mostly about machine learning, and interact solely with close friends (who may or may not be computational social scientists).
@@
 We now consider in more detail how each of these types of questions motivates a question-specific community.
-Later in Section~\ref{sec:conc} we will show how asking \emph{all} of these questions---instead of focusing on only one---gives a much deeper multi-faceted view of the overlapping \emph{and} disjoint communities that users belong to.
+Later in Section~\ref{sec:conc} we will show how asking \emph{all} of these questions---instead of focusing on only one---gives a much deeper multifaceted view of the overlapping \emph{and} disjoint communities that users belong to.
 
-Na\"ively the activity-based approach is motivated by the question of ``Which users in a network have similar activity profiles?"%, \emph{i.e.,} which user(s) cause groups of users to become active on the network.
-%, \emph{i.e.}, which user(s) cause a user(s) to interact with the network.
+Na\"ively the activity-based approach is motivated by the question of ``Which users in a network have similar activity profiles?"
+%--- \emph{i.e.,} which user(s) cause groups of users to become active on the network.  %, \emph{i.e.}, which user(s) cause a user(s) to interact with the network. 
  With this question in mind, a community can then be thought of as those users who use (or do not use) the service at similar times.
@@
 Transfer entropy is an information theoretic measure of \emph{directed} information flow.
-A positive transfer entropy from the tweet history of a user $u$ to a follower $f$'s tweet history implies that this relationship is causal in the Granger sense~\cite{granger1963economic}.
+Since transfer entropy is a nonlinear generalization of Granger causality \cite{granger1963economic}, we assume---as is standard---a positive transfer entropy from the tweet history of a user $u$ to a follower $f$'s tweet history implies that this relationship is causal in the Granger sense.
 Thus, communities detected in this way have members whose tweet histories are causally related in a Granger sense.
@@
 We call this relation ``PV-AC".
-While we are skeptical that this measure can capture social influence, later in this paper we show that this information theoretic measure agrees with other concepts of influence such as the Forbes list of ``Top 10 Social Media Influencers" and corroborates with the so-called strength of weak ties~\cite{granovetter1973strength}.
+As an aside, while we are skeptical that this measure can capture social influence, later in this paper we show that this information theoretic measure agrees with other concepts of influence such as the Forbes list of ``Top 10 Social Media Influencers" and corroborates with the so-called strength of weak ties~\cite{granovetter1973strength}.
 Even so, we do not explicitly treat---and we do not believe it should be treated---as a quantification of social influence.
-Instead this measure should be treated merely as a way to suggest users with casually related (in a Granger sense) tweet histories, i.e., users with PV-AC.
+Instead this measure should be treated merely as a way to suggest users with casually related (in a Granger sense) tweet histories, i.e., users with similar activity profiles (PV-AC).
 
@@
 Finally, we explore how communication patterns differ across and within the different community types.
-We conclude by illustrating that this multi-faceted question-oriented approach to community detection provides interesting insight into the intricate multi-faceted structure of several different users' communities; information that would not be available if only a single form of community detection was performed.
+We conclude by illustrating that this multifaceted question-oriented approach to community detection provides interesting insight into the intricate multifaceted structure of several different users' communities; information that would not be available if only a single form of community detection was performed.
 %\section{Related Work}

### 2014-11-20 paper-postreview/methods.tex
massive edits including abstract and title replace and finishing action list

@@
 \section{Methodology}
-
+\alert{this should be reworded to emphasize these are not all our methods!!}
 In the following sections, we introduce the problem of community detection, and present the data set used for our analyses.
@@
 It should be noted that, as (most) users are not constantly tweeting, these time series are quite sparse.
-This sparsity will skew the distribution of tweet activity toward being inactive, as the distribution should be to reflect realistic interaction patterns.
+This sparsity will skew the distribution of tweet activity toward being inactive, as the distribution should be to reflect realistic usage statistics.
 However, if this measure is to be used in practice a deeper analysis of the effects of binning, the resulting sparsity and their role in the activity-based community structure should be carried out.

### 2014-11-20 paper-postreview/paper.tex
massive edits including abstract and title replace and finishing action list

@@
 
-\title{Followers Are Not Enough: A Multi-faceted Approach to Community Detection in Online Social Networks}
+\title{Followers Are Not Enough: A Multifaceted Approach to Community Detection in Online Social Networks
+\\
+A Multifaceted Approach to Unveiling the Layered Communities of Online Social Networks
+\\
+ A Multifaceted Approach to Unveiling the Layers of Hidden Communities in Online Social Networks
+ \\ 
+A Multifaceted Approach for Unveiling Hidden Communities in Online Social Networks
+\\
+On the Importance of a Multifaceted Approach to Community Detection in Online Social Networks
+}
 
@@
 \begin{abstract}
+
+In online social media networks, users often have hundreds or even thousands of connections, which connect these users not only to friends, associates, and colleagues, but to news outlets, celebrities, government organizations and many others.
+In these complex social networks the concept of `community' becomes very general, and different definitions of community such as ``whom do we interact with?" and ``with whom do we share similar interests?" can lead to very different and interesting social groups.
+Taking into account the multifaceted nature of these networks, we claim that community detection in online social networks should also be multifaceted in order to capture all of the different and valuable viewpoints of `community'.
+In this paper we focus on three types of communities beyond follower-based structural communities: activity-based, topic-based, and interaction-based.
+We analyze a Twitter dataset using three different weightings of the structural network meant to highlight these three community types, and then infer the communities associated with these weightings.
+We show that interesting insights can be obtained about the multilayered community structure present in complex social networks by studying when, why and how these four different community types are similar as well as completely disjoint; structure that would be completely invisible if only using a single definition of community.
+\\\\
+
 %\begin{quote}
@@
 But online users often have hundreds or even thousands of such connections, many of which connect them with news outlets, governmental organizations, etc., in addition to their friends and associates.
-Because of the multi-faceted nature of these networks, we claim that community detection in online social networks should be question-oriented and rely on additional information beyond the simple structure of the network.
-The concept of `community' is very general, and different questions such as ``whom do we interact with?" and ``with whom do we share similar interests?" can lead to the discovery of different social groups.
-In this paper we focus on three types of communities beyond structural communities: activity-based, topic-based, and interaction-based.
+Because of the multifaceted nature of these networks, we claim that community detection in online social networks should be multifaceted, question-oriented and rely on additional information beyond the simple structure of the network.
+The concept of `community' is very general, and different questions such as ``whom do we interact with?" and ``with whom do we share similar interests?" can lead to the discovery of different and interesting social groups.
+In this paper we focus on three types of communities beyond follower-based structural communities: activity-based, topic-based, and interaction-based.
 We analyze a Twitter dataset using three different weightings of the structural network meant to highlight these three community types, and then infer the communities associated with these weightings.
-We show that the communities obtained in the three weighted cases are highly different from each other, and from the communities obtained by considering only the unweighted structural network.
-Our results confirm that asking a precise question is an unavoidable first step in community detection in online social networks, and that different questions can lead to different insights about the network under study.
+We show that interesting insights can be obtained about the true community structure of a social network by studying when and why these four different community types are disjoint and when they overlap.
+Community structure that would be missed if only doing a single layer of community detection.
+%%
+%We show that the communities obtained in the three weighted cases %are highly different from each other, and from the communities %obtained by considering only the unweighted structural network.
+%Our results confirm that asking a precise question is an unavoidable first step in community detection in online social networks, and that different questions can lead to different insights about the network under study.
+  Our results confirm that asking a series of precise question is an unavoidable first step in community detection in online social networks, and that different questions can lead to different insights about the network under study.
+
 %\end{quote}
@@
 
-Thanks to Cesar Flores, Lu\'is Seoane, Kevin Stadler, Jody Wright, and Nix Barnett for their contributions to preliminary ideas related to this paper and to Michelle Girvan, William Rand, Aaron Clauset, and Ryan James for their valuable comments and suggestions.
-Finally, we would like to acknowledge the Santa Fe Institute and its Complex Systems Summer School for providing the intellectually stimulating environment where this project began.
+Thanks to Cesar Flores, Lu\'is Seoane, Kevin Stadler, Jody Wright, and Nix Barnett for their contributions to preliminary ideas related to this paper and to Michelle Girvan, William Rand, Aaron Clauset, and Ryan James for their valuable comments and suggestions, and the
+anonymous reviewers whose comments strengthened the
+presentation. Finally, we would like to acknowledge the Santa Fe Institute and its Complex Systems Summer School for providing the intellectually stimulating environment where this project began.
 

### 2014-11-20 paper-postreview/results.tex
massive edits including abstract and title replace and finishing action list

@@
 In the previous sections we showed how the communities emerging from the different weightings of the follower-followee network differ quantitatively both at the macro and at the micro scale.
-Here we present some concrete examples of such different communities, in order to show more precisely the interest of using a multi-faceted approach to community detection.
+Here we present some concrete examples of such different communities, in order to show more precisely the interest of using a multifaceted approach to community detection.
 We explore this at two scale: firstly at the community level, and then at the individual level.
@@
 This means that he interacts and behaves alike the people talking about innovation and creativity, whereas he also talks about healthcare but he does not interact with (nor behave alike) the people talking about that.
-Secondly, user @jenajean also belongs to two different topic communities: she talks about Nasa and space but she does not interact nor behave alike people in that communities, whereas she also talks a lot about leadership, and the people she interacts with highly overlap with the people belonging to the topic-based community on leadership she belongs to.
-Lastly, @rajean, @Tekee, @Kimbirly and @mamamonroe are examples of users belonging to the topic community talking about Denver and Colorado (and to only that topic communitiy).
+Secondly, user @jenajean also belongs to two different topic communities: she talks about NASA and space but she does not interact nor behave alike people in that communities, whereas she also talks a lot about leadership, and the people she interacts with highly overlap with the people belonging to the topic-based community on leadership she belongs to.
+Lastly, @rajean, @Tekee, @Kimbirly and @mamamonroe are examples of users belonging to the topic community talking about Denver and Colorado (and to only that topic community).
 The activity-based community they belong to highly overlaps with the topic community (therefore they behave like the people that talk about Colorado), but they belong to different interaction-based communities, each of which does not overlap with the topic community a part for one or two users.

### 2014-11-23 paper-postreview/conclusions.tex
Reviewed section 3.4

@@
 Our findings may have important implications to a common problem in social network analysis: identification of influential individuals---but further work must be carried out.
-\alert{maybe move the top 10 people here}
+%\alert{maybe move the top 10 people here}
 Many network measures of influence are based on the various types of centrality (degree, betweenness, closeness, eigenvector, etc.)~\cite{newman2009networks}.
@@
 Based on our preliminary results, we conjecture that weighted generalizations of these centrality measures using transfer entropy might lead to better insights about who is actually influential in an online social network.
+It is interesting to note for example that two of the Forbes ``Top 10 Social Media Influencers", happen to be in our network, \emph{viz.}, Ann Tran and Jessica Northey, and transfer entropy also quantified these two users as having high PV-AC, i.e., the uncertainty about their followers activity on Twitter was reduced given their tweet histories.
+While we do not believe this information theoretic measure can capture social influence in its entirety,
+% members, as categorized by transfer entropy. 
+this suggests that this activity-based measure may be useful in finding influential members purely based on their temporal tweet history; even completely ignoring both tweet content and social status.
+However, a deeper analysis would need to be carried out to verify this finding.
 In addition to exploring this phenomenon further, we plan to explore a broader selection of choices for both the transfer-entropy lag and tweet history time resolution.

### 2014-11-24 paper-postreview/conclusions.tex
random edit

--- 2014-11-20 paper-postreview/conclusions.tex
@@
 Our findings may have important implications to a common problem in social network analysis: identification of influential individuals---but further work must be carried out.
-\alert{maybe move the top 10 people here}
  Many network measures of influence are based on the various types of centrality (degree, betweenness, closeness, eigenvector, etc.)~\cite{newman2009networks}.

### 2014-11-24 paper-postreview/results.tex

@@
 %\subsection{Qualitative Analysis of Community Memberships Across Types}
-\subsection{Answering the Questions}
+%\subsection{Answering the Questions}
+\subsection{Uncovering the Multifacetedness of Community Memberships}
 
@@
 
-In the previous sections we showed how the communities emerging from the different weightings of the follower-followee network differ quantitatively both at the macro and at the micro scale.
-Here we present some concrete examples of such different communities, in order to show more precisely the interest of using a multifaceted approach to community detection.
-We explore this at two scale: firstly at the community level, and then at the individual level.
+In the previous sections we showed that the communities emerging from the different weightings of the structural network quantitatively differ both at the macroscopic and at the microscopic scale.
+Here, we present some concrete examples of different community membership, in order to uncover the interest of using a multifaceted approach to community detection.
+We explore this at two scales: firstly at the community level, and then at the individual level.
 
@@
 
-As a sanity check, it is interesting to examine the intersection between this topic-based community and the overlapping activity-based communities and explore which users in the intersection of these community types had the highest PV-AC.
+As a sanity check, it is interesting to examine the intersection between this topic-based community and the overlapping activity-based communities and explore which users in the intersection of these community types have the highest PV-AC.
 Recall that this refers to a reduction in uncertainty about a follower(s) activity on Twitter given the tweet history of a followee.
@@
 Interestingly, among the highest PV-AC users in these communities---those with highest transfer entropy on average---we find @Colorado, which is the state official Twitter account, @ConnectColorado, a page created to connect Coloradans, and the CBS Denver account, a popular news agency.
-This means that these accounts had high predictive capacity in terms of their followers' activity on Twitter.
+This means that these accounts have high predictive capacity in terms of their followers' activity on Twitter.
 This is not surprising as these activity-based communities heavily overlapped with the topic-based communities that discuss Colorado (mentioned above) and these accounts provide information on this topic.
@@
 
-Lastly, it is interesting to note that two of the Forbes ``Top 10 Social Media Influencers", happen to be in our network, \emph{viz.}, Ann Tran and Jessica Northey, and transfer entropy also quantified these two users as having high PV-AC, i.e., the uncertainty about their followers activity on Twitter was reduced given their tweet histories.
-While we do not believe this information theoretic measure can capture social influence in its entirety,
-% members, as categorized by transfer entropy. 
-this suggests that this activity-based measure may be useful in finding influential members purely based on their temporal tweet history; even completely ignoring both tweet content and social status.
-However, a deeper analysis would need to be carried out to verify this finding.
-
-On an individual-based level, we also found some interesting cases of membership to different communities, which show that asking different questions leads indeed to finding different kinds of communities a user belongs to.
-For example, the user @JohnReaves belongs to two different topic communities: one talking about healthcare and the other talking about innovation and creativity.
-There is a almost $70\%$ overlap between the users in the innovation and creativity topic community and the interaction-based community and the activity-based community the user is in, whereas there is almost no overlap between these two and the healthcare community.
-This means that he interacts and behaves alike the people talking about innovation and creativity, whereas he also talks about healthcare but he does not interact with (nor behave alike) the people talking about that.
-Secondly, user @jenajean also belongs to two different topic communities: she talks about NASA and space but she does not interact nor behave alike people in that communities, whereas she also talks a lot about leadership, and the people she interacts with highly overlap with the people belonging to the topic-based community on leadership she belongs to.
-Lastly, @rajean, @Tekee, @Kimbirly and @mamamonroe are examples of users belonging to the topic community talking about Denver and Colorado (and to only that topic community).
-The activity-based community they belong to highly overlaps with the topic community (therefore they behave like the people that talk about Colorado), but they belong to different interaction-based communities, each of which does not overlap with the topic community a part for one or two users.
-Therefore they interact with other groups of people.
+At the individual-based level, we also found some interesting examples of multifaceted community membership, which show that asking different questions leads indeed to finding different kinds of communities a user belongs to.
+For example, the user @JohnReaves belongs to two different topic communities: one about healthcare and the other about innovation and creativity.
+There is a $~70\%$ overlap between the innovation and creativity topic community, the interaction-based, and the activity-based community the user is in, whereas there is almost no overlap between the latter two and the healthcare community.
+This means that the user interacts and behaves alike the people talking about innovation and creativity, whereas he also talks about healthcare but he does not interact with (nor behave alike) the people talking about that.
+Another interesting example is given by user @jenajean.
+She also belongs to two different topic communities: she talks about NASA and space but she does not interact nor behave alike people belonging to that topic community, whereas she also talks about leadership, and the people she interacts with highly overlap with the people belonging to the topic-based community on leadership she belongs to.
+Lastly, @rajean, @Tekee, @Kimbirly and @mamamonroe are examples of users belonging to the topic community talking about Denver and Colorado.
+The activity-based community they belong to highly overlaps with the topic community (therefore they behave alike the people that talk about Colorado), but they all belong to different interaction-based communities, each of which does not overlap with the topic community but for two users maximum.

### 2014-11-24 paper-markedup/revise-scripts.py
Added latexdiff-based version.
latexdiff isn’t working as cleanly as I’d like. We may have to hand
code some of the diffs, especially in the Methods section.

@@ -1,0 +1,15 @@
+import os
+
+original_path = '../paper-prereview/'
+
+edit_path = '../paper-postreview/'
+
+marked_path = '../paper-markedup/'
+
+names = ['paper.tex', 'appendices.tex', 'conclusions.tex', 'intro.tex', 'methods.tex', 'results.tex']
+
+
+for fname in names:
+	cmd = '/Users/daviddarmon/Documents/Reference/L/latex/latexdiff/latexdiff {}{} {}{} > {}{}'.format(original_path, fname, edit_path, fname, marked_path, fname)
+	
+	os.system(cmd)

### 2014-11-24 paper-postreview/results.tex
Attempting to fix latexdiff version.
Still needs work.

@@
 Said differently, users with the highest PV-AC in an activity-based community provide the highest reduction in uncertainty about that communities activity or inactivity on Twitter.
-Interestingly, among the highest PV-AC users in these communities---those with highest transfer entropy on average---we find @Colorado, which is the state official Twitter account, @ConnectColorado, a page created to connect Coloradans, and the CBS Denver account, a popular news agency.
+Interestingly, among the highest PV-AC users in these communities---those with highest transfer entropy on average---we find $@$Colorado, which is the state official Twitter account, $@$ConnectColorado, a page created to connect Coloradans, and the CBS Denver account, a popular news agency.
 This means that these accounts have high predictive capacity in terms of their followers' activity on Twitter.
@@
 At the individual-based level, we also found some interesting examples of multifaceted community membership, which show that asking different questions leads indeed to finding different kinds of communities a user belongs to.
-For example, the user @JohnReaves belongs to two different topic communities: one about healthcare and the other about innovation and creativity.
+For example, the user $@$JohnReaves belongs to two different topic communities: one about healthcare and the other about innovation and creativity.
 There is a $~70\%$ overlap between the innovation and creativity topic community, the interaction-based, and the activity-based community the user is in, whereas there is almost no overlap between the latter two and the healthcare community.
 This means that the user interacts and behaves alike the people talking about innovation and creativity, whereas he also talks about healthcare but he does not interact with (nor behave alike) the people talking about that.
-Another interesting example is given by user @jenajean.
+Another interesting example is given by user $@$jenajean.
 She also belongs to two different topic communities: she talks about NASA and space but she does not interact nor behave alike people belonging to that topic community, whereas she also talks about leadership, and the people she interacts with highly overlap with the people belonging to the topic-based community on leadership she belongs to.
-Lastly, @rajean, @Tekee, @Kimbirly and @mamamonroe are examples of users belonging to the topic community talking about Denver and Colorado.
+Lastly, $@$rajean, $@$Tekee, $@$Kimbirly and $@$mamamonroe are examples of users belonging to the topic community talking about Denver and Colorado.
 The activity-based community they belong to highly overlaps with the topic community (therefore they behave alike the people that talk about Colorado), but they all belong to different interaction-based communities, each of which does not overlap with the topic community but for two users maximum.

### 2014-11-25 paper-postreview/intro.tex
Addressing last of reviewer comments.

@@
 
-This activity-based approach was motivated by a method used by Shalizi \emph{et al.} in ~\cite{shalizi2007discovering} to detect functional communities within populations of neurons, but to the best of our knowledge, this is the first use of transfer entropy for community detection in online social networks.
+To the best of our knowledge, this is the first use of transfer entropy for community detection in online social networks.
 Various other information theoretic approaches have been used successfully to analyze online social networks, \emph{e.g.,} to gain insight into local user behavior~\cite{darmon2013understanding}, to detect communities based on \emph{undirected} information flow~\cite{darmon2013detecting}, and to perform network inference and link prediction~\cite{ver2012information}.

### 2014-11-25 paper-postreview/results.tex
Addressing last of reviewer comments.

@@
 The distribution of community sizes for lag larger than 2 is insensitive to the lag.
-Most importantly, we see that the distributions of community sizes differ across the community types, highlighting that the different networks give rise to different large-scale community structure dependent on the particular weighting of the structural network.
+Most importantly, we see that the distributions of community sizes differ across the community types, the large-scale community structure is highly dependent on the particular question posed.
 
@@
 The resulting $\text{NMI}(\mathcal{C}_{i}, \mathcal{C}_{j})$ are shown in Figure~\ref{Fig-compare_coverings}.
-We see that similarity between the coverings is dictated by the generic community type (structural, activity-based, etc.).
-That is, the transfer entropy coverings are more similar to each other than to any of the other coverings, with a similar result for the mention, retweet, and mention-retweet coverings.
+Note the block diagonal structure in Figure~\ref{Fig-compare_coverings}, which indicates that coverings are most similar within a question category.
+For example, the activity-based transfer entropy coverings are more similar to each other than to any of the other coverings.
+Similarly for the interaction-based mention, retweet, and mention-retweet coverings.
+This point may seem obvious, but the fact that the different weightings within a question category result in similar community structure indicates that each covering is capturing true, latent properties of the social network.
 Interestingly, the coverings resulting from the different weightings are all more similar to each other than to the structural covering from the unweighted network.
@@
 Values of normalized mutual information close to 1 indicate similarity in the community structure, while values close to 0 indicate dissimilarity.
-The normalized mutual information is computed with singletons and orphan nodes included.}
+The normalized mutual information is computed with singletons and orphan nodes included.
+Note the block-diagonal structure, indicating the strong relationship between question type and community membership.}
 \label{Fig-compare_coverings}

### 2014-11-25 paper-postreview/response-to-editor.txt
Added skeleton for response to reviewers.

Reviewer 1
==========

- The authors claim that the novelty of their work is based on the fact that community extraction has been done "blindly", i.e. without considering that actual type of network under analysis. It seems to the reviewer that this is simply not true, because the construction of the network is always done considering a specific representation of the problem under consideration. A link can represent an activity, an interaction, etc.

*

- In particular, as far as the activity-based approach is concerned, the definition of influence is very difficult to justify. The method itself is not particularly new. It was used in the past in [44]. In general, in my opinion, the use of transfer entropy for measuring the influence of a certain user on another user is fairly questionable. In fact, saying that a certain user influences another one considering th patterns of user activity might be rather questionable. What about different "followees" influencing the same person? What about external influences? In any case, I think that it is difficult to talk about "influence" in these cases. And then there is a fundamental question: it is not clear which information you can get using transfer entropy and its semantics.

*

- Also, the similarity based on topics is not a contribution per se in my opinion. Topic extraction techniques (also in more refined ones, as cited by the authors) have been used in several papers.

* As far as the evaluation is concerned, in Section 3.2 the authors compare their results by comparing the communities for different types of network structure. But, by doing this, the authors do not actually evaluate if their question based method is actually able to provide an "answer" considering the semantics of the question. I believe that a method based on a given semantics should be able to provide an answer to the question that is asked.

- "many of these connections do not correspond to real friendships or more generally to accounts that users interact with": This sentence is very difficult to understand. People in Twitter follow accounts that are not real friends, but news outlets, governmental organizations, etc.

*

- "structural communities": also these are structural communities based on a different type of weight.

*

- "we show that the communities obtained in the three weighted cases are highly different from each other": this is a fairly result. Different weights lead to different results.

*

- "contact filtering": this is not a common term/concept at all in my opinion. It seems that tit has been introduce by the authors.

*

- "However, with the prevalence of large rich data sets for online social networks": I think that the opposite is actually true. Sociologists usually go beyond simple structure and/or structure is used to describe dynamics.

*

- "On a more abstract level, a user might consider themselves part of a community of people discussing similar topics...": this is a standard approach to social network analysis. The membership is defined by the users themselves.

*

- "Interaction-based": why is this different from activity based? It seems to me that this is a sort of limit case of the "activity-based" considering a simplification of the problem: communication vs no communication.

*

- "We divide our approaches into four categories": I think that this is not strictly necessary since you have already mentioned this.

*

- "However, we conjecture": rightly, the authors say that this is just a conjecture. At the same time, very bold claims are based on this very simple conjecture.

*

- "For example [6],": the idea of building a network based on this is not particularly new.

*

- "However, this approach focused on data for a particular topic...": this is not a credible justification to dismiss the work. The fact that you present an approach based on structure together with this one does not represent a significant contribution per se in my opinion.

*

- The discussion of the selection of the clustering algorithm can be summarized in my opinion.

*

- "For this reason, we coarsen each time series by considering non-overlapping time intervals...": this time series might be rather sparse. A discussion of this issue might be helpful.

*

- "A positive value for the transfer...": this is just an assumption, you should say that you assume this.

*

- Formulae (2) and (3): you should use a different symbol for p in (2) and (3). In (4) the p can be very different. This formula is not correct in my opinion.

*

- In general, the 3 metrics listed in (2), (3) and (4) are not properly motivated in my opinion.

*

- Section 2.5: the extraction of the weights is pretty standard, I do not consider this as a contribution per se.

*

- The result in Figure 1 is not really significant. These are comparisons between different methods without a clear interpretation of the results.

*

- "That is, the transfer entropy coverings are more similar...": These findings are not particularly insightful in my opinion. These might be just artifacts of the definitions.

*

- Figure 2: I cannot se real insights from these plots.

*

- For meaningful community structure...:: It is not clear to me why this should be the case. You can have in theory similar communities. This is probably not the case, but you should avoid to say that you expect this behaviour.

*

- "If the community structure were arbitrary...": this is not true in general.

*

- "Similarly, for the coverings corresponding to...": it is not possible to compare these results directly, since they represent very different properties. They are not really normalized/scaled up.

*

- "This means that these accounts had high influence...": this is a strong claim. This might be simply due to the higher probability of retweet for that account, i.e., the use of the entropy transfer function might not necessary. The actual introduction of such a complex tool for describing this tool is not completely justified.

*

- "Lastly, it is interesting to note...": the same might be true for these accounts.

*

- "even activity-based influence": it depends, you can consider weights accordingly, for example based on the frequency/intensity of the interaction, etc. You can even add a weight using Granger correlation. You can put a weight if the correlation is higher than a certain given threshold for example - and only tnen apply the community detection algorithm.

*

- "erroneous results": how can you say that your resutls are corrects.

*

Reviewer 2
==========

- My only minor complaint is the following. Depending on the "type" of links considered, I expect the network to be different. Why did the authors focus only on communities, instead of considering also more basic network properties? I would add some statistics about it.

*

### 2014-11-25 paper-postreview/response-to-editor.txt
Begin drafting responses to reviewer 1.

@@
 
-*
+* We did not mean to claim that the community extraction was done blindly.
+In fact, we demonstrated exactly the opposite: by intentionally choosing a different question about the individuals in the social network, very different community structure may be extracted.
+We did wish to highlight that a question-oriented approach to community detection can be undertaken with the network at-hand, assuming the network was collected in a way that would not strongly bias any of the weighting metrics we utilized.
 
@@
 
-*
+* The method used in [44] is very different from our own.
+We originally cited this paper because it was the impetus for us considering point process-type models of user behavior in social media, but we see that this may have been misleading.
+The method in [44] assumes a weighted adjacency matrix based on the point-wise (in time) informational coherence between any two nodes in the network.
+The informational coherence is computed as the normalized mutual information between the marginal causal states associated with each node in the vertex, and thus measures whether or not the information processing between any two nodes is associated across time.
+Thus, this measure is neither directed, nor does it account for lagged effects in terms of the interaction between two nodes in network, as our method does.
 
@@
 
-* As far as the evaluation is concerned, in Section 3.2 the authors compare their results by comparing the communities for different types of network structure.
+* We do not believe that the contribution of our paper is any of the particular weightings, but rather in how the choice of a weighting can strongly impact.
+We sought to include simple, reasonable metrics motivated by the interaction-, topic-, and activity-based questions, but did not intend for these to be new or even state-of-the-art.
+
+- As far as the evaluation is concerned, in Section 3.2 the authors compare their results by comparing the communities for different types of network structure.
 But, by doing this, the authors do not actually evaluate if their question based method is actually able to provide an "answer" considering the semantics of the question.
 I believe that a method based on a given semantics should be able to provide an answer to the question that is asked.
+
+*
 

### 2014-11-25 paper-postreview/response-to-editor.txt
Added more responses to the reviewers' criticisms.

@@
 
-*
+* We have attempted to address this point more fully in section 3.4 of the revised manuscript.
+In particular, we demonstrate how the topic-based, interaction-based, and activity-based networks give rise to meaningful communities based on their respective interpretations of the meaning of 'community.' e.g.
+A topic-based community based around small businesses, an activity-based community based around individuals in Denver, CO, etc.
+Finally, we have added individual case studies to demonstrate how the community membership of a user across the different community types reveals different aspects of the user's online identity.
 
@@
 
-*
-
-- "structural communities": also these are structural communities based on a different type of weight.
-
-*
+* Thank you for this suggestion. We have revised this sentence to more accurately reflect the plurality of account-types that exist on Twitter.
 
@@
 
-*
+* The fact that different weightings should give rise to different communities is in our opinion non-trivial.
+For example, if all of the different weightings were strongly associated with each other, then we would expect to obtain the same communities, since the same structural backbone was used to to construct each weighted network.
+One might expect this to be the case with, for example, the interaction-based and activity-based weights.
+However, as both Figures 1 and 2 demonstrate, this is not the case.
 
@@
 
-*
+* We did not introduce the term/concept. It can be found in reference [5].
 
@@
 
-*
-
-- "On a more abstract level, a user might consider themselves part of a community of people discussing similar topics...": this is a standard approach to social network analysis.
-The membership is defined by the users themselves.
-
-*
+* We did not mean to claim that sociologists currently take this approach, but rather that this approach was more reasonable in the era of small-scale studies of human/human interaction (for example, the small-world experiment of Stanley Milgram, or Zachary's Karate club).
 
@@
 
-*
+* [[Josh]]
 
@@
 
-*
+* Thank you for this suggestion. We have revised the manuscript to remove this redundancy.
 
@@
 
-*
+* We agree that our original presentation of transfer entropy did not do a good enough job of stressing the difference between social and information theoretic influence.
+We have attempted to revise our presentation of transfer entropy to make it more clear exactly what we believe transfer entropy does and does not capture in the setting of our paper.
 
@@
 
-*
+* We agree.
+As stated above, we feel that our contribution with this paper is not to demonstrate new ways to construct networks from data derived from Twitter, but rather how to use many of those networks to highlight the multifaceted nature of user engagement with online social media.
 
@@
 
-*
-
-- The discussion of the selection of the clustering algorithm can be summarized in my opinion.
-
-*
+* See the previous response.
 
@@
 
-*
+* We have revised the manuscript to emphasize that this is a property that immediately follows from the definition of the transfer entropy, rather than an assumption that we have made.
+However, we admit that our interpretation of the positivity is an assumption, and we have attempted to make this interpretation more concrete in the revised manuscript.
 
@@
 
-*
+* Thank you for this suggestion.
+The p was not meant to be a variable, but rather to indicate the proportion of retweets / mentions.
+We have revised our notation to remove any confusion caused by the use of the prefix p.
 
@@
 
-*
+* [[Elisa]]
 
@@
 
-*
+* As noted in previous responses, the scope of this paper was not to present new weighting metrics, but rather to demonstrate the impact of standard weighting metrics on the communities extracted from a real-world online social network.
 
@@
 
-*
+* We believe that the differing distributions do demonstrate that the mesoscopic structure of the network looks different depending on the question-type employed to extract the communities.
+For example, using the follower network alone results in smaller communities that resolve together into larger communities after applying the weightings.
+Thus, those individuals who appear to be unassociated based on the follower network become associated after we include more information about their activity / interactions / topic profiles.
 
@@
 
-*
+* Thank you for pointing this out. We have revised the manuscript to emphasize those cases when we do / do not expect the edge weight distributions to vary depending on the conditioning.
 
@@
 
-*
+* Thank you for pointing this out. We have revised the manuscript to account for this.
 
@@
 
-*
+* We agree.
+Alternative activity-based metrics could and should certainly be applied.
+In this sentence, we meant to emphasize that the structural network alone would not capture this information, and therefore performing influence detection using this network might lead to
 
@@
 
-*
+* We have expanded on this point in the revised manuscript, and given examples of how influence detection based solely on the structural network could result in an incomplete understanding of the influence exhibited by users in an online social network.
 
@@
 
-*
+* Thank you for this suggestion.
+We decided to focus the paper on communities, and felt that going into more detail about the differences in other network properties went beyond the scope of our analysis.
+However, as we indicated in the Future Work section, we believe that such investigations could yield new insights into the multifaceted nature of online social networks.

### 2014-11-26 paper-postreview/intro.tex
Took a pass through the paper.
I made minor changes, mostly stylistic.

@@
 Because of the importance of structural networks in online social media, a large amount of work in this area has focused on using structural networks for community detection.
-In this traditional view, `community' is defined as a collection of nodes (users) within the network which are more highly connected to each other than to nodes (users) outside of the community
+In this traditional view, a community is defined as a collection of nodes (users) within the network which are more highly connected to each other than to nodes (users) outside of the community
 %Here, by `community' we mean the standard definition from the literature on social networks: a collection of nodes (users) within the network which are more highly connected to each other than to nodes (users) outside of the community
@@
 
-\item Ask \emph{several} questions about the communities that may be present in the network, each of which is aimed at revealing a new facet of the community present in the network---{\it e.g.,} which users are tightly connected structurally?
+\item Ask \emph{several} questions about the communities that may be present in the network, each of which is aimed at revealing a new facet of the community structure present in the network---{\it e.g.,} which users are tightly connected structurally?
 which groups of users have similar topical interests?
@@
 \item Derive a weighting scheme aimed at answering each of the questions asked in the first step and then perform community detection on each weighted network.
-\item Compare the disjoint \emph{and} overlapping communities that arise from this series of experiments on a micro and macro scale to unveil all the interesting facets of community present in the social network.
+\item Compare the disjoint \emph{and} overlapping communities that arise from this series of experiments on a micro and macro scale to unveil all the interesting facets of community structure present in the social network.
 \end{enumerate}
@@
 The simplest definition of community, as we have seen, might stem from the network of explicit connections between users on a service (friends, followers, etc.).
-On small time scales, these connections are more or less static, and we might instead determine communities, as is standard in the literature\alert{david or elisa can you add some citations please}\cite{}, based on who is talking to whom or which users talk about similar topics, providing a more dynamic picture of community.
-More abstractly, we could even define communities as groups of people who exhibit similar activity profiles.
-We can characterize these types of communities based on the types of questions we might ask about them:
+On small time scales, these connections are more or less static.
+To form a more dynamic picture of community structure, we might instead determine communities based on who is talking to whom or which users talk about similar topics.
+More abstractly, we could even define communities as groups of people who exhibit similar activity profiles. We can characterize these types of communities based on the questions that motivate them:
 \begin{itemize}
@@
 For this user, the answers to each question therefore correspond to more or less distinct communities.
-By contrast, a teenage user may only connect and interact with their friends, will most likely exhibit similar activity patterns dictated by the academic and extracurricular schedule of a student.
+By contrast, a teenage user may only connect and interact with their friends, will most likely exhibit similar activity patterns dictated by the academic and extracurricular schedule of a student, and will discuss topics typical of their demographic.
 For this user, the answers to each question map to the same community of users.
@@
 We now consider in more detail how each of these types of questions motivates a question-specific community.
-Later in Section~\ref{sec:conc} we will show how asking \emph{all} of these questions---instead of focusing on only one---gives a much deeper multifaceted view of the overlapping \emph{and} disjoint communities that users belong to.
+Later in Section~\ref{sec:conc} we will show how asking \emph{all} of these questions---instead of focusing on only one---gives a much deeper view of the overlapping \emph{and} disjoint communities that users belong to.
 
@@
 However, the measure we use is slightly more subtle that this.
-In particular, these communities can be thought of as groups of users who possess so-called ``predictive capacity" with one another, i.e., given a user $u$ and follower $f$ who are members of a community detected with this weighting, there exists a reduction in uncertainty about the activity profile of follower $f$ (tweeting or remaining silent), given the tweet history of user $u$.
+In particular, these communities can be thought of as groups of users who possess so-called ``predictive capacity" with one another, \emph{i.e.}, given a user $u$ and follower $f$ who are members of a community detected with this weighting, there exists a reduction in uncertainty about the activity profile of follower $f$ (tweeting or remaining silent), given the tweet history of user $u$.
 
@@
 As an aside, while we are skeptical that this measure can capture social influence, later in this paper we show that this information theoretic measure agrees with other concepts of influence such as the Forbes list of ``Top 10 Social Media Influencers" and corroborates with the so-called strength of weak ties~\cite{granovetter1973strength}.
-Even so, we do not explicitly treat---and we do not believe it should be treated---as a quantification of social influence.
+Even so, we do not explicitly treat transfer entropy---and we do not believe it should be treated---as a quantification of social influence.
 Instead this measure should be treated merely as a way to suggest users with casually related (in a Granger sense) tweet histories, i.e., users with similar activity profiles (PV-AC).

### 2014-11-26 paper-postreview/methods.tex
Took a pass through the paper.
I made minor changes, mostly stylistic.

--- 2014-11-20 paper-postreview/methods.tex
@@
 \section{Methodology}
-
 In the following sections, we introduce the problem of community detection, and present the data set used for our analyses.
@@
 In particular, we introduce an information theoretic statistic for activity-based communities, a retweet-mention statistic for interaction-based communities, and a hashtag similarity metric for defining topic-based communities.
+It should be noted that our goal is to choose representative weightings for each community type so that we may compare community structure across types, and not to introduce novel weighting schemes \emph{per se}.
 
@@
 Second, we are interested in not just the structure of links but also in their function, and to capture this we use edge weightings which must be incorporated into the community detection process.
-Finally, since people can belong to multiple and possibly overlapping social (e.g., college friends, co-workers, family, etc.) and topical (e.g., a user can be interested in both cycling and politics and use the network to discuss the two topics with the two different communities) communities, we are interested in finding \textit{overlapping} communities, rather than partitions of the weighted directed network.
+Finally, since people can belong to multiple and possibly overlapping social (e.g., college friends, co-workers, family, etc.) and topical (e.g., a user can be interested in both cycling and politics and use the network to discuss the two topics with the two different groups of users) communities, we are interested in finding \textit{overlapping} communities, rather than partitions of the weighted directed network.
 %For example, users can belong to multiple social groups such as college friends, %co-workers, family, etc.
@@
 The null model used is basically the same as the one adopted by Newman and Girvan in \cite{newman2004finding} to define modularity, {\it i.e.} it is a model that generates random graphs with a given degree distribution.
-The authors tested their algorithm on different benchmarks (LFR and Girvan-Newman) and real networks (such as the US air transportation and the word association network), and compared its performance against the best algorithms
+The authors tested their algorithm on different benchmarks (LFR and Girvan-Newman) and real networks (such as the US air transportation network and a word association network), and compared its performance against the best algorithms
 currently available (i.e the ones mentioned in the introduction), and found excellent results.
 Moreover, they showed that OSLOM is also able to recognize the absence, and not simply the presence, of community structure, by testing it on random graphs.
-This feature of the algorithm plays an important role in the analysis of real data networks, since it is not always the case that a community structure is indeed present and it is therefore useful to be able to detect its absence too.
+This feature of the algorithm plays an important role in the analysis of real world networks, since it is not always the case that community structure is indeed present and it is therefore useful to be able to detect its absence too.
 Therefore, given its versatility and performance with benchmark networks, in this paper we used OSLOM to detect \emph{overlapping} communities present in our \emph{weighted} and \emph{directed} networks.
@@
 It should be noted that, as (most) users are not constantly tweeting, these time series are quite sparse.
-This sparsity will skew the distribution of tweet activity toward being inactive, as the distribution should be to reflect realistic interaction patterns.
-However, if this measure is to be used in practice a deeper analysis of the effects of binning, the resulting sparsity and their role in the activity-based community structure should be carried out.
+%This sparsity will skew the distribution of tweet activity toward being inactive, as the distribution should be to reflect realistic usage statistics.
+However, if this measure is to be used in practice a deeper analysis of the effects of binning, the resulting sparsity, and their role in the activity-based community structure should be carried out.
 

### 2014-11-26 paper-postreview/paper.tex
Took a pass through the paper.
I made minor changes, mostly stylistic.

--- 2014-08-18 paper-for_arxiv/paper.tex
@@
 
-\title{Followers Are Not Enough: A Question-Oriented Approach to Community Detection in Online Social Networks}
+\title{Followers Are Not Enough: A Multifaceted Approach to Community Detection in Online Social Networks
+}
 
@@
 \begin{abstract}
+
+In online social media networks, individuals often have hundreds or even thousands of connections, which connect these users not only to friends, associates, and colleagues, but also to news outlets, celebrities, and government organizations.
+In these complex social networks, a `community' as studied in the social network literature, can have very different meaning depending on the property of the network under study.
+% and different definitions of community such as ``whom do we interact with?" and ``with whom do we share similar interests?" can lead to very different and interesting social groups. 
+Taking into account the multifaceted nature of these networks, we claim that community detection in online social networks should also be multifaceted in order to capture all of the different and valuable viewpoints of `community.' In this paper we focus on three types of communities beyond follower-based structural communities: activity-based, topic-based, and interaction-based.
+We analyze a Twitter dataset using three different weightings of the structural network meant to highlight these three community types, and then infer the communities associated with these weightings.
+We show that interesting insights can be obtained about the complex community structure present in  social networks by studying when and how these four community types give rise to similar as well as completely distinct community structure.
+\\\\
+
 %\begin{quote}
@@
 
-Community detection in online social networks is typically based on the analysis of the explicit connections between users, such as ``friends" on Facebook and ``followers" on Twitter.
-But online users often have hundreds or even thousands of such connections, and many of these connections do not correspond to real friendships or more generally to accounts that users interact with.
-We claim that community detection in online social networks should be question-oriented and rely on additional information beyond the simple structure of the network.
-The concept of `community' is very general, and different questions such as ``whom do we interact with?" and ``with whom do we share similar interests?" can lead to the discovery of different social groups.
-In this paper we focus on three types of communities beyond structural communities: activity-based, topic-based, and interaction-based.
+%Community detection in online social networks is typically based on the analysis of the explicit connections between users, such as ``friends" on Facebook and ``followers" on Twitter.
+But online users often have hundreds or even thousands of such connections, many of which connect them with news outlets, governmental organizations, etc., in addition to their friends and associates.
+Because of the multifaceted nature of these networks, we claim that community detection in online social networks should be multifaceted, question-oriented and rely on additional information beyond the simple structure of the network.
+The concept of `community' is very general, and different questions such as ``whom do we interact with?" and ``with whom do we share similar interests?" can lead to the discovery of different and interesting social groups.
+In this paper we focus on three types of communities beyond follower-based structural communities: activity-based, topic-based, and interaction-based.
 We analyze a Twitter dataset using three different weightings of the structural network meant to highlight these three community types, and then infer the communities associated with these weightings.
-We show that the communities obtained in the three weighted cases are highly different from each other, and from the communities obtained by considering only the unweighted structural network.
-Our results confirm that asking a precise question is an unavoidable first step in community detection in online social networks, and that different questions can lead to different insights about the network under study.
+We show that interesting insights can be obtained about the true community structure of a social network by studying when and why these four different community types are disjoint and when they overlap.
+Community structure that would be missed if only doing a single layer of community detection.
+%%
+%We show that the communities obtained in the three weighted cases %are highly different from each other, and from the communities %obtained by considering only the unweighted structural network.
+%Our results confirm that asking a precise question is an unavoidable first step in community detection in online social networks, and that different questions can lead to different insights about the network under study.
+ %Our results confirm that asking a series of precise question is an unavoidable first step in community detection in online social networks, and that different questions can lead to different insights about the network under study.
+
 %\end{quote}

### 2014-11-26 paper-postreview/results.tex
Took a pass through the paper.
I made minor changes, mostly stylistic.

@@
 
-As a sanity check, it is interesting to examine the intersection between this topic-based community and the overlapping activity-based communities and explore which users in the intersection of these community types have the highest PV-AC.
+It is interesting to examine the intersection between this topic-based community and the overlapping activity-based communities and explore which users in the intersection of these community types have the highest PV-AC.
 Recall that this refers to a reduction in uncertainty about a follower(s) activity on Twitter given the tweet history of a followee.
@@
 
-At the individual-based level, we also found some interesting examples of multifaceted community membership, which show that asking different questions leads indeed to finding different kinds of communities a user belongs to.
+At the individual-based level, we also found some interesting examples of multifaceted community membership, which show that asking different questions leads to finding different kinds of communities a user belongs to.
 For example, the user $@$JohnReaves belongs to two different topic communities: one about healthcare and the other about innovation and creativity.
 There is a $~70\%$ overlap between the innovation and creativity topic community, the interaction-based, and the activity-based community the user is in, whereas there is almost no overlap between the latter two and the healthcare community.
-This means that the user interacts and behaves alike the people talking about innovation and creativity, whereas he also talks about healthcare but he does not interact with (nor behave alike) the people talking about that.
+This means that the user interacts with and behaves like the people talking about innovation and creativity, whereas he also talks about healthcare but he does not interact with (nor behave like) the people talking about that.
 Another interesting example is given by user $@$jenajean.
-She also belongs to two different topic communities: she talks about NASA and space but she does not interact nor behave alike people belonging to that topic community, whereas she also talks about leadership, and the people she interacts with highly overlap with the people belonging to the topic-based community on leadership she belongs to.
+She also belongs to two different topic communities: she talks about NASA and space but she does not interact nor behave like people belonging to that topic community, whereas she also talks about leadership, and the people she interacts with highly overlap with the people belonging to the topic-based community on leadership she belongs to.
 Lastly, $@$rajean, $@$Tekee, $@$Kimbirly and $@$mamamonroe are examples of users belonging to the topic community talking about Denver and Colorado.
-The activity-based community they belong to highly overlaps with the topic community (therefore they behave alike the people that talk about Colorado), but they all belong to different interaction-based communities, each of which does not overlap with the topic community but for two users maximum.
+The activity-based community they belong to highly overlaps with the topic community (therefore they behave like the people that talk about Colorado), but they all belong to different interaction-based communities, each of which does not overlap with the topic community but for two users maximum.

### 2014-11-26 paper-postreview/response-to-editor.txt
Took a pass through the paper.

@@
 Thus, this measure is neither directed, nor does it account for lagged effects in terms of the interaction between two nodes in network, as our method does.
+(Elisa: I think this answers only the very first part of the comment. Josh, could you please elaborate also on the rest (I leave this to you since it's the transfer entropy stuff))
 
@@
 We sought to include simple, reasonable metrics motivated by the interaction-, topic-, and activity-based questions, but did not intend for these to be new or even state-of-the-art.
+(Elisa: I would eliminate "or even state-of-the-art".
+Also, I don't understand the first sentence.)
 
@@
 
-* [[Elisa]]
+* Thank you for this comment. We expanded section 2.4 in the revised manuscript in order to motivate more in details these metrics.
 
@@
 * As noted in previous responses, the scope of this paper was not to present new weighting metrics, but rather to demonstrate the impact of standard weighting metrics on the communities extracted from a real-world online social network.
+(Elisa: I would say "to compare" rather than "to demontrate")
 
@@
 However, as we indicated in the Future Work section, we believe that such investigations could yield new insights into the multifaceted nature of online social networks.
+(Elisa: where exactly did we write that (I personally can't really find what sentence you refer to)? If we added in the revised version we should say it explicitely)

### 2014-11-26 paper-postreview/intro.tex
Took a pass through the paper.

@@
 A large body of work exists on methods for automatic detection of communities within networks, {\it e.g.,} the stochastic blockmodel~\cite{Holland1983} (and its recent generalization to weighted networks~\cite{Aicher26062014}), the Girvan-Newman algorithm~\cite{newman2004finding}, clique percolation~\cite{PalEtAl05}, Infomap~\cite{Rosvall08mapsof}, Louvain~\cite{blondel2008fast}, and the recently introduced OSLOM~\cite{LancichinettiPlos}.
-All these methods begin with a given network, and then attempt to uncover structure present in the network, \emph{i.e.,} they are agnostic to how the network was constructed.
+All these methods begin with a given network, and then attempt to uncover structure present in the network\sout{, \emph{i.e.,} they are agnostic to how the network was constructed}.
+\textit{Elisa: I would take out this sentence, because they do know how it was constructed, they just decided to ignore additional information.}
 As opposed to this agnostic analysis, we propose---and illustrate the importance of---a \emph{multifaceted question-focused} approach.
@@
 \item Derive a weighting scheme aimed at answering each of the questions asked in the first step and then perform community detection on each weighted network.
-\item Compare the disjoint \emph{and} overlapping communities that arise from this series of experiments on a micro and macro scale to unveil all the interesting facets of community structure present in the social network.
+\item Compare the \sout{disjoint \emph{and} overlapping} different communities that arise from this series of experiments on a micro and macro scale to unveil all the interesting facets of community structure present in the social network.
+\textit{Elisa: The problem of talking about disjoint and overlapping communities is that it might confuse the reader since it's the same terminology we use when we claim that we want to detect overlapping communities.}
 \end{enumerate}
@@
 This is not meant to be an exhaustive list, but rather a list of some of the more common types of communities observed and studied in social networks.
-Instead of looking at each of these questions in isolation---which is the standard approach---we propose looking at when, why, and how communities motivated by these different questions overlap and are disjoint, and whether different approaches to asking the question, ``What community are you in?'' leads to different insights about a social network.
+Instead of looking at each of these questions in isolation---which is the standard approach---we propose looking at when and how communities motivated by these different questions overlap and are disjoint, and whether different approaches to asking the question ``What community are you in?'' leads to different insights about a social network.
 For example, a user on Twitter might connect mostly with computational social scientists, utilize the service nearly every time a particular user or group of users is active, talk mostly about machine learning, and interact solely with close friends (who may or may not be computational social scientists).
@@
 For this user, the answers to each question map to the same community of users.
-Thus, each question acts to highlight a particular `profile' of a user, and these profiles can help identify the ways in which a user interacts with and like other users in their online social network.
+\textit{Thus, each question acts to highlight a particular `profile' of a user, and these profiles can help identify the ways in which a user interacts with and like other users in their online social network.
+(Elisa: This sentence raises a very interesting point but I think it gives false hopes about what we actually do in the paper, since our goal is not to define user categories)}
 We now consider in more detail how each of these types of questions motivates a question-specific community.
-Later in Section~\ref{sec:conc} we will show how asking \emph{all} of these questions---instead of focusing on only one---gives a much deeper view of the overlapping \emph{and} disjoint communities that users belong to.
+Later in Section~\ref{sec:conc} we will show how asking \emph{all} of these questions---instead of focusing on only one---gives a much deeper view of the \sout{overlapping \emph{and} disjoint} different communities that users belong to.
 
-Na\"ively the activity-based approach is motivated by the question of ``Which users in a network have similar activity profiles?"
+Na\"ively the activity-based approach is motivated by the question of ``Which users in a network have similar activity profiles?".
 %--- \emph{i.e.,} which user(s) cause groups of users to become active on the network.  %, \emph{i.e.}, which user(s) cause a user(s) to interact with the network. 
@@
 
-According to~\cite{ver2012information} a positive transfer entropy between a user $u$ and a follower $f$ indicates that $u$ ``influences" $f$, or that $u$ and $f$ share a common influencer.
+\textcolor{blue}{According to~\cite{ver2012information} a positive transfer entropy between a user $u$ and a follower $f$ indicates that $u$ ``influences" $f$, or that $u$ and $f$ share a common influencer.
 We would like to point out however that we are skeptical whether this measure truly captures social influence in its entirety.
@@
 This provides an information theoretic framework in which we can capture communities with predictive capacity between users or users with similar activity profiles.
-We call this relation ``PV-AC".
+We call this relation ``PV-AC" \textit{(Elisa: Which stands for?)}.
 As an aside, while we are skeptical that this measure can capture social influence, later in this paper we show that this information theoretic measure agrees with other concepts of influence such as the Forbes list of ``Top 10 Social Media Influencers" and corroborates with the so-called strength of weak ties~\cite{granovetter1973strength}.
@@
 Instead this measure should be treated merely as a way to suggest users with casually related (in a Granger sense) tweet histories, i.e., users with similar activity profiles (PV-AC).
+\textit{(Elisa: I would move these two paragraphs (and maybe the next too?) to section 2.3.
+I think it's a bit too much here in the introduction.)}}
 
@@
 Studying how the communities derived from follower-followee, activity-based, topic-based, and interaction-based networks are disjoint as well as overlapping allow for a more complete picture of the \emph{implicit} networks present in online social media, as opposed to the \emph{explicit} social network indicated by follower links alone.
-In this paper, we explore the relation between these various possible networks and their corresponding communities.
+In this paper, we explore the relation between these various possible networks \sout{and}through their corresponding communities.
 We begin by describing the methodologies used to generate the various types of networks, and infer their community structure.
 We then explore how the communities of users differ depending on the type of network used.
-Finally, we explore how communication patterns differ across and within the different community types.
-We conclude by illustrating that this multifaceted question-oriented approach to community detection provides interesting insight into the intricate multifaceted structure of several different users' communities; information that would not be available if only a single form of community detection was performed.
+\emph{Finally, we explore how communication patterns differ across and within the different community types.
+(Elisa: We do that?)} We conclude by illustrating that this multifaceted question-oriented approach to community detection provides interesting insights into the intricate multifaceted structure of several different users' communities, information that would not be available if only a single form of community detection was performed.
 %\section{Related Work}

### 2014-11-26 paper-postreview/methods.tex
Took a pass through the paper.

@@
 Second, we are interested in not just the structure of links but also in their function, and to capture this we use edge weightings which must be incorporated into the community detection process.
-Finally, since people can belong to multiple and possibly overlapping social (e.g., college friends, co-workers, family, etc.) and topical (e.g., a user can be interested in both cycling and politics and use the network to discuss the two topics with the two different groups of users) communities, we are interested in finding \textit{overlapping} communities, rather than partitions of the weighted directed network.
+Finally, since people can belong to multiple and possibly overlapping social (e.g., college friends, co-workers, family, etc.) and topical (e.g., a user can be interested in both cycling and politics and use the network to discuss the two topics with two different groups of users) communities, we are interested in finding \textit{overlapping} communities, rather than partitions of the weighted directed network.
 %For example, users can belong to multiple social groups such as college friends, %co-workers, family, etc.
@@
 A recent method proposed in~\cite{LancichinettiPlos}, OSLOM (Order Statistics Local Optimization Method), is one of the first methods  able to deal with all of these features simultaneously.
-This method of Lancichinetti et al.
-relies on a fitness function that measures the statistical significance of clusters with respect to random fluctuations, and attempts to optimize this fitness function across all clusters.
+This method of Lancichinetti \emph{et al.} relies on a fitness function that measures the statistical significance of clusters with respect to random fluctuations, and attempts to optimize this fitness function across all clusters.
 Following~\cite{LancichinettiPlos}, the significance measure is defined as the probability of finding the cluster in a network without community structure.
@@
 
-Operationally, we expect users to interact with Twitter on a human time scale, and thus the natural one-second time resolution is too fine; since most humans do not write tweets on the time scale of seconds.
+Operationally, we expect users to interact with Twitter on a human time scale, and thus the natural one-second time resolution is too fine, since most humans do not write tweets on the time scale of seconds.
 For this reason, we coarsen each time series by considering non-overlapping time intervals ten minutes in length.
-For each time interval, we record a 1 if the user has tweeted during that time interval, and a 0 if they have not.
+For each time interval, we record a 1 if the user has tweeted during that time interval, and a 0 if he or she has not.
 Thus, the new coarsened time series now captures whether or not the user has been active on Twitter over any given ten minute time interval in our data set.
@@
 %This sparsity will skew the distribution of tweet activity toward being inactive, as the distribution should be to reflect realistic usage statistics.
-However, if this measure is to be used in practice a deeper analysis of the effects of binning, the resulting sparsity, and their role in the activity-based community structure should be carried out.
+\textit{However, if this measure is to be used in practice (Elisa: What does this mean?
+We are indeed using it)} a deeper analysis of the effects of binning, the resulting sparsity, and their role in the activity-based community structure should be carried out.
 
@@
 Secondly, we consider the number of mentions of $f$ made by user $u$.
-To account for the fact that some users/accounts are very popular and are often mentioned by so many other users that there is not real flow of information from the latter to the former, we normalize this measure by dividing over the total number of mentions received by $f$.
+To account for the fact that some users/accounts are very popular and are often mentioned by so many other users that the flow of information from the latter to the former is flushed out, we normalize this measure by dividing over the total number of mentions received by $f$.
 \begin{equation}

### 2014-11-29 paper-postreview/intro.tex
doing all my final edits

--- 2014-11-26 paper-postreview/intro.tex
@@
 Because of the importance of structural networks in online social media, a large amount of work in this area has focused on using structural networks for community detection.
-In this traditional view, a community is defined as a collection of nodes (users) within the network which are more highly connected to each other than to nodes (users) outside of the community
-%Here, by `community' we mean the standard definition from the literature on social networks: a collection of nodes (users) within the network which are more highly connected to each other than to nodes (users) outside of the community
-~\cite{girvan2002a, newman2004finding}.
+In this traditional view, a community is defined as a collection of nodes (users) within the network which are more highly connected to each other than to nodes (users) outside of the community~\cite{girvan2002a, newman2004finding}.
 For instance, in~\cite{java2009we}, the authors use a follower network to determine communities within Twitter, and note that conversations tend to occur within these communities.
 The approach of focusing on the structure of networks makes sense for `real-world' sociological experiments, where obtaining additional information about user interactions may be expensive and time-consuming.
-However, with the prevalence of large, rich data sets for online social networks, additional information beyond the structure alone may be incorporated, and these augmented networks more realistically reflect how users interact with each other on social media services~\cite{nguyen2011adaptive},~\cite{grabowicz2012social}.
+However, with the prevalence of large, rich data sets for online social networks, additional information beyond the structure alone may be incorporated, and these augmented networks more realistically reflect how users interact with each other on social media services~\cite{nguyen2011adaptive,grabowicz2012social}.
 
@@
 \item Derive a weighting scheme aimed at answering each of the questions asked in the first step and then perform community detection on each weighted network.
-\item Compare the disjoint \emph{and} overlapping communities that arise from this series of experiments on a micro and macro scale to unveil all the interesting facets of community structure present in the social network.
+\item Compare the (possibly) different communities that arise from this series of experiments on a micro and macro scale to unveil all the interesting facets of community structure present in the social network.
 \end{enumerate}
@@
 By contrast, a teenage user may only connect and interact with their friends, will most likely exhibit similar activity patterns dictated by the academic and extracurricular schedule of a student, and will discuss topics typical of their demographic.
-For this user, the answers to each question map to the same community of users.
-Thus, each question acts to highlight a particular `profile' of a user, and these profiles can help identify the ways in which a user interacts with and like other users in their online social network.
-We now consider in more detail how each of these types of questions motivates a question-specific community.
-Later in Section~\ref{sec:conc} we will show how asking \emph{all} of these questions---instead of focusing on only one---gives a much deeper view of the overlapping \emph{and} disjoint communities that users belong to.
+For this user, the answers to each question map to the same community of users, even though different definitions of community are being used.
+This highlights an important subtlety of this work: defining communities in different ways does not imply that the collection of users in each community \emph{must} be different.
+Said differently, it is not obvious---or always the case---that changing the definition of community will always change the communities that are detected.
+Studying when this change does and does not occur---as we will show---provides interesting insights into the complex community structure present in these networks.
+%Thus, each question acts to highlight a particular subset of users a particular user is connected with in an online social network, and this can help identify the possibly different communities the user belongs to.
+%Thus, each question acts to highlight a particular `profile' of a user, and these profiles or facets could help define the relationships of a user on an online social network more completely.
 
-Na\"ively the activity-based approach is motivated by the question of ``Which users in a network have similar activity profiles?"
+We now consider in more detail how each of these types of questions describes a unique facet of `community'.
+Later in Section~\ref{sec:conc} we will show how asking \emph{all} of these questions---instead of focusing on only one---gives a much deeper view of the (possibly) different communities that users belong to.
+
+Na\"ively the activity-based approach is motivated by the question of ``Which users in a network have similar activity profiles?".
 %--- \emph{i.e.,} which user(s) cause groups of users to become active on the network.  %, \emph{i.e.}, which user(s) cause a user(s) to interact with the network. 
@@
 However, the measure we use is slightly more subtle that this.
-In particular, these communities can be thought of as groups of users who possess so-called ``predictive capacity" with one another, \emph{i.e.}, given a user $u$ and follower $f$ who are members of a community detected with this weighting, there exists a reduction in uncertainty about the activity profile of follower $f$ (tweeting or remaining silent), given the tweet history of user $u$.
-
+In particular, these communities can be thought of as groups of users who possess so-called ``activity-based predictive capacity" with one another, \emph{i.e.}, given a user $u$ and follower $f$, who are members of a community detected with this weighting, there exists a reduction in uncertainty about the activity profile of follower $f$ (tweeting or remaining silent), given the tweet history of user $u$, ignoring the information present in the tweet history of follower $f$.
 To accomplish this, we consider each user on Twitter as an information processing unit, but completely ignore the \emph{content} of their tweets.
-We then weight the directed edges (the reported follower-followee relationships) between users with the so-called \emph{transfer entropy} introduced in~\cite{schreiber2000measuring}.
-Transfer entropy is an information theoretic measure of \emph{directed} information flow.
-Since transfer entropy is a nonlinear generalization of Granger causality \cite{granger1963economic}, we assume---as is standard---a positive transfer entropy from the tweet history of a user $u$ to a follower $f$'s tweet history implies that this relationship is causal in the Granger sense.
-Thus, communities detected in this way have members whose tweet histories are causally related in a Granger sense.
-As a result, transfer entropy is often thought of as a measure of ``influence" in an information theoretic sense.
-
-According to~\cite{ver2012information} a positive transfer entropy between a user $u$ and a follower $f$ indicates that $u$ ``influences" $f$, or that $u$ and $f$ share a common influencer.
-We would like to point out however that we are skeptical whether this measure truly captures social influence in its entirety.
-We instead treat this weighting as a way to explicitly quantify a reduction in uncertainty of whether a follower $f$ will be active or not given the tweet history of a user $u$.
-This provides an information theoretic framework in which we can capture communities with predictive capacity between users or users with similar activity profiles.
-We call this relation ``PV-AC".
-As an aside, while we are skeptical that this measure can capture social influence, later in this paper we show that this information theoretic measure agrees with other concepts of influence such as the Forbes list of ``Top 10 Social Media Influencers" and corroborates with the so-called strength of weak ties~\cite{granovetter1973strength}.
-Even so, we do not explicitly treat transfer entropy---and we do not believe it should be treated---as a quantification of social influence.
-Instead this measure should be treated merely as a way to suggest users with casually related (in a Granger sense) tweet histories, i.e., users with similar activity profiles (PV-AC).
-
-To the best of our knowledge, this is the first use of transfer entropy for community detection in online social networks.
-Various other information theoretic approaches have been used successfully to analyze online social networks, \emph{e.g.,} to gain insight into local user behavior~\cite{darmon2013understanding}, to detect communities based on \emph{undirected} information flow~\cite{darmon2013detecting}, and to perform network inference and link prediction~\cite{ver2012information}.
+We then weight the directed edges (the reported follower-followee relationships) between users with the so-called \emph{transfer entropy}~\cite{schreiber2000measuring}, calculated between the tweet history of follower $f$ and user $u$.
+This is discussed in more detail in Section~\ref{sec:method-activity}.
 
@@
 The LDA model can then be used to infer distributions over latent topics, and the similarity of two users with respect to topics may be defined in terms of the distance between their associated topic distributions.
-Because our focus is not on topic identification, we apply a simpler approach using hashtags as a proxy for topics similar to the approaches presented in~\cite{becker2011beyond,tsur2012s}.
+Because our focus is not on topic identification, we apply a simpler approach using hashtags as a proxy for topics, similar to the approaches presented in~\cite{becker2011beyond,tsur2012s}.
 We can then define the similarity of two users in terms of their hashtags, and use this similarity to build a topic-based network.
+This method is described in detail in Section~\ref{sec:method-topic}.
 
@@
 Previous research on communities in social networks focused almost exclusively on different network types in isolation.
-A notable exception to the analysis of isolated types of communities is~\cite{lim2012tweets}, that considered both structure-based and interaction-based communities on Twitter.
+A notable exception to this is~\cite{lim2012tweets}, that considered both structure-based and interaction-based communities on Twitter.
 However, this study focused on data collected based on particular topics (country music, tennis, and basketball), and not on a generic subpopulation of Twitter users.
@@
 The tensor can then be decomposed into factors in a generalization of the singular value decomposition of a matrix, and these factors can be used to determine `salient' users.
-However, this approach focused on data for a particular topic (the Occupy Movement) and did not collect users based on a structural network.
+However, unlike our work, this approach focused on data for a particular topic (the Occupy Movement) and did not collect users based on a structural network.
 
 Studying how the communities derived from follower-followee, activity-based, topic-based, and interaction-based networks are disjoint as well as overlapping allow for a more complete picture of the \emph{implicit} networks present in online social media, as opposed to the \emph{explicit} social network indicated by follower links alone.
-In this paper, we explore the relation between these various possible networks and their corresponding communities.
+In this paper, we explore the relation between these various possible networks through their corresponding communities.
 We begin by describing the methodologies used to generate the various types of networks, and infer their community structure.
 We then explore how the communities of users differ depending on the type of network used.
-Finally, we explore how communication patterns differ across and within the different community types.
-We conclude by illustrating that this multifaceted question-oriented approach to community detection provides interesting insight into the intricate multifaceted structure of several different users' communities; information that would not be available if only a single form of community detection was performed.
+\sout{\emph{Finally, we explore how communication patterns differ across and within the different community types.
+(Elisa: We do that?)}} We conclude by illustrating that this multifaceted question-oriented approach to community detection provides interesting insights into the intricate multifaceted structure of several different users' communities, information that would not be available if only a single form of community detection was performed.
 %\section{Related Work}

### 2014-11-29 paper-postreview/methods.tex
doing all my final edits

@@
 In particular, we introduce an information theoretic statistic for activity-based communities, a retweet-mention statistic for interaction-based communities, and a hashtag similarity metric for defining topic-based communities.
-It should be noted that our goal is to choose representative weightings for each community type so that we may compare community structure across types, and not to introduce novel weighting schemes \emph{per se}.
+It should be noted that our goal is to choose representative weightings for each community type so that we may compare community structure across types, and not to---aside from the activity-based weighting---introduce novel weighting schemes \emph{per se}.
 
@@
 Following~\cite{LancichinettiPlos}, the significance measure is defined as the probability of finding the cluster in a network without community structure.
-The null model used is basically the same as the one adopted by Newman and Girvan in \cite{newman2004finding} to define modularity, {\it i.e.} it is a model that generates random graphs with a given degree distribution.
+The null model used is highly similar to the one adopted by Newman and Girvan in \cite{newman2004finding} to define modularity, {\it i.e.,} it is a model that generates random graphs with a given degree distribution.
 The authors tested their algorithm on different benchmarks (LFR and Girvan-Newman) and real networks (such as the US air transportation network and a word association network), and compared its performance against the best algorithms
-currently available (i.e the ones mentioned in the introduction), and found excellent results.
+currently available ({\it i.e.,} the ones mentioned in the introduction), and found excellent results.
 Moreover, they showed that OSLOM is also able to recognize the absence, and not simply the presence, of community structure, by testing it on random graphs.
@@
 The users are embedded in a network collected by performing a breadth-first expansion from a random seed user.
-In particular, once the seed user was chosen, the network was expanded to include his/her followers, but only included users considered to be `active' (i.e., users who tweeted at least once per day over the past one hundred days).
+In particular, once the seed user was chosen, the network was expanded to include his/her followers, but only included users considered to be `active' ({\it i.e.,} users who tweeted at least once per day over the past one hundred days).
 Network collection continued in this fashion by considering the active followers of the active followers of the seed, and so on until 15,000 users were added to the network.
@@
 
-Since our goal is to explore the functional communities of this network, we filter the network down to the subset of users which actively interact with each other (e.g., via retweets and mentions).
+Since our goal is to explore the functional communities of this network, we filter the network down to the subset of users that actively interact with each other ({\it e.g.,} via retweets and mentions).
 We do this by measuring what we call (incoming/outgoing) information events.
@@
 It should be noted that, as (most) users are not constantly tweeting, these time series are quite sparse.
-%This sparsity will skew the distribution of tweet activity toward being inactive, as the distribution should be to reflect realistic usage statistics.
-\textit{However, if this measure is to be used in practice (Elisa: What does this mean?
-We are indeed using it)} a deeper analysis of the effects of binning, the resulting sparsity, and their role in the activity-based community structure should be carried out.
+For this particular application, this sparsity appropriately reflects the behavior of the users.
+However, this sparsity may not be appropriate for all applications; anytime this weighting is used in practice the effects of binning, sparsity, and their role in the activity-based community structure should be considered.
+We can then compute the flow of information from a user  $u$ to a follower $f$ by computing the transfer entropy between their time series $X_{t}(u)$ and $X_{t}(f).$ See Appendix A for a detailed introduction to transfer entropy and its estimation from data.
 
-We can then compute the flow of information from a user  $u$ to a follower $f$ by computing the transfer entropy between their time series $X_{t}(u)$ and $X_{t}(f).$ See Appendix A for a detailed introduction to transfer entropy and its estimation from data.
  For the communities based on transfer entropy, we weighted each edge from a user $u$ to a follower $f$ by the estimated transfer entropy of the user $u$ on $f$, 
@@
 \end{align}
-As discussed in the introduction, a positive value for the transfer entropy of the user $u$ on $f$ indicates that the time series $X(u)$ and $X(f)$, are casually related in a Granger sense, i.e, user $u$ has PV-AC with follower $f$.
-Said differently, there is a reduction in uncertainty about the activity of $f$ given the tweet history of user $u$.
+% Transfer entropy is an information theoretic measure of \emph{directed} information flow.
+Since transfer entropy is a nonlinear generalization of Granger causality \cite{granger1963economic}, we assume---as is standard---a positive transfer entropy from the tweet history of a user $u$ to a follower $f$'s tweet history implies that this relationship is causal in the Granger sense.
+Thus, communities detected in this way have members whose tweet histories are causally related in a Granger sense.
+%As a result, transfer entropy is often thought of as a measure of ``influence" in an information theoretic sense.
+Transfer entropy is an information theoretic measure of \emph{directed} information flow.
+We assume---as is standard---a positive transfer entropy from the tweet history of a user $u$ to $X(f)$ implies a reduction in uncertainty in the activity of the follower, given the information contained in $X(u)$, while removing the information already contained in $X(f)$.
+This provides an information theoretic framework in which we can capture communities with activity-based predictive capacity between users or users with similar activity profiles.
+We call this relation ``APC" (activity-based predictive capacity).
 
@@
 See Appendix A for a discussion of these issues.
+
+It should be noted that according to~\cite{ver2012information} a positive transfer entropy between $X(u)$ and $X(f)$  indicates that $u$ ``influences" $f$, or that $u$ and $f$ share a common influencer.
+Similarly, since transfer entropy is a nonlinear generalization of Granger causality \cite{granger1963economic}, it is common to assume a positive transfer entropy between a user $u$ and a follower $f$ implies the relationship is causal in the Granger sense.
+However, we are skeptical whether this measure truly captures social influence in its entirety, or even causality in the case of online social networks.
+So instead we simply treat this weighting as a way to explicitly quantify APC between users.
+
+As an aside, while we are skeptical that this measure can capture social influence, later in this paper we show that this information theoretic measure agrees with other concepts of influence such as the Forbes list of ``Top 10 Social Media Influencers" and corroborates with the so-called strength of weak ties~\cite{granovetter1973strength}.
+Even so, we do not explicitly treat transfer entropy---and we do not believe it should be treated without further investigation---as a quantification of social influence or causality.
+Instead this measure should be treated merely as a way to quantify APC between users.%, {\it i.e.,} a reduction in uncertainty of whether a follower $f$ will be active or not given the tweet history of a user $u$
+
+To the best of our knowledge, this is the first use of transfer entropy for community detection in online social networks.
+Various other information theoretic approaches have been used successfully to analyze online social networks, \emph{e.g.,} to gain insight into local user behavior~\cite{darmon2013understanding}, to detect communities based on \emph{undirected} information flow~\cite{darmon2013detecting}, and to perform network inference and link prediction~\cite{ver2012information}.
+
+\subsection{Topic-Based Communities and Hashtag Weighting}
+\label{sec:method-topic}
+
+In contrast to the activity-based approach, the topic-based (or topical) communities, \emph{i.e.,} communities defined by the topics users discuss, rely on the \emph{content} of a user's interactions and ignore their temporal components.
+In a topical community, users are defined to be a member of a community if they tweet \emph{about} similar topics as the other members of the community.
+%Another kind of community is the one based on the content of the tweets, and relies on the idea of finding people that talk about the same things. 
+In order to detect the topical communities, we weight the edges of the user-follower network through a measure based on the number of common hashtags between pairs of users.
+Hashtags are a good proxy for a tweet's content as hashtags are explicitly meant to be keywords indicating the topic of the tweet.
+Moreover they are widely used and straightforward to detect.
+
+To this end, we characterize each user $u$ by a vector $\vec{h}(u)$ of length equal to the number of unique hashtags in the dataset, and whose elements are defined as
+\begin{equation}
+h_i(u) = \phi_i(u)\log{ \frac{N}{n_i} },
+\end{equation}
+where $\phi_i(u)$ is the frequency of hashtag $i$ occuring in user $u$'s tweets, $N$ is the total number of users, and $n_i$ is the number of users that have used the hashtag $i$ in their tweets.
+This adapted term frequency--inverse document frequency (tf-idf) measure \cite{salton_introduction_1983} captures the importance of a hashtag in the users's tweets through the first factor, but at the same time smooths it through the second factor by giving less importance to hashtags that are too widely used (as $\frac{N}{n_i}$ approaches one, its logarithm approaches zero).
+
+For the topical communities we weight each directed edge from a user $u$ to a follower $f$ with the cosine similarity of their respective vectors $\vec{h}(u)$ and $\vec{h}(f)$:
+\begin{align}
+	w_{u \to f}^{\text{HT}} = \frac{\vec{h}(u) \cdot \vec{h}(f)}{\left|\left|\vec{h}(u)\right|\right| \ \ \left|\left|\vec{h}(f)\right|\right|}. \label{Eqn-EW-topic}
+\end{align}
+This weight captures the similarity between users in terms of the topics discussed in their tweets.
 
@@
 %	w_{u \to f}^{\text{MR}} = \frac{1}{2}\left(\frac{\mbox{\# mentions of }f %\mbox{ by }u}{\mbox{\# total mentions of }f} + \frac{\mbox{\# retweets of }u \mbox{ by }f}{\mbox{\# total retweets made by }f}\right).
-
-\subsection{Topic-Based Communities and Hashtag Weighting}
-\label{sec:method-topic}
-
-The final community we consider is a topic-based or topical community, i.e., a community defined by the content (topics) users discuss.
-In a topical community, users are defined to be a member of a community if they tweet \emph{about} similar topics as other members of the community.
-%Another kind of community is the one based on the content of the tweets, and relies on the idea of finding people that talk about the same things. 
-In order to detect the topical communities, we weight the edges of the user-follower network through a measure based on the number of common hashtags between pairs of users.
-Hashtags are a good proxy for a tweet's content as hashtags are explicitly meant to be keywords indicating the topic of the tweet.
-Moreover they are widely used and straightforward to detect.
-
-To this end, we characterize each user $u$ by a vector $\vec{h}(u)$ of length equal to the number of unique hashtags in the dataset, and whose elements are defined as
-\begin{equation}
-h_i(u) = \phi_i(u)\log{ \frac{N}{n_i} }
-\end{equation}
-where $\phi_i(u)$ is the frequency of hashtag $i$ occuring in user $u$'s tweets, $N$ is the total number of users, and $n_i$ is the number of users that have used the hashtag $i$ in their tweets.
-This adapted term frequency--inverse document frequency (tf-idf) measure \cite{salton_introduction_1983} captures the importance of a hashtag in the users's tweets through the first factor, but at the same time smooths it through the second factor by giving less importance to hashtags that are too widely used (as $\frac{N}{n_i}$ approaches one, its logarithm approaches zero).
-
-For the topical communities we weight each directed edge from a user $u$ to a follower $f$ with the cosine similarity of their respective vectors $\vec{h}(u)$ and $\vec{h}(f)$:
-\begin{align}
-	w_{u \to f}^{\text{HT}} = \frac{\vec{h}(u) \cdot \vec{h}(f)}{\left|\left|\vec{h}(u)\right|\right| \ \ \left|\left|\vec{h}(f)\right|\right|}. \label{Eqn-EW-topic}
-\end{align}
-This weight captures the similarity between users in terms of the topics discussed in their tweets.

### 2014-11-29 paper-postreview/results.tex
doing all my final edits

@@
 \section{Results and Discussion}
+In this section we show the importance and usefulness of a multifaceted approach to community detection in online social networks.
+We begin by showing that the communities emerging from the different weightings of the structural network  quantitatively differ both at the macroscopic ({\it e.g.,} number of communities and their size distribution) and microscopic ({\it e.g.,} specific memberships, comemberships) scale in interesting ways.
+Finally, in order to provide a practical illustration of the utility of this question-oriented multifaceted approach, we present several concrete examples of multifaceted community memberships discovered with this method.
+We will show examples both at the community and individual user level.
 
@@
 		T & 289 & 1064 \\
-		I & 252 & 2436 (1719) \\ \hline
+		I & 252 & 2436  \\ \hline
 	\end{tabular}
@@
 
-\begin{figure}[ht]
+\begin{figure}[ht!]
   \centering
@@
 In the previous sections we showed that the communities emerging from the different weightings of the structural network quantitatively differ both at the macroscopic and at the microscopic scale.
-Here, we present some concrete examples of different community membership, in order to uncover the interest of using a multifaceted approach to community detection.
-We explore this at two scales: firstly at the community level, and then at the individual level.
+Here, we present some concrete examples of different community membership, in order to provide a practical illustration of the utility of using a multifaceted approach to community detection.
+We explore this first on a community level and then at the individual level.
 
-In the topic-based communities, we find a single community consisting of 83 users who tweet about environmental issues and frequently use hashtags such as \#green, \#eco and \#sustainability.
-We also find a different community of 47 users who tweet about small businesses and entrepreneurship, using hashtags such as \#smallbiz, \#marketing and \#enterpreneur.
-In both cases most members of the topic-based communities are not found in the same community in the other networks, indicating that while these people talk about the same things and can therefore be considered a community based on their content, they do not strongly interact with each other nor behave the same, and so belong to different social groups with respect to interactions and behavior.
+In the topic-based communities, we found a single community consisting of 83 users who tweet about environmental issues and frequently use hashtags such as \#green, \#eco and \#sustainability.
+We also found a different community of 47 users who tweet about small businesses and entrepreneurship, using hashtags such as \#smallbiz, \#marketing and \#enterpreneur.
+In both cases, almost all members of these topic-based communities are not found in the same community in the other networks \emph{e.g.,} interaction- or activity-based, indicating that while these people talk about the same things and can therefore be considered a community based on their content, they do not strongly interact with each other nor behave the same, and so belong to different social groups with respect to interactions and behavior.
+This illustrates that the topics discussed by these users only define one facet of the users complex social network.
 
@@
 
-It is interesting to examine the intersection between this topic-based community and the overlapping activity-based communities and explore which users in the intersection of these community types have the highest PV-AC.
-Recall that this refers to a reduction in uncertainty about a follower(s) activity on Twitter given the tweet history of a followee.
-Said differently, users with the highest PV-AC in an activity-based community provide the highest reduction in uncertainty about that communities activity or inactivity on Twitter.
-Interestingly, among the highest PV-AC users in these communities---those with highest transfer entropy on average---we find $@$Colorado, which is the state official Twitter account, $@$ConnectColorado, a page created to connect Coloradans, and the CBS Denver account, a popular news agency.
-This means that these accounts have high predictive capacity in terms of their followers' activity on Twitter.
+It is interesting to examine the intersection between this topic-based community and the overlapping activity-based communities and explore which users in the intersection of these community types have the highest APC.
+Users with the highest APC in an activity-based community would provide the highest reduction in uncertainty on average about that communities activity or inactivity on Twitter.
+Interestingly, among the highest APC users in these communities---those with highest transfer entropy on average---we find $@$Colorado, which is the state official Twitter account, $@$ConnectColorado, a page created to connect Coloradans, and the CBS Denver account, a popular news agency.
+This means that these accounts have high activity-based predictive capacity in terms of their followers' activity on Twitter.
 This is not surprising as these activity-based communities heavily overlapped with the topic-based communities that discuss Colorado (mentioned above) and these accounts provide information on this topic.
-This provides a brief proof of concept that this measure makes sense and suggests this could be a useful measure for identifying individuals who possess high predictive capacity for a communities activity on a social media network.
+This provides a brief proof of concept that the APC measure makes sense and suggests this could be a useful measure for identifying individuals who possess high activity-based predictive capacity for a communities activity on a social media network.
 However, more work needs to be done to quantify this more fully.
 
-At the individual-based level, we also found some interesting examples of multifaceted community membership, which show that asking different questions leads to finding different kinds of communities a user belongs to.
-For example, the user $@$JohnReaves belongs to two different topic communities: one about healthcare and the other about innovation and creativity.
-There is a $~70\%$ overlap between the innovation and creativity topic community, the interaction-based, and the activity-based community the user is in, whereas there is almost no overlap between the latter two and the healthcare community.
-This means that the user interacts with and behaves like the people talking about innovation and creativity, whereas he also talks about healthcare but he does not interact with (nor behave like) the people talking about that.
+At the individual-based level, we also found interesting examples of multifaceted community membership, which show that asking multiple questions leads to finding different kinds of communities a user belongs to.
+For example, the user $@$JohnReaves belongs to two different topic communities: one about health care and the other about `innovation' and `creativity'.
+There was a $~70\%$ overlap between the innovation and creativity topic community, the interaction-based, and the activity-based community the user is in, whereas there is almost no overlap between the latter two and the healthcare community.
+This means that the user interacts with and behaves like the people talking about innovation and creativity, but even though he also talks about healthcare he does not interact with (nor behave like) the people talking about that.
 Another interesting example is given by user $@$jenajean.
-She also belongs to two different topic communities: she talks about NASA and space but she does not interact nor behave like people belonging to that topic community, whereas she also talks about leadership, and the people she interacts with highly overlap with the people belonging to the topic-based community on leadership she belongs to.
+She  belongs to two different topic communities: she talks about NASA and space but she does not interact nor behave like people belonging to that topic community, whereas she also talks about leadership, and the people she interacts with highly overlap with the people belonging to the topic-based community on leadership for which she belongs to.
 Lastly, $@$rajean, $@$Tekee, $@$Kimbirly and $@$mamamonroe are examples of users belonging to the topic community talking about Denver and Colorado.
-The activity-based community they belong to highly overlaps with the topic community (therefore they behave like the people that talk about Colorado), but they all belong to different interaction-based communities, each of which does not overlap with the topic community but for two users maximum.
+The activity-based community they belong to highly overlaps with the topic community (therefore they behave like the people that talk about Colorado), but they all belong to different interaction-based communities, each of which does not overlap in more than two users with the topic community.

### 2014-11-30 paper-postreview/response-to-editor.txt
editing response to editor

@@
 
-* [[Josh]]
+* The resultant time series were indeed rather sparse, but this sparsity accurately reflects the usage statistics we were trying to capture.
+As users are not constantly tweeting, the activity profiles, and any coarsening of such an activity profile, should reflect this.
+We appreciate this comment and completely agree that this discussion would be helpful and added a few sentences to discuss this issue in section 2.3 where we first introduced the binning procedure.
 
@@
 
-* We have revised the manuscript to emphasize that this is a property that immediately follows from the definition of the transfer entropy, rather than an assumption that we have made.
-However, we admit that our interpretation of the positivity is an assumption, and we have attempted to make this interpretation more concrete in the revised manuscript.
+* We have revised the manuscript to emphasize the property that immediately follows from the definition of transfer entropy, rather than an assumption that we have made.
+We admit that in the prior version our interpretation of the positivity was just an assumption, and we have performed significant refactoring of all of this work to make our interpretation more concrete in the revised manuscript.
+The assumption of positivity now is 100% the mathematical definition of a reduction in uncertainty and we now imply no further result such as influence or causality.
+Thank you for the suggestion.
 
@@
 
-* As noted in previous responses, the scope of this paper was not to present new weighting metrics, but rather to demonstrate the impact of standard weighting metrics on the communities extracted from a real-world online social network.
-(Elisa: I would say "to compare" rather than "to demontrate")
+* As noted in previous responses, the scope of this paper was not to present new weighting metrics, but rather to illustrate the importance of using *several* standard weighting metrics in order to extract several communities from a real-world online social network.
 
@@
 You can have in theory similar communities.
-This is probably not the case, but you should avoid to say that you expect this behaviour.
+This is probably not the case, but you should avoid to say that you expect this behavior.
 
@@
 
-* [[Josh]]
-
+and 
 - "Lastly, it is interesting to note...": the same might be true for these accounts.
 
-* [[Josh]]
+* As has been stated in previous responses the manuscript has been significantly refactored to not assume the implication of either influence or causality but simply use transfer entropy as a mathematical tool to quantify activity-based predictive capacity, which we define explicitly in the revised paper.
+While we tried to make it clear in the original manuscript that we were hesitant as whether this was truly a measure of social influence, the reviewers comments illustrated to us that we had not done this well enough.
+We hope that this refactoring of the paper makes this skepticism as well as our actual intentions with this method more clear.
 
@@
 Alternative activity-based metrics could and should certainly be applied.
-In this sentence, we meant to emphasize that the structural network alone would not capture this information, and therefore performing influence detection using this network might lead to
+In this sentence, we meant to emphasize that the structural network alone would not capture this information, and therefore performing influence detection using this network might lead to more accurate influence measures.
+We have added some sentences discussing and hopefully making this more clear.
 
-- "erroneous results": how can you say that your resutls are corrects.
+- "erroneous results": how can you say that your results are corrects.
 

### 2014-11-30 paper-postreview/response-to-editor.txt
working on letter

@@
 
-* We do not believe that the contribution of our paper is any of the particular weightings, but rather in how the choice of a weighting can strongly impact.
-We sought to include simple, reasonable metrics motivated by the interaction-, topic-, and activity-based questions, but did not intend for these to be new or even state-of-the-art.
-(Elisa: I would eliminate "or even state-of-the-art".
-Also, I don't understand the first sentence.)
+* Aside from he activity-based weighting.
+We do not believe that the contribution of our paper is any of the particular weightings, but rather that using them all in parallel provides a deeper analysis of the complex community structure present in online social networks.
+We sought to include simple, reasonable metrics motivated by the interaction-, topic-, and activity-based questions, in order to unveil the multifaceted communities present in these networks, but we did not intend for these to be new.
+We have rewritten several of the sections of the paper to emphasize this change.
+We have also re-titled the paper and completely rewritten the abstract to emphasize that the contribution is in the multifaceted approach not in the particular weightings.
+We hope this is now more clear.
 
@@
 
-* [[Josh]]
+* This is a very interesting point, while the interaction based and activity based will have *some* overlap they are not the same and not really a limiting case either.
+Consider the case where a person tweets in reaction to an individuals tweet but does not mention nor retweet the original user.
+This would be detected in the activity based but not the interaction based.
+You may also consider the case where a community is all tweeting about a particular event as that event is occurring but not actually talking to each other, this would register in the topic based and activity based but not in the interaction based.
+In the revised manuscript we provided concrete examples, from the experimental network, of both of these circumstances.
+We hope that this addition to the manuscript will help clear up this confusion.
 
@@
 * We agree that our original presentation of transfer entropy did not do a good enough job of stressing the difference between social and information theoretic influence.
-We have attempted to revise our presentation of transfer entropy to make it more clear exactly what we believe transfer entropy does and does not capture in the setting of our paper.
+We have completely refactored our presentation of transfer entropy to make it more clear exactly what we believe transfer entropy does and does not capture in the setting of our paper.
 
@@
 
-* As has been stated in previous responses the manuscript has been significantly refactored to not assume the implication of either influence or causality but simply use transfer entropy as a mathematical tool to quantify activity-based predictive capacity, which we define explicitly in the revised paper.
-While we tried to make it clear in the original manuscript that we were hesitant as whether this was truly a measure of social influence, the reviewers comments illustrated to us that we had not done this well enough.
+* The manuscript has been significantly refactored to not assume the implication of either influence or causality but simply use transfer entropy as a mathematical tool to quantify activity-based predictive capacity, which we define explicitly in the revised paper.
+While we tried to make it clear in the original manuscript that we were hesitant to whether this was truly a measure of social influence, the reviewers comments illustrated to us that we had not done this well enough.
 We hope that this refactoring of the paper makes this skepticism as well as our actual intentions with this method more clear.
@@
 We decided to focus the paper on communities, and felt that going into more detail about the differences in other network properties went beyond the scope of our analysis.
-However, as we indicated in the Future Work section, we believe that such investigations could yield new insights into the multifaceted nature of online social networks.
-(Elisa: where exactly did we write that (I personally can't really find what sentence you refer to)? If we added in the revised version we should say it explicitely)
+However, as we indicated in the revised Future Work section, we believe that such investigations could yield new insights into the multifaceted nature of online social networks and we do intend to do this analysis, but we believe this would be more appropriate for a separate paper.

### 2014-11-30 paper-postreview/intro.tex

@@
 We then explore how the communities of users differ depending on the type of network used.
-\sout{\emph{Finally, we explore how communication patterns differ across and within the different community types.
-(Elisa: We do that?)}} We conclude by illustrating that this multifaceted question-oriented approach to community detection provides interesting insights into the intricate multifaceted structure of several different users' communities, information that would not be available if only a single form of community detection was performed.
+%\sout{\emph{Finally, we explore how communication patterns differ across and within the different community types. (Elisa: We do that?)}} 
+We conclude by illustrating that this multifaceted question-oriented approach to community detection provides interesting insights into the intricate multifaceted structure of several different users' communities, information that would not be available if only a single form of community detection was performed.
 %\section{Related Work}

### 2014-11-30 paper-postreview/response-to-editor.txt
Beginning to put together new cover letter.

@@
+Dear Editor:
+
+Please find attached the revised manuscript of our paper "Followers Are Not Enough: A Multifaceted Approach to Community Detection in Online Social Networks" by David Darmon, Elisa Omodei, and Joshua Garland.
+
+We have included a revised version of our manuscript (paper.pdf), as well as a marked up version that highlights the changes from our original submission to current version (paper-marked.pdf).
+
+We have sought to address all of the reviewers’ comments and concerns to the best of our ability.
+We have addressed these concerns point-by-point in our responses to the review reports, and have also included them in the addendum of this letter.
+
+PUT MORE HERE.
+
+Thank you for all of the feedback. We believe that it has contributed to making our manuscript clearer, more concise, and more relevant to the research community.
+
+Sincerely,
+
+David Darmon
+Elisa Omodei
+Joshua Garland
+
 Reviewer 1

### 2014-11-30 paper-revised-tosubmit/conclusions.tex
Generated latexdiff-ed version of the paper.

--- 2014-11-23 paper-postreview/conclusions.tex
@@
 This result echos the `strength of weak ties' theory from~\cite{granovetter1973strength}, which has found empirical support in online social networks~\cite{grabowicz2012social}.
-This means that our use of transfer entropy not only defines boundaries that are meaningful divisions between communities but also illustrates that users who have a strong PV-AC on a community need not be a member of that community.
+This means that our use of transfer entropy not only defines boundaries that are meaningful divisions between communities but also illustrates that users who have a strong APC with a community need not be a member of that community.
 
@@
 Our findings may have important implications to a common problem in social network analysis: identification of influential individuals---but further work must be carried out.
-%\alert{maybe move the top 10 people here}
 Many network measures of influence are based on the various types of centrality (degree, betweenness, closeness, eigenvector, etc.)~\cite{newman2009networks}.
@@
 Based on our preliminary results, we conjecture that weighted generalizations of these centrality measures using transfer entropy might lead to better insights about who is actually influential in an online social network.
-It is interesting to note for example that two of the Forbes ``Top 10 Social Media Influencers", happen to be in our network, \emph{viz.}, Ann Tran and Jessica Northey, and transfer entropy also quantified these two users as having high PV-AC, i.e., the uncertainty about their followers activity on Twitter was reduced given their tweet histories.
+It is interesting to note for example that two of the Forbes ``Top 10 Social Media Influencers", happen to be in our network, \emph{viz.}, Ann Tran and Jessica Northey, and transfer entropy also quantified these two users as having two of the highest APC on average, i.e., there was a high reduction in uncertainty about their followers activity on Twitter given their tweet histories.
 While we do not believe this information theoretic measure can capture social influence in its entirety,
@@
 This work demonstrates the utility of a multifaceted question-oriented approach to community detection.
-This work shows that crafting \emph{several} facet-driven weighting schema, doing community detection for each weighting scheme and then comparing the similarities and differences across community types, is an unavoidable process for uncovering the hidden layered community structure present in online social networks.
+This work shows that crafting \emph{several} facet-driven weighting schema, doing community detection for each weighting scheme and then comparing the similarities and differences across community types, is an unavoidable process for uncovering the complex---and often hidden---community structure present in online social networks.
 More generally, this work illustrates that without a clear definition of community---or even only using a \emph{single} definition of community---many rich and interesting communities present in online social networks remain invisible.

### 2014-11-30 paper-revised-tosubmit/intro.tex
Generated latexdiff-ed version of the paper.

--- 2014-11-30 paper-postreview/intro.tex
@@
 The approach of focusing on the structure of networks makes sense for `real-world' sociological experiments, where obtaining additional information about user interactions may be expensive and time-consuming.
-However, with the prevalence of large, rich data sets for online social networks, additional information beyond the structure alone may be incorporated, and these augmented networks more realistically reflect how users interact with each other on social media services~\cite{nguyen2011adaptive,grabowicz2012social}.
+However, with the prevalence of large, rich data sets from online social networks, additional information beyond the structure alone may be incorporated, and these augmented networks more realistically reflect how users interact with each other on social media services~\cite{nguyen2011adaptive,grabowicz2012social}.
 
@@
 Previous research on communities in social networks focused almost exclusively on different network types in isolation.
-A notable exception to this is~\cite{lim2012tweets}, that considered both structure-based and interaction-based communities on Twitter.
+A notable exception to this is~\cite{lim2012tweets}, which considered both structure-based and interaction-based communities on Twitter.
 However, this study focused on data collected based on particular topics (country music, tennis, and basketball), and not on a generic subpopulation of Twitter users.

### 2014-11-30 paper-revised-tosubmit/methods.tex
Generated latexdiff-ed version of the paper.

--- 2014-11-29 paper-postreview/methods.tex
@@
 For this particular application, this sparsity appropriately reflects the behavior of the users.
-However, this sparsity may not be appropriate for all applications; anytime this weighting is used in practice the effects of binning, sparsity, and their role in the activity-based community structure should be considered.
+However, this sparsity may not be appropriate for all applications; anytime the following measure is used in practice the effects of binning, sparsity, and their role in the activity-based community structure should be considered.
 We can then compute the flow of information from a user  $u$ to a follower $f$ by computing the transfer entropy between their time series $X_{t}(u)$ and $X_{t}(f).$ See Appendix A for a detailed introduction to transfer entropy and its estimation from data.
@@
 We define three weighting schemes.
-Firstly, we consider the number of tweets of a user $u$ that were rebroadcast by a follower $f$, indicating a flow of information from $u$ to $f$.
+We first consider the number of tweets of a user $u$ that were rebroadcast by a follower $f$, indicating a flow of information from $u$ to $f$.
 Since different users produce different amounts of tweets and retweets, in order to take into account the relative importance of this measure we normalize it by dividing over the total number of retweets made by $f$,
@@
 \end{equation}
-Secondly, we consider the number of mentions of $f$ made by user $u$.
+We then consider the number of mentions of $f$ made by user $u$.
 To account for the fact that some users/accounts are very popular and are often mentioned by so many other users that the flow of information from the latter to the former is flushed out, we normalize this measure by dividing over the total number of mentions received by $f$.

### 2014-11-30 paper-revised-tosubmit/paper.tex
Generated latexdiff-ed version of the paper.

--- 2014-11-26 paper-postreview/paper.tex
@@
 \usepackage{enumitem}
+\usepackage[normalem]{ulem}
 
@@
 
-In online social media networks, individuals often have hundreds or even thousands of connections, which connect these users not only to friends, associates, and colleagues, but also to news outlets, celebrities, and government organizations.
+In online social media networks, individuals often have hundreds or even thousands of connections, which link these users not only to friends, associates, and colleagues, but also to news outlets, celebrities, and organizations.
 In these complex social networks, a `community' as studied in the social network literature, can have very different meaning depending on the property of the network under study.

### 2014-11-30 paper-postreview/response-to-editor.txt
my changes to the response letter

--- 2014-11-30 paper-postreview/response-to-editor.txt
@@
 
-* We did not mean to claim that the community extraction was done blindly.
+* We did not mean to claim that the community extraction was done blindly or that this was the novelty of our work.
 In fact, we demonstrated exactly the opposite: by intentionally choosing a different question about the individuals in the social network, very different community structure may be extracted.
-We did wish to highlight that a question-oriented approach to community detection can be undertaken with the network at-hand, assuming the network was collected in a way that would not strongly bias any of the weighting metrics we utilized.
+We did wish to highlight that a multifaceted question-oriented approach to community detection can be undertaken with the network at-hand, assuming the network was collected in a way that would not strongly bias any of the weighting metrics we utilized.
+We have made considerable edits to address this concern.
 
@@
 Thus, this measure is neither directed, nor does it account for lagged effects in terms of the interaction between two nodes in network, as our method does.
-(Elisa: I think this answers only the very first part of the comment. Josh, could you please elaborate also on the rest (I leave this to you since it's the transfer entropy stuff))
+As far as the reviewers comments on the connection between transfer entropy and social influence, we completely agree with the reviewer.
+In the original manuscript we tried to be careful about hedging this as a measure of influence and to illustrate our skepticism of this implication.
+Based on the reviewer comments we see that we did not make this clear enough.
+Since, as the authors, we are also skeptical of this implication we have taken this assumption completely out of the paper which resulted in a significant refactoring of the entire paper.
+Our original intention was to have transfer entropy simply be a weighting measure of activity based predictive capacity.
+Effectively TE measures a reduction in uncertainty about a followers activity on Twitter given the tweet history of a user, removing the information contained in the tweet history of the follower.
+In the literature this is often considered influence or causality.
+However, similar to the reviewer, we were skeptical about this.
+In the original manuscript we tried to state these things as possible implications while hedging that we were skeptical that TE actually captured social influence or even time-series causality.
+As a result of the reviewers comments we have completely refactored the entire discussion of activity-based communities to focus on the mathematical definition of TE which is activity-based predictive capacity (which is defined in the revised manuscript) and have completely removed all possible implications such as influence or casuality.
+Thank you for pointing out that this was not clear before.
 
@@
 We do not believe that the contribution of our paper is any of the particular weightings, but rather that using them all in parallel provides a deeper analysis of the complex community structure present in online social networks.
-We sought to include simple, reasonable metrics motivated by the interaction-, topic-, and activity-based questions, in order to unveil the multifaceted communities present in these networks, but we did not intend for these to be new.
-We have rewritten several of the sections of the paper to emphasize this change.
-We have also re-titled the paper and completely rewritten the abstract to emphasize that the contribution is in the multifaceted approach not in the particular weightings.
+We sought to include simple, reasonable metrics motivated by the interaction-, topic-, and activity-based questions, in order to unveil the multifaceted communities present in these networks, but we did not intend for these to be new or a contribution of the work.
+We have rewritten several of the sections of the paper to emphasize that this is not a contribution of the paper and added several citations to clarify this.
+We have also re-titled the paper and completely rewrote the abstract to emphasize that the contribution is in the multifaceted approach not in the particular weightings.
 We hope this is now more clear.
@@
 
-* We have attempted to address this point more fully in section 3.4 of the revised manuscript.
+* This is a great suggestion, and one we believe really strengthened this paper.
+We have attempted to address this point more explicitly in section 3.4 of the revised manuscript.
 In particular, we demonstrate how the topic-based, interaction-based, and activity-based networks give rise to meaningful communities based on their respective interpretations of the meaning of 'community.' e.g.
 A topic-based community based around small businesses, an activity-based community based around individuals in Denver, CO, etc.
-Finally, we have added individual case studies to demonstrate how the community membership of a user across the different community types reveals different aspects of the user's online identity.
+In addition, we have added several case studies on the community and individual user level to demonstrate how the community membership of a user across the different community types reveals different aspects of the user's online identity.
 
@@
 
-* The fact that different weightings should give rise to different communities is in our opinion non-trivial.
-For example, if all of the different weightings were strongly associated with each other, then we would expect to obtain the same communities, since the same structural backbone was used to to construct each weighted network.
-One might expect this to be the case with, for example, the interaction-based and activity-based weights.
-However, as both Figures 1 and 2 demonstrate, this is not the case.
+* The fact that different weightings should give rise to different communities is, in our opinion, non-trivial.
+For example, if a group of users constantly interacted with each other after school and used the same hash tags, then most likely all three activity-based, interaction-based and topic-based communities would completely overlap and these different weightings would not lead to different networks.
+Effectively, if all of the different weightings were strongly associated with each other, then we would expect to obtain the same communities, since the same structural backbone was used to to construct each weighted network.
+We have added several sentences in the paper addressing this concern.
+However, this was not always the case as both Figures 1 and 2 demonstrate.
+Some weightings resulted in similar communities, while others almost completely overlapped.
+The fact that the different weightings provide interesting viewpoints of the communities present in this network is in our opinion nontrivial and interesting.
+To make this point more clear we have added sentences to the introduction as well as case studies in Section 3.4.
 
@@
 
-* We did not introduce the term/concept. It can be found in reference [5].
+* We did not introduce the term/concept. It can be found in reference [5]. We have added this reference in a more prominent spot to make this more clear.
 
@@
 * We did not mean to claim that sociologists currently take this approach, but rather that this approach was more reasonable in the era of small-scale studies of human/human interaction (for example, the small-world experiment of Stanley Milgram, or Zachary's Karate club).
+This has been corrected in the revisions.
 
@@
 This would be detected in the activity based but not the interaction based.
-You may also consider the case where a community is all tweeting about a particular event as that event is occurring but not actually talking to each other, this would register in the topic based and activity based but not in the interaction based.
+You may also consider the case where members of a community are all tweeting about a particular event as that event is occurring but not actually talking to each other, this would register in the topic based and activity based but not in the interaction based.
 In the revised manuscript we provided concrete examples, from the experimental network, of both of these circumstances.
@@
 
-* We agree that our original presentation of transfer entropy did not do a good enough job of stressing the difference between social and information theoretic influence.
+* We agree that our original presentation of transfer entropy did not do a good enough job of stressing the difference between social influence and what this information theoretic measure actually gives you.
 We have completely refactored our presentation of transfer entropy to make it more clear exactly what we believe transfer entropy does and does not capture in the setting of our paper.
@@
 As users are not constantly tweeting, the activity profiles, and any coarsening of such an activity profile, should reflect this.
-We appreciate this comment and completely agree that this discussion would be helpful and added a few sentences to discuss this issue in section 2.3 where we first introduced the binning procedure.
+We appreciate this comment and completely agree that this discussion would be helpful and as a result we added a few sentences to discuss this issue in section 2.3 of the revised manuscript where we first introduced the binning procedure.
 
@@
 The assumption of positivity now is 100% the mathematical definition of a reduction in uncertainty and we now imply no further result such as influence or causality.
-Thank you for the suggestion.
+Thank you for the suggestion, we believe it strengthened this work.
 
@@
 
-* Thank you for this comment. We expanded section 2.4 in the revised manuscript in order to motivate more in details these metrics.
+* Thank you for this comment. We expanded section 2.4 in the revised manuscript in order to motivate these metrics in more detail.
 
@@
 
-*
+* [[David fill this in ]]
 
@@
 
-*
+* [[David please fill this in ]]
 
@@
 and
+
 - "Lastly, it is interesting to note...": the same might be true for these accounts.
@@
 * Thank you for this suggestion.
-We decided to focus the paper on communities, and felt that going into more detail about the differences in other network properties went beyond the scope of our analysis.
+We decided to focus the paper on communities, and felt that going into more detail about the differences in other network properties went beyond the scope of our analysis and would confuse the focus of the work.
 However, as we indicated in the revised Future Work section, we believe that such investigations could yield new insights into the multifaceted nature of online social networks and we do intend to do this analysis, but we believe this would be more appropriate for a separate paper.

### 2014-12-01 paper-postreview/response-to-editor.txt
Added responses to the reviewer's points.
Still need to fill in the PUT MORE HERE.

@@
 We have addressed these concerns point-by-point in our responses to the review reports, and have also included them in the addendum of this letter.
-
-PUT MORE HERE.
 
@@
 
-* [[David fill this in ]]
+* We do not believe that this result is an 'artifact' of the definitions, but rather because of the definitions.
+Recalling that the normalized mutual information measures how similar the coverings are, the fact that we observe similar coverings for similar, but not identical, weightings gives one indication that the underlying communities correspond true latent components of the network.
+For artifacts, we would expect either all of the coverings to be completely dissimilar (indicating that the community structure is purely driven by the weights), or for all of the coverings to be equally similar (indicating that the community structure is purely driven by the underlying structural network used in all of the weightings).
 
@@
 
-* [[David please fill this in ]]
+* This is meant to highlight the point from the previous response.
+Namely, we see a block diagonal structure in the normalized mutual information, indicating that coverings based on the same type of weight (interaction-, activity-, and topic-based), but not necessarily identical weight (lag-1 vs lag-2 transfer entropy, for example), are more similar.
+We believe this is relevant for the reason given in our response to the previous point.
 
@@
 
-* [[David please fill this in ]]
+* We agree that it is not meaningful to directly compare, for example, the median values for the transfer entropy weights and mention-retweet weights.
+However, this was not what we meant to highlight with this figure.
+Instead, we meant to highlight that the medians differ depending on whether one considers inter-, intra-, or mixed-type edges, and that these medians differ in systematic ways that do not depend on the weight type.
+We believe that this type of comparison, which depends on more qualitative distributional properties of the weights, is valid.
 

### 2014-12-01 paper-postreview/response-to-editor.txt
Finish up letter to editor.

@@
 We have addressed these concerns point-by-point in our responses to the review reports, and have also included them in the addendum of this letter.
+
+Overall, we have made the effort to make the contribution of this paper more clear.
+In particular, we do not believe and did not intend for our paper to contribute methodologically to the question of how to construct edge weights for a network derived from an online social network.
+Instead, the contribution of our paper was to highlight that using any one perspective of a network, especially one based solely on the structural network, leads to an incomplete view of the meaningful community structure present in online social networks, and that combining many perspectives provides a more complete picture of the network.
+We have also changed the title to "Followers Are Not Enough: A Multifaceted Approach to Community Detection in Online Social Networks" to reflect this focus.
+
+Moreover, we have sought to address the reviewer's concerns over our interpretation of transfer entropy in terms of social influence.
+We have been more careful in our language in those sections involving transfer entropy, emphasizing the difference between the mathematical and sociological definitions of influence, and making clear which type of these we invoke.
 

### 2014-12-01 paper-postreview/response-to-editor.txt
minor edits to response

@@
 We have sought to address all of the reviewers’ comments and concerns to the best of our ability.
-We have addressed these concerns point-by-point in our responses to the review reports, and have also included them in the addendum of this letter.
+We have addressed these concerns point-by-point in our responses to the reviewer reports, and have also included them in the addendum of this letter.
 
@@
 Moreover, we have sought to address the reviewer's concerns over our interpretation of transfer entropy in terms of social influence.
-We have been more careful in our language in those sections involving transfer entropy, emphasizing the difference between the mathematical and sociological definitions of influence, and making clear which type of these we invoke.
+We have been more careful in our language in those sections involving transfer entropy, emphasizing the difference between the mathematical and sociological definitions of influence, and making clear exactly what we intend transfer entropy to be used for in this context.
+To accomplish this we refactored a significant portion of the revised manuscript to emphasize and strictly rely on the mathematical definition of transfer entropy, rather than the implications and assumptions that commonly follow from this definition in the literature.
+We believe this refactoring significantly improved the clarity and presentation of this work and we hope it clears up the concern of Reviewer 1.
 

### 2015-01-28 paper-for_plos/paper.tex
Formatted paper for PLoS One.

% Template for PLoS
% Version 3.0 December 2014
%
% To compile to pdf, run:
% latex plos.template
% bibtex plos.template
% latex plos.template
% latex plos.template
% dvipdf plos.template
%
% % % % % % % % % % % % % % % % % % % % % %
%
% -- IMPORTANT NOTE
%
% This template contains comments intended 
% to minimize problems and delays during our production 
% process. Please follow the template instructions
% whenever possible.
%
% % % % % % % % % % % % % % % % % % % % % % % 
%
% Once your paper is accepted for publication, 
% PLEASE REMOVE ALL TRACKED CHANGES in this file and leave only
% the final text of your manuscript.
%
% There are no restrictions on package use within the LaTeX files except that 
% no packages listed in the template may be deleted.
%
% Please do not include colors or graphics in the text.
%
% Please do not create a heading level below \subsection. For 3rd level headings, use \paragraph{}.
%
% % % % % % % % % % % % % % % % % % % % % % %
%
% -- FIGURES AND TABLES
%
% Please include tables/figure captions directly after the paragraph where they are first cited in the text.
%
% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
% - Figures should be uploaded separately from your manuscript file. 
% - Figures generated using LaTeX should be extracted and removed from the PDF before submission. 
% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
% See http://www.plosone.org/static/figureGuidelines for PLOS figure guidelines.
%
% Tables should be cell-based and may not contain:
% - tabs/spacing/line breaks within cells to alter layout or alignment
% - vertically-merged cells (no tabular environments within tabular environments, do not use \multirow)
% - colors, shading, or graphic objects
% See http://www.plosone.org/static/figureGuidelines#tables for table guidelines.
%
% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
%
% % % % % % % % % % % % % % % % % % % % % % % %
%
% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
%
% IMPORTANT
% Below are a few tips to help format your equations and other special characters according to our specifications. For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://www.plosone.org/static/latexGuidelines
%
% Please be sure to include all portions of an equation in the math environment.
%
% Do not include text that is not math in the math environment. For example, CO2 will be CO\textsubscript{2}.
%
% Please add line breaks to long display equations when possible in order to fit size of the column. 
%
% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
%
% % % % % % % % % % % % % % % % % % % % % % % % 
%
% Please contact latex@plos.org with any questions.
%
% % % % % % % % % % % % % % % % % % % % % % % %

\documentclass[10pt,letterpaper]{article}
\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}

% Use adjustwidth environment to exceed column width (see example table in text)
\usepackage{changepage}

% Use Unicode characters when possible
\usepackage[utf8]{inputenc}

% textcomp package and marvosym package for additional characters
\usepackage{textcomp,marvosym}

% fixltx2e package for \textsubscript
\usepackage{fixltx2e}

% amsmath and amssymb packages, useful for mathematical formulas and symbols
\usepackage{amsmath,amssymb}

% cite package, to clean up citations in the main text. Do not remove.
\usepackage{cite}

% Use nameref to cite supporting information files (see Supporting Information section for more info)
\usepackage{nameref,hyperref}

% line numbers
\usepackage[right]{lineno}

% ligatures disabled
\usepackage{microtype}
\DisableLigatures[f]{encoding = *, family = * }

% rotating package for sideways tables
\usepackage{rotating}

% Remove comment for double spacing
%\usepackage{setspace} 
%\doublespacing

% Text layout
\raggedright
\setlength{\parindent}{0.5cm}
\textwidth 5.25in 
\textheight 8.75in

% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
% Captions will be left justified
\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}

% Custom (non-PLoS) packages:

\usepackage{amsmath} %for dealing with mathematics,
\usepackage{amsfonts}	%for dealing with mathematics,
\usepackage{amsthm} %for dealing with theorem environments,
%\usepackage{hyperref} %for linking the cross references % CA: I couldn't get it to work properly with this package
\usepackage{graphicx} %for dealing with figures.
%\usepackage{algorithm}
%\usepackage{algorithmic} %for describing algorithms
\usepackage{subfigure} %for getting the subfigures e.g., "Figure 1a and 1b" etc.
\usepackage{times}
\usepackage{helvet}
%\usepackage{courier}
\usepackage{multirow}
\usepackage{bigstrut}
\usepackage{booktabs}
\usepackage{multirow,bigstrut}
\usepackage{tabu}
\usepackage{authblk}
\usepackage{color}
%\usepackage{subfigure}
\usepackage{appendix}
\usepackage{url} %CA: I want to use hyperref -> but we get errors (see above)
\usepackage{enumitem}
\usepackage[normalem]{ulem}

% Use the PLoS provided BiBTeX style
\bibliographystyle{plos2009}

% Remove brackets from numbering in List of References
\makeatletter
\renewcommand{\@biblabel}[1]{\quad#1.}
\makeatother

% Leave date blank
\date{}

% Header and Footer with logo
\usepackage{lastpage,fancyhdr,graphicx}
\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
\lhead{\includegraphics[natwidth=1.3in,natheight=0.4in]{PLOSlogo.png}}
\rfoot{\thepage/\pageref{LastPage}}
\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
\fancyheadoffset[L]{2.25in}
\fancyfootoffset[L]{2.25in}
\lfoot{\sf PLOS}

%% Include all macros below

\newcommand{\lorem}{{\bf LOREM}}
\newcommand{\ipsum}{{\bf IPSUM}}

%% END MACROS SECTION

\begin{document}
\vspace*{0.35in}

% Title must be 150 characters or less
\begin{flushleft}
{\Large
\textbf\newline{Followers Are Not Enough: A Multifaceted Approach to Community Detection in Online Social Networks}
}
\newline
% Insert Author names, affiliations and corresponding author email.
\\
David Darmon\textsuperscript{1, *},
Elisa Omodei\textsuperscript{2},
Joshua Garland\textsuperscript{3},
\\
\bf{1} Dept. of Mathematics, University of Maryland, College Park, MD, United States
\\
\bf{2} LaTTiCe (CNRS, ENS, Paris 3), ISC-PIF, Paris, France
\\
\bf{3} Dept. of Computer Science, University of Colorado, Boulder, CO, United States
\\

% Insert additional author notes using the symbols described below. Insert symbol callouts after author names as necessary.
% 
% Remove or comment out the author notes below if they aren't used.
%
% Primary Equal Contribution Note
%\Yinyang These authors contributed equally to this work.

% Additional Equal Contribution Note
%\ddag These authors also contributed equally to this work.

% Current address notes
%\textcurrency a Insert current address of first author with an address update
% \textcurrency b Insert current address of second author with an address update
% \textcurrency c Insert current address of third author with an address update

% Deceased author note
%\dag Deceased

% Group/Consortium Author Note
%\textpilcrow Insert Collaborative Author line here

* E-mail: ddarmon@math.umd.edu
\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}
In online social media networks, individuals often have hundreds or even thousands of connections, which link these users not only to friends, associates, and colleagues, but also to news outlets, celebrities, and organizations. In these complex social networks, a `community' as studied in the social network literature, can have very different meaning depending on the property of the network under study. 
% and different definitions of community such as ``whom do we interact with?" and ``with whom do we share similar interests?" can lead to very different and interesting social groups. 
Taking into account the multifaceted nature of these networks, we claim that community detection in online social networks should also be multifaceted in order to capture all of the different and valuable viewpoints of `community.' In this paper we focus on three types of communities beyond follower-based structural communities: activity-based, topic-based, and interaction-based. We analyze a Twitter dataset using three different weightings of the structural network meant to highlight these three community types, and then infer the communities associated with these weightings. We show that interesting insights can be obtained about the complex community structure present in  social networks by studying when and how these four community types give rise to similar as well as completely distinct community structure.

\linenumbers

\section{Introduction}

Networks play a central role in online social media services like Twitter, Facebook, and Google+. These services allow a user to interact with others based on the online social network they curate through a process known as contact filtering~\cite{cazabet2012automated}. For example, `friends' on Facebook represent reciprocal links for sharing information, while `followers' on Twitter allow a single user to broadcast information in a one-to-many fashion. Central to all these interactions is the fact that the \emph{structure} of the social network influences how information can be broadcast or diffuse through the service.

Because of the importance of structural networks in online social media, a large amount of work in this area has focused on using structural networks for community detection. In this traditional view, a community is defined as a collection of nodes (users) within the network which are more highly connected to each other than to nodes (users) outside of the community~\cite{girvan2002a, newman2004finding}. For instance, in~\cite{java2009we}, the authors use a follower network to determine communities within Twitter, and note that conversations tend to occur within these communities. The approach of focusing on the structure of networks makes sense for `real-world' sociological experiments, where obtaining additional information about user interactions may be expensive and time-consuming. However, with the prevalence of large, rich data sets from online social networks, additional information beyond the structure alone may be incorporated, and these augmented networks more realistically reflect how users interact with each other on social media services~\cite{nguyen2011adaptive,grabowicz2012social}.

%A large body of work exists on methods for automatic detection of communities within networks~\cite{newman2004fast,newman2004finding,rosvall2008maps,blondel2008fast,LancichinettiPlos}. See~\cite{fortunato2010community} for a recent review. 
A large body of work exists on methods for automatic detection of communities within networks, {\it e.g.,} the stochastic blockmodel~\cite{Holland1983} (and its recent generalization to weighted networks~\cite{Aicher26062014}), the Girvan-Newman algorithm~\cite{newman2004finding}, clique percolation~\cite{PalEtAl05}, Infomap~\cite{Rosvall08mapsof}, Louvain~\cite{blondel2008fast}, and the recently introduced OSLOM~\cite{LancichinettiPlos}.
All these methods begin with a given network, and then attempt to uncover structure present in the network, \emph{i.e.,} they are agnostic to how the network was constructed.
As opposed to this agnostic analysis, we propose---and illustrate the importance of---a \emph{multifaceted question-focused} approach. We believe that in order to understand all of the communities present in a network, it is important to take the following crucial steps: 
\begin{enumerate}

\item Ask \emph{several} questions about the communities that may be present in the network, each of which is aimed at revealing a new facet of the community structure present in the network---{\it e.g.,} which users are tightly connected structurally? which groups of users have similar topical interests?

\item Derive a weighting scheme aimed at answering each of the questions asked in the first step and then perform community detection on each weighted network.
\item Compare the (possibly) different communities that arise from this series of experiments on a micro and macro scale to unveil all the interesting facets of community structure present in the social network. 
\end{enumerate}

This is especially true for social network analysis. In social networks, a `community' could refer to several possible structures. The simplest definition of community, as we have seen, might stem from the network of explicit connections between users on a service (friends, followers, etc.). On small time scales, these connections are more or less static. To form a more dynamic picture of community structure, we might instead determine communities based on who is talking to whom or which users talk about similar topics.
More abstractly, we could even define communities as groups of people who exhibit similar activity profiles. We can characterize these types of communities based on the questions that motivate them:
\begin{itemize}
	\item \textbf{Structure-based:} Who are your stated friends? Whom do you follow?
	\item \textbf{Activity-based:} Who shares similar activity profiles?
	\item \textbf{Topic-based:} What do you talk about?
	\item \textbf{Interaction-based:} Whom do you communicate with?
\end{itemize}

This is not meant to be an exhaustive list, but rather a list of some of the more common types of communities observed and studied in social networks. Instead of looking at each of these questions in isolation---which is the standard approach---we propose looking at when and how communities motivated by these different questions overlap and are disjoint, and whether different approaches to asking the question ``What community are you in?'' leads to different insights about a social network. For example, a user on Twitter might connect mostly with computational social scientists, utilize the service nearly every time a particular user or group of users is active, talk mostly about machine learning, and interact solely with close friends (who may or may not be computational social scientists). 
For this user, the answers to each question therefore correspond to more or less distinct communities. By contrast, a teenage user may only connect and interact with their friends, will most likely exhibit similar activity patterns dictated by the academic and extracurricular schedule of a student, and will discuss topics typical of their demographic. For this user, the answers to each question map to the same community of users, even though different definitions of community are being used. This highlights an important subtlety of this work: defining communities in different ways does not imply that the collection of users in each community \emph{must} be different. Said differently, it is not obvious---or always the case---that changing the definition of community will always change the communities that are detected. Studying when this change does and does not occur---as we will show---provides interesting insights into the complex community structure present in these networks.
%Thus, each question acts to highlight a particular subset of users a particular user is connected with in an online social network, and this can help identify the possibly different communities the user belongs to.
%Thus, each question acts to highlight a particular `profile' of a user, and these profiles or facets could help define the relationships of a user on an online social network more completely.

We now consider in more detail how each of these types of questions describes a unique facet of `community'. Later in Section~\ref{sec:conc} we will show how asking \emph{all} of these questions---instead of focusing on only one---gives a much deeper view of the (possibly) different communities that users belong to.

Na\"ively the activity-based approach is motivated by the question of ``Which users in a network have similar activity profiles?".
%--- \emph{i.e.,} which user(s) cause groups of users to become active on the network.  %, \emph{i.e.}, which user(s) cause a user(s) to interact with the network. 
 With this question in mind, a community can then be thought of as those users who use (or do not use) the service at similar times. However, the measure we use is slightly more subtle that this. In particular, these communities can be thought of as groups of users who possess so-called ``activity-based predictive capacity" with one another, \emph{i.e.}, given a user $u$ and follower $f$, who are members of a community detected with this weighting, there exists a reduction in uncertainty about the activity profile of follower $f$ (tweeting or remaining silent), given the tweet history of user $u$, ignoring the information present in the tweet history of follower $f$.  To accomplish this, we consider each user on Twitter as an information processing unit, but completely ignore the \emph{content} of their tweets. We then weight the directed edges (the reported follower-followee relationships) between users with the so-called \emph{transfer entropy}~\cite{schreiber2000measuring}, calculated between the tweet history of follower $f$ and user $u$. This is discussed in more detail in Section~\ref{sec:method-activity}.

The topic-based and interaction-based approaches, in contrast to the activity-based approach, rely on the \emph{content} of a user's interactions and ignore their temporal components. The content contains a great deal of information about communication between users.
There are two broad approaches to topic-based communities in the literature. \cite{rossi2012conversation} used a set of users collected based on their use of a single hashtag, and tracked the formation of follower and friendship links within that set of users. In~\cite{lim2012following}, the authors chose a set of topics to explore, and then seeded a network from a celebrity chosen to exemplify a particular topic. Both approaches thus begin with a particular topic in mind, and perform the data collection accordingly. Other approaches use probabilistic models for the topics and treat community membership as a latent variable~\cite{yin2012latent}.
For example, a popular approach to analyzing social media data is to use Latent Dirichlet Allocation (LDA) to infer topics based on the prevalence of words within a status~\cite{zhao2011comparing,michelson2010discovering}. The LDA model can then be used to infer distributions over latent topics, and the similarity of two users with respect to topics may be defined in terms of the distance between their associated topic distributions. Because our focus is not on topic identification, we apply a simpler approach using hashtags as a proxy for topics, similar to the approaches presented in~\cite{becker2011beyond,tsur2012s}. We can then define the similarity of two users in terms of their hashtags, and use this similarity to build a topic-based network. This method is described in detail in Section~\ref{sec:method-topic}.

Finally, the interaction-based approach relies on the meta-data and text of messages to identify whom a user converses with on the social media service. On Twitter, we can use mentions (indicating a directed communication) and retweets (indicating endorsement of another user) to identify conversation. 
A few works have investigated this type of community. For example, \cite{conover2011political} considered both mention and retweet networks in isolation for a collection of users chosen for their political orientation. In~\cite{deitrick2013mutually}, the authors construct a dynamic network based on simple time-windowed counts of mentions and retweets, and use the evolution of this network to aid in community detection.

Previous research on communities in social networks focused almost exclusively on different network types in isolation.
A notable exception to this is~\cite{lim2012tweets}, which considered both structure-based and interaction-based communities on Twitter. However, this study focused on data collected based on particular topics (country music, tennis, and basketball), and not on a generic subpopulation of Twitter users. Moreover, it did not explore the differences in community structure resulting from the different network weightings, and focused on aggregate statistics (community size, network statistics, etc.). Another notable exception is~\cite{kao2013talison}, where the authors used a tensor representation of user data to incorporate retweet and hashtag information into a study of the social media coverage of the Occupy Movement. The tensor can then be decomposed into factors in a generalization of the singular value decomposition of a matrix, and these factors can be used to determine `salient' users. However, unlike our work, this approach focused on data for a particular topic (the Occupy Movement) and did not collect users based on a structural network.

Studying how the communities derived from follower-followee, activity-based, topic-based, and interaction-based networks are disjoint as well as overlapping allow for a more complete picture of the \emph{implicit} networks present in online social media, as opposed to the \emph{explicit} social network indicated by follower links alone. In this paper, we explore the relation between these various possible networks through their corresponding communities. We begin by describing the methodologies used to generate the various types of networks, and infer their community structure.  We then explore how the communities of users differ depending on the type of network used.
%\sout{\emph{Finally, we explore how communication patterns differ across and within the different community types. (Elisa: We do that?)}} 
We conclude by illustrating that this multifaceted question-oriented approach to community detection provides interesting insights into the intricate multifaceted structure of several different users' communities, information that would not be available if only a single form of community detection was performed. 
%\section{Related Work}

% Structural:
% ==========

% \cite{java2009we} Determine friendship network on Twitter to define communities.

% \cite{nguyen2011adaptive} Uses a dynamic community detection algorithm (that uses snapshots of the network), but still focuses on \emph{structural} ties (Facebook friendship relationships)

% Interaction-based:
% ==================

% \cite{deitrick2013mutually} use 'dynamic' mention-retweet network to detect communities, but just augment the count of mentions retweets in the weighting (instead of using a proportion), and don't combine mentions and retweets.

% \cite{conover2011political} Retweet-mention analysis for political polarization analysis
% http://truthy.indiana.edu/site_media/pdfs/conover_icwsm2011_polarization.pdf

% Activity-based:
% ===============

% None, to the best of our knowledge.

% Topic-based:
% ============

% \cite{lim2012following} "We propose an efficient approach for detecting communities that share common interests on Twitter, based on linkages among followers of celebrities representing an interest category." Use both InfoMAP and clique percolation.

% \cite{rossi2012conversation} Collect users who use the same hashtag (a *single* hashtag, #XF5, for XFactor 5), and then note if this impacts the friend/follower network.

% \cite{xu2011sentiment} Generate 'sentiment' networks.

% Most-relevant:
% ==============

% \cite{lim2012tweets} This one is *very* important: they also note that structural links do not indicate communication. They use an interaction-based approach (mentions only). But they do not use a weighted version of the structural network. Instead, they use . And they do not go into much depth comparing how the two types of communities (structural and activity-based) differ. Moreover, they explicitly seed their network to focus around a particular topic (country music, tennis, basketball, etc.)

\section{Methodology}
In the following sections, we introduce the problem of community detection, and present the data set used for our analyses. We then describe our methodology for constructing the question-specific networks. In particular, we introduce an information theoretic statistic for activity-based communities, a retweet-mention statistic for interaction-based communities, and a hashtag similarity metric for defining topic-based communities. It should be noted that our goal is to choose representative weightings for each community type so that we may compare community structure across types, and not to---aside from the activity-based weighting---introduce novel weighting schemes \emph{per se}.

\subsection{Community Detection}

As discussed in the introduction, we adopt the standard definition of \emph{community}: a collection of nodes (users) within a network who are more densely connected to each other than with the rest of the network. Structural community detection is a well studied problem and several different methods and algorithms have been proposed. For a complete review of this subject we refer the reader to \cite{porter2009communities, fortunato2010community}. In this paper however we focus on a class of networks and communities that is far less studied, in particular we study networks which are both \textit{weighted} and \textit{directed} and communities within those weighted directed networks that can (but need not) \emph{overlap}. When selecting a detection algorithm we propose that all three (weight, direction, and overlap) are important for the following reasons. First, communication on Twitter occurs in a directed manner, with users broadcasting information to their followers. An undirected representation of the network would ignore this fact, and could lead to communities composed of users who do not actually share information. Second, we are interested in not just the structure of links but also in their function, and to capture this we use edge weightings which must be incorporated into the community detection process. Finally, since people can belong to multiple and possibly overlapping social (e.g., college friends, co-workers, family, etc.) and topical (e.g., a user can be interested in both cycling and politics and use the network to discuss the two topics with two different groups of users) communities, we are interested in finding \textit{overlapping} communities, rather than partitions of the weighted directed network. 
%For example, users can belong to multiple social groups such as college friends, %co-workers, family, etc. and these groups may but need not overlap. A user can also %belong to multiple topical communities, e.g., a user can be interested in both %cycling and politics and use the network to discuss the two topics with the two %different communities.

This last criterion in particular poses a problem because the majority of community detection algorithms developed so far are built to find partitions of a network and few are aimed at finding overlapping communities \cite{Aicher26062014,BaumesGKMP05,PalEtAl05,ZhaWanZha07,Gre07,PhysRevE.77.016107,Lancichinetti2009,PhysRevE.80.016105,Kovacs2010}. Among these methods, even fewer deal with directed or weighted networks. For example, the work of~\cite{PalEtAl05} on clique percolation can account for both features, but not at the same time. A recent method proposed in~\cite{LancichinettiPlos}, OSLOM (Order Statistics Local Optimization Method), is one of the first methods  able to deal with all of these features simultaneously. This method of Lancichinetti \emph{et al.} relies on a fitness function that measures the statistical significance of clusters with respect to random fluctuations, and attempts to optimize this fitness function across all clusters. 
Following~\cite{LancichinettiPlos}, the significance measure is defined as the probability of finding the cluster in a network without community structure. The null model used is highly similar to the one adopted by Newman and Girvan in \cite{newman2004finding} to define modularity, {\it i.e.,} it is a model that generates random graphs with a given degree distribution. The authors tested their algorithm on different benchmarks (LFR and Girvan-Newman) and real networks (such as the US air transportation network and a word association network), and compared its performance against the best algorithms
currently available ({\it i.e.,} the ones mentioned in the introduction), and found excellent results. Moreover, they showed that OSLOM is also able to recognize the absence, and not simply the presence, of community structure, by testing it on random graphs. This feature of the algorithm plays an important role in the analysis of real world networks, since it is not always the case that community structure is indeed present and it is therefore useful to be able to detect its absence too. 
Therefore, given its versatility and performance with benchmark networks, in this paper we used OSLOM to detect \emph{overlapping} communities present in our \emph{weighted} and \emph{directed} networks.
%For this paper we use OSLOM since it allowed us to detect \emph{overlapping} communities present in our \emph{weighted} and \emph{directed} network, and its authors showed that it performs very well on various types of artificial benchmark graphs and also on several real networks.

\subsection{The Initial Dataset and Network Construction}

The dataset for this study consisted of the tweets of 15,000 Twitter users over a 9 week period (from April 25th to June 25th 2011). The users are embedded in a network collected by performing a breadth-first expansion from a random seed user. In particular, once the seed user was chosen, the network was expanded to include his/her followers, but only included users considered to be `active' ({\it i.e.,} users who tweeted at least once per day over the past one hundred days). Network collection continued in this fashion by considering the active followers of the active followers of the seed, and so on until 15,000 users were added to the network. The only biasing steps in this procedure are the selection of the seed node and the filtering out of inactive users. However, because all of the community types we are interested in involve some aspect of the interaction between users, each other, and their content, this procedure provides a reasonable follower-followee network for use with the different question-based analyses.

Since our goal is to explore the functional communities of this network, we filter the network down to the subset of users that actively interact with each other ({\it e.g.,} via retweets and mentions). We do this by measuring what we call (incoming/outgoing) information events. We define an outgoing information event for a given user $u$ as either a mention made by $u$ of another user in the network, or a retweet of one of $u$'s tweets by another user in the network. The logic for this definition is as follows: if $u$ mentions a user $v$ this can be thought of as $u$ directly sending information to $v$, and if $u$ is retweeted by $v$ then $v$ received information from $u$ and rebroadcast it to their followers. In either case there was information outgoing from $u$ which affected the network in some way. Analogously, we define the incoming information event for $u$ as either being mentioned by a different user in the network, or as retweeting another user in the network.
%function and information share is important We then filter down this starting %network to include only users that [[what??]]. To do this 
%Since one of the community types we want to explore is based on the explicit interactions ( between users, we filter the dataset in order to take into account only users who make use of these kinds of features in their tweets. [[Seeems out of place]]
%We define an event of outgoing information for a given user $u$ as either a mention made by $u$ of another user in the network, or a retweet by another user of one of $u$'s tweets. 
%[[Switched the readers perspective]]When we mention someone we are in fact sending him some information, and when we are retweeted it means that the person that retweeted us has received some information from us and is sharing it. 
With (incoming/outgoing) information events defined we filtered the network by eliminating all users with less than a total of 9 outgoing \emph{and} incoming information events, {\it i.e.,} less than one information event per type per week on average. 
We then further restricted our analysis to the strong giant connected component of the network built from the (incoming/outgoing) information filtered set of users. %and whose link represent a user-follower relationship.
In this study the link is directed from the user to the follower because this is the direction in which information flows. Thus, for a pair of users $u$ and $v$, an edge $a_{v \to u}$ in the follower-followee network has weight 1 if user $u$ follows $v$, and 0 otherwise. The final network consists of 6,917 nodes and 1,481,131 edges.

\subsection{Activity-Based Communities and Transfer Entropy}
\label{sec:method-activity}

For the activity-based communities, we consider only the timing of each user's tweets and ignore any additional content. From this starting point, we can view the behavior of a user $u$ on Twitter as a point process, where at any instant $t$ the user has either emitted a tweet ($X_{t}(u) = 1$) or remained silent ($X_{t}(u) = 0$). This is the view of a user's dynamics taken in~\cite{darmon2013understanding} and~\cite{ver2012information}. Thus, we reduce all of the information generated by a user on Twitter to a time series $\{ X_{t}(u)\}$ where $t$ ranges over the time interval for which we have data (9 weeks in this case). Because status updates are only collected in discrete, 1-second time intervals, it is natural to consider only the discrete times $t = 1 \text{s}, 2 \text{s}, \ldots, $ relative to a reference time.

Operationally, we expect users to interact with Twitter on a human time scale, and thus the natural one-second time resolution is too fine, since most humans do not write tweets on the time scale of seconds. For this reason, we coarsen each time series by considering non-overlapping time intervals ten minutes in length. For each time interval, we record a 1 if the user has tweeted during that time interval, and a 0 if he or she has not. Thus, the new coarsened time series now captures whether or not the user has been active on Twitter over any given ten minute time interval in our data set. It should be noted that, as (most) users are not constantly tweeting, these time series are quite sparse. For this particular application, this sparsity appropriately reflects the behavior of the users. However, this sparsity may not be appropriate for all applications; anytime the following measure is used in practice the effects of binning, sparsity, and their role in the activity-based community structure should be considered. We can then compute the flow of information from a user  $u$ to a follower $f$ by computing the transfer entropy between their time series $X_{t}(u)$ and $X_{t}(f).$ See Appendix A for a detailed introduction to transfer entropy and its estimation from data.

 For the communities based on transfer entropy, we weighted each edge from a user $u$ to a follower $f$ by the estimated transfer entropy of the user $u$ on $f$, 
\begin{align}
	w_{u \to f}^{\text{TE}(k)} = \widetilde{\text{TE}}_{X(u) \to X(f)}^{(k)}. \label{Eqn-EW-activity}
\end{align}
% Transfer entropy is an information theoretic measure of \emph{directed} information flow. Since transfer entropy is a nonlinear generalization of Granger causality \cite{granger1963economic}, we assume---as is standard---a positive transfer entropy from the tweet history of a user $u$ to a follower $f$'s tweet history implies that this relationship is causal in the Granger sense.  Thus, communities detected in this way have members whose tweet histories are causally related in a Granger sense. %As a result, transfer entropy is often thought of as a measure of ``influence" in an information theoretic sense.
Transfer entropy is an information theoretic measure of \emph{directed} information flow. We assume---as is standard---a positive transfer entropy from the tweet history of a user $u$ to $X(f)$ implies a reduction in uncertainty in the activity of the follower, given the information contained in $X(u)$, while removing the information already contained in $X(f)$. This provides an information theoretic framework in which we can capture communities with activity-based predictive capacity between users or users with similar activity profiles. We call this relation ``APC" (activity-based predictive capacity).

 We computed the transfer entropy on each coarsened time series with lag $k$ ranging from 1 to 6, this corresponds to a lag of ten minutes to an hour. The choice of lag must balance a trade-off between additional information and sparsity of samples: as we increase the lag $k$, we account for longer range dependencies, but we also decrease the number of samples available to infer a higher dimensional predictive distribution.  Interestingly, as we will show later, the underlying communities resulting from the different lags have similar structure.  See \nameref{S1_Text} for a discussion of these issues.

It should be noted that according to~\cite{ver2012information} a positive transfer entropy between $X(u)$ and $X(f)$  indicates that $u$ ``influences" $f$, or that $u$ and $f$ share a common influencer. Similarly, since transfer entropy is a nonlinear generalization of Granger causality \cite{granger1963economic}, it is common to assume a positive transfer entropy between a user $u$ and a follower $f$ implies the relationship is causal in the Granger sense. However, we are skeptical whether this measure truly captures social influence in its entirety, or even causality in the case of online social networks. So instead we simply treat this weighting as a way to explicitly quantify APC between users.

As an aside, while we are skeptical that this measure can capture social influence, later in this paper we show that this information theoretic measure agrees with other concepts of influence such as the Forbes list of ``Top 10 Social Media Influencers" and corroborates with the so-called strength of weak ties~\cite{granovetter1973strength}. Even so, we do not explicitly treat transfer entropy---and we do not believe it should be treated without further investigation---as a quantification of social influence or causality. Instead this measure should be treated merely as a way to quantify APC between users.%, {\it i.e.,} a reduction in uncertainty of whether a follower $f$ will be active or not given the tweet history of a user $u$

To the best of our knowledge, this is the first use of transfer entropy for community detection in online social networks. Various other information theoretic approaches have been used successfully to analyze online social networks, \emph{e.g.,} to gain insight into local user behavior~\cite{darmon2013understanding}, to detect communities based on \emph{undirected} information flow~\cite{darmon2013detecting}, and to perform network inference and link prediction~\cite{ver2012information}.

\subsection{Topic-Based Communities and Hashtag Weighting}
\label{sec:method-topic}

In contrast to the activity-based approach, the topic-based (or topical) communities, \emph{i.e.,} communities defined by the topics users discuss, rely on the \emph{content} of a user's interactions and ignore their temporal components. In a topical community, users are defined to be a member of a community if they tweet \emph{about} similar topics as the other members of the community. 
%Another kind of community is the one based on the content of the tweets, and relies on the idea of finding people that talk about the same things. 
In order to detect the topical communities, we weight the edges of the user-follower network through a measure based on the number of common hashtags between pairs of users. Hashtags are a good proxy for a tweet's content as hashtags are explicitly meant to be keywords indicating the topic of the tweet. Moreover they are widely used and straightforward to detect.

To this end, we characterize each user $u$ by a vector $\vec{h}(u)$ of length equal to the number of unique hashtags in the dataset, and whose elements are defined as
\begin{equation}
h_i(u) = \phi_i(u)\log{ \frac{N}{n_i} },
\end{equation}
where $\phi_i(u)$ is the frequency of hashtag $i$ occuring in user $u$'s tweets, $N$ is the total number of users, and $n_i$ is the number of users that have used the hashtag $i$ in their tweets. This adapted term frequency--inverse document frequency (tf-idf) measure \cite{salton_introduction_1983} captures the importance of a hashtag in the users's tweets through the first factor, but at the same time smooths it through the second factor by giving less importance to hashtags that are too widely used (as $\frac{N}{n_i}$ approaches one, its logarithm approaches zero).

For the topical communities we weight each directed edge from a user $u$ to a follower $f$ with the cosine similarity of their respective vectors $\vec{h}(u)$ and $\vec{h}(f)$:
\begin{align}
	w_{u \to f}^{\text{HT}} = \frac{\vec{h}(u) \cdot \vec{h}(f)}{\left|\left|\vec{h}(u)\right|\right| \ \ \left|\left|\vec{h}(f)\right|\right|}. \label{Eqn-EW-topic}
\end{align}
This weight captures the similarity between users in terms of the topics discussed in their tweets.

\subsection{Interaction-Based Communities and Mention / Retweet Weighting}
\label{sec:method-interaction}

Retweets and mentions are two useful features of Twitter networks which can be used to track information flow through the network.
%A way of tracking the flow of information through users is by considering two useful features of this social network: mentions and retweets. 
With mentions, users are sending direct information to other users and with retweets users are rebroadcasting information from a user they follow to all of their followers.
%information from a user has been captured by a follower and shared with his/her own followers. 
This type of information flow defines a community in a much different way than transfer entropy. Instead of defining communities by the loss of uncertainty in one user's tweeting history based on another's, we define interaction-based communities by weighting the user-follower network with a measure proportional to the number of mentions and/or retweets between users. 
% We can therefore define interaction-based communities by weighting the user-follower network with a measure proportional to the number of mentions and retweets between users. 
% For the interaction-based communities we consider three weighting schemes: proportional retweets,
We define three weighting schemes. We first consider the number of tweets of a user $u$ that were rebroadcast by a follower $f$, indicating a flow of information from $u$ to $f$. Since different users produce different amounts of tweets and retweets, in order to take into account the relative importance of this measure we normalize it by dividing over the total number of retweets made by $f$,
\begin{equation}
w_{u \to f}^{\text{R}}=\frac{\mbox{\# retweets of }u \mbox{ by }f}{\mbox{\# total retweets made by }f},
\end{equation}
We then consider the number of mentions of $f$ made by user $u$. To account for the fact that some users/accounts are very popular and are often mentioned by so many other users that the flow of information from the latter to the former is flushed out, we normalize this measure by dividing over the total number of mentions received by $f$.
\begin{equation}
w_{u \to f}^{\text{M}} = \frac{\mbox{\# mentions of }f \mbox{ by }u}{\mbox{\# total mentions of }f},
\end{equation}
Finally, we define the mention-retweet proportion as the arithmetic mean of the two measures just defined,
%we weight each edge from a user $u$ to a follower $f$ through a combination of proportional mentions ($pM$):
% In more details, for each couple of user-follower $u$ and $f$, we use the arithmetic mean of the two following numbers:
%\begin{equation}
%w_{u \to f}^{\text{M}} = pM = \frac{\mbox{\# mentions of }f \mbox{ by }u}{\mbox{\# %total mentions of }f}
%\end{equation}
\begin{align}
	w_{u \to f}^{\text{MR}} = \frac{(w_{u \to f}^{\text{R}}+w_{u \to f}^{\text{M}})}{2}. \label{Eqn-EW-interaction}
\end{align}

%	w_{u \to f}^{\text{MR}} = \frac{1}{2}\left(\frac{\mbox{\# mentions of }f %\mbox{ by }u}{\mbox{\# total mentions of }f} + \frac{\mbox{\# retweets of }u \mbox{ by }f}{\mbox{\# total retweets made by }f}\right).

\section{Results and Discussion}
In this section we show the importance and usefulness of a multifaceted approach to community detection in online social networks. We begin by showing that the communities emerging from the different weightings of the structural network  quantitatively differ both at the macroscopic ({\it e.g.,} number of communities and their size distribution) and microscopic ({\it e.g.,} specific memberships, comemberships) scale in interesting ways. Finally, in order to provide a practical illustration of the utility of this question-oriented multifaceted approach, we present several concrete examples of multifaceted community memberships discovered with this method. We will show examples both at the community and individual user level.

\subsection{Comparing Aggregate Statistics of Community Structure}

We begin by examining the overall statistics for the communities inferred by OSLOM using the weightings defined in the previous sections. The number of communities by community type is given in Table~\ref{Table-comm_count}. We see that the topic- and interaction-based networks admit the most communities. The activity-based network admits the fewest communities.  One advantage of OSLOM over many other community detection algorithms is that it explicitly accounts for singleton `communities': those nodes who do not belong to \emph{any} extant communities. This is especially important when a network is collected via a breadth-first search, as in our network, where we begin from a seed node and then branch out. Such a search, once terminated, will result in a collection of nodes on the periphery of the network that may not belong to any community in the core.

% See here
% 	http://arxiv.org/pdf/1202.2684v2.pdf
% for possible useful references on core-periphery networks.

We see in Table~\ref{Table-comm_count} that the topic- and interaction-based communities have the most singletons. This result for the interaction-based community is partially an artifact of the retweet/mention weighting: 717 of the users were disconnected from the network by how the weights were defined, resulting in `orphan' nodes which we have included in the collection of singletons for all of our analyses. However, even after accounting for this artifact, the interaction-based network still has the most non-orphan singletons. This seems to indicate that a large fraction of the 6917 (nearly 25\%) do not interact with each other in a concerted way that would mark them as a community under our interaction-based definition. This agrees with a result previously reported in~\cite{romero2011influence} about how most users passively interact with incoming information on Twitter.

\begin{table}[ht]
	\caption{Number of non-singleton communities and singletons by community type: S(tructural), A(ctivity-based), T(opic-based), and I(nteraction-based).}
	\centering
	\begin{tabular}{| c | c | c |}
		\hline Community Type & \# of Communities & \# of Singletons \\ \hline
		% Structural & 201 \\
		% Activity, Lag 1 & 101 \\
		% Activity, Lag 2 & 99 \\
		% Activity, Lag 3 & 106 \\
		% Activity, Lag 4 & 105 \\
		% Activity, Lag 5 & 107 \\
		% Activity, Lag 6 & 106 \\
		% Topic & 289 \\
		% Interaction & 252 \\ \hline
		S & 201 & 308 \\
		A, Lag 1 & 101 & 951 \\
		A, Lag 2 & 99 & 600 \\
		A, Lag 3 & 106 & 611 \\
		A, Lag 4 & 105 & 668 \\
		A, Lag 5 & 107 & 632 \\
		A, Lag 6 & 106 & 642 \\
		T & 289 & 1064 \\
		I & 252 & 2436  \\ \hline
	\end{tabular}
	\label{Table-comm_count}
\end{table}

Next we consider the distribution of community sizes across the community types. The complementary cumulative distribution of community sizes is given in Figure~\ref{Fig-community_size_distribution}. Note that both axes are plotted on log-scales. Thus, for a fixed community size $s$, Figure~\ref{Fig-community_size_distribution} shows the proportion of communities of size greater than $s$ for each community type. We see that the community distributions have longer tails for the non-structural networks, and that the interaction-based network has the longest tail.
%The largest communities for the structural, activity-based, topic-based, and interaction-based networks have 198, 358, 338, and 811 members, respectively.
Note that the activity-based communities, using transfer entropy estimated with varying lags, seem to converge on a similar large-scale community structure around lag 3. That is, the communities based on lag 1 and lag 2 transfer entropies are generally larger, and these communities resolve into smaller communities as the lag increases beyond 2. The distribution of community sizes for lag larger than 2 is insensitive to the lag.
Most importantly, we see that the distributions of community sizes differ across the community types, the large-scale community structure is highly dependent on the particular question posed.

\begin{figure}[ht]
  \centering
%\includegraphics[width=1\textwidth]{cdf_comm_sizes}
\caption{\textbf{The proportion of communities greater than $s$ in size, across the different community types.} Note the logarithmic scale on the horizontal and vertical axes.}
\label{Fig-community_size_distribution}
\end{figure}

% Next, we compare the number of users which belong to more than one community. Figure~\ref{Fig-overlap_plot} shows the number of users belonging to 2, 3, or 4 communities. We see that as the number of mixed membership communities increases, the number of users with that number of mixed memberships decreases. This is especially true for the activity-based community \textbf{TK: speculate on what this means? Or save for the results section?}.  In addition, \textbf{TK: mention the 5, 6, and 7 cases, not included in the figure}. This corresponded to \textbf{TK: investigate which users are the high-overlap and what communities they belong to.}

% % The user with a structural overlap of 7 communities was 1630261,
% %	https://twitter.com/marksilva

% \begin{figure}[ht]
%   \centering
% \includegraphics[width=0.50\textwidth]{Figures/overlap_by_type.pdf}
% \caption{The number of users belonging to 2, 3, or 4 communities, by community type.}
% \label{Fig-overlap_plot}
% \end{figure}

\subsection{Comparing Community Structure with Normalized Mutual Information}

In the previous section, we saw that the large scale statistics of the communities were highly dependent on the type of community under consideration. However, macroscale network statistics do not account for differences in community structure that result from operations such as splitting or merging of communities. Moreover, this view does not account for which users belong to which communities, and in particular which users belong to the same communities across community types. To answer this question, we invoke methods for the comparison of clusters: given two different clusterings of nodes into communities, how similar are the two clusters? The standard approach to answering this question is to define a metric on the space of possible partitions.  
Because we detect coverings rather than partitions, standard cluster comparison metrics like variation of information~\cite{meilua2003comparing} are not appropriate. Instead, we use a generalization of variation of information first introduced in~\cite{Lancichinetti2009}, the normalized mutual information. The normalized mutual information stems from treating clustering as a community identification problem: given that we know a node's community membership(s) in the first covering, how much information do we have about its community membership(s) in the second covering, and vice versa? Consider the two coverings $\mathcal{C}_{1}$ and $\mathcal{C}_{2}.$ We think of the community memberships of a randomly chosen node in $\mathcal{C}_{1}$ as a binary random vector $\mathbf{X} \in \{0, 1\}^{|\mathcal{C}_{1}|}$ where the $i^{\text{th}}$ entry of the vector is 1 if the node belongs to community $i$ and 0 otherwise. Similarly, $\mathbf{Y} \in \{ 0, 1\}^{|\mathcal{C}_{2}|}$ is a binary random vector indicating the community memberships of the node in $\mathcal{C}_{2}$. Then the normalized mutual information is defined as
\begin{align}
	\text{NMI}(\mathcal{C}_{1}, \mathcal{C}_{2}) = 1 - \frac{1}{2} \left( \frac{H[\mathbf{X} | \mathbf{Y}]}{H[\mathbf{X}]} + \frac{H[\mathbf{Y} | \mathbf{X}]}{H[\mathbf{Y}]}\right)
\end{align}
where $H[\cdot]$ denotes a marginal entropy and $H[\cdot | \cdot]$ denotes a conditional entropy. The normalized mutual information varies from 0 to 1, attaining the value of 1 only when $\mathcal{C}_{1}$ and $\mathcal{C}_{2}$ are identical coverings up to a permutation of their labels. See the appendix of~\cite{Lancichinetti2009} for more details.

We considered the normalized mutual information between the communities inferred from the structural network and the networks weighted with lag 1 through 6 transfer entropies, hashtag similarity, and mention, retweet, and mention-retweet activity. The resulting $\text{NMI}(\mathcal{C}_{i}, \mathcal{C}_{j})$ are shown in Figure~\ref{Fig-compare_coverings}. Note the block diagonal structure in Figure~\ref{Fig-compare_coverings}, which indicates that coverings are most similar within a question category. For example, the activity-based transfer entropy coverings are more similar to each other than to any of the other coverings. Similarly for the interaction-based mention, retweet, and mention-retweet coverings. This point may seem obvious, but the fact that the different weightings within a question category result in similar community structure indicates that each covering is capturing true, latent properties of the social network. Interestingly, the coverings resulting from the different weightings are all more similar to each other than to the structural covering from the unweighted network. Also note that the covering based on the hashtag similarities are different from all of the other weight-based coverings. In agreement with the results reported in the previous section, we see that the activity-based communities share similar structure for lags greater than 2. Because of these two results, in the remainder of the paper, we focus on the activity-based communities inferred using the lag-4 transfer entropy.

\begin{figure}[ht!]
  \centering
%  \includegraphics[width=0.50\textwidth]{Figures/nmi_singleton}
  \caption{\textbf{The normalized mutual information between the coverings inferred from the different community types.}
%Community type 0 corresponds to the structural communities, community types 1 through 6 correspond to the activity-based communities with lag 1 through 6 transfer entropies, community type 7 corresponds to the topic-based communities, and community types 8, 9, and 10 correspond to the interaction-based communities using mentions, retweets, and both mentions and retweets. 
Values of normalized mutual information close to 1 indicate similarity in the community structure, while values close to 0 indicate dissimilarity. The normalized mutual information is computed with singletons and orphan nodes included. Note the block-diagonal structure, indicating the strong relationship between question type and community membership.}
\label{Fig-compare_coverings}
\end{figure}

Thus, we see that although the activity-based, interaction-based, and topic-based communities relied on the structural network, their community structure differs \emph{the most} from the community structure of the follower network. This agrees with the results from the previous section, and reinforces that the follower network is a necessary but not sufficient part of detecting communities characterized by properties beyond follower-followee relationships.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
%============================================================
% Old section on 'Comparing Edges Across Different Community Types'

% \subsection{Comparing Edges Across Different Community Types}

% We next explore how the edge weights defined by equations (\ref{Eqn-EW-activity}), (\ref{Eqn-EW-interaction}), and (\ref{Eqn-EW-topic}), and thus different forms of information flow, differ between community types. For a fixed community type, edges for a particular community may be partitioned into three sets: those from a user in the community to another user in the community (internal-to-internal), those from a user in the community to a user outside of the community (internal-to-external), and those from a user outside the community to a user inside the community (external-to-internal). See Figure~\ref{Fig-edge_types} for a schematic of this edge partitioning. For a meaningful community, we expect the distribution of weights within the community (internal-to-internal weights) to be different from the distribution of weights without the community (internal-to-external and external-to-internal).

% \begin{figure}[ht]
%   \centering
% \includegraphics[width=0.50\textwidth]{edge-types.eps}
% \caption{An example of the edges considered in determining the edge weight distribution for a given community (the focal community is in yellow). We focus on the internal-to-internal (red), internal-to-external (green), and external-to-internal (blue) edges. For a given focal community, all other edges (grey) are not considered.}
% \label{Fig-edge_types}
% \end{figure}

% As an example, Figure~\ref{Fig-dist_across_community} shows the distributions of hashtag-based weights for the largest community in the mention-retweet network. We see that the distribution of internal-to-internal hashtag weights has a longer tail than either the external-to-internal or internal-to-external hashtag weights, with edges within the community having higher weights than edges crossing the boundary of the community. Thus, while the community was defined in terms of interactions, we still see a shift in the distribution of topic-similarity.

% \begin{figure}[ht]
%   \centering
% \includegraphics[width=0.50\textwidth]{comm0_labels-hashtag_weights-mention-retweet-ecdf.pdf}
% \caption{The proportion of edges with a weight at least as large as the weight on the horizontal axis, across the types of edges described in Figure~\ref{Fig-edge_types}. The community is defined by user interactions, and the edge weights are determined by topic similarity. The dashed vertical lines indicate the median weight for each type of edge. Note the logarithmic scale on the horizontal axis.}
% \label{Fig-dist_across_community}
% \end{figure}

% \begin{figure}
%         \centering
%         \begin{subfigure}[b]{0.2\textwidth}
%                 \includegraphics[width=\textwidth]{labels-struc_weights-TE4-ecdf_by_type.pdf}
%         \end{subfigure}
%         \begin{subfigure}[b]{0.2\textwidth}
%                 \includegraphics[width=\textwidth]{labels-struc_weights-hashtag-ecdf_by_type.pdf}
%         \end{subfigure}
%         \begin{subfigure}[b]{0.2\textwidth}
%                 \includegraphics[width=\textwidth]{labels-struc_weights-mention-retweet-ecdf_by_type.pdf}
%         \end{subfigure}
%         \caption{Lorem ipsum.}
% \end{figure}

% This change in the tail of the distribution between edge types was typical of many of the community type / weight pairings. A useful summary statistic to quantify the change involves the median weights across the three types of edges, as demonstrated in Figure~\ref{Fig-dist_across_community}. In particular, by computing the ratio of the median weight for the internal-to-internal edges to the median weight for the internal/external-to-external/internal edges, we can quantify the ratio change in weight strength internal vs. external to a community. We computed this quantity for each of the top 100 largest communities defined by a particular community type (structure-based, activity-based, interaction-based, or topic-based), and report the median value across the 100 largest communities for each type in Table~\ref{Table-medians}. This statistic represents the typical ratio shift for each community type / weight pairing. Values greater than 1 indicate that the edge weights tend to be higher within the community, and values less than 1 indicate that the edge weights tend to be higher for those edges crossing the community boundary.

% \begin{table}
% 	\caption{The median value for the ratio of the median external/internal-to-internal/external weight to median internal-to-internal weight for the different community/weight pairings.}
% 	\centering
% 	\begin{tabular}{c | c | c  c  c  c}
% 		& & \multicolumn{4}{ c }{Community} \\ \hline
% 		\multirow{4}{*}{Weight} & & S & TE & MR & HT \\ \hline
% 		& TE & $0.0 / 0.0$ & $0.0 / 0.0$ & $0.0 / 0.0$ & $0.0 / 0.0$\\
% 		& MR & $0.0 / 0.0$ & $0.0 / 0.0$ & $0.0 / 0.0$ & $0.0 / 0.0$\\
% 		& HT & $0.0 / 0.0$ & $0.0 / 0.0$ & $0.0 / 0.0$ & $0.0 / 0.0$
% 	\end{tabular}
% \end{table}

% \begin{table}
% 	\label{Table-medians}
% 	\caption{The median value across the 100 largest communities for the ratio of the median internal-to-internal weight to the median external-to-internal / internal-to-external weight for the different community / weight pairings. Note: For mention-retweet weights, weight zero edges were excluded from the computation of the median. We indicate such cases with an asterisk.}
% 	\centering
% 	\begin{tabular}{c | c | c  c  c}
% 		& & \multicolumn{3}{ c }{Weight Type} \\ \cline{3-5}
% 		& & TE & MR & HT \\ \cline{2-5}
% 		\multirow{4}{*}{Community Type} & S & $0.96/0.94$& $1.7/2.1$*& $9.0/8.0$\\
% 		& A & $1.0/0.96$& $1.5/2.4$*& $24/17$\\
% 		& I & $0.83/0.86$& $3.2/4.4$& $10/8.5$\\
% 		& T & $0.9/0.89$& $2.4/2.6$*& $28/26$
% 	\end{tabular}
% \end{table}

% \begin{table}
% 	\caption{The median value across the 100 largest communities for the ratio of the median internal-to-internal weight to the median external-to-internal / internal-to-external weight for the different community / weight pairings. For each entry $a/b$ in the table, $a$ corresponds to median ratio value for edges external-to-internal, and $b$ corresponds to the median ratio value for edges internal-to-external . Community types correspond to S(tructural), A(ctivity-based), T(opic-based), and I(nteraction-based) communities. Weight types correspond to T(ransfer) E(ntropy), M(ention-)R(etweet), and H(ash)T(ag). Note: For mention-retweet weights, zero weight edges were excluded from the computation of the median. We indicate such cases with an asterisk.}
% 	\centering
% 	\begin{tabular}{c  c | c  c  c}
% 		& & \multicolumn{3}{ c }{Weight Type} \\ %\cline{3-5}
% 		& & TE & MR & HT \\ \cline{1-5}
% 		\multirow{4}{*}{Community} & S & $0.96/0.94$& $1.7/2.1$*& $9.0/8.0$\\
% 		\multirow{4}{*}{Type} & A & $1.0/0.96$& $1.5/2.4$*& $24/17$\\
% 		& I & $0.83/0.86$& $3.2/4.4$& $10/8.5$\\
% 		& T & $0.9/0.89$& $2.4/2.6$*& $28/26$
% 	\end{tabular}
% 	\label{Table-medians}
% \end{table}

% We see that for every weight type except transfer entropy, the weight on edges internal to the communities tend to be higher than on edges entering or exiting the communities, ranging from a factor of 1.5 times larger for the activity-based/mention-retweet pairing to a factor of 28 times larger for the topic-based/hashtag similarity pairing. As stated above, we expect this ratio to be high for community / weight pairings that match (e.g. considering mention-retweet weighting for interaction-based communities), and we see that this is the case for all but the activity-based / transfer entropy pairing. Moreover, for both the mention-retweet and hashtag weightings, the ratio is largest when they match with the interaction-based and topic-based communities, respectively.

% For all four community types, the transfer entropy tended to be higher for edges crossing community boundaries than for those internal to community boundaries. Recall that the transfer entropy $\text{TE}_{X(u) \to X(f)}$ quantifies the reduction in uncertainty about a follower $f$'s activity from knowing the activity of a user $u$. This result therefore implies that, in terms of prediction, it is more useful to know the time series of a user followed outside of the community compared to a user followed inside of the community. Thus, in an information theoretic sense, we see that novel information useful for prediction is more likely to flow \emph{across} community boundaries than \emph{within} community boundaries.

% Note that the communities defined by the follower network do tend to have higher edge weights internal compared to across community boundaries. Thus, we do see that the structural communities capture some information about the functional behavior of communities of users in terms of topics and interaction. However, the ratio is not as large as when we explicitly seek out communities based on a particular type of functional community. This again emphasizes the importance of properly formulating the goal of a community detection study in the context of online social networks.

% \begin{tabular}{cc|ccc}
% & & \multicolumn{3}{ c| }{Weight Type} \\ \cline{3-5}
% & & 2 & 3 & 5  \\ \cline{1-5}
% \multicolumn{1}{ c| }{\multirow{4}{*}{Powers} } &
% \multicolumn{1}{ c| }{504} & 3 & 2 & 0    \\ \cline{2-5}
% \multicolumn{1}{ c|  }{}                        &
% \multicolumn{1}{ c| }{540} & 2 & 3 & 1     \\
% \multicolumn{1}{ c| }{gcd} & 2 & 2 & 0 \\ \cline{2-5}
% \multicolumn{1}{ c  }{}                        &
% \multicolumn{1}{ c| }{lcm} & 3 & 3 & 1 \\ \cline{1-5}
% \end{tabular}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
%============================================================

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
%============================================================
% New section on 'Comparing Edges Across Different Community Types'

\subsection{Comparing Edges Across Different Community Types}

Any covering determined by OSLOM induces a natural partition of the edges in a directed network. In particular, let $u$ and $f$ be two users in the network, and let $M_{u}$ and $M_{f}$ be their community memberships. Then any edge $e_{u \to f}$ can be partitioned into one of three classes by
\begin{align}
	T(e_{u \to f}) = \left\{ \begin{array}{ll}
		\text{Inter-edge} &: \ \ \ M_{u} \cap M_{f} = \emptyset \\
		\text{Intra-edge} &: \ \ \ M_{u} = M_{f}\\
		\text{Mixed-edge} &: \ \ \ \text{ otherwise} \\
	\end{array}\right. \label{Eqn-edge_types}.
\end{align}
In words, an inter-edge connects two users who share no community memberships, an intra-edge connects two users who each belong to the same communities, and a mixed-edge connects two users who share some, but not all, community memberships. Thus, inter-edges cross community boundaries, intra-edges lie within community boundaries, and mixed-edges lie at the borders of community boundaries. See Figure~\ref{Fig-edge_types} for a schematic of this edge partitioning.

\begin{figure}[!h]
	\centering
%	\includegraphics[width=0.8\textwidth]{edge-types}
	\caption{\textbf{A schematic of how, given a covering, the edges of the network can be partitioned using (\ref{Eqn-edge_types}) into inter-edges, intra-edges, and mixed-edges.} Inter-edges (red dashed) cross community boundaries. Intra-edges (blue solid) remain inside community boundaries. Mixed-edges (purple dotted) both remain in and cross community boundaries due to overlap in community membership. Each column corresponds to the same collection of weights, but partitioned using a different covering. Each row corresponds to the same covering, but for the different weights.}
	\label{Fig-edge_types}
\end{figure}

%\begin{table}
%	\caption{The percentage of intra-, inter-, and mixed-edges associated %with the coverings for each of the four community types.}
%	\centering
%	\begin{tabular}{l | r r r}
%		Community Type & Intra & Inter & Mixed \\
%		\hline
%		Structural & 7.5 & 87.0 &  5.5 \\
%		Activity-based & 10.7 & 81.9 & 7.4 \\
%		Topic-based & 7.3 & 89.0  & 3.7 \\
%		Interaction-based & 42.3 & 47.9 & 9.8
%	\end{tabular}
%\end{table}

Each community type (Structural, Activity-based, Topic-based, Interaction-based) induces a different partition of the edges, and each edge type (Transfer Entropy, Hashtag, Mention-Retweet) induces a different distribution of weights. That is, let $W_{u \to f}$ be the weight on an edge $E_{u \to f}$ chosen uniformly at random from the network, and compute
\begin{align}
	P(W_{u \to f} \leq w_{u \to f} | T(E_{u \to f}) = t),
\end{align}
the empirical distribution over the edge weights conditioned on the edge type $t$ being one of inter, intra, and mixed. The densities associated with these distributions are shown in Figure~\ref{Fig-distributions_by_types}. By considering how the weights vary conditional on the edge type, we can explore whether and how each of the follower-, interaction-, activity-, and topic-based communities define functional units within the network. For example, if users interact more-or-less independently of the topics they discuss, then the distributions of the interaction-based / topic-based edge weights should be independent of the edge type determined from the topic-based / interaction-based communities. By contrast, if users tend to interact mostly with those users who discuss similar topics, then the edge weight distributions should vary with the edge type.
%For meaningful community structure, we expect the distribution of edge weights to differ with the edge type $t$. If the community structure were arbitrary, the edge weights would be independent of the edge type, and all three conditional distributions would be identical.
\begin{figure}[!h]
	\centering
%	\includegraphics[width=1\textwidth]{densities-edges}
	\caption{\textbf{The density of edge weights for different community types (rows) and weight types (columns).} The red,  blue, and purple values below each collection of densities indicate the median of weight on intra-, inter-, and mixed-edges, respectively.}
	\label{Fig-distributions_by_types}
\end{figure}

Each \emph{column} of Figure~\ref{Fig-distributions_by_types} demonstrates how the density of weights change with the community type used to induce the partition. For example, the second column shows how the density of hashtag weights change based on the community partition. In general, the densities differ in non-trivial ways across the edge types and coverings. However, we see that the medians of the distributions provide a useful summary statistic. Under each collection of density functions, we list the median value of the inter, intra, and mixed-edges in red, blue, and purple, respectively. Unsurprisingly, we see that the greatest difference between the distributions occurs when we consider matching Community-type / Weight-type pairs, since the communities are determined based on the corresponding weights. However, we also see differences in the distributions when the Community-type / Weight-type pairs do not match. For example, for the covering corresponding to the activity-based communities, the hashtag weights tend to be higher for edges internal to communities than between communities. Similarly, for the covering corresponding to the topic-based communities, the transfer entropy weights tend to be higher on edges within (intra) and between (inter) communities, and lower for edges between members with multiple, non-identical memberships (mixed).

We also note that the distribution of transfer entropy weights always tend to be higher for edges crossing community boundaries (inter- or mixed-edges) compared to those edges within community boundaries (intra-edges). This is a property not exhibited by either the hashtag or mention-retweet weights, independent of the covering used to partition the edges. Moreover, for all but the activity-based covering, the weights of mixed-edges tend to be highest overall.  Recall that the transfer entropy $\text{TE}_{X(u) \to X(f)}$ quantifies the reduction in uncertainty about a follower $f$'s activity from knowing the activity of a user $u$. This result therefore implies that, in terms of prediction, it is more useful to know the time series of a user followed outside of the community compared to a user followed inside of the community, and even more useful to know the time series of a user that shares some, but not all, of the same community memberships. Thus, in an information theoretic sense, we see that novel information useful for prediction is more likely to flow \emph{across} community boundaries than \emph{within} community boundaries.

% \subsection{Demonstration of the Question-Oriented Approach}
%
% Next, we demonstrate a particular instance of a question-oriented approach. Suppose we were interested in tracking where conversations occur in a social network. That is, we want to track groups of individuals who interact more with each other than with users outside of their group. For example, we might wish to select a seed group of individuals in order to spread a message to a subpopulation of a social network. We now demonstrate how the performance on this tracking problem depends on the community type under consideration.
%
% % * We want to track *where* conversations are occurring: amongst what group of people.
%
% % * This motivates using the interaction-based communities.
%
% The data set was divided into two disjoint time periods: from 9am April 25th 2011 to 9am May 23rd 2011 (28 days) and from 9am May 23rd 2011 to 9am June 25th 2011 (33 days). We then constructed the three weighted networks (the structural network is unchanged) using the activity, retweets, mentions, and hashtags from the first time period, as described in the methodology section. Using the coverings inferred by OSLOM for the weighted network, we define the inside and outside of a community in the same way as depicted in Figure~\ref{Fig-edge_types}, where now we consider mixed-type edges to be internal. Based on this partitioning of the edges, we then track how many of the retweets / mentions in the second time period fall inside vs outside of the communities. The percentages of retweets and mentions that occur internal to each of the community types are given in Table~\ref{Tab-mentionretweets}.
%
% \begin{table}
% 	\caption{The percentage of retweets and mentions that occur internal to communities for each of the four community types.}
% 	\centering
% 	\begin{tabular}{l | c c}
% 		Community Type & Percentage of Retweets Internal & Percentage of Mentions Internal \\
% 		\hline
% 		Structural & 47.5 & 70.9 \\
% 		Activity-based & 54.7 & 75.6 \\
% 		Topic-based & 49.4 & 66.8  \\
% 		Interaction-based & \textbf{67.2} & \textbf{84.2}
% 	\end{tabular}
% 	\label{Tab-mentionretweets}
% \end{table}
%
% Let $I_{c}$ be the number of conversations (defined as a retweet or mention) occuring internal to community $c$, and let $|\mathcal{C}|_{c}$ be the size of community $c$. Finally, let $N$ be the total number of conversations, both internal and external, involving the nodes. An alternative scoring function is then
% \begin{align}
% 	\frac{1}{N}\sum_{c} \frac{I_{c}}{|\mathcal{C}_{c}|}.
% 	\label{conversation-metric}
% \end{align}
% That is, this measures the average number of internal conversations per user in a community. This will be maximized when the communities are small and the number of internal conversations are large compared to the total number of conversations.
%
% \begin{table}
% 	\caption{The metric (\ref{conversation-metric}) for the four community types, computed using the held-out data.}
% 	\centering
% 	\begin{tabular}{l | c c}
% 		Community Type & Retweets & Mentions \\
% 		\hline
% 		Structural & 0.0289 & 0.0344 \\
% 		Activity-based & 0.0793 & 0.0645 \\
% 		Topic-based & 0.1031 & 0.1020  \\
% 		Interaction-based & 0.0690 & 0.0977
% 	\end{tabular}
% 	\label{Tab-mentionretweets2}
% \end{table}
%
% \begin{table}
% 	\caption{The value of the conversation metric proposed by Elisa, averaged over all of the communities in a given covering.}
% 	\centering
% 	\begin{tabular}{ l | c c}
% 		Community Type & Mentions & Retweets \\
% 		\hline
% 		Structural & 2.9347 & 0.4734 \\
% 		Activity-based & \textbf{3.3893} & 0.5173 \\
% 		Topic-based & 2.5944 & 0.5580 \\
% 		Interaction-based & 2.1984 & \textbf{1.1069}
% 	\end{tabular}
% \end{table}

%\subsection{Qualitative Analysis of Community Memberships Across Types}
%\subsection{Answering the Questions}
\subsection{Uncovering the Multifacetedness of Community Memberships}

%As demonstrated by~\cite{good2010performance} in the context of modularity maximization-based community detection, an exponential number of nearby partitions may exist that nearly maximize an objective function used to measure the goodness-of-fit of a graph partition used for community detection. Because of this and related issues, it is always wise to perform some sort of qualitative study of the communities returned by any  community detection algorithm to verify their meaningfulness with respect to the scientific question at hand. In this section, we consider a collection of communities in such a study.

In the previous sections we showed that the communities emerging from the different weightings of the structural network quantitatively differ both at the macroscopic and at the microscopic scale. Here, we present some concrete examples of different community membership, in order to provide a practical illustration of the utility of using a multifaceted approach to community detection. We explore this first on a community level and then at the individual level.

In the topic-based communities, we found a single community consisting of 83 users who tweet about environmental issues and frequently use hashtags such as \#green, \#eco and \#sustainability. We also found a different community of 47 users who tweet about small businesses and entrepreneurship, using hashtags such as \#smallbiz, \#marketing and \#enterpreneur. In both cases, almost all members of these topic-based communities are not found in the same community in the other networks \emph{e.g.,} interaction- or activity-based, indicating that while these people talk about the same things and can therefore be considered a community based on their content, they do not strongly interact with each other nor behave the same, and so belong to different social groups with respect to interactions and behavior. This illustrates that the topics discussed by these users only define one facet of the users complex social network.

Another interesting example is a community whose topics tend to focus on Denver and Colorado. These users do not belong to the same community in the interaction-based network, but most of them do belong to the same community in the activity-based network. This indicates that these users react to the same events and issues regarding Colorado and are therefore strongly connected in the topic-based and activity-based networks, but at the same time they do not directly interact with each other and are therefore more loosely connected in the interaction-based networks, where they belong to different communities.

It is interesting to examine the intersection between this topic-based community and the overlapping activity-based communities and explore which users in the intersection of these community types have the highest APC. Users with the highest APC in an activity-based community would provide the highest reduction in uncertainty on average about that communities activity or inactivity on Twitter. Interestingly, among the highest APC users in these communities---those with highest transfer entropy on average---we find $@$Colorado, which is the state official Twitter account, $@$ConnectColorado, a page created to connect Coloradans, and the CBS Denver account, a popular news agency. This means that these accounts have high activity-based predictive capacity in terms of their followers' activity on Twitter. This is not surprising as these activity-based communities heavily overlapped with the topic-based communities that discuss Colorado (mentioned above) and these accounts provide information on this topic. This provides a brief proof of concept that the APC measure makes sense and suggests this could be a useful measure for identifying individuals who possess high activity-based predictive capacity for a communities activity on a social media network. However, more work needs to be done to quantify this more fully.

At the individual-based level, we also found interesting examples of multifaceted community membership, which show that asking multiple questions leads to finding different kinds of communities a user belongs to. For example, the user $@$JohnReaves belongs to two different topic communities: one about health care and the other about `innovation' and `creativity'. There was a $~70\%$ overlap between the innovation and creativity topic community, the interaction-based, and the activity-based community the user is in, whereas there is almost no overlap between the latter two and the healthcare community. This means that the user interacts with and behaves like the people talking about innovation and creativity, but even though he also talks about healthcare he does not interact with (nor behave like) the people talking about that.
Another interesting example is given by user $@$jenajean. She  belongs to two different topic communities: she talks about NASA and space but she does not interact nor behave like people belonging to that topic community, whereas she also talks about leadership, and the people she interacts with highly overlap with the people belonging to the topic-based community on leadership for which she belongs to.
Lastly, $@$rajean, $@$Tekee, $@$Kimbirly and $@$mamamonroe are examples of users belonging to the topic community talking about Denver and Colorado. The activity-based community they belong to highly overlaps with the topic community (therefore they behave like the people that talk about Colorado), but they all belong to different interaction-based communities, each of which does not overlap in more than two users with the topic community.

\section{Conclusion and Future Work}

\label{sec:conc}

% What have we done:
% ==================

%In this study, we have demonstrated that the communities observed in online social %networks are highly question-dependent 
%[[Joshua:maybe reword this sentence to explicitly say what we mean by question-dependent", might be a little confusing]]
%, and that different definitions of communities reveal different relationships between users. More importantly, we have shown that these different views of the network are not revealed by using the structural network alone. We found that community structure differs across community types on both the macro (e.g. number of communities and their size distribution) and micro (e.g. specific memberships, comemberships) scale.

In this study, we have demonstrated that the communities observed in online social networks are highly question-dependent. The questions posed about a network \emph{a priori} have a strong impact on the communities observed.  Moreover, using different definitions of community reveal different and interesting relationships between users. More importantly, we have shown that these different views of the network are not revealed by using the structural network or any one weighting scheme alone. By varying the questions we asked about the network and then deriving weighting schema to answer each question, we found that community structure differed across community types on both the macro ({\it e.g.,} number of communities and their size distribution) and micro ({\it e.g.,} specific memberships, comemberships) scale in interesting ways.

%We have also demonstrated that boundaries between communities represent meaningful internal/external divisions, with conversations and topics tending to be most highly concentrated within communities than without. We found this to be the case even when the communities were defined by a different criteria from the edge weights. [[Wasn't this the opposite in the transfer entropy case? Maybe I am remembering wrong. If so maybe we can spend a few sentences explaining why this is so leading into the next paragraph]]

To verify the validity of these communities we demonstrated that boundaries between communities represent meaningful internal/external divisions. In particular, conversations ({\it e.g.,} retweets and mentions) and topics ({\it e.g.,} hashtags) tended to be most highly concentrated within communities. We found this to be the case even when the communities were defined by a different criterion from the edge weights under study.

% At first glance the boundaries defined by the communities in the activity-based network (those weighted with transfer entropy) seemed less meaningful. However, upon further investigation our novel use of transfer entropy for the detection of activity-based communities\footnote{It should be noted that while in previous work on online social media~\cite{ver2012information}, transfer entropy was found useful for identifying influence between users, it has not to the best of our knowledge been used to aid in the identification of communities.} brought to light a very interesting fact about this social network: influence tends to be higher across community boundaries than within them. This result echos the `strength of weak ties' theory from~\cite{granovetter1973strength}, which was supported empirically in~\cite{grabowicz2012social}. This means that our novel use of transfer entropy not only defines boundaries that are meaningful divisions between communities but it helps illustrate that influential users of a community need not be a member of that community.

% Removed the footnote.

At first glance the boundaries defined by the activity-based communities derived from the transfer entropy weighting seemed less meaningful. However, upon further investigation our novel use of transfer entropy for the detection of activity-based communities highlighted an important fact about this social network: information transmission tended to be higher across community boundaries than within them. This result echos the `strength of weak ties' theory from~\cite{granovetter1973strength}, which has found empirical support in online social networks~\cite{grabowicz2012social}. This means that our use of transfer entropy not only defines boundaries that are meaningful divisions between communities but also illustrates that users who have a strong APC with a community need not be a member of that community.

%Start of future work**
Our findings may have important implications to a common problem in social network analysis: identification of influential individuals---but further work must be carried out.
Many network measures of influence are based on the various types of centrality (degree, betweenness, closeness, eigenvector, etc.)~\cite{newman2009networks}. Most centralities depend explicitly on the structure of the network under consideration. But we have seen in our study that the structural network only highlights one of many possible ways that users interact with online social media.
Thus, a na\"ive application of centrality measures to a structural network may be answering a different question than the one motivating influence detection. For example, a user exhibiting high closeness centrality based on the structural network may be able to make a message visible to most other users in a social network, but this does not mean that those other users are likely to respond to or propagate that message. The importance of correctly framing network measures of influence has been explored previously~\cite{kitsak2010identification}, and our work further highlights its importance.

Based on our preliminary results, we conjecture that weighted generalizations of these centrality measures using transfer entropy might lead to better insights about who is actually influential in an online social network. 
It is interesting to note for example that two of the Forbes ``Top 10 Social Media Influencers", happen to be in our network, \emph{viz.}, Ann Tran and Jessica Northey, and transfer entropy also quantified these two users as having two of the highest APC on average, i.e., there was a high reduction in uncertainty about their followers activity on Twitter given their tweet histories. While we do not believe this information theoretic measure can capture social influence in its entirety, 
% members, as categorized by transfer entropy. 
this suggests that this activity-based measure may be useful in finding influential members purely based on their temporal tweet history; even completely ignoring both tweet content and social status. However, a deeper analysis would need to be carried out to verify this finding.
In addition to exploring this phenomenon further, we plan to explore a broader selection of choices for both the transfer-entropy lag and tweet history time resolution. We believe that by doing an in-depth analysis of both of these parameters we can discover interesting activity-based communities that occur on much broader time scales.
%End of futre work**
  %based on methods for model selection~\cite{claeskens2008model}.

%Our work has introduced a novel use of transfer entropy for the detection of activity-based communities.

%Our transfer entropy results thus reflect that influence tends to be higher across community boundaries than within them. This result echos the `strength of weak ties' theory from~\cite{granovetter1973strength}, which has found empirical support in~\cite{grabowicz2012social}. In addition to exploring this phenomenon further, we plan to consider more rigorous choices of both the lag and time resolution based on methods for model selection~\cite{claeskens2008model}.

% * Defined four types of communities based natural questions one might ask about users in online social media.

% * Proposed three weightings to detect such communities.

% * Demonstrated that the community structure differed between weighting to weighting.

% Future Work:
% ============

% More with transfer entropy.
% 	Why did information tend to flow *across*, rather than within, community boundaries?

% Longitudinal study:
% 	How do the different types of communities change over time? Are activity-based communities more stable than interaction-based, etc.? For example, preliminary studies indicate that `conversations,' as defined by mentions and retweets, tend to move outside of structural communities over time.

%[[This paragraph needs to be recrafted a bit. It just reads a little confusing]]

%Our work has introduced a novel use of transfer entropy for the detection of activity-based communities. In previous work on online social media~\cite{ver2012information}, transfer entropy was found useful for identifying influence between users. Our transfer entropy results thus reflect that influence tends to be higher across community boundaries than within them. This result echos the `strength of weak ties' theory from~\cite{granovetter1973strength}, which has found empirical support in~\cite{grabowicz2012social}. In addition to exploring this phenomenon further, we plan to consider more rigorous choices of both the lag and time resolution based on methods for model selection~\cite{claeskens2008model}.

% Why Care? (i.e. impact):
% ========================

% What does this mean for researchers in online social media? Businesses?

% Using concepts like centrality to determine influence 
% 	* These metrics are based solely on the structural network.
% 	* Your *activity* may be more important than your *topology* in determining
% 	  your influence.
%[[While I agree with this next paragraph completely I am not sure we covered this topic enough to be the final paragraph of the conclussion or even in the conclusion. I need to think about this...]]

% More generally, our work demonstrates that asking the proper question is an unavoidable first step to community detection, and that the rich data sets available from

This work demonstrates the utility of a multifaceted question-oriented approach to community detection. This work shows that crafting \emph{several} facet-driven weighting schema, doing community detection for each weighting scheme and then comparing the similarities and differences across community types, is an unavoidable process for uncovering the complex---and often hidden---community structure present in online social networks. More generally, this work illustrates that without a clear definition of community---or even only using a \emph{single} definition of community---many rich and interesting communities present in online social networks remain invisible. Multifaceted question-oriented community detection can bring those hidden communities into the light.

\section*{Supporting Information}

% Include only the SI item label in the subsection heading. Use the \nameref{label} command to cite SI items in the text.

\subsection*{S1 Text}
\label{S1_Text}
{\bf Transfer entropy and its estimation from data.} Let $\{X_{t}\}$ and $\{ Y_{t}\}$ be two strong-sense stationary stochastic processes\footnote{Recall that a stochastic process is strong-sense stationary if the joint distribution for the process evaluated at finitely many time points is invariant to an overall timeshift~\cite{grimmett2001probability}.}. In our work, these would correspond to the activities, $X_{t}(u)$ and $X_{t}(v),$ of two users $u$ and $v$. We use the notation $X_{t-k}^{t}$ to denote the values of the stochastic process from time $t-k$ to time $t$, $X_{t-k}^{t} = (X_{t-k}, X_{t-(k-1)}, \ldots, X_{t - 1}, X_{t})$. The lag-$k$ transfer entropy~\cite{schreiber2000measuring} of $Y$ on $X$ is defined as 
\begin{align}
	\text{TE}_{Y \to X}^{(k)} &= H\left[X_{t} | X_{t-k}^{t-1}\right] - H\left[X_{t} | X_{t-k}^{t-1}, Y_{t-k}^{t-1}\right], \label{Eqn-TE}
\end{align}
where
\begin{align}
	H\left[X_{t} | X_{t-k}^{t-1}\right] = - E\left[ \log_{2} p(X_{t} | X_{t-k}^{t-1}) \right]
\end{align}
and 
\begin{align}
	H\left[X_{t} | X_{t-k}^{t-1}, Y_{t-k}^{t-1}\right] = - E\left[ \log_{2} p(X_{t} | X_{t-k}^{t-1}, Y_{t-k}^{t-1}) \right]
\end{align}
are the usual conditional entropies over the conditional (predictive) distributions $p(x_{t} | x_{t-k}^{t-1})$ and $p(x_{t} | x_{t-k}^{t-1}, y_{t-k}^{t-1})$. This formulation was originally developed in~\cite{schreiber2000measuring}, where transfer entropy was proposed as an information theoretic measure of \emph{directed} information flow. Formally, recalling that $H\left[X_{t} | X_{t-k}^{t-1}\right]$ is the uncertainty in $X_{t}$ given its values at the previous $k$ time points, and that $H\left[X_{t} | X_{t-k}^{t-1}, Y_{t-k}^{t-1}\right]$ is the uncertainty in $X_{t}$ given the joint process $\{(X_{t}, Y_{t})\}$ at the previous $k$ time points, transfer entropy measures the reduction in uncertainty of $X_{t}$ by including information about $Y_{t-k}^{t-1},$ controlling for the information in $X_{t - k}^{t-1}$. By the `conditioning reduces entropy' result~\cite{cover2012elements}
\begin{align}
	H[X | Y, Z] \leq H[X | Y],
\end{align}
we can see that transfer entropy is always non-negative, and is zero precisely when $$H\left[X_{t} | X_{t-k}^{t-1}\right] = H\left[X_{t} | X_{t-k}^{t-1}, Y_{t-k}^{t-1}\right],$$ in which case knowing the past $k$ lags of $Y_{t}$ does not reduce the uncertainty in $X_{t}$. If the transfer entropy is positive, then $\{ Y_{t}\}$ is considered causal for $\{ X_{t}\}$ in the Granger sense~\cite{granger1963economic}.

When estimating transfer entropy from finite data, we will assume that the process $\{(X_{t}, Y_{t})\}$ is jointly stationary, which gives us that
\begin{align}
	p(x_{t} | x_{t-k}^{t-1}) = p(x_{k+1} | x_{1}^{k})
\end{align}
and
\begin{align}
	p(x_{t} | x_{t-k}^{t-1}, y_{t-k}^{t-1}) = p(x_{k+1} | x_{1}^{k}, y_{1}^{k})
\end{align}
for all $t$. That is, the predictive distribution only depends on the past, not on when the past is observed. Given this assumption, we compute estimators for $p(x_{k+1} | x_{1}^{k})$ and $p(x_{k+1} | x_{1}^{k}, y_{1}^{k})$ by `counting': for each possible marginal and joint past $x_{1}^{k}$ and $(x_{1}^{k}, y_{1}^{k})$, we count the number of times a future of type $x_{k+1}$ occurs, and normalize to obtain the appropriate estimators of the one-step-ahead predictive distributions. Call these estimators $\hat{p}(x_{k+1} | x_{1}^{k})$ and $\hat{p}(x_{k+1} | x_{1}^{k}, y_{1}^{k})$. Then the plug-in estimator for the transfer entropy is
\begin{align}
	\widehat{\text{TE}}_{Y \to X}^{(k)} &= \hat{H}\left[X_{t} | X_{t-k}^{t-1}\right] - \hat{H}\left[X_{t} | X_{t-k}^{t-1}, Y_{t-k}^{t-1}\right]
\end{align}
where we use the plug-in estimators $\hat{H}\left[X_{t} | X_{t-k}^{t-1}\right]$ and $\hat{H}\left[X_{t} | X_{t-k}^{t-1}, Y_{t-k}^{t-1}\right]$ for the entropies. It is well known that the plug-in estimator for entropy is biased~\cite{paninski2003estimation}. To account for this bias, we use the Miller-Madow adjustment to the plug-in estimator~\cite{miller1955note}. For a random variable $X$ taking on finitely many values from an alphabet $\mathcal{X}$, the Miller-Madow estimator is
	\begin{align}
		\tilde{H}[X] = \hat{H}[X] + \frac{|\hat{\mathcal{X}}| - 1}{2 n}
	\end{align}
	where $|\mathcal{\hat{X}}|$ is the number of observed symbols from the alphabet $\mathcal{X}$ and $n$ was the number of samples used to estimate $\hat{H}[X].$ The definition of transfer entropy~(\ref{Eqn-TE}) can be rewritten in terms of joint entropies as
	\begin{align}
		TE_{Y \to X}^{(k)} &= H[X_t | X_{t-k}^{t-1}] - H[X_t | X_{t-k}^{t-1},Y_{t-k}^{t-1}] \\ 
		&= H[X_t,X_{t-k}^{t-1}]-H[X_{t-k}^{t-1}]-H[X_t,X_{t-k}^{t-1},Y_{t-k}^{t-1}]+H[X_{t-k}^{t-1},Y_{t-k}^{t-1}],
	\end{align}
	We then apply the Miller-Madow adjustment individually to each of the entropy terms. For example, for the first term, we have
	\begin{align}
		\tilde{H}[X_{t}, X_{t - k}^{t-1}] = \tilde{H}[X_{t - k}^{t}] = \hat{H}[X_{t-k}^{t}] + \frac{|\widehat{\mathcal{X}^{k+1}}| - 1}{2n},
	\end{align}
	where $|\widehat{\mathcal{X}^{k+1}}|$ is the number of $(k + 1)$-tuples we actually observe (of the $2^{k + 1}$ possible tuples). Doing this for each term, the overall Miller-Madow estimator for the transfer entropy is
	\begin{align}
		\widetilde{TE}_{Y \to X}^{(k)} &= \tilde{H}[X_t | X_{t-k}^{t-1}] - \tilde{H}[X_t | X_{t-k}^{t-1},Y_{t-k}^{t-1}] \\ 
		&= \tilde{H}[X_t,X_{t-k}^{t-1}]-\tilde{H}[X_{t-k}^{t-1}]-\tilde{H}[X_t,X_{t-k}^{t-1},Y_{t-k}^{t-1}]+\tilde{H}[X_{t-k}^{t-1},Y_{t-k}^{t-1}].
	\end{align}
	One possible problem with this estimator is that it can result in \emph{negative} estimates of entropies. That usually occurs when $\hat{H}$ is very small. In these cases, we set the estimator to zero.

% Do NOT remove this, even if you are not including acknowledgments.
\section*{Acknowledgments}

\nolinenumbers

%\section*{References}
% Either type in your references using
% \begin{thebibliography}{}
% \bibitem{}
% Text
% \end{thebibliography}
%
% OR
%
% Compile your BiBTeX database using our plos2009.bst
% style file and paste the contents of your .bbl file
% here.
% 
\begin{thebibliography}{10}
\providecommand{\url}[1]{\texttt{#1}}
\providecommand{\urlprefix}{URL }
\expandafter\ifx\csname urlstyle\endcsname\relax
  \providecommand{\doi}[1]{doi:\discretionary{}{}{}#1}\else
  \providecommand{\doi}{doi:\discretionary{}{}{}\begingroup
  \urlstyle{rm}\Url}\fi
\providecommand{\bibAnnoteFile}[1]{%
  \IfFileExists{#1}{\begin{quotation}\noindent\textsc{Key:} #1\\
  \textsc{Annotation:}\ \input{#1}\end{quotation}}{}}
\providecommand{\bibAnnote}[2]{%
  \begin{quotation}\noindent\textsc{Key:} #1\\
  \textsc{Annotation:}\ #2\end{quotation}}
\providecommand{\eprint}[2][]{\url{#2}}

\bibitem{cazabet2012automated}
Cazabet R, Leguistin M, Amblard F (2012) Automated community detection on
  social networks: useful? efficient? asking the users.
\newblock In: Proc. of the 4th WI\&C. pp. 6:1--6:8.
\bibAnnoteFile{cazabet2012automated}

\bibitem{girvan2002a}
Girvan M, Newman ME (2002) Community structure in social and biological
  networks.
\newblock Proceedings of the National Academy of Sciences 99: 7821--7826.
\bibAnnoteFile{girvan2002a}

\bibitem{newman2004finding}
Newman ME, Girvan M (2004) Finding and evaluating community structure in
  networks.
\newblock Phys Rev E 69: 026113.
\bibAnnoteFile{newman2004finding}

\bibitem{java2009we}
Java A, Song X, Finin T, Tseng B (2009) Why we twitter: an analysis of a
  microblogging community.
\newblock In: Advances in Web Mining and Web Usage Analysis, Springer. pp.
  118--138.
\bibAnnoteFile{java2009we}

\bibitem{nguyen2011adaptive}
Nguyen NP, Dinh TN, Xuan Y, Thai MT (2011) Adaptive algorithms for detecting
  community structure in dynamic social networks.
\newblock In: Proc. of the IEEE 2011 INFOCOM. IEEE, pp. 2282--2290.
\bibAnnoteFile{nguyen2011adaptive}

\bibitem{grabowicz2012social}
Grabowicz PA, Ramasco JJ, Moro E, Pujol JM, Eguiluz VM (2012) Social features
  of online networks: The strength of intermediary ties in online social media.
\newblock PLoS ONE 7: e29358.
\bibAnnoteFile{grabowicz2012social}

\bibitem{Holland1983}
Holland PW, Laskey KB, Leinhardt S (1983) Stochastic blockmodels: First steps.
\newblock Social networks 2: 109--137.
\bibAnnoteFile{Holland1983}

\bibitem{Aicher26062014}
Aicher C, Jacobs AZ, Clauset A (2014) Learning latent block structure in
  weighted networks.
\newblock To appear, J Compl Netw .
\bibAnnoteFile{Aicher26062014}

\bibitem{PalEtAl05}
Palla G, Der{\'e}nyi I, Farkas I, Vicsek T (2005) Uncovering the overlapping
  community structure of complex networks in nature and society.
\newblock Nature 435: 814--818.
\bibAnnoteFile{PalEtAl05}

\bibitem{Rosvall08mapsof}
Rosvall M, Bergstrom CT (2008) Maps of random walks on complex networks reveal
  community structure.
\newblock Proc Natl Acad Sci 105: 1118--1123.
\bibAnnoteFile{Rosvall08mapsof}

\bibitem{blondel2008fast}
Blondel VD, Guillaume JL, Lambiotte R, Lefebvre E (2008) Fast unfolding of
  communities in large networks.
\newblock J Stat Mech 2008: P10008.
\bibAnnoteFile{blondel2008fast}

\bibitem{LancichinettiPlos}
Lancichinetti A, Radicchi F, Ramasco JJ, Fortunato S (2011) Finding
  statistically significant communities in networks.
\newblock PLoS ONE 6: e18961.
\bibAnnoteFile{LancichinettiPlos}

\bibitem{schreiber2000measuring}
Schreiber T (2000) Measuring information transfer.
\newblock Phys Rev Lett 85: 461--464.
\bibAnnoteFile{schreiber2000measuring}

\bibitem{rossi2012conversation}
Rossi L, Magnani M (2012) Conversation practices and network structure in
  twitter.
\newblock In: Proc. of the 6th ICWSM. pp. 563--566.
\bibAnnoteFile{rossi2012conversation}

\bibitem{lim2012following}
Lim KH, Datta A (2012) Following the follower: detecting communities with
  common interests on twitter.
\newblock In: Proc. of the 23rd ACM HT. ACM, pp. 317--318.
\bibAnnoteFile{lim2012following}

\bibitem{yin2012latent}
Yin Z, Cao L, Gu Q, Han J (2012) Latent community topic analysis: integration
  of community discovery with topic modeling.
\newblock ACM Trans Intell Syst Technol 3: 63:1--63:21.
\bibAnnoteFile{yin2012latent}

\bibitem{zhao2011comparing}
Zhao WX, Jiang J, Weng J, He J, Lim EP, et~al. (2011) Comparing twitter and
  traditional media using topic models.
\newblock In: Proc. of the 33rd ECIR, Springer. pp. 338--349.
\bibAnnoteFile{zhao2011comparing}

\bibitem{michelson2010discovering}
Michelson M, Macskassy SA (2010) Discovering users' topics of interest on
  twitter: a first look.
\newblock In: Proc. of the 4th workshop on analytics for noisy unstructured
  text data. ACM, pp. 73--80.
\bibAnnoteFile{michelson2010discovering}

\bibitem{becker2011beyond}
Becker H, Naaman M, Gravano L (2011) Beyond trending topics: real-world event
  identification on twitter.
\newblock In: Proc. of the 5th ICWSM. pp. 438--441.
\bibAnnoteFile{becker2011beyond}

\bibitem{tsur2012s}
Tsur O, Rappoport A (2012) What's in a hashtag?: content based prediction of
  the spread of ideas in microblogging communities.
\newblock In: Proc. of the 5th ACM WSDM. ACM, pp. 643--652.
\bibAnnoteFile{tsur2012s}

\bibitem{conover2011political}
Conover M, Ratkiewicz J, Francisco M, Gon{\c{c}}alves B, Menczer F, et~al.
  (2011) Political polarization on twitter.
\newblock In: Proc. of the 4th ICWSM. pp. 89--96.
\bibAnnoteFile{conover2011political}

\bibitem{deitrick2013mutually}
Deitrick W, Hu W (2013) Mutually enhancing community detection and sentiment
  analysis on twitter networks.
\newblock J Data Ana and Info Proc 1: 19--29.
\bibAnnoteFile{deitrick2013mutually}

\bibitem{lim2012tweets}
Lim KH, Datta A (2012) Tweets beget propinquity: detecting highly interactive
  communities on twitter using tweeting links.
\newblock In: Proc. of the IEEE/WIC/ACM WI-IAT. IEEE, pp. 214--221.
\bibAnnoteFile{lim2012tweets}

\bibitem{kao2013talison}
Kao A, Ferng W, Poteet S, Quach L, Tjoelker R (2013) Talison-tensor analysis of
  social media data.
\newblock In: Intelligence and Security Informatics. IEEE, pp. 137--142.
\bibAnnoteFile{kao2013talison}

\bibitem{porter2009communities}
Porter MA, Onnela JP, Mucha PJ (2009) Communities in networks.
\newblock Notices of the AMS 56: 1082--1097.
\bibAnnoteFile{porter2009communities}

\bibitem{fortunato2010community}
Fortunato S (2010) Community detection in graphs.
\newblock Phys Rep 486: 75--174.
\bibAnnoteFile{fortunato2010community}

\bibitem{BaumesGKMP05}
Baumes J, Goldberg MK, Krishnamoorthy MS, Magdon-Ismail M, Preston N (2005)
  Finding communities by clustering a graph into overlapping subgraphs.
\newblock In: Proc. of the IADIS AC. pp. 97-104.
\bibAnnoteFile{BaumesGKMP05}

\bibitem{ZhaWanZha07}
Zhang S, Wang RS, Zhang XS (2007) Identification of overlapping community
  structure in complex networks using fuzzy $c$-means clustering.
\newblock Phys A 374: 483--490.
\bibAnnoteFile{ZhaWanZha07}

\bibitem{Gre07}
Gregory S (2007) An algorithm to find overlapping community structure in
  networks.
\newblock In: Proc. of the 11th PKDD. pp. 91--102.
\bibAnnoteFile{Gre07}

\bibitem{PhysRevE.77.016107}
Nepusz T, Petr\'oczi A, N\'egyessy L, Bazs\'o F (2008) Fuzzy communities and
  the concept of bridgeness in complex networks.
\newblock Phys Rev E 77: 016107.
\bibAnnoteFile{PhysRevE.77.016107}

\bibitem{Lancichinetti2009}
Lancichinetti A, Fortunato S, Kert\'{e}sz J (2009) {Detecting the overlapping
  and hierarchical community structure in complex networks}.
\newblock New J Phys 11: 033015.
\bibAnnoteFile{Lancichinetti2009}

\bibitem{PhysRevE.80.016105}
Evans TS, Lambiotte R (2009) Line graphs, link partitions, and overlapping
  communities.
\newblock Phys Rev E 80: 016105.
\bibAnnoteFile{PhysRevE.80.016105}

\bibitem{Kovacs2010}
Kov\'{a}cs IA, Palotai R, Szalay MS, Csermely P (2010) Community landscapes: an
  integrative approach to determine overlapping network module hierarchy,
  identify key nodes and predict network dynamics.
\newblock PLoS ONE 5: e12528.
\bibAnnoteFile{Kovacs2010}

\bibitem{darmon2013understanding}
Darmon D, Sylvester J, Girvan M, Rand W (2013) Predictability of user behavior
  in social media: Bottom-up v. top-down modeling.
\newblock In: ASE/IEEE Int'l Conf. on Social Computing. pp. 102--107.
\bibAnnoteFile{darmon2013understanding}

\bibitem{ver2012information}
Ver~Steeg G, Galstyan A (2012) Information transfer in social media.
\newblock In: Proc. of the 21st Inter. WWW Conf. ACM, pp. 509--518.
\bibAnnoteFile{ver2012information}

\bibitem{granger1963economic}
Granger CWJ (1963) Economic processes involving feedback.
\newblock Inform Control 6: 28--48.
\bibAnnoteFile{granger1963economic}

\bibitem{granovetter1973strength}
Granovetter MS (1973) The strength of weak ties.
\newblock Am J Sociol 78: 1360--1380.
\bibAnnoteFile{granovetter1973strength}

\bibitem{darmon2013detecting}
Darmon D, Omodei E, Flores CO, Seoane LF, Stadler K, et~al. (2013) Detecting
  communities using information flow in social networks.
\newblock In: Proc. of the CSSS, Santa Fe Institute.
\bibAnnoteFile{darmon2013detecting}

\bibitem{salton_introduction_1983}
Salton G, {McGill} MJ (1983) Introduction to modern information retrieval.
\newblock New York: {McGraw-Hill}.
\bibAnnoteFile{salton_introduction_1983}

\bibitem{romero2011influence}
Romero DM, Galuba W, Asur S, Huberman BA (2011) Influence and passivity in
  social media.
\newblock In: Machine learning and knowledge discovery in databases, Springer.
  pp. 18--33.
\bibAnnoteFile{romero2011influence}

\bibitem{meilua2003comparing}
Meil{\u{a}} M (2003) Comparing clusterings by the variation of information.
\newblock In: Learning theory and kernel machines, Springer. pp. 173--187.
\bibAnnoteFile{meilua2003comparing}

\bibitem{newman2009networks}
Newman M (2009) Networks: an introduction.
\newblock Oxford University Press.
\bibAnnoteFile{newman2009networks}

\bibitem{kitsak2010identification}
Kitsak M, Gallos LK, Havlin S, Liljeros F, Muchnik L, et~al. (2010)
  Identification of influential spreaders in complex networks.
\newblock Nature Phys 6: 888--893.
\bibAnnoteFile{kitsak2010identification}

\bibitem{grimmett2001probability}
Grimmett G, Stirzaker D (2001) Probability and random processes.
\newblock Oxford University Press.
\bibAnnoteFile{grimmett2001probability}

\bibitem{cover2012elements}
Cover TM, Thomas JA (2006) Elements of information theory.
\newblock Wiley-Interscience.
\bibAnnoteFile{cover2012elements}

\bibitem{paninski2003estimation}
Paninski L (2003) Estimation of entropy and mutual information.
\newblock Neural Comput 15: 1191--1253.
\bibAnnoteFile{paninski2003estimation}

\bibitem{miller1955note}
Miller GA (1955) Note on the bias of information estimates.
\newblock In: Quastler H, editor, Information theory in psychology II-B,
  Glencoe, Illinois: Free Press. pp. 95--100.
\bibAnnoteFile{miller1955note}

\end{thebibliography}

\end{document}

### 2015-01-29 paper-for_plos/paper.tex
Update Elisa's affiliation.

@@
 \\
-David Darmon\textsuperscript{1, *},
-Elisa Omodei\textsuperscript{2},
-Joshua Garland\textsuperscript{3},
+David Darmon\textsuperscript{1,*},
+Elisa Omodei\textsuperscript{2,3},
+Joshua Garland\textsuperscript{4},
 \\
@@
 \\
-\bf{2} LaTTiCe (CNRS, ENS, Paris 3), ISC-PIF, Paris, France
+\bf{2} LaTTiCe-CNRS, ISC-PIF, Paris, France
 \\
-\bf{3} Dept. of Computer Science, University of Colorado, Boulder, CO, United States
+\bf{3} Department d'Enginyeria Informatica i Matematiques, Universitat Rovira i Virgili, Tarragona, Spain
+\\
+\bf{4} Dept. of Computer Science, University of Colorado, Boulder, CO, United States
 \\

### 2015-04-28 paper-for_plos/paper.tex
Added cover letter with responses to reviewers.

@@
 In these complex social networks, a `community' as studied in the social network literature, can have very different meaning depending on the property of the network under study.
-% and different definitions of community such as ``whom do we interact with?" and ``with whom do we share similar interests?" can lead to very different and interesting social groups. 
 Taking into account the multifaceted nature of these networks, we claim that community detection in online social networks should also be multifaceted in order to capture all of the different and valuable viewpoints of `community.' In this paper we focus on three types of communities beyond follower-based structural communities: activity-based, topic-based, and interaction-based.
@@
 
+Thanks to Cesar Flores, Lu\'is Seoane, Kevin Stadler, Jody Wright, and Nix Barnett for their contributions to preliminary ideas related to this paper and to Michelle Girvan, William Rand, Aaron Clauset, and Ryan James for their valuable comments and suggestions.
+Finally, we would like to acknowledge the Santa Fe Institute and its Complex Systems Summer School for providing the intellectually stimulating environment where this project began.
+
 \nolinenumbers

### 2015-04-28 paper-for_plos-revised/paper.tex
Made revisions for style.

--- 2015-04-28 paper-for_plos/paper.tex
@@
 \\
-David Darmon\textsuperscript{1,*},
-Elisa Omodei\textsuperscript{2,3},
-Joshua Garland\textsuperscript{4},
+David Darmon\textsuperscript{1,*\Yinyang},
+Elisa Omodei\textsuperscript{2,3\Yinyang},
+Joshua Garland\textsuperscript{4\Yinyang},
 \\
-\bf{1} Dept. of Mathematics, University of Maryland, College Park, MD, United States
+\bf{1} Department of Mathematics, University of Maryland, College Park, Maryland, United States of America
 \\
@@
 \\
-\bf{4} Dept. of Computer Science, University of Colorado, Boulder, CO, United States
+\bf{4} Department of Computer Science, University of Colorado, Boulder, Colorado, United States of America
 \\
@@
 % Primary Equal Contribution Note
-%\Yinyang These authors contributed equally to this work.
+\Yinyang These authors contributed equally to this work.
 
@@
 
-* E-mail: ddarmon@math.umd.edu
+* E-mail: ddarmon@math.umd.edu (DD)
 \end{flushleft}
@@
 The dataset for this study consisted of the tweets of 15,000 Twitter users over a 9 week period (from April 25th to June 25th 2011).
+The network and user activity (including tweets, mentions, and hashtags) were accessed using the Twitter API.
 The users are embedded in a network collected by performing a breadth-first expansion from a random seed user.
@@
 Next we consider the distribution of community sizes across the community types.
-The complementary cumulative distribution of community sizes is given in Figure~\ref{Fig-community_size_distribution}.
+The complementary cumulative distribution of community sizes is given in Fig.~\ref{Fig-community_size_distribution}.
 Note that both axes are plotted on log-scales.
-Thus, for a fixed community size $s$, Figure~\ref{Fig-community_size_distribution} shows the proportion of communities of size greater than $s$ for each community type.
+Thus, for a fixed community size $s$, Fig.~\ref{Fig-community_size_distribution} shows the proportion of communities of size greater than $s$ for each community type.
 We see that the community distributions have longer tails for the non-structural networks, and that the interaction-based network has the longest tail.
@@
 We considered the normalized mutual information between the communities inferred from the structural network and the networks weighted with lag 1 through 6 transfer entropies, hashtag similarity, and mention, retweet, and mention-retweet activity.
-The resulting $\text{NMI}(\mathcal{C}_{i}, \mathcal{C}_{j})$ are shown in Figure~\ref{Fig-compare_coverings}.
-Note the block diagonal structure in Figure~\ref{Fig-compare_coverings}, which indicates that coverings are most similar within a question category.
+The resulting $\text{NMI}(\mathcal{C}_{i}, \mathcal{C}_{j})$ are shown in Fig.~\ref{Fig-compare_coverings}.
+Note the block diagonal structure in Fig.~\ref{Fig-compare_coverings}, which indicates that coverings are most similar within a question category.
 For example, the activity-based transfer entropy coverings are more similar to each other than to any of the other coverings.
@@
 Thus, inter-edges cross community boundaries, intra-edges lie within community boundaries, and mixed-edges lie at the borders of community boundaries.
-See Figure~\ref{Fig-edge_types} for a schematic of this edge partitioning.
+See Fig.~\ref{Fig-edge_types} for a schematic of this edge partitioning.
 
@@
 the empirical distribution over the edge weights conditioned on the edge type $t$ being one of inter, intra, and mixed.
-The densities associated with these distributions are shown in Figure~\ref{Fig-distributions_by_types}.
+The densities associated with these distributions are shown in Fig.~\ref{Fig-distributions_by_types}.
 By considering how the weights vary conditional on the edge type, we can explore whether and how each of the follower-, interaction-, activity-, and topic-based communities define functional units within the network.
@@
 
-Each \emph{column} of Figure~\ref{Fig-distributions_by_types} demonstrates how the density of weights change with the community type used to induce the partition.
+Each \emph{column} of Fig.~\ref{Fig-distributions_by_types} demonstrates how the density of weights change with the community type used to induce the partition.
 For example, the second column shows how the density of hashtag weights change based on the community partition.

### 2015-04-29 code/mutual3/compare_coverings.py
Packaging together resubmission to PLoS.

@@ -10,7 +10,7 @@ singleton_type = 'singletons'
 
 file_dir = 'coverings/{}/'.format(singleton_type)
 
-num_types = 12
+num_types = 11
 
 mis = numpy.ones((num_types, num_types))*numpy.nan
 
@@ -33,5 +33,5 @@ pylab.figure()
 pylab.imshow(mis, interpolation = 'nearest', vmin = 0, vmax = 1, cmap = pylab.cm.gray_r)#, extent = (0, num_types, num_types, 0))
 pylab.xlabel('Community Type $j$'); pylab.ylabel('Community Type $i$')
 pylab.colorbar()
-pylab.savefig('nmi_{}.pdf'.format(singleton_type))
+pylab.savefig('nmi_{}.eps'.format(singleton_type))
 # pylab.show()

### 2015-04-29 paper-for_plos-revised/revise-scripts.py

@@ -1,0 +1,15 @@
+import os
+
+original_path = '../paper-for_plos/'
+
+edit_path = '../paper-for_plos-revised/'
+
+marked_path = '../paper-for_plos-markedup/'
+
+names = ['paper.tex']
+
+
+for fname in names:
+	cmd = '/Users/daviddarmon/Documents/Reference/L/latex/latexdiff/latexdiff {}{} {}{} > {}{}'.format(original_path, fname, edit_path, fname, marked_path, fname)
+	
+	os.system(cmd)
